### 2015-01-21 RMTW/Assignment_1/assignment_1.tex
Assignment 1 added, git ignore added

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: ienne $
%  $Date: 1995/09/15 15:20:59 $
%  $Revision: 1.4 $
%

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{assignment_1}
\usepackage{times}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{\LaTeX\ Author Guidelines 
       for {\boldmath $8.5 \times 11$-Inch} Proceedings Manuscripts}

\author{Paolo Ienne\\
Swiss Federal Institute of Technology\\ Microcomputing Laboratory \\ IN-F 
Ecublens, 1015 Lausanne, Switzerland\\ Paolo.Ienne@di.epfl.ch\\
% For a paper whose authors are all at the same institution, 
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'', 
% just like the second author.
\and
Second Author\\
Institution2\\
First line of institution2 address\\ Second line of institution2 address\\ 
SecondAuthor@institution2.com\\
}

\maketitle
\thispagestyle{empty}

\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top 
   of the left-hand column, below the author and affiliation 
   information. Use the word ``Abstract'' as the title, in 12-point 
   Times, boldface type, centered relative to the column, initially 
   capitalized. The abstract is to be in 10-point, single-spaced type. 
   The abstract may be up to 3 inches (7.62 cm) long. Leave two blank 
   lines after the Abstract, then begin the main text. 
\end{abstract}

%------------------------------------------------------------------------- 
\Section{Introduction}

Please follow the steps outlined below when submitting your 
manuscript to the IEEE Computer Society Press. Note there have 
been some changes to the measurements from previous instructions.

%------------------------------------------------------------------------- 
\Section{Instructions}

Please read the following carefully.

%------------------------------------------------------------------------- 
\SubSection{Language}

All manuscripts must be in English.

%------------------------------------------------------------------------- 
\SubSection{Printing your paper}

Print your properly formatted text on high-quality, $8.5 \times 11$-inch 
white printer paper. A4 paper is also acceptable, but please leave the 
extra 0.5 inch (1.27 cm) at the BOTTOM of the page.

%------------------------------------------------------------------------- 
\SubSection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be 
kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches 
(22.54 cm) high. Do not write or print anything outside the print area. 
Number your pages lightly, in pencil, on the upper right-hand corners of 
the BACKS of the pages (for example, 1/10, 2/10, or 1 of 10, 2 of 10, and 
so forth). Please do not write on the fronts of the pages, nor on the 
lower halves of the backs of the pages.

%------------------------------------------------------------------------ 
\SubSection{Formatting your paper}

All text must be in a two-column format. The total allowable width of 
the text area is 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm) 
high. Columns are to be 3-1/4 inches (8.25 cm) wide, with a 5/16 inch 
(0.8 cm) space between them. The main title (on the first page) should 
begin 1.0 inch (2.54 cm) from the top edge of the page. The second and 
following pages should begin 1.0 inch (2.54 cm) from the top edge. On 
all pages, the bottom margin should be 1-1/8 inches (2.86 cm) from the 
bottom edge of the page for $8.5 \times 11$-inch paper; for A4 paper, 
approximately 1-5/8 inches (4.13 cm) from the bottom edge of the page.

%------------------------------------------------------------------------- 
\SubSection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is 
available on your word processor, please use the font closest in 
appearance to Times that you have access to.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of 
the first page. The title should be in Times 14-point, boldface type. 
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and 
adverbs; do not capitalize articles, coordinate conjunctions, or 
prepositions (unless the title begins with such a word). Leave two blank 
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title 
and printed in Times 12-point, non-boldface type. This information is to 
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use 
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6 
inch or 0.422 cm). Make sure your text is fully justified---that is, 
flush left and flush right. Please do not place any additional blank 
lines between paragraphs. Figure and table captions should be 10-point 
Helvetica boldface type as in
\begin{figure}[h]
   \caption{Example of caption.}
\end{figure}

\noindent Long captions should be set as in 
\begin{figure}[h] 
   \caption{Example of long caption requiring more than one line. It is 
     not typed centered but aligned on both sides and indented with an 
     additional margin on both sides of 1~pica.}
\end{figure}

\noindent Callouts should be 9-point Helvetica, non-boldface type. 
Initially capitalize only the first word of section titles and first-, 
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction}) 
should be Times 12-point boldface, initially capitalized, flush left, 
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, {\elvbf 1.1. Database elements}) 
should be Times 11-point boldface, initially capitalized, flush left, 
with one blank line before, and one after. If you require a third-order 
heading (we discourage it), use 10-point Times, boldface, initially 
capitalized, flush left, preceded by one blank line, followed by a period 
and your text on the same line.

%------------------------------------------------------------------------- 
\SubSection{Footnotes}

Please use footnotes sparingly%
\footnote
   {%
     Or, better still, try to avoid footnotes altogether.  To help your 
     readers, avoid using footnotes altogether and include necessary 
     peripheral observations in the text (within parentheses, if you 
     prefer, as in this sentence).
   }
and place them at the bottom of the column on the page on which they are 
referenced. Use Times 8-point type, single-spaced.

%------------------------------------------------------------------------- 
\SubSection{References}

List and number all bibliographical references in 9-point Times, 
single-spaced, at the end of your paper. When referenced in the text, 
enclose the citation number in square brackets, for example~\cite{ex1}. 
Where appropriate, include the name(s) of editors of referenced books.

%------------------------------------------------------------------------- 
\SubSection{Illustrations, graphs, and photographs}

All graphics should be centered. Your artwork must be in place in the 
article (preferably printed as part of the text rather than pasted up). 
If you are using photographs and are able to have halftones made at a 
print shop, use a 100- or 110-line screen. If you must use plain photos, 
they must be pasted onto your manuscript. Use rubber cement to affix the 
images in place. Black and white, clear, glossy-finish photos are 
preferable to color. Supply the best quality photographs and 
illustrations possible. Penciled lines and very fine lines do not 
reproduce well. Remember, the quality of the book cannot be better than 
the originals provided. Do NOT use tape on your pages!

%------------------------------------------------------------------------- 
\SubSection{Color}

The use of color on interior pages (that is, pages other
than the cover) is prohibitively expensive. We publish interior pages in 
color only when it is specifically requested and budgeted for by the 
conference organizers. DO NOT SUBMIT COLOR IMAGES IN YOUR 
PAPERS UNLESS SPECIFICALLY INSTRUCTED TO DO SO.

%------------------------------------------------------------------------- 
\SubSection{Symbols}

If your word processor or typewriter cannot produce Greek letters, 
mathematical symbols, or other graphical elements, please use 
pressure-sensitive (self-adhesive) rub-on symbols or letters (available 
in most stationery stores, art stores, or graphics shops).

%------------------------------------------------------------------------ 
\SubSection{Copyright forms}

You must include your signed IEEE copyright release form when you submit 
your finished paper. We MUST have this form before your paper can be 
published in the proceedings.

%------------------------------------------------------------------------- 
\SubSection{Conclusions}

Please direct any questions to the production editor in charge of these 
proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or 
Fax (714) 761-1784.

%------------------------------------------------------------------------- 
\nocite{ex1,ex2}
\bibliographystyle{assignment_1}
\bibliography{assignment_1}

\end{document}

### 2015-01-21 IEEE_CS_Latex/latex8.tex
changed base template to include both the authors. Reflected these changes in assignment_1

--- 2015-01-21 RMTW/Assignment_1/assignment_1.tex
@@
 %
-%  $Author: ienne $
-%  $Date: 1995/09/15 15:20:59 $
-%  $Revision: 1.4 $
+%  $Author: John Burchell & William Granli $
+%  $Date: 2015/01/21 15:20:59 $
+%  $Revision: 1.0
 %
 
-\documentclass[times, 10pt,twocolumn]{article} 
-\usepackage{assignment_1}
+\documentclass[times, 10pt,twocolumn]{IEEEtran} 
+\usepackage{latex8}
 \usepackage{times}
@@
 
-\title{\LaTeX\ Author Guidelines 
-       for {\boldmath $8.5 \times 11$-Inch} Proceedings Manuscripts}
+\title{Title of the document here}
 
-\author{Paolo Ienne\\
-Swiss Federal Institute of Technology\\ Microcomputing Laboratory \\ IN-F 
-Ecublens, 1015 Lausanne, Switzerland\\ Paolo.Ienne@di.epfl.ch\\
-% For a paper whose authors are all at the same institution, 
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'', 
-% just like the second author.
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\ Second line of institution2 address\\ 
-SecondAuthor@institution2.com\\
+% author names and affiliations
+\author{\IEEEauthorblockN{
+  John Burchell\IEEEauthorrefmark{1} and
+  William Granli\IEEEauthorrefmark{1}}
+
+  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}
+
 }
@@
 \nocite{ex1,ex2}
-\bibliographystyle{assignment_1}
-\bibliography{assignment_1}
+\bibliographystyle{latex8}
+\bibliography{latex8}
 

### 2015-01-21 RMTW/Assignment_1/assignment_1.tex
changed base template to include both the authors. Reflected these changes in assignment_1

@@
 
-\documentclass[times, 10pt,twocolumn]{article} 
-\usepackage{assignment_1}
+\documentclass[times, 10pt,twocolumn]{IEEEtran} 
+\usepackage{latex8}
 \usepackage{times}
@@
 
-\title{\LaTeX\ Author Guidelines 
-       for {\boldmath $8.5 \times 11$-Inch} Proceedings Manuscripts}
+\title{Title of the document here}
 
-\author{Paolo Ienne\\
-Swiss Federal Institute of Technology\\ Microcomputing Laboratory \\ IN-F 
-Ecublens, 1015 Lausanne, Switzerland\\ Paolo.Ienne@di.epfl.ch\\
-% For a paper whose authors are all at the same institution, 
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'', 
-% just like the second author.
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\ Second line of institution2 address\\ 
-SecondAuthor@institution2.com\\
+% author names and affiliations
+\author{\IEEEauthorblockN{
+  John Burchell\IEEEauthorrefmark{1} and
+  William Granli\IEEEauthorrefmark{1}}
+
+  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}
+
 }
-
 \maketitle

### 2015-01-23 rmtw/assignment_1/assignment_1.tex
Draft of introduction

--- 2015-01-21 RMTW/Assignment_1/assignment_1.tex
@@
 
-Please follow the steps outlined below when submitting your 
-manuscript to the IEEE Computer Society Press. Note there have 
-been some changes to the measurements from previous instructions.
+1. Statement of the problem
+  Measuring the inherent readability of various programming languages. 
+2. Existing literature
+  No previous studies have compared the readability of different programming languages.
+There are however existing papers that explore the concept of readability.
+\cite{buse2010learning} talks about readability and presents a metric system to automatically measure readability.
+\cite{posnett2011simpler} build on \cite{buse2010learning}'s concept to provide a simpler and more accessible metric system.
+\cite{hansen2013makes} focus on what makes code hard to read and presents those factors.
+3. Why is it important? 
+1, 4 and 8
+
+Industry: To compare code of different language to be able to prioritize them. 
+Academia: To conduct more studies on the area which compare different languages.
 
 %------------------------------------------------------------------------- 
-\Section{Instructions}
+\Section{Purpose of the Study}
 
-Please read the following carefully.
+*Purpose statement (concise  and clear)  leading into  RQ(s)
+ -i.e.  describe  the purpose of  your  survey/questionnaire
 
 %------------------------------------------------------------------------- 
-\SubSection{Language}
-
-All manuscripts must be in English.
+\SubSection{Research Question}
+*State a clear and concise main  research  question  that  will  be  investigated
+*State another one or  two sub research  questions related to  the main  RQ.
 
 %------------------------------------------------------------------------- 
-\SubSection{Printing your paper}
+\SubSection{Methodology}
 
-Print your properly formatted text on high-quality, $8.5 \times 11$-inch 
-white printer paper. A4 paper is also acceptable, but please leave the 
-extra 0.5 inch (1.27 cm) at the BOTTOM of the page.
+* Describe  and explain the research  strategy (i.e.  Survey/Questionnaire)
+and investigation methods that  will  be  used  for the study.  Motivate  your  
+choice  of  survey/questionnaire  using relevant  references.
+* Describe  data  collection  procedures, sampling  method(s),  number  of  
+subjects, response  rate  etc.
+* Create  questions for your  survey  (include  the questions in  your  report)
+* Describe  the population  and size  of  population
+* Describe  and motive  method  for analyzing the data
+* Discuss validity  threats
 
 %-------------------------------------------------------------------------
-\SubSection{Margins and page numbering}
 
-All printed material, including text, illustrations, and charts, must be 
-kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches 
-(22.54 cm) high. Do not write or print anything outside the print area. 
-Number your pages lightly, in pencil, on the upper right-hand corners of 
-the BACKS of the pages (for example, 1/10, 2/10, or 1 of 10, 2 of 10, and 
-so forth). Please do not write on the fronts of the pages, nor on the 
-lower halves of the backs of the pages.
-
-%------------------------------------------------------------------------ 
-\SubSection{Formatting your paper}
-
-All text must be in a two-column format. The total allowable width of 
-the text area is 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm) 
-high. Columns are to be 3-1/4 inches (8.25 cm) wide, with a 5/16 inch 
-(0.8 cm) space between them. The main title (on the first page) should 
-begin 1.0 inch (2.54 cm) from the top edge of the page. The second and 
-following pages should begin 1.0 inch (2.54 cm) from the top edge. On 
-all pages, the bottom margin should be 1-1/8 inches (2.86 cm) from the 
-bottom edge of the page for $8.5 \times 11$-inch paper; for A4 paper, 
-approximately 1-5/8 inches (4.13 cm) from the bottom edge of the page.
-
-%------------------------------------------------------------------------- 
-\SubSection{Type-style and fonts}
-
-Wherever Times is specified, Times Roman may also be used. If neither is 
-available on your word processor, please use the font closest in 
-appearance to Times that you have access to.
-
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of 
-the first page. The title should be in Times 14-point, boldface type. 
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and 
-adverbs; do not capitalize articles, coordinate conjunctions, or 
-prepositions (unless the title begins with such a word). Leave two blank 
-lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title 
-and printed in Times 12-point, non-boldface type. This information is to 
-be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use 
-double-spacing. All paragraphs should be indented 1 pica (approx. 1/6 
-inch or 0.422 cm). Make sure your text is fully justified---that is, 
-flush left and flush right. Please do not place any additional blank 
-lines between paragraphs. Figure and table captions should be 10-point 
-Helvetica boldface type as in
-\begin{figure}[h]
-   \caption{Example of caption.}
-\end{figure}
-
-\noindent Long captions should be set as in 
-\begin{figure}[h] 
-   \caption{Example of long caption requiring more than one line. It is 
-     not typed centered but aligned on both sides and indented with an 
-     additional margin on both sides of 1~pica.}
-\end{figure}
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type. 
-Initially capitalize only the first word of section titles and first-, 
-second-, and third-order headings.
-
-FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction}) 
-should be Times 12-point boldface, initially capitalized, flush left, 
-with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS. (For example, {\elvbf 1.1. Database elements}) 
-should be Times 11-point boldface, initially capitalized, flush left, 
-with one blank line before, and one after. If you require a third-order 
-heading (we discourage it), use 10-point Times, boldface, initially 
-capitalized, flush left, preceded by one blank line, followed by a period 
-and your text on the same line.
-
-%------------------------------------------------------------------------- 
-\SubSection{Footnotes}
-
-Please use footnotes sparingly%
-\footnote
-   {%
-     Or, better still, try to avoid footnotes altogether.  To help your 
-     readers, avoid using footnotes altogether and include necessary 
-     peripheral observations in the text (within parentheses, if you 
-     prefer, as in this sentence).
-   }
-and place them at the bottom of the column on the page on which they are 
-referenced. Use Times 8-point type, single-spaced.
-
-%------------------------------------------------------------------------- 
-\SubSection{References}
-
-List and number all bibliographical references in 9-point Times, 
-single-spaced, at the end of your paper. When referenced in the text, 
-enclose the citation number in square brackets, for example~\cite{ex1}. 
-Where appropriate, include the name(s) of editors of referenced books.
-
-%------------------------------------------------------------------------- 
-\SubSection{Illustrations, graphs, and photographs}
-
-All graphics should be centered. Your artwork must be in place in the 
-article (preferably printed as part of the text rather than pasted up). 
-If you are using photographs and are able to have halftones made at a 
-print shop, use a 100- or 110-line screen. If you must use plain photos, 
-they must be pasted onto your manuscript. Use rubber cement to affix the 
-images in place. Black and white, clear, glossy-finish photos are 
-preferable to color. Supply the best quality photographs and 
-illustrations possible. Penciled lines and very fine lines do not 
-reproduce well. Remember, the quality of the book cannot be better than 
-the originals provided. Do NOT use tape on your pages!
-
-%------------------------------------------------------------------------- 
-\SubSection{Color}
-
-The use of color on interior pages (that is, pages other
-than the cover) is prohibitively expensive. We publish interior pages in 
-color only when it is specifically requested and budgeted for by the 
-conference organizers. DO NOT SUBMIT COLOR IMAGES IN YOUR 
-PAPERS UNLESS SPECIFICALLY INSTRUCTED TO DO SO.
-
-%------------------------------------------------------------------------- 
-\SubSection{Symbols}
-
-If your word processor or typewriter cannot produce Greek letters, 
-mathematical symbols, or other graphical elements, please use 
-pressure-sensitive (self-adhesive) rub-on symbols or letters (available 
-in most stationery stores, art stores, or graphics shops).
-
-%------------------------------------------------------------------------ 
-\SubSection{Copyright forms}
-
-You must include your signed IEEE copyright release form when you submit 
-your finished paper. We MUST have this form before your paper can be 
-published in the proceedings.
-
-%------------------------------------------------------------------------- 
-\SubSection{Conclusions}
-
-Please direct any questions to the production editor in charge of these 
-proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or 
-Fax (714) 761-1784.
-
-%------------------------------------------------------------------------- 
 \nocite{ex1,ex2}

### 2015-01-23 rmtw/assignment_1/assignment_1.tex
Added sources
Finished draft of introduction

@@
   Measuring the inherent readability of various programming languages. 
+  \newline \newline
 2. Existing literature
@@
 \cite{hansen2013makes} focus on what makes code hard to read and presents those factors.
+  \newline \newline
 3. Why is it important?
-1, 4 and 8
+\cite{aggarwal2002integrated} talks about code maintainability and mentions readability as a factor related to maintainability.
 
-Industry: To compare code of different language to be able to prioritize them. 
-Academia: To conduct more studies on the area which compare different languages.
+\cite{elshoff1982improving} also talks about readability and how it impacts maintainability.
+\cite{elshoff1982improving} brings up specific coding standards/conventions/practices to show differences in readability.
+
+\textbf{Industry}: To compare code of different language to be able to prioritize them. \\
+\textbf{Academia}: To conduct more studies on the area which compare different languages. \\
+To determine which languages are most suited for academic teaching. (When other attributes of programming languages are not constraints).
 
@@
 
-\nocite{ex1,ex2}
 \bibliographystyle{assignment_1}

### 2015-01-23 rmtw/assignment_1/assignment_1.tex
Started writing intro

@@
 \Section{Introduction}
+Comparisons between programming languages are difficult to perform, due to characteristical differences between languages, such as syntax.
+One aspect of code is its readability, which in turn is a determining factor of a piece of software's quality and maintainability \cite{aggarwal2002integrated, elshoff1982improving}.
+Buse \& Westley define readability as ``a property that influences how easily a given piece of code can be read and understood'' \cite{buse2010learning}.
+Existing studies related to the concept of code readability focus on differences between specific languages, which can be seen in \cite{buse2010learning}.
+Buse \& Westley introduce a metrics system for measuring the readability of code, and Java is the language of choice in the study \cite{buse2010learning}.
+Buse \& Westley also discuss readability and its impact on programming language design, but they do not explore the readability differences between languages \cite{buse2010learning}.
+Posnett et al.
+\cite{posnett2011simpler} have further developed Buse \& Westley's metrics model to provide a simpler and more practical model which builds on size metrics as well as Halstead metrics \cite{halstead1977elements}.
 
-1. Statement of the problem
-  Measuring the inherent readability of various programming languages. 
-  \newline \newline
 2. Existing literature
@@
 \cite{hansen2013makes} focus on what makes code hard to read and presents those factors.
-  \newline \newline
  3. Why is it important?
@@
 \textbf{Industry}: To compare code of different language to be able to prioritize them. \\
+Further studies can be conducted to see if there is a correlation between popularity of projects and the readability of the langauage(s) used in the project. \\
 \textbf{Academia}: To conduct more studies on the area which compare different languages. \\

### 2015-01-26 rmtw/assignment_1/assignment_1.tex
Finished first version of intro

@@
 \Section{Introduction}
-Comparisons between programming languages are difficult to perform, due to characteristical differences between languages, such as syntax.
+%Problem and definition
+Comparisons between programming languages are difficult to perform, due to inherent differences between languages, such as syntax.
 One aspect of code is its readability, which in turn is a determining factor of a piece of software's quality and maintainability \cite{aggarwal2002integrated, elshoff1982improving}.
 Buse \& Westley define readability as ``a property that influences how easily a given piece of code can be read and understood'' \cite{buse2010learning}.
-Existing studies related to the concept of code readability focus on differences between specific languages, which can be seen in \cite{buse2010learning}.
+\newline
+
+%%Existing literature
+Existing studies in the field focus on readability within of different coding styles for a set language, which can be seen in for example \cite{buse2010learning}.
 Buse \& Westley introduce a metrics system for measuring the readability of code, and Java is the language of choice in the study \cite{buse2010learning}.
@@
 \cite{posnett2011simpler} have further developed Buse \& Westley's metrics model to provide a simpler and more practical model which builds on size metrics as well as Halstead metrics \cite{halstead1977elements}.
+Hanen et al.
+have presented a study in the field which aims to identify details in code which makes it hard to read and the main focus is put on syntactical elements such as indentation or curly brackets \cite{hansen2013makes}.
+Even though direct comparisons between languages were not presented in the study \cite{hansen2013makes}, conclusions related to this can be drawn thanks to the fact that these syntactical elements only exist in some languages.
+\newline
 
-2. Existing literature
-  No previous studies have compared the readability of different programming languages.
-There are however existing papers that explore the concept of readability.
-\cite{buse2010learning} talks about readability and presents a metric system to automatically measure readability.
-\cite{posnett2011simpler} build on \cite{buse2010learning}'s concept to provide a simpler and more accessible metric system.
-\cite{hansen2013makes} focus on what makes code hard to read and presents those factors.
- 3. Why is it important?
-\cite{aggarwal2002integrated} talks about code maintainability and mentions readability as a factor related to maintainability.
-
-\cite{elshoff1982improving} also talks about readability and how it impacts maintainability.
-\cite{elshoff1982improving} brings up specific coding standards/conventions/practices to show differences in readability.
+The importance of code readability may be overlooked, since it does not directly affect runtime performance.
+Aggarwal et al., however claim that code's readability impacts it's maintainability \cite{aggarwal2002integrated}.
+This claim is also supported by \cite{elshoff1982improving} et al.
+who also introduce examples of certain coding practices that are more readable and maintainable than others \cite{elshoff1982improving}.
+\newline
 

### 2015-01-26 rmtw/assignment_1/assignment_1.tex
First draft of the purpose section

@@
 
-*Purpose statement (concise  and clear)  leading into  RQ(s)
- -i.e.  describe  the purpose of  your  survey/questionnaire
+%Introduction, specifying why this is urgent, needed etc from the notes above
+
+ The purpose of this survey study is therefore to test the theory that the readability differences between computer programming languages affects the given languages suitability for teaching.
+
+ The Independent variables will be defined as the experience, age, preferred language, least preferred language and the working language of the participant.
+The dependent variables, appeal and suitability, will highlight the relationship between the independent and dependent variables.
+
+ The survey data will be collected from professionals, teachers, students and hobbyists via a series of on-line surveys.
+The respondents will then be asked to review a series of code snippets from popular languages and will be subsequently asked to rate their readability.
+
+ The data will highlight the readability of the languages and combined with their roles will allow us to make suggestions as to where these languages would be most suitable.
 
@@
 
+What are the measurable differences in readability between programming languages.
+
+How do the measurable differences between languages correlate to their use in academia for teaching?
+
+How do the measurable differences between languages correlate to the popularity of the language 
 %------------------------------------------------------------------------- 

### 2015-01-26 rmtw/assignment_1/assignment_1.tex
New Draft of Purpose

@@
 
- The purpose of this survey study is therefore to test the theory that the readability differences between computer programming languages affects the given languages suitability for teaching.
+Both industry and academia face the problem of maintainability.
+As stated previously, many times the readability of code affects the codes maintainability.
+This study could help some in industry to pick languages for certain tasks for maintainability reasons alone.
+Further studies could be conducted by to determine if there is a correlation between the popularity of projects and the readability of their languages.
+Furthermore, academia would be interested in which languages are more popular and useful for learning.
+By further investigating the design of the programming languages themselves, future languages which are developed could build upon the success of those which came before them.
+\newline
+The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages.
+With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
+\newline
 
 The Independent variables will be defined as the experience, age, preferred language, least preferred language and the working language of the participant.
-The dependent variables, appeal and suitability, will highlight the relationship between the independent and dependent variables.
+The dependent variable in this example will be the readability of the language.
+\newline
 
@@
 The respondents will then be asked to review a series of code snippets from popular languages and will be subsequently asked to rate their readability.
-
- The data will highlight the readability of the languages and combined with their roles will allow us to make suggestions as to where these languages would be most suitable.
+\newline
 

### 2015-01-26 rmtw/assignment_1/assignment_1.tex
Changes to assignment_1, started notes on methodology

@@
 \newline
-The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages.
+The purpose of this survey study is therefore to find what are the differences in readability between five common and well known programming languages.
 With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
@@
 
-The Independent variables will be defined as the experience, age, preferred language, least preferred language and the working language of the participant.
+The Independent variables will be defined as the experience, occupation, preferred language, least preferred language and the working language of the participant.
 The dependent variable in this example will be the readability of the language.
@@
 choice  of  survey/questionnaire  using relevant  references.
+
+The main purpose of our study is to discover differences between the perceived readability of code.
+To discover an answer to this question, we would likely collect data and opinions from a broad population.
+As such, we most likely need to perform a research survey.
+This is reinforced by Easterbrook et.
+al \cite{easterbrook2008selecting} who stated ``Survey research is used to identify the characteristics of a broad population of individuals''.
+
+ case-control design - ``asks each participant about several related issues in 
+order to establish whether a correlation exists between them,'' \cite{easterbrook2008selecting}
+
+We will use a survey/questionnaire to collect the data.
+Sampling - ID a small subset of the entire population
+
 * Describe  data  collection  procedures, sampling  method(s),  number  of  
 subjects, response  rate  etc.
+
+Random sampling from 200 people(guess). Sample 10\%, collect online via survey, Response rate of 15/20 (75\%)
+
+Sampling bias - What we might face, how we overcome. State which threats and how they were minimised
+
 * Create  questions for your  survey  (include  the questions in  your  report)
+%Table goes here
 * Describe  the population  and size  of  population
+
+The population will be software developers in the SEM program.
+This includes teachers, students, professionals and hobbyists.
+Lets say the sample is 20 persons from the whole of SEM, 1st, 2nd, 3rd and staff.
+
+\cite{easterbrook2008selecting} - ``A major challenge in survey research is to control for sampling bias'' \& `` the respondents to 
+the survey may not be representative of the target population. ''
+
 * Describe  and motive  method  for analyzing the data
+
 * Discuss validity  threats
+  Sampling Bias ?
 

### 2015-01-26 rmtw/assignment_1/assignment_1.tex
Made a teebel

--- 2015-01-26 rmtw/assignment_1/assignment_1.tex
@@
 who also introduce examples of certain coding practices that are more readable and maintainable than others \cite{elshoff1982improving}.
-\newline
-
-\textbf{Industry}: To compare code of different language to be able to prioritize them. \\
-Further studies can be conducted to see if there is a correlation between popularity of projects and the readability of the langauage(s) used in the project. \\
-\textbf{Academia}: To conduct more studies on the area which compare different languages. \\
-To determine which languages are most suited for academic teaching. (When other attributes of programming languages are not constraints).
 
@@
 \newline
+
 The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages.
@@
 \SubSection{Research Question}
-*State a clear and concise main  research  question  that  will  be  investigated
-*State another one or  two sub research  questions related to  the main  RQ.
+This study has been designed with one main research question in mind:
+\begin{itemize}
+\item \textit{RQ1:} What are the measurable differences in readability between programming languages?
+\end{itemize}
 
-What are the measurable differences in readability between programming languages.
+The results of RQ1 will then be used to answer the following two sub research questions. 
+\begin{itemize}
+\item \textit{SRQ1}: How do the measurable differences between languages correlate to their use in academia for teaching?
+\item \textit{SRQ2}: How do the measurable differences between languages correlate to the popularity of the language?
+\end{itemize}
 
-How do the measurable differences between languages correlate to their use in academia for teaching?
-
-How do the measurable differences between languages correlate to the popularity of the language 
+\begin{tabular}{| l | r | c |}
+	\hline
+	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
+	Occupation & RQ1, SQ1 & \\ \hline
+	Experience & RQ1, SQ1 & \\ \hline
+	Preferred Language & RQ1, SQ2 & \\ \hline
+	Least Preferred Language & RQ1, SQ2& \\  \hline
+	Working Language & RQ1, SQ2 & \\ 
+	\hline
+	\end{tabular}
 %------------------------------------------------------------------------- 
-\SubSection{Methodology}
+\Section{Methodology}
 
@@
 
+\textbf{Industry}: To compare code of different language to be able to prioritize them. \\
+Further studies can be conducted to see if there is a correlation between popularity of projects and the readability of the langauage(s) used in the project. \\
+\textbf{Academia}: To conduct more studies on the area which compare different languages. \\
+To determine which languages are most suited for academic teaching. (When other attributes of programming languages are not constraints).
+
 \bibliographystyle{assignment_1}

### 2015-01-27 rmtw/assignment_1/assignment_1.tex

--- 2015-01-26 rmtw/assignment_1/assignment_1.tex
@@
 \newline
+
+The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages.
+With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
+
 The purpose of this survey study is therefore to find what are the differences in readability between five common and well known programming languages.
 With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
+
 \newline

### 2015-01-28 rmtw/assignment_1/assignment_1.tex
fixed compilation error
Started methodology section

@@
 With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
+\newline
 
@@
 With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
-
 \newline
@@
 \Section{Methodology}
+The main purpose of this study is to discover differences in the perceived readability of code.
+The study will be carried out in three phases.
+In phase 1, we will identify the target population.
+In phase 2, the survey will be designed and carried out.
+In phase 3, the results will be analysed.
+The investigation method will be in the form of a questionnaire.
+The main argument for the questionnaire is that the survey must be distributed to a large amount of people.
+A quantitative is also well-suited for this study since there are no existing publications that explore readability differences between languages.
+
+\SubSection{Identifying the Population}
+As mentioned before, the goal of this study is to identify the inherent differences in readability of programming languages.
+To research this, a broad population is required, since there may be strong correlation between the perception of readability and the previously defined independent variables.
+As such, a research survey will be conducted.
+This reasoning is reinforced by Easterbrook et al.
+\cite{easterbrook2008selecting} who state ``Survey research is used to identify the characteristics of a broad population of individuals''.
 
@@
 choice  of  survey/questionnaire  using relevant  references.
+\newline
 
-The main purpose of our study is to discover differences between the perceived readability of code.
-To discover an answer to this question, we would likely collect data and opinions from a broad population.
-As such, we most likely need to perform a research survey.
-This is reinforced by Easterbrook et.
-al \cite{easterbrook2008selecting} who stated ``Survey research is used to identify the characteristics of a broad population of individuals''.
+\SubSection{Questionnaire}
+Blabla
 
- case-control design - ``asks each participant about several related issues in 
-order to establish whether a correlation exists between them,'' \cite{easterbrook2008selecting}
+\SubSection{Results Analysis}
 
@@
 Sampling - ID a small subset of the entire population
+\newline
 
@@
 subjects, response  rate  etc.
+\newline
 
 Random sampling from 200 people(guess). Sample 10\%, collect online via survey, Response rate of 15/20 (75\%)
+\newline
 
 Sampling bias - What we might face, how we overcome. State which threats and how they were minimised
+\newline
 
@@
 %Table goes here
+\newline
+
 * Describe  the population  and size  of  population
-
+\newline
 The population will be software developers in the SEM program.
@@
 Lets say the sample is 20 persons from the whole of SEM, 1st, 2nd, 3rd and staff.
-
+\newline
 \cite{easterbrook2008selecting} - ``A major challenge in survey research is to control for sampling bias'' \& `` the respondents to 
 the survey may not be representative of the target population. ''
+\newline
 
 * Describe  and motive  method  for analyzing the data
+\newline
 
@@
   Sampling Bias ?
+
+\SubSection{Literature Review}
+The first phase will include a literature review.
+The main goal is to review previously published papers which are related to code readability.
+The existing studies will serve as a foundation for our study, as the goal of our study is not to further develop or research code readability, but compare readability between languages (using academia's existing definition of readability).
+The review will also serve as a base for the second phase, where the target population will be decided.
+\newline
+
+In phase 1, an initial literature review will be conducted. The aim is to cover previously published studies to be able to provide a study which is purposeful for academia.
 

### 2015-02-05 rmtw/assignment_1/assignment_1.tex
Meth

--- 2015-01-26 rmtw/assignment_1/assignment_1.tex
@@
 
-The Independent variables will be defined as the experience, age, preferred language, least preferred language and the working language of the participant.
+The purpose of this survey study is therefore to find what are the differences in readability between five common and well known programming languages.
+With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
+\newline
+
+The Independent variables will be defined as the experience, occupation, preferred language, least preferred language and the working language of the participant.
 The dependent variable in this example will be the readability of the language.
@@
 
+%------------------------------------------------------------------------- 
+\Section{Methodology}
+The main purpose of this study is to discover differences in the perceived readability of code.
+The study will be carried out in three phases.
+In phase 1, we will identify the target population.
+In phase 2, the survey will be designed and carried out.
+In phase 3, the results of the survey will be analysed.
+The investigation method will be in the form of a questionnaire.
+The main argument for the questionnaire is that the survey must be distributed to a large amount of people.
+A quantitative is also well-suited for this study since there are no existing publications that explore readability differences between languages.
+
+\SubSection{Identifying the Population}
+As mentioned before, the goal of this study is to identify the inherent differences in readability of programming languages.
+To research this, a broad population is required, to avoid results influenced by a possible correlation between the perception of readability and the previously defined independent variables.
+As such, a research survey has been conducted.
+This reasoning is reinforced by Easterbrook et al.
+\cite{easterbrook2008selecting} who state ``Survey research is used to identify the characteristics of a broad population of individuals''.
+\newline
+
+The population of this survey is the students of the Software Engineering and Management programme (SEM) at Gothenburg University.
+The industry is left out of the population since they are more likely to have a lot of experience with certain languages which may cause them to be biased towards that language.
+The SEM program was chosen due to it being accessible for the researchers.
+\newline
+
+\SubSection{Questionnaire Design}
+TODO: 
+Write briefly about why we chose the languages we chose. (different paradigms etc)
+Write some formal stuff about how the survey was designed. (Shit about open-ended questions etc.)
+Write which tool was used etc.
+
+Write how the questionnaire was distributed. (I.e. facebook pages of all 3 years):::::
+Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting} and thus the questionnaire will be distributed to the Facebook page of all three year's.
+
+\SubSection{Results Analysis}
+TODO:
+* Describe  and motive  method  for analyzing the data
+
+\SubSection{Threats to Validity}
+Bias in languages and experience
+
+\bibliographystyle{assignment_1}
+\bibliography{assignment_1}
+
 \begin{tabular}{| l | r | c |}
@@
 	\end{tabular}
-%------------------------------------------------------------------------- 
-\Section{Methodology}
-
-* Describe  and explain the research  strategy (i.e.  Survey/Questionnaire)
-and investigation methods that  will  be  used  for the study.  Motivate  your  
-choice  of  survey/questionnaire  using relevant  references.
-* Describe  data  collection  procedures, sampling  method(s),  number  of  
-subjects, response  rate  etc.
-* Create  questions for your  survey  (include  the questions in  your  report)
-* Describe  the population  and size  of  population
-* Describe  and motive  method  for analyzing the data
-* Discuss validity  threats
-
-%-------------------------------------------------------------------------
-
-\textbf{Industry}: To compare code of different language to be able to prioritize them. \\
-Further studies can be conducted to see if there is a correlation between popularity of projects and the readability of the langauage(s) used in the project. \\
-\textbf{Academia}: To conduct more studies on the area which compare different languages. \\
-To determine which languages are most suited for academic teaching. (When other attributes of programming languages are not constraints).
-
-\bibliographystyle{assignment_1}
-\bibliography{assignment_1}
 

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
sasda

@@
 
-Write how the questionnaire was distributed. (I.e. facebook pages of all 3 years):::::
-Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting} and thus the questionnaire will be distributed to the Facebook page of all three year's.
+Write how the questionnaire was distributed.
+(I.e.
+facebook pages of all 3 years --> Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting} and thus the questionnaire will be distributed to the Facebook page of all three years (and not only 1st years with Java experience, for example).
 

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Design Section
Draft of design section, added notes to other areas we might need to
expand

--- 2015-02-05 rmtw/assignment_1/assignment_1.tex
@@
 
-Both industry and academia face the problem of maintainability.
-As stated previously, many times the readability of code affects the codes maintainability.
-This study could help some in industry to pick languages for certain tasks for maintainability reasons alone.
+Industry and academia both face the problem of code maintainability, and by association, readability and as was highlighte previously, the readability of code can affect its maintainability.
+This study could help some in industry to decide which languages should be used if maintainability is of high concern.
 Further studies could be conducted by to determine if there is a correlation between the popularity of projects and the readability of their languages.
-Furthermore, academia would be interested in which languages are more popular and useful for learning.
-By further investigating the design of the programming languages themselves, future languages which are developed could build upon the success of those which came before them.
+Furthermore, academia would be interested in which languages are more popular and those that have a higher readability, especially for novice developers.
+Further investigation into the design of these programming languages could yield insights into what makes them so popular and potentially well suited for teaching.
 \newline
@@
 The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages.
-With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
+With the aim of suggesting a metric which describes the readability of a given program, taking into account the inherent readability of the language in which it is written.
 \newline
@@
 The survey data will be collected from professionals, teachers, students and hobbyists via a series of on-line surveys.
-The respondents will then be asked to review a series of code snippets from popular languages and will be subsequently asked to rate their readability.
+The respondents will then be asked some information about their development background.
+The will then be asked to review a series of code snippets from popular languages and to rate their readability.
 \newline
@@
 The main argument for the questionnaire is that the survey must be distributed to a large amount of people.
-A quantitative is also well-suited for this study since there are no existing publications that explore readability differences between languages.
+A quantitative study is also well-suited for this study since there are no existing publications that explore readability differences between languages.
+
+Longitudinal servey - Collected over time (cross-sectional is one isntance in time)
+Purpose: To generalise perceived readability of different programming languages by novices - Ref papers from the book
+Indicate why a survey is the preferred type of data collection - Consider advantages of surveys (economy and design and rapid data collection - (Fowler 2009) -> discuss advantage of identifying attributes of a large population from a small group of individuals
+Form: Internet based (nesbary 2000, sue \& ritter 2012) - Provide a rationale for its use, strengths and weaknesses. Costs, data availability and convenience
+  peer reviewed with collegues, tested on a small group that we supervise
+
+  Population: limited to the SEM program. (Count students if it's available somewhere).
+  Cluster sampling / single stage - Not possible to get all the names of all possible respondents - Babbie 2007
+  nonprobability sample - convenience sample - chosen on their availability and convenience.
+Not ideal, but best we can probably do considering its single stage etc (ideally we would do random sampling)
+  stratification will not occur.
+Ideally we will have a good representation, but again, due to not having all the names and the convenience method, we cannot ensure that the population is stratisfied plus irrelevent
+  total at SEM = ~300.
+(Count how many in the facebook groups, that's the sample size - Estimate how many will actually respond, how much error we can tolerate (\%4 probably - confidence interval) - Use the sample size method by fowler?
 
@@
 
+TABLE HERE
+Variable : RQ : Item on Survey
+
 \SubSection{Questionnaire Design}
-TODO: 
-Write briefly about why we chose the languages we chose. (different paradigms etc)
-Write some formal stuff about how the survey was designed. (Shit about open-ended questions etc.)
-Write which tool was used etc.
 
-Write how the questionnaire was distributed. (I.e. facebook pages of all 3 years):::::
-Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting} and thus the questionnaire will be distributed to the Facebook page of all three year's.
+The five languages represented in the questionnaire were C++, Erlang, Go, Java and Python.
+They were chosen for multiple reasons.
+One being that all the students in the SE\&M course will have taken an introductory Java programming course by now and as such should be familiar with the syntax.
+The other languages were chosen for similar reasons.
+Erlang was chosen as it's the first language taught after Java and it uses a different development paradigm.
+C++ was chosen as it is used heavily in project course during the 4th semester and python was chosen for similars reasons.
+Golang was picked as we wanted to see how students would perceive a language that is popular but has not really entered the academic landscape as of yet.
+
+Google Sheets was decided upon as the appropriate tool of choice for our survey.
+It has a good reputation for use in surveys and it was recommended to us by Branson.
+We also have prior experience the tool from previous research projects.
+The questionnaire consists of structured and partially structured questions.
+The questions are followed by two code snippets per language mentioned previously with a scale requesting the respondent to rate whether they feel that the code is easy or difficult to read in the style of the Likert Scale.
+The questions were written with as little ambiguity as possible.
+They were field tested by colleagues in a small example of our survey.
+Examples of these questions can be found in ***Appendix Item Here***.
+The aforementioned chart shows how some of our independent variables, research questions and survey items correlate.
+
+Taking into consideration potential biases that may occur, the code snippets were designed so that the code should be easily understood by first year students who have only had exposure to Java.
+For example, each code snippet has a standard ``Hello World'' example and a simple for loop with a counter that is returned at the conclusion of the loop.
+The only exception to this is Erlang.
+While erlang does support for loops, recursion is the tool of choice to perform iterations.
+As such, we feel it was a valid example and should not affect the results for this specific language drastically considering, by this point and time in their education, all SE\&M students will have been exposed to recursion.
+The choices of languages do leave us open to a potential validity and bias issue.
+Inexperienced students who have only seen Java may rate it as easily readable purely because they are only familiar with Java, this is why the relative level of experience is requested first in the survey, so that we might be able to pick up this potential bias during the results analysis.
+To help alleviate this issue, the questionnaire was distributed to all three year groups currently studying at SE\&M (2012,2013,2014).
+
+Other potential validity threats we must take into consideration are those that arise from the nature of survey.
+Since we are performing single stage data collection, the respondents of the surveys are answering our questions at their convenience.
+This opens the door for some validity threats, such as the willingness to participate.
+Our data are at the mercy of those willing to participate; we cannot anticipate how many will respond.
+There is little incentive for the respondents to partake in the survey other than for their own self interest.
+
+Non responses are another issue we will likely face. *** add more?
 
@@
 
+Results Anal
+- Present data 
+- Check for response bias
+- conduct descriptive analysis
+- collapse items into scales
+- check for reliability of scales
+- Run inferential statistics to answer research question or results
+** If number is too small, do we stop there?
+- How will the results be interpreted?
+
 \SubSection{Threats to Validity}
 Bias in languages and experience
+
+  Validity threats:
+    Willingness to participate - There is no incentive other than that they might have to do this next year
+    The results could be meaningless
+    How we will handle response bias:
+      Non responses, how we handle them
+  Potential errors - sampling errors and biases
+
+  Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting}
 

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Results analysis

@@
 \SubSection{Results Analysis}
-TODO:
-* Describe  and motive  method  for analyzing the data
+The response rate for the questionnaire was 11\%.
+The questionnaire was distributed to 270 members of the sample group and 29 members returned the survey.
+An additional 6 students have answered the questionnaire in a second iteration, where they were personally contacted based on which year they were attending.
+Table XXX1 displays information of the respondents experience level.
+Table XXX2 shows the year which the students are attending.
+\newline
+
+\begin{table}[ht]
+  \centering
+  \begin{tabular}{| l | r |}
+    \hline
+    \textbf{Experience} & \textbf{Distribution} \\ \hline
+    Less than a year & 70\% \\ \hline
+    Between 1 and 3 years & 20\% \\ \hline
+    More than 3 years & 10\% \\ 
+    \hline
+  \end{tabular}
+  \caption{ Hiadsdsafdsaf}
+\end{table}
+
+\begin{table}[ht]
+  \centering
+  \begin{tabular}{| l | r |}
+    \hline
+    \textbf{Academic Year} & \textbf{Distribution} \\ \hline
+    1st year & 80\% \\ \hline
+    2nd year & 15\% \\ \hline
+    3rd year & 5\% \\ 
+    \hline
+  \end{tabular}
+  \caption{ Hiadsdsafdsaf}
+\end{table}
+
+Response bias has been determined mostly through analysing the correlation between the independent variables and the dependent variables.
+Readability of a language is likely to be strongly correlated with the reader's experience of the language.
+Due to there being a high response rate amongst 1st year students, it suggests that the nonrespones may have affected the results.
+This is not necessarily negative, since our study aims to measure the inherent readability of a programming language, where the experience of the reader has as little effect as possible.
+\newline
+
+The data was collected with a questionnaire consisting of 15 questions.
+Re
 
 Results Anal
-- Present data 
-- Check for response bias
+
 - conduct descriptive analysis
@@
 
+\begin{table}[ht]
+  \centering
   \begin{tabular}{| l | r | c |}
@@
   	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
-	Occupation & RQ1, SQ1 & \\ \hline
-	Experience & RQ1, SQ1 & \\ \hline
-	Preferred Language & RQ1, SQ2 & \\ \hline
-	Least Preferred Language & RQ1, SQ2& \\  \hline
-	Working Language & RQ1, SQ2 & \\ 
+  	Experience & RQ1, SQ1 & 1 \\ \hline
+    Academic Year & RQ1, SQ1 & 2 \\ \hline
+  	Preferred Language & RQ1, SQ2 & 3 \\ \hline
+  	Least Preferred Language & RQ1, SQ2& 4 \\  \hline
+  	Experience of Language & RQ1, SQ2 & 5 \\ 
   	\hline
 	\end{tabular}
+  \caption{ Hiadsdsafdsaf}
+\end{table}
 

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Results analysis

@@
 
-\begin{table}[ht]
-  \centering
-  \begin{tabular}{| l | r |}
-    \hline
-    \textbf{Experience} & \textbf{Distribution} \\ \hline
-    Less than a year & 70\% \\ \hline
-    Between 1 and 3 years & 20\% \\ \hline
-    More than 3 years & 10\% \\ 
-    \hline
-  \end{tabular}
-  \caption{ Hiadsdsafdsaf}
-\end{table}
-
-\begin{table}[ht]
-  \centering
-  \begin{tabular}{| l | r |}
-    \hline
-    \textbf{Academic Year} & \textbf{Distribution} \\ \hline
-    1st year & 80\% \\ \hline
-    2nd year & 15\% \\ \hline
-    3rd year & 5\% \\ 
-    \hline
-  \end{tabular}
-  \caption{ Hiadsdsafdsaf}
-\end{table}
-
 Response bias has been determined mostly through analysing the correlation between the independent variables and the dependent variables.
@@
 Re
-
-Results Anal
-
-- conduct descriptive analysis
-- collapse items into scales
-- check for reliability of scales
-- Run inferential statistics to answer research question or results
-** If number is too small, do we stop there?
-- How will the results be interpreted?
 

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Fixed merge conflict between versions

@@
 Not ideal, but best we can probably do considering its single stage etc (ideally we would do random sampling)
-  stratification will not occur.
-Ideally we will have a good representation, but again, due to not having all the names and the convenience method, we cannot ensure that the population is stratisfied plus irrelevent
+  stratification will not be enforced. Ideally we will have 1/3,1/3,1/3 but we cannot enfore. The groups are open and public
   total at SEM = ~300.
@@
 The industry is left out of the population since they are more likely to have a lot of experience with certain languages which may cause them to be biased towards that language.
+Furthermore, Höst, Regnell and Whohlin \cite{host2000using} make the case that ``The reason to use students as subjects is often that they are available at universities
+and they are willing to participate in studies as part of courses they attend.'' which is highly approprpiate given that we will be asking our peers and those in lower years who will eventually also be required to perform research tasks.
 The SEM program was chosen due to it being accessible for the researchers.
+
+99 - 3rd year
+168 - 2nd year
+190 - 1st year
+
+Overlap: 50 (Those who are in another group)
+Total: 397
+
+Population in the facebook groups.
+
+count here - estimate desired response rate, error rate etc
+Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting}
+
 \newline
-
-TABLE HERE
-Variable : RQ : Item on Survey
 
@@
 
-Non responses are another issue we will likely face. *** add more?
-
 \SubSection{Results Analysis}
@@
 \SubSection{Threats to Validity}
-Bias in languages and experience
+As in all research there are threats to the validty of the study being undertaken.
+Our largest threat would be the external validty of the data collected.
+The students were selected from the three current years studying at the University of Gothenburg.
+Most of the respondants indicated that they are in the first year of their studties and as such their inexperience could be a limiting factor on their answers to the survey.
+The students may also have had a bias for one of the languages; Java.
+So far, the students in the first year have been formally taught in only Java.
+This means that there is a lower chance they would be familiar with reading other language syntax other than java and as such they would be more likely to see Java favourably than others.
+We cannot therefore generalise that Java has higher readability than that of the other languages despite what the results show.
 
-  Validity threats:
-    Willingness to participate - There is no incentive other than that they might have to do this next year
-    The results could be meaningless
-    How we will handle response bias:
-      Non responses, how we handle them
-  Potential errors - sampling errors and biases
+A further threat that we were unable to counteract adequately was the willing to participate of our respondants.
+The participants had little or no incentive to actually partake in the study and as such many most likely simply ingored it.
+This is to be expected when one attempts to undertakes a single stage sampling method.
+One idea to improve the response rate for further surveys could be to form some incentive for the respondants.
 
-  Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting}
+Threat - Open groups. No control over who is in them so potentially we can have respondants who are not knowledgeable answering questions.
 

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Finished threats

@@
 
-Threat - Open groups. No control over who is in them so potentially we can have respondants who are not knowledgeable answering questions.
+The fact that the questionnaire was distributed online via facebook groups also meant that there was another threat to the validty of the responses.
+These groups are not offically controled by the university and as such admission into these groups is up to the students who are organising them.
+This means that there is potential that some of the responses came from people not within the SE\&M isntitutions and this should be taken into consideration when analysing the results.
 

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Results analysis

@@
 The data was collected with a questionnaire consisting of 15 questions.
-Re
+The data has been analysed with simple descriptive analysis where mean values have been the main source to analyse the readability of a language (RQ1).
+Correlation between the independent and dependent variables have been the main analysis to answer SRQ1 and SRQ2.
+Score ranges have been used to analyse the strength of replies.
+More advanced data analysis methods have not been utilized due to the relatively low number of respondants.
 

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
removed abstract+duplicate text and moved table

@@
 \thispagestyle{empty}
-
-\begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top 
-   of the left-hand column, below the author and affiliation 
-   information. Use the word ``Abstract'' as the title, in 12-point 
-   Times, boldface type, centered relative to the column, initially 
-   capitalized. The abstract is to be in 10-point, single-spaced type. 
-   The abstract may be up to 3 inches (7.62 cm) long. Leave two blank 
-   lines after the Abstract, then begin the main text. 
-\end{abstract}
 
@@
 
-The purpose of this survey study is therefore to find what are the differences in readability between five common and well known programming languages.
-With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
-\newline
-
-The Independent variables will be defined as the experience, occupation, preferred language, least preferred language and the working language of the participant.
+The independent variables will be defined as the experience, occupation, preferred language, least preferred language and the working language of the participant.
 The dependent variable in this example will be the readability of the language.
@@
 
-\newline
-
 \SubSection{Questionnaire Design}
@@
 
+\begin{table}[ht]
+  \centering
+  \begin{tabular}{| l | r | c |}
+    \hline
+    \textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
+    Experience & RQ1, SQ1 & 1 \\ \hline
+    Academic Year & RQ1, SQ1 & 2 \\ \hline
+    Preferred Language & RQ1, SQ2 & 3 \\ \hline
+    Least Preferred Language & RQ1, SQ2& 4 \\  \hline
+    Experience of Language & RQ1, SQ2 & 5 \\ 
+    \hline
+  \end{tabular}
+  \caption{Independant variables' relation to Research Questions}
+\end{table}
+
 \SubSection{Results Analysis}
@@
 An additional 6 students have answered the questionnaire in a second iteration, where they were personally contacted based on which year they were attending.
-Table XXX1 displays information of the respondents experience level.
-Table XXX2 shows the year which the students are attending.
 \newline
@@
 
-\begin{table}[ht]
-  \centering
-  \begin{tabular}{| l | r | c |}
-  	\hline
-  	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
-  	Experience & RQ1, SQ1 & 1 \\ \hline
-    Academic Year & RQ1, SQ1 & 2 \\ \hline
-  	Preferred Language & RQ1, SQ2 & 3 \\ \hline
-  	Least Preferred Language & RQ1, SQ2& 4 \\  \hline
-  	Experience of Language & RQ1, SQ2 & 5 \\ 
-  	\hline
-	\end{tabular}
-  \caption{ Hiadsdsafdsaf}
-\end{table}
-
 \end{document}

### 2015-02-06 rmtw/assignment_1/assignment_1.tex
Finsihed up meth section and did some formatting

@@
 
+\usepackage[utf8]{inputenc}
+
 %\documentstyle[times,art10,twocolumn,latex8]{article}
@@
 
-\title{Title of the document here}
+\title{Measuring the Inherent Readability of Five Common Programming Languages}
 
@@
 %------------------------------------------------------------------------- 
-\SubSection{Research Question}
+\SubSection{Research Questions}
 This study has been designed with one main research question in mind:
@@
 \Section{Methodology}
-The main purpose of this study is to discover differences in the perceived readability of code.
+The main purpose of this study is to discover differences in the perceived readability of code and use that to be able to generalise percieved readability of different programming languages by novice programmers.
+The study will be performed as a survey, mainly due to economy and time constraints \cite{fowler2008survey}.
 The study will be carried out in three phases.
@@
 In phase 2, the survey will be designed and carried out.
+The data will be collected over time, and thus this study can be characterized as a longitudinal survey.
 In phase 3, the results of the survey will be analysed.
@@
 A quantitative study is also well-suited for this study since there are no existing publications that explore readability differences between languages.
-
-Longitudinal servey - Collected over time (cross-sectional is one isntance in time)
-Purpose: To generalise perceived readability of different programming languages by novices - Ref papers from the book
-Indicate why a survey is the preferred type of data collection - Consider advantages of surveys (economy and design and rapid data collection - (Fowler 2009) -> discuss advantage of identifying attributes of a large population from a small group of individuals
-Form: Internet based (nesbary 2000, sue \& ritter 2012) - Provide a rationale for its use, strengths and weaknesses. Costs, data availability and convenience
-  peer reviewed with collegues, tested on a small group that we supervise
-
-  Population: limited to the SEM program. (Count students if it's available somewhere).
-  Cluster sampling / single stage - Not possible to get all the names of all possible respondents - Babbie 2007
-  nonprobability sample - convenience sample - chosen on their availability and convenience.
-Not ideal, but best we can probably do considering its single stage etc (ideally we would do random sampling)
-  stratification will not be enforced. Ideally we will have 1/3,1/3,1/3 but we cannot enfore. The groups are open and public
-  total at SEM = ~300.
-(Count how many in the facebook groups, that's the sample size - Estimate how many will actually respond, how much error we can tolerate (\%4 probably - confidence interval) - Use the sample size method by fowler?
 
@@
 
-The population of this survey is the students of the Software Engineering and Management programme (SEM) at Gothenburg University.
+The population of this survey is the students of the Software Engineering and Management programme (SE\&M) at Gothenburg University.
+The number of students attending the SE\&M programme is 270.
+110 of those are in the 1st year, 90 are in the 2nd year and the remaining 70 are in the 3rd year.
+The desired response rate is 10\%.
+Stratification of the population will not be enforced and thus there may be a stastistically incorrect representation of the independent variables.
+This has, however, been taken into account in the analysis of the results.
+\newline
+
 The industry is left out of the population since they are more likely to have a lot of experience with certain languages which may cause them to be biased towards that language.
-Furthermore, Höst, Regnell and Whohlin \cite{host2000using} make the case that ``The reason to use students as subjects is often that they are available at universities
-and they are willing to participate in studies as part of courses they attend.'' which is highly approprpiate given that we will be asking our peers and those in lower years who will eventually also be required to perform research tasks.
-The SEM program was chosen due to it being accessible for the researchers.
-
-99 - 3rd year
-168 - 2nd year
-190 - 1st year
-
-Overlap: 50 (Those who are in another group)
-Total: 397
-
-Population in the facebook groups.
-
-count here - estimate desired response rate, error rate etc
-Sampling bias is a considerable challenge in research \cite{easterbrook2008selecting}
+Furthermore, Höst, Regnell and Whohlin \cite{host2000using} make the case that ``The reason to use students as subjects is often that they are available at universities and they are willing to participate in studies as part of courses they attend.'' which is highly appropriate given that we will be asking our peers and those in lower years who will eventually also be required to perform research tasks.
+The SE\&M program was chosen due to it being accessible for the researchers.
+More sophisticated sampling methods such as cluster-sampling or random sampling have not been used due to time-constraints.
 
@@
 Golang was picked as we wanted to see how students would perceive a language that is popular but has not really entered the academic landscape as of yet.
+\newline
 
@@
 The aforementioned chart shows how some of our independent variables, research questions and survey items correlate.
+\newline
 
@@
 To help alleviate this issue, the questionnaire was distributed to all three year groups currently studying at SE\&M (2012,2013,2014).
+\newline
 
@@
 There is little incentive for the respondents to partake in the survey other than for their own self interest.
+\newline
+
+The questionnaire has been peer reviewed by colleagues Jani Kellaris and Patrik Bäckström and it has been tested on a 6 students in 2nd year which we supervise.
 
@@
 We cannot therefore generalise that Java has higher readability than that of the other languages despite what the results show.
+\newline
 
@@
 One idea to improve the response rate for further surveys could be to form some incentive for the respondants.
+\newline
 
@@
 
+\vfill
+\eject
+
+\Section{Acknowledgments}
+\textbf{William} has had the main responsibility for the following sections:
+\begin{itemize} \renewcommand{\labelitemi}{$\bullet$} 
+\item I. Introduction
+\item II. A. Research Questions
+\item III. Methodology
+\item III. A. Identifying the Population
+\item III. C. Results Analysis
+\end{itemize}
+\
+
+\textbf{John} has had the main responsibility for the following sections:
+\begin{itemize} \renewcommand{\labelitemi}{$\bullet$} 
+\item II. Purpose of the Study
+\item III. B. Questionnaire Design
+\item III. D. Threats to Validity
+\item *Creating the questionnaire (writing code snippets etc.)
+\end{itemize}
+\
+
+We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John. 
+\newline
+
+We would also like to note that the numbers related to how many are in the SE\&M program are estimated.
+We saw no real purpose of asking teachers for the real numbers for this assignment.
+(We assume this is fine).
+
 \end{document}

### 2015-02-08 rmtw/assignment_1/assignment_1.tex
Small changes to spelling and typos

@@
 \usepackage{times}
-
+\usepackage{url}
 \usepackage[utf8]{inputenc}
@@
 %%Existing literature
-Existing studies in the field focus on readability within of different coding styles for a set language, which can be seen in for example \cite{buse2010learning}.
+Existing studies in the field focus on readability within different coding styles for a set language, which can be seen in for example \cite{buse2010learning}.
 Buse \& Westley introduce a metrics system for measuring the readability of code, and Java is the language of choice in the study \cite{buse2010learning}.
@@
 The importance of code readability may be overlooked, since it does not directly affect runtime performance.
-Aggarwal et al., however claim that code's readability impacts it's maintainability \cite{aggarwal2002integrated}.
-This claim is also supported by \cite{elshoff1982improving} et al.
+Aggarwal et al., however claim that code's readability impacts its maintainability \cite{aggarwal2002integrated}.
+This claim is also supported by \cite{elshoff1982improving} elshoff et al.
 who also introduce examples of certain coding practices that are more readable and maintainable than others \cite{elshoff1982improving}.
@@
 
-Industry and academia both face the problem of code maintainability, and by association, readability and as was highlighte previously, the readability of code can affect its maintainability.
+Industry and academia both face the problem of code maintainability and by association, readability.
+As was highlighted previously, the readability of code can affect its maintainability.
 This study could help some in industry to decide which languages should be used if maintainability is of high concern.
@@
 
-The survey data will be collected from professionals, teachers, students and hobbyists via a series of on-line surveys.
+The survey data will be collected from students studying at the University of Gothenburg via a series of on-line surveys.
 The respondents will then be asked some information about their development background.
-The will then be asked to review a series of code snippets from popular languages and to rate their readability.
+They will then be asked to review a series of code snippets from popular languages and to rate their readability.
 \newline
@@
 In phase 3, the results of the survey will be analysed.
-The investigation method will be in the form of a questionnaire.
+The investigation method will be in the form of a questionnaire\footnote{\url{https://docs.google.com/forms/d/1UxMx4avPhcqxxmBAs2VAf_CixiN23pKWjF9gbo69vlA/viewform}}.
 The main argument for the questionnaire is that the survey must be distributed to a large amount of people.
@@
 
-The population of this survey is the students of the Software Engineering and Management programme (SE\&M) at Gothenburg University.
+The population of this survey are the students of the Software Engineering and Management programme (SE\&M) at Gothenburg University.
 The number of students attending the SE\&M programme is 270.
@@
 Erlang was chosen as it's the first language taught after Java and it uses a different development paradigm.
-C++ was chosen as it is used heavily in project course during the 4th semester and python was chosen for similars reasons.
+C++ was chosen as it is used heavily in project course during the 4th semester and Python was chosen for similars reasons.
 Golang was picked as we wanted to see how students would perceive a language that is popular but has not really entered the academic landscape as of yet.
@@
 Google Sheets was decided upon as the appropriate tool of choice for our survey.
-It has a good reputation for use in surveys and it was recommended to us by Branson.
+It has a good reputation for use in surveys and it was recommended to us by Dr.
+Richard Berntsson Svensson.
 We also have prior experience the tool from previous research projects.
@@
 They were field tested by colleagues in a small example of our survey.
-Examples of these questions can be found in ***Appendix Item Here***.
+Examples of these questions can be found in table 1.
 The aforementioned chart shows how some of our independent variables, research questions and survey items correlate.
@@
 Taking into consideration potential biases that may occur, the code snippets were designed so that the code should be easily understood by first year students who have only had exposure to Java.
-For example, each code snippet has a standard ``Hello World'' example and a simple for loop with a counter that is returned at the conclusion of the loop.
+For example, each code snippet has a standard ``Hello World'' example and a simple for-loop with a counter that is returned at the conclusion of the loop.
 The only exception to this is Erlang.
-While erlang does support for loops, recursion is the tool of choice to perform iterations.
+While Erlang does support for-loops, recursion is the tool of choice to perform iterations.
 As such, we feel it was a valid example and should not affect the results for this specific language drastically considering, by this point and time in their education, all SE\&M students will have been exposed to recursion.
@@
 \SubSection{Results Analysis}
-The response rate for the questionnaire was 11\%.
-The questionnaire was distributed to 270 members of the sample group and 29 members returned the survey.
-An additional 6 students have answered the questionnaire in a second iteration, where they were personally contacted based on which year they were attending.
+The response rate for the questionnaire was 11\%. The questionnaire was distributed to 270 members of the sample group and 29 members returned the survey.
 \newline
@@
 Readability of a language is likely to be strongly correlated with the reader's experience of the language.
-Due to there being a high response rate amongst 1st year students, it suggests that the nonrespones may have affected the results.
+Due to there being a high response rate amongst 1st year students, it suggests that the nonresponses may have affected the results.
 This is not necessarily negative, since our study aims to measure the inherent readability of a programming language, where the experience of the reader has as little effect as possible.
@@
 \SubSection{Threats to Validity}
-As in all research there are threats to the validty of the study being undertaken.
+As in all research there are threats to the validity of the study being undertaken.
 Our largest threat would be the external validty of the data collected.
@@
 
-The fact that the questionnaire was distributed online via facebook groups also meant that there was another threat to the validty of the responses.
-These groups are not offically controled by the university and as such admission into these groups is up to the students who are organising them.
+The fact that the questionnaire was distributed online via Facebook groups also meant that there was another threat to the validty of the responses.
+These groups are not offically controlled by the university and as such admission into these groups is up to the students who are organising them.
 This means that there is potential that some of the responses came from people not within the SE\&M isntitutions and this should be taken into consideration when analysing the results.

### 2015-02-09 rmtw/a1_review/latex8.tex
Added review of a1

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: John Burchell & William Granli $
%  $Date: 2015/01/21 15:20:59 $
%  $Revision: 1.0
%

\documentclass[times, 10pt,twocolumn]{IEEEtran} 
\usepackage{latex8}
\usepackage{times}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{Review of Group 8 by Group 1}

% author names and affiliations
\author{\IEEEauthorblockN{
  John Burchell\IEEEauthorrefmark{1} and
  William Granli\IEEEauthorrefmark{1}}

  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}

}

\maketitle
\thispagestyle{empty}

%-------------------------------------------------------------------------

\Section{Introduction}
The literature review is well-written, extensive and seems to cover a lot of surrounding studies. It is good that a paper supporting the importance of personal fulfilment has been cited, since your paper almost stands and falls by this. One improvement for the Related Work section could be to write it as one text where you content drive the text instead of listing the papers one by one. This way you would get a more condensed text which is constructed around your paper.

\Section{Purpose Statement}
The problem statement is very clear. It would be good to state a couple of incentives for the industry, however. What would your paper bring to the industry? The benefits to academia have been mentioned in a good way. The sentence ``The purpose of this survey is to collect data about'' could probably be elaborated a bit. Explain what you will do with the data, for example. 
\\

The definition of expertise is a bit too vague and ambiguous, in our opinion. You can probably replace expertise with years of experience and achieve the same results, since there should be a strong correlation between the two. The same goes for partner's skill level. It is a bit unclear from the paper what partner's skill level means. It can probably be clarified that partner's skill level is a 1-5 rating made by the other partner.

\Section{Research Question}
The research questions are yes-no questions. The main research question could be rephrased to, for example: ``How does pair programming affect/correlate to personal fulfilment of a developer?''. The sub-questions could be rephrased in similar style. 
\\

The sub-questions are good, but it is quite unclear what your intent with them is. The difference between expertise and skill-level isn't really clear and it should probably be emphasised that you want to measure the difference between ``actual skill-level'' and ``skill-level as perceived by your partner''.

\Section{Suitable Research Design}
The description of your population is clear and well-researched. It is good that you spent time to research how you find the most meaningful population, by for example leaving out inexperienced developers. One improvement to your research design section would be to, in the introduction, briefly outline your research process and describe which stages it includes and it what order they will be carried out. 
\\

In the results analysis section, you should probably mention which type of analysis you will apply. It is probably descriptive analysis in your case. You should also motivate why a more extensive approach was not ensued. 
\\

The identified limitations are good. One suggestion we have would be to research how different types of pair-programming impact personal fulfilment. You mentioned the driver and navigator style. Maybe there are other styles that would get widely different results in the survey. If this seems feasible, a ``type of pair-programming'' independent variable could be added to your survey.

\Section{Other}
Below sentence does not make sense: \\
``The purpose of this survey study is to assess the impact of pair programming on personal fulfilment, controlling for expertise of developers with pair programming at mid sized software development organisations. ''

\end{document}

### 2015-02-10 rmtw/a1_review/latex8.tex
Changed some things and added more comments

@@
 It is good that a paper supporting the importance of personal fulfilment has been cited, since your paper almost stands and falls by this.
-One improvement for the Related Work section could be to write it as one text where you content drive the text instead of listing the papers one by one.
+One improvement for the Related Work section could be to write it as one text where your content drives the text instead of listing the papers one by one.
 This way you would get a more condensed text which is constructed around your paper.
@@
 It can probably be clarified that partner's skill level is a 1-5 rating made by the other partner.
+It also might be nice to define what you think a mid-sized team is prior to talking about how many people are at the companies.
+Is it 300-400, 400-500 persons etc, does this include all staff or just developers etc.
 
@@
 The description of your population is clear and well-researched.
-It is good that you spent time to research how you find the most meaningful population, by for example leaving out inexperienced developers.
-One improvement to your research design section would be to, in the introduction, briefly outline your research process and describe which stages it includes and it what order they will be carried out.
+It is good that you spent time to research how you find the most meaningful population, for example leaving out inexperienced developers.
+One improvement to your research design section would be to, in the introduction, briefly outline your research process and describe which stages it includes and in what order they will be carried out.
 \\
@@
 \Section{Other}
-Below sentence does not make sense: \\
+Below sentence does not make much sense: \\
 ``The purpose of this survey study is to assess the impact of pair programming on personal fulfilment, controlling for expertise of developers with pair programming at mid sized software development organisations.

### 2015-02-10 rmtw/a3/latex8.tex
Started a3

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: John Burchell & William Granli $
%  $Date: 2015/01/21 15:20:59 $
%  $Revision: 1.0
%

\documentclass[times, 10pt,twocolumn]{IEEEtran} 
\usepackage{latex8}
\usepackage{times}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{Review of Group 8 by Group 1}

% author names and affiliations
\author{\IEEEauthorblockN{
  John Burchell\IEEEauthorrefmark{1} and
  William Granli\IEEEauthorrefmark{1}}

  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}

}

\maketitle
\thispagestyle{empty}

%-------------------------------------------------------------------------

​\Section{Introduction}
*5 references must be used to support claims in Introduction
Use parts of Abstract and Intro from CM. 
\SubSection{Problem Statement}
Take this from CM. 
How do large companies implement changes in environments which are split by two programming paradigms?

\SubSection{Existing Literature}
Use parts of the CM report. 
Most relevant is probably Jani's but could find stuff in the other's too.

\SubSection{Motivation for Research}
Academia: Has not been done before. (I.e. all CM papers talk about implementing something in a homogenous environment). 
Industry: It's useful to Ericsson. They have had problems implementing changes and keeping up with the competition. It might be good to look up other companies which use MDSD and make a case for them as well.

\Section{Purpose of the Study}
It's an exploratory study. We want to find out how CM is done in such environemnts, if it's successful and how it can be improved.

\SubSection{Research Question(s)}
RQ: How is change managed in a company which has a split development strategy (e.g. mdsd+manual)?
SRQ1: How can it be done better blabla?
SRQ2: etc.

\Section{Case Company Description}
TBA

\Section{Methodology}
We aim to conduct an exploratory study. ("finding out what is happening, seeking new insights and generating ideas
and hypotheses for new research.", runesson host)

Data Triangulation:
Data (source) triangulation—using more than one data source or collecting the same
data at different occasions.
Observer triangulation—using more than one observer in the study.
Methodological triangulation—combining different types of data collection methods,
e.g. qualitative and quantitative methods.
Theory triangulation—using alternative theories or viewpoints.

The design will be flexible based on the data collected (runesson host). 
	Come up with examples on how x data can affect the study.

Why case study? 
Case studies offer an approach which does not need a strict boundary between the studied object and its environment; perhaps the key to understanding is in the interaction between the two? (runesson host)

Steps\&Phases
1. Case study design: Objectives are defined and the case study is planned.

\begin{itemize}
\item Describe and explain the research strategy (i.e. case study)
\item Describe and explain the investigation methods that will be used
\item Motivate the choice of case study using relevant references
\item Describe the data collection procedures, sampling method(s), number of subjects etc.
\item Describe the subjects and how they were selected
\item Create questions for your interviews (include the questions in your report)
\item Describe and motivate the method for analyzing the data
\item Discuss validity threats
\end{itemize}

\Section{References}
Make real ref list later

\Section{Acknowledgements}
Write who did what

\end{document}

### 2015-02-10 rmtw/a3/latex8.tex
Added notes for meth section

@@
 
-Steps\&Phases
+Steps \& Phases
 1. Case study design: Objectives are defined and the case study is planned. 
+Runesson+Höst mention the importance of carefully planning case studies, despite them being of the flexible type. 
+Planning consists of which methods to use for the data collection, which departments to visit, which documents to read, who to interview, when interviews should be conducted, etc.
+These can be formulated in a case study protocol.
+It should contain: 
+Objective: What to achieve?
+The case: What is studied?
+Theory: Frame of reference?
+Research questions: What to know?
+Methods: How to collect data?
+Selection strategy: Where to seek data?
+
+2. Preparation for data collection: procedures and protocols for data collection are defined
+3. Collecting evidence: Execution with data collection on the studied case
+A direct method (first degree) (Lethbridge et al. 2005) will be used. (Interviews).
+Third degree (Lethbridge et al. 2005) can also be used. I.e. analyse work artifacts. (The time-to-market based on requirments thing). (More info page 19)
+
+Mix of open/closed questions + semi-structured.
+
+4. Analysis of collected data
+Analysis will be done in tandem with the data gatheritng to be able to iteratively improve the data collection process+tools
+
+Hypothesis generation will be an important part of the data analysis, since the outcome/goal of the study is not clear.
+
+5. Reporting
+(Descriptions on page 8 of the pdf in runessson host paper)
+
+Case study protocol
+\#	Goals and Scope		Data collection and filtering	Analysis and presentation	Interpretation and Improvement
+(More info on Page 11 of the host pdf)
+
+Mention stuff about ethical problems (page 12)
 

### 2015-02-10 rmtw/a3/latex8.tex
Adding my changes to the document

@@
 
+%Deficiencies introduction model
+
 ​\Section{Introduction}
@@
 Use parts of Abstract and Intro from CM.
+
+Coping with change in the software development domain is difficult at best, this is further exasperated by trying to apply changes that do not mesh well with existing development paradigms.
+How then, do large companies, especially those utilising multiple development paradigms, cope with this kind of change?
+
 \SubSection{Problem Statement}
-Take this from CM. 
-How do large companies implement changes in environments which are split by two programming paradigms?
+The purpose of this paper is therefore to determine whether an organisation's development paradigm should be the basis for deciding which process and design changes to adopt.
+
+%Maybe not this bit-----------------------------------------------------------
+To explore this area, we focus on process and design practices that have been introduced at Ericsson EPG.
+%Maybe not this bit-----------------------------------------------------------
 
@@
 Most relevant is probably Jani's but could find stuff in the other's too.
+
+Little existing literature.
+There are gaps: see: nothing about applying changes to two different paradigms at the same time.
+
+\SubSection{Deficiencies in Literature}
+What is missing
 

### 2015-02-11 rmtw/a1/assignment_1.tex
Changed survey type in Methodology section

--- 2015-02-08 rmtw/assignment_1/assignment_1.tex
@@
 
-The importance of code readability may be overlooked, since it does not directly affect runtime performance.
+The importance of code readability may be overlooked, since it does not directly affect run-time performance.
 Aggarwal et al., however claim that code's readability impacts its maintainability \cite{aggarwal2002integrated}.
-This claim is also supported by \cite{elshoff1982improving} elshoff et al.
+This claim is also supported by \cite{elshoff1982improving} Elshoff et al.
 who also introduce examples of certain coding practices that are more readable and maintainable than others \cite{elshoff1982improving}.
@@
 \begin{itemize}
-\item \textit{RQ1:} What are the measurable differences in readability between programming languages?
+\item \textit{RQ1:} What are the measurable differences in perceived readability between programming languages?
 \end{itemize}
@@
 \Section{Methodology}
-The main purpose of this study is to discover differences in the perceived readability of code and use that to be able to generalise percieved readability of different programming languages by novice programmers.
+The main purpose of this study is to discover differences in the perceived readability of code and use that to be able to generalise perceived readability of different programming languages by novice programmers.
 The study will be performed as a survey, mainly due to economy and time constraints \cite{fowler2008survey}.
@@
 In phase 2, the survey will be designed and carried out.
-The data will be collected over time, and thus this study can be characterized as a longitudinal survey.
+Data will be collected once per respondent and the survey will run for a total of 2 weeks.
+Thus, the survey\footnote{\url{https://docs.google.com/forms/d/1UxMx4avPhcqxxmBAs2VAf_CixiN23pKWjF9gbo69vlA/viewform}} is considered to be cross-sectional.
 In phase 3, the results of the survey will be analysed.
-The investigation method will be in the form of a questionnaire\footnote{\url{https://docs.google.com/forms/d/1UxMx4avPhcqxxmBAs2VAf_CixiN23pKWjF9gbo69vlA/viewform}}.
+The investigation method will be in the form of a questionnaire.
 The main argument for the questionnaire is that the survey must be distributed to a large amount of people.
@@
 The desired response rate is 10\%.
-Stratification of the population will not be enforced and thus there may be a stastistically incorrect representation of the independent variables.
+Stratification of the population will not be enforced and thus there may be a statistically incorrect representation of the independent variables.
 This has, however, been taken into account in the analysis of the results.
@@
 Erlang was chosen as it's the first language taught after Java and it uses a different development paradigm.
-C++ was chosen as it is used heavily in project course during the 4th semester and Python was chosen for similars reasons.
+C++ was chosen as it is used heavily in project course during the 4th semester and Python was chosen for similar reasons.
 Golang was picked as we wanted to see how students would perceive a language that is popular but has not really entered the academic landscape as of yet.
@@
   \end{tabular}
-  \caption{Independant variables' relation to Research Questions}
+  \caption{Independent variables' relation to Research Questions}
 \end{table}
@@
 Readability of a language is likely to be strongly correlated with the reader's experience of the language.
-Due to there being a high response rate amongst 1st year students, it suggests that the nonresponses may have affected the results.
+Due to there being a high response rate amongst 1st year students, it suggests that the non-responses may have affected the results.
 This is not necessarily negative, since our study aims to measure the inherent readability of a programming language, where the experience of the reader has as little effect as possible.
@@
 Score ranges have been used to analyse the strength of replies.
-More advanced data analysis methods have not been utilized due to the relatively low number of respondants.
+More advanced data analysis methods have not been utilised due to the relatively low number of respondent.
 
@@
 As in all research there are threats to the validity of the study being undertaken.
-Our largest threat would be the external validty of the data collected.
+Our largest threat would be the external validity of the data collected.
 The students were selected from the three current years studying at the University of Gothenburg.
-Most of the respondants indicated that they are in the first year of their studties and as such their inexperience could be a limiting factor on their answers to the survey.
+Most of the respondents indicated that they are in the first year of their studies and as such their inexperience could be a limiting factor on their answers to the survey.
 The students may also have had a bias for one of the languages; Java.
@@
 
-A further threat that we were unable to counteract adequately was the willing to participate of our respondants.
-The participants had little or no incentive to actually partake in the study and as such many most likely simply ingored it.
+A further threat that we were unable to counteract adequately was the willing to participate of our respondents.
+The participants had little or no incentive to actually partake in the study and as such many most likely simply ignored it.
 This is to be expected when one attempts to undertakes a single stage sampling method.
-One idea to improve the response rate for further surveys could be to form some incentive for the respondants.
+One idea to improve the response rate for further surveys could be to form some incentive for the respondents.
 \newline
 
-The fact that the questionnaire was distributed online via Facebook groups also meant that there was another threat to the validty of the responses.
-These groups are not offically controlled by the university and as such admission into these groups is up to the students who are organising them.
-This means that there is potential that some of the responses came from people not within the SE\&M isntitutions and this should be taken into consideration when analysing the results.
+The fact that the questionnaire was distributed online via Facebook groups also meant that there was another threat to the validity of the responses.
+These groups are not officially controlled by the university and as such admission into these groups is up to the students who are organising them.
+This means that there is potential that some of the responses came from people not within the SE\&M institutions and this should be taken into consideration when analysing the results.
 
@@
 
-\Section{Acknowledgments}
+\Section{Acknowledgements}
 \textbf{William} has had the main responsibility for the following sections:

### 2015-02-11 rmtw/a1/assignment_1.tex
More changes based on feedback

@@
 They were field tested by colleagues in a small example of our survey.
-Examples of these questions can be found in table 1.
-The aforementioned chart shows how some of our independent variables, research questions and survey items correlate.
+An example of one question used in the survey is as follows:
+
 \newline
@@
 So far, the students in the first year have been formally taught in only Java.
-This means that there is a lower chance they would be familiar with reading other language syntax other than java and as such they would be more likely to see Java favourably than others.
+This means that there is a lower chance they would be familiar with reading other language syntax other than Java and as such they would be more likely to see Java favourably than others.
 We cannot therefore generalise that Java has higher readability than that of the other languages despite what the results show.

### 2015-02-12 rmtw/a3/latex8.tex
Added another RQ
First version of meth (a3)

--- 2015-02-10 rmtw/a3/latex8.tex
@@
 SRQ1: How can it be done better blabla?
-SRQ2: etc.
+SRQ2: How can a company determine if a change will conflict with a current paradigm?
 
@@
 TBA
+\newpage
 
 \Section{Methodology}
-We aim to conduct an exploratory study. ("finding out what is happening, seeking new insights and generating ideas
-and hypotheses for new research.", runesson host)
 
-Data Triangulation:
-Data (source) triangulation—using more than one data source or collecting the same
-data at different occasions.
-Observer triangulation—using more than one observer in the study.
-Methodological triangulation—combining different types of data collection methods,
-e.g. qualitative and quantitative methods.
-Theory triangulation—using alternative theories or viewpoints.
+\SubSection{Case Study Design}
+The study has been conducted with an exploratory goal in mind.
+Analysing how Company X tackle the problems related to the research questions has been the most central part of the study.
+Because of the exploratory nature of the study, a flexible process design has been used.
+The study has been carried out using an iterative approach, where the data collected, and the result gathered from analyzing the data has been the main driver for shaping and improving the scope and goal of the study.
+The research has been conducted using a case study approach.
+The reason for that is that the goal of our study is to analyze MDSD, which is a common practice in software engineering, in a very specific setting.
+This line of thought is supported by Runesson \& Höst in CITE XXX.
+Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies CITE XXX.
 
-The design will be flexible based on the data collected (runesson host). 
-	Come up with examples on how x data can affect the study.
+In the initial stage of the study, careful planning was conducted.
+The two major goals of this phase were to a) find meaningful objectives and design for the research, and b) facilitate and design the interviews.
+Although a flexible approach was taken, major effort was spent on planning the study.
+Most of the planning related to communication with Company X, to facilitate the interviews.
+A timeline for the interviews was created and established with Company X.
+The objective of analysing change implementation in enviroments which are split into by two different development activities was also defined during this stage.
 
-Why case study? 
-Case studies offer an approach which does not need a strict boundary between the studied object and its environment; perhaps the key to understanding is in the interaction between the two?
-(runesson host)
+\SubSection{Preparation for Data Collection}
+During this stage the interviews were designed.
+The initial design of the interview was pilot tested on three employees of Company X.
+The results from the pilot tests were used to test if the interviews would fulfil the objective of the study.
+The number of subjects for the main interviews were 15.
+They were sampled randomly from employment records in Company X.
 
-Steps\&Phases
-1. Case study design: Objectives are defined and the case study is planned.
+During this stage, the all ethical precautions of the study were taken.
+It was established that Company X wanted to remain anonymous and that all interviews must happen on voluntary basis.
+An agreement on to which extent Company X's documentation could be used was also made during this stage.
+
+\SubSection{Data Gathering}
+The data has mainly been gathered through first degree interviews CITE LETHBRIDGE 2005 XXX.
+The subjects of the interviews can be divided into three sub-groups: a) Managers b) Developers c) Change Agents.
+Data triangulation has been used to compare and verify the results based on which role the interviewee had.
+The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes.
+The interviews have been carried out using a mix of open-ended and close-ended questions, and a semi-structured approach has been used.
+The fact that the interviewees have widely differing backgrounds and roles was the main reason for not using a structured approach.
+A semi-structured approach was chosen over a unstructured approach to be able to get results that are closely related to eachother, so that meaningful comparison and analysis can be carried out.
+Company X's change process documentation has also been analysed to provide further depth to the analysis.
+Please see Appendix A for a full list of interview questions.
+
+\SubSection{Data Analysis}
+The data analysis of the interviews has been done in tandem with the data gathering to be able to iteratively improve the data collection process.
+This data analysis has had the main purpose of generating hypotheses and to refine the research questions.
+The interviews were analysed by manually reading and comparing answers.
+Spreadsheets and tables were also used to provide an overview of the results.
+
+When all the interview data had been collected, the data analysis goal was switched to focus on confirmation of the hypothesis.
+As mentioned in Section IV.
+C, data triangulation was the main tool used to confirm the hypothesis.
+
+\Section{Threats to Validity}
 
 \begin{itemize}
-\item Describe and explain the research strategy (i.e. case study)
-\item Describe and explain the investigation methods that will be used
-\item Motivate the choice of case study using relevant references
-\item Describe the data collection procedures, sampling method(s), number of subjects etc.
-\item Describe the subjects and how they were selected
 \item Create questions for your interviews (include the questions in your report)
-\item Describe and motivate the method for analyzing the data
 \item Discuss validity threats

### 2015-02-13 rmtw/a3/latex8.tex
First draft of introduction. Added bib file also

@@
 ​\Section{Introduction}
-*5 references must be used to support claims in Introduction
-Use parts of Abstract and Intro from CM.
 
-Coping with change in the software development domain is difficult at best, this is further exasperated by trying to apply changes that do not mesh well with existing development paradigms.
+Coping with change in the software development domain is difficult at best, it is further exasperated by trying to apply changes that do not mesh well with existing development paradigms.
 How then, do large companies, especially those utilising multiple development paradigms, cope with this kind of change?
@@
 
-Little existing literature.
-There are gaps: see: nothing about applying changes to two different paradigms at the same time.
+According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI) or change management (CM) strategies [CITE BOTH].
 
-\SubSection{Deficiencies in Literature}
-What is missing
+SPI is X and is usually performed with XYZ
+
+Similar to SPI is the concept of Evidence Based Software Engineering \cite{dyba2005evidence}.
+EBSE can be used as support for SPI, as suggested by the creators of the strategy.
+The main aim of which is to find a technology which is suitable for use and to then implement it in an organisation.
+
+Literature tells us that there are many factors for both success and failure when implementing change.
+X define this type of activity as Software Process Improvement (SPI) [GET REF].
+SPI utilises many methods and techniques to implement changes in a companies existing software process.
+
+CMMI is such an example of one of these methods.
+
+In 2002 Hall, Rainer and Baddoo \cite{hall2002implementing} published a report wherein they illustrated results of a study which looked at 85 companies throughout the UK.
+The study focused mostly on how the companies perform SPI and how effective their efforts were.
+The authors discovered that, while most companies do attempt SPI, many are unsuccessful due to a combined lack of evaluation and funding.
+
+A further, more specific example is a study conducted by Staron \cite{staron2006adopting}.
+In this study a case study is conducted with two companies wishing or in the process of adopting MDSD.
+In the findings, Staron provides a set of conditions for adopting MDSD, one being the compatibility of MDSD and existing principles in the company.
+Staron states that the adoption of this new process must be usable by the previous processes in place \cite{staron2006adopting}.
+He concludes by stating that this compatibility is especially important for larger companies due to the heavy effort required to implement the change.
+In a second study \cite{staron2008transitioning}, Staron provides possible reasons for the adoption of MDSD to fail.
+He suggests that the large investment in time and money, immature technology and organisational resistance are all factors to overcome in the adoption of new processes.
+
+However, there are is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms.
 
 \SubSection{Motivation for Research}
-Academia: Has not been done before. (I.e. all CM papers talk about implementing something in a homogenous environment). 
-Industry: It's useful to Ericsson.
-They have had problems implementing changes and keeping up with the competition.
-It might be good to look up other companies which use MDSD and make a case for them as well.
+Performing this study would therefore be an attempt at filling in a gap in literature. Academia would be interested in this for its own merit or, most likely, as a stepping stone to further research.
+
+Industry are just as likely to be interested.
+We have performed this study at an organisation, to which the results would be of great value.
+The organisation in question has had problems in the past with implementing effective change to keep up with their competition.
+
+Furthermore, companies that operate in a similar, or even a different manner would most likely be able to appreciate the efforts made in the study.
+In the most hopeful of cases, applying the lessons learned to their own situations.
+
+Given that MDSD has seen a considerable rise in adoption by many companies\cite{millermda}, the results of the research would undoubtedly be of use to these companies also.
 

### 2015-02-13 rmtw/a3/latex8.tex
All but Purpose Completed

@@
 \SubSection{Existing Literature}
-Use parts of the CM report. 
-Most relevant is probably Jani's but could find stuff in the other's too.
-
-According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI) or change management (CM) strategies [CITE BOTH].
-
-SPI is X and is usually performed with XYZ
+According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI)\cite{pettersson2008practitioner}\cite{unterkalmsteiner2012evaluation} or change management (CM) strategies.
+SPI is an attempt to alter an existing company or organisations software process, the main intention of which is to increase product quality, time to market all the while reducing inefficiency and other obstacles for creating good software.
 
@@
 
-Literature tells us that there are many factors for both success and failure when implementing change.
-X define this type of activity as Software Process Improvement (SPI) [GET REF].
-SPI utilises many methods and techniques to implement changes in a companies existing software process.
-
-CMMI is such an example of one of these methods.
+CM on the other hand could be seen as an umbrella for many theories and strategies. Such an example of this is the concept of innovation values fit by [CITE].
 
@@
 \SubSection{Motivation for Research}
-Performing this study would therefore be an attempt at filling in a gap in literature. Academia would be interested in this for its own merit or, most likely, as a stepping stone to further research.
+Performing this study would therefore be an attempt at filling in a gap in literature.
+Academia would be interested in this for its own merit or, most likely, as a stepping stone towards further research.
 
-Industry are just as likely to be interested.
-We have performed this study at an organisation, to which the results would be of great value.
+Industry is just as likely to be interested as change is something they face regularly.
+If this study can help to shed some light about specific methods of to help accommodate change.
+The study will be conducted in tandem with an organisation, to which the results would also be of great value.
 The organisation in question has had problems in the past with implementing effective change to keep up with their competition.

### 2015-02-16 rmtw/a3/latex8.tex
Minor changes to the purpose

@@
 
-CM on the other hand could be seen as an umbrella for many theories and strategies. Such an example of this is the concept of innovation values fit by [CITE].
+CM on the other hand could be seen as an umbrella for a plethora of theories and strategies. An example of a theory is the concept of innovation values fit by [CITE].
 
@@
 \Section{Purpose of the Study}
-It's an exploratory study. We want to find out how CM is done in such environemnts, if it's successful and how it can be improved.
+The purpose of this study is to explore how changes to software processes are incorporated into a company where differing development paradigms are used.
+This exploratory study will take place at a large and successful telecommunications company.
+Much of the qualitative data will originate from current employees via a series of interviews.
+While the study will only take place at a single location, it will be conducted in such a way that it is applicable to any company willing to partake.
 

### 2015-02-16 rmtw/a1/assignment_1.tex
Fixed formatting shit for a1

@@
 
-\documentclass[times, 10pt,twocolumn]{IEEEtran} 
+\documentclass[times, 10pt,twocolumn]{Article} 
 \usepackage{latex8}
@@
 \usepackage[utf8]{inputenc}
+\usepackage{tabularx}
 
@@
 
-% author names and affiliations
+author names and affiliations
 \author{\IEEEauthorblockN{
@@
   William Granli\IEEEauthorrefmark{1}}
+  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}}
 
-  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}
-
-}
 \maketitle
@@
 Buse \& Westley define readability as ``a property that influences how easily a given piece of code can be read and understood'' \cite{buse2010learning}.
-\newline
 
@@
 Even though direct comparisons between languages were not presented in the study \cite{hansen2013makes}, conclusions related to this can be drawn thanks to the fact that these syntactical elements only exist in some languages.
-\newline
 
@@
 Further investigation into the design of these programming languages could yield insights into what makes them so popular and potentially well suited for teaching.
-\newline
 
@@
 With the aim of suggesting a metric which describes the readability of a given program, taking into account the inherent readability of the language in which it is written.
-\newline
 
@@
 The dependent variable in this example will be the readability of the language.
-\newline
 
@@
 They will then be asked to review a series of code snippets from popular languages and to rate their readability.
-\newline
 
@@
 \cite{easterbrook2008selecting} who state ``Survey research is used to identify the characteristics of a broad population of individuals''.
-\newline
 
@@
 This has, however, been taken into account in the analysis of the results.
-\newline
 
@@
 Golang was picked as we wanted to see how students would perceive a language that is popular but has not really entered the academic landscape as of yet.
-\newline
 
@@
 
-\newline
-
 Taking into consideration potential biases that may occur, the code snippets were designed so that the code should be easily understood by first year students who have only had exposure to Java.
@@
 To help alleviate this issue, the questionnaire was distributed to all three year groups currently studying at SE\&M (2012,2013,2014).
-\newline
 
@@
 There is little incentive for the respondents to partake in the survey other than for their own self interest.
-\newline
 
@@
   \centering
-  \begin{tabular}{| l | r | c |}
+  \begin{tabularx}
+  {\linewidth}{| l | X | X |}
     \hline
@@
     \hline
-  \end{tabular}
+  \end{tabularx}
   \caption{Independent variables' relation to Research Questions}
@@
 The response rate for the questionnaire was 11\%. The questionnaire was distributed to 270 members of the sample group and 29 members returned the survey.
-\newline
 
@@
 This is not necessarily negative, since our study aims to measure the inherent readability of a programming language, where the experience of the reader has as little effect as possible.
-\newline
 
 The data was collected with a questionnaire consisting of 15 questions.
-The data has been analysed with simple descriptive analysis where mean values have been the main source to analyse the readability of a language (RQ1).
+The data has been analysed with simple descriptive analysis gwhere mean values have been the main source to analyse the readability of a language (RQ1).
 Correlation between the independent and dependent variables have been the main analysis to answer SRQ1 and SRQ2.
@@
 We cannot therefore generalise that Java has higher readability than that of the other languages despite what the results show.
-\newline
 
@@
 One idea to improve the response rate for further surveys could be to form some incentive for the respondents.
-\newline
 
@@
 We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John.
-\newline
 

### 2015-02-16 rmtw/a3/latex8.tex
Fixed formatting shit for a1

@@
 \item Discuss validity threats
+\item Triangulation = counteract research bias
+\item In meth, mention how the interviewees were selected and contacted (you have a gatekeeper which selects the people for you)
+\item Mention how many of each role and why each role was included (triangulation)
+\item convenience sampling (yo uhave contact at company already and use them) and maximum varation (i aim to have as many as possible)
+\item Mention how the company was selected and what the criteria was (there was some lazy w)
 \end{itemize}

### 2015-02-16 rmtw/a3/latex8.tex
Fixed formatting for a3
Added citation for innovation values fit

@@
 
-\title{Review of Group 8 by Group 1}
+\title{Assignment 3}
 
 % author names and affiliations
-\author{\IEEEauthorblockN{
-  John Burchell\IEEEauthorrefmark{1} and
-  William Granli\IEEEauthorrefmark{1}}
-
-  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}
-
-}
+\author{John Burchell and William Granli \\
+john.a.burchell, william.granli@gmail.com}
 
@@
 
-CM on the other hand could be seen as an umbrella for a plethora of theories and strategies. An example of a theory is the concept of innovation values fit by [CITE].
+CM on the other hand could be seen as an umbrella for a plethora of theories and strategies.
+An example of a theory is the concept of innovation values fit by \cite{klein1996challenge} which aims to describe if and when a company should make changes, based upon how a potential change fits with the values currently held by the company.
 

### 2015-02-16 rmtw/a3/latex8.tex
Minor changes to 2nd section

@@
 Because of the exploratory nature of the study, a flexible process design has been used.
-The study has been carried out using an iterative approach, where the data collected, and the result gathered from analyzing the data has been the main driver for shaping and improving the scope and goal of the study.
+The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study.
 The research has been conducted using a case study approach.
-The reason for that is that the goal of our study is to analyze MDSD, which is a common practice in software engineering, in a very specific setting.
+The reason for this is that the goal of our study is to analyse MDSD, which is a common practice in software engineering, in a very specific setting.
 This line of thought is supported by Runesson \& Höst in CITE XXX.
@@
 
-In the initial stage of the study, careful planning was conducted.
-The two major goals of this phase were to a) find meaningful objectives and design for the research, and b) facilitate and design the interviews.
+During the initial stage of the study, careful planning was conducted.
+The two major goals of this phase were to find meaningful objectives with an appropriate design for the research and secondly to facilitate and design the interviews.
 Although a flexible approach was taken, major effort was spent on planning the study.
-Most of the planning related to communication with Company X, to facilitate the interviews.
-A timeline for the interviews was created and established with Company X.
-The objective of analysing change implementation in enviroments which are split into by two different development activities was also defined during this stage.
+Most of the planning was related to communicating with Company X to facilitate the interviews.
+A time-line for the interviews was created and established with company X.
+The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage.
 
@@
 The results from the pilot tests were used to test if the interviews would fulfil the objective of the study.
-The number of subjects for the main interviews were 15.
-They were sampled randomly from employment records in Company X.
+The number of subjects for the main interviews was 15.
+They were sampled randomly from employment records at Company X.
 
-During this stage, the all ethical precautions of the study were taken.
-It was established that Company X wanted to remain anonymous and that all interviews must happen on voluntary basis.
-An agreement on to which extent Company X's documentation could be used was also made during this stage.
+During this stage, all ethical precautions of the study were taken.
+It was established that Company X wanted to remain anonymous and that all interviews must happen on a voluntary basis.
+An agreement on to what extent Company X's documentation could be used was also made during this stage.
+%Add what was agreed
 
@@
 The data has mainly been gathered through first degree interviews CITE LETHBRIDGE 2005 XXX.
-The subjects of the interviews can be divided into three sub-groups: a) Managers b) Developers c) Change Agents.
-Data triangulation has been used to compare and verify the results based on which role the interviewee had.
+The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents.
+Data triangulation was performed to compare and verify the results based on which role the interviewee had.
 The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes.
-The interviews have been carried out using a mix of open-ended and close-ended questions, and a semi-structured approach has been used.
-The fact that the interviewees have widely differing backgrounds and roles was the main reason for not using a structured approach.
-A semi-structured approach was chosen over a unstructured approach to be able to get results that are closely related to eachother, so that meaningful comparison and analysis can be carried out.
-Company X's change process documentation has also been analysed to provide further depth to the analysis.
+The interviews were carried out using a mix of open-ended and close-ended questions in combination with a semi-structured approach.
+The fact that the interviewees had widely differing backgrounds and roles was the main reason for not using a structured approach.
+A semi-structured approach was chosen over a unstructured approach to be able to obtain results which were closely related to each other.
+This was performed so that meaningful comparison and analysis could be carried out.
+Company X's change process documentation was also analysed to provide further depth to the analysis already performed.
 Please see Appendix A for a full list of interview questions.
@@
 \SubSection{Data Analysis}
-The data analysis of the interviews has been done in tandem with the data gathering to be able to iteratively improve the data collection process.
-This data analysis has had the main purpose of generating hypotheses and to refine the research questions.
-The interviews were analysed by manually reading and comparing answers.
-Spreadsheets and tables were also used to provide an overview of the results.
+The data analysis of the interviews were completed in tandem with the data gathering phase.
+This was performed so that we could iteratively improve upon the data collection process.
+The main purpose of analysing this data was to generate hypotheses and to refine the proposed research questions.
+The interviews were analysed by manually reading and comparing answers between the respondents.
+Spreadsheets and tables were used to provide an overview of the results.
 
-When all the interview data had been collected, the data analysis goal was switched to focus on confirmation of the hypothesis.
+Once all the interview data had been collected, the goal of the data analysis shifted to focus upon confirmation of the hypothesis.
 As mentioned in Section IV.
-C, data triangulation was the main tool used to confirm the hypothesis.
+C, data triangulation was the primary tool used to confirm the hypothesis.
 

### 2015-02-16 rmtw/a3/latex8.tex
Therefore

@@
 
+Give a clear introduction to what we mean by different paradigms. Just introduce manual/mdsd and the difference.
+
 ​\Section{Introduction}
@@
 \SubSection{Problem Statement}
-The purpose of this paper is therefore to determine whether an organisation's development paradigm should be the basis for deciding which process and design changes to adopt.
+The purpose of this paper is therefore (XXX probably shouldn't use therefore to refer to the prev section.) to determine whether an organisation's development paradigm should be the basis for deciding which process and design changes to adopt.
 
@@
 \SubSection{Motivation for Research}
-Performing this study would therefore be an attempt at filling in a gap in literature.
+Performing this study would therefore (XXX same) be an attempt at filling in a gap in literature.
 Academia would be interested in this for its own merit or, most likely, as a stepping stone towards further research.
@@
 TBA
-\newpage
 
@@
 
-\Section{References}
-Make real ref list later
+\bibliographystyle{latex8}
+\bibliography{latex8}
 

### 2015-02-16 rmtw/a3/latex8.tex
Added RQs

@@
 \Section{Purpose of the Study}
-The purpose of this study is to explore how changes to software processes are incorporated into a company where differing development paradigms are used.
-This exploratory study will take place at a large and successful telecommunications company.
-Much of the qualitative data will originate from current employees via a series of interviews.
-While the study will only take place at a single location, it will be conducted in such a way that it is applicable to any company willing to partake.
+The purpose of this case study is to explore how changes to software processes are incorporated into a company where multiple development paradigms are used.
+The study has been designed for change agents and it has been conducted at the EPG department at Ericsson.
+At this stage in the research, the central phenomenon being studied, how changes are implemented in companies where more than one development paradigms are used, will be generally defined as implementing change in multi-paradigm environments.
 
 \SubSection{Research Question(s)}
-RQ: How is change managed in a company which has a split development strategy (e.g. mdsd+manual)?
-SRQ1: How can it be done better blabla?
-SRQ2: How can a company determine if a change will conflict with a current paradigm?
+RQ: How is change managed in multi-paradigm environments?
+SRQ1: What are the challanges of implementing change in multi-paradigm environments?
+SRQ2: How can a company determine if a change will conflict with the currently used development paradigms?
+SRQ3: How can an organisation's development paradigm be used as a basis for deciding which changes to adopt?
 
@@
 
-\Section{Threats to Validity}
-
 \begin{itemize}
@@
 \item Mention how the company was selected and what the criteria was (there was some lazy w)
+\item the documents analysis (triangulation) will mostly be used to verify what the change agents say
 \end{itemize}
+
+\Section{Threats to Validity}
 

### 2015-02-16 rmtw/a3/latex8.tex
Small changes to a few sections

--- 2015-02-16 rmtw/a3/latex8.tex
@@
 \SubSection{Problem Statement}
-The purpose of this paper is therefore to determine whether an organisation's development paradigm should be the basis for deciding which process and design changes to adopt.
-
-%Maybe not this bit-----------------------------------------------------------
-To explore this area, we focus on process and design practices that have been introduced at Ericsson EPG.
-%Maybe not this bit-----------------------------------------------------------
+%big problem in industry implementing change
+%could a reason for this be because they're trying to fit one thing onto something different. Focus on implementation rather than what the changes are
 

### 2015-02-16 rmtw/a3/latex8.tex

--- 2015-02-16 rmtw/a3/latex8.tex
@@
 \SubSection{Problem Statement}
-The purpose of this paper is therefore (XXX probably shouldn't use therefore to refer to the prev section.) to determine whether an organisation's development paradigm should be the basis for deciding which process and design changes to adopt.
-
-%Maybe not this bit-----------------------------------------------------------
-To explore this area, we focus on process and design practices that have been introduced at Ericsson EPG.
-%Maybe not this bit-----------------------------------------------------------
+%big problem in industry implementing change
+%could a reason for this be because they're trying to fit one thing onto something different. Focus on implementation rather than what the changes are
 

### 2015-02-16 rmtw/a3/latex8.tex
Spellcheck

@@
 Give a clear introduction to what we mean by different paradigms. Just introduce manual/mdsd and the difference.
+
+give examples of what we mean by changes, i.e. implementing scrum, TDD.
 
@@
 RQ: How is change managed in multi-paradigm environments?
-SRQ1: What are the challanges of implementing change in multi-paradigm environments?
+SRQ1: What are the challenges of implementing change in multi-paradigm environments?
 SRQ2: How can a company determine if a change will conflict with the currently used development paradigms?
@@
 \item Mention how many of each role and why each role was included (triangulation)
-\item convenience sampling (yo uhave contact at company already and use them) and maximum varation (i aim to have as many as possible)
+\item convenience sampling (yo uhave contact at company already and use them) and maximum variation (i aim to have as many as possible)
 \item Mention how the company was selected and what the criteria was (there was some lazy w)
@@
 \Section{Threats to Validity}
+%getting too close, potential bias
+%change manager bias, if they implemented
+%generalisability
+
+%Check text for more.
+%% Talk about generalisability tomorrow with willski
+
+%gatekeeper to help sample, he could, in some way, select persons that are positive. We give up control to the judgement of the gatekeeper
+
+%only doing it at EPG.
+%doing it at different times, only one company -> generalise
 

### 2015-02-16 rmtw/a3/latex8.tex
Draft of Validity threats and new introduction

@@
 
+Paradigms in this context will be considered to be those which relate to software development.
+For example, we would consider Model Driven Software Development[CITE] to be a paradigm.
+Specifically, in this situation with our partner company, we use the term manual coding to mean development without the use of any particular paradigm.
+The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process.
+Other examples of change could be seen as a company wishing to implement processes such as Scrum or introducing Test Driven Development.
+
 \SubSection{Problem Statement}
-%big problem in industry implementing change
-%could a reason for this be because they're trying to fit one thing onto something different. Focus on implementation rather than what the changes are
+Change is always a challenge in industry and one that is not going away anytime soon.
+This is especially true when it comes to changing development processes or paradigms.
+One possible reason that these changes are far more difficult than others could be because the companies introducing these changes overlook the possibility that the changes they wish to implement are at odds with their current development paradigms or processes.
+This is the problem that this paper will attempt to address; how industry can determine what changes are suitable to implement taking into consideration their existing paradigms?
 
@@
 \Section{Threats to Validity}
-%getting too close, potential bias
-%change manager bias, if they implemented
-%generalisability
 
-%Check text for more.
-%% Talk about generalisability tomorrow with willski
+While designing the study, validity concerns were taken into consideration.
+The most pressing of which would be the limited scope of the study.
+The fact that the study only occurred in a subset of Ericsson and not a larger part of the company means that we cannot reliably make any generalities about the results.
+This is something that could be overcome during a potential triangulation period.
+For example, further studies could be conducted within Ericsson at other departments which could then be used to strengthen or diminish the results from this study.
 
-%gatekeeper to help sample, he could, in some way, select persons that are positive. We give up control to the judgement of the gatekeeper
-
-%only doing it at EPG.
-%doing it at different times, only one company -> generalise
+Other validity issues concern bias.
+The potential for bias lies with both the subjects and researchers of the study [maybe cite?].
+There is a risk that we, the researches, can be drawn too close to the company and as such might overlook or miss certain results that would otherwise be obvious to someone not so intimately involved.
+The potential for this bias is greater considering one of the researchers has previously held employment in the EPG department where the study took place.
+This potential for bias extends further to the respondents of the interviews.
+The respondents might have been intimidated by the interview procedure and potentially for repercussions to their positions within the company based on their answers to the questions.
+This is entirely possible despite the assurance that the responses would be anonymous.
+Finally, the gatekeeper is also a potential point of bias.
+In this study, the gatekeeper assisted with the sampling of potential interview candidates, while unlikely, there is potential that the gatekeeper could have selected individuals whom would have a favourable opinion about the material that the interview questions were concerned with.
 

### 2015-02-16 rmtw/a3/latex8.tex
Finished up my sections

@@
 
-\Section{Case Company Description}
-TBA
+\Section{Methodology}
 
-\Section{Methodology}
+\SubSection{Case Company Description}
+The subject case organisation in this study is Ericsson.
+Ericsson operates in the domain of communications technology, and their main products are in the domain of mobility, broadband and cloud-based services \cite{a7} \cite{a8}.
+Ericsson has 117,508 employees (as of September 30, 2014), 25,300 of which work in R\&D (Research and Development).
+\cite{a7}.
+
+Our research has been conducted at the Evolved Packet Gateway (EPG) department of Ericsson.
+The EPG department consists of approximately 700 employees, the majority of hwich work on software development related tasks.
+EPG delivers and maintains the EPG product which is a part of Ericsson's product for deployment of Long Term Evolution (LTE) networks \cite{a9}.
+The EPG product serves as a gateway between Ericsson's packet core network and other packet data networks, such as the Internet \cite{a9}.
+The EPG product is utilized in technologies such as 2G, 2G+, 3G, 4G and Wi-Fi hotspots \cite{a9}.
+
+The company was sampled through convenience sampling, and a maximum varation strategy was used.
+As such, the goal was to include as many companies as possible in this study.
+Since the study is conducted at a large communications technology company, it indicates that the study may be generalisable to similar companies.
 
@@
 The study has been conducted with an exploratory goal in mind.
-Analysing how Company X tackle the problems related to the research questions has been the most central part of the study.
+Analysing how Ericsson tackle the problems related to the research questions has been the most central part of the study.
 Because of the exploratory nature of the study, a flexible process design has been used.
@@
 The reason for this is that the goal of our study is to analyse MDSD, which is a common practice in software engineering, in a very specific setting.
-This line of thought is supported by Runesson \& Höst in CITE XXX.
-Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies CITE XXX.
+This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}.
+Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}.
 
@@
 Although a flexible approach was taken, major effort was spent on planning the study.
-Most of the planning was related to communicating with Company X to facilitate the interviews.
-A time-line for the interviews was created and established with company X.
+Most of the planning was related to communicating with Ericsson to facilitate the interviews.
+A time-line for the interviews was created and established with Ericsson.
 The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage.
@@
 \SubSection{Preparation for Data Collection}
-During this stage the interviews were designed.
-The initial design of the interview was pilot tested on three employees of Company X.
-The results from the pilot tests were used to test if the interviews would fulfil the objective of the study.
-The number of subjects for the main interviews was 15.
-They were sampled randomly from employment records at Company X.
+The interviewees were sampled using random sampling, with help of a gatekeeper at the company.
+The reason a gatekeeper was used was to reduce research bias.
+The random sampling was done on official employee records.
+The number of subjects for the interviews was (XXX or were?) 15.
+The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents, and 5 of each role were interviewed.
+The main reason the three different roles were included was to be able to reduce reserach bias through data triangulation.
+
+The interviewees were selected based on two criterion: they must have been employed at Ericsson for a minimum of 5 years and they must work at the EPG department.
+5 years expirence was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson.
+The reason only employees from EPG were accepted was to ensure that the population was cohesive.
 
 During this stage, all ethical precautions of the study were taken.
-It was established that Company X wanted to remain anonymous and that all interviews must happen on a voluntary basis.
-An agreement on to what extent Company X's documentation could be used was also made during this stage.
-%Add what was agreed
+It was established that Ericsson did not require anonymity and that all interviews must happen on a voluntary basis.
+An agreement that Ericsson's change process documentation could be used as a data source in the study was also made.
 
 \SubSection{Data Gathering}
-The data has mainly been gathered through first degree interviews CITE LETHBRIDGE 2005 XXX.
-The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents.
-Data triangulation was performed to compare and verify the results based on which role the interviewee had.
-The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes.
+The data has mainly been gathered through first degree interviews \cite{lethbridge2005studying}.
 The interviews were carried out using a mix of open-ended and close-ended questions in combination with a semi-structured approach.
@@
 This was performed so that meaningful comparison and analysis could be carried out.
-Company X's change process documentation was also analysed to provide further depth to the analysis already performed.
-Please see Appendix A for a full list of interview questions.
+Data triangulation was performed to compare and verify the results based on which role the interviewee had.
+The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes.
+
+Ericsson's change process documentation was also analysed to provide further depth to the analysis already performed.
+The documentation was also used to triangulate the interview answers that related to Ericsson's change strategy.
+The reason for was to reduce risks of research bias.
+Please see Appendix A (XXX or 1?) for a full list of interview questions.
 
@@
 \item Create questions for your interviews (include the questions in your report)
-\item Discuss validity threats
-\item Triangulation = counteract research bias
-\item In meth, mention how the interviewees were selected and contacted (you have a gatekeeper which selects the people for you)
-\item Mention how many of each role and why each role was included (triangulation)
-\item convenience sampling (yo uhave contact at company already and use them) and maximum variation (i aim to have as many as possible)
 \item Mention how the company was selected and what the criteria was (there was some lazy w)
-\item the documents analysis (triangulation) will mostly be used to verify what the change agents say
 \end{itemize}

### 2015-02-17 rmtw/a3/latex8.tex
Fixed visual stuff
Fixed a typo in the introduction

@@
 
-\documentclass[times, 10pt,twocolumn]{Article} 
+\documentclass[10pt,twocolumn]{article} 
 \usepackage{latex8}
-\usepackage{times}
+\usepackage{url}
 
@@
 \begin{document}
+
+\overfullrule=2cm
 
@@
 Paradigms in this context will be considered to be those which relate to software development.
-For example, we would consider Model Driven Software Development[CITE] to be a paradigm.
-Specifically, in this situation with our partner company, we use the term manual coding to mean development without the use of any particular paradigm.
+For example, we would consider Model Driven Software Development[CITE] to be a development paradigm.
+In this study we use the term manual coding to mean development without the use of any particular paradigm.
 The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process.
-Other examples of change could be seen as a company wishing to implement processes such as Scrum or introducing Test Driven Development.
+Our definition of change is not limited to the aforementioned examples, we would consider any changes to development paradigms such as a company wishing to implement processes such as Scrum or introducing Test Driven Development.
 
 \SubSection{Problem Statement}
-Change is always a challenge in industry and one that is not going away anytime soon.
+Change is always a challenge in industry and one that is not going away any time soon.
 This is especially true when it comes to changing development processes or paradigms.

### 2015-02-17 rmtw/a3/latex8.tex
Added interview and spell check

@@
 %Deficiencies introduction model
-
-Give a clear introduction to what we mean by different paradigms. Just introduce manual/mdsd and the difference.
-
-give examples of what we mean by changes, i.e. implementing scrum, TDD.
 
@@
 RQ: How is change managed in multi-paradigm environments?
+
 SRQ1: What are the challenges of implementing change in multi-paradigm environments?
+
 SRQ2: How can a company determine if a change will conflict with the currently used development paradigms?
+
 SRQ3: How can an organisation's development paradigm be used as a basis for deciding which changes to adopt?
@@
 Our research has been conducted at the Evolved Packet Gateway (EPG) department of Ericsson.
-The EPG department consists of approximately 700 employees, the majority of hwich work on software development related tasks.
+The EPG department consists of approximately 700 employees, the majority of which work on software development related tasks.
 EPG delivers and maintains the EPG product which is a part of Ericsson's product for deployment of Long Term Evolution (LTE) networks \cite{a9}.
 The EPG product serves as a gateway between Ericsson's packet core network and other packet data networks, such as the Internet \cite{a9}.
-The EPG product is utilized in technologies such as 2G, 2G+, 3G, 4G and Wi-Fi hotspots \cite{a9}.
+The EPG product is utilised in technologies such as 2G, 2G+, 3G, 4G and Wi-Fi hotspots \cite{a9}.
 
-The company was sampled through convenience sampling, and a maximum varation strategy was used.
+The company was sampled through convenience sampling, and a maximum variation strategy was used.
 As such, the goal was to include as many companies as possible in this study.
@@
 The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents, and 5 of each role were interviewed.
-The main reason the three different roles were included was to be able to reduce reserach bias through data triangulation.
+The main reason the three different roles were included was to be able to reduce research bias through data triangulation.
 
 The interviewees were selected based on two criterion: they must have been employed at Ericsson for a minimum of 5 years and they must work at the EPG department.
-5 years expirence was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson.
+5 years experience was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson.
 The reason only employees from EPG were accepted was to ensure that the population was cohesive.
@@
 \Section{Acknowledgements}
-Write who did what
+John had the main responsibility for sections 1 \& 2.
+William had the main responsibility for section 3.
+Section 4 and the interview questions were written together.
+We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John.
+
+We have re-used some material from our DIT037 course.
+(Mostly in literature review and case company description).
+Because of this some of the text might show up on Urkund.
+For the most important parts, such as methodology and research questions we have not used any material from our DIT035 paper.
+
+\newpage
+\appendix
+
+\section{Interview Questions}
+\begin{itemize}
+\item \textbf{Organisation}
+\begin{itemize}
+\item How long have you worked at Ericsson?
+\item How would you describe your role?
+\item Do you work in a manual coding or MDSD team?
+\end{itemize}
+
+\item \textbf{General Change}
+\begin{itemize}
+\item Do you feel that the changes in Ericsson have had a clear plan?
+\item How have the goals of the changes been communicated? 
+\item What has been the largest obstacle for change?
+\item What has been the main driving for change previously?
+\item Do you feel that some previously introduced changes do not work well together?
+\item Do you feel that the changes are targeted towards individuals or teams? 
+\item If you have had previous experience of changes, how is change at Ericsson different? 
+\end{itemize}
+
+\item \textbf{Multi-paradigm Change}
+\begin{itemize}
+\item Do you feel that changes are implemented differently based on what development paradigm is used?
+\item Do you feel that the implemented changes work well with both paradigms? 
+\item Do you feel that anything has changed in the change strategy since MDSD was introduced? 
+\end{itemize}
+
+\end{itemize}
 

### 2015-02-17 rmtw/a3/latex8.tex
Small changes
Changes to case study design

@@
 The purpose of this case study is to explore how changes to software processes are incorporated into a company where multiple development paradigms are used.
-The study has been designed for change agents and it has been conducted at the EPG department at Ericsson.
+The results of the study have been designed for change agents and it has been conducted at the EPG department at Ericsson.
 At this stage in the research, the central phenomenon being studied, how changes are implemented in companies where more than one development paradigms are used, will be generally defined as implementing change in multi-paradigm environments.
@@
 The research has been conducted using a case study approach.
-The reason for this is that the goal of our study is to analyse MDSD, which is a common practice in software engineering, in a very specific setting.
+The reason for this is that the goal of our study is to analyse how changes are implemented in the context of multi-paradigm development environments in software engineering.
 This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}.
 Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}.
+Another reason for conducting this study using a case study approach is that there is little existing research conducted in the area, and that input from industry is vital to the success of the research.
 

### 2015-02-17 rmtw/a3/latex8.tex
Removed itemize, fixed issues in design and prep sections

--- 2015-02-17 rmtw/a3/latex8.tex
@@
 \SubSection{Case Company Description}
-The subject case organisation in this study is Ericsson.
-Ericsson operates in the domain of communications technology, and their main products are in the domain of mobility, broadband and cloud-based services \cite{a7} \cite{a8}.
+The subject case organisation in this study is Ericsson AB.
+Ericsson operates in the domain of communications technology, their main products are in the domain of mobility, broadband and cloud-based services \cite{a7} \cite{a8}.
 Ericsson has 117,508 employees (as of September 30, 2014), 25,300 of which work in R\&D (Research and Development).
@@
 The study has been conducted with an exploratory goal in mind.
-Analysing how Ericsson tackle the problems related to the research questions has been the most central part of the study.
-Because of the exploratory nature of the study, a flexible process design has been used.
+Analysing how Ericsson tackles the problems related to the research questions has been the central part of the study.
+Due to the exploratory nature of the study, a flexible process design has been used.
 The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study.
@@
 The interviewees were sampled using random sampling, with help of a gatekeeper at the company.
-The reason a gatekeeper was used was to reduce research bias.
-The random sampling was done on official employee records.
-The number of subjects for the interviews was (XXX or were?) 15.
-The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents, and 5 of each role were interviewed.
+The reason a gatekeeper was used was to reduce research bias but does eliminate it.
+Random sampling was performed on official employee records.
+15 employees were chosen to be the subjects for the interviews.
+The subjects were divided into three sub-groups; managers, developers and change agents with 5 of each role being interviewed.
 The main reason the three different roles were included was to be able to reduce research bias through data triangulation.
@@
 C, data triangulation was the primary tool used to confirm the hypothesis.
-
-\begin{itemize}
-\item Create questions for your interviews (include the questions in your report)
-\item Mention how the company was selected and what the criteria was (there was some lazy w)
-\end{itemize}
 

### 2015-02-17 rmtw/a3/latex8.tex

@@
 The study has been conducted with an exploratory goal in mind.
-Analysing how Ericsson tackles the problems related to the research questions has been the central part of the study.
+Analysing how Ericsson tackle the problems related to the research questions has been the central part of the study.
 Due to the exploratory nature of the study, a flexible process design has been used.

### 2015-02-17 rmtw/a3/latex8.tex
XXX
Changes to methodology

@@
 The documentation was also used to triangulate the interview answers that related to Ericsson's change strategy.
-The reason for was to reduce risks of research bias.
-Please see Appendix A (XXX or 1?) for a full list of interview questions.
+The reason for this was to reduce the risks of research bias.
+Please see Appendix A for a full list of interview questions.
 
 \SubSection{Data Analysis}
-The data analysis of the interviews were completed in tandem with the data gathering phase.
+Data analysis of the interviews was completed in tandem with the data gathering phase.
 This was performed so that we could iteratively improve upon the data collection process.
@@
 Other validity issues concern bias.
-The potential for bias lies with both the subjects and researchers of the study [maybe cite?].
+The potential for bias lies with both the subjects and the researchers of our study.
 There is a risk that we, the researches, can be drawn too close to the company and as such might overlook or miss certain results that would otherwise be obvious to someone not so intimately involved.

### 2015-02-17 rmtw/a3/latex8.tex
YOLO

@@
 
-\title{Assignment 3}
+\title{Implementing Change in Multi-paradigm Environments, a Case Study}
 
@@
 Paradigms in this context will be considered to be those which relate to software development.
-For example, we would consider Model Driven Software Development[CITE] to be a development paradigm.
-In this study we use the term manual coding to mean development without the use of any particular paradigm.
+For example, we would consider Model Driven Software Development to be a development paradigm.
+In this study we use the term manual coding to describe development without the use of any particular paradigm.
 The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process.
@@
 \SubSection{Motivation for Research}
-Performing this study would therefore (XXX same) be an attempt at filling in a gap in literature.
+A major motivation for this study is to fill a gap in the literature, since there is no previous research which analyses how change is managed in multi-paradigm settings.
 Academia would be interested in this for its own merit or, most likely, as a stepping stone towards further research.

### 2015-02-17 rmtw/a3/latex8.tex
Changes in validity section
Y O L O

@@
 
-However, there are is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms.
+However, there is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms.
 
@@
 
-\SubSection{Research Question(s)}
+\SubSection{Research Questions}
 RQ: How is change managed in multi-paradigm environments?
@@
 For example, further studies could be conducted within Ericsson at other departments which could then be used to strengthen or diminish the results from this study.
+Furthermore, our study only involved model driven development and manual coding.
+As such we cannot generalise about the applicability concerning other paradigms.
 
@@
 Because of this some of the text might show up on Urkund.
-For the most important parts, such as methodology and research questions we have not used any material from our DIT035 paper.
+For the most important parts, such as methodology and research questions we have not used any material from our DIT037 paper.
 

### 2015-02-17 rmtw/a3/latex8.tex
removed scentence regarding previous employment from validity threats

@@
 There is a risk that we, the researches, can be drawn too close to the company and as such might overlook or miss certain results that would otherwise be obvious to someone not so intimately involved.
-The potential for this bias is greater considering one of the researchers has previously held employment in the EPG department where the study took place.
-This potential for bias extends further to the respondents of the interviews.
+The potential for bias extends further to the respondents of the interviews.
 The respondents might have been intimidated by the interview procedure and potentially for repercussions to their positions within the company based on their answers to the questions.

### 2015-02-18 rmtw/a4/latex8.tex
Added a4 Y O L O

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: John Burchell & William Granli $
%  $Date: 2015/01/21 15:20:59 $
%  $Revision: 1.0
%

\documentclass[10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{url}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{Assignment 4}

% author names and affiliations
\author{John Burchell and William Granli \\
john.a.burchell, william.granli@gmail.com}

\maketitle
\thispagestyle{empty}

%-------------------------------------------------------------------------

%Deficiencies introduction model

​\Section{Introduction}
Software inspections have since its inception [1] more than
25 years ago spawned quite some interest both from the
research community and industrial practice. The research
includes changes to the inspection process, e.g. [2], support to
the process, e.g. [3] and empirical studies, e.g. [4]. The
suggested improvements include active design reviews [5] and
perspective-based reading [6]. Industry has studied the
benefits of conducting software inspections [7].
The objective of this study is to compare and hence
evaluate how well the use-case based reading performs in
comparison to other methods. The study presents a controlled
experiment where use-case based reading is compared to
checklist-based reading.

\Section{Purpose of the Study}
* Purpose statement (copy paste from the file ‘Experiment\_Design.pdf’ file)

* Research Questions (copy paste from the file ‘Experiment\_Design.pdf’ file)

* Hypothesis (copy paste from the file ‘Experiment\_Design.pdf’ file)

\Section{Methodology}
* Method(s) for analyzing the data (Statistical analysis)

* Motivation of why these statistical tests where used

\Section{Results}
Read \url{https://dl.dropboxusercontent.com/u/2437798/Juristo%20Basics%20of%20Software%20Engineering%20Experimentation.pdf} pp. 133

*Report the results

*Discuss what does the results means, how do we interpret it

\bibliographystyle{latex8}
\bibliography{latex8}

\Section{Acknowledgements}
U w0T m8

\end{document}

### 2015-02-23 rmtw/a5/latex8.tex
Added a5

--- 2015-02-17 rmtw/a3/latex8.tex
@@
 
-\overfullrule=2cm
-
-\title{Implementing Change in Multi-paradigm Environments, a Case Study}
+\title{Assignment 4}
 
@@
 
-Coping with change in the software development domain is difficult at best, it is further exasperated by trying to apply changes that do not mesh well with existing development paradigms.
-How then, do large companies, especially those utilising multiple development paradigms, cope with this kind of change?
-
-Paradigms in this context will be considered to be those which relate to software development.
-For example, we would consider Model Driven Software Development to be a development paradigm.
-In this study we use the term manual coding to describe development without the use of any particular paradigm.
-The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process.
-Our definition of change is not limited to the aforementioned examples, we would consider any changes to development paradigms such as a company wishing to implement processes such as Scrum or introducing Test Driven Development.
-
-\SubSection{Problem Statement}
-Change is always a challenge in industry and one that is not going away any time soon.
-This is especially true when it comes to changing development processes or paradigms.
-One possible reason that these changes are far more difficult than others could be because the companies introducing these changes overlook the possibility that the changes they wish to implement are at odds with their current development paradigms or processes.
-This is the problem that this paper will attempt to address; how industry can determine what changes are suitable to implement taking into consideration their existing paradigms?
+\SubSection{Statement of the Problem}
 
 \SubSection{Existing Literature}
-According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI)\cite{pettersson2008practitioner}\cite{unterkalmsteiner2012evaluation} or change management (CM) strategies.
-SPI is an attempt to alter an existing company or organisations software process, the main intention of which is to increase product quality, time to market all the while reducing inefficiency and other obstacles for creating good software.
 
-Similar to SPI is the concept of Evidence Based Software Engineering \cite{dyba2005evidence}.
-EBSE can be used as support for SPI, as suggested by the creators of the strategy.
-The main aim of which is to find a technology which is suitable for use and to then implement it in an organisation.
+\SubSection{Motivation for Study}
 
-CM on the other hand could be seen as an umbrella for a plethora of theories and strategies.
-An example of a theory is the concept of innovation values fit by \cite{klein1996challenge} which aims to describe if and when a company should make changes, based upon how a potential change fits with the values currently held by the company.
-
-In 2002 Hall, Rainer and Baddoo \cite{hall2002implementing} published a report wherein they illustrated results of a study which looked at 85 companies throughout the UK.
-The study focused mostly on how the companies perform SPI and how effective their efforts were.
-The authors discovered that, while most companies do attempt SPI, many are unsuccessful due to a combined lack of evaluation and funding.
-
-A further, more specific example is a study conducted by Staron \cite{staron2006adopting}.
-In this study a case study is conducted with two companies wishing or in the process of adopting MDSD.
-In the findings, Staron provides a set of conditions for adopting MDSD, one being the compatibility of MDSD and existing principles in the company.
-Staron states that the adoption of this new process must be usable by the previous processes in place \cite{staron2006adopting}.
-He concludes by stating that this compatibility is especially important for larger companies due to the heavy effort required to implement the change.
-In a second study \cite{staron2008transitioning}, Staron provides possible reasons for the adoption of MDSD to fail.
-He suggests that the large investment in time and money, immature technology and organisational resistance are all factors to overcome in the adoption of new processes.
-
-However, there is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms.
-
-\SubSection{Motivation for Research}
-A major motivation for this study is to fill a gap in the literature, since there is no previous research which analyses how change is managed in multi-paradigm settings.
-Academia would be interested in this for its own merit or, most likely, as a stepping stone towards further research.
-
-Industry is just as likely to be interested as change is something they face regularly.
-If this study can help to shed some light about specific methods of to help accommodate change.
-The study will be conducted in tandem with an organisation, to which the results would also be of great value.
-The organisation in question has had problems in the past with implementing effective change to keep up with their competition.
-
-Furthermore, companies that operate in a similar, or even a different manner would most likely be able to appreciate the efforts made in the study.
-In the most hopeful of cases, applying the lessons learned to their own situations.
-
-Given that MDSD has seen a considerable rise in adoption by many companies\cite{millermda}, the results of the research would undoubtedly be of use to these companies also.
+*5 references only needed for above (re-use from a1)
 
 \Section{Purpose of the Study}
-The purpose of this case study is to explore how changes to software processes are incorporated into a company where multiple development paradigms are used.
-The results of the study have been designed for change agents and it has been conducted at the EPG department at Ericsson.
-At this stage in the research, the central phenomenon being studied, how changes are implemented in companies where more than one development paradigms are used, will be generally defined as implementing change in multi-paradigm environments.
+Purpose leading into RQs
 
-\SubSection{Research Questions}
-RQ: How is change managed in multi-paradigm environments?
-
-SRQ1: What are the challenges of implementing change in multi-paradigm environments?
-
-SRQ2: How can a company determine if a change will conflict with the currently used development paradigms?
-
-SRQ3: How can an organisation's development paradigm be used as a basis for deciding which changes to adopt?
+\SubSection{Research Question(s)}
+One clear main research question
+Sub qs
 
@@
 
-\SubSection{Case Company Description}
-The subject case organisation in this study is Ericsson AB.
-Ericsson operates in the domain of communications technology, their main products are in the domain of mobility, broadband and cloud-based services \cite{a7} \cite{a8}.
-Ericsson has 117,508 employees (as of September 30, 2014), 25,300 of which work in R\&D (Research and Development).
-\cite{a7}.
-
-Our research has been conducted at the Evolved Packet Gateway (EPG) department of Ericsson.
-The EPG department consists of approximately 700 employees, the majority of which work on software development related tasks.
-EPG delivers and maintains the EPG product which is a part of Ericsson's product for deployment of Long Term Evolution (LTE) networks \cite{a9}.
-The EPG product serves as a gateway between Ericsson's packet core network and other packet data networks, such as the Internet \cite{a9}.
-The EPG product is utilised in technologies such as 2G, 2G+, 3G, 4G and Wi-Fi hotspots \cite{a9}.
-
-The company was sampled through convenience sampling, and a maximum variation strategy was used.
-As such, the goal was to include as many companies as possible in this study.
-Since the study is conducted at a large communications technology company, it indicates that the study may be generalisable to similar companies.
-
-\SubSection{Case Study Design}
-The study has been conducted with an exploratory goal in mind.
-Analysing how Ericsson tackle the problems related to the research questions has been the central part of the study.
-Due to the exploratory nature of the study, a flexible process design has been used.
-The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study.
-The research has been conducted using a case study approach.
-The reason for this is that the goal of our study is to analyse how changes are implemented in the context of multi-paradigm development environments in software engineering.
-This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}.
-Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}.
-Another reason for conducting this study using a case study approach is that there is little existing research conducted in the area, and that input from industry is vital to the success of the research.
-
-During the initial stage of the study, careful planning was conducted.
-The two major goals of this phase were to find meaningful objectives with an appropriate design for the research and secondly to facilitate and design the interviews.
-Although a flexible approach was taken, major effort was spent on planning the study.
-Most of the planning was related to communicating with Ericsson to facilitate the interviews.
-A time-line for the interviews was created and established with Ericsson.
-The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage.
-
-\SubSection{Preparation for Data Collection}
-The interviewees were sampled using random sampling, with help of a gatekeeper at the company.
-The reason a gatekeeper was used was to reduce research bias but does eliminate it.
-Random sampling was performed on official employee records.
-15 employees were chosen to be the subjects for the interviews.
-The subjects were divided into three sub-groups; managers, developers and change agents with 5 of each role being interviewed.
-The main reason the three different roles were included was to be able to reduce research bias through data triangulation.
-
-The interviewees were selected based on two criterion: they must have been employed at Ericsson for a minimum of 5 years and they must work at the EPG department.
-5 years experience was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson.
-The reason only employees from EPG were accepted was to ensure that the population was cohesive.
-
-During this stage, all ethical precautions of the study were taken.
-It was established that Ericsson did not require anonymity and that all interviews must happen on a voluntary basis.
-An agreement that Ericsson's change process documentation could be used as a data source in the study was also made.
-
-\SubSection{Data Gathering}
-The data has mainly been gathered through first degree interviews \cite{lethbridge2005studying}.
-The interviews were carried out using a mix of open-ended and close-ended questions in combination with a semi-structured approach.
-The fact that the interviewees had widely differing backgrounds and roles was the main reason for not using a structured approach.
-A semi-structured approach was chosen over a unstructured approach to be able to obtain results which were closely related to each other.
-This was performed so that meaningful comparison and analysis could be carried out.
-Data triangulation was performed to compare and verify the results based on which role the interviewee had.
-The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes.
-
-Ericsson's change process documentation was also analysed to provide further depth to the analysis already performed.
-The documentation was also used to triangulate the interview answers that related to Ericsson's change strategy.
-The reason for this was to reduce the risks of research bias.
-Please see Appendix A for a full list of interview questions.
-
-\SubSection{Data Analysis}
-Data analysis of the interviews was completed in tandem with the data gathering phase.
-This was performed so that we could iteratively improve upon the data collection process.
-The main purpose of analysing this data was to generate hypotheses and to refine the proposed research questions.
-The interviews were analysed by manually reading and comparing answers between the respondents.
-Spreadsheets and tables were used to provide an overview of the results.
-
-Once all the interview data had been collected, the goal of the data analysis shifted to focus upon confirmation of the hypothesis.
-As mentioned in Section IV.
-C, data triangulation was the primary tool used to confirm the hypothesis.
-
-\Section{Threats to Validity}
-
-While designing the study, validity concerns were taken into consideration.
-The most pressing of which would be the limited scope of the study.
-The fact that the study only occurred in a subset of Ericsson and not a larger part of the company means that we cannot reliably make any generalities about the results.
-This is something that could be overcome during a potential triangulation period.
-For example, further studies could be conducted within Ericsson at other departments which could then be used to strengthen or diminish the results from this study.
-Furthermore, our study only involved model driven development and manual coding.
-As such we cannot generalise about the applicability concerning other paradigms.
-
-Other validity issues concern bias.
-The potential for bias lies with both the subjects and the researchers of our study.
-There is a risk that we, the researches, can be drawn too close to the company and as such might overlook or miss certain results that would otherwise be obvious to someone not so intimately involved.
-The potential for bias extends further to the respondents of the interviews.
-The respondents might have been intimidated by the interview procedure and potentially for repercussions to their positions within the company based on their answers to the questions.
-This is entirely possible despite the assurance that the responses would be anonymous.
-Finally, the gatekeeper is also a potential point of bias.
-In this study, the gatekeeper assisted with the sampling of potential interview candidates, while unlikely, there is potential that the gatekeeper could have selected individuals whom would have a favourable opinion about the material that the interview questions were concerned with.
+\begin{itemize}
+\item Describe and explain the research strategy (i.e. SLR) and investigation methods that will be used for the study. 
+\item Motivate your choice of experiment using relevant references. 
+\item Search string including keywords and used databases
+\item inclusion/exlusion criteria
+\item data extraction
+\item data synthesis
+\item quality assessment
+\end{itemize}
 
@@
 \Section{Acknowledgements}
-John had the main responsibility for sections 1 \& 2.
-William had the main responsibility for section 3.
-Section 4 and the interview questions were written together.
-We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John.
-
-We have re-used some material from our DIT037 course.
-(Mostly in literature review and case company description).
-Because of this some of the text might show up on Urkund.
-For the most important parts, such as methodology and research questions we have not used any material from our DIT037 paper.
-
-\newpage
-\appendix
-
-\section{Interview Questions}
-\begin{itemize}
-\item \textbf{Organisation}
-\begin{itemize}
-\item How long have you worked at Ericsson?
-\item How would you describe your role?
-\item Do you work in a manual coding or MDSD team?
-\end{itemize}
-
-\item \textbf{General Change}
-\begin{itemize}
-\item Do you feel that the changes in Ericsson have had a clear plan?
-\item How have the goals of the changes been communicated? 
-\item What has been the largest obstacle for change?
-\item What has been the main driving for change previously?
-\item Do you feel that some previously introduced changes do not work well together?
-\item Do you feel that the changes are targeted towards individuals or teams? 
-\item If you have had previous experience of changes, how is change at Ericsson different? 
-\end{itemize}
-
-\item \textbf{Multi-paradigm Change}
-\begin{itemize}
-\item Do you feel that changes are implemented differently based on what development paradigm is used?
-\item Do you feel that the implemented changes work well with both paradigms? 
-\item Do you feel that anything has changed in the change strategy since MDSD was introduced? 
-\end{itemize}
-
-\end{itemize}
+U w0T m8
 

### 2015-02-23 rmtw/a5/latex8.tex
Y O LO

@@
 
+kithcneham start
+
+\textbf{Planning the review}
+\begin{itemize}
+\item Identification of the need for a review (5.1)
+Check other SLRs in the field and evaluate them
+\item Commissioning a review (5.2)
+not needed
+\item Specifying the research question(s) (5.3)
+this is very impoirtant :)
+the search process must identify primary studies htat address the research questions
+the data extraction proccess must extract the data items needed to answer the questions
+the data analysis process must synthesise the data in such a way that the questions cna b eansewrd.
+
+read the questions in 5.3.1 to come up with similar ones for readability
+
+\item Developing a review protocol (5.4)
+
+\item Evaluating the review protocol (5.5)
+\end{itemize}
+
+\textbf{Conducting the review}
+\begin{itemize}
+\item Identification of research (6.1)
+\item Selection of primary studies (6.2)
+\item Study quality assessment (6.3)
+\item Data extraction and monitoring (6.4)
+\item Data synthesis
+\end{itemize}
+
+\textbf{Reporting the review}
+\begin{itemize}
+\item Specifying dissemination mechanisms (7.1)
+\item Formatting the main report (7.2)
+\item Evaluating the report (7.3)
+\end{itemize}
+
 \bibliographystyle{latex8}

### 2015-02-23 rmtw/a5/latex8.tex
Research question added
Added notes for problem statement

@@
 
-\title{Assignment 4}
+\title{Assignment 5}
 
@@
 \SubSection{Statement of the Problem}
+Companies don't know if adopting MDD will be beneficial in terms of money and improved software quality.
 
@@
 One clear main research question
-Sub qs
+RQ 1 - In which situations should companies expect MDD to be successfully adopted?
 
@@
 \item Search string including keywords and used databases
-\item inclusion/exlusion criteria
+\item inclusion/exclusion criteria
 \item data extraction
@@
 \item Specifying the research question(s) (5.3)
-this is very impoirtant :)
-the search process must identify primary studies htat address the research questions
-the data extraction proccess must extract the data items needed to answer the questions
-the data analysis process must synthesise the data in such a way that the questions cna b eansewrd.
+this is very important :)
+the search process must identify primary studies that address the research questions
+the data extraction process must extract the data items needed to answer the questions
+the data analysis process must synthesise the data in such a way that the questions can be answered.
 

### 2015-02-23 rmtw/a5/latex8.tex
john = fag

@@
 RQ 1 - In which situations should companies expect MDD to be successfully adopted?
+RQ1 alt: In which situations should companies expect that the adoption of MDD would lead to a performance boost?
+
+RQ 1.1:
+In which domain(s) has MDSD been the most successful?
+
+RQ 1.2:
+Which software development process has been most successfully used in conjunction with MDSD?
+
+RQ 1.3:
+What are the characteristics of systems where MDSD has been successfully implemented?
 

### 2015-02-24 rmtw/a5/latex8.tex
Improved the RQs a bit

--- 2015-02-23 rmtw/a5/latex8.tex
@@
 
-\SubSection{Research Question(s)}
-One clear main research question
-RQ 1 - In which situations should companies expect MDD to be successfully adopted?
+\SubSection{Research Questions}
+\begin{itemize}
+\item \textbf{RQ1:} In which situations should companies expect that changing to MDSD would lead to positive effects? 
+\item \textbf{RQ1.1:} In which domain(s) is MDSD the most successful? 
+\item \textbf{RQ1.2:} Which software development process(es) has been most successfully used in conjunction with MDSD?
+\item \textbf{RQ1.3:} What are the characteristics of the systems of the companies that successfully use MDSD?
+\end{itemize}
+
+\begin{itemize}
+\item They are probably not worded optimally... Here're some alturnutuves:
+\item In which situations should companies expect MDD to be successfully adopted?
+\item In which situations should companies expect that the adoption of MDD would lead to a performance boost?
+\end{itemize}
 

### 2015-02-24 rmtw/a5/latex8.tex
YoL0

@@
 \author{John Burchell and William Granli \\
-john.a.burchell, william.granli@gmail.com}
+john.a.burchell@gmail.com, william.granli@gmail.com}
 
@@
 
-%Deficiencies introduction model
+​\Section{Introduction}
+Coping with change in the software development domain is difficult at best, it is further exasperated by trying to apply changes that do not mesh well with existing development paradigms.
+How then, do large companies, especially those utilising multiple development paradigms, cope with this kind of change?
 
-​\Section{Introduction}
+Paradigms in this context will be considered to be those which relate to software development.
+For example, we would consider Model Driven Software Development to be a development paradigm.
+In this study we use the term manual coding to describe development without the use of any particular paradigm.
+The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process.
+Our definition of change is not limited to the aforementioned examples, we would consider any changes to development paradigms such as a company wishing to implement processes such as Scrum or introducing Test Driven Development.
 
@@
 \SubSection{Existing Literature}
+According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI)\cite{pettersson2008practitioner}\cite{unterkalmsteiner2012evaluation} or change management (CM) strategies.
+SPI is an attempt to alter an existing company or organisations software process, the main intention of which is to increase product quality, time to market all the while reducing inefficiency and other obstacles for creating good software.
+
+Similar to SPI is the concept of Evidence Based Software Engineering \cite{dyba2005evidence}.
+EBSE can be used as support for SPI, as suggested by the creators of the strategy.
+The main aim of which is to find a technology which is suitable for use and to then implement it in an organisation.
+
+CM on the other hand could be seen as an umbrella for a plethora of theories and strategies.
+An example of a theory is the concept of innovation values fit by \cite{klein1996challenge} which aims to describe if and when a company should make changes, based upon how a potential change fits with the values currently held by the company.
+
+In 2002 Hall, Rainer and Baddoo \cite{hall2002implementing} published a report wherein they illustrated results of a study which looked at 85 companies throughout the UK.
+The study focused mostly on how the companies perform SPI and how effective their efforts were.
+The authors discovered that, while most companies do attempt SPI, many are unsuccessful due to a combined lack of evaluation and funding.
+
+A further, more specific example is a study conducted by Staron \cite{staron2006adopting}.
+In this study a case study is conducted with two companies wishing or in the process of adopting MDSD.
+In the findings, Staron provides a set of conditions for adopting MDSD, one being the compatibility of MDSD and existing principles in the company.
+Staron states that the adoption of this new process must be usable by the previous processes in place \cite{staron2006adopting}.
+He concludes by stating that this compatibility is especially important for larger companies due to the heavy effort required to implement the change.
+In a second study \cite{staron2008transitioning}, Staron provides possible reasons for the adoption of MDSD to fail.
+He suggests that the large investment in time and money, immature technology and organisational resistance are all factors to overcome in the adoption of new processes.
+
+However, there is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms.
 

### 2015-02-24 rmtw/a5/latex8.tex
Intro

@@
 ​\Section{Introduction}
-Coping with change in the software development domain is difficult at best, it is further exasperated by trying to apply changes that do not mesh well with existing development paradigms.
-How then, do large companies, especially those utilising multiple development paradigms, cope with this kind of change?
+Ever since the first computer programs were written, researchers and developers have been working on new programming concepts in order to decrease the level of complexity needed to develop programs.
+The abstraction level has been increased with help of compilers, object-oriented programming (OOP) and Unified Modelling Language (UML).
+The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate OOP code.
 
-Paradigms in this context will be considered to be those which relate to software development.
-For example, we would consider Model Driven Software Development to be a development paradigm.
-In this study we use the term manual coding to describe development without the use of any particular paradigm.
-The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process.
-Our definition of change is not limited to the aforementioned examples, we would consider any changes to development paradigms such as a company wishing to implement processes such as Scrum or introducing Test Driven Development.
+The benefits of MDSD have consistently been reported in academia.
+Many large companies such as Ericsson and Volvo also use MDSD as a part of their development chain.
+In industry, however, MDSD struggles to make a (full) (x-wide) (XXX) breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.
 

### 2015-02-24 rmtw/a5/latex8.tex
Staronified the intro, nahamsayin

@@
 The abstraction level has been increased with help of compilers, object-oriented programming (OOP) and Unified Modelling Language (UML).
-The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate OOP code.
+The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate OOP code \cite{staron2006adopting}.
 
-The benefits of MDSD have consistently been reported in academia.
-Many large companies such as Ericsson and Volvo also use MDSD as a part of their development chain.
+The benefits of MDSD have consistently been reported in academia .
+Many large companies such as Ericsson, Volvo and ABB also use MDSD as a part of their development chain.
 In industry, however, MDSD struggles to make a (full) (x-wide) (XXX) breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.

### 2015-02-24 rmtw/a3_review/latex8.tex
Added review of group 8, assignment 3

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: John Burchell & William Granli $
%  $Date: 2015/01/21 15:20:59 $
%  $Revision: 1.0
%

\documentclass[times, 10pt,twocolumn]{IEEEtran} 
\usepackage{latex8}
\usepackage{times}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{Review of Group 8 by Group 1}

% author names and affiliations
\author{\IEEEauthorblockN{
  John Burchell\IEEEauthorrefmark{1} and
  William Granli\IEEEauthorrefmark{1}}

  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}

}

\maketitle
\thispagestyle{empty}

%-------------------------------------------------------------------------

\Section{Introduction \& Related Work}
The introduction was once again very well written. Good use of italicising the new and key terms meant that the phenomena and key ideas are easily identifiable.

``The introduction was once again very well written. Good use of italicising the new and key terms. '' However reads very strangely, I presume this was an oversight? The first paragraph of the related work section also sounds a little strange. The related work does a great job of giving a good background and introduction into. It seems to have been very well researched and there are convincing arguments for inclusions and exclusions of concepts.

\Section{Purpose Statement}

The purpose statement is clear but with one minor issue, there is no definition of expertise. What do you mean by expertise in this context, years of experience? How ``good'' a developer is, if so, compared to what or who? What their discipline is? Just a slight clarification would be nice. On the other hand, it was good to include a reason why you were ignoring personal ratings of expertise.

\Section{Research Question}
Research Questions make sense and are logical compared to the purpose statement and the sub-questions presented.
RQ2 - Is that what you mean by expertise? A combination of general programming ability combined with pair programming experience?

\Section{Methodology}
page 2, line 4 ``the purpose the study''.
The methodology is well written and provides a good argument for why a case study is being conducted. There was some good information regarding the agreement to keep the results and participants of the study anonymous for various reasons.

\subsection*{Data Collection}
Good information here especially in relation to how the studies are going to be conducted. Especially, the note about how the subjects will be studied twice and the reasons for this. Perhaps consider mentioning that the study is exploratory a little sooner in the paper?

\subsection*{Data Analysis}
The data analysis was very thorough, with special attention being paid to the codification and to how the data will be used. In particular, the suggested next steps by means of finding and support hypothesis for future research.

slight typo here: ``to protect the subject’s identify '', end of second paragraph.

\subsection*{Interview Structure}
This section gave a nice overview of the interview structure which is supported by the index and other tables of information. The inclusion of the immediate feedback loop for the interview questions was a good point to illustrate.

One problem there could be with the questions is that terms such as engagement might be a bit ambiguous to some people, does it refer to how engaged they feel in the task?

However, the sub questions and open ended questions are written very well, they clearly state what the researchers should be gathering from their subjects by explicitly stating it under the question.

\Section{Validity threats}
Nice and concise with no major flaws other than the fact that you didn't mention how the person (Your company contact) who will chose the participants of the interviews could be a potential validity threat, i.e. he might pick those whom he feels are the best pairs, or worst pairs e.t.c.

\Section{Other}
What would you look out for when observing? Is there anything in particular? If so, it might be nice to see these notes, or even a ``suggested form'' that the researchers might be using to log these findings in.

\end{document}

### 2015-02-24 rmtw/a5/latex8.tex
xD

@@
 Ever since the first computer programs were written, researchers and developers have been working on new programming concepts in order to decrease the level of complexity needed to develop programs.
-The abstraction level has been increased with help of compilers, object-oriented programming (OOP) and Unified Modelling Language (UML).
-The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate OOP code \cite{staron2006adopting}.
+The abstraction level has been increased with help of compilers, object-oriented programming and Unified Modelling Language (UML).
+The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate object-oriented code \cite{staron2006adopting}.
 
@@
 \SubSection{Statement of the Problem}
-Companies don't know if adopting MDD will be beneficial in terms of money and improved software quality.
+The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed.
+Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability.
+Since there seems to be a consensus in academia that MDSD is the future, and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.
 

### 2015-02-24 rmtw/a3_review/latex8.tex
lol
Added in the part which didn't make sense

@@
 
-\documentclass[times, 10pt,twocolumn]{IEEEtran} 
+\documentclass[times, 10pt,twocolumn]{article} 
 \usepackage{latex8}
@@
 % author names and affiliations
-\author{\IEEEauthorblockN{
-  John Burchell\IEEEauthorrefmark{1} and
-  William Granli\IEEEauthorrefmark{1}}
-
-  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}
-
-}
+\author{John Burchell and William Granli \\
+john.a.burchell@gmail.com, william.granli@gmail.com}
 
@@
 
-``The introduction was once again very well written.
-Good use of italicising the new and key terms.
-'' However reads very strangely, I presume this was an oversight?
+``consider the personal fulfilment factors related to qualities such as personal fulfilment factors related to qualities such as engagement,'' Reads very strangely, I presume this was an oversight?
 The first paragraph of the related work section also sounds a little strange.

### 2015-02-24 rmtw/a3_review/latex8.tex
reviewception

@@
 
-\Section{Purpose Statement}
-
-The purpose statement is clear but with one minor issue, there is no definition of expertise.
-What do you mean by expertise in this context, years of experience?
-How ``good'' a developer is, if so, compared to what or who?
-What their discipline is?
-Just a slight clarification would be nice.
-On the other hand, it was good to include a reason why you were ignoring personal ratings of expertise.
-
 \Section{Research Question}
@@
 
-\subsection*{Data Collection}
+\subsection{Data Collection}
 Good information here especially in relation to how the studies are going to be conducted.
@@
 
-\subsection*{Data Analysis}
+\subsection{Data Analysis}
 The data analysis was very thorough, with special attention being paid to the codification and to how the data will be used.
@@
 
-\subsection*{Interview Structure}
+\subsection{Interview Structure}
 This section gave a nice overview of the interview structure which is supported by the index and other tables of information.
@@
 One problem there could be with the questions is that terms such as engagement might be a bit ambiguous to some people, does it refer to how engaged they feel in the task?
-
 However, the sub questions and open ended questions are written very well, they clearly state what the researchers should be gathering from their subjects by explicitly stating it under the question.
@@
 Nice and concise with no major flaws other than the fact that you didn't mention how the person (Your company contact) who will chose the participants of the interviews could be a potential validity threat, i.e.
-he might pick those whom he feels are the best pairs, or worst pairs e.t.c.
+he might pick those whom he feels are the best pairs, or worst pairs etc.
 

### 2015-02-24 rmtw/a5/latex8.tex
xxx

@@
 
-The benefits of MDSD have consistently been reported in academia .
-Many large companies such as Ericsson, Volvo and ABB also use MDSD as a part of their development chain.
+The benefits of MDSD have consistently been reported in academia \cite{staron2006adopting} \cite{volter2013model}.
+Many large companies such as Ericsson and ABB \cite{staron2006adopting} also use MDSD as a part of their development chain.
 In industry, however, MDSD struggles to make a (full) (x-wide) (XXX) breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.
@@
 Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability.
-Since there seems to be a consensus in academia that MDSD is the future, and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.
+Since there seems to be a consensus in academia that MDSD is an improvement compared traditional software development \cite{staron2006adopting} \cite{volter2013model} and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.
 
@@
 \item \textbf{RQ1.3:} What are the characteristics of the systems of the companies that successfully use MDSD?
+\item \textbf{RQ1.4:} Which change strategy has most successful in implementing MDSD? 
 \end{itemize}

### 2015-02-24 rmtw/a5/latex8.tex
lldsal
Added my additions to existing lit

--- 2015-02-24 rmtw/a5/latex8.tex
@@
 \SubSection{Statement of the Problem}
-The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed.
+The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the system requirements are and in which environment the system is developed.
+
 Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability.
-Since there seems to be a consensus in academia that MDSD is the future, and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.
+Since there seems to be a consensus in academia that MDSD is the future, and that most large software companies choose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.
 
 \SubSection{Existing Literature}
-According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI)\cite{pettersson2008practitioner}\cite{unterkalmsteiner2012evaluation} or change management (CM) strategies.
-SPI is an attempt to alter an existing company or organisations software process, the main intention of which is to increase product quality, time to market all the while reducing inefficiency and other obstacles for creating good software.
 
-Similar to SPI is the concept of Evidence Based Software Engineering \cite{dyba2005evidence}.
-EBSE can be used as support for SPI, as suggested by the creators of the strategy.
-The main aim of which is to find a technology which is suitable for use and to then implement it in an organisation.
+Good examples
 
-CM on the other hand could be seen as an umbrella for a plethora of theories and strategies.
-An example of a theory is the concept of innovation values fit by \cite{klein1996challenge} which aims to describe if and when a company should make changes, based upon how a potential change fits with the values currently held by the company.
+Bad examples
 
-In 2002 Hall, Rainer and Baddoo \cite{hall2002implementing} published a report wherein they illustrated results of a study which looked at 85 companies throughout the UK.
-The study focused mostly on how the companies perform SPI and how effective their efforts were.
-The authors discovered that, while most companies do attempt SPI, many are unsuccessful due to a combined lack of evaluation and funding.
+What is the actual result, is it good or bad?
+
+Why do they contradict, environment vs system?
 
@@
 
-However, there is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms.
-
 \SubSection{Motivation for Study}
@@
 *5 references only needed for above (re-use from a1)
+
+Industry contradicts academia.
 

### 2015-02-24 rmtw/a5/latex8.tex

@@
 \SubSection{Statement of the Problem}
-The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the system requirements are and in which environment the system is developed.
 
+The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed.
 Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability.
-Since there seems to be a consensus in academia that MDSD is the future, and that most large software companies choose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.
+Since there seems to be a consensus in academia that MDSD is an improvement compared traditional software development \cite{staron2006adopting} \cite{volter2013model} and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.
 
@@
 
+\SubSection{Notes4John}
+\cite{volter2013model} says that MDSD will: increase development speed, increase quality, improve reusability, improved manageability through abstraction etc.
+
 \SubSection{Motivation for Study}

### 2015-02-24 rmtw/a5/latex8.tex
Added more to related work

@@
 
-Good examples
+Volter et al\cite{volter2013model} says that successful adoption of MDSD should increase development speed, increase software quality, improve reusability and improve manageability through abstraction.
 
-Bad examples
-
-What is the actual result, is it good or bad?
-
-Why do they contradict, environment vs system?
+Whittle and Hutchinson \cite{whittle2012mismatches} conducted a study whereby they examined 17 companies who were adopting MDSD.
+While they agreed that the successful adoption of MDSD can improve productivity through code generation, there are many pitfalls which can cause the adoption to fail.
+Whittle and Hutchinson found that in companies where the change was implemented bottom up, there was a higher degree of success.
+On the contrary to this, when change was top down, as suggested by academia and education, the adoption was often not as successful.
+A focus on Domain Specific Languages (DSLs) is what Whittle and Hutchinson suggest helps MDSD become successful in a company setting.
 
@@
 He suggests that the large investment in time and money, immature technology and organisational resistance are all factors to overcome in the adoption of new processes.
-
-\SubSection{Notes4John}
-\cite{volter2013model} says that MDSD will: increase development speed, increase quality, improve reusability, improved manageability through abstraction etc.
 

### 2015-02-24 rmtw/a5/latex8.tex
dsd

--- 2015-02-24 rmtw/a5/latex8.tex
@@
 \SubSection{Statement of the Problem}
-
 The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed.
@@
 \SubSection{Existing Literature}
+According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI)\cite{pettersson2008practitioner}\cite{unterkalmsteiner2012evaluation} or change management (CM) strategies.
+SPI is an attempt to alter an existing company or organisations software process, the main intention of which is to increase product quality, time to market all the while reducing inefficiency and other obstacles for creating good software.
 
-Good examples
+Similar to SPI is the concept of Evidence Based Software Engineering \cite{dyba2005evidence}.
+EBSE can be used as support for SPI, as suggested by the creators of the strategy.
+The main aim of which is to find a technology which is suitable for use and to then implement it in an organisation.
 
-Bad examples
+CM on the other hand could be seen as an umbrella for a plethora of theories and strategies.
+An example of a theory is the concept of innovation values fit by \cite{klein1996challenge} which aims to describe if and when a company should make changes, based upon how a potential change fits with the values currently held by the company.
 
-What is the actual result, is it good or bad?
-
-Why do they contradict, environment vs system?
+In 2002 Hall, Rainer and Baddoo \cite{hall2002implementing} published a report wherein they illustrated results of a study which looked at 85 companies throughout the UK.
+The study focused mostly on how the companies perform SPI and how effective their efforts were.
+The authors discovered that, while most companies do attempt SPI, many are unsuccessful due to a combined lack of evaluation and funding.
 
@@
 
+However, there is no existing research that aims to tackle the problem of applying the same change to an organisation that utilises two differing development paradigms. 
 \SubSection{Notes4John}
 \cite{volter2013model} says that MDSD will: increase development speed, increase quality, improve reusability, improved manageability through abstraction etc.
+
+\SubSection{Notes4John2}
+\cite{mattsson2009linking} talk about the link between MDSD and software architecture.
+They mention the importance of automatic enforcement of architectural rules and that MDSD is only benefecial if used correctly.
 
@@
 *5 references only needed for above (re-use from a1)
-
-Industry contradicts academia.
 

### 2015-02-24 rmtw/a5/latex8.tex
finish rel work

--- 2015-02-24 rmtw/a5/latex8.tex
@@
 He suggests that the large investment in time and money, immature technology and organisational resistance are all factors to overcome in the adoption of new processes.
+
+Mattsson et al.
+\cite{mattsson2009linking} discuss the correlation between MDSD and software architecture.
+The idea that MDSD is benefitial if done right is presented, and one important factor brought up is the need of automatic enforcment of architectural rules \cite{mattsson2009linking}.
+If this has to be done manually, it will become a bottleneck in large MDSD projects \cite{mattsson2009linking}.
 

### 2015-02-24 rmtw/a5/latex8.tex
Motivation added

@@
 Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability.
-Since there seems to be a consensus in academia that MDSD is an improvement compared traditional software development \cite{staron2006adopting} \cite{volter2013model} and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.
 
@@
 
-*5 references only needed for above (re-use from a1)
+Academia appears to be united in the opinion that MDSD is an improvement compared with traditional software development \cite{staron2006adopting} \cite{volter2013model}.
+However, why then do most large software companies chose not to adopt MDSD?
 
-Industry contradicts academia.
-
-\Section{Purpose of the Study}
-Purpose leading into RQs
+This gap in the literature is the motivation for our study.
+There is therefore a need to methodically investigate the existing literature in which studies of the adoption of MDSD, advantages and disadvantages of MDSD are explored.
+Not only this but how and when should MDSD be adopted and how it can be ensured to succeed.
 

### 2015-02-24 rmtw/a5/latex8.tex
Small changes YOLO

@@
 \cite{mattsson2009linking} discuss the correlation between MDSD and software architecture.
-The idea that MDSD is benefitial if done right is presented, and one important factor brought up is the need of automatic enforcment of architectural rules \cite{mattsson2009linking}.
-If this has to be done manually, it will become a bottleneck in large MDSD projects \cite{mattsson2009linking}.
+The idea that MDSD is beneficial if performed correctly is presented, and one important factor discussed is the need of automatic enforcement of architectural rules \cite{mattsson2009linking}.
+If this has to be performed manually, it will become a bottleneck in large MDSD projects \cite{mattsson2009linking}.
 

### 2015-02-25 rmtw/a3/latex8.tex
xd
Changed threats to subsection under meth
Changes have been made

@@
 \begin{document}
-
-\overfullrule=2cm
 
@@
 The authors discovered that, while most companies do attempt SPI, many are unsuccessful due to a combined lack of evaluation and funding.
+--Change this to something useful?
 
@@
 
+Mention criteria for pool of companies and clarify this a bit.
+Rephrase the first two sentences
+
 \SubSection{Case Study Design}
@@
 
+#Clarifications on terms for MC/MDD
+
 \SubSection{Preparation for Data Collection}
@@
 
+3-3 Clarify how and what department is chosen, i.e. we only looked at EPG so don't make it sound like we did something else.
+
 \SubSection{Data Gathering}
@@
 
+#Bit more explanation for distinction between the roles and phrasing of the sentence
+
 Ericsson's change process documentation was also analysed to provide further depth to the analysis already performed.
@@
 \SubSection{Data Analysis}
+#Add initially, tandem implies something else, add more detail here, explaining the analysis more, how the data is constructed, what tools are used and how it's processed.
+i.e.
+more detail about spreadsheets and tables.
+
 Data analysis of the interviews was completed in tandem with the data gathering phase.
@@
 
-\Section{Threats to Validity}
+\SubSection{Threats to Validity}
+#Revisit the triangulation period
 
@@
 \Section{Acknowledgements}
-John had the main responsibility for sections 1 \& 2.
+John had the main responsibility for sections 1, 2.
 William had the main responsibility for section 3.
-Section 4 and the interview questions were written together.
+Section 3.6 and the interview questions were written together.
 We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John.
@@
 
+%Recap question, describe the interview and questions
+%Timeline could be created and added
+
 \end{itemize}

### 2015-02-25 rmtw/a5/latex8.tex
added start of methodology

@@
 
+The method we shall use to attempt to answer our research questions is a Systematic Literature Review (SLR) \cite{keele2007guidelines}.
+An SLR is the most appropriate research methodology for two main reasons, we wish to summarise the existing evidence of when MDSD is applicable in industry and to fill gaps in literature for examples of when MDSD is not applicable \cite{keele2007guidelines}.
+For these same reasons, other methodology techniques are not as applicable.
+For example, a quantitative study is not appropriate as we are not trying to prove, disprove or generalise a hypothesis.
+A qualitative study would be useful if we were interested in exploring a hypothesis and for similar reasons a case study would not be applicable as we are not concerning ourselves with how MDSD works in a real setting.
+Likewise, as industry and academia seem to differ, it implies that there can be bias in both camps.
+By performing an SLR we help to alleviate some of this bias but we do not eliminate it entirely \cite{keele2007guidelines}.
+
+It's important to note that we will not be performing either a Systematic Mapping Study nor a Tertiary Review of existing literature.
+There is sufficient evidence in existence for the applicability of MDSD such that we can rule out the need to perform a Systematic Mapping Study.
+Furthermore, there insufficient SLRs that have been conducted thus a Tertiary Review is not possible nor appropriate at this time.
+
 \begin{itemize}
@@
 \item Identification of research (6.1)
+
 \item Selection of primary studies (6.2)

### 2015-02-25 rmtw/a5/latex8.tex
Started planning

--- 2015-02-24 rmtw/a5/latex8.tex
@@
 \textbf{Planning the review}
+Initially, existing SLRs were identified and evaluated, with the goal of mapping and identifying the gap in the existing literature.
+All identified SLRs \cite{santiagion2012model} \cite{dias2007survey} \cite{loniewski2010systematic} \cite{nicolas2009generation} were, however, researching the usage of model-driven techniques in other fields, such as traceability management \cite{santiagion2012model}, testing \cite{dias2007survey} and requirements engineering \cite{loniewski2010systematic} \cite{nicolas2009generation}.
+Based on these results, the need to evaluate previous research on model driven \textit{software} development was identified.
+
+The next step was to define the research questions.
+The main research question was constructed to create a wide scope to be able to investigate which characteristics are most vital to consider when adopting MDSD.
+The sub-questions were constructed to provide more detailed answers for specific questions that are valuable to the industry and companies who are condering to implement MDSD.
+
 \begin{itemize}
-\item Identification of the need for a review (5.1)
-Check other SLRs in the field and evaluate them
-\item Commissioning a review (5.2)
-not needed
-\item Specifying the research question(s) (5.3)
-this is very important :)
-the search process must identify primary studies that address the research questions
-the data extraction process must extract the data items needed to answer the questions
-the data analysis process must synthesise the data in such a way that the questions can be answered.
-
-read the questions in 5.3.1 to come up with similar ones for readability
 

### 2015-02-25 rmtw/a5/latex8.tex
fds

@@
 A qualitative study would be useful if we were interested in exploring a hypothesis and for similar reasons a case study would not be applicable as we are not concerning ourselves with how MDSD works in a real setting.
-Likewise, as industry and academia seem to differ, it implies that there can be bias in both camps.
+Likewise, as industry and academia seem to differ in opinion, it implies that there can be bias in both XXX camps.
 By performing an SLR we help to alleviate some of this bias but we do not eliminate it entirely \cite{keele2007guidelines}.
 
-It's important to note that we will not be performing either a Systematic Mapping Study nor a Tertiary Review of existing literature.
+It is important to note that we will not be performing either a Systematic Mapping Study nor a Tertiary Review of existing literature.
 There is sufficient evidence in existence for the applicability of MDSD such that we can rule out the need to perform a Systematic Mapping Study.

### 2015-02-25 rmtw/a5/latex8.tex
Updated to correct tense in methodology

--- 2015-02-25 rmtw/a5/latex8.tex
@@
 
+The method used to attempt to answer our research questions was a Systematic Literature Review (SLR) \cite{keele2007guidelines}.
+An SLR was the most appropriate research methodology for two main reasons.
+Firstly, we wished to summarise the existing evidence of when MDSD is applicable in industry and secondly to fill gaps in literature for examples of when MDSD is not applicable \cite{keele2007guidelines}.
+For these same reasons, other methodology techniques were not as applicable.
+For example, a quantitative study was not appropriate as we were not trying to prove, disprove or generalise a hypothesis.
+A qualitative study would have been useful if we were interested in exploring a hypothesis.
+For similar reasons a case study would also not have been applicable as we were not concerning ourselves with how MDSD works in a real setting.
+Likewise, as industry and academia seem to differ in opinion, there is an implication that there could have been be bias in both sides of the argument.
+By performing an SLR we helped to alleviate some of this bias but we did not eliminate it entirely \cite{keele2007guidelines}.
+
+It is important to note that did not perform either a Systematic Mapping Study nor a Tertiary Review of existing literature.
+There was sufficient evidence in existence for the applicability of MDSD such that we could rule out the need to perform a Systematic Mapping Study.
+Furthermore, there was insufficient SLRs that had been conducted prior to our study, thus, a Tertiary Review was not possible nor appropriate at that time.
+
 \begin{itemize}

### 2015-02-25 rmtw/a5/latex8.tex
gay

@@
 Initially, existing SLRs were identified and evaluated, with the goal of mapping and identifying the gap in the existing literature.
-All identified SLRs \cite{santiagion2012model} \cite{dias2007survey} \cite{loniewski2010systematic} \cite{nicolas2009generation} were, however, researching the usage of model-driven techniques in other fields, such as traceability management \cite{santiagion2012model}, testing \cite{dias2007survey} and requirements engineering \cite{loniewski2010systematic} \cite{nicolas2009generation}.
+All identified SLRs \cite{santiago2012model} \cite{dias2007survey} \cite{loniewski2010systematic} \cite{nicolas2009generation} were, however, researching the usage of model-driven techniques in other fields, such as traceability management \cite{santiago2012model}, testing \cite{dias2007survey} and requirements engineering \cite{loniewski2010systematic} \cite{nicolas2009generation}.
 Based on these results, the need to evaluate previous research on model driven \textit{software} development was identified.

### 2015-02-25 rmtw/a5/latex8.tex
SADADSDS

@@
 Many large companies such as Ericsson and ABB \cite{staron2006adopting} also use MDSD as a part of their development chain.
-In industry, however, MDSD struggles to make a (full) (x-wide) (XXX) breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.
+In industry, however, MDSD has struggled to make a complete breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.
 
@@
 \begin{itemize}
-\item They are probably not worded optimally... Here're some alturnutuves:
+\item They are probably not worded optimally... Here're some alternatives:
 \item In which situations should companies expect MDD to be successfully adopted?
@@
 There was sufficient evidence in existence for the applicability of MDSD such that we could rule out the need to perform a Systematic Mapping Study.
-Furthermore, there was insufficient SLRs that had been conducted prior to our study, thus, a Tertiary Review was not possible nor appropriate at that time.
+Furthermore, there were insufficient SLRs that had been conducted prior to our study, thus, a Tertiary Review was not possible nor appropriate at that time.
 
-\begin{itemize}
-\item Describe and explain the research strategy (i.e. SLR) and investigation methods that will be used for the study. 
-\item Motivate your choice of experiment using relevant references. 
-\item Search string including keywords and used databases
-\item inclusion/exclusion criteria
-\item data extraction
-\item data synthesis
-\item quality assessment
-\end{itemize}
-
-kithcneham start
-
-\textbf{Planning the review}
+\SubSection{Planning the Study}
 Initially, existing SLRs were identified and evaluated, with the goal of mapping and identifying the gap in the existing literature.
@@
 The main research question was constructed to create a wide scope to be able to investigate which characteristics are most vital to consider when adopting MDSD.
-The sub-questions were constructed to provide more detailed answers for specific questions that are valuable to the industry and companies who are condering to implement MDSD.
+The sub-questions were constructed to provide more detailed answers for specific questions that are valuable to the industry and companies who are considering to implement MDSD.
 
@@
 
+\SubSection{Conducting}
 \textbf{Conducting the review}
@@
 
+\SubSection{Reporting (probably skip)}
 \textbf{Reporting the review}
@@
 \Section{Acknowledgements}
-U w0T m8
+
+\begin{itemize}
+\item \textbf{these bulletins are from the assignment specification}
+\item Describe and explain the research strategy (i.e. SLR) and investigation methods that will be used for the study. 
+\item Motivate your choice of experiment using relevant references. 
+\item Search string including keywords and used databases
+\item inclusion/exclusion criteria
+\item data extraction
+\item data synthesis
+\item quality assessment
+\end{itemize}
 

### 2015-02-25 rmtw/a5/latex8.tex
Changes, they have been made
asd

@@
 Academia appears to be united in the opinion that MDSD is an improvement compared with traditional software development \cite{staron2006adopting} \cite{volter2013model}.
-However, why then do most large software companies chose not to adopt MDSD?
+However, why do many large software companies chose not to adopt MDSD?
 
@@
 
+Protocol
+1. Search process (table)
+2. Incl
+include search terms here and databases
+
+3. Excl
+
+Informal literature surveys (no defined research questions, no search process, no
+defined data extraction or data analysis process). 
+• Papers not subject to peer-review. 
+non english
+
+Make a table somwhere stating that william picks some and john checks the same vice versa.
+
+4. Tabulate the findings (overview)
+
+5. check the data colleciton part
+
 \begin{itemize}
@@
 \item Selection of primary studies (6.2)
-\item Study quality assessment (6.3)
-\item Data extraction and monitoring (6.4)
-\item Data synthesis
+\item Study quality assessment (6.3) x
+\item Data extraction and monitoring (6.4) x
+\item Data synthesis x
 \end{itemize}

### 2015-02-27 rmtw/a5/latex8.tex
adsa
Pushing my bits

@@
 
+Trial Search, Checking vs already performed studies.
+We picked 6 well known studies, our search strings did manage to find them all.
+
+Didn't check other disciplines as the area is not relevant.
+
+Summarise publication bias.
+
+Table, showing what sources we searched, what dates, what strategy, Years covered by search, what journal and conference proceedings were covered.
+
+Justify the when, the where and the how.
+
 \item Selection of primary studies (6.2)
+Sources that provide direct evidence about the research question. Refined search criteria here?
+
 \item Study quality assessment (6.3) x
+
+Apply the inclusion and exclusion criteria here, keeping a list of all excluded articles.
+
+Studies not related to Software Engineering were excluded first and as such have not been included in the exclusion list due to their irrelevance.
+
+Cohen Kappa statistic. Initial value here. Disagreements will be discussed and resolved.
+
 \item Data extraction and monitoring (6.4) x
+
+Quality of the papers must also be considered before they are examined for use in the study, this is done along with the inclusion and exclusion criteria.
+
 \item Data synthesis x

### 2015-02-27 rmtw/a5/latex8.tex
sda

@@
 1. Search process (table)
+
 2. Incl
@@
 
-Informal literature surveys (no defined research questions, no search process, no
-defined data extraction or data analysis process). 
-• Papers not subject to peer-review. 
-non english
+* Informal literature surveys (no defined research questions, no search process, no defined data extraction or data analysis process). 
+* Papers not subject to peer-review, such as book
+* non-english
 

### 2015-02-27 rmtw/a5/latex8.tex
Review protocol d0ne

--- 2015-02-27 rmtw/a5/latex8.tex
@@
 \usepackage{url}
+\usepackage{tabularx}
+\usepackage{appendix}
 
@@
 
-\begin{itemize}
-\item They are probably not worded optimally... Here're some alternatives:
-\item In which situations should companies expect MDD to be successfully adopted?
-\item In which situations should companies expect that the adoption of MDD would lead to a performance boost?
-\end{itemize}
-
 \Section{Methodology}
-
 The method used to attempt to answer our research questions was a Systematic Literature Review (SLR) \cite{keele2007guidelines}.
@@
 
-Protocol
-1. Search process (table)
-2. Incl
-include search terms here and databases
+\subsubsection{Review Protocol}
+The next step was to (<- XXX re-phrase that) define the review protocol.
+The list of databases included can be seen in Table I.
+The included databases have been chosen based on recommendations in \cite{brereton2007lessons}.
+SpringerLink was included as advised in \cite{keele2007guidelines}.
+The databases were divided evenly between the two researchers.
 
-3. Excl
+The search terms used can be found in Appendix A. The main search terms are related to MDSD, but related terms such as Model Driven Engineering and code generation were also included.
 
-Informal literature surveys (no defined research questions, no search process, no
-defined data extraction or data analysis process). 
-• Papers not subject to peer-review. 
-non english
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{|l|l|} 
+		\hline
+		\textbf{Database} & \textbf{Link}  \\
+		\hline
+		IEEExplore &  Granli \\
+		\hline
+		ACM Digital library &  Granli \\
+		\hline
+		Google Scholar &  Granli \\
+		\hline
+		Citeseer Library & Granli \\
+		\hline
+		Inspec &  Burchell \\
+		\hline
+		ScienceDirect & Burchell \\
+		\hline
+		EI Compendex &  Burchell \\
+		\hline
+		SpringerLink & Burchell \\
+		\hline
+	\end{tabular}
+	\caption{Databases included in review}
+\end{table}
 
-Make a table somwhere stating that william picks some and john checks the same vice versa.
+The inclusion criteria were defined as follows: \newline
+\begin{itemize} 
+\item Studies including examples about the application of MDSD in industry
+\end{itemize}
 
-4. Tabulate the findings (overview)
+The exclusion critiera were defined as follows: \newline
+\begin{itemize}
+\item Informal papers (no defined research questions, no methodology)
+\item Non-peer reviewed papers (books, white papers etc.)
+\end{itemize}
 
-5. check the data colleciton part
+Once papers were selected, the following data was selected: Publication year, topic area, methodology type, authors, summary of the paper, conclusion.
+This data was the used as a base for analysis when evaluating the research questions for each paper.
 
-\begin{itemize}
-
-\item Developing a review protocol (5.4)
-
-\item Evaluating the review protocol (5.5)
-\end{itemize}
+Evaluating the review protocol (5.5)
 
@@
 
+\begin{appendices}
+\section{Search Terms}
+MDD, MDSD, model-driven software development, model-driven development, MDE, model-driven engineering, model driven engineering, code generation
+\end{appendices}
+
 \end{document}

### 2015-02-27 rmtw/a1/assignment_1.tex
Fixed formatting for a3
fixed some shit in a1

@@
 
-author names and affiliations
-\author{\IEEEauthorblockN{
-  John Burchell\IEEEauthorrefmark{1} and
-  William Granli\IEEEauthorrefmark{1}}
-  \IEEEauthorblockA{\IEEEauthorrefmark{1}john.a.burchell, william.granli@gmail.com}}
+\author{John Burchell and William Granli \\
+john.a.burchell, william.granli@gmail.com}
 
@@
 
-The independent variables will be defined as the experience, occupation, preferred language, least preferred language and the working language of the participant.
-The dependent variable in this example will be the readability of the language.
-
 The survey data will be collected from students studying at the University of Gothenburg via a series of on-line surveys.
@@
 \begin{itemize}
-\item \textit{RQ1:} What are the measurable differences in perceived readability between programming languages?
-\end{itemize}
-
-The results of RQ1 will then be used to answer the following two sub research questions. 
-\begin{itemize}
-\item \textit{SRQ1}: How do the measurable differences between languages correlate to their use in academia for teaching?
-\item \textit{SRQ2}: How do the measurable differences between languages correlate to the popularity of the language?
+\item \textit{RQ1:} What are the inherent differences in perceived readability between programming languages?
 \end{itemize}
@@
 As mentioned before, the goal of this study is to identify the inherent differences in readability of programming languages.
-To research this, a broad population is required, to avoid results influenced by a possible correlation between the perception of readability and the previously defined independent variables.
+To research this, a broad population is required, to avoid results influenced by a possible correlation between the perception of readability and for example experience.
 As such, a research survey has been conducted.
@@
 The desired response rate is 10\%.
-Stratification of the population will not be enforced and thus there may be a statistically incorrect representation of the independent variables.
+Stratification of the population will not be enforced and thus there may be a statistically incorrect representation based on experience or preferred language of the participant.
 This has, however, been taken into account in the analysis of the results.
@@
 
-Other potential validity threats we must take into consideration are those that arise from the nature of survey.
-Since we are performing single stage data collection, the respondents of the surveys are answering our questions at their convenience.
-This opens the door for some validity threats, such as the willingness to participate.
-Our data are at the mercy of those willing to participate; we cannot anticipate how many will respond.
-There is little incentive for the respondents to partake in the survey other than for their own self interest.
-
 The questionnaire has been peer reviewed by colleagues Jani Kellaris and Patrik Bäckström and it has been tested on a 6 students in 2nd year which we supervise.
@@
   \end{tabularx}
-  \caption{Independent variables' relation to Research Questions}
+  \caption{Survey variables' relation to Research Questions}
 \end{table}
@@
 
-Response bias has been determined mostly through analysing the correlation between the independent variables and the dependent variables.
+Response bias has been determined mostly through analysing the correlation between the previously defined variables and readability score.
 Readability of a language is likely to be strongly correlated with the reader's experience of the language.
@@
 The data has been analysed with simple descriptive analysis gwhere mean values have been the main source to analyse the readability of a language (RQ1).
-Correlation between the independent and dependent variables have been the main analysis to answer SRQ1 and SRQ2.
+Correlation between the variables and the readability score have been the main analysis to answer SRQ1 and SRQ2.
 Score ranges have been used to analyse the strength of replies.
@@
 This means that there is potential that some of the responses came from people not within the SE\&M institutions and this should be taken into consideration when analysing the results.
+
+Other potential validity threats we must take into consideration are those that arise from the nature of survey.
+Since we are performing single stage data collection, the respondents of the surveys are answering our questions at their convenience.
+This opens the door for some validity threats, such as the willingness to participate.
+Our data are at the mercy of those willing to participate; we cannot anticipate how many will respond.
+There is little incentive for the respondents to partake in the survey other than for their own self interest.
 

### 2015-03-02 rmtw/a5/latex8.tex
review prot0col d0ne
Conducting the study

@@
 \usepackage{appendix}
+\usepackage{pbox}
 
@@
 
-The search terms used can be found in Appendix A. The main search terms are related to MDSD, but related terms such as Model Driven Engineering and code generation were also included.
-
 \begin{table}[ht]
@@
 
+The search terms used can be found in Appendix A. The main search terms are related to MDSD, but related terms such as Model Driven Engineering and code generation were also included.
+
 The inclusion criteria were defined as follows: \newline
@@
 
-The exclusion critiera were defined as follows: \newline
+The exclusion criteria were defined as follows: \newline
 \begin{itemize}
@@
 
-Evaluating the review protocol (5.5)
+The protocol was evaluated by Ioannis Kellaris and Patrik B\"ackstr\"om.
+The main objective of the review was to ascertain that the current protocol would properly address the research questions.
+Each step of the review protocol was evaluated based on this criteria.
 
-\SubSection{Conducting}
+\SubSection{Conducting the Study}
 \textbf{Conducting the review}
@@
 
-Trial Search, Checking vs already performed studies.
-We picked 6 well known studies, our search strings did manage to find them all.
+To ensure that our search criteria had be selected correctly, a small trial study was performed to ensure that our criteria could find six predetermined and well known papers which are relevant to our study.
+%Cite the papers here?
 
-Didn't check other disciplines as the area is not relevant.
+While Kitchenham\cite{keele2007guidelines} suggest the inclusion of papers from related disciplines, this was not undertaken for this study.
+Other disciplines, while appropriate for some research we shall review, are not appropriate or relevant.
 
-Summarise publication bias.
-
-Table, showing what sources we searched, what dates, what strategy, Years covered by search, what journal and conference proceedings were covered.
-
-Justify the when, the where and the how.
+As suggested by Kitchenham\cite{keele2007guidelines}, publication bias is something that we will have to overcome in our study.
+From our trial study and previous research into related work, it became clear that there seems to exist some bias towards the adoption of MDSD; there are few papers which speak ill of it.
+To help alleviate this we shall check, but not include, grey literature (non-formally published papers), conference proceedings.
+We shall also attempt to contact researchers and change agents with experience of implementing MDSD to ascertain if they have unpublished results which can balance the positive bias.
 
 \item Selection of primary studies (6.2)
-Sources that provide direct evidence about the research question. Refined search criteria here?
 
-\item Study quality assessment (6.3) x
+In order to correctly collect all the relevant papers, a particular search process had to be defined. The table below shows the correlation between the types of sources and how they were searched.
 
-Apply the inclusion and exclusion criteria here, keeping a list of all excluded articles.
+\begin{table}[ht]
+	\centering
+    \begin{tabular}{ | l | p{5cm} |}
+    \hline
+    \textbf{Data Source} & \textbf{Data Collected} \\ \hline
+    Digital Sources & Database Name \newline Date of Search \newline Year span \\ \hline
+    Conference Proceedings & Conference Title \newline Conference Name \newline Journal Name \\ \hline
+    Unpublished Studies & Names of those contacted \newline Research websites searched (Date and URL) \\
+    \hline
+    \end{tabular}
+	\caption{Searching Strategies}
+\end{table}
 
-Studies not related to Software Engineering were excluded first and as such have not been included in the exclusion list due to their irrelevance.
+The digital libraries, mentioned in section Table 1 were chosen for their extensive catalogues, reliability and availability of the data.
+Hand searching of journals was not performed as we decided to limit the scope of the search to digital libraries, conferences and other sources.
 
-Cohen Kappa statistic. Initial value here. Disagreements will be discussed and resolved.
+Given that MDSD is a relatively new process, we have decided to limit the search starting in 1990 to the current date.
+We feel that this limitation on the search will not hinder our results as we were unable to find any papers published prior to this date concerning MDSD.
+
+The selection criteria for the papers will be further refined during this stage.
+After applying the initial exclusion and inclusion criteria, we can exclude and include based on practicality.
+Below is a short list of these criteria.
+
+\begin{itemize}
+\item Language
+\item Date of publication
+\end{itemize}
+
+\item Study Quality Assessment (6.3) x
+
+The Quality of the papers must also be considered before they are examined for use in the study.
+Determination of paper quality will be performed after initial exclusions and inclusions have been performed.
+These additional quality checks will seek to eliminate papers with excessive bias, quality of the paper and the reliability of the results.
+
+%Maybe this needs more backup, or some more oomph?
+
+To assess the reliability of the inclusions and exclusions, Fleiss' kappa index will be applied on both researchers findings.
+All conflicts regarding to acceptance of papers will be discussed and resolved prior to their inclusion in the SLR.
+Ideally, the kappa rating achieved will be from 0.61 - 0.80 indicating a strong alignment between the researchers.
+
+Furthermore, as per the suggestion from Kitchenham \cite{keele2007guidelines} after the application of the inclusion and exclusion criteria any paper failing to meet these criteria will be retained and shown in the results of the SLR.
+
+%Skipping some steps of this as they don't feel that relevant, discuss with willy.
 
@@
 
-Quality of the papers must also be considered before they are examined for use in the study, this is done along with the inclusion and exclusion criteria.
+In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{keele2007guidelines}.
+These forms will be created and the pilot tested by the researchers taking part in the study.
+This allows the researchers to discover potential issues before the study takes place, such as ambiguity the data form questions.
+
+The data extraction will be performed by both researchers on each individual study, meaning each study is extracted twice.
+By doing this, the chance for bias and misinterpretation is reduced.
+As suggested by kitchenham \cite{keele2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data.
+In the case of duplication, the most robust study will be chosen.
+
+Data from ongoing studies will be not included in our data extraction.
+The primary reason behind this stance is that we are interested in the complete adoption of MDSD and as such a study which is either examining the adoption and is half way through will not help us answer this question.
 
@@
 \item Specifying dissemination mechanisms (7.1)
+
+As the the results will be intended to have some impact upon whether or not MDSD is adopted in practice.
+As such the results will ideally be disseminated via journals, publications and via web pages to reach a broad audience.
+
 \item Formatting the main report (7.2)

### 2015-03-03 rmtw/a5/latex8.tex
Fixed Keele ref

@@
 \Section{Methodology}
-The method used to attempt to answer our research questions was a Systematic Literature Review (SLR) \cite{keele2007guidelines}.
+The method used to attempt to answer our research questions was a Systematic Literature Review (SLR) \cite{kitchenham2007guidelines}.
 An SLR was the most appropriate research methodology for two main reasons.
-Firstly, we wished to summarise the existing evidence of when MDSD is applicable in industry and secondly to fill gaps in literature for examples of when MDSD is not applicable \cite{keele2007guidelines}.
+Firstly, we wished to summarise the existing evidence of when MDSD is applicable in industry and secondly to fill gaps in literature for examples of when MDSD is not applicable \cite{kitchenham2007guidelines}.
 For these same reasons, other methodology techniques were not as applicable.
@@
 Likewise, as industry and academia seem to differ in opinion, there is an implication that there could have been be bias in both sides of the argument.
-By performing an SLR we helped to alleviate some of this bias but we did not eliminate it entirely \cite{keele2007guidelines}.
+By performing an SLR we helped to alleviate some of this bias but we did not eliminate it entirely \cite{kitchenham2007guidelines}.
 
@@
 The included databases have been chosen based on recommendations in \cite{brereton2007lessons}.
-SpringerLink was included as advised in \cite{keele2007guidelines}.
+SpringerLink was included as advised in \cite{kitchenham2007guidelines}.
 The databases were divided evenly between the two researchers.
@@
 
-While Kitchenham\cite{keele2007guidelines} suggest the inclusion of papers from related disciplines, this was not undertaken for this study.
+While Kitchenham\cite{kitchenham2007guidelines} suggest the inclusion of papers from related disciplines, this was not undertaken for this study.
 Other disciplines, while appropriate for some research we shall review, are not appropriate or relevant.
 
-As suggested by Kitchenham\cite{keele2007guidelines}, publication bias is something that we will have to overcome in our study.
+As suggested by Kitchenham\cite{kitchenham2007guidelines}, publication bias is something that we will have to overcome in our study.
 From our trial study and previous research into related work, it became clear that there seems to exist some bias towards the adoption of MDSD; there are few papers which speak ill of it.
@@
 
-Furthermore, as per the suggestion from Kitchenham \cite{keele2007guidelines} after the application of the inclusion and exclusion criteria any paper failing to meet these criteria will be retained and shown in the results of the SLR.
+Furthermore, as per the suggestion from Kitchenham \cite{kitchenham2007guidelines} after the application of the inclusion and exclusion criteria any paper failing to meet these criteria will be retained and shown in the results of the SLR.
 
@@
 
-In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{keele2007guidelines}.
+In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{kitchenham2007guidelines}.
 These forms will be created and the pilot tested by the researchers taking part in the study.
@@
 By doing this, the chance for bias and misinterpretation is reduced.
-As suggested by kitchenham \cite{keele2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data.
+As suggested by kitchenham \cite{kitchenham2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data.
 In the case of duplication, the most robust study will be chosen.

### 2015-03-03 rmtw/a5/latex8.tex
Added some changes

--- 2015-03-02 rmtw/a5/latex8.tex
@@
 These forms will be created and the pilot tested by the researchers taking part in the study.
-This allows the researchers to discover potential issues before the study takes place, such as ambiguity the data form questions.
+This allows the researchers to discover potential issues before the study takes place, such as ambiguity of questions in the form.
 
@@
 By doing this, the chance for bias and misinterpretation is reduced.
-As suggested by kitchenham \cite{keele2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data.
+As suggested by Kitchenham \cite{keele2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data.
 In the case of duplication, the most robust study will be chosen.
@@
 \item Data synthesis x
+
+We will probably want to qualitative. We're not really going after data points as such. Perhaps even a narrative.
+
+If we do, we'll need a sensitivity analysis to
+
 \end{itemize}
@@
 \item Specifying dissemination mechanisms (7.1)
+
+Difficult to say which to use when the study has not been performed.
 

### 2015-03-03 rmtw/a5/latex8.tex
yolo

--- 2015-03-03 rmtw/a5/latex8.tex
@@
 
-Once papers were selected, the following data was selected: Publication year, topic area, methodology type, authors, summary of the paper, conclusion.
-This data was the used as a base for analysis when evaluating the research questions for each paper.
-
 The protocol was evaluated by Ioannis Kellaris and Patrik B\"ackstr\"om.
@@
 \SubSection{Conducting the Study}
-\textbf{Conducting the review}
-\begin{itemize}
-\item Identification of research (6.1)
 
@@
 We shall also attempt to contact researchers and change agents with experience of implementing MDSD to ascertain if they have unpublished results which can balance the positive bias.
-
-\item Selection of primary studies (6.2)
 
@@
 
-\item Study Quality Assessment (6.3) x
-
 The Quality of the papers must also be considered before they are examined for use in the study.
@@
 
-\item Data extraction and monitoring (6.4) x
-
 In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{kitchenham2007guidelines}.
@@
 
-\item Data synthesis x
-\end{itemize}
-
-\SubSection{Reporting (probably skip)}
-\textbf{Reporting the review}
-\begin{itemize}
-\item Specifying dissemination mechanisms (7.1)
-
-As the the results will be intended to have some impact upon whether or not MDSD is adopted in practice.
-As such the results will ideally be disseminated via journals, publications and via web pages to reach a broad audience.
-
-\item Formatting the main report (7.2)
-\item Evaluating the report (7.3)
-\end{itemize}
+Data synthesis x
 
@@
 \Section{Acknowledgements}
-
-\begin{itemize}
-\item \textbf{these bulletins are from the assignment specification}
-\item Describe and explain the research strategy (i.e. SLR) and investigation methods that will be used for the study. 
-\item Motivate your choice of experiment using relevant references. 
-\item Search string including keywords and used databases
-\item inclusion/exclusion criteria
-\item data extraction
-\item data synthesis
-\item quality assessment
-\end{itemize}
 

### 2015-03-03 rmtw/a5/latex8.tex

@@
 
-In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{kitchenham2007guidelines}.
+\item Data extraction and monitoring (6.4) x
+
+In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{keele2007guidelines}.
 These forms will be created and the pilot tested by the researchers taking part in the study.
-This allows the researchers to discover potential issues before the study takes place, such as ambiguity the data form questions.
+This allows the researchers to discover potential issues before the study takes place, such as ambiguity of questions in the form.
 
@@
 By doing this, the chance for bias and misinterpretation is reduced.
-As suggested by kitchenham \cite{kitchenham2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data.
+As suggested by Kitchenham \cite{keele2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data.
 In the case of duplication, the most robust study will be chosen.
@@
 
-Data synthesis x
+\item Data synthesis x
+
+We will probably want to qualitative. We're not really going after data points as such. Perhaps even a narrative.
+
+If we do, we'll need a sensitivity analysis to
+
+\end{itemize}
+
+\SubSection{Reporting (probably skip)}
+\textbf{Reporting the review}
+\begin{itemize}
+\item Specifying dissemination mechanisms (7.1)
+
+Difficult to say which to use when the study has not been performed.
+
+As the the results will be intended to have some impact upon whether or not MDSD is adopted in practice.
+As such the results will ideally be disseminated via journals, publications and via web pages to reach a broad audience.
+
+\item Formatting the main report (7.2)
+\item Evaluating the report (7.3)
+\end{itemize}
 

### 2015-03-03 rmtw/a5/latex8.tex
hej
Hello

--- 2015-03-03 rmtw/a5/latex8.tex
@@
 By doing this, the chance for bias and misinterpretation is reduced.
-As suggested by kitchenham \cite{kitchenham2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data.
+As suggested by Kitchenham \cite{kitchenham2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data.
 In the case of duplication, the most robust study will be chosen.
@@
 
-Data synthesis x
+We will probably want to qualitative. We're not really going after data points as such. Perhaps even a narrative.
+
+If we do, we'll need a sensitivity analysis to
 

### 2015-03-03 rmtw/a5/latex8.tex
Data extraction form table

@@
 \item \textbf{RQ1.3:} What are the characteristics of the systems of the companies that successfully use MDSD?
-\item \textbf{RQ1.4:} Which change strategy has most successful in implementing MDSD? 
+\item \textbf{RQ1.4:} Which change strategy has most been successful in implementing MDSD? 
 \end{itemize}
@@
 	\centering
-    \begin{tabular}{ | l | p{5cm} |}
+    \begin{tabular}{ | l | p{3.5cm} |}
     \hline
@@
     Conference Proceedings & Conference Title \newline Conference Name \newline Journal Name \\ \hline
-    Unpublished Studies & Names of those contacted \newline Research websites searched (Date and URL) \\
+    Unpublished Studies & Names of those contacted \newline Research websites\newline searched (Date and URL) \\
     \hline
@@
 
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{|l|l|l|} 
+		\hline
+		\textbf{Data Item} & \textbf{Value} & \textbf{Notes}  \\
+		\hline
+		Data Extractor &  &  \\
+		\hline
+		Data Checker &  & \\
+		\hline
+		Study Identifier &  & \\
+		\hline
+		Industry Domain & & \\
+		\hline
+		Search Keyword &  & \\
+		\hline
+		Study Methodology & & \\
+		\hline
+		Number of Companies Involved &  & \\
+		\hline
+		Existing Development Practices & & \\
+		\hline
+		Change Strategies Utilised & & \\
+		\hline
+		Positive or Negative Conclusion & & \\
+		\hline
+	\end{tabular}
+	\caption{Example Extraction Form}
+\end{table}
+
 We will probably want to qualitative. We're not really going after data points as such. Perhaps even a narrative.

### 2015-03-03 rmtw/a1/assignment_1.tex
sda

@@
 The data was collected with a questionnaire consisting of 15 questions.
-The data has been analysed with simple descriptive analysis gwhere mean values have been the main source to analyse the readability of a language (RQ1).
+The data has been analysed with simple descriptive analysis where mean values have been the main source to analyse the readability of a language (RQ1).
 Correlation between the variables and the readability score have been the main analysis to answer SRQ1 and SRQ2.

### 2015-03-03 rmtw/a5/latex8.tex
Wu-Tang Clan
sda
Data synthesis

@@
 
-\title{Assignment 5}
+\title{Wu-Tang Clan}
 
@@
 \subsubsection{Review Protocol}
-The next step was to (<- XXX re-phrase that) define the review protocol.
+Subsequently, the reivew protocol was defined.
 The list of databases included can be seen in Table I.
@@
 \item Studies including examples about the application of MDSD in industry
+\item Studies carried out using a qualitative methodology
 \end{itemize}
@@
 \item Non-peer reviewed papers (books, white papers etc.)
+\item Studies carried out using a quantitative methodology
 \end{itemize}
@@
 We shall also attempt to contact researchers and change agents with experience of implementing MDSD to ascertain if they have unpublished results which can balance the positive bias.
+
+\subsubsection{Study Selection}
 
@@
 
+\subsubsection{Quality Assessment}
+
 The Quality of the papers must also be considered before they are examined for use in the study.
@@
 
+\subsubsection{Data Extraction}
+
 In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{kitchenham2007guidelines}.
@@
 
-Data from ongoing studies will be not included in our data extraction.
-The primary reason behind this stance is that we are interested in the complete adoption of MDSD and as such a study which is either examining the adoption and is half way through will not help us answer this question.
+Data from ongoing studies was not included in our data extraction.
+The primary reason behind this stance is that we were interested in the complete adoption of MDSD and as such a study which is either examining the adoption and is half way through will not help us answer this question.
 
@@
 
-We will probably want to qualitative. We're not really going after data points as such. Perhaps even a narrative.
+\subsubsection{Data Synthesis}
 
-If we do, we'll need a sensitivity analysis to
+As our study included only qualitative studies, a reciprocal translation was was performed.
+As we focused upon qualitative studies, we were faced with comparing studies consisting of mostly natural language.
+Consequently, there were some studies which contained differing language for similar concepts but the use of a reciprocal study allowed us to translate the studies so that they could be compared to each other.
 

### 2015-03-03 rmtw/a5/latex8.tex
Spellcheck
Changed tense

@@
 \subsubsection{Review Protocol}
-Subsequently, the reivew protocol was defined.
+Subsequently, the review protocol was defined.
 The list of databases included can be seen in Table I.
@@
 
-The digital libraries, mentioned in section Table 1 were chosen for their extensive catalogues, reliability and availability of the data.
+The digital libraries, mentioned in section Table 1, were chosen for their extensive catalogues, reliability and availability of the data.
 Hand searching of journals was not performed as we decided to limit the scope of the search to digital libraries, conferences and other sources.
 
-Given that MDSD is a relatively new process, we have decided to limit the search starting in 1990 to the current date.
-We feel that this limitation on the search will not hinder our results as we were unable to find any papers published prior to this date concerning MDSD.
+Given that MDSD is a relatively new process, we decided to limit the search starting to papers published 1990 to the current date.
+We feel that this limitation on the search did not hinder the results as we were unable to find any papers published prior to this date concerning MDSD.
 
-The selection criteria for the papers will be further refined during this stage.
-After applying the initial exclusion and inclusion criteria, we can exclude and include based on practicality.
+The selection criteria for the papers was further refined during this stage.
+After applying the initial exclusion and inclusion criteria, exclusions and inclusions were based on practicality.
 Below is a short list of these criteria.
@@
 
-The Quality of the papers must also be considered before they are examined for use in the study.
-Determination of paper quality will be performed after initial exclusions and inclusions have been performed.
-These additional quality checks will seek to eliminate papers with excessive bias, quality of the paper and the reliability of the results.
+The Quality of the papers was also considered before they were examined for use in the study.
+Determination of paper quality occurred after initial exclusions and inclusions had been performed.
+These additional quality checks sought to eliminate papers with excessive bias, low quality and the unreliable results.
 
@@
 
-To assess the reliability of the inclusions and exclusions, Fleiss' kappa index will be applied on both researchers findings.
-All conflicts regarding to acceptance of papers will be discussed and resolved prior to their inclusion in the SLR.
-Ideally, the kappa rating achieved will be from 0.61 - 0.80 indicating a strong alignment between the researchers.
+To assess the reliability of the inclusions and exclusions, Fleiss' kappa index was applied on both researchers findings.
+All conflicts regarding to acceptance of papers was discussed and resolved prior to their inclusion in the SLR.
+The initial kappa rating achieved was 0.78, which lies in the band 0.61 - 0.80 indicating a strong alignment between the researchers.
 
-Furthermore, as per the suggestion from Kitchenham \cite{kitchenham2007guidelines} after the application of the inclusion and exclusion criteria any paper failing to meet these criteria will be retained and shown in the results of the SLR.
+Furthermore, as per the suggestion from Kitchenham \cite{kitchenham2007guidelines} after the application of the inclusion and exclusion criteria any paper failing to meet these criteria was retained and will be shown in the results of the SLR.
 
@@
 In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{kitchenham2007guidelines}.
-These forms will be created and the pilot tested by the researchers taking part in the study.
-This allows the researchers to discover potential issues before the study takes place, such as ambiguity of questions in the form.
+We created and pilot tested these forms prior to the data extraction.
+This allowed us to discover potential issues before the study took place, such as ambiguity of questions in the form.
 
-The data extraction will be performed by both researchers on each individual study, meaning each study is extracted twice.
-By doing this, the chance for bias and misinterpretation is reduced.
-As suggested by Kitchenham \cite{kitchenham2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data.
-In the case of duplication, the most robust study will be chosen.
+The data extraction was performed by both researchers on each individual study, meaning each study was extracted twice.
+By doing this, the chance for bias and misinterpretation was reduced.
+As suggested by Kitchenham \cite{kitchenham2007guidelines}, care was taken to avoid the acceptance of duplicate studies of the same data.
+In the case of duplication, the most robust study was chosen.
 
@@
 \Section{Acknowledgements}
+John had the main responsibility for sections 1.2, 1.3, 2.0.
+William had the main responsibility for sections 1.0, 1.1, 2.1, 2.2.
+The research questions were written together.
+We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John.
 

### 2015-03-03 rmtw/a5/latex8.tex
DSA

--- 2015-03-03 rmtw/a5/latex8.tex
@@
 
-Volter et al\cite{volter2013model} says that successful adoption of MDSD should increase development speed, increase software quality, improve reusability and improve manageability through abstraction.
+Volter et al.
+\cite{volter2013model} state that successful adoption of MDSD should increase development speed, increase software quality, improve reusability and improve manageability through abstraction.
 
@@
 Academia appears to be united in the opinion that MDSD is an improvement compared with traditional software development \cite{staron2006adopting} \cite{volter2013model}.
-However, why do many large software companies chose not to adopt MDSD?
+However, why do many large software companies choose to not adopt MDSD?
 
@@
 
-It is important to note that did not perform either a Systematic Mapping Study nor a Tertiary Review of existing literature.
+It is important to note that did not perform either a Systematic Mapping Study nor a Tertiary Review of (XXX cite?) existing literature.
 There was sufficient evidence in existence for the applicability of MDSD such that we could rule out the need to perform a Systematic Mapping Study.
-Furthermore, there were insufficient SLRs that had been conducted prior to our study, thus, a Tertiary Review was not possible nor appropriate at that time.
+Furthermore, there were insufficient SLRs that had been conducted prior to our study, thus, a Tertiary Review \cite{kitchenham2007guidelines} was not possible nor appropriate at that time.
 
@@
 
-To ensure that our search criteria had be selected correctly, a small trial study was performed to ensure that our criteria could find six predetermined and well known papers which are relevant to our study.
-%Cite the papers here?
+To ensure that our search criteria had be meaningfully defined, a small trial study was performed to guarantee that our criteria could find six predetermined and well known papers which are relevant to our study.
+As Kitchenham \cite{kitchenham2007guidelines} suggests, papers from other disciplines will be included in the literature review.
 
-While Kitchenham\cite{kitchenham2007guidelines} suggest the inclusion of papers from related disciplines, this was not undertaken for this study.
-Other disciplines, while appropriate for some research we shall review, are not appropriate or relevant.
-
-As suggested by Kitchenham\cite{kitchenham2007guidelines}, publication bias is something that we will have to overcome in our study.
-From our trial study and previous research into related work, it became clear that there seems to exist some bias towards the adoption of MDSD; there are few papers which speak ill of it.
-To help alleviate this we shall check, but not include, grey literature (non-formally published papers), conference proceedings.
-We shall also attempt to contact researchers and change agents with experience of implementing MDSD to ascertain if they have unpublished results which can balance the positive bias.
+Possible publication bias was taken into account during the study.
+From our trial study and previous research into related work, it became clear that there existed bias towards the adoption of MDSD; there were few papers which spoke ill of it.
+To help alleviate this we checked, but did not include, grey literature (non-formally published papers) and conference proceedings.
+We also contacted researchers and change agents with experience of implementing MDSD to discover if they had unpublished results which could balance the positive bias.
 
@@
 
-The digital libraries, mentioned in section Table 1, were chosen for their extensive catalogues, reliability and availability of the data.
+The digital libraries, mentioned in Table 1, were chosen for their extensive catalogues, reliability and availability of the data.
 Hand searching of journals was not performed as we decided to limit the scope of the search to digital libraries, conferences and other sources.
@@
 
-The selection criteria for the papers was further refined during this stage.
+The selection criteria for the papers were refined during this stage.
 After applying the initial exclusion and inclusion criteria, exclusions and inclusions were based on practicality.
@@
 
-The Quality of the papers was also considered before they were examined for use in the study.
+The quality of the papers was also considered before they were examined for use in the study.
 Determination of paper quality occurred after initial exclusions and inclusions had been performed.
@@
 
-To assess the reliability of the inclusions and exclusions, Fleiss' kappa index was applied on both researchers findings.
+To assess the reliability of the inclusions and exclusions, Fleiss' Kappa index was applied on both researchers findings.
 All conflicts regarding to acceptance of papers was discussed and resolved prior to their inclusion in the SLR.
-The initial kappa rating achieved was 0.78, which lies in the band 0.61 - 0.80 indicating a strong alignment between the researchers.
+The initial Kappa rating achieved was 0.78, which lies in the band 0.61 - 0.80 indicating a strong alignment between the researchers.
 
@@
 
+Parts Section 1.2 have been re-used from previous assignments. Because of this, the paper may show up on Urkund.
+
 \begin{appendices}

### 2015-03-03 rmtw/a5/latex8.tex
Finished assignment 5

@@
 Ever since the first computer programs were written, researchers and developers have been working on new programming concepts in order to decrease the level of complexity needed to develop programs.
-The abstraction level has been increased with help of compilers, object-oriented programming and Unified Modelling Language (UML).
+The abstraction level has been increased with help of compilers, object-oriented programming and he Unified Modelling Language (UML).
 The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate object-oriented code \cite{staron2006adopting}.
@@
 
-The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed.
+The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the system requirements are and in what environment the system is being developed.
 Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability.
@@
 Whittle and Hutchinson found that in companies where the change was implemented bottom up, there was a higher degree of success.
-On the contrary to this, when change was top down, as suggested by academia and education, the adoption was often not as successful.
+Contrary to this, when change was top down, as suggested by academia and education, the adoption was often not as successful.
 A focus on Domain Specific Languages (DSLs) is what Whittle and Hutchinson suggest helps MDSD become successful in a company setting.
 
-A further, more specific example is a study conducted by Staron \cite{staron2006adopting}.
-In this study a case study is conducted with two companies wishing or in the process of adopting MDSD.
+A further, more specific example, is a study conducted by Staron \cite{staron2006adopting}.
+In this study a case study is conducted with two companies in the process of adopting MDSD.
 In the findings, Staron provides a set of conditions for adopting MDSD, one being the compatibility of MDSD and existing principles in the company.
@@
 There is therefore a need to methodically investigate the existing literature in which studies of the adoption of MDSD, advantages and disadvantages of MDSD are explored.
-Not only this but how and when should MDSD be adopted and how it can be ensured to succeed.
+Not only this but how and when should MDSD be adopted and how success can be assured.
 
@@
 For example, a quantitative study was not appropriate as we were not trying to prove, disprove or generalise a hypothesis.
-A qualitative study would have been useful if we were interested in exploring a hypothesis.
-For similar reasons a case study would also not have been applicable as we were not concerning ourselves with how MDSD works in a real setting.
+A qualitative study would have been useful if we were interested in exploring a particular hypothesis.
+For similar reasons, a case study would also not have been applicable as we were not concerning ourselves with how MDSD works in a real setting.
 Likewise, as industry and academia seem to differ in opinion, there is an implication that there could have been be bias in both sides of the argument.
@@
 
-It is important to note that did not perform either a Systematic Mapping Study nor a Tertiary Review of (XXX cite?) existing literature.
+It is important to note that did not perform either a Systematic Mapping Study nor a Tertiary Review of \cite{kitchenham2007guidelines} existing literature.
 There was sufficient evidence in existence for the applicability of MDSD such that we could rule out the need to perform a Systematic Mapping Study.
@@
 All identified SLRs \cite{santiago2012model} \cite{dias2007survey} \cite{loniewski2010systematic} \cite{nicolas2009generation} were, however, researching the usage of model-driven techniques in other fields, such as traceability management \cite{santiago2012model}, testing \cite{dias2007survey} and requirements engineering \cite{loniewski2010systematic} \cite{nicolas2009generation}.
-Based on these results, the need to evaluate previous research on model driven \textit{software} development was identified.
+Based on these results, the need to evaluate previous research on model-driven \textit{software} development was identified.
 
@@
 The main research question was constructed to create a wide scope to be able to investigate which characteristics are most vital to consider when adopting MDSD.
-The sub-questions were constructed to provide more detailed answers for specific questions that are valuable to the industry and companies who are considering to implement MDSD.
+The sub-questions were constructed to provide more detailed answers for specific questions that are valuable to the industry and to companies which are considering implementing MDSD.
 
@@
 Possible publication bias was taken into account during the study.
-From our trial study and previous research into related work, it became clear that there existed bias towards the adoption of MDSD; there were few papers which spoke ill of it.
+From our trial study and previous research into related work, it became clear that there existed bias towards the adoption of MDSD; there were few papers which had a negative outlook on the adoption of MDSD.
 To help alleviate this we checked, but did not include, grey literature (non-formally published papers) and conference proceedings.
@@
 
-The digital libraries, mentioned in Table 1, were chosen for their extensive catalogues, reliability and availability of the data.
+The digital libraries, mentioned in Table 1, were chosen for their extensive catalogues, reliability and availability of data.
 Hand searching of journals was not performed as we decided to limit the scope of the search to digital libraries, conferences and other sources.
 
-Given that MDSD is a relatively new process, we decided to limit the search starting to papers published 1990 to the current date.
-We feel that this limitation on the search did not hinder the results as we were unable to find any papers published prior to this date concerning MDSD.
+Given that MDSD is a relatively new process, we decided to limit the search to papers published from 1990 to the current date.
+We feel that this limitation on the search did not hinder the results as we were unable to find any papers published prior to this date concerning the adoption of MDSD.
 
 The selection criteria for the papers were refined during this stage.
-After applying the initial exclusion and inclusion criteria, exclusions and inclusions were based on practicality.
+After applying the initial exclusion and inclusion criteria, further exclusions and inclusions were based on practicality.
 Below is a short list of these criteria.
@@
 All conflicts regarding to acceptance of papers was discussed and resolved prior to their inclusion in the SLR.
-The initial Kappa rating achieved was 0.78, which lies in the band 0.61 - 0.80 indicating a strong alignment between the researchers.
+The initial Kappa rating achieved was 0.78, which lies in the band 0.61 - 0.80, indicating a strong alignment between the researchers.
 
-Furthermore, as per the suggestion from Kitchenham \cite{kitchenham2007guidelines} after the application of the inclusion and exclusion criteria any paper failing to meet these criteria was retained and will be shown in the results of the SLR.
+Furthermore, as per the suggestion from Kitchenham \cite{kitchenham2007guidelines}, after the application of the inclusion and exclusion criteria, any paper failing to meet these criteria was retained in an exclusion list.
+This list be shown with the results of the SLR.
 

### 2015-03-05 rmtw/a4/stat/script.R
Added R stuff

@@ -1,0 +1,28 @@
+uc_eff <- c(1.3, 8.0, 2.7, 2.7, 6.7, 9.3, 2.7, 5.3, 2.7, 16.0, 4.0, 
+          2.7, 4.0, 14.7, 5.3, 6.7, 4.0, 2.7, 4.0, 13.3, 2.7, 6.7, 
+          13.3, 5.3, 2.7, 10.7)
+
+uc_rate <- c(0.03, 0.16, 0.05, 0.05, 0.13, 0.18, 0.05, 0.11, 0.05, 
+             0.32, 0.08, 0.05, 0.08, 0.29, 0.11, 0.13, 0.08, 0.05, 
+             0.08, 0.26, 0.05, 0.13, 0.26, 0.11, 0.05, 0.21)
+
+cl_eff <- c(2.7, 1.3, 10.7, 13.3, 8.0, 10.7, 8.0, 13.3, 9.3, 8.0, 
+            9.3, 8.0, 4.0, 10.7, 6.7, 6.7, 5.3, 5.3, 4.0, 5.3, 
+            2.7, 5.3, 5.3, 5.3, 13.3, 7.3)
+cl_eff_mean = mean(cl_eff)
+
+
+cl_rate <- c(0.05, 0.03, 0.21, 0.26, 0.16, 0.21, 0.16, 0.26, 0.18,
+             0.16, 0.18, 0.16, 0.08, 0.21, 0.13, 0.13, 0.11, 0.11, 
+             0.08, 0.11, 0.05, 0.11, 0.11, 0.11, 0.26, 0.1448)
+cl_rate_mean = mean(cl_rate)
+
+eff_data <- data.frame(uc_eff, cl_eff)
+
+rate_data <- data.frame(uc_rate, cl_rate)
+
+boxplot(rate_data)
+
+
+
+

### 2015-03-05 rmtw/a4/latex8.tex
Added tests for H eff and H rate

@@
 
+\Section{Tests for eff}
+
+%R output start
+	F test to compare two variances
+
+data:  uc_eff and cl_eff
+F = 1.61, num df = 25, denom df = 25, p-value = 0.2407
+alternative hypothesis: true ratio of variances is not equal to 1
+95 percent confidence interval:
+ 0.721893 3.590874
+sample estimates:
+ratio of variances 
+          1.610039 
+%R output end
+
+Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.
+
+------------------------------------------------------------
+
+%R output start
+	Two Sample t-test
+
+data:  uc_eff and cl_eff
+t = -1.0786, df = 50, p-value = 0.286
+alternative hypothesis: true difference in means is not equal to 0
+95 percent confidence interval:
+ -3.2585387  0.9816156
+sample estimates:
+mean of x mean of y 
+ 6.161538  7.300000 
+ %R output end
+
+According to the test, the efficiency of CL is 7.3 while the efficiency of UC is 6.16 and H1 eff is therefore accepted.
+
+\Section{Tests for rate}
+
+%R output start
+	F test to compare two variances
+
+data:  uc_rate and cl_rate
+F = 1.7018, num df = 25, denom df = 25, p-value = 0.1907
+alternative hypothesis: true ratio of variances is not equal to 1
+95 percent confidence interval:
+ 0.7630304 3.7955018
+sample estimates:
+ratio of variances 
+          1.701788 
+%R output end
+
+Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.
+
+------------------------------------------------------------
+
+%R output start
+	Two Sample t-test
+
+data:  uc_rate and cl_rate
+t = -1.1416, df = 50, p-value = 0.2591
+alternative hypothesis: true difference in means is not equal to 0
+95 percent confidence interval:
+ -0.06525100  0.01795869
+sample estimates:
+mean of x mean of y 
+0.1211538 0.1448000 
+%R output end
+
+According to the test, the rate of CL is 1.45 while the effectiveness of UC is 0.12 and H1 rate is therefore accepted.
+
 \bibliographystyle{latex8}

### 2015-03-05 rmtw/a4/stat/script.R

@@ -18,10 +18,23 @@ cl_rate <- c(0.05, 0.03, 0.21, 0.26, 0.16, 0.21, 0.16, 0.26, 0.18,
 cl_rate_mean = mean(cl_rate)
 
 eff_data <- data.frame(uc_eff, cl_eff)
-
 rate_data <- data.frame(uc_rate, cl_rate)
 
-boxplot(rate_data)
+rate_box <- boxplot(rate_data)
+eff_box <- boxplot(eff_data)
+
+
+
+
+
+var.test(uc_eff, cl_eff)
+
+t.test(uc_eff, cl_eff, var.equal=TRUE)
+
+var.test(uc_rate, cl_rate)
+
+t.test(uc_rate, cl_rate, var.equal=TRUE)
+
 
 
 

### 2015-03-05 rmtw/a4/latex8.tex
Added chi test for #3

--- 2015-02-18 rmtw/a4/latex8.tex
@@
 \usepackage{url}
+\usepackage{verbatim}
 
@@
 
-%Deficiencies introduction model
-
-​\Section{Introduction}
-Software inspections have since its inception [1] more than
-25 years ago spawned quite some interest both from the
-research community and industrial practice. The research
-includes changes to the inspection process, e.g. [2], support to
-the process, e.g. [3] and empirical studies, e.g. [4]. The
-suggested improvements include active design reviews [5] and
-perspective-based reading [6]. Industry has studied the
-benefits of conducting software inspections [7].
-The objective of this study is to compare and hence
-evaluate how well the use-case based reading performs in
-comparison to other methods. The study presents a controlled
-experiment where use-case based reading is compared to
-checklist-based reading.
-
-\Section{Purpose of the Study}
-* Purpose statement (copy paste from the file ‘Experiment\_Design.pdf’ file)
-
-* Research Questions (copy paste from the file ‘Experiment\_Design.pdf’ file)
-
-* Hypothesis (copy paste from the file ‘Experiment\_Design.pdf’ file)
-
 \Section{Methodology}
@@
 \Section{Results}
-Read \url{https://dl.dropboxusercontent.com/u/2437798/Juristo%20Basics%20of%20Software%20Engineering%20Experimentation.pdf} pp. 133
 
@@
 
+\Section{Tests for eff}
+
+\verbatiminput{f_eff.txt}
+
+Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.
+
+\verbatiminput{t_eff.txt}
+
+According to the test, the efficiency of CL is 7.3 while the efficiency of UC is 6.16 and H0 eff is therefore rejected.
+
+\Section{Tests for rate}
+
+\verbatiminput{f_rate.txt}
+
+Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.
+
+\verbatiminput{t_rate.txt}
+
+According to the test, the rate of CL is 1.45 while the effectiveness of UC is 0.12 and h0 rate is therefore rejected.
+
+\Section{Tests for #3}
+
+%%R output
+	Chi-squared test for given probabilities
+
+data:  ct
+X-squared = 5.4847, df = 2, p-value = 0.06442
+
+Since our significance level is 0.05 and p > 0.05, there is no significant difference and h1 is rejected. 
+%%R output
+
+Chi-square test requirements[edit]
+Quantitative data.
+One or more categories.
+Independent observations.
+Adequate sample size (at least 10).
+Simple random sample.
+Data in frequency form.
+All observations must be used.
 \bibliographystyle{latex8}

### 2015-03-05 rmtw/a4/stat/script.R

@@ -38,4 +38,242 @@ t.test(uc_rate, cl_rate, var.equal=TRUE)
 
 
 
+data <- read.table(header=TRUE, text='
+          condition result
+                  CL  A
+                  CL	B
+                  CL	C
+                   CL	C
+                   CL	B
+                   CL	B
+                   CL	C
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	C
+                   CL	A
+                   CL	B
+                   CL	A
+                   CL	B
+                   CL	A
+                   CL	B
+                   CL	C
+                   CL	C
+                   CL	A
+                   CL	A
+                   CL	C
+                   CL	C
+                   CL	C
+                   CL	B
+                   CL	C
+                   CL	C
+                   CL	C
+                   CL	C
+                   CL	A
+                   CL	A
+                   CL	A
+                   CL	B
+                   CL	A
+                   CL	B
+                   CL	A
+                   CL	B
+                   CL	A
+                   CL	B
+                   CL	A
+                   CL	C
+                   CL	C
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	A
+                   CL	A
+                   CL	A
+                   CL	B
+                   CL	A
+                   CL	B
+                   CL	B
+                   CL	A
+                   CL	C
+                   CL	C
+                   CL	C
+                   CL	A
+                   CL	A
+                   CL	C
+                   CL	B
+                   CL	C
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	A
+                   CL	C
+                   CL	B
+                   CL	A
+                   CL	B
+                   CL	C
+                   CL	B
+                   CL	A
+                   CL	A
+                   CL	B
+                   CL	C
+                   CL	C
+                   CL	A
+                   CL	A
+                   CL	B
+                   CL	A
+                   CL	B
+                   CL	B
+                   CL	A
+                   CL	A
+                   CL	B
+                   CL	B
+                   CL	A
+                   CL	B
+                   CL	C
+                   CL	A
+                   CL	B
+                   CL	C
+                   CL	C
+                   CL	C
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	C
+                   CL	C
+                   CL	B
+                   CL	B
+                   CL	B
+                   CL	C
+                   CL	B
[…]

### 2015-03-07 rmtw/a4/latex8.tex
dsaf

@@
 \usepackage{verbatim}
-
+\usepackage{fixltx2e}
+\usepackage{graphicx}
 %\documentstyle[times,art10,twocolumn,latex8]{article}
@@
 \Section{Methodology}
+This section will describe which statistical tests were used, and why. The level of significance used for all tests is 5\%.
+
+\SubSection{Tests Used for H\textsubscript{eff} and H\textsubscript{rate}}
+Initially, Kolmogorov-Smirnov (KS) Goodness-of-Fit and Shapiro-Wilks (SW) tests were used to determine if the assumption of normality could be held for the data set.
+The KS and SW tests both reported p-values < 0.05 and thus the null hypotheses of the data being normally distributed was rejected.
+See Table 1 for the results of the KS and SW tests.
+
+\begin{table}
+	\centering
+	\begin{tabular}[ht]{| l | l | l |}
+	\hline
+	Test & Sample & p-value  \\
+	\hline
+	KS & UC & =< 2.2e-16 \\
+	\hline
+	SW & UC & 0.000969 \\
+	\hline
+	KS & CL & =< 2.2e-16 \\
+	\hline
+	SW & CL & 0.309 \\	
+	\hline
+	\end{tabular}
+	\caption{Results of normality tests}
+\end{table}
+
+A graphical representation of the level of normalisation can be seen in Figure 1 and 2. The results from the tests are supported by the sparseness of the data points.
+
+\begin{figure}[Ht!]
+\centering
+\includegraphics[width=90mm]{uc_qq.png}
+\caption{Use Case Q-Q plot}
+\end{figure}
+
+\begin{figure}[Ht!]
+\centering
+\includegraphics[width=90mm]{cl_qq.png}
+\caption{Checklist Q-Q plot}
+\end{figure}
+
+The next step was to perform outlier test. The method used was boxplots. As seen in Figure 3 and 4, no outliers were detected and thus no data points were removed in the tests performed.
+
+\begin{figure}[Ht!]
+\centering
+\includegraphics[width=90mm]{uc_box.png}
+\caption{Use Case Boxplot}
+\end{figure}
+
+\begin{figure}[Ht!]
+\centering
+\includegraphics[width=90mm]{cl_box.png}
+\caption{Checklist Boxplot}
+\end{figure}
+
+Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum teset was chosen instead of the Student's T-test as the final test.
+The result of the WMW test was W=250, p=0.1063 and with the significance level of 89 (cite www.sussex) H0 is rejected.
+(Note that this was done on the raw data and not /45*60).
+
+http://www.sussex.ac.uk/Users/grahamh/RM1web/WilcoxonTable2005.pdf
+
+MWW = good for cont tests as well.
+ Mann, Henry B.; Whitney, Donald R.
+(1947).
+"On a Test of Whether one of Two Random Variables is Stochastically Larger than the Other".
+Annals of Mathematical Statistics 18 (1): 50–60.
+doi:10.1214/aoms/1177730491.
+MR 22058.
+Zbl 0041.26103.
+
+1 and 2.
+Box
+->
+Histo, QQ, kolmogorov, z-test?
+->
+T
+
+3.
+Z-test verkar vara ett alternativ till chi
+
 * Method(s) for analyzing the data (Statistical analysis)
@@
 
-\Section{Tests for #3}
+\Section{Tests for 3}
 

### 2015-03-07 rmtw/a4/stat/first.R

@@ -1,0 +1,45 @@
+
+uc_eff <- c(1.3, 8.0, 2.7, 2.7, 6.7, 9.3, 2.7, 5.3, 2.7, 16.0, 4.0, 
+          2.7, 4.0, 14.7, 5.3, 6.7, 4.0, 2.7, 4.0, 13.3, 2.7, 6.7, 
+          13.3, 5.3, 2.7, 10.7)
+
+
+uc_eff <- c(2.7, 1.3, 10.7, 13.3, 8.0, 10.7, 8.0, 13.3, 9.3, 8.0, 
+            9.3, 8.0, 4.0, 10.7, 6.7, 6.7, 5.3, 5.3, 4.0, 5.3, 
+            2.7, 5.3, 5.3, 5.3, 13.3, 7.3)
+
+
+uc_rate <- c(0.03, 0.16, 0.05, 0.05, 0.13, 0.18, 0.05, 0.11, 0.05, 
+             0.32, 0.08, 0.05, 0.08, 0.29, 0.11, 0.13, 0.08, 0.05, 
+             0.08, 0.26, 0.05, 0.13, 0.26, 0.11, 0.05, 0.21)
+
+cl_rate <- c(0.05, 0.03, 0.21, 0.26, 0.16, 0.21, 0.16, 0.26, 0.18,
+             0.16, 0.18, 0.16, 0.08, 0.21, 0.13, 0.13, 0.11, 0.11, 
+             0.08, 0.11, 0.05, 0.11, 0.11, 0.11, 0.26, 0.1448)
+
+UC = c(1, 6, 2, 2, 5, 7, 2, 4, 2, 12, 3, 2, 3, 11, 4, 5, 3, 2, 3, 10, 2, 5, 10, 4, 2, 8)
+
+CL = c(2, 1, 8, 10, 6, 8, 6, 10, 7, 6, 7, 6, 3, 8, 5, 5, 4, 4, 3, 4, 2, 4, 4, 4, 10, 5.48)
+m = mean(CL)
+
+#box_data <- data.frame(UC, CL)
+#boxplot(box_data)
+#boxplot(UC, main = "UC Boxplot")
+#boxplot(CL, main = "CL Boxplot")
+
+
+#ks.test(UC, "pnorm")
+#shapiro.test(UC)
+#ks.test(CL, "pnorm")
+#shapiro.test(CL)
[…]

### 2015-03-07 rmtw/a4/stat/script.R

@@ -17,6 +17,8 @@ cl_rate <- c(0.05, 0.03, 0.21, 0.26, 0.16, 0.21, 0.16, 0.26, 0.18,
              0.08, 0.11, 0.05, 0.11, 0.11, 0.11, 0.26, 0.1448)
 cl_rate_mean = mean(cl_rate)
 
+
+
 eff_data <- data.frame(uc_eff, cl_eff)
 rate_data <- data.frame(uc_rate, cl_rate)
 
@@ -38,242 +40,17 @@ t.test(uc_rate, cl_rate, var.equal=TRUE)
 
 
 
-data <- read.table(header=TRUE, text='
-          condition result
-                  CL  A
-                  CL	B
-                  CL	C
-                   CL	C
-                   CL	B
-                   CL	B
-                   CL	C
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	C
-                   CL	A
-                   CL	B
-                   CL	A
-                   CL	B
-                   CL	A
-                   CL	B
-                   CL	C
-                   CL	C
-                   CL	A
-                   CL	A
-                   CL	C
-                   CL	C
-                   CL	C
-                   CL	B
-                   CL	C
-                   CL	C
-                   CL	C
-                   CL	C
-                   CL	A
-                   CL	A
-                   CL	A
-                   CL	B
-                   CL	A
-                   CL	B
-                   CL	A
-                   CL	B
-                   CL	A
-                   CL	B
-                   CL	A
-                   CL	C
-                   CL	C
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	A
-                   CL	A
-                   CL	A
-                   CL	B
-                   CL	A
-                   CL	B
-                   CL	B
-                   CL	A
-                   CL	C
-                   CL	C
-                   CL	C
-                   CL	A
-                   CL	A
-                   CL	C
-                   CL	B
-                   CL	C
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	B
-                   CL	A
-                   CL	C
-                   CL	B
-                   CL	A
-                   CL	B
-                   CL	C
-                   CL	B
-                   CL	A
-                   CL	A
-                   CL	B
-                   CL	C
-                   CL	C
-                   CL	A
-                   CL	A
-                   CL	B
-                   CL	A
-                   CL	B
[…]

### 2015-03-09 rmtw/a4/latex8.tex
sfa

@@
 \Section{Methodology}
-This section will describe which statistical tests were used, and why. The level of significance used for all tests is 5\%.
+This section will describe which statistical tests were used, and why. The level of significance used for all tests is 0.05.
 
@@
 Initially, Kolmogorov-Smirnov (KS) Goodness-of-Fit and Shapiro-Wilks (SW) tests were used to determine if the assumption of normality could be held for the data set.
-The KS and SW tests both reported p-values < 0.05 and thus the null hypotheses of the data being normally distributed was rejected.
-See Table 1 for the results of the KS and SW tests.
+The data used for the tests was the number faults found by each participant.
+The reason this data was chosen was that it directly correlates to the data used in H\textsubscript{eff} and H\textsubscript{rate}.
+The KS and SW tests both reported p-values < 0.05.
+See Table 1 for the p-values of the KS and SW tests.
+The critical value analysis for the KS and SW showed similar results and thus the null hypotheses of the data being normally distributed was rejected.
+See Table 2 for more information about the critical value results of the KS and SW tests.
 
@@
 	\centering
-	\begin{tabular}[ht]{| l | l | l |}
+	\begin{tabular}[Ht]{| l | l | l |}
 	\hline
@@
 	\hline
-	KS & UC & =< 2.2e-16 \\
+	KS & UC & \textless 2.2e-16 \\
 	\hline
@@
 	\hline
-	KS & CL & =< 2.2e-16 \\
+	KS & CL & \textless 2.2e-16 \\
 	\hline
@@
 	\end{tabular}
-	\caption{Results of normality tests}
+	\caption{KS \& SW tests - p-value}
+\end{table}
+
+\begin{table}
+	\centering
+	\begin{tabular}[Ht]{| l | l | l | l |}
+	\hline
+	Test & Sample & Critical Value & D (result)  \\
+	\hline
+	KS & UC & 0.270 & 0.9388 \\
+	\hline
+	SW & UC & 0.964 &  0.8412 \\
+	\hline
+	KS & CL & 0.270 & 0.9388 \\
+	\hline
+	SW & CL & 0.964 & 0.9553 \\	
+	\hline
+	\end{tabular}
+	\caption{KS \& SW tests - Critical Value}
 \end{table}
@@
 
-\begin{figure}[Ht!]
+\begin{figure}[Ht]
 \centering

### 2015-03-09 rmtw/a4/stat/first.R

@@ -1,45 +1,33 @@
-
 uc_eff <- c(1.3, 8.0, 2.7, 2.7, 6.7, 9.3, 2.7, 5.3, 2.7, 16.0, 4.0, 
           2.7, 4.0, 14.7, 5.3, 6.7, 4.0, 2.7, 4.0, 13.3, 2.7, 6.7, 
           13.3, 5.3, 2.7, 10.7)
-
-
 uc_eff <- c(2.7, 1.3, 10.7, 13.3, 8.0, 10.7, 8.0, 13.3, 9.3, 8.0, 
             9.3, 8.0, 4.0, 10.7, 6.7, 6.7, 5.3, 5.3, 4.0, 5.3, 
             2.7, 5.3, 5.3, 5.3, 13.3, 7.3)
-
-
 uc_rate <- c(0.03, 0.16, 0.05, 0.05, 0.13, 0.18, 0.05, 0.11, 0.05, 
              0.32, 0.08, 0.05, 0.08, 0.29, 0.11, 0.13, 0.08, 0.05, 
              0.08, 0.26, 0.05, 0.13, 0.26, 0.11, 0.05, 0.21)
-
 cl_rate <- c(0.05, 0.03, 0.21, 0.26, 0.16, 0.21, 0.16, 0.26, 0.18,
              0.16, 0.18, 0.16, 0.08, 0.21, 0.13, 0.13, 0.11, 0.11, 
              0.08, 0.11, 0.05, 0.11, 0.11, 0.11, 0.26, 0.1448)
 
-UC = c(1, 6, 2, 2, 5, 7, 2, 4, 2, 12, 3, 2, 3, 11, 4, 5, 3, 2, 3, 10, 2, 5, 10, 4, 2, 8)
 
+UC = c(1, 6, 2, 2, 5, 7, 2, 4, 2, 12, 3, 2, 3, 11, 4, 5, 3, 2, 3, 10, 2, 5, 10, 4, 2, 8)
 CL = c(2, 1, 8, 10, 6, 8, 6, 10, 7, 6, 7, 6, 3, 8, 5, 5, 4, 4, 3, 4, 2, 4, 4, 4, 10, 5.48)
 m = mean(CL)
 
 #box_data <- data.frame(UC, CL)
 #boxplot(box_data)
-#boxplot(UC, main = "UC Boxplot")
+boxplot(UC, main = "UC Boxplot")
 #boxplot(CL, main = "CL Boxplot")
 
 
[…]

### 2015-03-09 rmtw/a4/latex8.tex
adsffdsa

@@
 
-The next step was to perform outlier test. The method used was boxplots. As seen in Figure 3 and 4, no outliers were detected and thus no data points were removed in the tests performed.
+The next step was to perform an outlier test. The method used was boxplots. As seen in Figure 3 and 4, no outliers were detected and thus no data points were removed in the tests performed.
 
-\begin{figure}[Ht!]
+\begin{figure}[Ht]
 \centering
@@
 
+\Section{Results}
+
+\subsection{first hypothesis}
 Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum teset was chosen instead of the Student's T-test as the final test.
-The result of the WMW test was W=250, p=0.1063 and with the significance level of 89 (cite www.sussex) H0 is rejected.
-(Note that this was done on the raw data and not /45*60).
+The data used for the WMW test was the efficiency of each participant.
+The result of the WMW test was W=250, p=0.1063 and with the significance level of 536 H0 is rejected.
+
+\subsection{second hyphothesis}
 
@@
 
-1 and 2.
-Box
-->
-Histo, QQ, kolmogorov, z-test?
-->
-T
-
-3.
-Z-test verkar vara ett alternativ till chi
-
-* Method(s) for analyzing the data (Statistical analysis)
-
-* Motivation of why these statistical tests where used
-
-\Section{Results}
-
-*Report the results
-
-*Discuss what does the results means, how do we interpret it
-
 \Section{Tests for eff}
 
-\verbatiminput{f_eff.txt}
-
-Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.
-
-\verbatiminput{t_eff.txt}
-
-According to the test, the efficiency of CL is 7.3 while the efficiency of UC is 6.16 and H0 eff is therefore rejected.
-
-\Section{Tests for rate}
-
-\verbatiminput{f_rate.txt}
-
-Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.
-
-\verbatiminput{t_rate.txt}
-
-According to the test, the rate of CL is 1.45 while the effectiveness of UC is 0.12 and h0 rate is therefore rejected.
-
 \Section{Tests for 3}
-
-%%R output
-	Chi-squared test for given probabilities
-
-data:  ct
-X-squared = 5.4847, df = 2, p-value = 0.06442
-
-Since our significance level is 0.05 and p > 0.05, there is no significant difference and h1 is rejected. 
-%%R output
 

### 2015-03-09 rmtw/a4/stat/first.R

@@ -1,7 +1,7 @@
 uc_eff <- c(1.3, 8.0, 2.7, 2.7, 6.7, 9.3, 2.7, 5.3, 2.7, 16.0, 4.0, 
           2.7, 4.0, 14.7, 5.3, 6.7, 4.0, 2.7, 4.0, 13.3, 2.7, 6.7, 
           13.3, 5.3, 2.7, 10.7)
-uc_eff <- c(2.7, 1.3, 10.7, 13.3, 8.0, 10.7, 8.0, 13.3, 9.3, 8.0, 
+cl_eff <- c(2.7, 1.3, 10.7, 13.3, 8.0, 10.7, 8.0, 13.3, 9.3, 8.0, 
             9.3, 8.0, 4.0, 10.7, 6.7, 6.7, 5.3, 5.3, 4.0, 5.3, 
             2.7, 5.3, 5.3, 5.3, 13.3, 7.3)
 uc_rate <- c(0.03, 0.16, 0.05, 0.05, 0.13, 0.18, 0.05, 0.11, 0.05, 
@@ -16,18 +16,21 @@ UC = c(1, 6, 2, 2, 5, 7, 2, 4, 2, 12, 3, 2, 3, 11, 4, 5, 3, 2, 3, 10, 2, 5, 10, 
 CL = c(2, 1, 8, 10, 6, 8, 6, 10, 7, 6, 7, 6, 3, 8, 5, 5, 4, 4, 3, 4, 2, 4, 4, 4, 10, 5.48)
 m = mean(CL)
 
+
+
+
 #box_data <- data.frame(UC, CL)
 #boxplot(box_data)
-boxplot(UC, main = "UC Boxplot")
+#boxplot(UC, main = "UC Boxplot")
 #boxplot(CL, main = "CL Boxplot")
 
 
 #ks.test(UC, "pnorm")
-shapiro.test(UC)
+#shapiro.test(UC)
 #ks.test(CL, "pnorm")
-shapiro.test(CL)
+#shapiro.test(CL)
 #qqnorm(UC, main="Use Case Q-Q"); qqline(UC, col = 2,lwd=2,lty=2)
 #qqnorm(CL, main="Checklist Q-Q"); qqline(CL, col = 2,lwd=2,lty=2)
 
-#wilcox.test(UC, CL) 
-#wilcox.test(x,z, paired=TRUE)
+wilcox.test(uc_eff, cl_eff) 
+

### 2015-03-09 rmtw/a4/latex8.tex
sdf

@@
 \subsection{first hypothesis}
-Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum teset was chosen instead of the Student's T-test as the final test.
+Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test.
 The data used for the WMW test was the efficiency of each participant.

### 2015-03-09 rmtw/a4/stat/first.R
added WMW test for 2nd hyp

@@ -33,4 +33,5 @@ m = mean(CL)
 #qqnorm(CL, main="Checklist Q-Q"); qqline(CL, col = 2,lwd=2,lty=2)
 
 wilcox.test(uc_eff, cl_eff) 
+wilcox.test(uc_rate, cl_rate)
 

### 2015-03-09 rmtw/a4/latex8.tex
added WMW test for 2nd hyp
Updated section headers and added subscripts

@@
 
-\subsection{first hypothesis}
+\subsection{There is no difference in efficiency}
 Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test.
 The data used for the WMW test was the efficiency of each participant.
-The result of the WMW test was W=250, p=0.1063 and with the significance level of 536 H0 is rejected.
+The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0 Eff} is rejected.
 
-\subsection{second hyphothesis}
+\subsection{There is no difference in effectiveness}
+The same test was chosen for Hrate, based on the same reasoning.
+The result of the WMW test for Hrate was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0 Rate} is rejected.
 
@@
 (1947).
-"On a Test of Whether one of Two Random Variables is Stochastically Larger than the Other".
+``On a Test of Whether one of Two Random Variables is Stochastically Larger than the Other''.
 Annals of Mathematical Statistics 18 (1): 50–60.

### 2015-03-09 rmtw/a4/latex8.tex
Changes have been made!

@@
 The data used for the WMW test was the efficiency of each participant.
-The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0 Eff} is rejected.
+The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0} Eff is rejected.
 
@@
 The same test was chosen for Hrate, based on the same reasoning.
-The result of the WMW test for Hrate was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0 Rate} is rejected.
+The result of the WMW test for Hrate was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0} Rate is rejected.
 

### 2015-03-09 rmtw/a4/stat/first.R
sdf

@@ -32,6 +32,12 @@ m = mean(CL)
 #qqnorm(UC, main="Use Case Q-Q"); qqline(UC, col = 2,lwd=2,lty=2)
 #qqnorm(CL, main="Checklist Q-Q"); qqline(CL, col = 2,lwd=2,lty=2)
 
-wilcox.test(uc_eff, cl_eff) 
-wilcox.test(uc_rate, cl_rate)
+#wilcox.test(uc_eff, cl_eff) 
+#wilcox.test(uc_rate, cl_rate)
 
+uc_row = c(36, 40, 35)
+cl_row = c(31, 47, 28)
+
+data.table = rbind(uc_row, cl_row)
+
+chisq.test(data.table)

### 2015-03-10 rmtw/a4/latex8.tex
dsf
coppy papsste

@@
 \usepackage{graphicx}
+\usepackage{enumitem}
 %\documentstyle[times,art10,twocolumn,latex8]{article}
@@
 
+\section{Introduction}
+Software inspections have since its inception [1] more than
+25 years ago spawned quite some interest both from the
+research community and industrial practice. The research
+includes changes to the inspection process, e.g. [2], support to
+the proceThe dependent variables are analyzed to evaluate the
+hypotheses of the experiment. The main null and alternative
+hypotheses [12] are stated below. These are evaluated for all
+faults, class A faults and class A\&B faults. The hypotheses
+concern efficiency, effectiveness and fault detecting
+differences:ss, e.g. [3] and empirical studies, e.g. [4]. The
+suggested improvements include active design reviews [5] and
+perspective-based reading [6]. Industry has studied the
+benefits of conducting software inspections [7].
+
+\section{Purpose of the Study}
+This section will describe the purpose of the study, the research questions and the hypotheses.
+
+\subsection{Purpose Statement}
+The objective of this study is to compare and hence
+evaluate how well the use-case based reading performs in
+comparison to other methods. The study presents a controlled
+experiment where use-case based reading is compared to
+checklist-based reading.
+
+\subsubsection{Variables}
+Three types of variables are defined for the experiment,
+independent, controlled, and dependent variables.
+
+\begin{enumerate}[label=(\alph*)]
+
+\item Independent Variable: The independent variable is
+the reading technique used. The experiment groups used either
+Use-Cased Based Reading or Checklist-Based Reding.
+\item Controlled Variable: The controll variable is the
+experience of the reviwers and it is measured on an ordinal
+scale. The reviwers were asked to fill in a questionnare
+comprising seven questions.
+\item Dependent Variables: The dependent varialbles
+measured are faults. The four variables are: (1) Number of
+faults found by each reviwer, (2) Number of faults found by
+each experiment group, (3) efficiency (faults/hour) and is
+measured as: 60*(number of fault found/inspection time which
+is 45 min), and (4) effectivness (detection rate) and is mesured
+as: number of faults found/total number of faults.
+
+\end{enumerate}
+
+\subsection{Research Questions}
+
+\subsection{Hypothesis}
+The general hypothesis of the experiment is that Use-Case
+Based Reading is more efficient and effective in finding faults
+of the most critical fault classes, i.e. Checklist-Based Reading
+is assumed to find more faults per time unit, and to find a
+larger rate of the critical faults.
+The dependent variables are analyzed to evaluate the
+hypotheses of the experiment. The main null and alternative
+hypotheses [12] are stated below. These are evaluated for all
+faults, class A faults and class A\&B faults. The hypotheses
+concern efficiency, effectiveness and fault detecting
+differences:
+\begin{itemize}
+\item H\textsubscript{0 Eff} - There is no difference in efficiency (i.e.found faults per hour) between the reviewers applying use cases and the reviewers using a checklist.
+\item H\textsubscript{1 Eff} - There is a difference in efficiency between the reviewers applying prioritized use cases and the reviewers using a checklist.
+\item H\textsubscript{0 Rate} - There is no difference in effectiveness (i.e. rate of faults found) between the reviewers applying use cases and the reviewers using a checklist.
+\item H\textsubscript{1 Rate} - There is a difference in effectiveness between the reviewers applying use cases and the reviewers using a checklist.
+\item H\textsubscript{0 Fault} - The reviewers applying use cases do not detect different faults than the reviewers using a checklist.
+\item H\textsubscript{1 Fault} - The reviewers applying use cases detect different faults than the reviewers using a checklist.
+
+\end{itemize}
+
 \Section{Methodology}
@@
 	\centering
-	\begin{tabular}[Ht]{| l | l | l |}
+	\begin{tabular}[ht]{| l | l | l |}
 	\hline
@@
 	\centering
-	\begin{tabular}[Ht]{| l | l | l | l |}
+	\begin{tabular}[ht]{| l | l | l | l |}
 	\hline
@@
 
-\begin{figure}[Ht]
+\begin{figure}[ht]
 \centering
@@
 The result of the WMW test for Hrate was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0} Rate is rejected.
+
+\subsection{Results for Hfault}
+
+data:  data.table
+X-squared = 1.5998, df = 2, p-value = 0.4494
 

### 2015-03-10 rmtw/a4/latex8.tex
Added Hyp3 stuff

@@
 
+\SubSection{Test Used for H\textsubscript{fault}}
+The frequency of A, B and C faults found were tabularised against the groups which found them.
+An example of this is found in table 3.
+In order to determine if they do find the same faults, a Chi-Square test of independence was performed on the tabulated results.
+
+\begin{table}
+	\centering
+	\begin{tabular}[Ht]{| l | l | l | l |}
+	\hline
+	 & A Faults & B Faults & C Faults  \\
+	\hline
+	Group A & 36 & 40 & 35 \\
+	\hline
+	Group B & 31 & 47 & 28 \\
+	\hline
+	\end{tabular}
+	\caption{Fault counts of risk type per group}
+\end{table}
+
 \begin{table}

### 2015-03-10 rmtw/a4/latex8.tex
fdsa
Added reason for Chi-Test

@@
 
-\SubSection{Test Used for H\textsubscript{fault}}
-The frequency of A, B and C faults found were tabularised against the groups which found them.
-An example of this is found in table 3.
-In order to determine if they do find the same faults, a Chi-Square test of independence was performed on the tabulated results.
-
-\begin{table}
-	\centering
-	\begin{tabular}[Ht]{| l | l | l | l |}
-	\hline
-	 & A Faults & B Faults & C Faults  \\
-	\hline
-	Group A & 36 & 40 & 35 \\
-	\hline
-	Group B & 31 & 47 & 28 \\
-	\hline
-	\end{tabular}
-	\caption{Fault counts of risk type per group}
-\end{table}
-
 \begin{table}
@@
 
+\SubSection{Test Used for H\textsubscript{Fault}}
+The frequency of A, B and C faults found were tabularised against the groups which found them.
+Any response that was not not applicable (NA) was discarded from the table.
+An example of this is found in table 3.
+In order to determine if they do find the same faults, a Chi-Square test of independence was performed on the tabulated results.
+The reason the Chi-Square test of independence was used was primarily because the data we wished to use were catagorical and the frequency of each category was at least 5.
+Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows.
+Fishers test should only be used for 2x2 tables.
+
+\begin{table}
+	\centering
+	\begin{tabular}[Ht]{| l | l | l | l |}
+	\hline
+	 & A Faults & B Faults & C Faults  \\
+	\hline
+	Group A & 36 & 40 & 35 \\
+	\hline
+	Group B & 31 & 47 & 28 \\
+	\hline
+	\end{tabular}
+	\caption{Fault counts of risk type per group}
+\end{table}
+
 \Section{Results}

### 2015-03-10 rmtw/a4/latex8.tex
Fixed Typo

@@
 In order to determine if they do find the same faults, a Chi-Square test of independence was performed on the tabulated results.
-The reason the Chi-Square test of independence was used was primarily because the data we wished to use were catagorical and the frequency of each category was at least 5.
+The reason the Chi-Square test of independence was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5.
 Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows.
@@
 
-\subsection{Results for Hfault}
+\subsection{Results for H\textsubscript{Fault}}
 

### 2015-03-10 rmtw/a4/latex8.tex
sdfsa

@@
 
-\SubSection{Tests Used for H\textsubscript{eff} and H\textsubscript{rate}}
+\SubSection{Tests Used for H\textsubscript{Eff} and H\textsubscript{Rate}}
 Initially, Kolmogorov-Smirnov (KS) Goodness-of-Fit and Shapiro-Wilks (SW) tests were used to determine if the assumption of normality could be held for the data set.
 The data used for the tests was the number faults found by each participant.
-The reason this data was chosen was that it directly correlates to the data used in H\textsubscript{eff} and H\textsubscript{rate}.
-The KS and SW tests both reported p-values < 0.05.
+The reason this data was chosen was that it directly correlates to the data used in H\textsubscript{Eff} and H\textsubscript{Rate}.
+No data points were removed from the data set before performing any tests for H\textsubscript{Eff} or H\textsubscript{Rate}.
+The reasoning for this was that the hypotheses only concern number of occurances and not the qualitative attributes of the data.
+This means that data points which, for example, contained ``incorrect'' \textit{Item numbers} were still used in the calculation.
+
+The KS and SW tests both reported p-values \textless 0.05.
 See Table 1 for the p-values of the KS and SW tests.

### 2015-03-10 rmtw/a4/latex8.tex
Fault results

@@
 	\end{tabular}
-	\caption{Fault counts of risk type per group}
+	\caption{Fault frequency of risk type per group}
 \end{table}
@@
 \subsection{Results for H\textsubscript{Fault}}
+As mentioned previously, the Chi-Square test of independence was used to determine if the reviewers discovered the same frequency of results.
+The result of the X\textsubscript{2} was 1.5998, generating a p-value of 0.4494.
+Thus, the null hypothesis H\textsubscript{0} Fault is rejected.
 

### 2015-03-10 rmtw/a4/latex8.tex
sdt

@@
 \section{Introduction}
-Software inspections have since its inception [1] more than
+Software inspections have since its inception \cite{fagan2002design} more than
 25 years ago spawned quite some interest both from the
 research community and industrial practice. The research
-includes changes to the inspection process, e.g. [2], support to
+includes changes to the inspection process, e.g. \cite{bisant1989two}, support to
 the proceThe dependent variables are analyzed to evaluate the
 hypotheses of the experiment. The main null and alternative
-hypotheses [12] are stated below. These are evaluated for all
+hypotheses \cite{montgomery2008design} are stated below. These are evaluated for all
 faults, class A faults and class A\&B faults. The hypotheses
 concern efficiency, effectiveness and fault detecting
-differences:ss, e.g. [3] and empirical studies, e.g. [4]. The
-suggested improvements include active design reviews [5] and
-perspective-based reading [6]. Industry has studied the
-benefits of conducting software inspections [7].
+differences:ss, e.g. \cite{basili1996empirical} and empirical studies, e.g. \cite{basili1999building}. The
+suggested improvements include active design reviews \cite{parnas1985active} and
+perspective-based reading \cite{shull2000perspective}. Industry has studied the
+benefits of conducting software inspections \cite{weller1993lessons}.
 
@@
 hypotheses of the experiment. The main null and alternative
-hypotheses [12] are stated below. These are evaluated for all
+hypotheses \cite{montgomery2008design} are stated below. These are evaluated for all
 faults, class A faults and class A\&B faults. The hypotheses
@@
 differences:
+
 \begin{itemize}
@@
 \Section{Results}
+This section will cover the results of the experiment.
 
-\subsection{There is no difference in efficiency}
+\subsection{Efficiency and Effectiveness A}
 Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test.
@@
 
-\subsection{There is no difference in effectiveness}
+\subsection{Efficiency and Effectiveness B}
 The same test was chosen for Hrate, based on the same reasoning.
@@
 
-http://www.sussex.ac.uk/Users/grahamh/RM1web/WilcoxonTable2005.pdf
-
-MWW = good for cont tests as well.
- Mann, Henry B.; Whitney, Donald R.
-(1947).
-``On a Test of Whether one of Two Random Variables is Stochastically Larger than the Other''.
-Annals of Mathematical Statistics 18 (1): 50–60.
-doi:10.1214/aoms/1177730491.
-MR 22058.
-Zbl 0041.26103.
-
-\Section{Tests for eff}
-
-\Section{Tests for 3}
-
-Chi-square test requirements[edit]
-Quantitative data.
-One or more categories.
-Independent observations.
-Adequate sample size (at least 10).
-Simple random sample.
-Data in frequency form.
-All observations must be used.
 \bibliographystyle{latex8}

### 2015-03-10 rmtw/a4/latex8.tex
Added first draft of results section

@@
 
+The results of the study show some interesting results.
+The rejection of \textsubscript{0} Eff indicates that there is a difference between the efficiency of the inspection methods.
+This difference could be down to the
+
 \subsection{Efficiency and Effectiveness B}
@@
 
+\begin{table}
+	\centering
+	\begin{tabular}[Ht]{| l | l | l | l | l | l | l |}
+	\hline
+	 & A Faults & B Faults & C Faults & Mean & Median & Detection Rate\\
+	\hline
+	UC & 36 & 40 & 35 & 4.615384615 & 3.5 & 0.12 \\
+	\hline
+	CL & 31 & 47 & 28 & 5.48 & 5 & 0.14 \\
+	\hline
+	\end{tabular}
+	\caption{Results Summary}
+\end{table}
+
+The results of the experiment appear to suggest that a check-list(CL) based review technique is more effective than a use-case(UC) based review technique.
+Given that the null hypothesis H\textsubscript{Eff} was rejected, it is a fair assumption to make.
+UC appears to find many more class A faults than CL, however, CL finds more class B faults and UC finds more class C faults.
+However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC.
+The slight variation in favour of the CL technique is further evidence that CL is more efficient and therefore more effective than UC.
+
 \bibliographystyle{latex8}

### 2015-03-10 rmtw/a4/latex8.tex
dsaf

@@
 \usepackage{enumitem}
+\usepackage{amsmath}
+\usepackage{mathtools}
 %\documentstyle[times,art10,twocolumn,latex8]{article}
@@
 includes changes to the inspection process, e.g. \cite{bisant1989two}, support to
-the proceThe dependent variables are analyzed to evaluate the
-hypotheses of the experiment. The main null and alternative
-hypotheses \cite{montgomery2008design} are stated below. These are evaluated for all
-faults, class A faults and class A\&B faults. The hypotheses
-concern efficiency, effectiveness and fault detecting
-differences:ss, e.g. \cite{basili1996empirical} and empirical studies, e.g. \cite{basili1999building}. The
+the process, e.g. \cite{basili1996empirical} and empirical studies, e.g. \cite{basili1999building}. The
 suggested improvements include active design reviews \cite{parnas1985active} and
@@
 	the reading technique used. The experiment groups used either
-	Use-Cased Based Reading or Checklist-Based Reding.
-	\item Controlled Variable: The controll variable is the
-	experience of the reviwers and it is measured on an ordinal
-	scale. The reviwers were asked to fill in a questionnare
+	Use-Cased Based Reading or Checklist-Based Reading.
+	\item Controlled Variable: The controlled variable is the
+	experience of the reviewers and it is measured on an ordinal
+	scale. The reviewers were asked to fill in a questionnaire
 	comprising seven questions.
-	\item Dependent Variables: The dependent varialbles
+	\item Dependent Variables: The dependent variables
 	measured are faults. The four variables are: (1) Number of
-	faults found by each reviwer, (2) Number of faults found by
+	faults found by each reviewer, (2) Number of faults found by
 	each experiment group, (3) efficiency (faults/hour) and is
 	measured as: 60*(number of fault found/inspection time which
-	is 45 min), and (4) effectivness (detection rate) and is mesured
+	is 45 min), and (4) effectiveness (detection rate) and is measured
 	as: number of faults found/total number of faults.
@@
 \subsection{Research Questions}
+\begin{itemize}
+\item RQ1 - Is there a difference in effectiveness between Use-Case Based Reading and Checklist-Based Reading?
+\item RQ2 - Is there a difference in efficiency between Use-Case Based Reading and Checklist-Based Reading?
+\item RQ3 - Are different faults found by inspectors using Use-Case Based Reading than faults found by inspectors using Checklist-Based Reading? 
+\end{itemize}
 
@@
 larger rate of the critical faults.
-The dependent variables are analyzed to evaluate the
+The dependent variables are analysed to evaluate the
 hypotheses of the experiment. The main null and alternative
@@
 \item H\textsubscript{0 Eff} - There is no difference in efficiency (i.e.found faults per hour) between the reviewers applying use cases and the reviewers using a checklist.
-\item H\textsubscript{1 Eff} - There is a difference in efficiency between the reviewers applying prioritized use cases and the reviewers using a checklist.
+\item H\textsubscript{1 Eff} - There is a difference in efficiency between the reviewers applying prioritised use cases and the reviewers using a checklist.
 \item H\textsubscript{0 Rate} - There is no difference in effectiveness (i.e. rate of faults found) between the reviewers applying use cases and the reviewers using a checklist.
@@
 No data points were removed from the data set before performing any tests for H\textsubscript{Eff} or H\textsubscript{Rate}.
-The reasoning for this was that the hypotheses only concern number of occurances and not the qualitative attributes of the data.
+The reasoning for this was that the hypotheses only concern number of occurrences and not the qualitative attributes of the data.
 This means that data points which, for example, contained ``incorrect'' \textit{Item numbers} were still used in the calculation.
@@
 An example of this is found in table 3.
-In order to determine if they do find the same faults, a Chi-Square test of independence was performed on the tabulated results.
-The reason the Chi-Square test of independence was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5.
+In order to determine if they do find the same faults, a Chi-Square (CS) test of independence was performed on the tabulated results.
+The reason the CS was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5.
 Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows.
@@
 \subsection{Results for H\textsubscript{Fault}}
-As mentioned previously, the Chi-Square test of independence was used to determine if the reviewers discovered the same frequency of results.
+As mentioned previously, the CS test was used to determine if the reviewers discovered the same frequency of results.
 The result of the X\textsubscript{2} was 1.5998, generating a p-value of 0.4494.
-Thus, the null hypothesis H\textsubscript{0} Fault is rejected.
-
-data:  data.table
-X-squared = 1.5998, df = 2, p-value = 0.4494
+For v=2 and alpha = 0.05, the upper critical value is 5.991 and the lower critical value is 0.103.
+Since 1.5998 is \textless 5.991 and \textgreater 0.103, the alternative hypothesis of the CS test is rejected.
+Since \textsubscript{0 Fault} and \textsubscript{1 Fault} are inverted compared to the hypothesis of the CS test, the null hypothesis of H\textsubscript{Fault} is rejected.
 

### 2015-03-10 rmtw/a4/latex8.tex
plz don't finish my scentence

@@
 \SubSection{Test Used for H\textsubscript{Fault}}
-The frequency of A, B and C faults found were tabularised against the groups which found them.
+The frequency of A, B and C faults found were tabulated against the inspection groups which found them.
 Any response that was not not applicable (NA) was discarded from the table.
@@
 
-The results of the study show some interesting results.
-The rejection of \textsubscript{0} Eff indicates that there is a difference between the efficiency of the inspection methods.
-This difference could be down to the
+The results of the study show some interesting results. The rejection of \textsubscript{0} Eff indicates that there is a difference between the efficiency of the inspection methods.
 
@@
 
+When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults.
+However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC.
+This, coupled with the rejection of the H\texsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding.
+A suggestion for a follow up study would be to determine exactly  and why one inspection process finds them over the other.
+
 \begin{table}
@@
 	\hline
-	UC & 36 & 40 & 35 & 4.615384615 & 3.5 & 0.12 \\
+	UC & 36 & 40 & 35 & 4.61 & 3.5 & 0.12 \\
 	\hline
@@
 
-The results of the experiment appear to suggest that a check-list(CL) based review technique is more effective than a use-case(UC) based review technique.
-Given that the null hypothesis H\textsubscript{Eff} was rejected, it is a fair assumption to make.
-UC appears to find many more class A faults than CL, however, CL finds more class B faults and UC finds more class C faults.
-However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC.
 The slight variation in favour of the CL technique is further evidence that CL is more efficient and therefore more effective than UC.

### 2015-03-10 rmtw/a4/latex8.tex
Finished sections

@@
 However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC.
-This, coupled with the rejection of the H\texsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding.
-A suggestion for a follow up study would be to determine exactly  and why one inspection process finds them over the other.
+This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding.
+A suggestion for a follow up study would be to determine why CL and UC discover different tests.
 
@@
 
-The slight variation in favour of the CL technique is further evidence that CL is more efficient and therefore more effective than UC.
+Given that H\textsubscript{Eff}, H\textsubscript{Rate} and H\textsubscript{Fault} all reject their null hypothesise, we can assume that there is a noticeable difference between the two inspection methods.
 

### 2015-03-10 rmtw/a4/latex8.tex
learn to write messages john

--- 2015-03-10 rmtw/a4/latex8.tex
@@
 However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC.
-This, coupled with the rejection of the H\texsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding.
+This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding.
 A suggestion for a follow up study would be to determine exactly  and why one inspection process finds them over the other.
@@
 	\centering
-	\begin{tabular}[Ht]{| l | l | l | l | l | l | l |}
+	\begin{tabular}[Ht]{|l|l|l|}
 	\hline
-	 & A Faults & B Faults & C Faults & Mean & Median & Detection Rate\\
+	& UC & CL \\
 	\hline
-	UC & 36 & 40 & 35 & 4.61 & 3.5 & 0.12 \\
+	Mean(Total faults found) & 4.61 & 5.48 \\
 	\hline
-	CL & 31 & 47 & 28 & 5.48 & 5 & 0.14 \\
+	Median(Total faults found) & 3.5 & 5.0 \\
+	\hline
+	Detection Rate & 0.12 & 0.14 \\
+	\hline
+	A Faults & 36 & 31 \\
+	\hline
+	B Faults & 40 & 47 \\
+	\hline
+	C Faults & 35 & 20 \\
 	\hline

### 2015-03-10 rmtw/a4/latex8.tex
Willy commit
Added reasoning for Test3

@@
 \SubSection{Test Used for H\textsubscript{Fault}}
-The frequency of A, B and C faults found were tabulated against the inspection groups which found them.
+
+To determine if the inspection processes find different risks, we looked at the total frequency of the types of risks found.
+We decided to use the risk type of the fault as opposed to using the class of fault (Missing, Wrong) as the fault type had more categories to chose from (A,B,C).
+We chose not to use the section in which the data was located and the item number as the data were mostly incomplete or incorrect.
+
+The frequency of A, B and C risks found were tabulated against the inspection groups which found them.
 Any response that was not not applicable (NA) was discarded from the table.
 An example of this is found in table 3.
-In order to determine if they do find the same faults, a Chi-Square (CS) test of independence was performed on the tabulated results.
+In order to determine if they do find the same risks, a Chi-Square (CS) test of independence was performed on the tabulated results.
 The reason the CS was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5.

### 2015-03-10 rmtw/a4/latex8.tex
stdio

@@
 \Section{Methodology}
-This section will describe which statistical tests were used, and why. The level of significance used for all tests is 0.05.
+This section will describe which statistical tests were used, and why.
+The level of significance used for all tests is 0.05.
+The results have been analysed using a descriptive approach together with a statistical approach.
 
@@
 This section will cover the results of the experiment.
+The results for H\textsubscript{Eff} and H\textsubscript{Rate} are described in the same sub-sections, since the results are similar and since the results both are relative to the number of average faults found.
 
-\subsection{Efficiency and Effectiveness A}
+\subsection{Results for H\textsubscript{Eff} and H\textsubscript{Rate}}
 Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test.
 The data used for the WMW test was the efficiency of each participant.
-The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0} Eff is rejected.
+The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0 Eff} is rejected.
 
-The results of the study show some interesting results. The rejection of \textsubscript{0} Eff indicates that there is a difference between the efficiency of the inspection methods.
+The same test was chosen for H\textsubscript{Rate}, based on the same reasoning.
+The result of the WMW test for H\textsubscript{Rate} was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0 Rate} is rejected.
 
-\subsection{Efficiency and Effectiveness B}
-The same test was chosen for Hrate, based on the same reasoning.
-The result of the WMW test for Hrate was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0} Rate is rejected.
+As evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar.
+Both show that there is a difference between the two inspection methods, and both show greater results for CL.
+
+%% ctrl+F for "exactly  and why one inspection process"
 
@@
 As mentioned previously, the CS test was used to determine if the reviewers discovered the same frequency of results.
-The result of the X\textsubscript{2} was 1.5998, generating a p-value of 0.4494.
+The result of the X\textsuperscript{2} was 1.5998, generating a p-value of 0.4494.
 For v=2 and alpha = 0.05, the upper critical value is 5.991 and the lower critical value is 0.103.
@@
 	\centering
-	\begin{tabular}[Ht]{|l|l|l|}
+	\begin{tabular}[ht]{|l|l|l|}
 	\hline
@@
 	Detection Rate & 0.12 & 0.14 \\
-	\hline
-	A Faults & 36 & 31 \\
-	\hline
-	B Faults & 40 & 47 \\
-	\hline
-	C Faults & 35 & 20 \\
 	\hline

### 2015-03-10 rmtw/a4/latex8.tex
Updated changes

@@
 The reason the CS was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5.
-Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows.
-Fishers test should only be used for 2x2 tables.
+Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows and Fishers test should only be used for tables that are 2x2 in size.
 

### 2015-03-10 rmtw/a4/latex8.tex
asd
MAde some sense

@@
 	\centering
-	\begin{tabular}[ht]{| l | l | l | l |}
+	\begin{tabular}[ht]{| l | l | l | l | l |}
 	\hline
-	 & A Faults & B Faults & C Faults  \\
+	 & A Faults & B Faults & C Faults & Excluded\\
 	\hline
-	Group A & 36 & 40 & 35 \\
+	UC & 36 & 40 & 35 & 9\\
 	\hline
-	Group B & 31 & 47 & 28 \\
+	CL & 31 & 47 & 28 & 27\\
 	\hline
@@
 Both show that there is a difference between the two inspection methods, and both show greater results for CL.
-
-%% ctrl+F for "exactly  and why one inspection process"
+Table 3 shows that UC finds more faults of risk type A and C, but the fact that the CL data contained 18 more faults that contained an incorrect fault risk entry could be a possible explanation for that.
 
@@
 This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding.
-A suggestion for a follow up study would be to determine exactly  and why one inspection process finds them over the other.
+A suggestion for a follow up study would be to determine why one inspection process finds faults that the other does not and if this affects the effectiveness of that process.
 

### 2015-03-10 rmtw/a4/latex8.tex
Added Title
sad

@@
 
-\title{Assignment 4}
+\title{A Comparison of Use-Case Based and Checklist-
+Based Reading: A Controlled Experiment}
 
@@
 
-\Section{Acknowledgements}
-U w0T m8
+\Section{Acknowledgement}
+John had the main responsibility for sections 3.2, 4.2.
+William had the main responsibility for sections 3.1, 4.1.
+The research questions were written together.
+We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John.
+The testing has been done using a ``pair-testing'' approach.
+
+Note: We were a bit unsure whether to only analyse the tests with help of the p-value or analysing the p-value together with test result and critical-value was the correct.
+We decided to do the latter and would like feedback on this.
 

### 2015-03-12 rmtw/a3/latex8.tex
dsaf

--- 2015-02-17 rmtw/a3/latex8.tex
@@
 
-\overfullrule=2cm
-
 \title{Implementing Change in Multi-paradigm Environments, a Case Study}
@@
 For example, we would consider Model Driven Software Development to be a development paradigm.
-In this study we use the term manual coding to describe development without the use of any particular paradigm.
+In this study we use the term manual coding to describe traditional development where no modeling techniques are used to produce code, i.e.
+the code is ``hand-written''.
 The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process.
@@
 
-\Section{Methodology}
-
-\SubSection{Case Company Description}
+\Section{Case Company Description}
 The subject case organisation in this study is Ericsson AB.
@@
 
-The company was sampled through convenience sampling, and a maximum variation strategy was used.
+Ericsson has in the last 10 years gone through major changes which relate to way of working, processes, and technical activities and tools.
+The most major change, which is still ongoing, is the change towards implementing MDSD.
+Since EPG are still in the process of changing to MDSD, they are now developing their product using two different development paradigms (manual coding and MDSD).
+
+The company and department was sampled through convenience sampling, and a maximum variation strategy was used.
 As such, the goal was to include as many companies as possible in this study.
 Since the study is conducted at a large communications technology company, it indicates that the study may be generalisable to similar companies.
+
+\Section{Methodology}
+This section will describe the methodology used for the study.
 
@@
 The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study.
-The research has been conducted using a case study approach.
+
+The methodology used has been case study.
 The reason for this is that the goal of our study is to analyse how changes are implemented in the context of multi-paradigm development environments in software engineering.
@@
 The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage.
+The case study protocol \cite{brereton2008using} developed and used during this phase can be seen in Table 1.
+The protocol can be viewed as a high-level timeline for our study.
+
+\begin{table}
+	\centering
+	\begin{tabular}[Ht]{|l|p{3cm}|p{3.5cm}|}
+	\hline
+	\textbf{Phase} & \textbf{Activity} & \textbf{Description} \\
+	\hline
+	1 & Background & Identify related work and research questions \\
+	\hline
+	2 & Case Study Design & Design the case study, identify object of the study \\
+	\hline
+	3 & Case Selection & Define criteria for case selection \\
+	\hline
+	4 & Roles and Responsibilites & Plan and decide roles and responsibilites for researchers \\
+	\hline
+	5 & Data Collection & Design the data collection phase \\
+	\hline
+	6 & Data Analyis & Design the data analysis phase \\
+	\hline
+	7 & Validity & Design plan for how to reduce validity threats \\
+	\hline
+	8 & Remaining Validity & Identify remaining threats to validity \\
+	\hline
+	9 & Design Reporting & Identify target audience \\
+	\hline
+	10 & Schedule & Design a schedule and estimate time for each phase \\
+	\hline
+
+	\hline
+	\end{tabular}
+	\caption{Case Study Protocol}
+\end{table}
 
@@
 The interviewees were sampled using random sampling, with help of a gatekeeper at the company.
-The reason a gatekeeper was used was to reduce research bias but does eliminate it.
-Random sampling was performed on official employee records.
+The reason a gatekeeper was used was to reduce research bias.
+Random sampling was performed on official EPG employee records.
+Before the records were sampled, the gatekeeper excluded employees which have worked less than 5 years at Ericsson.
+5 years experience was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson.
 15 employees were chosen to be the subjects for the interviews.
 The subjects were divided into three sub-groups; managers, developers and change agents with 5 of each role being interviewed.
-The main reason the three different roles were included was to be able to reduce research bias through data triangulation.
-
-The interviewees were selected based on two criterion: they must have been employed at Ericsson for a minimum of 5 years and they must work at the EPG department.
-5 years experience was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson.
-The reason only employees from EPG were accepted was to ensure that the population was cohesive.
+The main reason the three different roles were included was to be able to reduce bias correlating with roles.
+The implemented changes might also have different effects on different roles, and thus might provide valuable insight to the study.
 
@@
 This was performed so that meaningful comparison and analysis could be carried out.
-Data triangulation was performed to compare and verify the results based on which role the interviewee had.
+The data was analysed based on which role the interviewee had.
 The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes.
@@
 \SubSection{Data Analysis}
-Data analysis of the interviews was completed in tandem with the data gathering phase.
+Data analysis of the interviews was initially carried out in tandem with the data gathering phase.
 This was performed so that we could iteratively improve upon the data collection process.
@@
 
-\Section{Threats to Validity}
-
+\SubSection{Threats to Validity}
 While designing the study, validity concerns were taken into consideration.
@@
 The fact that the study only occurred in a subset of Ericsson and not a larger part of the company means that we cannot reliably make any generalities about the results.
-This is something that could be overcome during a potential triangulation period.
 For example, further studies could be conducted within Ericsson at other departments which could then be used to strengthen or diminish the results from this study.
@@
 \begin{itemize}
-\item Do you feel that the changes in Ericsson have had a clear plan?
+\item How do you think the goals for the changes are defined?
 \item How have the goals of the changes been communicated? 
@@
 \item Do you feel that anything has changed in the change strategy since MDSD was introduced? 
+\item Do you think changes have been more effective after MDSD was introduced? 
+\item How do you think MDSD has affected ongoing changes?
+\item How do you think change should be designed in multi-paradigm environments?
+\item Which changes do you feel should only be adopted in MDSD/manual coding teams?
+\item Which changes do you feel should be adopted for both MDSD and manual coding teams?
 \end{itemize}

### 2015-03-12 rmtw/a4/latex8.tex
dsaf

@@
 \Section{Methodology}
-This section will describe which statistical tests were used, and why.
-The level of significance used for all tests is 0.05.
+This section will describe which statistical tests were used, and why they were chosen.
+The level of significance ($\alpha$) used for all tests is 0.05.
 The results have been analysed using a descriptive approach together with a statistical approach.
@@
 No data points were removed from the data set before performing any tests for H\textsubscript{Eff} or H\textsubscript{Rate}.
-The reasoning for this was that the hypotheses only concern number of occurrences and not the qualitative attributes of the data.
-This means that data points which, for example, contained ``incorrect'' \textit{Item numbers} were still used in the calculation.
+The reasoning for this was that the hypotheses only concerned with the number of occurrences and not the qualitative attributes of the data.
+This means that data points which, for example, with ``incorrect'' \textit{Positions} were still used in the calculation.
 
@@
 
-The next step was to perform an outlier test. The method used was boxplots. As seen in Figure 3 and 4, no outliers were detected and thus no data points were removed in the tests performed.
+The next step was to perform an outlier test.
+To identify these, boxplots were generated and reviewed.
+As seen in Figure 3 and 4, no outliers were detected and thus no data points were removed in the subsequent tests.
 
@@
 To determine if the inspection processes find different risks, we looked at the total frequency of the types of risks found.
-We decided to use the risk type of the fault as opposed to using the class of fault (Missing, Wrong) as the fault type had more categories to chose from (A,B,C).
-We chose not to use the section in which the data was located and the item number as the data were mostly incomplete or incorrect.
+We decided to use the risk type of the fault as opposed to using the class of fault (Missing, Wrong) as the fault type had more categories to choose from (A,B,C).
+We chose not to use \textit{Position} as the data were mostly incomplete or incorrect.
 
 The frequency of A, B and C risks found were tabulated against the inspection groups which found them.
-Any response that was not not applicable (NA) was discarded from the table.
-An example of this is found in table 3.
+Any response that was not applicable (NA) was discarded from the table.
+An example of this is found in Table 3.
 In order to determine if they do find the same risks, a Chi-Square (CS) test of independence was performed on the tabulated results.
-The reason the CS was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5.
-Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows and Fishers test should only be used for tables that are 2x2 in size.
+The reason the CS test was used was primarily because the risk data were categorical and the frequency of each category was at least 5.
+Other tests, such as Fishers Exact Test were not applicable, for example, as our table was greater than 2x2 rows and Fishers test should only be used for tables that are 2x2 in size.
 
@@
 This section will cover the results of the experiment.
-The results for H\textsubscript{Eff} and H\textsubscript{Rate} are described in the same sub-sections, since the results are similar and since the results both are relative to the number of average faults found.
+The results for H\textsubscript{Eff} and H\textsubscript{Rate} are described in the same sub-section, since the results are similar and since the results both hypotheses are relative to the number of average faults found.
 
 \subsection{Results for H\textsubscript{Eff} and H\textsubscript{Rate}}
-Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test.
+Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was performed instead of the Student's T-test as the test for H\textsubscript{Eff}.
 The data used for the WMW test was the efficiency of each participant.
-The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0 Eff} is rejected.
+The result of the WMW test was p=0.1063 and thus the alternative hypothesis, H\textsubscript{1 Eff}, is rejected.
 
-The same test was chosen for H\textsubscript{Rate}, based on the same reasoning.
-The result of the WMW test for H\textsubscript{Rate} was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0 Rate} is rejected.
+The same test was chosen for H\textsubscript{Rate}, based on the same reasoning. The result of the WMW test for H\textsubscript{Rate} was p=0.1063 and thus H\textsubscript{1 Rate} is rejected.
 
 As evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar.
-Both show that there is a difference between the two inspection methods, and both show greater results for CL.
-Table 3 shows that UC finds more faults of risk type A and C, but the fact that the CL data contained 18 more faults that contained an incorrect fault risk entry could be a possible explanation for that.
+Both show that there is a slight difference between the two inspection methods, and there is a slight better result for CL.
+The results are, however, not statistically significant enough for the null hypotheses to be rejected.
+Table 3 shows that UC finds more faults of risk type A and C, but the fact that the CL data contained 18 more faults that contained an incorrect fault risk entry is be a possible explanation for this result.
 
@@
 As mentioned previously, the CS test was used to determine if the reviewers discovered the same frequency of results.
-The result of the X\textsuperscript{2} was 1.5998, generating a p-value of 0.4494.
-For v=2 and alpha = 0.05, the upper critical value is 5.991 and the lower critical value is 0.103.
+The result of the $\chi $ \textsuperscript{2} was 1.5998, generating a p-value of 0.4494.
+For $\nu$=2 and $\alpha$=0.05, the upper critical value is 5.991 and the lower critical value is 0.103.
 Since 1.5998 is \textless 5.991 and \textgreater 0.103, the alternative hypothesis of the CS test is rejected.
-Since \textsubscript{0 Fault} and \textsubscript{1 Fault} are inverted compared to the hypothesis of the CS test, the null hypothesis of H\textsubscript{Fault} is rejected.
+Since H\textsubscript{0 Fault} and H\textsubscript{1 Fault} are inverted compared to the hypothesis of the CS test, the null hypothesis of H\textsubscript{Fault} is rejected.
 
-When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults.
+When looking at the results of the study, UC appears to find more class A and class B faults than CL, however, CL finds more class B faults.
 However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC.
 This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding.
-A suggestion for a follow up study would be to determine why one inspection process finds faults that the other does not and if this affects the effectiveness of that process.
 
@@
 	\hline
-	Mean(Total faults found) & 4.61 & 5.48 \\
+	Mean(Total faults found) & 4.62 & 5.48 \\
 	\hline
@@
 \end{table}
-
-The slight variation in favour of the CL technique is further evidence that CL is more efficient and therefore more effective than UC.
 
@@
 The testing has been done using a ``pair-testing'' approach.
+\newline
 
-Note: We were a bit unsure whether to only analyse the tests with help of the p-value or analysing the p-value together with test result and critical-value was the correct.
+\noindent
+\textbf{Notes:}
+\begin{itemize}
+\item We were a bit unsure whether to only analyse the tests with help of the p-value or analysing the p-value together with test result and critical-value was correct.
 We decided to do the latter and would like feedback on this.
+\item We ended up creating our own research questions based on the alternative hypotheses, since they were not included in Experiment\_Design.pdf. Hopefully this is what you were looking for.
+\end{itemize}
 

### 2015-03-12 rmtw/a4/stat/first.R

@@ -1,12 +1,15 @@
 uc_eff <- c(1.3, 8.0, 2.7, 2.7, 6.7, 9.3, 2.7, 5.3, 2.7, 16.0, 4.0, 
           2.7, 4.0, 14.7, 5.3, 6.7, 4.0, 2.7, 4.0, 13.3, 2.7, 6.7, 
           13.3, 5.3, 2.7, 10.7)
+
 cl_eff <- c(2.7, 1.3, 10.7, 13.3, 8.0, 10.7, 8.0, 13.3, 9.3, 8.0, 
             9.3, 8.0, 4.0, 10.7, 6.7, 6.7, 5.3, 5.3, 4.0, 5.3, 
             2.7, 5.3, 5.3, 5.3, 13.3, 7.3)
+
 uc_rate <- c(0.03, 0.16, 0.05, 0.05, 0.13, 0.18, 0.05, 0.11, 0.05, 
              0.32, 0.08, 0.05, 0.08, 0.29, 0.11, 0.13, 0.08, 0.05, 
              0.08, 0.26, 0.05, 0.13, 0.26, 0.11, 0.05, 0.21)
+
 cl_rate <- c(0.05, 0.03, 0.21, 0.26, 0.16, 0.21, 0.16, 0.26, 0.18,
              0.16, 0.18, 0.16, 0.08, 0.21, 0.13, 0.13, 0.11, 0.11, 
              0.08, 0.11, 0.05, 0.11, 0.11, 0.11, 0.26, 0.1448)
@@ -15,7 +18,7 @@ cl_rate <- c(0.05, 0.03, 0.21, 0.26, 0.16, 0.21, 0.16, 0.26, 0.18,
 UC = c(1, 6, 2, 2, 5, 7, 2, 4, 2, 12, 3, 2, 3, 11, 4, 5, 3, 2, 3, 10, 2, 5, 10, 4, 2, 8)
 CL = c(2, 1, 8, 10, 6, 8, 6, 10, 7, 6, 7, 6, 3, 8, 5, 5, 4, 4, 3, 4, 2, 4, 4, 4, 10, 5.48)
 m = mean(CL)
-
+m2 =mean(UC)
 
 
 

### 2015-03-16 rmtw/a1/assignment_1.tex
Added group 9 review for assignment 5

@@
 As in all research there are threats to the validity of the study being undertaken.
-Our largest threat would be the external validity of the data collected.
+The comparison of the perceived readability of programming languages cannot be fully determined from a single study, as such, more are required to make more concrete generalisations.
+Given this, the threats to internal and construct validity are among the most important for this study.
+The most import however would be the external validity of the study.
+
 The students were selected from the three current years studying at the University of Gothenburg.

### 2015-03-16 rmtw/a5_review/latex8.tex
Added group 9 review for assignment 5

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: John Burchell & William Granli $
%  $Date: 2015/01/21 15:20:59 $
%  $Revision: 1.0
%

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{times}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{Review of Group 9 by Group 1}

% author names and affiliations
\author{John Burchell and William Granli \\
john.a.burchell@gmail.com, william.granli@gmail.com}

\maketitle
\thispagestyle{empty}

%-------------------------------------------------------------------------

\Section{Introduction}

Most of the way into the introduction and I don't know what the paper is really about, other than it's related to MDD. Maybe you should consider splitting the introduction upon into smaller sections, such as having a general introduction to the problem, a problem statement and then some related work to show why this is a problem?

Good paragraph with Orlikowski \& Gash, well referenced and backed up with another good paper.

\Section{Purpose of the Study}
As mentioned before, this should probably be mentioned a little earlier than here. Some of the wording could be improved here, it's a little repetitive.

Again, the structure is something that I would consider changing here, the research questions should be separated from the text, they should be very easy to locate and to find, maybe put them in a list? Also, your question doesn't even have a question mark at the end.

I would suggest moving most of the text out of this section and into others. For example, I would move the supporting comments and reasons before you state the actual research questions. This applies to the sub questions also.

\Section{Methodology}

The first time that you mention the research strategy is in the methodology itself, while I know that the assignment was an SLR, it's probably a good idea to mention it before the methodology in passing, for example in the problem statement.

Good arguments and explanation of the SLR, however, it might flow better to start with explaining the SLR, explaining why it was picked and then the validity threats, on that note validity threats should be their own section.

\Section {Database and search keywords}

It might be a little more prudent to have a nice list of the words used and to put it into the appendix rather than having it in the middle of the papers text. Also for the amount of papers found, it would look and read much more easily if they were tabulated, i.e. you have each database used with the amount of papers found.

Little inconsistency with the search term, was it ``Benefits'' or benefits?

\Section {Inclusion Exclusion Criteria}

The criteria were good but it's a bit difficult to read when it's all put into a single block. This section could do with some more substance, for example, are you including only positive papers? Are you excluding negative papers? If including the positive, how are you going to alleviate the research bias that this brings with it?

\Section {Data Extraction}

The data extraction section is ok overall, however the mentioning of the pen and paper tools feels a little strange. Also, you mention drawbacks and benefits of these tools and that they should be taken into consideration. What are the drawbacks and benefits of the tools you picked?

Furthermore, is each reviewer going to review each paper twice, or once? You should probably include this and why for either reason decided. The section detailing the forms is good, if you have time it might be nice to see an example of the form that you might use.

\Section {Data Synthesis}
I'm not sure what you intended this section to show or do, but all I understood is that you stored the data. What did you actually do to synthesise the data? How was it combined? It needs much more information.

\Section {Quality Assessment}
Good points about the criteria and quality, but what about other kinds of threats? Other validity threats?

\end{document}

### 2015-03-16 rmtw/a4_review/latex8.tex
Added review for 4 and finished review for 5

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: John Burchell & William Granli $
%  $Date: 2015/01/21 15:20:59 $
%  $Revision: 1.0
%

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{url}
\usepackage{tabularx}
\usepackage{appendix}
\usepackage{pbox}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{Review of Group 9 by Group 1}

% author names and affiliations
\author{John Burchell and William Granli \\
john.a.burchell@gmail.com, william.granli@gmail.com}

\maketitle
\thispagestyle{empty}

%-------------------------------------------------------------------------

\Section{Introduction}
The text for Section I and II are good, and fit the purpose of the sections. We chose to copy and paste the same part from Richard's pdf. The formatting of the sections could be improved, however. The overall structure of the paper is good, but it has some minor issues.

\section{Tests}
It is not clear how you performed the normality tests or which tests you used. Our tests showed that the sampling was non-normal, so I suggest that you with suitable tests try it again. It is hard to comment on or give more feedback on this since your approach was is not transparent from the paper. Possible tests you could use to determine the normality are Kolmogorov-Smirnov or Shapiro-Wilks. You could also plot the data using density plots or QQ-plots to visualise the normality of the data. We also suggest that you check the data for outliers, and explain what you chose to do with possible outliers.

If you perform the normality tests again, and get a different result; you should probably consider using another test, since the t-test is not appropriate for non-normal data. We also could not find information on which test was used for the third hypothesis.

We also suggest that you calculate the p-values for each test to be able to determine if your results are statistically significant. Doing this (and all statistical testing) by hand, is quite tedious - so we suggest that you use a language like R to perform the tests.

Based on what we have seen in other papers which analyse the data using a statistical approach, we also suggest that you leave out the calculations (in Appendix). If other researchers want to cross-check your results, they probably would not look at your calculations, but perform the tests again and compare the results.

\section{Writing and Structure}​​
​​The two first paragraphs of Section III don't really apply to this study. It seems to be more of a general explanation of why and when one should perform a statistical analysis.

Most of what is discussed in Section IV should probably be put in Section III. The 3 first paragraphs explain how the tests were performed, and is related to the Methodology and not the Results. Only the last paragraph relates to the actual results of the tests.

In general, it seems that you do not back your statements and explain why you choose to do something. Try to make it clear what the reasoning is behind each decision, especially in the Methodology section.

You also did not make any attempt at rejecting any hypothesis, which should be the main goal of an experiment.

\end{document}

### 2015-03-16 rmtw/a5_review/latex8.tex
Added review for 4 and finished review for 5

@@
 \usepackage{latex8}
-\usepackage{times}
+\usepackage{url}
+\usepackage{tabularx}
+\usepackage{appendix}
+\usepackage{pbox}
 
@@
 
-%-------------------------------------------------------------------------
-
 \Section{Introduction}
-
-Most of the way into the introduction and I don't know what the paper is really about, other than it's related to MDD.
+The introduction contains good information, however the structure is a little hard to read.
+For example, you don't mention the focus of the paper until the fourth paragraph.
 Maybe you should consider splitting the introduction upon into smaller sections, such as having a general introduction to the problem, a problem statement and then some related work to show why this is a problem?
@@
 Also, your question doesn't even have a question mark at the end.
-
 I would suggest moving most of the text out of this section and into others.
-For example, I would move the supporting comments and reasons before you state the actual research questions.
-This applies to the sub questions also.
 
 \Section{Methodology}
-
 The first time that you mention the research strategy is in the methodology itself, while I know that the assignment was an SLR, it's probably a good idea to mention it before the methodology in passing, for example in the problem statement.
@@
 \Section {Database and search keywords}
-
 It might be a little more prudent to have a nice list of the words used and to put it into the appendix rather than having it in the middle of the papers text.
@@
 
-Little inconsistency with the search term, was it ``Benefits'' or benefits?
-
 \Section {Inclusion Exclusion Criteria}
-
 The criteria were good but it's a bit difficult to read when it's all put into a single block.
@@
 \Section {Data Extraction}
-
-The data extraction section is ok overall, however the mentioning of the pen and paper tools feels a little strange.
-Also, you mention drawbacks and benefits of these tools and that they should be taken into consideration.
+The data extraction section is ok overall.
+You mention drawbacks and benefits of these tools and that they should be taken into consideration.
 What are the drawbacks and benefits of the tools you picked?
 
-Furthermore, is each reviewer going to review each paper twice, or once?
-You should probably include this and why for either reason decided.
-The section detailing the forms is good, if you have time it might be nice to see an example of the form that you might use.
+Furthermore, is each reviewer going to review each paper twice, or once? You should probably include this and why for either reason decided. The section detailing the forms is good and informative.
 

### 2015-03-17 rmtw/a6/latex8.tex
Added A6

--- 2015-03-10 rmtw/a4/latex8.tex
@@
 \usepackage{latex8}
-\usepackage{url}
-\usepackage{verbatim}
-\usepackage{fixltx2e}
-\usepackage{graphicx}
-\usepackage{enumitem}
-\usepackage{amsmath}
-\usepackage{mathtools}
 %\documentstyle[times,art10,twocolumn,latex8]{article}
@@
 \section{Introduction}
-Software inspections have since its inception \cite{fagan2002design} more than
-25 years ago spawned quite some interest both from the
-research community and industrial practice. The research
-includes changes to the inspection process, e.g. \cite{bisant1989two}, support to
-the process, e.g. \cite{basili1996empirical} and empirical studies, e.g. \cite{basili1999building}. The
-suggested improvements include active design reviews \cite{parnas1985active} and
-perspective-based reading \cite{shull2000perspective}. Industry has studied the
-benefits of conducting software inspections \cite{weller1993lessons}.
+Statement of the problem and why it	is important
 
-\section{Purpose of the Study}
-This section will describe the purpose of the study, the research questions and the hypotheses.
+\subsection*{Problem Statement}
+Include existing literature about the problem, 5-10 references required.
 
-\subsection{Purpose Statement}
-The objective of this study is to compare and hence
-evaluate how well the use-case based reading performs in
-comparison to other methods. The study presents a controlled
-experiment where use-case based reading is compared to
-checklist-based reading.
+\subsection*{Purpose Statement}
+Concise, clear
 
-\subsubsection{Variables}
-Three types of variables are defined for the experiment,
-independent, controlled, and dependent variables.
+\section{Company Case Description}
 
-\begin{enumerate}[label=(\alph*)]
-
-	\item Independent Variable: The independent variable is
-	the reading technique used. The experiment groups used either
-	Use-Cased Based Reading or Checklist-Based Reading.
-	\item Controlled Variable: The controlled variable is the
-	experience of the reviewers and it is measured on an ordinal
-	scale. The reviewers were asked to fill in a questionnaire
-	comprising seven questions.
-	\item Dependent Variables: The dependent variables
-	measured are faults. The four variables are: (1) Number of
-	faults found by each reviewer, (2) Number of faults found by
-	each experiment group, (3) efficiency (faults/hour) and is
-	measured as: 60*(number of fault found/inspection time which
-	is 45 min), and (4) effectiveness (detection rate) and is measured
-	as: number of faults found/total number of faults.
-
-\end{enumerate}
-
-\subsection{Research Questions}
-\begin{itemize}
-\item RQ1 - Is there a difference in effectiveness between Use-Case Based Reading and Checklist-Based Reading?
-\item RQ2 - Is there a difference in efficiency between Use-Case Based Reading and Checklist-Based Reading?
-\item RQ3 - Are different faults found by inspectors using Use-Case Based Reading than faults found by inspectors using Checklist-Based Reading? 
-\end{itemize}
-
-\subsection{Hypothesis}
-The general hypothesis of the experiment is that Use-Case
-Based Reading is more efficient and effective in finding faults
-of the most critical fault classes, i.e. Checklist-Based Reading
-is assumed to find more faults per time unit, and to find a
-larger rate of the critical faults.
-The dependent variables are analysed to evaluate the
-hypotheses of the experiment. The main null and alternative
-hypotheses \cite{montgomery2008design} are stated below. These are evaluated for all
-faults, class A faults and class A\&B faults. The hypotheses
-concern efficiency, effectiveness and fault detecting
-differences:
-
-\begin{itemize}
-\item H\textsubscript{0 Eff} - There is no difference in efficiency (i.e.found faults per hour) between the reviewers applying use cases and the reviewers using a checklist.
-\item H\textsubscript{1 Eff} - There is a difference in efficiency between the reviewers applying prioritised use cases and the reviewers using a checklist.
-\item H\textsubscript{0 Rate} - There is no difference in effectiveness (i.e. rate of faults found) between the reviewers applying use cases and the reviewers using a checklist.
-\item H\textsubscript{1 Rate} - There is a difference in effectiveness between the reviewers applying use cases and the reviewers using a checklist.
-\item H\textsubscript{0 Fault} - The reviewers applying use cases do not detect different faults than the reviewers using a checklist.
-\item H\textsubscript{1 Fault} - The reviewers applying use cases detect different faults than the reviewers using a checklist.
-
-\end{itemize}
-
-\Section{Methodology}
-This section will describe which statistical tests were used, and why.
-The level of significance used for all tests is 0.05.
-The results have been analysed using a descriptive approach together with a statistical approach.
-
-\SubSection{Tests Used for H\textsubscript{Eff} and H\textsubscript{Rate}}
-Initially, Kolmogorov-Smirnov (KS) Goodness-of-Fit and Shapiro-Wilks (SW) tests were used to determine if the assumption of normality could be held for the data set.
-The data used for the tests was the number faults found by each participant.
-The reason this data was chosen was that it directly correlates to the data used in H\textsubscript{Eff} and H\textsubscript{Rate}.
-No data points were removed from the data set before performing any tests for H\textsubscript{Eff} or H\textsubscript{Rate}.
-The reasoning for this was that the hypotheses only concern number of occurrences and not the qualitative attributes of the data.
-This means that data points which, for example, contained ``incorrect'' \textit{Item numbers} were still used in the calculation.
-
-The KS and SW tests both reported p-values \textless 0.05.
-See Table 1 for the p-values of the KS and SW tests.
-The critical value analysis for the KS and SW showed similar results and thus the null hypotheses of the data being normally distributed was rejected.
-See Table 2 for more information about the critical value results of the KS and SW tests.
-
-\begin{table}
-	\centering
-	\begin{tabular}[ht]{| l | l | l |}
-	\hline
-	Test & Sample & p-value  \\
-	\hline
-	KS & UC & \textless 2.2e-16 \\
-	\hline
-	SW & UC & 0.000969 \\
-	\hline
-	KS & CL & \textless 2.2e-16 \\
-	\hline
-	SW & CL & 0.309 \\	
-	\hline
-	\end{tabular}
-	\caption{KS \& SW tests - p-value}
-\end{table}
-
-\begin{table}
-	\centering
-	\begin{tabular}[ht]{| l | l | l | l |}
-	\hline
-	Test & Sample & Critical Value & D (result)  \\
-	\hline
-	KS & UC & 0.270 & 0.9388 \\
-	\hline
-	SW & UC & 0.964 &  0.8412 \\
-	\hline
-	KS & CL & 0.270 & 0.9388 \\
-	\hline
-	SW & CL & 0.964 & 0.9553 \\	
-	\hline
-	\end{tabular}
-	\caption{KS \& SW tests - Critical Value}
-\end{table}
-
-A graphical representation of the level of normalisation can be seen in Figure 1 and 2. The results from the tests are supported by the sparseness of the data points.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=90mm]{uc_qq.png}
-\caption{Use Case Q-Q plot}
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=90mm]{cl_qq.png}
-\caption{Checklist Q-Q plot}
-\end{figure}
-
-The next step was to perform an outlier test. The method used was boxplots. As seen in Figure 3 and 4, no outliers were detected and thus no data points were removed in the tests performed.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=90mm]{uc_box.png}
-\caption{Use Case Boxplot}
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=90mm]{cl_box.png}
-\caption{Checklist Boxplot}
-\end{figure}
-
-\SubSection{Test Used for H\textsubscript{Fault}}
-
-To determine if the inspection processes find different risks, we looked at the total frequency of the types of risks found.
-We decided to use the risk type of the fault as opposed to using the class of fault (Missing, Wrong) as the fault type had more categories to chose from (A,B,C).
-We chose not to use the section in which the data was located and the item number as the data were mostly incomplete or incorrect.
-
-The frequency of A, B and C risks found were tabulated against the inspection groups which found them.
-Any response that was not not applicable (NA) was discarded from the table.
-An example of this is found in table 3.
-In order to determine if they do find the same risks, a Chi-Square (CS) test of independence was performed on the tabulated results.
-The reason the CS was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5.
-Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows and Fishers test should only be used for tables that are 2x2 in size.
-
-\begin{table}
-	\centering
-	\begin{tabular}[ht]{| l | l | l | l | l |}
-	\hline
-	 & A Faults & B Faults & C Faults & Excluded\\
-	\hline
-	UC & 36 & 40 & 35 & 9\\
-	\hline
-	CL & 31 & 47 & 28 & 27\\
-	\hline
-	\end{tabular}
-	\caption{Fault frequency of risk type per group}
-\end{table}
-
-\Section{Results}
-This section will cover the results of the experiment.
-The results for H\textsubscript{Eff} and H\textsubscript{Rate} are described in the same sub-sections, since the results are similar and since the results both are relative to the number of average faults found.
-
-\subsection{Results for H\textsubscript{Eff} and H\textsubscript{Rate}}
-Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test.
-The data used for the WMW test was the efficiency of each participant.
-The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0 Eff} is rejected.
-
-The same test was chosen for H\textsubscript{Rate}, based on the same reasoning.
-The result of the WMW test for H\textsubscript{Rate} was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0 Rate} is rejected.
-
-As evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar.
-Both show that there is a difference between the two inspection methods, and both show greater results for CL.
-Table 3 shows that UC finds more faults of risk type A and C, but the fact that the CL data contained 18 more faults that contained an incorrect fault risk entry could be a possible explanation for that.
-
-\subsection{Results for H\textsubscript{Fault}}
-As mentioned previously, the CS test was used to determine if the reviewers discovered the same frequency of results.
-The result of the X\textsuperscript{2} was 1.5998, generating a p-value of 0.4494.
-For v=2 and alpha = 0.05, the upper critical value is 5.991 and the lower critical value is 0.103.
-Since 1.5998 is \textless 5.991 and \textgreater 0.103, the alternative hypothesis of the CS test is rejected.
-Since \textsubscript{0 Fault} and \textsubscript{1 Fault} are inverted compared to the hypothesis of the CS test, the null hypothesis of H\textsubscript{Fault} is rejected.
-
-When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults.
-However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC.
-This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding.
-A suggestion for a follow up study would be to determine why one inspection process finds faults that the other does not and if this affects the effectiveness of that process.
-
-\begin{table}
-	\centering
-	\begin{tabular}[ht]{|l|l|l|}
-	\hline
-	& UC & CL \\
-	\hline
-	Mean(Total faults found) & 4.61 & 5.48 \\
-	\hline
-	Median(Total faults found) & 3.5 & 5.0 \\
-	\hline
-	Detection Rate & 0.12 & 0.14 \\
-	\hline
-	\end{tabular}
-	\caption{Results Summary}
-\end{table}
-
-The slight variation in favour of the CL technique is further evidence that CL is more efficient and therefore more effective than UC.
+\section{Methodology}
+• State	your	research	question(s)	(and	hypothesis	if	applicable)
+• Describe	and	explain	the	research	strategy	and	investigation	methods that	will	be	used	for	the	project.	Motivate	your	choice?
+• Research	strategy	(research	methodology)
+• data	collection	procedures	(e.g.	interviews?	survey?	and	sampling?)	
+• method	for	analyzing	the	data	(grounded	theory?	Thematic	analysis?	
+Statistical	analysis?)	strategies	for	validating	findings
 
@@
 
-\Section{Acknowledgements}
-U w0T m8
+\Section{Acknowledgement}
 
+\noindent
 \end{document}

### 2015-03-17 rmtw/a6/latex8.tex
Pushed initial layout for a6

@@
 \section{Introduction}
-Statement of the problem and why it	is important
+%Literature intro
+%A bit unclear what to write here - check with Branson
 
-\subsection*{Problem Statement}
-Include existing literature about the problem, 5-10 references required.
+\subsection{Problem Statement}
 
-\subsection*{Purpose Statement}
-Concise, clear
+\subsection{Purpose Statement}
 
-\section{Company Case Description}
+\subsection{Research Questions}
+
+\section{Related Work}
+
+\subsection{API Design}
+
+\subsection{Software Evolution}
+
+\subsection{Architecture / Reverse Engineering (or tracing previously made decisions)}
+
+\section{Case Company Description}
+*Not sure if this should be a sub-heading somewhere
 
 \section{Methodology}
-• State	your	research	question(s)	(and	hypothesis	if	applicable)
-• Describe	and	explain	the	research	strategy	and	investigation	methods that	will	be	used	for	the	project.	Motivate	your	choice?
-• Research	strategy	(research	methodology)
-• data	collection	procedures	(e.g.	interviews?	survey?	and	sampling?)	
-• method	for	analyzing	the	data	(grounded	theory?	Thematic	analysis?	
-Statistical	analysis?)	strategies	for	validating	findings
+Brief intro, saying we will do a case study and what data collection methods will be used. (Also citing the paper from where we steal the case study process... höst).
+
+\subsection{Case Study Design}
+
+\subsection{Preparation for Data Collection}
+
+\subsection{Data Gathering}
+
+\subsection{Data Analysis}
+
+\subsection{Threats to Validity}
 

### 2015-03-17 rmtw/a1/assignment_1.tex
Updated assignment 1 based on feedback

@@
 %
-
-\documentclass[times, 10pt,twocolumn]{Article} 
+\documentclass[10pt,twocolumn]{article} 
 \usepackage{latex8}
@@
 Comparisons between programming languages are difficult to perform, due to inherent differences between languages, such as syntax.
-One aspect of code is its readability, which in turn is a determining factor of a piece of software's quality and maintainability \cite{aggarwal2002integrated, elshoff1982improving}.
+One aspect of code is its readability, which in turn is a determining factor of a piece of software's quality and maintainability \cite{aggarwal2002integrated},\cite{elshoff1982improving}.
 Buse \& Westley define readability as ``a property that influences how easily a given piece of code can be read and understood'' \cite{buse2010learning}.
@@
 This study could help some in industry to decide which languages should be used if maintainability is of high concern.
-Further studies could be conducted by to determine if there is a correlation between the popularity of projects and the readability of their languages.
+Further studies could be conducted to determine if there is a correlation between the popularity of projects and the readability of their languages.
 Furthermore, academia would be interested in which languages are more popular and those that have a higher readability, especially for novice developers.
@@
 
-The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages.
-With the aim of suggesting a metric which describes the readability of a given program, taking into account the inherent readability of the language in which it is written.
+The purpose of this survey study is therefore to discover how different levels of experience affect the perceived readability of code.
 
@@
 \begin{itemize}
-\item \textit{RQ1:} What are the inherent differences in perceived readability between programming languages?
+\item \textit{RQ1:} How do different programming languages differ in readability?
+\begin{itemize}
+\item \textit{SQ1:} How does readability correlate to popularity?
+\end{itemize}
+\item \textit{RQ2:} How differently do students of differing levels of experience rate code readability?
 \end{itemize}
@@
 The SE\&M program was chosen due to it being accessible for the researchers.
-More sophisticated sampling methods such as cluster-sampling or random sampling have not been used due to time-constraints.
 
@@
 Golang was picked as we wanted to see how students would perceive a language that is popular but has not really entered the academic landscape as of yet.
+The code snippets do not show which language they are written in.
+This was done to help eliminate bias towards known languages by their names.
 
@@
 Inexperienced students who have only seen Java may rate it as easily readable purely because they are only familiar with Java, this is why the relative level of experience is requested first in the survey, so that we might be able to pick up this potential bias during the results analysis.
-To help alleviate this issue, the questionnaire was distributed to all three year groups currently studying at SE\&M (2012,2013,2014).
+Complicated code snippets were therefore excluded as we were not specifically aiming for a ``Code reading'' exercise.
+The questionnaire was distributed to all three year groups currently studying at SE\&M (2012,2013,2014).
 
@@
     \textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
-    Experience & RQ1, SQ1 & 1 \\ \hline
-    Academic Year & RQ1, SQ1 & 2 \\ \hline
-    Preferred Language & RQ1, SQ2 & 3 \\ \hline
-    Least Preferred Language & RQ1, SQ2& 4 \\  \hline
-    Experience of Language & RQ1, SQ2 & 5 \\ 
+    Experience & RQ1 & 1 \\ \hline
+    Academic Year & RQ1 & 2 \\ \hline
+    Preferred Language & RQ1, SQ1 & 3 \\ \hline
+    Least Preferred Language & RQ1, SQ1 & 4 \\  \hline
+    Experience of Language & RQ1, SQ1 & 5 \\ 
     \hline
@@
 The comparison of the perceived readability of programming languages cannot be fully determined from a single study, as such, more are required to make more concrete generalisations.
-Given this, the threats to internal and construct validity are among the most important for this study.
-The most import however would be the external validity of the study.
+Given this, the threats to internal and construct validity are among the most important for this study with the most import being the external validity of the study.
 
-The students were selected from the three current years studying at the University of Gothenburg.
-Most of the respondents indicated that they are in the first year of their studies and as such their inexperience could be a limiting factor on their answers to the survey.
+Threats to \textit{external validity} include using students as participants, the size of the code snippets used in the survey and the distribution of the survey.
+Using students as participants is a threat mainly due to their experience levels.
+This threat is diminished as we are interesting in the disparity between the levels of experience, furthermore, the use of students in surveys is recommended by Höst, Regnell and Whohlin \cite{host2000using}.
+The size and complexity of the code snippets provided was minimised.
+The students have all had at least one course in Java and as such we felt that the simplicity of the code snippets used for the other languages would be appropriate.
+
+As mentioned previously, a pilot study was conducted among peers and students whom we supervise.
+The goal of this action was to identify and thereby reduce ambiguity in our questionnaire, thus limiting \textit{construction validity} threats.
+
+In regards to \textit{internal validity} threats, we had to cope with performing a convenience survey and random distribution of the surveys.
+The participants had little or no incentive to actually partake in the study and as such many most likely simply ignored it.
+One idea to improve the response rate for further surveys could be to form some incentive for the respondents.
+
+The questionnaire being distributed online via Facebook groups was another threat to the \textit{internal validity}.
+These groups are not officially controlled by the university and as such admission into these groups is up to the students who are organising them.
+This means that there is potential that some of the responses came from people not within the SE\&M institutions and this should be taken into consideration when analysing the results.
+One way to overcome this in future studies could be to use formal mailing lists, thus limiting the participants to only those students whom are enrolled at the university.
+
+A final \textit{internal validity} threat is that the students were selected from the three current years studying at the University of Gothenburg.
+Most of the respondents indicated that they are in the first year of their studies and as such their inexperience could be a limiting factor of their responses.
 The students may also have had a bias for one of the languages; Java.
@@
 This means that there is a lower chance they would be familiar with reading other language syntax other than Java and as such they would be more likely to see Java favourably than others.
-We cannot therefore generalise that Java has higher readability than that of the other languages despite what the results show.
-
-A further threat that we were unable to counteract adequately was the willing to participate of our respondents.
-The participants had little or no incentive to actually partake in the study and as such many most likely simply ignored it.
-This is to be expected when one attempts to undertakes a single stage sampling method.
-One idea to improve the response rate for further surveys could be to form some incentive for the respondents.
-
-The fact that the questionnaire was distributed online via Facebook groups also meant that there was another threat to the validity of the responses.
-These groups are not officially controlled by the university and as such admission into these groups is up to the students who are organising them.
-This means that there is potential that some of the responses came from people not within the SE\&M institutions and this should be taken into consideration when analysing the results.
-
-Other potential validity threats we must take into consideration are those that arise from the nature of survey.
-Since we are performing single stage data collection, the respondents of the surveys are answering our questions at their convenience.
-This opens the door for some validity threats, such as the willingness to participate.
-Our data are at the mercy of those willing to participate; we cannot anticipate how many will respond.
-There is little incentive for the respondents to partake in the survey other than for their own self interest.
+This is both an internal and external threat and in order to overcome it, we would most likely need to perform further studies.
 
@@
 \bibliography{assignment_1}
-
-\vfill
-\eject
 

### 2015-03-17 rmtw/a3/latex8.tex
hi john

@@
 \usepackage{url}
+\usepackage[toc,page]{appendix}
 
@@
 
-\title{Implementing Change in Multi-paradigm Environments, a Case Study}
+\title{Implementing Change in Multi-paradigm Environments: a Case Study}
 
@@
 
-\SubSection{Existing Literature}
+\SubSection{Related Work}
 According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI)\cite{pettersson2008practitioner}\cite{unterkalmsteiner2012evaluation} or change management (CM) strategies.
@@
 Due to the exploratory nature of the study, a flexible process design has been used.
-The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study.
+The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data have been the main driver for shaping and improving the scope and goal of the study.
 
@@
 The reason for this is that the goal of our study is to analyse how changes are implemented in the context of multi-paradigm development environments in software engineering.
-This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}.
-Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}.
+This line of thought is supported by Runesson \& H\"{o}st in \cite{runeson2009guidelines}.
+Runesson \& H\"{o}st also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}.
 Another reason for conducting this study using a case study approach is that there is little existing research conducted in the area, and that input from industry is vital to the success of the research.
@@
 Most of the planning was related to communicating with Ericsson to facilitate the interviews.
-A time-line for the interviews was created and established with Ericsson.
 The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage.
-The case study protocol \cite{brereton2008using} developed and used during this phase can be seen in Table 1.
-The protocol can be viewed as a high-level timeline for our study.
+
+A case study protocol \cite{brereton2008using} was developed and used as a formal plan for the study.
+The main reasons for using a case study protocol were to have a solid plan that is reviewable by other researchers, and to make sure that all researchers had a common strategy for conducting the study.
+The case study protocol served as a plan for the whole duration of the research.
+A list of which areas were planned and described in the case study protocl can be seen in Table 1.
 
@@
 	\centering
-	\begin{tabular}[Ht]{|l|p{3cm}|p{3.5cm}|}
+	\begin{tabular}[Ht]{|c|l|}
 	\hline
-	\textbf{Phase} & \textbf{Activity} & \textbf{Description} \\
+	\textbf{Phase} & \textbf{Activity}\\
 	\hline
-	1 & Background & Identify related work and research questions \\
+	1 & Background 1\\
 	\hline
-	2 & Case Study Design & Design the case study, identify object of the study \\
+	2 & Case Study Design \\
 	\hline
-	3 & Case Selection & Define criteria for case selection \\
+	3 & Case Selection \\
 	\hline
-	4 & Roles and Responsibilites & Plan and decide roles and responsibilites for researchers \\
+	4 & Roles and Responsibilites \\
 	\hline
-	5 & Data Collection & Design the data collection phase \\
+	5 & Data Collection \\
 	\hline
-	6 & Data Analyis & Design the data analysis phase \\
+	6 & Data Analyis \\
 	\hline
-	7 & Validity & Design plan for how to reduce validity threats \\
+	7 & Validity Design \\
 	\hline
-	8 & Remaining Validity & Identify remaining threats to validity \\
+	8 & Remaining Validity \\
 	\hline
-	9 & Design Reporting & Identify target audience \\
+	9 & Reporting Design \\
 	\hline
-	10 & Schedule & Design a schedule and estimate time for each phase \\
+	10 & Schedule \\
 	\hline
 
-	\hline
 	\end{tabular}
@@
 \newpage
-\appendix
+\begin{appendices}
 
@@
 
+\end{appendices}
+
 \end{document}

### 2015-03-17 rmtw/a6/latex8.tex
hi john

@@
 %A bit unclear what to write here - check with Branson
+Explain what APIs are. 
+Explain how and that APIs change. (Link it to the software evolution in a nice way).
 
 \subsection{Problem Statement}
+1.
 
-\subsection{Purpose Statement}
+\subsection{Purpose of the Study}
+Academia: 
+The results of what *actually* (i.e. our study) affects APIs could be compared to what literature says should affect design (i.e. best practices).
+
+Industry: 
+If a company can study their API's evolution and be able to track changes and design decisions, it can give them more knowledge to further improve and develop their API.
+
+If companies can identify changes, they can also identify what *was* bad.
+
+Changing APIs is usually not a good thing. If you can identify what changes APIs you can spend more time on that in development to avoid too much change in the future.
 
 \subsection{Research Questions}
+RQ1: What drives API evolution? 
+SRQ1: To what extent can we reverse engineer API change decisions?
+SRQ2:
 
@@
 \section{Case Company Description}
-*Not sure if this should be a sub-heading somewhere
 

### 2015-03-18 rmtw/a4_review/latex8.tex
Made some small changes to a4 review

@@
 
-\Section{Introduction}
-The text for Section I and II are good, and fit the purpose of the sections.
-We chose to copy and paste the same part from Richard's pdf.
-The formatting of the sections could be improved, however.
-The overall structure of the paper is good, but it has some minor issues.
-
 \section{Tests}
@@
 \section{Writing and Structure}​​
+The title of the paper should probably be copied from Richard's Experiment\_Design.pdf.
+The text for Section I and II are good, and fit the purpose of the sections.
+We chose to copy the same part from Richard's pdf.
+The formatting of the sections could be improved, however.
+The overall structure of the paper is good, but it has some minor issues.
+
 ​​The two first paragraphs of Section III don't really apply to this study. It seems to be more of a general explanation of why and when one should perform a statistical analysis.
@@
 
+There are quite a few grammatical errors in the text, so you should probably read through it again and think of where you can improve the phrasing. We found no spelling errors.
+
 \end{document}

### 2015-03-18 rmtw/a6/latex8.tex
Added purpose + notes to A6

--- 2015-03-17 rmtw/a6/latex8.tex
@@
 \section{Introduction}
-%Literature intro
-%A bit unclear what to write here - check with Branson
+
+\subsection{Introduction to Topics}
+
+\subsubsection{API Design}
+Explain what APIs are. 
+Explain how and that APIs change.
+
+\subsubsection{Software Evolution}
+Introduce software evolution. 
+Link this paragraph nicely to the previous one.
 
 \subsection{Problem Statement}
+Talk about how changing APIs is costly and how it might be hard to avoid changes since a lot of how good an API is depends on the user of the API.
+(Maybe even a reference to someone saying that user testing is expensive).
 
-\subsection{Purpose Statement}
+\subsection{Gap in the Literature}
+API change + software evolution.
+
+\subsection{Purpose of the Study}
+The purpose of the study is to find the motives behind modifications of APIs.
+This would be of value to academia, since APIs in the context of software evolution are relatively unexplored (!!!cite).
+The value of such a study is especially high since modifying APIs has a large impact on the API user {!!!cite, google talk}.
+This study is also of value for companies who wish to improve their APIs.
+By exploring why APIs change it can help companies in API design through highlighting areas where extra effort could be put in during the development (or improvement) of APIs.
 
 \subsection{Research Questions}
+RQ1: What drives API evolution? 
+SRQ1: To what extent can we reverse engineer API change decisions?
+SRQ2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
 

### 2015-03-18 rmtw/a6/latex8.tex
Intro for a6

--- 2015-03-17 rmtw/a6/latex8.tex
@@
 \section{Introduction}
-%Literature intro
-%A bit unclear what to write here - check with Branson
+%API Design
+An API is an interface defined in a programming language (in code) which can be accessed programatically by other software. (!!!Re-word this sentence a bit) %Add some more filler stuff here
 
-\subsection{Problem Statement}
+%Software Evolution 
+In the discipline of Software Evolution, such updates to applications are studied from an evolutionary standpoint.
+Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive \cite{lientz1980software}.
+%explain these factors a bit more closely in the related work?
 
-\subsection{Purpose Statement}
+%Gap in Literature
+There are no existing studies which analyse the motives behind API modifications using accepted Software Evolution theories.
+Studies that explore the intent behind API modifications exist \cite{hou2011exploring}, but only APIs to programming languages have been studied before.
+%%add the 2nd paper that hou2011exploring intent linked to (john mentioned this) to above cite /// also add the honey language or whatever...
+john said "or is this a language" and googled it
+
+%Problem statement
+There is consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it may will the users of the API to update the code that is accessing the API.
+(!!!re-word) The most common reason for modifying an API after it has been deployed (!!!
+word?) is refactoring \cite{dig2005role} \cite{xing2006refactoring}.
+%refactoring isn't the reason...
+it's the process.
+look up why refactoring is done or change wording.
+
+%Motivation
+Because of the negative implications that modifications to to APIs cause for the API users, it is important to understand why changes to APIs happen.
+If most common pitfalls are known before the development of new APIs are know, these mistakes can mitigated.
 
 \subsection{Research Questions}
+\begin{itemize}
+\item RQ1: What drives API evolution? 
+\item RQ1.1: To what extent can we reverse engineer API change decisions?
+\item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
+\end{itemize}
 

### 2015-03-19 rmtw/a6/latex8.tex
change structure of intro
Intro v1.more_or_less_done

@@
 \section{Introduction}
-%API Design
-An API is an interface defined in a programming language (in code) which can be accessed programatically by other software. (!!!Re-word this sentence a bit) %Add some more filler stuff here
-
+%API Design (and a little bit of ecosystems, and a bit of problem statement)
+An API is an interface defined in a programming language (in code) which can be accessed programatically by other software.
+(!!!Re-word this sentence a bit) There is a consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it will require the users of the API to update the code that is accessing the API (!!!re-word), and thus cause a disruption in the software ecosystem \cite{messerschmitt2005software} that the API's platform is a part of.
+Most commonly, already deployed APIs are modified due to code refactoring being made.
+\cite{dig2005role} \cite{xing2006refactoring}.
 %Software Evolution 
-In the discipline of Software Evolution, such updates to applications are studied from an evolutionary standpoint.
-Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive \cite{lientz1980software}.
-%explain these factors a bit more closely in the related work?
+In the discipline of Software Evolution, such updates to software are studied from an evolutionary standpoint.
+Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software} \cite{iso}.
 
 %Gap in Literature
-There are no existing studies which analyse the motives behind API modifications using accepted Software Evolution theories.
-Studies that explore the intent behind API modifications exist \cite{hou2011exploring}, but only APIs to programming languages have been studied before.
-%%add the 2nd paper that hou2011exploring intent linked to (john mentioned this) to above cite /// also add the honey language or whatever...
-john said "or is this a language" and googled it
+Existing studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
+There are however no studies that attempt to map the motives behind changes to business needs or existing software evolution theories such as the four categories of maintenance \cite{lientz1980software}.
+The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
+No studies that explore the motives behind or the effects of API evolution have previously been performed on embedded platform APIs.
 
-%Problem statement
-There is consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it may will the users of the API to update the code that is accessing the API.
-(!!!re-word) The most common reason for modifying an API after it has been deployed (!!!
-word?) is refactoring \cite{dig2005role} \cite{xing2006refactoring}.
-%refactoring isn't the reason...
-it's the process.
-look up why refactoring is done or change wording.
-
-%Motivation
+%Purpose (and a bit of problem statement)
 Because of the negative implications that modifications to to APIs cause for the API users, it is important to understand why changes to APIs happen.
-If most common pitfalls are known before the development of new APIs are know, these mistakes can mitigated.
+If most common pitfalls are known before the development of new APIs are known, these mistakes can mitigated.
+Before the industry can make use of this information, the proposed common pitfalls must also be validated.
 
@@
 \subsection{Software Evolution}
-
-\subsection{Architecture / Reverse Engineering (or tracing previously made decisions)}
 

### 2015-03-19 rmtw/a6/latex8.tex
reworded last sentence of intro and spellcheck

@@
 %API Design (and a little bit of ecosystems, and a bit of problem statement)
-An API is an interface defined in a programming language (in code) which can be accessed programatically by other software.
+An API is an interface defined in a programming language (in code) which can be accessed programmatically by other software.
 (!!!Re-word this sentence a bit) There is a consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it will require the users of the API to update the code that is accessing the API (!!!re-word), and thus cause a disruption in the software ecosystem \cite{messerschmitt2005software} that the API's platform is a part of.
@@
 If most common pitfalls are known before the development of new APIs are known, these mistakes can mitigated.
-Before the industry can make use of this information, the proposed common pitfalls must also be validated.
+Before the industry can make use of this information, we must also critically assess to what degree we trace such motives.
 

### 2015-03-19 rmtw/a6/latex8.tex
intro is good now, oh yeah

@@
 %API Design (and a little bit of ecosystems, and a bit of problem statement)
-An API is an interface defined in a programming language (in code) which can be accessed programmatically by other software.
-(!!!Re-word this sentence a bit) There is a consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it will require the users of the API to update the code that is accessing the API (!!!re-word), and thus cause a disruption in the software ecosystem \cite{messerschmitt2005software} that the API's platform is a part of.
-Most commonly, already deployed APIs are modified due to code refactoring being made.
-\cite{dig2005role} \cite{xing2006refactoring}.
+As the software industry and the open source movement are growing steadily, number of public APIs is increasing.
+APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
+There is a consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it will require the users of the API to update the code that is accessing the API, thus causing a disruption in the software ecosystem \cite{messerschmitt2005software} that the API's platform is a part of.
+Most commonly, already deployed APIs are modified due to code refactoring being made \cite{dig2005role} \cite{xing2006refactoring}.
 %Software Evolution 
@@
 The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
-No studies that explore the motives behind or the effects of API evolution have previously been performed on embedded platform APIs.
+To the best of our knowledge, no studies that explore the motives behind or the effects of API evolution have previously been performed on embedded platform APIs.
 
@@
 Because of the negative implications that modifications to to APIs cause for the API users, it is important to understand why changes to APIs happen.
-If most common pitfalls are known before the development of new APIs are known, these mistakes can mitigated.
+If most common pitfalls are known before the development of new APIs begin, these mistakes could be mitigated.
 Before the industry can make use of this information, we must also critically assess to what degree we trace such motives.
+To achieve this, we will perform a case study which aims to investigate the underlying factors behind what drives changes to APIs.
+This will be done by empirically analysing the changes between two versions of an API.
+Subsequently, the designers of the API will be interviewed and to verify (!!!does this imply that our findings will be accurate?) the results of our analysis.
 
@@
 \item RQ1.1: To what extent can we reverse engineer API change decisions?
-\item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
+% \item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
 \end{itemize}

### 2015-03-19 rmtw/a6/latex8.tex
sfds
Added my sections in the related work

@@
 %API Design (and a little bit of ecosystems, and a bit of problem statement)
-As the software industry and the open source movement are growing steadily, number of public APIs is increasing.
+As the software industry and the open source movement steadily grow, the number of public APIs is increasing.
 APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
@@
 
-\subsection{Software Evolution}
+API design is notoriously difficult with a myriad of design and performance decisions to take into consideration \cite{!!!
+MS, Design Doc}.
+Some studies have created a generalisable usability study with the aim of analysing the design decisions taken when creating an API \cite{}.
+Another empirical study, which involved working with 25 programmers, highlighted API design problems such as assigning names to API features and difficulty in naming types \cite{An Empirical Study of API Usability}.
+The study also found that in order to create a usable API, one must ensure that the API is understandable via good documentation, it’s not too abstract, has high reusability and that it is easy to learn \cite{API Usability}.
+Both studies also highlighted that API designers must ensure that, when using design patterns, such as the concrete factory pattern, that the intent of the API is clear to the user \cite{both}.
+
+A further study involved combining semiotic and cognitive methods to evaluate APIs as a means of facilitating communication, via an artefact, between programmers and designers.
+\cite{Evaluating application programming interfaces as communication artefacts}.
+However, these studies do not highlight the actual reasons behind changes of APIs.
+
+\subsection{API Change}
+Previous studies that have attempted to identify the reason behind API changes have primarily focused APIs that are a part of large programming languages, such as Java and Smalltalk (!!!
+cite).
+The intent of the study was to uncover the intents behind the changes made in the AWT/Swing Java libraries.
+The study found that the use of a strong architecture was vital in ensuring a smooth evolution of the API.
+
+However, when APIs are changed, problems tend to occur.
+One study investigated three frameworks and one library in which the study found that 80\% of re-factoring changes to APIs negatively affected existing applications.
+Re-factorings are not the only changes to APIs that can impact existing projects negatively.
+Another study was conducted regarding the changes, or, ripple effect that changes in APIs have on an entire ecosystem.
+This particular empirical study found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{!!!
+cite me plz}.
+
+Furthermore, a study of the impact of reliable APIs was undertaken in the Android ecosystem.
+The study aimed to discover if APIs with high rates of faults affected the success of an application.
+The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success.
 

### 2015-03-19 rmtw/a6/latex8.tex
Added citations

--- 2015-03-19 rmtw/a6/latex8.tex
@@
 
-\subsection{Software Evolution}
+API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective},\cite{afonso2012evaluating}, \cite{stylos2006comparing}.
+Some studies have created a generalisable usability study with the aim of analysing the design decisions taken when creating an API \cite{}.
+Another empirical study, which involved working with 25 programmers, highlighted API design problems such as assigning names to API features and difficulty in naming types \cite{shi2011empirical}.
+The study also found that in order to create a usable API, one must ensure that the API is understandable via good documentation, it’s not too abstract, has high reusability and that it is easy to learn \cite{shi2011empirical}.
+Both studies also highlighted that API designers must ensure that, when using design patterns, such as the concrete factory pattern, that the intent of the API is clear to the user \cite{shi2011empirical},\cite{stylos2006comparing}.
+
+A further study involved combining semiotic and cognitive methods to evaluate APIs as a means of facilitating communication, via an artefact, between programmers and designers.
+\cite{afonso2012evaluating}.
+However, these studies do not highlight the actual reasons behind changes of APIs.
+
+\subsection{API Change}
+Previous studies that have attempted to identify the reason behind API changes have primarily focused APIs that are a part of large programming languages, such as Java and Smalltalk \cite{robbes2012developers}, \cite{shi2011empirical}, \cite{hou2011exploring}.
+The intent of the study was to uncover the intents behind the changes made in the AWT/Swing Java libraries.
+The study found that the use of a strong architecture was vital in ensuring a smooth evolution of the API \cite{hou2011exploring}.
+
+However, when APIs are changed, problems tend to occur.
+One study investigated three frameworks and one library in which the study found that 80\% of re-factoring changes to APIs negatively affected existing applications.
+Re-factorings are not the only changes to APIs that can impact existing projects negatively.
+Another study was conducted regarding the changes, or, ripple effect that changes in APIs have on an entire ecosystem.
+This particular empirical study found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.
+
+Furthermore, a study of the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}.
+The study aimed to discover if APIs with high rates of faults affected the success of an application.
+The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.
 

### 2015-03-19 rmtw/a6/latex8.tex
updates to thesis proposal
1. Added section descriptions to intro

2. Added notes for methodology

3. Added notes for case company description

--- 2015-03-19 rmtw/a6/latex8.tex
@@
 
+The sections following the Introduction are structured as follows: In Section II, we present a literature review on research related to our study.
+Section II describes the case company and how it was selected.
+A description of our methodology is introduced in Section III.
+
 \subsection{Research Questions}
@@
 \item RQ1.1: To what extent can we reverse engineer API change decisions?
-% \item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
+%\item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
 \end{itemize}
@@
 \section{Case Company Description}
+Mention the country, size and domain. 
+Focus mostly on the API since that's what's relevant to our study.
+
+Also try to get some information on the users of the API. (it might be relevant).
+
+The case was selected using convenience sampling \cite{flyvbjerg2006five}, and a maximum variation strategy was used \cite{benbasat1987case}.
+As such, the goal was to include as many companies as possible in this study.
+[Ask Richard: Do you think we can claim that our case is typical, critical, revelatory or unique?
+Or is our current description adequate?]
 
 \section{Methodology}
-Brief intro, saying we will do a case study and what data collection methods will be used. (Also citing the paper from where we steal the case study process... höst).
 
-\subsection{Case Study Design}
+\subsection{Research strategy and investigation methods}
+• Describe and explain the research strategy and investigation methods that will be used for the project. Motivate your choice? Use relevant references.
+AKA EXPLAIN WHY WE DO
 
-\subsection{Preparation for Data Collection}
+Brief intro, saying we will do a case study \cite{runeson2009guidelines} and what data collection methods will be used.
 
-\subsection{Data Gathering}
+Explain why case study was chosen i.e. cuz we look at something in it's natural environment (it wouldn't work to look at example data)
+
+Another reason that the case study approach was chosen is that there is little existing research conducted in the area, and that input from the industry is vital to the success of the research.
+(Especially to validate if the proposed ``pitfalls''  are correct).
+
+Explain why we chose case study compared to for example design research.
+
+\subsection{Case Study Design and Planning}
+
+not sure if we will need this as a section
+*Do we create a case study protocol or is it too early?
+
+\subsection{Summary of methodology}
+
+• Research strategy (research methodology) 
+AKA EXPLAIN HOW
+
+The goal of the study is twofold
+
+*Define what type of goal and explain why it is ( exploratory, descriptive, explanatory, or improving.)
+
+*It will be an embedded case study since both the code and documentation will be used as a unit of analysis. (We can discuss if interviews will be a unit of analysis or not).
+
+\subsection{Data Collection}
+• data collection procedures (e.g. interviews? survey? and sampling?) 
+The main form of data collection will be performed through code and documentation analysis (third degree aka independent).
+In addition to this analysis, interviews will be conducted.
+The main purpose of the interviews is to provide insight regarding RQ1.1, but also to support data triangulation.
+
+Explain how we will sample the interviewees. (Ask Imed how this will be done).
 
 \subsection{Data Analysis}
+• method for analyzing the data (grounded theory? Thematic analysis? Statistical analysis?) strategies for validating findings
 
-\subsection{Threats to Validity}
+How will data be analyzed?
 

### 2015-03-19 rmtw/a6/latex8.tex
asdda

@@
 \section{Related Work}
+Our work is mainly related to the research area of APIs.
+This discipline will be discussed in both section 2.1 and 2.2.
+Our research is directly related to the fields of software evolution and software ecosystems.
+Section 2.2 will describe APIs in the context of those two fields.
 
@@
 \Section{Acknowledgement}
+John had the main responsibility for sections 1, 2.
+William had the main responsibility for section 3.
+Section 3.6 and the interview questions were written together.
+We have, however, worked on all sections jointly and all sections have been reviewed by both William and John.
 

### 2015-03-19 rmtw/a6/latex8.tex
sad

@@
 APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
-There is a consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it will require the users of the API to update the code that is accessing the API, thus causing a disruption in the software ecosystem \cite{messerschmitt2005software} that the API's platform is a part of.
+There is a consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it will require the users of the API to update the code that is accessing the API, thus causing a disruption in the software ecosystem that the API's platform is a part of \cite{messerschmitt2005software}.
 Most commonly, already deployed APIs are modified due to code refactoring being made \cite{dig2005role} \cite{xing2006refactoring}.

### 2015-03-19 rmtw/a6/latex8.tex
Added authorblock

@@
 \usepackage{latex8}
-%\documentstyle[times,art10,twocolumn,latex8]{article}
+\usepackage{authblk}
 
-%------------------------------------------------------------------------- 
-% take the % away on next line to produce the final camera-ready version 
-\pagestyle{empty}
+\title{Wu-Tang Clan}
 
-%------------------------------------------------------------------------- 
+% \author[*]{John Burchell}
+% \author[x]{William Granli}
+% \affil[*x]{Software Engineering \& Management}
+% \affil[*x]{University Of Gothenburg}
+% \affil[*]{john.a.burchell@gmail.com}
+% \affil[x]{william.granli@gmail.com}
+
 \begin{document}
 
-\title{A Comparison of Use-Case Based and Checklist-
-Based Reading: A Controlled Experiment}
-
-% author names and affiliations
-\author{John Burchell and William Granli \\
-john.a.burchell, william.granli@gmail.com}
+\author{\textsuperscript{*}John Burchell \qquad \textsuperscript{x}William Granli \\
+		\textsuperscript{*}john.a.burchell@gmail.com \qquad \textsuperscript{x}william.granli@gmail.com \\
+		\textsuperscript{*x}Software Engineering \& Management  \\
+		\textsuperscript{*x}University of Gothenburg }
 
 \maketitle
-\thispagestyle{empty}
-
-%-------------------------------------------------------------------------
 
@@
 
+%Structure of the paper
 The sections following the Introduction are structured as follows: In Section II, we present a literature review on research related to our study.
@@
 \section{Related Work}
-Our work is mainly related to the research area of APIs.
-This discipline will be discussed in both section 2.1 and 2.2.
-Our research is directly related to the fields of software evolution and software ecosystems.
-Section 2.2 will describe APIs in the context of those two fields.
+Our work is mainly related to the research area of API design.
+This discipline is discussed in Section 2.1.
+The motives and effects of changes to APIs is directly related related to the fields of software evolution and software ecosystems, and this will be discussed in Section 2.2.
 

### 2015-03-20 rmtw/a6/latex8.tex
sadasd
sad

@@
 
-\author{\textsuperscript{*}John Burchell \qquad \textsuperscript{x}William Granli \\
-		\textsuperscript{*}john.a.burchell@gmail.com \qquad \textsuperscript{x}william.granli@gmail.com \\
-		\textsuperscript{*x}Software Engineering \& Management  \\
-		\textsuperscript{*x}University of Gothenburg }
+% \author{\textsuperscript{*}John Burchell \qquad \textsuperscript{x}William Granli \\
+% 		\textsuperscript{*}john.a.burchell@gmail.com \qquad \textsuperscript{x}william.granli@gmail.com \\
+% 		\textsuperscript{*x} Computer Science and Engineering  \\
+% 		\textsuperscript{*x}University of Gothenburg }
+\author{John Burchell \qquad William Granli \\
+		john.a.burchell@gmail.com \qquad william.granli@gmail.com \\
+		Computer Science and Engineering  \\
+		University of Gothenburg }
 
@@
 %Structure of the paper
-The sections following the Introduction are structured as follows: In Section II, we present a literature review on research related to our study.
-Section II describes the case company and how it was selected.
-A description of our methodology is introduced in Section III.
+The sections following the Introduction are structured as follows: In Section 2, we present a literature review on research related to our study.
+Section 3 describes the case company and how it was selected.
+A description of our methodology is introduced in Section 4.
 

### 2015-03-20 rmtw/a6/latex8.tex
Review of intro

@@
 APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
-There is a consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it will require the users of the API to update the code that is accessing the API, thus causing a disruption in the software ecosystem that the API's platform is a part of \cite{messerschmitt2005software}.
-Most commonly, already deployed APIs are modified due to code refactoring being made \cite{dig2005role} \cite{xing2006refactoring}.
-%Software Evolution 
-In the discipline of Software Evolution, such updates to software are studied from an evolutionary standpoint.
+There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers}.
+The main reason being that it will require the users to update the code, which is using the API, thus causing a disruption in the applicaiton's software ecosystem \cite{messerschmitt2005software}.
+The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}.
+%software evolution 
+In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint.
 Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software} \cite{iso}.
@@
 %Gap in Literature
-Existing studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
-There are however no studies that attempt to map the motives behind changes to business needs or existing software evolution theories such as the four categories of maintenance \cite{lientz1980software}.
+Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
+There are, however, no studies that attempt to map the motives behind changes to business needs or existing software evolution theories, such as the four categories of maintenance \cite{lientz1980software} \cite{iso}.
 The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
@@
 %Purpose (and a bit of problem statement)
-Because of the negative implications that modifications to to APIs cause for the API users, it is important to understand why changes to APIs happen.
+Due to the negative implications that modifications to to APIs cause for API users, it is important to understand why changes to APIs occur.
 If most common pitfalls are known before the development of new APIs begin, these mistakes could be mitigated.
-Before the industry can make use of this information, we must also critically assess to what degree we trace such motives.
-To achieve this, we will perform a case study which aims to investigate the underlying factors behind what drives changes to APIs.
-This will be done by empirically analysing the changes between two versions of an API.
-Subsequently, the designers of the API will be interviewed and to verify (!!!does this imply that our findings will be accurate?) the results of our analysis.
+Before the industry can make use of this information, we must also critically assess to what degree we can trace such motives.
+To achieve this, we will perform a case study which aims to investigate the underlying factors behind API changes.
+This will be achieved by empirically analysing the changes between two versions of an API.
+Subsequently, the designers of the API will be interviewed and asked to verify the accuracy of our findings.
 
@@
 This discipline is discussed in Section 2.1.
-The motives and effects of changes to APIs is directly related related to the fields of software evolution and software ecosystems, and this will be discussed in Section 2.2.
+The motives and effects of changes to APIs is directly related related to the fields of software evolution and software ecosystems.
+This will be discussed in Section 2.2.
 

### 2015-03-20 rmtw/a6/latex8.tex
Updated related work based on feedback. Added new entry to bib.

@@
 
-API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective},\cite{afonso2012evaluating}, \cite{stylos2006comparing}.
-Some studies have created a generalisable usability study with the aim of analysing the design decisions taken when creating an API \cite{}.
+API design is notoriously difficult as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective}\cite{afonso2012evaluating}\cite{stylos2006comparing}.
+In previous research generalisable usability studies have been created, with the aim of analysing the design decisions taken when creating an API \cite{stylos2006comparing}.
 Another empirical study, which involved working with 25 programmers, highlighted API design problems such as assigning names to API features and difficulty in naming types \cite{shi2011empirical}.
-The study also found that in order to create a usable API, one must ensure that the API is understandable via good documentation, it’s not too abstract, has high reusability and that it is easy to learn \cite{shi2011empirical}.
-Both studies also highlighted that API designers must ensure that, when using design patterns, such as the concrete factory pattern, that the intent of the API is clear to the user \cite{shi2011empirical},\cite{stylos2006comparing}.
+The study also introduced four factors which are important to consider when creating an API: a) The API  must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
+Both studies also highlighted that the intent of the API must be clear to the user when using design patters, such as the concrete factory pattern \cite{shi2011empirical} \cite{stylos2006comparing}.
 
-A further study involved combining semiotic and cognitive methods to evaluate APIs as a means of facilitating communication, via an artefact, between programmers and designers.
+An additional study involved combining semiotic and cognitive methods to evaluate APIs as a means of facilitating communication, between programmers and designers.
 \cite{afonso2012evaluating}.
-However, these studies do not highlight the actual reasons behind changes of APIs.
+However, these studies do not highlight the motives behind changes to APIs.
 
 \subsection{API Change}
-Previous studies that have attempted to identify the reason behind API changes have primarily focused APIs that are a part of large programming languages, such as Java and Smalltalk \cite{robbes2012developers}, \cite{shi2011empirical}, \cite{hou2011exploring}.
-The intent of the study was to uncover the intents behind the changes made in the AWT/Swing Java libraries.
-The study found that the use of a strong architecture was vital in ensuring a smooth evolution of the API \cite{hou2011exploring}.
+Previous studies that have attempted to identify the motives behind API changes have primarily focused on APIs that are a part of large programming languages, such as Java \cite{shi2011empirical} \cite{hou2011exploring} and Smalltalk \cite{robbes2012developers}.
+One study attempted to uncover the intents behind the changes made in the AWT and Swing Java libraries.
+This particular study found that the use of a strong architecture was vital in ensuring a successful evolution of the API \cite{hou2011exploring}.
 
 However, when APIs are changed, problems tend to occur.
-One study investigated three frameworks and one library in which the study found that 80\% of re-factoring changes to APIs negatively affected existing applications.
-Re-factorings are not the only changes to APIs that can impact existing projects negatively.
-Another study was conducted regarding the changes, or, ripple effect that changes in APIs have on an entire ecosystem.
+One study \cite{dig2005role} investigated three frameworks and one library in which the study found that 80\% of refactoring changes to APIs negatively affected existing applications.
+Refactorings are not the only changes to APIs that can impact existing projects negatively.
+Another study was conducted regarding the changes, which the researchers refer to as ripple effects \cite{robbes2012developers}.
+They found that changes in APIs have an effect upon the entire ecosystem.
 This particular empirical study found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.

### 2015-03-20 rmtw/a5/latex8.tex
Added R stuff
been be

@@
 
-\title{Wu-Tang Clan}
+\title{The Applications of Model-driven Software Development, A Systematic Literature Review}
 
@@
 For similar reasons, a case study would also not have been applicable as we were not concerning ourselves with how MDSD works in a real setting.
-Likewise, as industry and academia seem to differ in opinion, there is an implication that there could have been be bias in both sides of the argument.
+Likewise, as industry and academia seem to differ in opinion, there is an implication that there could have been bias in both sides of the argument.
 By performing an SLR we helped to alleviate some of this bias but we did not eliminate it entirely \cite{kitchenham2007guidelines}.
@@
 
-Parts Section 1.2 have been re-used from previous assignments. Because of this, the paper may show up on Urkund.
+Section 1.2 have been re-used from previous assignments. Because of this, the paper may show up on Urkund.
 

### 2015-03-20 rmtw/a6/latex8.tex
Added more notes to meth a6

@@
 Mention the country, size and domain. 
+In domain of surveillance cameras and they develop embedded software for the cameras. 
 Focus mostly on the API since that's what's relevant to our study. 
+Something about market leader in their domain - and that means that changes to their API could have large consequences.
 
-Also try to get some information on the users of the API. (it might be relevant).
+Also try to get some information on the users of the API. (it might be relevant). %%Not sure if we can get htat now, maybe thorugh the interviews or by asking Imed
 
@@
 As such, the goal was to include as many companies as possible in this study.
-[Ask Richard: Do you think we can claim that our case is typical, critical, revelatory or unique?
+[Note to Richard: Do you think we can claim that our case is typical, critical, revelatory or unique?
 Or is our current description adequate?]
+
+%%Add why we didn't use other sampling methods for the final handin.
 
@@
 Explain why we chose case study compared to for example design research.
-
-\subsection{Case Study Design and Planning}
-
-not sure if we will need this as a section
-*Do we create a case study protocol or is it too early?
-
-\subsection{Summary of methodology}
-
-• Research strategy (research methodology) 
-AKA EXPLAIN HOW
+%Thius might not have to be in the proposal
 
@@
 *It will be an embedded case study since both the code and documentation will be used as a unit of analysis. (We can discuss if interviews will be a unit of analysis or not).
+
+\subsection{Case Study Design and Planning}
+
+not sure if we will need this as a section
+*Do we create a case study protocol or is it too early?
 
@@
 Explain how we will sample the interviewees. (Ask Imed how this will be done).
+
+It is importnat that we explain exactly why we chose the collection methods we did. It is also important htat we clearly explain which methods relate to which RQs.
+
+Also explain why for example questionnaire wasn't used.
 

### 2015-03-20 rmtw/a6/latex8.tex
sadsa
Added first draft of Data Collection

@@
 \subsection{Data Collection}
-• data collection procedures (e.g. interviews? survey? and sampling?) 
-The main form of data collection will be performed through code and documentation analysis (third degree aka independent).
+% • data collection procedures (e.g. interviews? survey? and sampling?) 
+% The main form of data collection will be performed through code and documentation analysis (third degree aka independent).
 In addition to this analysis, interviews will be conducted.
@@
 
-Explain how we will sample the interviewees. (Ask Imed how this will be done).
+% Explain how we will sample the interviewees. (Ask Imed how this will be done).
 
-It is importnat that we explain exactly why we chose the collection methods we did. It is also important htat we clearly explain which methods relate to which RQs.
+% It is importnat that we explain exactly why we chose the collection methods we did. It is also important htat we clearly explain which methods relate to which RQs.
 
-Also explain why for example questionnaire wasn't used.
+% Also explain why for example questionnaire wasn't used.
+
+% Interviews will be used for:
+% Main: Verify our findings
+% Sub1: Provide additional insight (find stuff we missed)
+% SUb2: Get more info about the user of the api
+
+The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of relating documentation.
+From the source code we extracted information regarding the public facing APIs.
+Specifically, we collected information about return types, parameters and method names.
+The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
+From the archival documentation we collected information regarding the intent behind the functionality in API calls.
+For example, we examined differences in descriptions of methods prior to and after return types or parameters were renamed.
+This information provided insight into the motivation behind the changes.
+
+These collection methods were the most appropriate given that the data were readily available from the company.
+This did bring with it concerns that the data were not collected for the purpose of research \cite{!!!
+host}, meaning that some of the data had the risk of being irrelevant and that erroneous data had the potential to exist.
+Collection from another techniques were required to fill in the missing data.
+
+A first degree interview was also be conducted after the initial source inspections had taken place.
+The main purpose was to validate our findings with the architects of the API.
+Furthermore, the interviews provided additional insight into decisions and motivations behind changes that we were unaware of.
+The interviews also provided us with more insight about the end users of the system.
+Another added benefit was that we were able to triangulate our results with responses in the interviews, allowing us to validate, or refute our findings.
 

### 2015-03-20 rmtw/a6/latex8.tex
added intro to meth

@@
 \section{Case Company Description}
+The case company is a 
 Mention the country, size and domain. 
@@
 As such, the goal was to include as many companies as possible in this study.
-[Note to Richard: Do you think we can claim that our case is typical, critical, revelatory or unique?
+[!!!Note to Richard \#1: Do you think we can claim that our case is typical, critical, revelatory or unique?
 Or is our current description adequate?]
@@
 \section{Methodology}
+This study has been conducted using the case study methodology \cite{runeson2009guidelines}.
+The goal of the study was twofold.
+Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs, and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's.
+Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have used as units of analysis [!!!Note to Richard \#2: Do you agree with this?]
 
-\subsection{Research strategy and investigation methods}
-• Describe and explain the research strategy and investigation methods that will be used for the project. Motivate your choice? Use relevant references.
-AKA EXPLAIN WHY WE DO
+The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
+The applicability of case studies in such scenarios is supported by existing studies \cite{runeson2009guidelines} \cite{benbasat1987case} \cite{yin2013case} \cite{robson2002real}.
+An alternative approach that was considered was design research, but if a ``toy program" was to be used instead of an API tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines} [!!!Note to Richard \#3: Do you think this is a valid reason?
+Or is it a stretch to assume that all design research involves toy programs].
 
-Brief intro, saying we will do a case study \cite{runeson2009guidelines} and what data collection methods will be used.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to assess the validity of the findings related to RQ1.
 
-Explain why case study was chosen i.e. cuz we look at something in it's natural environment (it wouldn't work to look at example data)
-
-Another reason that the case study approach was chosen is that there is little existing research conducted in the area, and that input from the industry is vital to the success of the research.
-(Especially to validate if the proposed ``pitfalls''  are correct).
-
-Explain why we chose case study compared to for example design research.
-%Thius might not have to be in the proposal
-
-The goal of the study is twofold
-
-*Define what type of goal and explain why it is ( exploratory, descriptive, explanatory, or improving.)
-
-*It will be an embedded case study since both the code and documentation will be used as a unit of analysis. (We can discuss if interviews will be a unit of analysis or not).
+We have structured our research around three major steps. Initially, the study was planned. Following that, we collected the data and lastly, we analysed the data.
 

### 2015-03-20 rmtw/a6/latex8.tex
added case compnay description a6

@@
 % 		\textsuperscript{*x}University of Gothenburg }
+
 \author{John Burchell \qquad William Granli \\
@@
 \section{Case Company Description}
-The case company is a 
-Mention the country, size and domain. 
-In domain of surveillance cameras and they develop embedded software for the cameras. 
-Focus mostly on the API since that's what's relevant to our study. 
-Something about market leader in their domain - and that means that changes to their API could have large consequences.
+The case company is a medium-sized company in the domain of security cameras.
+The company has its headquarters in Lund, Sweden, but it operates worldwide.
+The company is the global market leader in the markets of network cameras and video encoders.
+The company develops embedded software for the security cameras, and some cameras are designed to be accessible by APIs that are also developed by the company.
 
-Also try to get some information on the users of the API. (it might be relevant). %%Not sure if we can get htat now, maybe thorugh the interviews or by asking Imed
+%Try to get information about the users of the API. Either through Imed, or through the interviews.
 
@@
 
-%%Add why we didn't use other sampling methods for the final handin.
+%Try to motivate why other sampling methods weren't used.
 
@@
 The goal of the study was twofold.
-Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs, and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's.
-Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have used as units of analysis [!!!Note to Richard \#2: Do you agree with this?]
+Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs, and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's explanation of their motives.
+Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis [!!!Note to Richard \#2: Do you agree with this?]
 
@@
 An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to assess the validity of the findings related to RQ1.
-
-We have structured our research around three major steps. Initially, the study was planned. Following that, we collected the data and lastly, we analysed the data.
-
-\subsection{Case Study Design and Planning}
-
-not sure if we will need this as a section
-*Do we create a case study protocol or is it too early?
 

### 2015-03-20 rmtw/a6/latex8.tex
title wip

@@
 
-\title{Wu-Tang Clan}
+\title{Exploring and Validating the Motives Behind API Evolution: A Case Study}
 
@@
 
-The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of relating documentation.
-From the source code we extracted information regarding the public facing APIs.
-Specifically, we collected information about return types, parameters and method names.
+%Explain that we have two versions of the API, old and new
+%Explain about how we'll collect them, i.e. in tables and spreadsheets. Different versions etc
+%Double inspection will be performed. Two steps, independently by each of us to reduce research bias and human error.
+
+The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of accompanying  documentation.
+The source code was comprised of two versions of APIs which the company had developed.
+An older version which is currently released and a newer version which is soon to be deployed.
+Each version of the API had its own relevant documentation.
+The documentation provided explanations of the features offered by the API and illustrated some examples of its usage.
+
+From the APIs we collected data about method names, parameters and return types.
 The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
-From the archival documentation we collected information regarding the intent behind the functionality in API calls.
+From the archival documentation we collected information regarding the motive behind the functionality in API calls.
+This information provided insight into the motives behind the changes.
 For example, we examined differences in descriptions of methods prior to and after return types or parameters were renamed.
-This information provided insight into the motivation behind the changes.
+
+A double inspection and a single joint inspection were used to collect the information from the APIs and the documentation.
+This was performed to reduce researcher bias and human error.
+Once collected, the data were input into tables and spreadsheets according to the API version.
 
 These collection methods were the most appropriate given that the data were readily available from the company.
-This did bring with it concerns that the data were not collected for the purpose of research \cite{!!!
-host}, meaning that some of the data had the risk of being irrelevant and that erroneous data had the potential to exist.
-Collection from another techniques were required to fill in the missing data.
+This brought concerns that the data were not collected for the purpose of research \cite{runeson2009guidelines}, meaning there was a risk of data being irrelevant or erroneous.
 
-A first degree interview was also be conducted after the initial source inspections had taken place.
+Collecting data by using other techniques were required to fill in the missing data.
+First degree interviews were also conducted after the initial source inspections had taken place.
 The main purpose was to validate our findings with the architects of the API.
@@
 Another added benefit was that we were able to triangulate our results with responses in the interviews, allowing us to validate, or refute our findings.
+
+%why methods apply to our study, why the techniques were used. Motivate relationship between the techniques and the RQs
 

### 2015-03-20 rmtw/a6/latex8.tex
Second version of data collection
removed ocmment

@@
 \subsection{Data Collection}
-% • data collection procedures (e.g. interviews? survey? and sampling?) 
-% The main form of data collection will be performed through code and documentation analysis (third degree aka independent).
-In addition to this analysis, interviews will be conducted.
-The main purpose of the interviews is to provide insight regarding RQ1.1, but also to support data triangulation.
-
-% Explain how we will sample the interviewees. (Ask Imed how this will be done).
-
-% It is importnat that we explain exactly why we chose the collection methods we did. It is also important htat we clearly explain which methods relate to which RQs.
-
-% Also explain why for example questionnaire wasn't used.
-
-% Interviews will be used for:
-% Main: Verify our findings
-% Sub1: Provide additional insight (find stuff we missed)
-% SUb2: Get more info about the user of the api
-
-%Explain that we have two versions of the API, old and new
-%Explain about how we'll collect them, i.e. in tables and spreadsheets. Different versions etc
-%Double inspection will be performed. Two steps, independently by each of us to reduce research bias and human error.
-
 The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of accompanying  documentation.

### 2015-03-20 rmtw/a6/latex8.tex
Added validity threats v1

@@
 There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers}.
-The main reason being that it will require the users to update the code, which is using the API, thus causing a disruption in the applicaiton's software ecosystem \cite{messerschmitt2005software}.
+The main reason being that it will require the users to update the code, which is using the API, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
 The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}.
@@
 This will be achieved by empirically analysing the changes between two versions of an API.
-Subsequently, the designers of the API will be interviewed and asked to verify the accuracy of our findings.
+Subsequently, the architects of the API will be interviewed and asked to verify the accuracy of our findings.
 
@@
 
-API design is notoriously difficult as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective}\cite{afonso2012evaluating}\cite{stylos2006comparing}.
+API design is notoriously difficult as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective} \cite{afonso2012evaluating} \cite{stylos2006comparing}.
 In previous research generalisable usability studies have been created, with the aim of analysing the design decisions taken when creating an API \cite{stylos2006comparing}.
@@
 An older version which is currently released and a newer version which is soon to be deployed.
-Each version of the API had its own relevant documentation.
-The documentation provided explanations of the features offered by the API and illustrated some examples of its usage.
+Each version of the API had its own respective documentation.
+The documentation was analysed to find explanations of the features offered by the API.
 
@@
 From the archival documentation we collected information regarding the motive behind the functionality in API calls.
-This information provided insight into the motives behind the changes.
-For example, we examined differences in descriptions of methods prior to and after return types or parameters were renamed.
+The reason this was analysed was to provide insight into the motives behind the changes.
+For example, we examined differences in descriptions of methods prior to and after parameters were renamed.
 
-A double inspection and a single joint inspection were used to collect the information from the APIs and the documentation.
-This was performed to reduce researcher bias and human error.
-Once collected, the data were input into tables and spreadsheets according to the API version.
+A double inspection and a single joint inspection were used to collect the information from the APIs code and the documentation.
+This was performed to reduce research bias and human error.
+As part of the collection phase, the data were input into tables and spreadsheets, according to the API version.
 
 These collection methods were the most appropriate given that the data were readily available from the company.
-This brought concerns that the data were not collected for the purpose of research \cite{runeson2009guidelines}, meaning there was a risk of data being irrelevant or erroneous.
+This brought concerns that the data were not produced for the purpose of our research \cite{runeson2009guidelines}, meaning there was a risk of data being irrelevant or erroneous.
 
-Collecting data by using other techniques were required to fill in the missing data.
-First degree interviews were also conducted after the initial source inspections had taken place.
-The main purpose was to validate our findings with the architects of the API.
-Furthermore, the interviews provided additional insight into decisions and motivations behind changes that we were unaware of.
+First degree interviews were also conducted after the initial source code inspections had taken place.
+The main purpose was to validate our findings with the architects of the APIs.
+Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection.
+The final reason for interviewing the architects of the APIs was to provide further insight of the users of the API.
+
+\subsection{Data Analysis}
+• method for analysing the data (grounded theory? Thematic analysis? Statistical analysis?) strategies for validating findings
+
 The interviews also provided us with more insight about the end users of the system.
@@
 
-%why methods apply to our study, why the techniques were used. Motivate relationship between the techniques and the RQs
+\subsection{Validity Threats}
+This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.
 
-\subsection{Data Analysis}
-• method for analyzing the data (grounded theory? Thematic analysis? Statistical analysis?) strategies for validating findings
+%Internal Validity
+\textit{Internal Validity} threats for our study have been greatly reduced by the methodologies we have employed.
+By performing a dual inspection and then a joint inspection of both the API source code, documentation and results analysis, \textit{internal validity} is significantly reduced.
+Triangulation of the results with the use of interviewing the architects is key step in reducing potential validity threats in our study.
 
-How will data be analyzed?
+%External Validity
+Regarding \textit{external validity}, generalisability and the appropriateness of our results are at risk.
+In our study we have striven to ensure that our findings will be as useful as possible to others.
+Given that there are some similar studies to ours and that ours is an exploratory study, our results will be useful to others who perform similar studies in the future.
+Our results come from both APIs either in production or soon to be in production.
+As such, the results of this study will hopefully be of use to the company at which they were studied, be it now for their current API or in the future when they inevitably develop others.
+Likewise, other companies in similar positions could use the results of our study when creating their own APIs.
+
+%Reliability
+The largest \textit{reliability} threat facing our study was the reproducibility.
+To counter this threat, we have provided a clear and concise coding method for the collected data.
+Furthermore, as mentioned previously, we have attempted to limit bias and ambiguity in our interview questions where possible.
+To ensure clarity of the questions, we have field tested the interview with some of our peers, altering the questions based on their feedback.
+
+[!!!Note to Richard \#4: We struggled to find construct threats as we've not done the study so we don't know any yet, is it normal or OK to exclude one of the categories?]
 

### 2015-03-20 rmtw/a6/latex8.tex
analysis

@@
 
-A double inspection and a single joint inspection were used to collect the information from the APIs code and the documentation.
-This was performed to reduce research bias and human error.
+To reduce risks of research bias and human error, the data collection was performed by both researchers individually and indepenedtly.
+If the data differed, the cause was investigated and resolved.
 As part of the collection phase, the data were input into tables and spreadsheets, according to the API version.
@@
 \subsection{Data Analysis}
-• method for analysing the data (grounded theory? Thematic analysis? Statistical analysis?) strategies for validating findings
+The data analysis was conducted in two major phases \cite{andersson2007spiral}.
+During the first phase, a hypothesis generating approach \cite{seaman1999qualitative} was used to be able to fulfil the exploratory goal of the study.
+It was during this phase that the analysis of the API code and documentation was carried out.
+The second phase included analysis of the interviews, the goal of it was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase.
 
-The interviews also provided us with more insight about the end users of the system.
+Both phases were performed iteratively, together with the data collection.
+The reason for this create the opportunity of being able to improve the process of analysis as the study progressed, as well as to be able to adapt to possible changes in direction due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
+
+The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
+More specifically, the approach undertaken was divided into three steps where the data first was coded based on which category of maintenance \cite{iso} the motive of the change corresponded with.
+Secondly, the codes were analysed from a high-level point of view, and the main goal was to identify trends in the codes.
+The third step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.
+
+Following the analysis of the archival data, the results of the interviews were analysed.
+The interviews were analysed using the same approach taken for the archival data.
+The results of this analysis was then compared and correlated with the results of the code analysis.
+
+We took the same approach (roles/double stuff) as in the collection to reduce human rerror + reseach bias.
+
 Another added benefit was that we were able to triangulate our results with responses in the interviews, allowing us to validate, or refute our findings.
-
-\subsection{Validity Threats}
-This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.
-
-%Internal Validity
-\textit{Internal Validity} threats for our study have been greatly reduced by the methodologies we have employed.
-By performing a dual inspection and then a joint inspection of both the API source code, documentation and results analysis, \textit{internal validity} is significantly reduced.
-Triangulation of the results with the use of interviewing the architects is key step in reducing potential validity threats in our study.
-
-%External Validity
-Regarding \textit{external validity}, generalisability and the appropriateness of our results are at risk.
-In our study we have striven to ensure that our findings will be as useful as possible to others.
-Given that there are some similar studies to ours and that ours is an exploratory study, our results will be useful to others who perform similar studies in the future.
-Our results come from both APIs either in production or soon to be in production.
-As such, the results of this study will hopefully be of use to the company at which they were studied, be it now for their current API or in the future when they inevitably develop others.
-Likewise, other companies in similar positions could use the results of our study when creating their own APIs.
-
-%Reliability
-The largest \textit{reliability} threat facing our study was the reproducibility.
-To counter this threat, we have provided a clear and concise coding method for the collected data.
-Furthermore, as mentioned previously, we have attempted to limit bias and ambiguity in our interview questions where possible.
-To ensure clarity of the questions, we have field tested the interview with some of our peers, altering the questions based on their feedback.
-
-[!!!Note to Richard \#4: We struggled to find construct threats as we've not done the study so we don't know any yet, is it normal or OK to exclude one of the categories?]
 

### 2015-03-20 rmtw/a6/latex8.tex
Merged sentence and re-added validity threats

@@
 Each version of the API had its own respective documentation.
-The documentation was analysed to find explanations of the features offered by the API.
+The documentation was inspected and organised to find explanations of the features offered by the API.
 
@@
 The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
-From the archival documentation we collected information regarding the motive behind the functionality in API calls.
-The reason this was analysed was to provide insight into the motives behind the changes.
-For example, we examined differences in descriptions of methods prior to and after parameters were renamed.
+The collected data were input into tables and spreadsheets, according to the API version.
+From the archival documentation we collected data regarding the motive behind the functionality in API calls.
+Data gathered from the documentation was also stored in tables and spreadsheets and was organised together with its corresponding method.
 
-To reduce risks of research bias and human error, the data collection was performed by both researchers individually and indepenedtly.
-If the data differed, the cause was investigated and resolved.
-As part of the collection phase, the data were input into tables and spreadsheets, according to the API version.
+To reduce risks of research bias and human error, the data collection was performed by both researchers individually and independently. If the data differed, the cause was investigated and resolved.
 
@@
 
+\subsection{Validity Threats}
+This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.
+
+%Internal Validity
+\textit{Internal Validity} threats for our study have been greatly reduced by the methodologies we have employed.
+By performing a individual inspection of  the API source code, documentation and individual results analysis, \textit{internal validity} is significantly reduced.
+Triangulation of the results with the use of interviewing the architects is key step in reducing potential validity threats in our study.
+
+%External Validity
+Regarding \textit{external validity}, generalisability and the appropriateness of our results are at risk.
+In our study we have striven to ensure that our findings will be as useful as possible to others.
+Given that there are some similar studies to ours and that ours is an exploratory study, our results will be useful to others who perform similar studies in the future.
+Our results come from both APIs either in production or soon to be in production.
+As such, the results of this study will hopefully be of use to the company at which they were studied, be it now for their current API or in the future when they inevitably develop others.
+Likewise, other companies in similar positions could use the results of our study when creating their own APIs.
+
+%Reliability
+The largest \textit{reliability} threat facing our study was the reproducibility.
+To counter this threat, we have provided a clear and concise coding method for the collected data.
+Furthermore, as mentioned previously, we have attempted to limit bias and ambiguity in our interview questions where possible.
+To ensure clarity of the questions, we have field tested the interview with some of our peers, altering the questions based on their feedback.
+
+[!!!Note to Richard \#4: We struggled to find construct threats as we've not done the study so we don't know any yet, is it normal or OK to exclude one of the categories?]
+
 \bibliographystyle{latex8}

### 2015-03-20 rmtw/a6/latex8.tex
Changed some wurdz
dsaasd

@@
 
-To reduce risks of research bias and human error, the data collection was performed by both researchers individually and independently. If the data differed, the cause was investigated and resolved.
+To reduce risks of research bias and human errors, the data collection was performed independently by both researchers. If the data differed, the cause was investigated and resolved.
 
@@
 The interviews were analysed using the same approach taken for the archival data.
-The results of this analysis was then compared and correlated with the results of the code analysis.
+The results of this analysis was then compared and correlated with the results of the code analysis, with the goal of confirming the hypotheses that were formulated.
 
-We took the same approach (roles/double stuff) as in the collection to reduce human rerror + reseach bias.
+The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.
 

### 2015-03-20 rmtw/a6/latex8.tex
sadads

@@
 
-%Structure of the paper
-The sections following the Introduction are structured as follows: In Section 2, we present a literature review on research related to our study.
-Section 3 describes the case company and how it was selected.
-A description of our methodology is introduced in Section 4.
-
 \subsection{Research Questions}
@@
 \end{itemize}
+
+%Structure of the paper
+The sections following the Introduction are structured as follows: In Section 2, we present a literature review on research related to our study.
+Section 3 describes the case company and how it was selected.
+A description of our methodology is introduced in Section 4.
 
@@
 The results of this analysis was then compared and correlated with the results of the code analysis, with the goal of confirming the hypotheses that were formulated.
+This was done to triangulate the our findings, to help reduce internal validity.
 
 The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.
-
-Another added benefit was that we were able to triangulate our results with responses in the interviews, allowing us to validate, or refute our findings.
 
@@
 %Internal Validity
-\textit{Internal Validity} threats for our study have been greatly reduced by the methodologies we have employed.
+\textit{Internal validity} threats for our study have been greatly reduced by the methodologies we have employed.
 By performing a individual inspection of  the API source code, documentation and individual results analysis, \textit{internal validity} is significantly reduced.

### 2015-03-20 rmtw/a6/latex8.tex
sendin it to ioannis

@@
 
-\title{Exploring and Validating the Motives Behind API Evolution: A Case Study}
+\title{To Be Announced}
 
@@
 \subsection{API Change}
+%%The first sentence of this pargraph... did all 3 really look at motive/intent?
 Previous studies that have attempted to identify the motives behind API changes have primarily focused on APIs that are a part of large programming languages, such as Java \cite{shi2011empirical} \cite{hou2011exploring} and Smalltalk \cite{robbes2012developers}.
@@
 The company is the global market leader in the markets of network cameras and video encoders.
-The company develops embedded software for the security cameras, and some cameras are designed to be accessible by APIs that are also developed by the company.
+The company develops embedded software for the security cameras, and some of their products are designed to be accessible through APIs that are also developed by the company.
 
@@
 As such, the goal was to include as many companies as possible in this study.
-[!!!Note to Richard \#1: Do you think we can claim that our case is typical, critical, revelatory or unique?
-Or is our current description adequate?]
+[Note to reviewer \#1: Do you think we can claim that our case is typical, critical, revelatory or unique?
+Or is the current description adequate?]
 
@@
 Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs, and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's explanation of their motives.
-Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis [!!!Note to Richard \#2: Do you agree with this?]
+Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis [Note to reviewer \#2: Do you agree with this?]
 
@@
 The applicability of case studies in such scenarios is supported by existing studies \cite{runeson2009guidelines} \cite{benbasat1987case} \cite{yin2013case} \cite{robson2002real}.
-An alternative approach that was considered was design research, but if a ``toy program" was to be used instead of an API tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines} [!!!Note to Richard \#3: Do you think this is a valid reason?
-Or is it a stretch to assume that all design research involves toy programs].
+An alternative approach that was considered was design research, but if a ``toy program" was to be used instead of an API tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines} [Note to reviewer \#3: Do you think this is a valid reason?
+Or does it imply that all design research involves toy programs?].
 
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to assess the validity of the findings related to RQ1.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to answer RQ1.1.
 
@@
 The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of accompanying  documentation.
-The source code was comprised of two versions of APIs which the company had developed.
+The source code was comprised of two versions of the same API which the company had developed.
 An older version which is currently released and a newer version which is soon to be deployed.
@@
 First degree interviews were also conducted after the initial source code inspections had taken place.
-The main purpose was to validate our findings with the architects of the APIs.
+The main purpose of these was to validate our findings with the architects of the APIs.
 Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection.
@@
 It was during this phase that the analysis of the API code and documentation was carried out.
-The second phase included analysis of the interviews, the goal of it was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase.
+The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase.
 
 Both phases were performed iteratively, together with the data collection.
-The reason for this create the opportunity of being able to improve the process of analysis as the study progressed, as well as to be able to adapt to possible changes in direction due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
+The reason for this created the opportunity to improve the process of analysis as the study progressed, as well as to be able to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
 
 The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
-More specifically, the approach undertaken was divided into three steps where the data first was coded based on which category of maintenance \cite{iso} the motive of the change corresponded with.
+More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{iso} the motive of the change corresponded to.
 Secondly, the codes were analysed from a high-level point of view, and the main goal was to identify trends in the codes.
@@
 The results of this analysis was then compared and correlated with the results of the code analysis, with the goal of confirming the hypotheses that were formulated.
-This was done to triangulate the our findings, to help reduce internal validity.
+This was done to triangulate our findings, to help reduce internal validity.
 
@@
 \subsection{Validity Threats}
-This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.
+% This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.
 
@@
 \textit{Internal validity} threats for our study have been greatly reduced by the methodologies we have employed.
-By performing a individual inspection of  the API source code, documentation and individual results analysis, \textit{internal validity} is significantly reduced.
+By performing a individual inspection of  the API source code, documentation and individual results analysis, internal validity is significantly reduced.
 Triangulation of the results with the use of interviewing the architects is key step in reducing potential validity threats in our study.
@@
 The largest \textit{reliability} threat facing our study was the reproducibility.
-To counter this threat, we have provided a clear and concise coding method for the collected data.
+To counter this threat, we have followed a well-proven method for analysing the collected data.
 Furthermore, as mentioned previously, we have attempted to limit bias and ambiguity in our interview questions where possible.
-To ensure clarity of the questions, we have field tested the interview with some of our peers, altering the questions based on their feedback.
+To ensure clarity of the questions, we have field tested the interview with some of our peers, improving the questions based on their feedback.
 
-[!!!Note to Richard \#4: We struggled to find construct threats as we've not done the study so we don't know any yet, is it normal or OK to exclude one of the categories?]
+[Note to reviewer \#4: We struggled to find construct threats as we've not done the study so we don't know any yet, is it normal or OK to exclude one of the categories?]
 
@@
 \Section{Acknowledgement}
-John had the main responsibility for sections 1, 2.
-William had the main responsibility for section 3.
-Section 3.6 and the interview questions were written together.
-We have, however, worked on all sections jointly and all sections have been reviewed by both William and John.
+John had the main responsibility for sections 2, 4.1 and 4.3.
+William had the main responsibility for sections 1, 3, 4.0 and 4.3.
+We have, however, worked on all sections jointly and all sections have been reviewed by both of us.
 
-\noindent
 \end{document}

### 2015-03-21 rmtw/a6/latex8.tex
janis review fixes

@@
 APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
-There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers}.
-The main reason being that it will require the users to update the code, which is using the API, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
+There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
+The main reason is that it will require the users to update the code, which is using the API, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
 The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}.
@@
 %Purpose (and a bit of problem statement)
-Due to the negative implications that modifications to to APIs cause for API users, it is important to understand why changes to APIs occur.
+Due to the negative implications that modifications to APIs cause for its users, it is important to understand why changes to them occur.
 If most common pitfalls are known before the development of new APIs begin, these mistakes could be mitigated.
@@
 
+%Didn't change:
+%* 'the motive behind...' behind what? I get the grammar, but drop 'behind', methinks
+
 \subsection{Research Questions}
@@
 \item RQ1: What drives API evolution? 
-\item RQ1.1: To what extent can we reverse engineer API change decisions?
+\item RQ2: To what extent can we reverse engineer API change decisions?
 %\item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
@@
 This discipline is discussed in Section 2.1.
-The motives and effects of changes to APIs is directly related related to the fields of software evolution and software ecosystems.
+The motives and effects of changes to APIs are directly related to the fields of software evolution and software ecosystems.
 This will be discussed in Section 2.2.
@@
 
-API design is notoriously difficult as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective} \cite{afonso2012evaluating} \cite{stylos2006comparing}.
-In previous research generalisable usability studies have been created, with the aim of analysing the design decisions taken when creating an API \cite{stylos2006comparing}.
+API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective} \cite{afonso2012evaluating} \cite{stylos2006comparing}.
+In previous research, generalisable usability studies have been created, with the aim of analysing the design decisions taken when creating an API \cite{stylos2006comparing}.
 Another empirical study, which involved working with 25 programmers, highlighted API design problems such as assigning names to API features and difficulty in naming types \cite{shi2011empirical}.
@@
 
-Furthermore, a study of the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}.
+Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}.
 The study aimed to discover if APIs with high rates of faults affected the success of an application.
@@
 The applicability of case studies in such scenarios is supported by existing studies \cite{runeson2009guidelines} \cite{benbasat1987case} \cite{yin2013case} \cite{robson2002real}.
-An alternative approach that was considered was design research, but if a ``toy program" was to be used instead of an API tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines} [Note to reviewer \#3: Do you think this is a valid reason?
+An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines} [Note to reviewer \#3: Do you think this is a valid reason?
 Or does it imply that all design research involves toy programs?].
-
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to answer RQ1.1.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to answer RQ2.
 
@@
 \textit{Internal validity} threats for our study have been greatly reduced by the methodologies we have employed.
-By performing a individual inspection of  the API source code, documentation and individual results analysis, internal validity is significantly reduced.
-Triangulation of the results with the use of interviewing the architects is key step in reducing potential validity threats in our study.
+By performing an individual inspection of  the API source code, documentation and individual results analysis, internal validity is significantly reduced.
+Triangulation of the results with the use of interviewing the architects is a key step in reducing potential validity threats in our study.
 

### 2015-03-21 ibp/ibp.tex
Added ibp

\documentclass{article}

\usepackage[utf]{inputenc}
\usepackage{url}
\title{Industrial Best Practice}

\begin{document}

\author{John Burchell \qquad William Granli \\
		john.a.burchell@gmail.com \qquad william.granli@gmail.com \\
		Computer Science and Engineering  \\
		University of Gothenburg }

\maketitle
\section{Executive Summary, 1p}
Do this last!

\section{Problem Formulation, 3p}

\begin{itemize}
	\item Description of what problem you are trying to solve
	\item The description should highlight why the problem is important, for whom it is important and how it advances the state of the art/company business
	\item Description of similar solutions available for the market
\end{itemize}

\section{Roadmap and Plan, 5p}

\begin{itemize}
	\item Description on how to solve the problem using a roadmap
	\item If the solution is a model – how to develop, implement, adopt, evaluate, etc.
	\item Project plan for the solution – the time scale can be thesis work or another project
\end{itemize}

\url{http://en.wikipedia.org/wiki/Technology_roadmap}

\section{Dissemination plan, 2p}

\begin{itemize}
	\item Description on how to present/sell the solution to the company
	\item Description on how to communicate the solution
\end{itemize}

\url{http://www.webarchive.org.uk/wayback/archive/20140614222502/http://www.jisc.ac.uk/fundingopportunities/projectmanagement/planning/dissemination.aspx}

\section{Impact assessment, 2p}

\begin{itemize}
	\item Description of how the solution advances the state of the art
	\item Description of how the solution advances the society in general (e.g. better cars, faster mobiles)
\end{itemize}

\url{http://en.wikipedia.org/wiki/Impact_assessment}

\section{Summary, 1p}

\begin{itemize}
	\item Account of how you can use the knowledge from the course in your further work
\end{itemize}

\end{document}

### 2015-03-21 ibp/ibp.tex
Roadmap pic

@@
 
+\usepackage{rotating}
+\usepackage{graphicx}
 \usepackage[utf]{inputenc}
@@
 \section{Roadmap and Plan, 5p}
+\subsection{Designing the Roadmap}
+Workshop 1 - Market
+*Performance dimensions
+*Market/business drivers
+*Prioritisation
+*Gaps
+
+Workshop 2 - Product
+*Product feature concepts
+*Grouping
+*Impact ranking
+*Product strategy
+*Gaps
+
+Workshop 3 - Technology
+*Technology solutions
+*Grouping
+*Impact ranking
+
+Workshop 4 - Roadmapping
+*Linking technology resources to future market opportunities
+*Gaps
+
+\begin{sidewaysfigure}[ht]
+\centering
+\includegraphics[width=220mm]{RoadMap.png}
+\caption{The full lines denote in which way the organisation should ``logically'' view the roadmap. The dotted lines denote that one activity will lead to another. }
+\end{sidewaysfigure}
+%TODO: Add colours+graphix, extend dotted borders to left side as well, add x+y axes.
 

### 2015-03-21 ibp/ibp.tex
v1 of roadmap

--- 2015-03-21 ibp/ibp.tex
@@
 
+\usepackage{rotating}
+\usepackage{graphicx}
 \usepackage[utf]{inputenc}
 \usepackage{url}
+
 \title{Industrial Best Practice}
@@
 
+\url{http://unilearning.uow.edu.au/report/4bi1.html}
+
 \section{Problem Formulation, 3p}
@@
 
-\section{Roadmap and Plan, 5p}
+\section{Plan and Roadmap, 5p}
+As mentioned in Section 2, the effects mo ifications to APIs have on the platform’s ecosystem are explored as being negative.
+However, there are no existing systematic guidelines or framewor s that take the ecosystem into account for how to best modify an API.
+Our proposed process for creating such a framework will be can be seen in Figure \ref{fig:roadmap}.
+This is an initial version of the roadmap \cite{!!!roadmap}, and it is advised that it is updated dur ng the process.
+The main reason for this is that it is impo tant to adapt to changes in the market, and if new needs are identified, the strategy should be redesigned to meet them.
 
-\begin{itemize}
-	\item Description on how to solve the problem using a roadmap
-	\item If the solution is a model – how to develop, implement, adopt, evaluate, etc.
-	\item Project plan for the solution – the time scale can be thesis work or another project
-\end{itemize}
+\subsection{Designing the Roadmap}
+The roadmap was developed using the standard T-Plan process \cite{!!!roadmap}.
+As such, identifying the market need was done as a part of the initial step.
+Following that, the products and technology needed to fill that gap were identified.
+As a final step the dependencies and ordering of the identified activites were sorted out which resulted in the current version of the roadmap.
+An overview of the process used to create the roadmap can be seen in Table \ref{tab:proc}
 
-\url{http://en.wikipedia.org/wiki/Technology_roadmap}
+\begin{table}[ht]
+\centering
+\begin{tabular}[ht]{|c|l|l|}
+\hline
+\textbf{\#} & \textbf{Phase} & \textbf{Description} \\
+\hline
+1 & External & Identify the market needs \\
+\hline
+2 & Products & Identify required studies \& frameworks \\
+\hline
+3 & Technology & Identify required knowledge \\
+\hline
+4 & Organize & Identify what pull factors require which push factors \\
+\hline
+\end{tabular}
+\caption{Roadmap Design Process}
+\label{tab:proc}
+\end{table}
 
-\section{Dissemination plan, 2p}
+\subsection{Knowledge Development}
+Since we have made the assessment that the market need will remain relatively stable, careful research is essential to be able to deliver a product that meets the market needs.
+The main way of performing the initial study, to be able to increase the knowledge, will be through studying the existing literature.
+The reason for this is that three fields (API design, software evolution and software ecoystems) are currently well-explored, but the correlation and relationship between them has not yet been identified.
+Therefore, these fields will be explored in literature and a set of ``best practices" will be gathered from each field.
+
+In addition to the literature review, a case study will be conducted to gather information from a state of the art company.
+The goal of the data collection made in the case study, will also be to gather a set of best practices for each of the three fields.
+This will be achieved by analysing the changes between two versions of the company's platform API.
+
+\subsection{Implementing the Framework}
+To be able to create a framework which uses as much as possible of the knowledge and technology that exists in the world, the results from the literature review and the case study will both be analysed and compared.
+A set of best practices based on both data collections will be defined and become the basis for the framework.
+That we bring in important factors from each of the three fields in the discussion is of the highest importance.
+The goal of this phase is to create an Minimum Viable Product (MVP) that can be adopted and evaluated at the case company.
+
+\subsection{Adoption and Evaluation}
+The final stage of the roadmap will take a more iterative approach, where the MVP will be continuously evaluated and improved at the case company.
+The main way of evaluating the success of the framework will be to measure if there is an decrease in the negative effects that the API has on its ecosystem, while it still is able to remain its original complexity and usability.
+
+\begin{sidewaysfigure}[p]
+\centering
+\includegraphics[width=220mm]{RoadMap.png}
+\caption{The full lines denote in which way the organisation should ``logically'' view the roadmap. The dotted lines denote that one activity will lead to another. }
+\label{fig:roadmap}
+\end{sidewaysfigure}
+%TODO: Add colours+graphix so that it's innovative and stuff
+
+\section{Dissemination Plan, 2p}
 
@@
 
-\section{Impact assessment, 2p}
+\section{Impact Assessment, 2p}
 

### 2015-03-22 ibp/ibp.tex
started impact ass

@@
 
+%8.5 pages is 60% 14 pages, which is the max
 \title{Industrial Best Practice}
@@
 \section{Plan and Roadmap, 5p}
-As mentioned in Section 2, the effects mo ifications to APIs have on the platform’s ecosystem are explored as being negative.
-However, there are no existing systematic guidelines or framewor s that take the ecosystem into account for how to best modify an API.
+As mentioned in Section 2, the effects modifications to APIs have on the platform’s ecosystem are explored as being negative.
+However, there are no existing systematic guidelines or framework s that take the ecosystem into account for how to best modify an API.
 Our proposed process for creating such a framework will be can be seen in Figure \ref{fig:roadmap}.
-This is an initial version of the roadmap \cite{!!!roadmap}, and it is advised that it is updated dur ng the process.
-The main reason for this is that it is impo tant to adapt to changes in the market, and if new needs are identified, the strategy should be redesigned to meet them.
+This is an initial version of the roadmap \cite{!!!roadmap}, and it is advised that it is updated during the process.
+The main reason for this is that it is important to adapt to changes in the market, and if new needs are identified, the strategy should be redesigned to meet them.
 
@@
 Following that, the products and technology needed to fill that gap were identified.
-As a final step the dependencies and ordering of the identified activites were sorted out which resulted in the current version of the roadmap.
+As a final step the dependencies and ordering of the identified activities were sorted out which resulted in the current version of the roadmap.
 An overview of the process used to create the roadmap can be seen in Table \ref{tab:proc}
@@
 \hline
-4 & Organize & Identify what pull factors require which push factors \\
+4 & Organise & Identify what pull factors require which push factors \\
 \hline
@@
 The main way of performing the initial study, to be able to increase the knowledge, will be through studying the existing literature.
-The reason for this is that three fields (API design, software evolution and software ecoystems) are currently well-explored, but the correlation and relationship between them has not yet been identified.
+The reason for this is that three fields (API design, software evolution and software ecosystems) are currently well-explored, but the correlation and relationship between them has not yet been identified.
 Therefore, these fields will be explored in literature and a set of ``best practices" will be gathered from each field.
@@
 
-\url{http://www.webarchive.org.uk/wayback/archive/20140614222502/http://www.jisc.ac.uk/fundingopportunities/projectmanagement/planning/dissemination.aspx}
+Research findings and products—What is going to be disseminated?
+
+II.
+End users—Who will apply it in practice?
+
+III.
+Dissemination partners—Individuals, organisations or networks through whom you can reach end users?
+
+IV.
+Communication—How you convey the research outcomes?
+
+V.
+Evaluation—How you determine what worked?
+
+VI.
+Dissemination work plan—Where you start?
+\newpage
 
 \section{Impact Assessment, 2p}
+This section will describe the impact that our framework will have.
+
+\subsection{Now}
+The key impact of our new API framework would be that it would transform the way companies and organisations motivate their design decisions for APIs.
+Today's software engineering companies mainly take into account their own agendas, and APIs are commonly changes for refactoring reasons or to reduce complexity.
+The most important factor when designing or changing APIs is, however, the users of the API and their needs.
+In the recent years, this has been realised by the software engineering industry.
+This has lead to less deprecations in the code of the API users.
+
+\subsection{Impact on Technology and State of the Art}
+The next step that we propose the industry takes, is to weigh the needs of the whole ecosystem in the assessment when creating APIs.
+This would lead to a more homogeneous environment where API platforms and API users can change their code jointly, to reduce the risk of deprecating for example methods.
+The impact of this could even be that companies start changing and improving their APIs to help the ecosystem, and thus causing a domino effect in the ecosystem which can even spread to other ecosystems.
+Probable areas where this could have an especially great impact would be in the areas of web development APIs, since they are widely used by a great amount of users.
+Another reason that web APIs would be impacted is that very clear boundaries between the ecosystems exist.
+The toolchain in web development is usually referred to as a ``stack" which literally is a set of frameworks and APIs that you use together to develop your application.
+
+\subsection{Impact on Society}
+If companies start developing their APIs to fit the needs of ecosystems, it would not only have a great impact on these specific isolated environments; it would develop the whole software engineering industry.
+In modern software development, very few applications are written without the use of APIs, and this means if APIs become better; it can increase the performance of software development.
+It might be hard to
+
+This would have an especially great impact in web development APIs or programming language APIs.
+
+*The key difference is that changes to APIs will not only be motivated for internal reasons, but also to help develop the whole ecosystem 
+*This means that companies can help develop the environment they are in, and if done on a large scale it will drastically develop the world of software.
 

### 2015-03-22 ibp/ibp.tex
v1 of impact azz

@@
 
-\subsection{Now}
+\subsection{Background}
 The key impact of our new API framework would be that it would transform the way companies and organisations motivate their design decisions for APIs.
@@
 In modern software development, very few applications are written without the use of APIs, and this means if APIs become better; it can increase the performance of software development.
-It might be hard to
-
-This would have an especially great impact in web development APIs or programming language APIs.
-
-*The key difference is that changes to APIs will not only be motivated for internal reasons, but also to help develop the whole ecosystem 
-*This means that companies can help develop the environment they are in, and if done on a large scale it will drastically develop the world of software.
-
-\begin{itemize}
-	\item Description of how the solution advances the state of the art
-	\item Description of how the solution advances the society in general (e.g. better cars, faster mobiles)
-\end{itemize}
-
-\url{http://en.wikipedia.org/wiki/Impact_assessment}
+It might be hard to envision that companies would actually spend resources to help their ecosystem without helping themselves (directly).
+But examples of where similar things are happening can already be found today, and one example is that Ericsson are spending a lot of resources to develop open-source software such as Eclipse and Papyrus.
+If this would catch on, it would basically lead to a world where all software has better quality and is developed faster.
 

### 2015-03-22 ibp/ibp.tex
v1 dissemniationp lan

@@
 \section{Dissemination Plan, 2p}
+This section will describe the dissemination plan for our framework.
 
-\begin{itemize}
-	\item Description on how to present/sell the solution to the company
-	\item Description on how to communicate the solution
-\end{itemize}
+\subsection{End-users}
 
-Research findings and products—What is going to be disseminated?
+Two major end-users of our framework have been identified, 1) open-source projects and 2) web development APIs.
+The reason open-source projects have been identified as potential users of our API is that they generally have a good-will mindset when it comes to developing the software engineering industry.
+Their goals are not set on making profit, but delivering a product that is as good as possible.
+The open-source community also takes care of itself and thus it cares about the well-being of its ecosystems.
+The second area where this could have an especially great impact would be in the area of web development APIs, since they are widely used by a great amount of users.
+Another reason that web APIs would be impacted is that very clear boundaries between the ecosystems exist.
+The toolchain in web development is usually referred to as a ``stack" which literally is a set of frameworks and APIs that you use together to develop your application.
 
-II.
-End users—Who will apply it in practice?
+\subsection{Presentation and Communication}
+The main way of conveying our message would be through the research community.
+The initial studies that will be conducted (as mentioned in Section 3) will lead to a number of published research papers.
+These will be used to create awareness and attention of our framework.
+The papers may also lead to other researchers building on our research which would only help our cause which is to improve APIs everywhere.
 
-III.
-Dissemination partners—Individuals, organisations or networks through whom you can reach end users?
+In addition to reaching out to the research community, conferences related to web development would be targeted especially.
+One example of such a conference is JDays, where many APIs that are developed in JavaScript are discussed.
+The main reason for targeting such conferences is that a large part of the important persons of the community attend.
+This would help to create further awereness and publicity.
 
-IV.
-Communication—How you convey the research outcomes?
-
-V.
-Evaluation—How you determine what worked?
-
-VI.
-Dissemination work plan—Where you start?
-\newpage
+The last way of presenting our framework would be through directly targeting a set of companies that operate in the same software ecosystem.
+One example of that would be to target a company which develops a game engine, and at the same time contact the most prominent game developers which utilise this game engine.
+If the company developing the game engine realises that there is large interest from the main users of their API, it is much more likely that they would be interested in using our API.
 
@@
 The impact of this could even be that companies start changing and improving their APIs to help the ecosystem, and thus causing a domino effect in the ecosystem which can even spread to other ecosystems.
-Probable areas where this could have an especially great impact would be in the areas of web development APIs, since they are widely used by a great amount of users.
-Another reason that web APIs would be impacted is that very clear boundaries between the ecosystems exist.
-The toolchain in web development is usually referred to as a ``stack" which literally is a set of frameworks and APIs that you use together to develop your application.
 

### 2015-03-22 ibp/ibp.tex
Description
Added first stuff for the starting section - Might have to add more
about the companies

@@
 
+As the software industry and the open source movement steadily grow, the number of publicly available APIs is increasing.
+APIs can improve development speed \cite{stylos2006comparing}, improve software quality \cite{stylos2006comparing} and can increase software reusability \cite{afonso2012evaluating}.
+There is a consensus amount literature and experts that modifications to deployed APIs can have negative impacts on the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
+The main reason is that it will require the users to update the code using the API, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
+The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}.
+
+The problem, put simply, is this; how can effective changes be made to deployed APIs with minimal impact upon the ecosystem in which the API is utilised?
+
+%Highlight problem and who it's for here.
+Having a stable and well designed API is vital to the success of a company or product, especially if they are built around a particular API.
+For example, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}.
+The study aimed to discover if APIs with high rates of faults affected the success of an application.
+The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.
+
+Due to the negative implications that modifications to APIs cause for users, it is important to understand why changes occur.
+If the most common pitfalls are known before the development of new APIs begin, these mistakes could be mitigated.
+Likewise, if common dangers of changes to existing APIs are fully studied and understood, informed changes can be made to lessen the affect on the users.
+Furthermore, industry and academia can use these lessons learned to create, or enhance existing best practices of API design.
+
+Given that software is prevalent in our lives, it is likely that poor API design changes have affected our lives at some point.
+One could therefore argue that this problem is important to everyone; customers, businesses and developers.
+
+%This needs fluffing
+Our solution is to provide a set of guidelines, or framework with which to follow when making changes to APIs. The framework will prioritise business motives and needs when tackling design decisions.
+
+Exhaustive research has found that there exists very few similar soultions similar to our own.
+While there are countless books related to the subject [!!!list some?], very few actually aim to address the needs of busniness and customers; they are primarily focused on the developer.
+
+%Examples of similar products
+Apiary is a popular online API design service.
+Apiary focuses on a collaborative approach to creating APIs, the tool offers the ability to work with between 5 and 50 contributors on a single project.
+The unique part of this tool is that it provides a "mock" API by which customers, developers or anyone with access can work with.
+This stage allows quick prototyping and testing of an API before any real coding has taken place.
+The tool, while useful, doesn't aim to solve the problem of handling changes to APIs but is instead a good platform to quickly prototype ideas.
+
+Mashery provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:
+
+Increase productivity through uniformity and accessibility of data
+Develop better customer experiences faster, for mobile and web-based applications
+Achieve real-time data exchange between platforms and applications
+Enhance visibility into data consumption to optimize APIs
+
+While mashery have a more business oriented approach, they do not offer anything resembling a framework for both business and developers to use when making API design decisions.
+
 \begin{itemize}
@@
 As mentioned in Section 2, the effects modifications to APIs have on the platform’s ecosystem are explored as being negative.
-However, there are no existing systematic guidelines or framework s that take the ecosystem into account for how to best modify an API.
-Our proposed process for creating such a framework will be can be seen in Figure \ref{fig:roadmap}.
+However, there are no existing systematic guidelines or frameworks that take the ecosystem into account for how to best modify an API.
+Our proposed process for creating such a framework can be seen in Figure \ref{fig:roadmap}.
 This is an initial version of the roadmap \cite{!!!roadmap}, and it is advised that it is updated during the process.

### 2015-03-22 ibp/ibp.tex
typos fixed

@@
 
-Exhaustive research has found that there exists very few similar soultions similar to our own.
-While there are countless books related to the subject [!!!list some?], very few actually aim to address the needs of busniness and customers; they are primarily focused on the developer.
+Exhaustive research has found that there exists very few similar solutions similar to our own.
+While there are countless books related to the subject [!!!list some?], very few actually aim to address the needs of business and customers; they are primarily focused on the developer.
 
 %Examples of similar products
+\subsection{Related Products}
+% http://apiary.io/products
 Apiary is a popular online API design service.
@@
 The tool, while useful, doesn't aim to solve the problem of handling changes to APIs but is instead a good platform to quickly prototype ideas.
+Apiary also includes some Github integration adding to it's already strong collaboration tools.
 
+%http://www.mashery.com
 Mashery provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:
@@
 While mashery have a more business oriented approach, they do not offer anything resembling a framework for both business and developers to use when making API design decisions.
+
+%http://swagger.io/
+Swagger 2.0 is another online design tool for APIs.
+Swagger has the added bonus of including a "Generator" for creating some basic library code for users to build upon.
+Swagger, online Apiary, is primarily used for RESTful APIs.
+Similarly to the previously mentioned companies, Swagger is more of a tool solution rather than a guideline or framework.
 

### 2015-03-23 ibp/ibp.tex
0rd or 0st or 0th

--- 2015-03-22 ibp/ibp.tex
@@
 
-%8.5 pages is 60% 14 pages, which is the max
+%8.5 pages is 60% 14 (max) pages
 \title{Industrial Best Practice}
@@
 \section{Problem Formulation, 3p}
+This section will describe the problem that we are trying to solve, why it is important and what related products exist on the market today.
+
+\subsection{Description of the Problem}
 
@@
 APIs can improve development speed \cite{stylos2006comparing}, improve software quality \cite{stylos2006comparing} and can increase software reusability \cite{afonso2012evaluating}.
-There is a consensus amount literature and experts that modifications to deployed APIs can have negative impacts on the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
+There is a consensus among literature and experts that modifications to deployed APIs can have negative impacts on the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
 The main reason is that it will require the users to update the code using the API, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
@@
 %Highlight problem and who it's for here.
+\subsection{Why is this important?}
 Having a stable and well designed API is vital to the success of a company or product, especially if they are built around a particular API.
@@
 
-Exhaustive research has found that there exists very few similar soultions similar to our own.
-While there are countless books related to the subject [!!!list some?], very few actually aim to address the needs of busniness and customers; they are primarily focused on the developer.
+\subsection{Related Products}
+Exhaustive research has found that there exists very few similar solutions similar to our own.
+While there are countless books related to the subject, very few actually aim to address the needs of busniness and customers; they are primarily focused on the developer.
 
-%Examples of similar products
 Apiary is a popular online API design service.
 Apiary focuses on a collaborative approach to creating APIs, the tool offers the ability to work with between 5 and 50 contributors on a single project.
-The unique part of this tool is that it provides a "mock" API by which customers, developers or anyone with access can work with.
+The unique part of this tool is that it provides a ``mock" API by which customers, developers or anyone with access can work with.
 This stage allows quick prototyping and testing of an API before any real coding has taken place.
@@
 
-Increase productivity through uniformity and accessibility of data
-Develop better customer experiences faster, for mobile and web-based applications
-Achieve real-time data exchange between platforms and applications
-Enhance visibility into data consumption to optimize APIs
+\begin{itemize}
+\item Increase productivity through uniformity and accessibility of data
+\item Develop better customer experiences faster, for mobile and web-based applications
+\item Achieve real-time data exchange between platforms and applications
+\item Enhance visibility into data consumption to optimize APIs
+\end{itemize}
 
 While mashery have a more business oriented approach, they do not offer anything resembling a framework for both business and developers to use when making API design decisions.
-
-\begin{itemize}
-	\item Description of what problem you are trying to solve
-	\item The description should highlight why the problem is important, for whom it is important and how it advances the state of the art/company business
-	\item Description of similar solutions available for the market
-\end{itemize}
 
@@
 Our proposed process for creating such a framework can be seen in Figure \ref{fig:roadmap}.
-This is an initial version of the roadmap \cite{!!!roadmap}, and it is advised that it is updated during the process.
+This is an initial version of the roadmap \cite{phaal2004technology}, and it is advised that it is updated during the process.
 The main reason for this is that it is important to adapt to changes in the market, and if new needs are identified, the strategy should be redesigned to meet them.
@@
 \subsection{Designing the Roadmap}
-The roadmap was developed using the standard T-Plan process \cite{!!!roadmap}.
+The roadmap was developed using the standard T-Plan process \cite{phaal2004technology}.
 As such, identifying the market need was done as a part of the initial step.
@@
 
+\bibliographystyle{bib}
+\bibliography{bib}
+
 \end{document}

### 2015-03-23 ibp/ibp.tex
Updated work

@@
 \section{Executive Summary, 1p}
-Do this last!
+This report presents a plan for how to develop and distribute a framework for designing and improving APIs in the context of software evolution and software ecosystems.
 
-\url{http://unilearning.uow.edu.au/report/4bi1.html}
+\url{http://unilearning.uow.edu.au/report/4bi1.html	}
 
@@
 \subsection{Knowledge Development}
-Since we have made the assessment that the market need will remain relatively stable, careful research is essential to be able to deliver a product that meets the market needs.
-The main way of performing the initial study, to be able to increase the knowledge, will be through studying the existing literature.
-The reason for this is that three fields (API design, software evolution and software ecosystems) are currently well-explored, but the correlation and relationship between them has not yet been identified.
-Therefore, these fields will be explored in literature and a set of ``best practices" will be gathered from each field.
+Since we have made the assessment that the market need will to remain relatively stable, careful research is essential to be able to deliver a product that meets the market needs.
+The primary method of performing the initial study, to be able to improve knowledge, will be through studying the existing literature.
+The reason for this is that three fields, API design, software evolution and software ecosystems, are currently well-explored, but the correlation and relationship between them has not yet been identified.
+Therefore, these fields will be explored in literature and a set of ``best practices" will be gathered from each of them.
 
-In addition to the literature review, a case study will be conducted to gather information from a state of the art company.
-The goal of the data collection made in the case study, will also be to gather a set of best practices for each of the three fields.
-This will be achieved by analysing the changes between two versions of the company's platform API.
+In addition to the literature review, a case study will be conducted to gather information from a company leading its field.
+The goal of the data collection performed in the case study will also be to gather a set of best practices for each of the three fields.
+To determine these best practices, an analysis of the companies current API and a future API will be performed.
+The changes between the two versions of the company's platform API will be of great significance and it is from these changes that we will base some of our best practices upon.
 
 \subsection{Implementing the Framework}
-To be able to create a framework which uses as much as possible of the knowledge and technology that exists in the world, the results from the literature review and the case study will both be analysed and compared.
-A set of best practices based on both data collections will be defined and become the basis for the framework.
-That we bring in important factors from each of the three fields in the discussion is of the highest importance.
-The goal of this phase is to create an Minimum Viable Product (MVP) that can be adopted and evaluated at the case company.
+In order to collate as much existing knowledge and research as possible, a thorough, extensive literature review will be conducted.
+This will be complimented by a case study which is shall be performed in conjunction with the previously mentioned case company.
+The results of both the review and the case study will be analysed and compared.
+A set of best practices, based on the data collected in the review and case study, will be used to create the basis of the framework that will make up our best practices.
+Bringing in important factors from each of the three fields in the discussion is of the highest importance.
+The goal of this phase is therefore to create an Minimum Viable Product (MVP) that can be adopted and evaluated at the case company.
 
 \subsection{Adoption and Evaluation}
-The final stage of the roadmap will take a more iterative approach, where the MVP will be continuously evaluated and improved at the case company.
-The main way of evaluating the success of the framework will be to measure if there is an decrease in the negative effects that the API has on its ecosystem, while it still is able to remain its original complexity and usability.
+The final stage of the roadmap will be performed using an iterative approach, where the MVP will be continuously evaluated and improved at the case company.
+The primary result of evaluating the success of the framework will be to measure if there is any visible reduction in the amount of negative effects that changes to an API has on its ecosystem, while retaining the original complexity and usability before the changes were made.
 
@@
 
-Two major end-users of our framework have been identified, 1) open-source projects and 2) web development APIs.
-The reason open-source projects have been identified as potential users of our API is that they generally have a good-will mindset when it comes to developing the software engineering industry.
-Their goals are not set on making profit, but delivering a product that is as good as possible.
-The open-source community also takes care of itself and thus it cares about the well-being of its ecosystems.
-The second area where this could have an especially great impact would be in the area of web development APIs, since they are widely used by a great amount of users.
-Another reason that web APIs would be impacted is that very clear boundaries between the ecosystems exist.
+Two immediate end-users of our framework have been identified, 1) open-source projects and 2) web development APIs.
+Open-source projects have been identified as potential users of our API as they generally have a good-will mindset when it comes to furthering and helping to improve the software engineering industry.
+Generally speaking, most open-source developers do no prioritise making a profit from their work, instead, they focus on delivering a product that is as complete and functional as possible.
+The open-source community is a well established and has existed for a long time, with a long tradition of autonomy, it can be said that they care about the well-being of their software ecosystems.
+
+The second area where this could have an especially great impact would be in the area of web development APIs.
+Web APIs are widely used by vast amount of developers, performing many varied tasks.
+The web is a constantly evolving and expanding market, as such many companies rise and fall based on the success of their API.
+Therefore, it's not surprising that changes to a web API have significant impacts on the ecosystems of the systems.
 The toolchain in web development is usually referred to as a ``stack" which literally is a set of frameworks and APIs that you use together to develop your application.
@@
 \subsection{Presentation and Communication}
-The main way of conveying our message would be through the research community.
+The most appropriate method of conveying our message and findings would be through the research community.
 The initial studies that will be conducted (as mentioned in Section 3) will lead to a number of published research papers.
-These will be used to create awareness and attention of our framework.
-The papers may also lead to other researchers building on our research which would only help our cause which is to improve APIs everywhere.
+These papers will be used to generate awareness and attention of our framework and the successes that it can bring.
+The papers may propagate research and act as a stepping stone for other research.
+Other researchers could quite easily build upon the research which we have conducted.
+The outcome of which would only help our cause; to improve APIs everywhere.
 
-In addition to reaching out to the research community, conferences related to web development would be targeted especially.
+In addition to reaching out to the research community, conferences, especially those related to web development, would be targeted for publication.
 One example of such a conference is JDays, where many APIs that are developed in JavaScript are discussed.
-The main reason for targeting such conferences is that a large part of the important persons of the community attend.
-This would help to create further awereness and publicity.
+The main reason for targeting such conferences is that, generally speaking, these types of conferences tend to attract the prominent figures in a particular industry or a narrower aspect of it.
+Bringing this to the awareness of these key players would help to create further awareness and publicity of the research, and by association, the best practices that we shall develop.
 

### 2015-03-23 ibp/ibp.tex
Reviewed whole doc, added more stuff

@@
 \subsection{Background}
-The key impact of our new API framework would be that it would transform the way companies and organisations motivate their design decisions for APIs.
-Today's software engineering companies mainly take into account their own agendas, and APIs are commonly changes for refactoring reasons or to reduce complexity.
-The most important factor when designing or changing APIs is, however, the users of the API and their needs.
+The most significant impact of our new API framework would be that it could potentially transform the way companies and organisations motivate their design decisions for APIs.
+Today's software engineering companies mainly take into account their own agendas, and APIs are changed for refactoring reasons, such as name changes, or to reduce complexity.
+The most important factor when designing or changing APIs is, however, how the changes will impact the users of the API and how their needs are being met.
 In the recent years, this has been realised by the software engineering industry.
-This has lead to less deprecations in the code of the API users.
+As a result, the consensus is to have less deprecations when changing APIs and thus these changes have had their impact upon users reduced.
 
 \subsection{Impact on Technology and State of the Art}
-The next step that we propose the industry takes, is to weigh the needs of the whole ecosystem in the assessment when creating APIs.
-This would lead to a more homogeneous environment where API platforms and API users can change their code jointly, to reduce the risk of deprecating for example methods.
-The impact of this could even be that companies start changing and improving their APIs to help the ecosystem, and thus causing a domino effect in the ecosystem which can even spread to other ecosystems.
+The next step that we propose the industry takes, is to weigh the needs of the whole ecosystem and not just the immediate needs of the user when creating or modifying APIs.
+By doing this, a more homogeneous environment would be possible where API platforms and API users can change their code simultaneously.
+For example, it would have the potential to reduce the risks taken when deprecating methods as users and developers would be able to communicate their needs effectively.
+The impact of this could even be that companies begin changing and improving their APIs with the view of helping the ecosystem instead of purely their own immediate needs.
+This would have the potential to cause a a domino effect in the ecosystem which would hopefully spread to other ecosystems and ultimately would become a part of their overall software design process.
 
 \subsection{Impact on Society}
-If companies start developing their APIs to fit the needs of ecosystems, it would not only have a great impact on these specific isolated environments; it would develop the whole software engineering industry.
-In modern software development, very few applications are written without the use of APIs, and this means if APIs become better; it can increase the performance of software development.
-It might be hard to envision that companies would actually spend resources to help their ecosystem without helping themselves (directly).
-But examples of where similar things are happening can already be found today, and one example is that Ericsson are spending a lot of resources to develop open-source software such as Eclipse and Papyrus.
-If this would catch on, it would basically lead to a world where all software has better quality and is developed faster.
+If companies begin developing their APIs to fit the needs of ecosystems, it would not only have a great impact on these specific isolated environments; it would develop the whole software engineering industry.
+Therefore, the impact on society is potentially huge.
+Given that software is used by everyone, daily, improving software overall could improve peoples quality of life.
+
+In modern software development, very few applications are written without the use of APIs.
+The consequence of which means, if APIs are designed more thoroughly, software performance is likely to rise.
+It might be difficult to envision that companies would actually spend resources to help their ecosystem without seeing and direct and immediate improvements for themselves.
+However, examples of where similar changes are happening can already be found today.
+One example is Ericsson.
+Ericsson are spending a lot of resources to develop open-source software such as Eclipse and Papyrus.
+The improvement of this software helps Ericsson directly, as they are using the software themselves.
+However, by improving open source software, they inadvertently help anyone else who uses this software.
+If this trend were to catch on, it could potentially lead to a world where all software has higher quality and is developed faster.
 

### 2015-03-23 ibp/ibp.tex
Added some summary

@@
 \maketitle
-\section{Executive Summary, 1p}
+\section{Executive Summary}
 This report presents a plan for how to develop and distribute a framework for designing and improving APIs in the context of software evolution and software ecosystems.
 
-\url{http://unilearning.uow.edu.au/report/4bi1.html	}
+The research behind the framework has been made through reviewing existing literature, and through analysing changes between  different versions on an industry API.
+The main way of assessing the API has been through measuring the impact it has on its ecosystem.
+The development of the framework has been supported by a solid technology roadmap, dissemination plan and impact assessment.
 
-\section{Problem Formulation, 3p}
+The findings of our initial studies show that the changes to APIs have negative effects, and that they primarily affect the users of the API.
+They also show that modifications to APIs heavily influence the ecosystem.
+
+With this report we conclude that the improvement potential to the current ways of designing APIs is huge.
+This can especially be achieved by weighing in the needs of the whole ecosystem when designing APIs.
+We also conclude that there is a large need for a framework such as the one we are proposing, and that it could lead to major improvements in areas such as the open-source community and in web development.
+The three most important benefits of our paper are:
+
+\begin{itemize}
+\item Increased usability of your API
+\item Reduced negative impacts when changing your API
+\item A software ecosystem existing in symbiosis
+\end{itemize}
+
+One limitation to this report is that the development of the framework has not started yet, and that only the initial studies have been started.
+Another limitation is that the no extensive research on whether or not companies have the desire spend resources that do not have an immediate impact on their revenue.
+
+\section{Problem Formulation}
 This section will describe the problem that we are trying to solve, why it is important and what related products exist on the market today.
@@
 Exhaustive research has found that there exists very few similar solutions similar to our own.
-While there are countless books related to the subject, very few actually aim to address the needs of busniness and customers; they are primarily focused on the developer.
+While there are countless books related to the subject, very few actually aim to address the needs of business and customers; they are primarily focused on the developer.
 
@@
 \item Achieve real-time data exchange between platforms and applications
-\item Enhance visibility into data consumption to optimize APIs
+\item Enhance visibility into data consumption to optimise APIs
 \end{itemize}
 
-While mashery have a more business oriented approach, they do not offer anything resembling a framework for both business and developers to use when making API design decisions.
+While Mashery have a more business oriented approach, they do not offer anything resembling a framework for both business and developers to use when making API design decisions.
 
-\section{Plan and Roadmap, 5p}
+\section{Plan and Roadmap}
 As mentioned in Section 2, the effects modifications to APIs have on the platform’s ecosystem are explored as being negative.
@@
 
-\section{Impact Assessment, 2p}
+\section{Impact Assessment}
 This section will describe the impact that our framework will have.
@@
 
+The knowledge gained from the course has had both immediate and long term effects.
+Immediately, we were able to use the information regarding finding research topics, collaborating with industry and performing research.
+These topics were invaluable for us when it came to finding a research topic and company for our thesis.
+In regards to the long term value, information for working at a company or in a professional environment will undoubtedly be of use for us.
+
+The guest lectures were very useful as we received first hand accounts of how research is conducted within industry.
+This was particularly valuable given how our our solution is heavily involved with research and academia.
+If either of us wish to pursue a career in research, we now have some idea of what it would require and to some extent what it might be like to do so.
+
+The second guest lecture was also of great help when for this report. The methods and ideas presented were vital in helping us generate ideas and solutions to our given problem.
+
 \begin{itemize}

### 2015-03-23 ibp/ibp.tex
Changes in section 3

@@
 
+Once this information has been fully analysed and documented, with the best practices found, the framework can be created in full.
+The framework needs to be language agnostic and apply to no specific technical area, rather it should be applicable to all.
+
 \subsection{Adoption and Evaluation}
@@
 The primary result of evaluating the success of the framework will be to measure if there is any visible reduction in the amount of negative effects that changes to an API has on its ecosystem, while retaining the original complexity and usability before the changes were made.
+
+To ease the adoption process, a series of tests and evaluations will be performed on pilot studies.
+The goal of these pilot studies would be to verify and improve the best practices.
+For example, we will perform an analysis of an exist API and it's changes against an existing framework.
+We will then apply our framework and best practices to see if our framework suggests better and more robust changes, taking into account the affects of these changes on the ecosystem.
+Feedback will then be collected from the company who owns the API based on our frameworks suggested changes.
+This will be done to determine if our suggested changes are achieving the same goals as their changes would have done.
 

### 2015-03-23 ibp/ibp.tex
finshd summary

@@
 
-\section{Summary, 1p}
-
-The knowledge gained from the course has had both immediate and long term effects.
+\section{Summary}
+The knowledge gained from the course has had both immediate and long term benefits.
 Immediately, we were able to use the information regarding finding research topics, collaborating with industry and performing research.
@@
 
-\begin{itemize}
-	\item Account of how you can use the knowledge from the course in your further work
-\end{itemize}
+The course has thought us how to apply the theoretical knowledge we have in a business setting.
+Other courses, such as pure programming courses, only teach you how to do something in theory but not how to use the skills in projects or at a company.
+This course in combination with the project courses will definitely help us in that.
+
+Another more practical use of this course will be that it will help us to take a more structured and systematic approach in planning our career.
+Before we have only set goals that are quite loose and undefined, but now we can use real industry methods such as roadmaps to structure our career plan.
+This will definitely help us to choose a wiser path in our career and hopefully help us to find a job that suits us!
 

### 2015-03-23 rmtw/a6_review/latex8.tex
a6 rev

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: John Burchell & William Granli $
%  $Date: 2015/01/21 15:20:59 $
%  $Revision: 1.0
%

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{url}
\usepackage{tabularx}
\usepackage{appendix}
\usepackage{pbox}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{Review of Group 10 by Group 1}

% author names and affiliations
\author{John Burchell and William Granli \\
john.a.burchell@gmail.com, william.granli@gmail.com}

\maketitle
\thispagestyle{empty}

\section{Title}

The title could be improved. The current one doesn't describe the connection you will make between working climate and gender aspects. An example would be: ``Comparing and Contrasting the Perception of Work Climate Between Sexes". We would use the word work instead of working and the  word sex instead of gender. Gender is usually used in grammar and sex when talking about men and women.

\section{Introduction}
The first sentence of the paper is incorrectly cited. The paper mentions the engineering profession in general but you write ``computer science". The paper also only has 1 cite, so you should probably reconsider the quality of it.

There is no clear problem statement. (We assume that you 2nd paragraph is the problem statement). Make it more clear and define an explicit problem.

You should also consider adding a bit more references to back up your statements and to show that there has been more than 1 paper in an area. (Add several references to 1 sentence). If you can't find more papers, state that in your study so that it is clear to the reader.

\section{Related Work}
The stuff about schools/education and pair programming seems a bit unrelated to your topic. If it is relevant, make the connection more clear.

\section{Purpose}
Very good! Clear and explains what it should!

\section{Case Company Description}
The first sentence gives the impression that your study is something negative for the company. You could reword this to ``The company involved has wished to remain anonymous due to internal policies".

A good general intro to the company. You should, however, explain why this case is well-suited to perform gender studies at. (For example, the 25\% thing is a good reason, so that could be mentioned a bit more clearly). You should also explain what criteria you used for selecting the case company and how they were sampled.

\section{Methodology}
``We have created some key area": You need to argue why these are the most optimal to answer your research questions. Why were they chosen? Please also explain what all the areas mean in this context. ``Knowledge'', for example is quite ambiguous.

Is there a clear difference between sub-questions a, b and c? It seems like a should bring up everything that b and c answers. The sub-questions should also be re-written so that they are full and standalone questions.

The paragraph after the research questions: The arguments  are a bit hard to follow, consider improving this paragraph. The next section is very good!

\subsection{Data Collection}
You use the word convenient, and it sounds like you are doing things to make it easy for yourself. Try to reword this. (We assume it wasn't your intention).

Try to explain why these data collection methods are good to answer your research questions. E.g. why are interviews needed to answer your specific questions?

Otherwise the section is good!

\subsection{Data Analysis}
One of your best sections, except the last part. You mention your company's initiative to increase the number of female managers etc. This probably reduces the validity of your study since it introduces bias in the data you are analysing, so keep this in mind.

\subsection{Validity Threats}
Have a look at the [Case] paper. It has a really good explanation on how to write these sections for case studies. You should probably explain how you would counteract bias towards publishing results that are positive for one of the genders. (For example, that there is bias in something which would lead to positive results about men). Since this is a central part of your study. Also explain how you have counteracted that bias.

The final validity threat (about career and political correctness) is really good!

\end{document}

### 2015-03-24 rmtw/a5/latex8.tex
fixes to a5
Added table of search keywords

@@
 
-\SubSection{Statement of the Problem}
-
 The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the system requirements are and in what environment the system is being developed.
@@
 
-\SubSection{Existing Literature}
+Academia appears to be united in the opinion that MDSD is an improvement compared with traditional software development \cite{staron2006adopting} \cite{volter2013model}.
+However, why do many large software companies choose to not adopt MDSD?
+
+This gap in the literature is the motivation for our study.
+There is therefore a need to methodically investigate the existing literature in which studies of the adoption of MDSD, advantages and disadvantages of MDSD are explored.
+Not only this but how and when should MDSD be adopted and how success can be assured.
+
+\SubSection{Research Questions}
+\begin{itemize}
+\item \textbf{RQ1:} In which situations should companies expect that changing to MDSD would lead to positive effects? 
+\item \textbf{RQ1.1:} In which domain(s) is MDSD the most successful? 
+\item \textbf{RQ1.2:} Which software development process(es) has been most successfully used in conjunction with MDSD?
+\item \textbf{RQ1.3:} What are the characteristics of the systems of the companies that successfully use MDSD?
+\item \textbf{RQ1.4:} Which change strategy has most been successful in implementing MDSD? 
+\end{itemize}
+
+\SubSection{Related Work}
 
@@
 If this has to be performed manually, it will become a bottleneck in large MDSD projects \cite{mattsson2009linking}.
-
-\SubSection{Motivation for Study}
-
-Academia appears to be united in the opinion that MDSD is an improvement compared with traditional software development \cite{staron2006adopting} \cite{volter2013model}.
-However, why do many large software companies choose to not adopt MDSD?
-
-This gap in the literature is the motivation for our study.
-There is therefore a need to methodically investigate the existing literature in which studies of the adoption of MDSD, advantages and disadvantages of MDSD are explored.
-Not only this but how and when should MDSD be adopted and how success can be assured.
-
-\SubSection{Research Questions}
-\begin{itemize}
-\item \textbf{RQ1:} In which situations should companies expect that changing to MDSD would lead to positive effects? 
-\item \textbf{RQ1.1:} In which domain(s) is MDSD the most successful? 
-\item \textbf{RQ1.2:} Which software development process(es) has been most successfully used in conjunction with MDSD?
-\item \textbf{RQ1.3:} What are the characteristics of the systems of the companies that successfully use MDSD?
-\item \textbf{RQ1.4:} Which change strategy has most been successful in implementing MDSD? 
-\end{itemize}
 
@@
 
+\newpage
 \begin{appendices}
-\section{Search Terms}
-MDD, MDSD, model-driven software development, model-driven development, MDE, model-driven engineering, model driven engineering, code generation
+\section{Search Keywords}
+\begin{table}[Ht*]
+	\centering
+	\begin{tabular}{|l|l|} 
+		\hline
+		\textbf{Population} & \textbf{Intervention}  \\
+		\hline
+		``Model-Driven Software Development'' OR & ``Domain'' OR \\ 
+		``Model-Driven Development'' OR & ``Paradigm'' \\
+		``Model-Driven Engineering'' OR & \\
+		``Model Driven Engineering'' OR & \\
+		``MDD'' OR & \\
+		``MDSD'' OR & \\
+		``MDE'' & \\
+		\hline
+		\end{tabular}
+	\caption{Search Keywords}
+\end{table}
 \end{appendices}

### 2015-03-24 rmtw/a5/latex8.tex
rev a5

@@
 
-The search terms used can be found in Appendix A. The main search terms are related to MDSD, but related terms such as Model Driven Engineering and code generation were also included.
+The search keywords used can be found in Appendix A. The main search keywords are related to MDSD, but related keywords such as Model Driven Engineering and code generation were also included.
+\newline
 
-The inclusion criteria were defined as follows: \newline
+The inclusion criteria were defined as follows: 
 \begin{itemize} 
@@
 
-The exclusion criteria were defined as follows: \newline
+The reason only qualitative studies are included is that they are most appropriate for answering our research questions.
+This is also supported by Petticrew and Roberts who state that qualitative studies are well-suited for assessing whether a new technology is useful for the type of systems they have to build \cite{petticrew2008systematic}.
+\newline
+
+The exclusion criteria were defined as follows: 
 \begin{itemize}

### 2015-03-24 ibp/ibp.tex
yolo
changes to roadmap

@@
 %8.5 pages is 60% 14 (max) pages
-\title{Industrial Best Practice}
+\title{A Framework for Coping with API Evolution in a Software Ecosystem Setting}
 
@@
 \section{Executive Summary}
-This report presents a plan for how to develop and distribute a framework for designing and improving APIs in the context of software evolution and software ecosystems.
+This report presents a plan for how to develop and distribute a framework for designing and improving Application Programming Interfaces (APIs) in the context of software evolution and software ecosystems.
+\smallskip
 
@@
 The development of the framework has been supported by a solid technology roadmap, dissemination plan and impact assessment.
+\smallskip
 
@@
 They also show that modifications to APIs heavily influence the ecosystem.
+\smallskip
 
@@
 \begin{itemize}
-\item Increased usability of your API
-\item Reduced negative impacts when changing your API
+\item Increased usability APIs
+\item Reduced negative impacts when changing APIs
 \item A software ecosystem existing in symbiosis
@@
 
-The problem, put simply, is this; how can effective changes be made to deployed APIs with minimal impact upon the ecosystem in which the API is utilised?
+\subsection{Research Question}
+\begin{itemize}
+\item How can effective changes be made to deployed APIs with minimal impact upon the ecosystem in which the API is utilised?
+\end{itemize}
 
@@
 The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.
+\smallskip
 
@@
 Likewise, if common dangers of changes to existing APIs are fully studied and understood, informed changes can be made to lessen the affect on the users.
-Furthermore, industry and academia can use these lessons learned to create, or enhance existing best practices of API design.
+Furthermore, industry and academia can use these lessons learned to create, or enhance existing best practices of API design.\smallskip
 
@@
 One could therefore argue that this problem is important to everyone; customers, businesses and developers.
+\smallskip
 
 %This needs fluffing
-Our solution is to provide a set of guidelines, or framework with which to follow when making changes to APIs. The framework will prioritise business motives and needs when tackling design decisions.
+Our solution is to provide a set of guidelines, or framework with which to follow when making changes to APIs.
+The framework will prioritise business motives and needs when tackling design decisions.
+The framework will also take into account the business need, not only of the organisation which owns the API, but the business needs of all organisations existing in the ecosystem.
 
@@
 While there are countless books related to the subject, very few actually aim to address the needs of business and customers; they are primarily focused on the developer.
+\smallskip
 
@@
 The tool, while useful, doesn't aim to solve the problem of handling changes to APIs but is instead a good platform to quickly prototype ideas.
+\smallskip
 
-Mashery provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:
+Mashery provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they: \smallskip
 
@@
 Therefore, these fields will be explored in literature and a set of ``best practices" will be gathered from each of them.
+\smallskip
 
@@
 The changes between the two versions of the company's platform API will be of great significance and it is from these changes that we will base some of our best practices upon.
+\smallskip
 
@@
 The goal of this phase is therefore to create an Minimum Viable Product (MVP) that can be adopted and evaluated at the case company.
+\smallskip
 
@@
 The primary result of evaluating the success of the framework will be to measure if there is any visible reduction in the amount of negative effects that changes to an API has on its ecosystem, while retaining the original complexity and usability before the changes were made.
+\smallskip
 
@@
 The open-source community is a well established and has existed for a long time, with a long tradition of autonomy, it can be said that they care about the well-being of their software ecosystems.
+\smallskip
 
@@
 The outcome of which would only help our cause; to improve APIs everywhere.
+\smallskip
 
@@
 Bringing this to the awareness of these key players would help to create further awareness and publicity of the research, and by association, the best practices that we shall develop.
+\smallskip
 
@@
 \section{Impact Assessment}
-This section will describe the impact that our framework will have.
+This section will describe the impact that our framework will have on the business market and society in general.
 
@@
 Given that software is used by everyone, daily, improving software overall could improve peoples quality of life.
+\smallskip
 
@@
 In regards to the long term value, information for working at a company or in a professional environment will undoubtedly be of use for us.
+\smallskip
 
@@
 If either of us wish to pursue a career in research, we now have some idea of what it would require and to some extent what it might be like to do so.
+\smallskip
 
-The second guest lecture was also of great help when for this report. The methods and ideas presented were vital in helping us generate ideas and solutions to our given problem.
+The second guest lecture was also of great help when for this report. The methods and ideas presented were vital in helping us generate ideas and solutions to our given problem. \smallskip
 
@@
 This course in combination with the project courses will definitely help us in that.
+\smallskip
 

### 2015-03-24 ibp/ibp.tex
Made changes to Summary and state of the art. Added references in the bib to the websites that were also missing

--- 2015-03-23 ibp/ibp.tex
@@
 
-Apiary is a popular online API design service.
+Apiary \cite{Apiary} is a popular online API design service.
 Apiary focuses on a collaborative approach to creating APIs, the tool offers the ability to work with between 5 and 50 contributors on a single project.
@@
 
-Mashery provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:
+Mashery \cite{Mashery} provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:
 
@@
 
+More importantly, the companies themselves will likely benefit from such a framework.
+Potentially, the framework could allow companies to develop APIs, and therefore software, quickly and more efficiently thus increasing their development speed.
+Furthermore, the framework could help companies make changes to existing APIs to have fewer side effects within their ecosystems, for example, it could allow companies to communicate more easily with their users when making changes to the APIs that they are using.
+This could mean that companies could make changes more frequently with less side effects.
+
 \subsection{Impact on Society}
+Companies are not the only entity that could benefit from the this framework.
 If companies begin developing their APIs to fit the needs of ecosystems, it would not only have a great impact on these specific isolated environments; it would develop the whole software engineering industry.
@@
 
+The software engineering and management programme has helped us immensely with our thesis.
+Specifically, Technical Analysis and design and the Software Architecture courses have provided us with a good background for designing systems.
+Coupling this with programming and the design and development of embedded systems courses means that we have all the skills we require to complete our thesis.
+It also goes without saying that all the courses in the program will be invaluable when it comes to future work.
+Be it studying for a masters degree, continuing the thesis study or starting down our desired career path, our studies in this program have equipped us well for the future.
+
 \bibliographystyle{bib}

### 2015-03-24 ibp/ibp.tex
review ibp

@@
 
-The research behind the framework has been made through reviewing existing literature, and through analysing changes between  different versions on an industry API.
+The research behind the framework has been made through reviewing existing literature, and through analysing changes between  different versions of a product API.
 The main way of assessing the API has been through measuring the impact it has on its ecosystem.
@@
 The findings of our initial studies show that the changes to APIs have negative effects, and that they primarily affect the users of the API.
-They also show that modifications to APIs heavily influence the ecosystem.
+They also show that modifications to APIs heavily influence the ecosystem in which the API is used.
 \smallskip
@@
 \item Reduced negative impacts when changing APIs
-\item A software ecosystem existing in symbiosis
+\item Maintaining a healthy equilibrium of a software ecosystem
 \end{itemize}
@@
 One limitation to this report is that the development of the framework has not started yet, and that only the initial studies have been started.
-Another limitation is that the no extensive research on whether or not companies have the desire spend resources that do not have an immediate impact on their revenue.
+Another limitation is that no extensive research on whether or not companies have the desire spend resources that do not have an immediate impact on their revenue.
 
@@
 
-As the software industry and the open source movement steadily grow, the number of publicly available APIs is increasing.
+As the software industry and the open-source movement steadily grow, the number of publicly available APIs is increasing.
 APIs can improve development speed \cite{stylos2006comparing}, improve software quality \cite{stylos2006comparing} and can increase software reusability \cite{afonso2012evaluating}.
@@
 
-%This needs fluffing
 Our solution is to provide a set of guidelines, or framework with which to follow when making changes to APIs.
 The framework will prioritise business motives and needs when tackling design decisions.
-The framework will also take into account the business need, not only of the organisation which owns the API, but the business needs of all organisations existing in the ecosystem.
+The framework will also take the business needs, not only of the organisation which owns the API, but of all organisations existing in the ecosystem into account.
 
 \subsection{Related Products}
-Exhaustive research has found that there exists very few similar solutions similar to our own.
-While there are countless books related to the subject, very few actually aim to address the needs of business and customers; they are primarily focused on the developer.
+Exhaustive research has found that there exists very few similar solutions related to our framework.
+While there are countless books related to the subject, very few actually aim to address the needs of business and customers; they primarily focus on the developer.
 \smallskip
@@
 Apiary focuses on a collaborative approach to creating APIs, the tool offers the ability to work with between 5 and 50 contributors on a single project.
-The unique part of this tool is that it provides a ``mock" API by which customers, developers or anyone with access can work with.
+The unique aspect of this tool is that it provides a ``mock" API by which customers, developers or anyone with access can work with.
 This stage allows quick prototyping and testing of an API before any real coding has taken place.
-The tool, while useful, doesn't aim to solve the problem of handling changes to APIs but is instead a good platform to quickly prototype ideas.
+The tool, while useful, does not aim to solve the problem of handling changes to APIs but instead, it is a platform which allows for quick prototyping of ideas.
 
-Mashery \cite{Mashery} provide a more business oriented approach to API development. They offer a wide variety of services with API management being one of them. Quoting their website, they:
+Mashery \cite{Mashery} provide a more business-oriented approach to API development. They offer a wide variety of services and one of which is API management. Quoting their website, they:
 
@@
 
-While Mashery have a more business oriented approach, they do not offer anything resembling a framework for both business and developers to use when making API design decisions.
+While Mashery have a more business-oriented approach, they do not offer anything resembling a framework for both business and developers to use when making API design decisions.
 
@@
 \subsection{Knowledge Development}
-Since we have made the assessment that the market need will to remain relatively stable, careful research is essential to be able to deliver a product that meets the market needs.
+Since we have made the assessment that the market will remain relatively stable, careful research is essential to be able to deliver a product that meets the market needs.
 The primary method of performing the initial study, to be able to improve knowledge, will be through studying the existing literature.
@@
 The goal of the data collection performed in the case study will also be to gather a set of best practices for each of the three fields.
-To determine these best practices, an analysis of the companies current API and a future API will be performed.
+To determine these best practices, an analysis of the companies' current APIs and a future APIs will be performed.
 The changes between the two versions of the company's platform API will be of great significance and it is from these changes that we will base some of our best practices upon.
 \smallskip
-
-\subsection{Implementing the Framework}
-In order to collate as much existing knowledge and research as possible, a thorough, extensive literature review will be conducted.
-This will be complimented by a case study which is shall be performed in conjunction with the previously mentioned case company.
-The results of both the review and the case study will be analysed and compared.
-A set of best practices, based on the data collected in the review and case study, will be used to create the basis of the framework that will make up our best practices.
-Bringing in important factors from each of the three fields in the discussion is of the highest importance.
-The goal of this phase is therefore to create an Minimum Viable Product (MVP) that can be adopted and evaluated at the case company.
-\smallskip
-
-Once this information has been fully analysed and documented, with the best practices found, the framework can be created in full.
-The framework needs to be language agnostic and apply to no specific technical area, rather it should be applicable to all.
-
-\subsection{Adoption and Evaluation}
-The final stage of the roadmap will be performed using an iterative approach, where the MVP will be continuously evaluated and improved at the case company.
-The primary result of evaluating the success of the framework will be to measure if there is any visible reduction in the amount of negative effects that changes to an API has on its ecosystem, while retaining the original complexity and usability before the changes were made.
-\smallskip
-
-To ease the adoption process, a series of tests and evaluations will be performed on pilot studies.
-The goal of these pilot studies would be to verify and improve the best practices.
-For example, we will perform an analysis of an exist API and it's changes against an existing framework.
-We will then apply our framework and best practices to see if our framework suggests better and more robust changes, taking into account the affects of these changes on the ecosystem.
-Feedback will then be collected from the company who owns the API based on our frameworks suggested changes.
-This will be done to determine if our suggested changes are achieving the same goals as their changes would have done.
 
@@
 
+\subsection{Implementing the Framework}
+In order to obtain as much existing knowledge and research as possible, a thorough, extensive literature review will be conducted.
+This will be complimented by a case study which is shall be performed in conjunction with the previously mentioned case company.
+The results of both the review and the case study will be analysed and compared.
+A set of best practices, based on the data collected in the review and case study, will be used to create the basis of the framework that will make up our best practices.
+Bringing in important factors from each of the three fields in the discussion is of the highest importance.
+The goal of this phase is therefore to create a Minimum Viable Product (MVP) that can be adopted and evaluated at the case company.
+\smallskip
+
+Once this information has been fully analysed and documented, with the best practices found, the framework can be created in full.
+The framework needs to be language agnostic and must be generic enough so that it is applicable to a wide range of areas.
+
+\subsection{Adoption and Evaluation}
+The final stage of the roadmap will be performed using an iterative approach, where the MVP will be continuously evaluated and improved at the case company.
+The primary result of evaluating the success of the framework will be to measure if there is any visible reduction in the amount of negative effects that changes to an API has on its ecosystem, while retaining the original complexity and usability before the changes were made.
+\smallskip
+
+To ease the adoption process, a series of tests and evaluations will be performed on pilot studies.
+The goal of these pilot studies would be to verify and improve the best practices.
+For example, we will perform an analysis of an existing API and its changes.
+We will then apply our framework and best practices to see if our framework suggests better and more robust changes, taking into account the effects of these changes on the ecosystem.
+Feedback will then be collected from the company who owns the API based on our frameworks suggested changes.
+This will be done to determine if our suggested changes are achieving the same goals as their changes would have done.
+
 \section{Dissemination Plan, 2p}
-This section will describe the dissemination plan for our framework.
+This section will describe a plan for how our framework shall be distributed and communicated, and which organisations that will be targeted.
 
@@
 Open-source projects have been identified as potential users of our API as they generally have a good-will mindset when it comes to furthering and helping to improve the software engineering industry.
-Generally speaking, most open-source developers do no prioritise making a profit from their work, instead, they focus on delivering a product that is as complete and functional as possible.
-The open-source community is a well established and has existed for a long time, with a long tradition of autonomy, it can be said that they care about the well-being of their software ecosystems.
+Generally speaking, most open-source developers do not prioritise making a profit from their work, instead, they focus on delivering a product that is as complete and functional as possible.
+The open-source community is well established and has existed for a long time, with a long tradition of autonomy, it can be said that they care about the well-being of their software ecosystems.
 
-The second area where this could have an especially great impact would be in the area of web development APIs.
-Web APIs are widely used by vast amount of developers, performing many varied tasks.
+The second area where this could have an especially great impact would be in the area of web development.
+Web development APIs are widely used by a vast amount of developers, performing a wide variety of tasks.
 The web is a constantly evolving and expanding market, as such many companies rise and fall based on the success of their API.
-Therefore, it's not surprising that changes to a web API have significant impacts on the ecosystems of the systems.
+Therefore, it is not surprising that changes to a web API have significant impacts on the ecosystems of the systems.
 The toolchain in web development is usually referred to as a ``stack" which literally is a set of frameworks and APIs that you use together to develop your application.
@@
 These papers will be used to generate awareness and attention of our framework and the successes that it can bring.
-The papers may propagate research and act as a stepping stone for other research.
+The studies may propagate research and act as a stepping stone for other research.
 Other researchers could quite easily build upon the research which we have conducted.
@@
 The main reason for targeting such conferences is that, generally speaking, these types of conferences tend to attract the prominent figures in a particular industry or a narrower aspect of it.
-Bringing this to the awareness of these key players would help to create further awareness and publicity of the research, and by association, the best practices that we shall develop.
+Bringing this to the awareness of these key players would help to create further awareness and publicity for the research and the developed framework.
 
@@
 \section{Impact Assessment}
-This section will describe the impact that our framework will have.
+This section will describe the impact that our framework will have on the software engineering community and on the companies that operate in that area.
+It will also be discussed how the framework can impact and improve society.
 
@@
 Today's software engineering companies mainly take into account their own agendas, and APIs are changed for refactoring reasons, such as name changes, or to reduce complexity.
-The most important factor when designing or changing APIs is, however, how the changes will impact the users of the API and how their needs are being met.
+The most important factor when changing APIs is how the changes will impact the users of the API and how their needs are being met.
 In the recent years, this has been realised by the software engineering industry.
@@
 For example, it would have the potential to reduce the risks taken when deprecating methods as users and developers would be able to communicate their needs effectively.
-The impact of this could even be that companies begin changing and improving their APIs with the view of helping the ecosystem instead of purely their own immediate needs.
-This would have the potential to cause a a domino effect in the ecosystem which would hopefully spread to other ecosystems and ultimately would become a part of their overall software design process.
+The impact of this could even be that companies begin changing and improving their APIs with the view of helping the ecosystem instead of purely satisfying their own immediate needs.
+This would have the potential to cause a domino effect in the ecosystem which would hopefully spread to other ecosystems and ultimately would become a part of their overall software design process.
 
@@
 Potentially, the framework could allow companies to develop APIs, and therefore software, quickly and more efficiently thus increasing their development speed.
-Furthermore, the framework could help companies make changes to existing APIs to have fewer side effects within their ecosystems, for example, it could allow companies to communicate more easily with their users when making changes to the APIs that they are using.
-This could mean that companies could make changes more frequently with less side effects.
+Furthermore, the framework could help companies make changes to existing APIs leading to fewer side effects within their ecosystems.
+For example, it could allow companies to communicate effectively with their users when making changes to the APIs that they are using.
+This could mean that companies could make changes more frequently and with less side effects.
 
 \subsection{Impact on Society}
-Companies are not the only entity that could benefit from the this framework.
+Not only companies could benefit from this framework.
 If companies begin developing their APIs to fit the needs of ecosystems, it would not only have a great impact on these specific isolated environments; it would develop the whole software engineering industry.
 Therefore, the impact on society is potentially huge.
-Given that software is used by everyone, daily, improving software overall could improve peoples quality of life.
+Given that software is used by everyone, daily, improving software overall could improve people's quality of life.
 
 In modern software development, very few applications are written without the use of APIs.
-The consequence of which means, if APIs are designed more thoroughly, software performance is likely to rise.
-It might be difficult to envision that companies would actually spend resources to help their ecosystem without seeing and direct and immediate improvements for themselves.
+The consequence of which, may be that are APIs are designed more thoroughly, the performance of the software is likely to improve.
+It might be difficult to envision that companies would actually spend resources to help their ecosystem without seeing any direct and immediate improvements for themselves.
 However, examples of where similar changes are happening can already be found today.
@@
 The improvement of this software helps Ericsson directly, as they are using the software themselves.
-However, by improving open source software, they inadvertently help anyone else who uses this software.
-If this trend were to catch on, it could potentially lead to a world where all software has higher quality and is developed faster.
+However, by improving open-source software, they inadvertently help anyone else who uses this software.
+If this trend were to continue, it could potentially lead to a world where software has higher quality and is developed faster.
 
 \section{Summary}
-The knowledge gained from the course has had both immediate and long term benefits.
+The knowledge gained from the course has had both immediate and long-term benefits.
 Immediately, we were able to use the information regarding finding research topics, collaborating with industry and performing research.
 These topics were invaluable for us when it came to finding a research topic and company for our thesis.
-In regards to the long term value, information for working at a company or in a professional environment will undoubtedly be of use for us.
+In regards to the long-term value, information for working at a company or in a professional environment will undoubtedly be of use for us.
 
@@
 If either of us wish to pursue a career in research, we now have some idea of what it would require and to some extent what it might be like to do so.
-
-The second guest lecture was also of great help when for this report. The methods and ideas presented were vital in helping us generate ideas and solutions to our given problem.
+The second guest lecture was also of great help when for this report.
+The methods and ideas presented were vital in helping us generate ideas and solutions to our given problem.
 
@@
 
-Another more practical use of this course will be that it will help us to take a more structured and systematic approach in planning our career.
+Another, more practical, use of this course will be that it will help us to take a more structured and systematic approach in planning our career.
 Before we have only set goals that are quite loose and undefined, but now we can use real industry methods such as roadmaps to structure our career plan.
@@
 Coupling this with programming and the design and development of embedded systems courses means that we have all the skills we require to complete our thesis.
-It also goes without saying that all the courses in the program will be invaluable when it comes to future work.
-Be it studying for a masters degree, continuing the thesis study or starting down our desired career path, our studies in this program have equipped us well for the future.
+It also goes without saying that all the courses in the program will be invaluable when it comes to future work: Be it studying for a masters degree, continuing the thesis study or starting down our desired career path, our studies in this program have equipped us well for the future.
 

### 2015-03-25 rmtw/a4/latex8.tex
feedback a4

@@
 The data used for the WMW test was the efficiency of each participant.
-The result of the WMW test was p=0.1063 and thus the alternative hypothesis, H\textsubscript{1 Eff}, is rejected.
+The result of the WMW test was p=0.1063 and thus the results are not statistically significant enough to reject the null hypothesis.
 
-The same test was chosen for H\textsubscript{Rate}, based on the same reasoning. The result of the WMW test for H\textsubscript{Rate} was p=0.1063 and thus H\textsubscript{1 Rate} is rejected.
+The same test was chosen for H\textsubscript{Rate}, based on the same reasoning.
+The result of the WMW test for H\textsubscript{Rate} was p=0.1063 and thus the results are not statistically significant enough to reject H\textsubscript{0 Rate}.
 
-As evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar.
-Both show that there is a slight difference between the two inspection methods, and there is a slight better result for CL.
+As is evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar.
+Both show that there is a slight difference between the two inspection methods, and there is a slightly better result for CL.
 The results are, however, not statistically significant enough for the null hypotheses to be rejected.
@@
 For $\nu$=2 and $\alpha$=0.05, the upper critical value is 5.991 and the lower critical value is 0.103.
-Since 1.5998 is \textless 5.991 and \textgreater 0.103, the alternative hypothesis of the CS test is rejected.
-Since H\textsubscript{0 Fault} and H\textsubscript{1 Fault} are inverted compared to the hypothesis of the CS test, the null hypothesis of H\textsubscript{Fault} is rejected.
+Since 1.5998 is \textless 5.991 and \textgreater 0.103, the results are not statistically significant enough for the null hypothesis to be rejected.
 

### 2015-03-25 rmtw/a4/latex8.tex
dsad

@@
 However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC.
-This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding.
 
@@
 
-\noindent
-\textbf{Notes:}
-\begin{itemize}
-\item We were a bit unsure whether to only analyse the tests with help of the p-value or analysing the p-value together with test result and critical-value was correct.
-We decided to do the latter and would like feedback on this.
-\item We ended up creating our own research questions based on the alternative hypotheses, since they were not included in Experiment\_Design.pdf. Hopefully this is what you were looking for.
-\end{itemize}
-
 \end{document}

### 2015-03-25 thesis/latex8.tex
dsad

--- 2015-03-21 rmtw/a6/latex8.tex
@@
 
-\title{To Be Announced}
+\title{Exploring and Reverse Engineering the Motives Behind API Modifications}
 
@@
 
-\section{Introduction}
+\section{Main Idea of Study}
 %API Design (and a little bit of ecosystems, and a bit of problem statement)
@@
 Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
-There are, however, no studies that attempt to map the motives behind changes to business needs or existing software evolution theories, such as the four categories of maintenance \cite{lientz1980software} \cite{iso}.
+There are, however, no studies that attempt to map the motives behind changes to existing software evolution theories, such as the four categories of maintenance \cite{lientz1980software} \cite{iso}.
 The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
@@
 Subsequently, the architects of the API will be interviewed and asked to verify the accuracy of our findings.
-
-%Didn't change:
-%* 'the motive behind...' behind what? I get the grammar, but drop 'behind', methinks
-
-\subsection{Research Questions}
-\begin{itemize}
-\item RQ1: What drives API evolution? 
-\item RQ2: To what extent can we reverse engineer API change decisions?
-%\item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
-\end{itemize}
-
-%Structure of the paper
-The sections following the Introduction are structured as follows: In Section 2, we present a literature review on research related to our study.
-Section 3 describes the case company and how it was selected.
-A description of our methodology is introduced in Section 4.
 
@@
 \subsection{API Change}
-%%The first sentence of this pargraph... did all 3 really look at motive/intent?
-Previous studies that have attempted to identify the motives behind API changes have primarily focused on APIs that are a part of large programming languages, such as Java \cite{shi2011empirical} \cite{hou2011exploring} and Smalltalk \cite{robbes2012developers}.
+Previous studies that have attempted analyse APIs in the context of software evolution have primarily focused on APIs that are a part of large programming languages, such as Java \cite{shi2011empirical} \cite{hou2011exploring} and Smalltalk \cite{robbes2012developers}.
 One study attempted to uncover the intents behind the changes made in the AWT and Swing Java libraries.
@@
 As such, the goal was to include as many companies as possible in this study.
-[Note to reviewer \#1: Do you think we can claim that our case is typical, critical, revelatory or unique?
-Or is the current description adequate?]
 
 %Try to motivate why other sampling methods weren't used.
+
+\section{Research Questions}
+\begin{itemize}
+\item RQ1: What drives API evolution? 
+\item RQ2: To what extent can we reverse engineer API change decisions?
+%\item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
+\end{itemize}
 
@@
 Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs, and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's explanation of their motives.
-Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis [Note to reviewer \#2: Do you agree with this?]
+Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.
 
@@
 The applicability of case studies in such scenarios is supported by existing studies \cite{runeson2009guidelines} \cite{benbasat1987case} \cite{yin2013case} \cite{robson2002real}.
-An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines} [Note to reviewer \#3: Do you think this is a valid reason?
-Or does it imply that all design research involves toy programs?].
+An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
 An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to answer RQ2.
@@
 
-To reduce risks of research bias and human errors, the data collection was performed independently by both researchers. If the data differed, the cause was investigated and resolved.
+The data collection was performed independently by both researchers, to reduce the risk of human errors affecting the results.
+If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.
 
@@
 
-[Note to reviewer \#4: We struggled to find construct threats as we've not done the study so we don't know any yet, is it normal or OK to exclude one of the categories?]
+\section{Timeplan}
+Table 1 is an initial timeline of milestones in our study. The dates are approximate and we aim to finish ahead of schedule.
+
+\begin{table}
+	\centering
+	\begin{tabular}[!HT]{| l | l | l |}
+	\hline
+	\textbf{\#} & \textbf{Description} & \textbf{Deadline} \\
+	\hline
+	1 & Literature Review & 5 April \\
+	\hline
+	2 & Data Collection (Archival) & 12 April \\
+	\hline
+	3 & Data Analysis (Archival) & 19 April \\
+	\hline
+	4 & Data Collection (Interview) & 26 April \\
+	\hline
+	5 & Data Analysis (Everything) & 11 May \\
+	\hline
+	6 & Report Results & 25 May \\
+	\hline
+\end{tabular}
+	\caption{Timeplan}
+\end{table}
 
@@
 
-\Section{Acknowledgement}
-John had the main responsibility for sections 2, 4.1 and 4.3.
-William had the main responsibility for sections 1, 3, 4.0 and 4.3.
-We have, however, worked on all sections jointly and all sections have been reviewed by both of us.
-
 \end{document}

### 2015-03-26 rmtw/a6/latex8.tex
random title to a6
added notes from imed

@@
 \subsection{API Design}
-
 API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective} \cite{afonso2012evaluating} \cite{stylos2006comparing}.
@@
 As such, the goal was to include as many companies as possible in this study.
-[Note to reviewer \#1: Do you think we can claim that our case is typical, critical, revelatory or unique?
-Or is the current description adequate?]
 
@@
 
-[Note to reviewer \#4: We struggled to find construct threats as we've not done the study so we don't know any yet, is it normal or OK to exclude one of the categories?]
-
 \bibliographystyle{latex8}

### 2015-03-27 rmtw/a6/latex8.tex
sda

@@
 
+%Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}.
+The study aimed to discover if APIs with high rates of faults affected the success of an application.
+The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.
+
 \section{Introduction}
@@
 The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}.
-%software evolution 
+%Software Evolution 
 In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint.
@@
 
+\subsection{Background}
+
+\subsubsection{API}
+
+\subsubsection{Software Evolution}
+
+\subsubsection{Software Ecosystems}
+
+\subsection{Related Work}
+
 \subsection{API Design}
@@
 This particular empirical study found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.
-
-Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}.
-The study aimed to discover if APIs with high rates of faults affected the success of an application.
-The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.
 
@@
 \subsection{Data Collection}
-The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of accompanying  documentation.
+The data were collected primarily through inspections of the source code and the archival analysis of accompanying  documentation.
 The source code was comprised of two versions of the same API which the company had developed.
@@
 
-From the APIs we collected data about method names, parameters and return types.
+From the APIs we collected method names, parameters and return types.
+(Additional data will collected.
+This is just an initial ``estimation" for the proposal).
 The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
@@
 
-First degree interviews were also conducted after the initial source code inspections had taken place.
+Interviews were also conducted after the initial source code inspections had taken place.
 The main purpose of these was to validate our findings with the architects of the APIs.
@@
 % This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.
+This section has been structured around a well-known schema used for classifying validity threats \cite{runeson2009guidelines}.
 

### 2015-03-27 rmtw/a6/latex8.tex
asds

@@
 In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint.
-Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software} \cite{iso}.
+Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software}.
 
@@
 Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
-There are, however, no studies that attempt to map the motives behind changes to existing software evolution theories, such as the four categories of maintenance \cite{lientz1980software} \cite{iso}.
+There are, however, no studies that attempt to map the motives behind changes to existing software evolution theories, such as the four categories of maintenance \cite{lientz1980software}.
 The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
@@
 The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
-More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{iso} the motive of the change corresponded to.
+More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{lientz1980software} the motive of the change corresponded to.
 Secondly, the codes were analysed from a high-level point of view, and the main goal was to identify trends in the codes.

### 2015-03-27 rmtw/a6/latex8.tex
dsafd

@@
 
-%Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}.
-The study aimed to discover if APIs with high rates of faults affected the success of an application.
-The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.
-
 \section{Introduction}
@@
 
+%%Integrate this with Introduction:
+%Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}.
+The study aimed to discover if APIs with high rates of faults affected the success of an application.
+The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.
+
 \subsection{Research Questions}
@@
 \subsubsection{API}
-
-\subsubsection{Software Evolution}
-
-\subsubsection{Software Ecosystems}
-
-\subsection{Related Work}
-
-\subsection{API Design}
 API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective} \cite{afonso2012evaluating} \cite{stylos2006comparing}.
@@
 
-\subsection{API Change}
+\subsubsection{Software Evolution}
+The concept of software evolution has existed since the 1960s, often being interchangeable with software maintenance. Well known studies from this era established the need for
+
+\subsubsection{Software Ecosystems}
+
+\subsection{Related Work}
 Previous studies that have attempted analyse APIs in the context of software evolution have primarily focused on APIs that are a part of large programming languages, such as Java \cite{shi2011empirical} \cite{hou2011exploring} and Smalltalk \cite{robbes2012developers}.
@@
 This particular empirical study found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.
+
+\subsection{API Design}
 

### 2015-03-27 rmtw/a6/latex8.tex
Added some bibs n stuff
added evolution section

@@
 \subsubsection{Software Evolution}
-The concept of software evolution has existed since the 1960s, often being interchangeable with software maintenance. Well known studies from this era established the need for
+
+Software evolution can be described as being the application of software maintenance activities and processes, resulting in a new, \textit{evolved} version of the software.
+
+The concept of software maintenance has existed since the 1960s.
+Well known studies from this era established the importance of software maintenance \cite{canning1972maintenance}\cite{lientz1980software}.
+One study would go on to have a particularly profound effect on software maintenance by establishing a set of four categories which describe the intents behind change to software.
+These categories were refined in a further study, which saw the count of categories increase from four to twelve \cite{chapin2001types}; enhancive,corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training.
+
+Each category describes an intent behind changes to software, focusing around one of 3 particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}.
+This study also helped to further the distinction between software maintenance and software evolution.
+The study suggested that software maintenance is a part of software evolution and that the two are not interchangeable \cite{chapin2001types}.
 

### 2015-03-27 rmtw/a6/latex8.tex
adsaf

@@
 
-\subsubsection{API}
+\subsubsection{API Design}
+%%Wait a bit with adding a general introduction (explaining what an API is, what an API architect is etc.). Wait until we've read conference papers to see how they do it. 
 API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective} \cite{afonso2012evaluating} \cite{stylos2006comparing}.
@@
 Both studies also highlighted that the intent of the API must be clear to the user when using design patters, such as the concrete factory pattern \cite{shi2011empirical} \cite{stylos2006comparing}.
-
-An additional study involved combining semiotic and cognitive methods to evaluate APIs as a means of facilitating communication, between programmers and designers.
-\cite{afonso2012evaluating}.
-However, these studies do not highlight the motives behind changes to APIs.
+These factors that have to be considered when designing APIs can also be viewed from a usability.
+One study proposes a framework consisting of twelve cognitive cognitive dimensions that have an impact on the interaction between the user and the API \cite{clarke2004measuring}.
 
@@
 Previous studies that have attempted analyse APIs in the context of software evolution have primarily focused on APIs that are a part of large programming languages, such as Java \cite{shi2011empirical} \cite{hou2011exploring} and Smalltalk \cite{robbes2012developers}.
-One study attempted to uncover the intents behind the changes made in the AWT and Swing Java libraries.
-This particular study found that the use of a strong architecture was vital in ensuring a successful evolution of the API \cite{hou2011exploring}.
+One study \cite{hou2011exploring} attempted to uncover the intents behind the changes made in the AWT and Swing Java libraries.
+They found that the use of a strong architecture was vital in ensuring a successful evolution of the API \cite{hou2011exploring}.
+In their study, the intents were categorised around technical facot
 
-However, when APIs are changed, problems tend to occur.
 One study \cite{dig2005role} investigated three frameworks and one library in which the study found that 80\% of refactoring changes to APIs negatively affected existing applications.
@@
 This particular empirical study found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.
-
-\subsection{API Design}
 

### 2015-03-27 rmtw/a6/latex8.tex
Asdsa
asd

@@
 
-\section{Related Work}
-Our work is mainly related to the research area of API design.
-This discipline is discussed in Section 2.1.
-The motives and effects of changes to APIs are directly related to the fields of software evolution and software ecosystems.
-This will be discussed in Section 2.2.
+\section{Existing Literature}
 
-\subsection{Background}
-
-\subsubsection{API Design}
+\subsection{API Design}
 %%Wait a bit with adding a general introduction (explaining what an API is, what an API architect is etc.). Wait until we've read conference papers to see how they do it. 
@@
 
-\subsubsection{Software Evolution}
+\subsection{Software Evolution}
 
@@
 
-\subsubsection{Software Ecosystems}
+\subsection{Software Ecosystems}
 
@@
 They found that the use of a strong architecture was vital in ensuring a successful evolution of the API \cite{hou2011exploring}.
-In their study, the intents were categorised around technical facot
+In their study, the intents were categorised around programming related factors such as reducing coupling or conformance to naming conventions.
 

### 2015-03-27 rmtw/a6/latex8.tex
Updated data anal

@@
 The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
-More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{lientz1980software} the motive of the change corresponded to.
-Secondly, the codes were analysed from a high-level point of view, and the main goal was to identify trends in the codes.
-The third step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.
+
+More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{chapin2001types} the motive of the change corresponded to.
+The data were then mapped and coded to the laws presented by (!!!).
+The codes were then analysed from a high-level point of view, the main goal of which was to identify trends in the codes.
+The final step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.
 
@@
 This was done to triangulate our findings, to help reduce internal validity.
+
+A combination of the analysis between the changes to APIs, Lehmans laws and the software evolution categories \cite{chapin2001types} (!!!cites) allowed us to answer RQ1.
+The ability to answer RQ1 was the basis upon which we determined the answer to RQ2.
 

### 2015-03-27 rmtw/a6/latex8.tex
asdas

--- 2015-03-27 rmtw/a6/latex8.tex
@@
 
-% \author[*]{John Burchell}
-% \author[x]{William Granli}
-% \affil[*x]{Software Engineering \& Management}
-% \affil[*x]{University Of Gothenburg}
-% \affil[*]{john.a.burchell@gmail.com}
-% \affil[x]{william.granli@gmail.com}
-
 \begin{document}
-
-% \author{\textsuperscript{*}John Burchell \qquad \textsuperscript{x}William Granli \\
-% 		\textsuperscript{*}john.a.burchell@gmail.com \qquad \textsuperscript{x}william.granli@gmail.com \\
-% 		\textsuperscript{*x} Computer Science and Engineering  \\
-% 		\textsuperscript{*x}University of Gothenburg }
 
@@
 \item RQ2: To what extent can we reverse engineer API change decisions?
-%\item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
 \end{itemize}
@@
 \subsection{Software Evolution}
-
-Software evolution can be described as being the application of software maintenance activities and processes, resulting in a new, \textit{evolved} version of the software.
+Software evolution can be described as being the application of software maintenance activities and processes, resulting in a new, evolved version of the software.
 
 The concept of software maintenance has existed since the 1960s.
-Well known studies from this era established the importance of software maintenance \cite{canning1972maintenance}\cite{lientz1980software}.
-One study would go on to have a particularly profound effect on software maintenance by establishing a set of four categories which describe the intents behind change to software.
-These categories were refined in a further study, which saw the count of categories increase from four to twelve \cite{chapin2001types}; enhancive,corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training.
+Well known studies from this era established the importance of software maintenance \cite{canning1972maintenance} \cite{lientz1980software}.
+One study would go on to have a particularly profound effect on software maintenance by establishing a set of four categories which describe the intents behind change to software \cite{lientz1980software}.
+These categories were refined in a further study, which saw the count of categories increase from four to twelve \cite{chapin2001types}; enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training.
 
@@
 
-\subsection{Software Ecosystems}
+An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}.
+The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6)Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
+The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity".
 
@@
 From the APIs we collected method names, parameters and return types.
-(Additional data will collected.
-This is just an initial ``estimation" for the proposal).
+(Note to Morgan: Additional data will collected.
+This is just an early ``estimation" for the proposal).
 The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.

### 2015-03-27 rmtw/a6/latex8.tex
Updated incorrect reference
dsfsa

@@
 %%Integrate this with Introduction:
-%Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}.
+%Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{linares2013api}.
 The study aimed to discover if APIs with high rates of faults affected the success of an application.
-The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.
+The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{linares2013api}.
 
@@
 
-A combination of the analysis between the changes to APIs, Lehmans laws and the software evolution categories \cite{chapin2001types} (!!!cites) allowed us to answer RQ1.
+A combination of the analysis between the changes to APIs, Lehman's laws and the software evolution categories \cite{chapin2001types} (!!!cites) allowed us to answer RQ1.
 The ability to answer RQ1 was the basis upon which we determined the answer to RQ2.

### 2015-03-27 rmtw/a6/latex8.tex
Added cites to lehman in methodology

@@
 More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{chapin2001types} the motive of the change corresponded to.
-The data were then mapped and coded to the laws presented by (!!!).
+The data were then mapped and coded to the laws presented by \cite{lehman1980programs}.
 The codes were then analysed from a high-level point of view, the main goal of which was to identify trends in the codes.
@@
 
-A combination of the analysis between the changes to APIs, Lehman's laws and the software evolution categories \cite{chapin2001types} (!!!cites) allowed us to answer RQ1.
+A combination of the analysis between the changes to APIs, Lehmans laws and the software evolution categories \cite{chapin2001types}\cite{lehman1980programs} allowed us to answer RQ1.
 The ability to answer RQ1 was the basis upon which we determined the answer to RQ2.

### 2015-03-27 rmtw/a6/latex8.tex
Edited data analysis section

@@
 \section{Existing Literature}
+This section will introduce the topics of API design andsoftware evolution, and provide a review of literature which is directly related to our study.
 
@@
 The final step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.
+The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.
 
@@
 
-A combination of the analysis between the changes to APIs, Lehmans laws and the software evolution categories \cite{chapin2001types}\cite{lehman1980programs} allowed us to answer RQ1.
-The ability to answer RQ1 was the basis upon which we determined the answer to RQ2.
-
-The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.
+Software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer RQ1.
+The software evolution categories were used to map and explore motives behind changes and Lehman's laws were used to see what drives the natural evolution of APIs.
+Our ability to correctly predict the motives compared to the actual motives of the architects which were made clear during the interviews, will serve as the basis for answering RQ2.
 

### 2015-03-27 rmtw/a6/latex8.tex
sdf

@@
 \section{Existing Literature}
-This section will introduce the topics of API design andsoftware evolution, and provide a review of literature which is directly related to our study.
+This section will introduce the topics of API design and software evolution, and provide a review of literature which is directly related to our study.
 
@@
 
-Software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer RQ1.
+The software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer RQ1.
 The software evolution categories were used to map and explore motives behind changes and Lehman's laws were used to see what drives the natural evolution of APIs.

### 2015-03-27 rmtw/a6/latex8.tex
ASD

@@
 
-\title{Exploring and Reverse Engineering the Motives Behind API Modifications}
+\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
 
@@
 Both studies also highlighted that the intent of the API must be clear to the user when using design patters, such as the concrete factory pattern \cite{shi2011empirical} \cite{stylos2006comparing}.
-These factors that have to be considered when designing APIs can also be viewed from a usability.
-One study proposes a framework consisting of twelve cognitive cognitive dimensions that have an impact on the interaction between the user and the API \cite{clarke2004measuring}.
+One study proposes an usability framework consisting of twelve cognitive dimensions that have an impact on the interaction between the user and the API \cite{clarke2004measuring}.
 

### 2015-03-27 thesis/latex8.tex
ASD

@@
 
-\title{Exploring and Reverse Engineering the Motives Behind API Modifications}
-
-% \author[*]{John Burchell}
-% \author[x]{William Granli}
-% \affil[*x]{Software Engineering \& Management}
-% \affil[*x]{University Of Gothenburg}
-% \affil[*]{john.a.burchell@gmail.com}
-% \affil[x]{william.granli@gmail.com}
+\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
 
 \begin{document}
-
-% \author{\textsuperscript{*}John Burchell \qquad \textsuperscript{x}William Granli \\
-% 		\textsuperscript{*}john.a.burchell@gmail.com \qquad \textsuperscript{x}william.granli@gmail.com \\
-% 		\textsuperscript{*x} Computer Science and Engineering  \\
-% 		\textsuperscript{*x}University of Gothenburg }
 
@@
 The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}.
-%software evolution 
+%Software Evolution 
 In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint.
-Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software} \cite{iso}.
+Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software}.
 
@@
 
-\section{Related Work}
-Our work is mainly related to the research area of API design.
-This discipline is discussed in Section 2.1.
-The motives and effects of changes to APIs are directly related to the fields of software evolution and software ecosystems.
-This will be discussed in Section 2.2.
+%Didn't change:
+%* 'the motive behind...' behind what? I get the grammar, but drop 'behind', methinks
+
+%%Integrate this with Introduction:
+%Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{linares2013api}.
+The study aimed to discover if APIs with high rates of faults affected the success of an application.
+The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{linares2013api}.
+
+\section{Literature Review}
+This section will introduce the topics of API design and software evolution, and provide a review of literature which is directly related to our study.
 
 \subsection{API Design}
-
+%%Wait a bit with adding a general introduction (explaining what an API is, what an API architect is etc.). Wait until we've read conference papers to see how they do it.
 API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective} \cite{afonso2012evaluating} \cite{stylos2006comparing}.
@@
 Both studies also highlighted that the intent of the API must be clear to the user when using design patters, such as the concrete factory pattern \cite{shi2011empirical} \cite{stylos2006comparing}.
+One study proposes an usability framework consisting of twelve cognitive dimensions that have an impact on the interaction between the user and the API \cite{clarke2004measuring}.
 
-An additional study involved combining semiotic and cognitive methods to evaluate APIs as a means of facilitating communication, between programmers and designers.
-\cite{afonso2012evaluating}.
-However, these studies do not highlight the motives behind changes to APIs.
+\subsection{Software Evolution}
+Software evolution can be described as being the application of software maintenance activities and processes, resulting in a new, evolved version of the software.
 
-\subsection{API Change}
+The concept of software maintenance has existed since the 1960s.
+Well known studies from this era established the importance of software maintenance \cite{canning1972maintenance} \cite{lientz1980software}.
+One study would go on to have a particularly profound effect on software maintenance by establishing a set of four categories which describe the intents behind change to software \cite{lientz1980software}.
+These categories were refined in a further study, which saw the count of categories increase from four to twelve \cite{chapin2001types}; enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training.
+
+Each category describes an intent behind changes to software, focusing around one of 3 particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}.
+This study also helped to further the distinction between software maintenance and software evolution.
+The study suggested that software maintenance is a part of software evolution and that the two are not interchangeable \cite{chapin2001types}.
+
+An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}.
+The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6)Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
+The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity".
+
+\subsection{Related Work}
 Previous studies that have attempted analyse APIs in the context of software evolution have primarily focused on APIs that are a part of large programming languages, such as Java \cite{shi2011empirical} \cite{hou2011exploring} and Smalltalk \cite{robbes2012developers}.
-One study attempted to uncover the intents behind the changes made in the AWT and Swing Java libraries.
-This particular study found that the use of a strong architecture was vital in ensuring a successful evolution of the API \cite{hou2011exploring}.
+One study \cite{hou2011exploring} attempted to uncover the intents behind the changes made in the AWT and Swing Java libraries.
+They found that the use of a strong architecture was vital in ensuring a successful evolution of the API \cite{hou2011exploring}.
+In their study, the intents were categorised around programming related factors such as reducing coupling or conformance to naming conventions.
 
-However, when APIs are changed, problems tend to occur.
 One study \cite{dig2005role} investigated three frameworks and one library in which the study found that 80\% of refactoring changes to APIs negatively affected existing applications.
@@
 
-Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{mcdonnell2013empirical}.
-The study aimed to discover if APIs with high rates of faults affected the success of an application.
-The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{mcdonnell2013empirical}.
+\section{Research Questions}
+\begin{itemize}
+\item RQ1: What drives API evolution? 
+\item RQ2: To what extent can we reverse engineer API change decisions?
+\end{itemize}
 
@@
 
-\section{Research Questions}
-\begin{itemize}
-\item RQ1: What drives API evolution? 
-\item RQ2: To what extent can we reverse engineer API change decisions?
-%\item SRQ1.2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
-\end{itemize}
-
-\section{Methodology}
+\section{Research Strategy}
 This study has been conducted using the case study methodology \cite{runeson2009guidelines}.
@@
 
-From the APIs we collected data about method names, parameters and return types.
+From the APIs we collected method names, parameters and return types.
+(Note to Morgan: Additional data will collected.
+This is just an early ``estimation" for the proposal).
 The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
@@
 The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
-More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{iso} the motive of the change corresponded to.
-Secondly, the codes were analysed from a high-level point of view, and the main goal was to identify trends in the codes.
-The third step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.
+
+More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{chapin2001types} the motive of the change corresponded to.
+The data were then mapped and coded to the laws presented by \cite{lehman1980programs}.
+The codes were then analysed from a high-level point of view, the main goal of which was to identify trends in the codes.
+The final step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.
+The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.
 
@@
 
-The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.
+The software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer RQ1.
+The software evolution categories were used to map and explore motives behind changes and Lehman's laws were used to see what drives the natural evolution of APIs.
+Our ability to correctly predict the motives compared to the actual motives of the architects which were made clear during the interviews, will serve as the basis for answering RQ2.
 
@@
 
-\section{Timeplan}
-Table 1 is an initial timeline of milestones in our study. The dates are approximate and we aim to finish ahead of schedule.
-
-\begin{table}
-	\centering
-	\begin{tabular}[!HT]{| l | l | l |}
-	\hline
-	\textbf{\#} & \textbf{Description} & \textbf{Deadline} \\
-	\hline
-	1 & Literature Review & 5 April \\
-	\hline
-	2 & Data Collection (Archival) & 12 April \\
-	\hline
-	3 & Data Analysis (Archival) & 19 April \\
-	\hline
-	4 & Data Collection (Interview) & 26 April \\
-	\hline
-	5 & Data Analysis (Everything) & 11 May \\
-	\hline
-	6 & Report Results & 25 May \\
-	\hline
-\end{tabular}
-	\caption{Timeplan}
-\end{table}
-
 \bibliographystyle{latex8}

### 2015-03-27 thesis/latex8.tex
sdsadf

@@
 
-\author{John Burchell \qquad William Granli \\
-		john.a.burchell@gmail.com \qquad william.granli@gmail.com \\
+\author{John Burchell \qquad William Granli  \qquad Imed Hammouda \\
+		john.a.burchell@gmail.com \qquad william.granli@gmail.com \qquad hammouda@chalmers.se \\
 		Computer Science and Engineering  \\
@@
 
+\section{Timeplan}
+Table 1 is an initial timeline of milestones in our study. The dates are approximate and we aim to finish ahead of schedule.
+
+\begin{table}
+	\centering
+	\begin{tabular}[!HT]{| l | l | l |}
+	\hline
+	\textbf{\#} & \textbf{Description} & \textbf{Deadline} \\
+	\hline
+	1 & Literature Review & 5 April \\
+	\hline
+	2 & Data Collection (Archival) & 12 April \\
+	\hline
+	3 & Data Analysis (Archival) & 19 April \\
+	\hline
+	4 & Data Collection (Interview) & 26 April \\
+	\hline
+	5 & Data Analysis (Everything) & 11 May \\
+	\hline
+	6 & Report Results & 25 May \\
+	\hline
+\end{tabular}
+	\caption{Timeplan}
+\end{table}
+
 \bibliographystyle{latex8}

### 2015-03-30 rmtw/a6/latex8.tex
changed to ieeetran

@@
 \usepackage{authblk}
+\usepackage{blindtext}
 
@@
 %API Design (and a little bit of ecosystems, and a bit of problem statement)
-As the software industry and the open source movement steadily grow, the number of public APIs is increasing.
+As the software industry and the open-source movement steadily grow, the number of public APIs is increasing.
 APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
@@
 Due to the negative implications that modifications to APIs cause for its users, it is important to understand why changes to them occur.
-If most common pitfalls are known before the development of new APIs begin, these mistakes could be mitigated.
+If most common pitfalls are known before the development of new APIs begin, these mistakes can be mitigated.
 Before the industry can make use of this information, we must also critically assess to what degree we can trace such motives.
@@
 Subsequently, the architects of the API will be interviewed and asked to verify the accuracy of our findings.
-
-%Didn't change:
-%* 'the motive behind...' behind what? I get the grammar, but drop 'behind', methinks
-
-%%Integrate this with Introduction:
-%Furthermore, a study on the impact of reliable APIs was undertaken in the Android ecosystem \cite{linares2013api}.
-The study aimed to discover if APIs with high rates of faults affected the success of an application.
-The study found that the 50 least popular applications had APIs which were 500\% more error prone, ultimately concluding that there is indeed a correlation between API stability and application success \cite{linares2013api}.
 
@@
 %Structure of the paper
-The sections following the Introduction are structured as follows: In Section 2, we present a literature review on research related to our study.
+The sections following the Introduction are structured as follows: In Section 2, we present the existing literature related to our study.
 Section 3 describes the case company and how it was selected.
 A description of our methodology is introduced in Section 4.
+In Section 5, the results of our study are presented, and in Section 6, we discuss the findings of our study.
 
@@
 \subsection{Validity Threats}
-% This section highlights how we have either diminished or overcome the most concerning validity threats facing our study.
-This section has been structured around a well-known schema used for classifying validity threats \cite{runeson2009guidelines}.
+In this section we discuss possible threats to construct validity, internal validity, external validity and reliability \cite{runeson2009guidelines}.
+
+%We must add construct validity.
 
@@
 
+\section{Results}
+
+\blindtext
+
+\section{Conclusion}
+
+\blindtext
+
+\section*{Acknowledgment}
+
 \bibliographystyle{latex8}

### 2015-03-30 thesis/paper/thesis.tex
changed to ieeetran

--- 2015-03-30 rmtw/a6/latex8.tex
@@
-%
-%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
-%
-%  $Author: John Burchell & William Granli $
-%  $Date: 2015/01/21 15:20:59 $
-%  $Revision: 1.0
-%
-
-\documentclass[10pt,twocolumn]{article} 
-\usepackage{latex8}
-\usepackage{authblk}
+\documentclass[conference]{IEEEtran}
 \usepackage{blindtext}
 
+\begin{document}
 \title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
 
-\begin{document}
-
-\author{John Burchell \qquad William Granli \\
-		john.a.burchell@gmail.com \qquad william.granli@gmail.com \\
-		Computer Science and Engineering  \\
-		University of Gothenburg }
+\author{\IEEEauthorblockN{John Burchell}
+\IEEEauthorblockA{Computer Science and Engineering\\University of Gothenburg\\Gothenburg, Sweden\\
+Email: john.a.burchell@gmail.com} \and
+\IEEEauthorblockN{William Granli}
+\IEEEauthorblockA{Computer Science and Engineering\\University of Gothenburg\\Gothenburg, Sweden\\
+Email: william.granli@gmail.com}}
 
 \maketitle
+
+\begin{abstract}
+\blindtext
+\end{abstract}
 
@@
 
-\bibliographystyle{latex8}
-\bibliography{latex8}
+\bibliographystyle{bibstyle}
+\bibliography{bib}
 

### 2015-03-30 thesis/paper/thesis.tex
improved rel work

@@
 \section{Existing Literature}
-This section will introduce the topics of API design and software evolution, and provide a review of literature which is directly related to our study.
+This section will introduce the topics of API design and software evolution, and provide a review of studies that are directly related to our study.
 
 \subsection{API Design}
-%%Wait a bit with adding a general introduction (explaining what an API is, what an API architect is etc.). Wait until we've read conference papers to see how they do it.
 API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective} \cite{afonso2012evaluating} \cite{stylos2006comparing}.
-In previous research, generalisable usability studies have been created, with the aim of analysing the design decisions taken when creating an API \cite{stylos2006comparing}.
-Another empirical study, which involved working with 25 programmers, highlighted API design problems such as assigning names to API features and difficulty in naming types \cite{shi2011empirical}.
-The study also introduced four factors which are important to consider when creating an API: a) The API  must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
-Both studies also highlighted that the intent of the API must be clear to the user when using design patters, such as the concrete factory pattern \cite{shi2011empirical} \cite{stylos2006comparing}.
-One study proposes an usability framework consisting of twelve cognitive dimensions that have an impact on the interaction between the user and the API \cite{clarke2004measuring}.
+Examples of such decisions are whether to use the factory pattern or constructors to create objects, or if the API should display errors during compilation or runtime \cite{stylos2006comparing}.
+More trivial design problems, such as, assigning names to API features and difficulty in naming types also have a large impact on the usability of the API \cite{shi2011empirical}.
+When facing such design decisions, the following four factors are important to consider: a) The API  must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
+One of the most important qualities in an API is that the intent of the API is clear to the user when, for example, using design patterns, such as the concrete factory pattern \cite{shi2011empirical} \cite{stylos2006comparing}.
+The sum of all design decisions taken during the development of an API will decide the usability of the API.
+Measuring such a factor can be done by measuring the twelve cognitive dimensions which are factors that are impacted by the interaction between the API and the user of it \cite{clarke2004measuring}.
 
 \subsection{Software Evolution}
-Software evolution can be described as being the application of software maintenance activities and processes, resulting in a new, evolved version of the software.
+Software evolution is a field which studies the application of software maintenance activities and processes on software, and the resulting, evolved versions of the software.
+The concept of software maintenance has existed since the 1960s.
+Well-known studies from this era established the importance of software maintenance \cite{canning1972maintenance} \cite{lientz1980software}.
+One study would go on to have a particularly profound effect on software maintenance by establishing a set of four categories which describe the intents behind change to software \cite{lientz1980software}.
+These categories were refined in a further study, in which the number of categories were increased from four to twelve \cite{chapin2001types}.
+The categories proposed were: Enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training \cite{chapin2001types}.
 
-The concept of software maintenance has existed since the 1960s.
-Well known studies from this era established the importance of software maintenance \cite{canning1972maintenance} \cite{lientz1980software}.
-One study would go on to have a particularly profound effect on software maintenance by establishing a set of four categories which describe the intents behind change to software \cite{lientz1980software}.
-These categories were refined in a further study, which saw the count of categories increase from four to twelve \cite{chapin2001types}; enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training.
-
-Each category describes an intent behind changes to software, focusing around one of 3 particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}.
+Each category describes a type of software maintenance activity which relate to one of three particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}.
 This study also helped to further the distinction between software maintenance and software evolution.
@@
 From the APIs we collected method names, parameters and return types.
-(Note to Morgan: Additional data will collected.
-This is just an early ``estimation" for the proposal).
-The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
+(!!!Add more here) The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
 The collected data were input into tables and spreadsheets, according to the API version.
@@
 \section{Results}
-
-\blindtext
+\Blindtext
 
 \section{Conclusion}
+\Blindtext
 
+\section*{Acknowledgement}
 \blindtext
-
-\section*{Acknowledgment}
 

### 2015-03-30 thesis/paper/thesis.tex
reviewed data collection

@@
 This will be achieved by empirically analysing the changes between two versions of an API.
-Subsequently, the architects of the API will be interviewed and asked to verify the accuracy of our findings.
+Subsequently, the designers of the API will be interviewed and asked to verify the accuracy of our findings.
 
 \subsection{Research Questions}
-\begin{itemize}
-\item RQ1: What drives API evolution? 
-\item RQ2: To what extent can we reverse engineer API change decisions?
-\end{itemize}
+\begin{description}
+\item[\textbf{RQ1:}] What drives API evolution?
+\item[\textbf{RQ2:}] To what extent can we reverse engineer API change decisions?
+\end{description}
 
@@
 The categories proposed were: Enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training \cite{chapin2001types}.
-
 Each category describes a type of software maintenance activity which relate to one of three particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}.
@@
 \subsection{Data Collection}
+%Consider adding subsub for code+doc and interviews later
 The data were collected primarily through inspections of the source code and the archival analysis of accompanying  documentation.
@@
 From the APIs we collected method names, parameters and return types.
-(!!!Add more here) The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
+(!!!Add more here.
+Maybe put it in a table?) The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
 The collected data were input into tables and spreadsheets, according to the API version.
-From the archival documentation we collected data regarding the motive behind the functionality in API calls.
+From the documentation we collected data regarding the motive behind the functionality in API calls.
 Data gathered from the documentation was also stored in tables and spreadsheets and was organised together with its corresponding method.
 
-The data collection was performed independently by both researchers, to reduce the risk of human errors affecting the results.
+The data collection from code and documentation was performed independently by both researchers, to reduce the risk of human errors affecting the results.
 If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.
 
-These collection methods were the most appropriate given that the data were readily available from the company.
-This brought concerns that the data were not produced for the purpose of our research \cite{runeson2009guidelines}, meaning there was a risk of data being irrelevant or erroneous.
-
-Interviews were also conducted after the initial source code inspections had taken place.
-The main purpose of these was to validate our findings with the architects of the APIs.
+After the initial source code inspection had been performed, interviews were conducted.
+The main purpose of these was to validate our findings during the code inspection with the designers of the APIs.
 Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection.
-The final reason for interviewing the architects of the APIs was to provide further insight of the users of the API.
+The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API.
 
@@
 The software evolution categories were used to map and explore motives behind changes and Lehman's laws were used to see what drives the natural evolution of APIs.
-Our ability to correctly predict the motives compared to the actual motives of the architects which were made clear during the interviews, will serve as the basis for answering RQ2.
+Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, will serve as the basis for answering RQ2.
 
@@
 By performing an individual inspection of  the API source code, documentation and individual results analysis, internal validity is significantly reduced.
-Triangulation of the results with the use of interviewing the architects is a key step in reducing potential validity threats in our study.
+Triangulation of the results with the use of interviewing the designers is a key step in reducing potential validity threats in our study.
 

### 2015-03-30 thesis/paper/thesis.tex
formatted referneces

@@
 
-\section{Introduction}
+\section{Introduction} \label{introduction}
 %API Design (and a little bit of ecosystems, and a bit of problem statement)
@@
 
-\subsection{Research Questions}
+\subsection{Research Questions} \label{rqs}
 \begin{description}
@@
 %Structure of the paper
-The sections following the Introduction are structured as follows: In Section 2, we present the existing literature related to our study.
-Section 3 describes the case company and how it was selected.
-A description of our methodology is introduced in Section 4.
-In Section 5, the results of our study are presented, and in Section 6, we discuss the findings of our study.
+The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the existing literature related to our study.
+Section \ref{case_company_description} describes the case company and how it was selected.
+A description of our methodology is introduced in Section \ref{methodology}.
+In Section \ref{results}, the results of our study are presented, and in Section \ref{conclusion}, we discuss the findings of our study.
 
-\section{Existing Literature}
+\section{Existing Literature} \label{existing_literature}
 This section will introduce the topics of API design and software evolution, and provide a review of studies that are directly related to our study.
 
-\subsection{API Design}
+\subsection{API Design} \label{api_design}
 API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective} \cite{afonso2012evaluating} \cite{stylos2006comparing}.
@@
 
-\subsection{Software Evolution}
+\subsection{Software Evolution} \label{software_evolution}
+%%Categories of maintenance and types of maintenance
 Software evolution is a field which studies the application of software maintenance activities and processes on software, and the resulting, evolved versions of the software.
 The concept of software maintenance has existed since the 1960s.
-Well-known studies from this era established the importance of software maintenance \cite{canning1972maintenance} \cite{lientz1980software}.
+Well-known studies from this era established the importance of software maintenance \cite{lientz1980software}.
 One study would go on to have a particularly profound effect on software maintenance by establishing a set of four categories which describe the intents behind change to software \cite{lientz1980software}.
@@
 
+%%Lehman's laws (!!!improve later)
 An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}.
@@
 
-\subsection{Related Work}
+\subsection{Related Work} \label{related_work}
 Previous studies that have attempted analyse APIs in the context of software evolution have primarily focused on APIs that are a part of large programming languages, such as Java \cite{shi2011empirical} \cite{hou2011exploring} and Smalltalk \cite{robbes2012developers}.
@@
 
-\section{Case Company Description}
+\section{Case Company Description} \label{case_company_description}
 The case company is a medium-sized company in the domain of security cameras.
@@
 
-\section{Methodology}
+\section{Methodology} \label{methodology}
+%Intro and summary
 This study has been conducted using the case study methodology \cite{runeson2009guidelines}.
@@
 
+%Reasons for choosing case study
 The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
@@
 
-\subsection{Data Collection}
 %Consider adding subsub for code+doc and interviews later
+\subsection{Data Collection} \label{data_collection}
+%Intro to code inspection
 The data were collected primarily through inspections of the source code and the archival analysis of accompanying  documentation.
@@
 
+%Description of inspection
 From the APIs we collected method names, parameters and return types.
@@
 
+%Reduce human error
 The data collection from code and documentation was performed independently by both researchers, to reduce the risk of human errors affecting the results.
@@
 
+%Interviews !!!improve later
 After the initial source code inspection had been performed, interviews were conducted.
@@
 
-\subsection{Data Analysis}
+\subsection{Data Analysis} \label{data_analysis}
+%Intro and summary
 The data analysis was conducted in two major phases \cite{andersson2007spiral}.
@@
 The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase.
-
 Both phases were performed iteratively, together with the data collection.
 The reason for this created the opportunity to improve the process of analysis as the study progressed, as well as to be able to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
-
 The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
 
+%Description of code analysis
 More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{chapin2001types} the motive of the change corresponded to.
@@
 
+%Description of interview analysis
 Following the analysis of the archival data, the results of the interviews were analysed.
 The interviews were analysed using the same approach taken for the archival data.
-The results of this analysis was then compared and correlated with the results of the code analysis, with the goal of confirming the hypotheses that were formulated.
-This was done to triangulate our findings, to help reduce internal validity.
+The results of this analysis was then compared and correlated with the results of the code analysis, with the goal of confirming the hypotheses that had been formulated.
+This support also supported triangulation of our results.
 
+%Relate to RQs
 The software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer RQ1.
@@
 
-\subsection{Validity Threats}
+\subsection{Validity Threats} \label{validity_threats}
 In this section we discuss possible threats to construct validity, internal validity, external validity and reliability \cite{runeson2009guidelines}.
@@
 
-\section{Results}
-\Blindtext
+\section{Results} \label{results}
 
-\section{Conclusion}
-\Blindtext
+\section{Conclusion} \label{conclusion}
 
-\section*{Acknowledgement}
-\blindtext
+\section*{Acknowledgement} \label{acknowledgement}
 

### 2015-03-30 thesis/paper/thesis.tex
hello wurld

@@
 \subsection{API Design} \label{api_design}
-API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{bloch2008effective} \cite{afonso2012evaluating} \cite{stylos2006comparing}.
+API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{stylos2006comparing} \cite{afonso2012evaluating} \cite{bloch2008effective}.
 Examples of such decisions are whether to use the factory pattern or constructors to create objects, or if the API should display errors during compilation or runtime \cite{stylos2006comparing}.
@@
 When facing such design decisions, the following four factors are important to consider: a) The API  must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
-One of the most important qualities in an API is that the intent of the API is clear to the user when, for example, using design patterns, such as the concrete factory pattern \cite{shi2011empirical} \cite{stylos2006comparing}.
+One of the most important qualities in an API is that the intent of the API is clear to the user when, for example, using design patterns, such as the concrete factory pattern \cite{stylos2006comparing} \cite{shi2011empirical}.
 The sum of all design decisions taken during the development of an API will decide the usability of the API.
@@
 An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}.
-The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6)Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
+The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
 The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity".
@@
 \subsection{Related Work} \label{related_work}
-Previous studies that have attempted analyse APIs in the context of software evolution have primarily focused on APIs that are a part of large programming languages, such as Java \cite{shi2011empirical} \cite{hou2011exploring} and Smalltalk \cite{robbes2012developers}.
+Previous studies that have attempted analyse APIs in the context of software evolution have primarily focused on APIs that are a part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}.
 One study \cite{hou2011exploring} attempted to uncover the intents behind the changes made in the AWT and Swing Java libraries.
@@
 The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
-The applicability of case studies in such scenarios is supported by existing studies \cite{runeson2009guidelines} \cite{benbasat1987case} \cite{yin2013case} \cite{robson2002real}.
+The applicability of case studies in such scenarios is supported by existing studies \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}.
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to answer RQ2.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to answer \textbf{RQ2}.
 
@@
 %Relate to RQs
-The software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer RQ1.
+The software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer \textbf{RQ1}.
 The software evolution categories were used to map and explore motives behind changes and Lehman's laws were used to see what drives the natural evolution of APIs.
-Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, will serve as the basis for answering RQ2.
+Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, will serve as the basis for answering \textbf{RQ2}.
 

### 2015-04-29 thesis/paper/thesis.tex
Asdsa
hi

@@
 \begin{description}
-\item[\textbf{RQ1:}] What drives API evolution?
+\item[\textbf{RQ1:}] What drives API evolution?x
 \item[\textbf{RQ2:}] To what extent can we reverse engineer API change decisions?
@@
 %Structure of the paper
-The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the existing literature related to our study.
+The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the background and previously published work that is related to our study.
 Section \ref{case_company_description} describes the case company and how it was selected.
@@
 The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
-The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity".
+The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.o
 
@@
 The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
-The applicability of case studies in such scenarios is supported by existing studies \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}.
+The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}.
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.

### 2015-04-29 thesis/paper/thesis.tex
Added new paragraph for purpose/problem statement

@@
 %Purpose (and a bit of problem statement)
+%%****NEW*****
+Making changes to existing APIs can have a negative impact upon the users of those APIs.
+It is therefore important to understand why these changes occur.
+Understanding the motives behind the changes could help API designers prevent or avoid potential changes to their APIs.
+In order to achieve this and to provide immediate benefit to industry, an exploratory case study will be undertaken to investigate the underlying motives behind API changes of an existing API.
+Empirical analysis of changes between two major versions of an API will be undertaken, following which an interview with the architects will be used to verify the findings of our study.
+%%****^NEW^****
+
 Due to the negative implications that modifications to APIs cause for its users, it is important to understand why changes to them occur.

### 2015-04-29 thesis/paper/thesis.tex
added subsections for results
res
Added superscript and fixed some random letters at the end of scentences

@@
 \begin{description}
-\item[\textbf{RQ1:}] What drives API evolution?x
+\item[\textbf{RQ1:}] What drives API evolution?
 \item[\textbf{RQ2:}] To what extent can we reverse engineer API change decisions?
@@
 The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
-The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.o
+The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.
 
@@
 
-\section{Results} \label{results}
+ \newpage
+\section{RQ1} \label{results}
+This section will cover the results.
+
+\subsection{New}
+Intro...
+
+\subsubsection{axaudio}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsubsection{axptz}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsubsection{axstorage}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsubsection{axserialport}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsection{Modified}
+Intro...
+
+\subsubsection{axevent}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsubsection{axhttp}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsubsection{axparameter}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsection{Removed}
+Intro...
+
+\subsubsection{Burst Mode}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsection{General Trends}
+
+Intro...
+
+\subsubsection{Example Code}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsubsection{Documentation}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsubsection{Interfaces}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsubsection{Error Handling}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\subsubsection{3\textsuperscript{rd} Party}
+
+%%Describe the change
+
+%%Relate it to Categories
+
+%%Relate it to Lehman
+
+\section{RQ2}
+Have a table with ours and hers
 

### 2015-04-29 thesis/paper/thesis.tex
Added RQ2 results

@@
 
+%Info from the interview, add to this section
+Has been released, in the form we looked at (supports that we’re doing a ‘real’ case study)
+They have “partners” which develop applications using their API. These applications are then used by the end-users of the camera.
+
 \section{Methodology} \label{methodology}
@@
 
+\subsubsection{axptz}
+
+%%Describe the change 
+Added functionality related movement of the physical camera
+
+%%Relate it to Categories
+Enable users to write applications that mechanically (or digitally) moves the camera
+Requested from partners
+Request ultimately came down from project management
+
+%%Relate it to Lehman
+
 \subsubsection{axaudio}
@@
 %%Describe the change 
+Added functionality related to audio streams
 
 %%Relate it to Categories
-
-%%Relate it to Lehman
-
-\subsubsection{axptz}
-
-%%Describe the change
-
-%%Relate it to Categories
+The most common usage of their API is to analyze video data - but some partners required audio analysis. (At least one partner did already do it, without there being an API for it).
 
@@
 %%Describe the change 
+Added functionality which allows connection to external storage devices
+Before they just put the files in “the normal file system”
 
 %%Relate it to Categories
+Requested from partners
 
@@
 %%Describe the change 
+Adds functionality which allows to connect with other hardware through serial communication
+Allows the possibility to integrate other systems with the camera (such as a ticket dispenser (i guess))
 
 %%Relate it to Categories
+Requested by partners
 
@@
 
+Used to create and handle events such as detecting movement 
+Split up into more files, added functionality, certain structs have been made into their own header files
+
 %%Relate it to Categories
+Re-written because of the other changes to the API (to conform with the new standards)
+They were hard to use
+They were marked as deprecated so that it would not break existing applications using them. 
+They were however not included in the new SDK, so that it would encourage users to use the new, rewritten code
 
@@
 %%Describe the change 
+Converts the data so that it can be displayed on web pages
+Split up into more files, added functionality (concurrency)
 
 %%Relate it to Categories
+Re-written because of the other changes to the API (to conform with the new standards)
+They were hard to use
+They were marked as deprecated so that it would not break existing applications using them. 
+They were however not included in the new SDK, so that it would encourage users to use the new, rewritten code
 
@@
 %%Describe the change 
+Used to change parameters (settings) such as framerate
+Not many changes, but changed so it corresponds with the new design of the API
 
 %%Relate it to Categories
+Re-written because of the other changes to the API (to conform with the new standards)
+They were hard to use
+They were marked as deprecated so that it would not break existing applications using them. 
+They were however not included in the new SDK, so that it would encourage users to use the new, rewritten code
 
@@
 %%Describe the change 
+Burst mode was deprecated
+In Version 2.0 the methods only return null
 
 %%Relate it to Categories
+The feature would have to be re-implemented because of changes to the camera (hardware)
+This would be costly and because of this it was investigated whether or not it would be safe to remove the feature.
+The investigation showed that the impact of the removal would not be significant enough and thus it was removed.
 
@@
 
+Increased commenting and explanations
+Improved examples that cover more functionality
+
 %%Relate it to Categories
+The partners used the examples a lot
+The old examples varied a lot in how they were implemented
+The old ones weren’t good enough
+
+From what she is saying, the intent was mainly:
+to have a unified standard
+which helps the partners to write ‘good’ code
+to cover the new functionality
+to cover specific features
+to show how the features can be used together
 
@@
 
+The documentation has mainly been changed to correspond with the changes to the API itself
+LaTeX support has been removed
+
 %%Relate it to Categories
+One of the main “requests” was to increase functionality (such as ptz) - and the documentation had to be updated accordingly.
 
@@
 %%Describe the change 
+They have gone from having direct access to the headers, to having a facade to access each module
 
 %%Relate it to Categories
+Improvements related to coding standard. (cosmetic)
+These decisions were based on internal discussion.
+Wanted an event driven system
+Driven by internal struggles with using the API to create applications
+
+The need for change was identified through discussions with API users which asked why “it isn’t possible to do it this way instead etc”
 
@@
 %%Describe the change 
+They now store errors in enums in separate header files
+This suggests that changed their error handling to use exceptions
 
 %%Relate it to Categories
+The error handling was changed to correspond with how glib handles errors. 
+The error handling should be more informative + increase usability
+The change would have happened even if glib wasn’t added (but with glib made it “more obvious”)
 
@@
 %%Describe the change 
+2.0 utilizes more 3rd party libraries
+axsound, for example, uses alsa
+All modules use glib
 
 %%Relate it to Categories
+
+Architects decided to use glib, part of an internal decision.
 
@@
 Have a table with ours and hers
+
+\subsection{Continuing Change — an E-type system must be continually adapted or it becomes progressively less satisfactory}
+
+\subsection{Increasing Complexity — as an E-type system evolves, its complexity increases unless work is done to maintain or reduce it}
+
+\subsection{Self Regulation — E-type system evolution processes are self-regulating with the distribution of product and process measures close to normal}
+
+\subsection{Conservation of Organisational Stability (invariant work rate) - the average effective global activity rate in an evolving E-type system is invariant over the product's lifetime}
+
+\subsection{Conservation of Familiarity — as an E-type system evolves, all associated with it, developers, sales personnel and users, for example, must maintain mastery of its content and behaviour to achieve satisfactory evolution.
+Excessive growth diminishes that mastery.
+Hence the average incremental growth remains invariant as the system evolves.}
+
+\subsection{Continuing Growth — the functional content of an E-type system must be continually increased to maintain user satisfaction over its lifetime}
+
+\subsection{Declining Quality — the quality of an E-type system will appear to be declining unless it is rigorously maintained and adapted to operational environment changes}
+
+\subsection{Feedback System — E-type evolution processes constitute multi-level, multi-loop, multi-agent feedback systems and must be treated as such to achieve significant improvement over any reasonable base}
 

### 2015-04-29 thesis/paper/thesis.tex
Shortened headers for lehman

@@
 
-\subsection{Continuing Change — an E-type system must be continually adapted or it becomes progressively less satisfactory}
+\subsection{Continuing Change — a system must be continually adapted or it becomes progressively less satisfactory}
 
-\subsection{Increasing Complexity — as an E-type system evolves, its complexity increases unless work is done to maintain or reduce it}
+\subsection{Increasing Complexity — as system evolves, its complexity increases unless work is done to maintain or reduce it}
 
@@
 
-\subsection{Conservation of Organisational Stability (invariant work rate) - the average effective global activity rate in an evolving E-type system is invariant over the product's lifetime}
+\subsection{Conservation of Organisational Stability - global work rate is invariant over the product's lifetime}
 
-\subsection{Conservation of Familiarity — as an E-type system evolves, all associated with it, developers, sales personnel and users, for example, must maintain mastery of its content and behaviour to achieve satisfactory evolution.
-Excessive growth diminishes that mastery.
-Hence the average incremental growth remains invariant as the system evolves.}
+\subsection{Conservation of Familiarity — developers, sales personnel and users, for example, must maintain mastery of content and behaviour to achieve satisfactory evolution}
 
-\subsection{Continuing Growth — the functional content of an E-type system must be continually increased to maintain user satisfaction over its lifetime}
+\subsection{Continuing Growth — the functional content must be continually increased to maintain user satisfaction}
 
-\subsection{Declining Quality — the quality of an E-type system will appear to be declining unless it is rigorously maintained and adapted to operational environment changes}
+\subsection{Declining Quality — the quality will appear to decline unless it is rigorously maintained and adapted}
 
-\subsection{Feedback System — E-type evolution processes constitute multi-level, multi-loop, multi-agent feedback systems and must be treated as such to achieve significant improvement over any reasonable base}
+\subsection{Feedback System — multi-level, multi-loop, multi-agent feedback systems}
 

### 2015-04-29 thesis/paper/thesis.tex
Added interview data

@@
 \begin{description}
-\item[\textbf{RQ1:}] What drives API evolution?
-\item[\textbf{RQ2:}] To what extent can we reverse engineer API change decisions?
+\item[\textbf{RQ1:}] How do companies actively drive API evolution?
+\item[\textbf{RQ2:}] How do APIs evolve?
+\item[\textbf{RQ3:}] To what extent can we reverse engineer API change decisions?
+
 \end{description}
@@
 They have “partners” which develop applications using their API. These applications are then used by the end-users of the camera.
+
+%%
+Hardware
+The API platform is developed for many different types of cameras. 
+Some have audio, some don’t, for example.
 
@@
 
-%%Relate it to Lehman
-
 \subsubsection{axaudio}
@@
 The most common usage of their API is to analyze video data - but some partners required audio analysis. (At least one partner did already do it, without there being an API for it).
-
-%%Relate it to Lehman
 
@@
 
-%%Relate it to Lehman
-
 \subsubsection{axserialport}
@@
 Requested by partners
-
-%%Relate it to Lehman
 
@@
 
-%%Relate it to Lehman
-
 \subsubsection{axhttp}
@@
 
-%%Relate it to Lehman
-
 \subsubsection{axparameter}
@@
 They were however not included in the new SDK, so that it would encourage users to use the new, rewritten code
-
-%%Relate it to Lehman
 
@@
 The investigation showed that the impact of the removal would not be significant enough and thus it was removed.
-
-%%Relate it to Lehman
 
@@
 
-%%Relate it to Lehman
-
 \subsubsection{Documentation}
@@
 
-%%Relate it to Lehman
-
 \subsubsection{Interfaces}
@@
 They have gone from having direct access to the headers, to having a facade to access each module
+
+The new interfaces are all based on callbacks. 
+One interface that was not touched was capture.h (Except for the deprecated burst method).
+She thinks that it probably should have been re-implemented to bring it in line and to be consistent they should bring it into line at some point.
+It wasn’t required as the implementation didn’t actually change.
 
@@
 The need for change was identified through discussions with API users which asked why “it isn’t possible to do it this way instead etc”
-
-%%Relate it to Lehman
 
@@
 
-%%Relate it to Lehman
-
 \subsubsection{3\textsuperscript{rd} Party}
@@
 
-%%Relate it to Lehman
+\section{RQ2 Lehman}
 
-\section{RQ2}
-Have a table with ours and hers
+\subsection{1 Continuing Change — a system must be continually adapted or it becomes progressively less satisfactory}
 
-\subsection{Continuing Change — a system must be continually adapted or it becomes progressively less satisfactory}
+Their partners are good at solving problems, so anything lacking from the API was solved, but in a way that they didn’t not think was a good way.
 
-\subsection{Increasing Complexity — as system evolves, its complexity increases unless work is done to maintain or reduce it}
+Overall the impression given suggested that it is important to improve the APIs. She even told us that some partners had requested more frequent updates to include or add new features to the API.
 
-\subsection{Self Regulation — E-type system evolution processes are self-regulating with the distribution of product and process measures close to normal}
+\subsection{2 Increasing Complexity — as system evolves, its complexity increases unless work is done to maintain or reduce it}
 
-\subsection{Conservation of Organisational Stability - global work rate is invariant over the product's lifetime}
+Previously she had mentioned that it’s important to have consistency and to follow standards, especially when creating an API.
 
-\subsection{Conservation of Familiarity — developers, sales personnel and users, for example, must maintain mastery of content and behaviour to achieve satisfactory evolution}
+She did mention that one, albeit minor reason for re-implementation of certain parts of the API was to bring into line with the rest of the new interfaces.
 
-\subsection{Continuing Growth — the functional content must be continually increased to maintain user satisfaction}
+It’s often easier to make a good API if you follow a guideline which tells you how to make a good API. Following these tends to lead to good APIs.
 
-\subsection{Declining Quality — the quality will appear to decline unless it is rigorously maintained and adapted}
+She feels it’s more important to have more features than to have a strong emphasis on the cosmetic side. However, they should work well together and be simple to use.
 
-\subsection{Feedback System — multi-level, multi-loop, multi-agent feedback systems}
+One counter example of this however is that they did not re-implement the capture.h interface, despite the fact it had some redacted features and that it retains the previous implementation style.
 
-\section{Conclusion} \label{conclusion}
+\subsection{3 Self Regulation — E-type system evolution processes are self-regulating with the distribution of product and process measures close to normal}
+If we look at the system growth as a normal distribution curve, it grew slowly in the beginning (1.0-1.4) and right now (2.0) we're in the peak of the curve and she said about hte future that it was going to be slow with few changes.
+
+Post 2.0 - The API will continue to improve, but in they are far away in the future.
+If there is a new API coming, there will not be a big bang this time but instead incremental steps.
+For example adding new suitable features for partners.
+It won’t be a 2.0->3.0 big bang again.
+
+\subsection{4 Conservation of Organisational Stability - global work rate is invariant over the product's lifetime}
+Before 1.4
+No major changes have been made. 
+The only change was that you could build it for more platforms
+
+Version 1.0 was created, with incremental increases due to making other platforms available.
+There was only one major update which was to 2.0.
+In total there has only been two major updates (1.0 and 2.0).
+Impression was that there was not even many official incremental builds internally.
+She did express earlier on in the interview that features were being created internally that ended up becoming part of the 2.0 API.
+
+\subsection{5 Conservation of Familiarity — developers, sales personnel and users, for example, must maintain mastery of content and behaviour to achieve satisfactory evolution}
+There are no current restrictions on ACAP so it’s essentially a Linux system, meaning that they can do whatever they want with it.
+
+Primarily the SDK is what was communicated to the partners / users of the API.
+
+Little to no influence over the APIs.
+There are things that could be better than they are, for example they have to query the camera to see what it supports.
+She feels that they need to improve on this aspect.
+It’s hard to know this / do this when you’re not using the API.
+(This seems to suggest that they don’t use it as often internally, or that there is something missing in the documentation?)
+
+\subsection{6 Continuing Growth — the functional content must be continually increased to maintain user satisfaction}
+
+She reiterated that they want to add new features and modules.
+They want to encourage applications to be written by their partners, so if they don’t add new modules they will not have new applications created for them.
+When partners write applications for their cameras, the value of the cameras are enhanced so they would like to encourage partners creating new applications for their cameras.
+
+It’s better to provide good solutions so that they don’t need to create their own custom solutions and enable good applications to be made.
+(Assuming that she's talking about add more functionality so that people won't have to do stuff in their own weird ways)
+
+She was surprised that the view was that the API is more stable than they thought it was.
+i.e.
+the partners would like more changes.
+Firmware upgrades always worked with the API, there were very few issues.
+
+\subsection{7 Declining Quality — the quality will appear to decline unless it is rigorously maintained and adapted}
+Updates to documentation
+Updates to interfaces and error handling
+
+It's not 100\% true for APIs, because updating it too often will cause other problems --> ``rigorously''
+
+\subsection{8 Feedback System — multi-level, multi-loop, multi-agent feedback systems}
+She would like to get more feedback from the API users and the end-users - to better include this in the feedback loop and in turn use it to form change decisions
+
+No “scientific” theories have been used when creating the APIs - most decisions have been based on experience (expertise) and previous experience
+
+There hasn’t been anything created by the users which has then been implemented into the API.
+However, there are partners who have created features which were then later included.
+i.e.
+Audio (This is not to say that they used the API that the partners had developed!)
+
+She is unaware of any metrics that they have.
+She would have to ask the ADP engineers for anything like this.
+She doesn’t personally know if there have been any issues or problems with the current API.
+She would like to have more feedback and input when things are working correctly, normally they only have feedback when things don’t work.
+Other than the feedback she mentioned previously, i.e.
+partners requesting features.
+
+They had some kind of validation testing whereby they had someone internally attempt to create an application using all parts of the API.
+It was during the development process and was successful but it also provided them with some key feedback.
+She suggested that this kind of testing should be increased and that they do need more of it.
+(This was only one application, as it differs a lot)
+
+Communication with users currently only really gives them bug reports, FAQs (Educational Issues) or queries about how to do something could indicate that there are missing features in the API.
+This is something that the product management deal with, rather than her.
+She focuses more on the how rather than the what.
+What it comes to decide what interface to do, PM decide and she then comes along and decides how it would look / be done.
+
+\section{RQ3 Reverse Engineer}
+Table of hers and ours
+
+And one section discussing why her answers correspond to the categories we chose.
+
+\section{Conclusion RQ2} \label{conclusion}
+
+%%John add conclusion ideas here
+
+Considering the Ecosystem and considering it as a whole when designing the API.
+She does not think that they did take it into consideration at all.
+They had not thought about them when designing the APIs.
+She does think about who is going to use it and how but nothing in regards to how it affects an ecosystem as a whole.
+Things like allowing embedded webpages for the ACAP allows users to get more information from their system meaning they don’t need to ask for as much help and assistance.
+They usually integrate this with the VMS.
+Overall there was not much thought about ecosystem when the API was designed.
+She’s unsure if it’s one ecosystem or two.
+The network APIs and their API.
+Perhaps it is one ecosystem.
+(this is something Imed is looking at).
+It seems that a focus on ecosystems might be starting to come through but that they already thought about them without calling them ecosystems.
+For example, her mentioning that they already did think about the users of the API and how they would be using it gives a slight clue that they do already think about the wider audience of their API.
+
+%%William add conclusion ideas here
+
+\subsection{Law 1}
+
+Problem: Leads to potentially unsafe implementations to get around shortcomings of the API
 

### 2015-04-29 thesis/paper/thesis.tex
law 1

@@
 \section{RQ2 Lehman}
+This section will present results related to \textbf{RQ2}. The information introduced was collected during the interview with the case company.
 
 \subsection{1 Continuing Change — a system must be continually adapted or it becomes progressively less satisfactory}
-
-Their partners are good at solving problems, so anything lacking from the API was solved, but in a way that they didn’t not think was a good way.
-
-Overall the impression given suggested that it is important to improve the APIs. She even told us that some partners had requested more frequent updates to include or add new features to the API.
+From the information that was gathered in the interviews, we can conclude that Law \# 1 is holds for APIs.
+The case company described that including new functional content was one of the top priorities for the 2.0 release.
+It was also mentioned that the API users had previously reqeusted more frequent updates to the API, despite the drawbacks this could have.
+One of the main reasons for continuously adapting the API is also to force (!!!wording) the API users to use the API in the way that it is intended.
+Previously, many applications which worked around the lacking (!!!negative wording) functionality had been developed.
+These applications were fully functional, but were developed very differently from user to user (!!!wording).
 
@@
 %%William add conclusion ideas here
+It's interesting that the partners have mentioned that they want more frequent updates... maybe API developers should be less afraid of updating them?
 

### 2015-04-29 thesis/paper/thesis.tex
law 2

@@
 
+\newpage
 \section{RQ2 Lehman}
@@
 \subsection{1 Continuing Change — a system must be continually adapted or it becomes progressively less satisfactory}
-From the information that was gathered in the interviews, we can conclude that Law \# 1 is holds for APIs.
 The case company described that including new functional content was one of the top priorities for the 2.0 release.
+This is supported by the characteristic of the changes identified in this study.
+4 of the 13 changes were additions of new modules, and in the re-implemented modules a lot of functional content was added, too.
 It was also mentioned that the API users had previously reqeusted more frequent updates to the API, despite the drawbacks this could have.
@@
 These applications were fully functional, but were developed very differently from user to user (!!!wording).
+We therefore conclude that Law \#1 holds for APIs.
 
 \subsection{2 Increasing Complexity — as system evolves, its complexity increases unless work is done to maintain or reduce it}
-
-Previously she had mentioned that it’s important to have consistency and to follow standards, especially when creating an API.
-
-She did mention that one, albeit minor reason for re-implementation of certain parts of the API was to bring into line with the rest of the new interfaces.
-
-It’s often easier to make a good API if you follow a guideline which tells you how to make a good API. Following these tends to lead to good APIs.
-
-She feels it’s more important to have more features than to have a strong emphasis on the cosmetic side. However, they should work well together and be simple to use.
-
-One counter example of this however is that they did not re-implement the capture.h interface, despite the fact it had some redacted features and that it retains the previous implementation style.
+A large part of the changes made to the API were made to improve the structure and the way that the API is used.
+Many of these changes were related to the same design choices, which enforced a certain implementation style on the whole API.
+One example of this is the change to the interfaces which set a standard for the whole API.
+During the interview it was also concluded that consistency and following certain standards is an important factor to consider when designing APIs.
+It was also made clear a contributing factor for changing certain parts of the API was to bring it in line with the new interfaces.
+The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that the company currently did not make use of these.
+Even though the importance of maintaining the API to reduce complexity was stated, arguments which support that it is of lesser importance than releasing functional content was also presented.
+One example of where this is evident in the evolution of the API, is in the module that handles the video capturing and video stream.
+It was decided that this module would not be re-written to conform with the new interface standard, as there was not much functional content that would change in this module, anyways (!!!reword).
+Thus, Law \#2 holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.
 

### 2015-04-29 thesis/paper/thesis.tex
law 3

@@
 \subsection{3 Self Regulation — E-type system evolution processes are self-regulating with the distribution of product and process measures close to normal}
-If we look at the system growth as a normal distribution curve, it grew slowly in the beginning (1.0-1.4) and right now (2.0) we're in the peak of the curve and she said about hte future that it was going to be slow with few changes.
-
-Post 2.0 - The API will continue to improve, but in they are far away in the future.
-If there is a new API coming, there will not be a big bang this time but instead incremental steps.
-For example adding new suitable features for partners.
-It won’t be a 2.0->3.0 big bang again.
+When version 1.4 was introduced, no new functionality or re-structuring was introduced.
+Version 1.4 only added support for additional build platforms.
+When comparing the changes introduced in 2.0 to the ones previously introduced, it is clear that the growth of the API has increased gradually.
+During the interview it was also mentioned that the future plans for the API did not include any major changes, and that only a few minor changes were planned in the near future.
+The future updates to the API will also be made incrementally, and there will not be a big bang update similar to the one of 2.0.
+This supports that Law \#3 can be applied to APIs, assuming that the current stage of the life-cycle of the API can be considered as the center of the normal distribution curve of the APIs growth.
 

### 2015-04-29 thesis/paper/thesis.tex
Added drafts for Added parts of the API

@@
 \section{RQ1} \label{results}
-This section will cover the results.
+
+Each change is categorised by a type, such as new, reimplementation etc
+
+Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories.
 
 \subsection{New}
-Intro...
+
+%%TODO Finish this off
+New additions to the API were the most frequent change that we observed.
+Each addition added new functionality to the API, ranging from controlling the camera, enabling audio analysis, allowing external storage connections and providing a serial port to interface with other devices.
 
@@
 
-%%Describe the change 
-Added functionality related movement of the physical camera
+This change introduced the ability to perform Pan, Tilt and Zoom (ptz) manoeuvres both mechanically and digitally on the camera.
+For example, zooming in on a particular section of a large image, panning the camera to the left to view a certain area.
 
-%%Relate it to Categories
-Enable users to write applications that mechanically (or digitally) moves the camera
-Requested from partners
-Request ultimately came down from project management
+When categorising this change, we concluded that this was enhancive, simply  because it was a brand-new feature of the API. No sub categories were found to be suitable for this change.
+
+%%Explain what she said
+The interviewee described how this change and the 3 following changes were all included in the new API at the request of both API users and product management.
+The feature was sought after by API users frequently, while they were able to control the camera, there was no official application for doing so and as such, it was a good candidate for inclusion in the new API.
+
+%%Explain how this relates to the category
+Based on the interviewees comments, we concluded that we had correctly identified the change as being enhancive.
+Furthermore, we were also correct in our assumption that there were no suitable subcategories as there was no additional insight into other motivations for the inclusion of this feature.
 
@@
 %%Describe the change 
-Added functionality related to audio streams
+By and large the most common usage of the camera is to analyse video data, however some of the API users require audio data.
+The inclusion of axaudio allows these users to perform audio analysis upon audio streams captured by Axis devices.
 
 %%Relate it to Categories
-The most common usage of their API is to analyze video data - but some partners required audio analysis. (At least one partner did already do it, without there being an API for it).
+This change was also determined to be enhancive as it was an inclusion of a brand-new feature to the API.
+Similarly to the axptz, there were no suitable sub categories that could be found to apply to this change.
+
+%%What she said
+Audio analysis had not previously been possible on Axis devices.
+However, the interviewer informed us that an API user had managed to create their own audio analysis using the current (1.4) API.
+Given the demand for audio analysis, it was a logical choice to include it as a new feature in the new version of the API.
+
+%%Category based on her information
+Based on the information available, we concluded that we had successfully determined that the change was enhancive.
+Once more, there was no supporting evidence to suggest any suitable subcategories for this change.
 
@@
 %%Describe the change 
-Added functionality which allows connection to external storage devices
-Before they just put the files in “the normal file system”
+Prior to the newest version of the API, storage for the devices existed solely on the cameras or the Video Management System (VMS) itself.
+The release of version 2.0 saw the inclusion of alternative storage solutions.
+axstorage now allows Axis devices to interface with external storage devices, such as
+
+Ehancive was once again chosen to be the most applicable category of change given that axstorage was a brand-new inclusion in the newest version of the API.
+Similarly, there were no appropriate subcategories for this change.
+
+%%Her information
+The limited storage options for the Axis devices meant that this feature was strongly requested by API users and as such was included in this new version of the API.
 
 %%Relate it to Categories
-Requested from partners
+The information gathered from the interview suggests (!!!Better word than this?) that were correct in our choice of enhancive for this change.
+Once more there was no inclusion of an appropriate subcategory.
 
@@
 
+The final new feature of the API was the inclusion of axserial.
+This part of the API allows API users to connect various devices to their cameras through the use of a serial port.
+This effectively allows users to integrate multiple kinds of devices to create their own unique solutions.
+In the previous version of the API there was no ability to connect to devices outside of the VMS.
+
 %%Relate it to Categories
-Requested by partners
+The inclusion of this new feature was once again determined to be an ehancive change as it involved the addition of a brand new feature. No relevant subcategories were found.
+
+Our interviewee described scenarios whereby a camera could be used with external devices to create, for example, a ticketing system which reacts to users interacting with it in close proximity.
+This was just one scenario in which users might wish to use the camera with other devices.
+As such it was included in the new API to meet the demand of the API users.
+
+%%Real category
+Given this information, we concluded that we were correct in deciding that this change was also enhancive.
+Again, we were also correct in the assumption that there were no suitable subcategories for this change.
 
 \subsection{Modified}
-Intro...
 

### 2015-04-29 thesis/paper/thesis.tex
Added more drafts

@@
 \subsection{Modified}
+These changes were deemed to be modifications or re-implementations of existing functionality of the API.
+
+In regards to re-implementations, during the interview it was mentioned that one intent behind the re-implementations was to bring them inline with the newly created functionality which take advantage of Glib, a new kind of error handling and extensive use of callbacks.
 
@@
 %%Describe the change 
-
-Used to create and handle events such as detecting movement 
-Split up into more files, added functionality, certain structs have been made into their own header files
+Version 2.0 of the API has been designed around an event driven system, as such, it's not surprising that the old event system had to be re-implemented.
+The new event system is used by all features of the new API, for example events are sent when movement is detected by the camera.
+This event system is combined with the use of callbacks to create a robust event driven API.
 
 %%Relate it to Categories
-Re-written because of the other changes to the API (to conform with the new standards)
-They were hard to use
-They were marked as deprecated so that it would not break existing applications using them. 
-They were however not included in the new SDK, so that it would encourage users to use the new, rewritten code
+Given that this feature was a re-implementation, we concluded that it should be classified mainly as an enhancive change with the subcategory of change being classified as groomative.
+Groomative was chosen as a subcategory due to the alternate intention of bringing the new feature in line with the new interface.
+
+The interviewee mentioned that the previous version of axevent, event, was being deprecated in favour of this new implementation.
+The primary reason was to bring the implementation into line with the new way that the API handles events and interfaces as a whole.
+The interviewee mentioned that they realised that the API was hard to use previously and that improving it this way, through the use of re-implementations, could allow them to create an easier to use API.
+
+Groomative is therefore the obvious choice for the main category for this change with enhancive being the subcategory.
+This is the opposite of what we concluded and as such means that we incorrectly determined the intent for this change.
 
@@
 The need for change was identified through discussions with API users which asked why “it isn’t possible to do it this way instead etc”
+
+Re-written because of the other changes to the API (to conform with the new standards)
+They were hard to use
+They were marked as deprecated so that it would not break existing applications using them. 
+They were however not included in the new SDK, so that it would encourage users to use the new, rewritten code
 

### 2015-04-29 thesis/paper/thesis.tex
law 4

@@
 
-\subsection{1 Continuing Change — a system must be continually adapted or it becomes progressively less satisfactory}
+\subsection{Law 1: Continuing Change}
 The case company described that including new functional content was one of the top priorities for the 2.0 release.
@@
 
-\subsection{2 Increasing Complexity — as system evolves, its complexity increases unless work is done to maintain or reduce it}
+\subsection{Law 2: Increasing Complexity}
 A large part of the changes made to the API were made to improve the structure and the way that the API is used.
@@
 
-\subsection{3 Self Regulation — E-type system evolution processes are self-regulating with the distribution of product and process measures close to normal}
+\subsection{Law 3: Self Regulation} \label{law3}
 When version 1.4 was introduced, no new functionality or re-structuring was introduced.
@@
 
-\subsection{4 Conservation of Organisational Stability - global work rate is invariant over the product's lifetime}
-Before 1.4
-No major changes have been made. 
-The only change was that you could build it for more platforms
+\subsection{Law 4: Conservation of Organisational Stability}
+The changes to the ACAP API has been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
+As mentioned in Section \ref{law3} the changes introduced in version 1.4 did not involve any changes to the existing API functions.
+Consequently, the only significant update to the API was made in the transition to version 2.0.
+The internal development of the API has also been made sporadically, and there have been periods where the API has not been actively developed.
+This suggests that Law \#4 does not apply to APIs.
 
-Version 1.0 was created, with incremental increases due to making other platforms available.
-There was only one major update which was to 2.0.
-In total there has only been two major updates (1.0 and 2.0).
-Impression was that there was not even many official incremental builds internally.
-She did express earlier on in the interview that features were being created internally that ended up becoming part of the 2.0 API.
+\subsection{Law 5: Conservation of Familiarity}
+The SDK that is included with the API.
 
-\subsection{5 Conservation of Familiarity — developers, sales personnel and users, for example, must maintain mastery of content and behaviour to achieve satisfactory evolution}
 There are no current restrictions on ACAP so it’s essentially a Linux system, meaning that they can do whatever they want with it.

### 2015-04-29 thesis/paper/thesis.tex
law 5

@@
 
-\subsection{Law 1: Continuing Change}
+\subsection{Law \#1: Continuing Change}
 The case company described that including new functional content was one of the top priorities for the 2.0 release.
@@
 
-\subsection{Law 2: Increasing Complexity}
+\subsection{Law \#2: Increasing Complexity}
 A large part of the changes made to the API were made to improve the structure and the way that the API is used.
@@
 
-\subsection{Law 3: Self Regulation} \label{law3}
+\subsection{Law \#3: Self Regulation} \label{law3}
 When version 1.4 was introduced, no new functionality or re-structuring was introduced.
@@
 
-\subsection{Law 4: Conservation of Organisational Stability}
+\subsection{Law \#4: Conservation of Organisational Stability}
 The changes to the ACAP API has been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
@@
 
-\subsection{Law 5: Conservation of Familiarity}
-The SDK that is included with the API.
+\subsection{Law \#5: Conservation of Familiarity}
+The SDK that is included with the API was rigorously updated with the introduction of version 2.0.
+All functionality which was added or modified in version 2.0 was updated accordlingly in the SDK.
+The same pattern can be seen for the example code, which went through major changes as a result of the changes to the API code.
+The case company's intent to control the way that their API is used also suggests that the knowledge of how to use the API is of importance, since if the API is used in too many different ways, it will be more difficult for the case company to have relevant documentation and example code.
+It was also expressed during the interview that further transparency in how the API should be used could be achieved.
+One example of this is to improve the information to the user regarding which API functions are supported on which hardware types.
+These facts support that the conservation of familiarity is an important factor to consider when maintaining APIs.
 
-There are no current restrictions on ACAP so it’s essentially a Linux system, meaning that they can do whatever they want with it.
-
-Primarily the SDK is what was communicated to the partners / users of the API.
-
-Little to no influence over the APIs.
-There are things that could be better than they are, for example they have to query the camera to see what it supports.
-She feels that they need to improve on this aspect.
-It’s hard to know this / do this when you’re not using the API.
-(This seems to suggest that they don’t use it as often internally, or that there is something missing in the documentation?)
-
-\subsection{6 Continuing Growth — the functional content must be continually increased to maintain user satisfaction}
+\subsection{Law \#6: Continuing Growth — the functional content must be continually increased to maintain user satisfaction}
 

### 2015-04-30 thesis/acm/paper.tex
Added acm template

--- 2015-04-29 thesis/paper/thesis.tex
@@
-\documentclass[conference]{IEEEtran}
+\documentclass{sig-alternate}
 \usepackage{blindtext}
@@
 \begin{document}
-\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
 
-\author{\IEEEauthorblockN{John Burchell}
-\IEEEauthorblockA{Computer Science and Engineering\\University of Gothenburg\\Gothenburg, Sweden\\
-Email: john.a.burchell@gmail.com} \and
-\IEEEauthorblockN{William Granli}
-\IEEEauthorblockA{Computer Science and Engineering\\University of Gothenburg\\Gothenburg, Sweden\\
-Email: william.granli@gmail.com}}
+\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+
+\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective
+\titlenote{(Produces the permission block, and
+copyright information). For use with
+SIG-ALTERNATE.CLS. Supported by ACM.}}
+\subtitle{[Extended Abstract]
+\titlenote{A full version of this paper is available as \textit{Author's Guide to Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.acm.org/eaddress.htm}}}
+
+\numberofauthors{3}
+
+\author{
+% 1st. author
+\alignauthor
+John Burhcell\titlenote{I am da main author}\\
+       \affaddr{Institute for Clarity in Documentation}\\
+       \affaddr{1932 Wallamaloo Lane}\\
+       \affaddr{Wallamaloo, New Zealand}\\
+       \email{trovato@corporation.com}
+% 2nd. author
+\alignauthor
+William Granli\titlenote{I am da main author}\\
+       \affaddr{Institute for Clarity in Documentation}\\
+       \affaddr{P.O. Box 1212}\\
+       \affaddr{Dublin, Ohio 43017-6221}\\
+       \email{webmaster@marysville-ohio.com}
+% 3rd. author
+\alignauthor Imed Hammouda\titlenote{I am da co-author}\\
+       \affaddr{The Th{\o}rv{\"a}ld Group}\\
+       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
+       \affaddr{Hekla, Iceland}\\
+       \email{larst@affiliation.org}
+}
 
 \maketitle
-
 \begin{abstract}
@@
 \end{abstract}
+
+% A category with the (minimum) three required fields
+\category{H.4}{Information Systems Applications}{Miscellaneous}
+%A category including the fourth, optional field follows...
+\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+
+\terms{Theory}
+
+\keywords{ACM proceedings, \LaTeX, text tagging}
 
@@
 
-\section*{Acknowledgement} \label{acknowledgement}
+\section{Acknowledgments}
 
-\bibliographystyle{bibstyle}
+\bibliographystyle{abbrv}
 \bibliography{bib}

### 2015-04-30 thesis/acm/paper.tex
law 6

@@
 
+%Old
 Due to the negative implications that modifications to APIs cause for its users, it is important to understand why changes to them occur.
@@
 Subsequently, the designers of the API will be interviewed and asked to verify the accuracy of our findings.
+%Old
 
@@
 
-\subsection{Law \#1: Continuing Change}
+\subsection{Continuing Change}
 The case company described that including new functional content was one of the top priorities for the 2.0 release.
@@
 These applications were fully functional, but were developed very differently from user to user (!!!wording).
-We therefore conclude that Law \#1 holds for APIs.
+We therefore conclude that the law of continuing change holds for APIs.
 
-\subsection{Law \#2: Increasing Complexity}
+\subsection{Increasing Complexity}
 A large part of the changes made to the API were made to improve the structure and the way that the API is used.
@@
 It was decided that this module would not be re-written to conform with the new interface standard, as there was not much functional content that would change in this module, anyways (!!!reword).
-Thus, Law \#2 holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.
+Thus, the law of increasing complexity holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.
 
-\subsection{Law \#3: Self Regulation} \label{law3}
+\subsection{Self Regulation} \label{law3}
 When version 1.4 was introduced, no new functionality or re-structuring was introduced.
@@
 The future updates to the API will also be made incrementally, and there will not be a big bang update similar to the one of 2.0.
-This supports that Law \#3 can be applied to APIs, assuming that the current stage of the life-cycle of the API can be considered as the center of the normal distribution curve of the APIs growth.
+This supports that the law of self regulation applies to APIs, assuming that the current stage of the life-cycle of the API can be considered as the center of the normal distribution curve of the APIs growth.
 
-\subsection{Law \#4: Conservation of Organisational Stability}
+\subsection{Conservation of Organisational Stability}
 The changes to the ACAP API has been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
@@
 The internal development of the API has also been made sporadically, and there have been periods where the API has not been actively developed.
-This suggests that Law \#4 does not apply to APIs.
+This suggests that the law of conservation of organisational stability does not apply to APIs.
 
-\subsection{Law \#5: Conservation of Familiarity}
+\subsection{Conservation of Familiarity}
 The SDK that is included with the API was rigorously updated with the introduction of version 2.0.
@@
 One example of this is to improve the information to the user regarding which API functions are supported on which hardware types.
-These facts support that the conservation of familiarity is an important factor to consider when maintaining APIs.
+These facts support that the law of conservation of familiarity is true for APIs.
 
-\subsection{Law \#6: Continuing Growth — the functional content must be continually increased to maintain user satisfaction}
+\subsection{Continuing Growth}
+Large parts of the changes between the versions were strictly additions of new functional content.
+4 new modules were added, and significant additions of new functionality were added to the modules which were re-structured from version 1.4.
+The interviewee also made it clear that increasing the functionality was one of the major goals with the 2.0 update.
+This also ties in with the ambition of controlling the way the API users use the API, as mentioned previously.
+It was also mentioned that the case company had recieved feedback from the API users that more frequent updates to the functional content was desirable, even though this may require them to update their application code.
+Because of this, we conclude that the law of continuing growth applies to APIs.
 
-She reiterated that they want to add new features and modules.
-They want to encourage applications to be written by their partners, so if they don’t add new modules they will not have new applications created for them.
-When partners write applications for their cameras, the value of the cameras are enhanced so they would like to encourage partners creating new applications for their cameras.
-
-It’s better to provide good solutions so that they don’t need to create their own custom solutions and enable good applications to be made.
-(Assuming that she's talking about add more functionality so that people won't have to do stuff in their own weird ways)
-
-She was surprised that the view was that the API is more stable than they thought it was.
-i.e.
-the partners would like more changes.
-Firmware upgrades always worked with the API, there were very few issues.
-
-\subsection{7 Declining Quality — the quality will appear to decline unless it is rigorously maintained and adapted}
+\subsection{Declining Quality — the quality will appear to decline unless it is rigorously maintained and adapted}
 Updates to documentation
@@
 
-\subsection{8 Feedback System — multi-level, multi-loop, multi-agent feedback systems}
+\subsection{Feedback System — multi-level, multi-loop, multi-agent feedback systems}
 She would like to get more feedback from the API users and the end-users - to better include this in the feedback loop and in turn use it to form change decisions
@@
 What it comes to decide what interface to do, PM decide and she then comes along and decides how it would look / be done.
-
-\section{RQ3 Reverse Engineer}
-Table of hers and ours
-
-And one section discussing why her answers correspond to the categories we chose.
 

### 2015-04-30 thesis/acm/paper.tex
Initial Draft of My sections

@@
 \alignauthor
-John Burhcell\titlenote{I am da main author}\\
+John Burchell\titlenote{I am da main author}\\
        \affaddr{Institute for Clarity in Documentation}\\
@@
 
-Each change is categorised by a type, such as new, reimplementation etc
-
+Each change between versions has been identified and grouped into three particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
 Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories.
+Each change was given a main category of maintenance and a subcategory if appropriate.
 
@@
 
-When categorising this change, we concluded that this was enhancive, simply  because it was a brand-new feature of the API. No sub categories were found to be suitable for this change.
+We concluded that this change was enhancive as it is a brand-new feature of the API. No sub categories were found to be suitable.
 
@@
 
-Ehancive was once again chosen to be the most applicable category of change given that axstorage was a brand-new inclusion in the newest version of the API.
+Enhancive was once again chosen to be the most applicable category of change given that axstorage was a brand-new inclusion in the newest version of the API.
 Similarly, there were no appropriate subcategories for this change.
@@
 
-The final new feature of the API was the inclusion of axserial.
+The final new feature of the API was the inclusion of axserialport.
 This part of the API allows API users to connect various devices to their cameras through the use of a serial port.
@@
 %%Relate it to Categories
-The inclusion of this new feature was once again determined to be an ehancive change as it involved the addition of a brand new feature. No relevant subcategories were found.
+The inclusion of this new feature was once again determined to be an enhancive change as it involved the addition of a brand new feature. No relevant subcategories were found.
 
@@
 
-In regards to re-implementations, during the interview it was mentioned that one intent behind the re-implementations was to bring them inline with the newly created functionality which take advantage of Glib, a new kind of error handling and extensive use of callbacks.
+In regards to re-implementations, during the interview it was mentioned that one intent behind the re-implementations was to bring them in-line with the newly created functionality which take advantage of Glib, a new kind of error handling and extensive use of callbacks.
 
@@
 Groomative is therefore the obvious choice for the main category for this change with enhancive being the subcategory.
-This is the opposite of what we concluded and as such means that we incorrectly determined the intent for this change.
+This is the reverse of what we concluded and as such means that we incorrectly determined the intent for this change.
 
@@
 %%Describe the change 
-Converts the data so that it can be displayed on web pages
-Split up into more files, added functionality (concurrency)
+axhttp was re-implemented from the previous version of the API to follow the new interface and callbacks standards while also including the event driven architecture of 2.0.
+Functionality remained similar in that it allowed the conversion of data into html in order to display on web pages.
 
-%%Relate it to Categories
-Re-written because of the other changes to the API (to conform with the new standards)
-They were hard to use
-They were marked as deprecated so that it would not break existing applications using them. 
-They were however not included in the new SDK, so that it would encourage users to use the new, rewritten code
+This change is very similar to the previously mentioned change and as such is classified in the same way; a main categorisation of enhancive with groomative as the subcategory of change.
+
+The interviewee again described how the main intent to changing this part of the API came about most to bring it into line with the new event driven and callback focused architecture.
+Similarly to the previous change, this feature was redesigned and re-implemented with added functionality.
+
+Our conclusion of enhancive and groomative was also backwards for this change.
+As per the previous change, the primary intent was to bring these parts of the API into line with the new standard; improving functionality was an added bonus.
 
@@
 %%Describe the change 
-Used to change parameters (settings) such as framerate
-Not many changes, but changed so it corresponds with the new design of the API
+The final re-implementation updated the parameter setting features of the API.
+This particular module had very few changes to it's functionality except for bringing into line, once again, with the new standard.
 
-%%Relate it to Categories
-Re-written because of the other changes to the API (to conform with the new standards)
-They were hard to use
-They were marked as deprecated so that it would not break existing applications using them. 
-They were however not included in the new SDK, so that it would encourage users to use the new, rewritten code
+This change was also deemed to be primarily enhancive with a subcategory of groomative.
+The reason being that this change was part of the broader re-implementation and while it did not purely add new functionality, it did change aid in changing the behaviour of this particular part of the API.
+
+The interviewee once again clarified how this change was indeed primarily concerned with meeting the new standards of version 2.0.
+They agreed that little had actually changed in terms of what functionality the API offered and gave the same reasoning suggested for the two prior changes.
+
+Once again our conclusion was incorrect for the categorisation of this change.
+Given the information from the interview, we deemed that this change was also primarily groomative with a subcategory of enhancive.
 
 \subsection{Removed}
-Intro...
 
+While the changes between versions 1.4 and 2.0 included many deprecations, only one of them was not re-implemented in a new part of the API. 
 \subsubsection{Burst Mode}
 
-%%Describe the change 
-Burst mode was deprecated
-In Version 2.0 the methods only return null
+The burst mode feature of the API allowed users to buffer a series of images for closer analysis. This feature was deprecated during the transition between 1.4 and 2.0 and was not re-implemented.
 
-%%Relate it to Categories
-The feature would have to be re-implemented because of changes to the camera (hardware)
-This would be costly and because of this it was investigated whether or not it would be safe to remove the feature.
-The investigation showed that the impact of the removal would not be significant enough and thus it was removed.
+This change presented itself as a clear example of a reductive category of maintenance as it was simply removed and not replaced anywhere else.
+We also concluded that this change had no suitable subcategory in which to classify the change.
+
+The interviewee did shed some light onto why this change occurred.
+We were informed that in order to continue using this feature in 2.0 and in newer versions of the camera hardware, it would have to be re-implemented from scratch.
+A cost analysis was performed on taking this action and it was deemed that the impact would be minimal resulting in it's removal from the API.
+
+Given this information we can safely say that we correctly concluded that this was a reductive maintenance task and that there are indeed no other subcategories which are applicable to describe this change.
 
@@
 
-Intro...
+While the main focus of our investigation of the source code and documentation was to identify changes between the versions, it was also to discover differences larger trends of the API.
+The trends were also analysed and given an appropriate maintenance category.
 
@@
 
-%%Relate it to Categories
-The partners used the examples a lot
-The old examples varied a lot in how they were implemented
-The old ones weren’t good enough
+As with many APIs, Axis included a selection of example programs to assist developers in creating applications by giving explicit examples of their usage.
+This trend continued in 2.0 but there were some significant improvements.
+The number of example programs increased, as did the amount of comments accompanying the code which lead to an overall more robust set of examples.
 
-From what she is saying, the intent was mainly:
-to have a unified standard
-which helps the partners to write ‘good’ code
-to cover the new functionality
-to cover specific features
-to show how the features can be used together
+We therefore concluded that this change was updative as the example code was updated to the new API and the new techniques which it utilises.
+We further decided that this change also had a subcategory of reformative.
+
+From the interview it became clear that the improvement of the example code was an important change between the two versions.
+The interviewee described to us how the examples were used frequently by their customers, however, the old examples varied significantly between how different and even similar tasks were implemented.
+This ultimately meant that the old examples were not good enough and new ones needed to be created, preferably conforming to a single standard of implementation techniques.
+The new examples made sure to cover the new functionality, specific new features and they to show how they can be combined to create applications.
+
+With this information we concluded that our categorisation was incorrect.
+It became clear that this change was in actual fact primarily reformative, given that the changes to the documentation we being performed to meet the needs of the API users.
+It was also clear that the subcategory should therefore be updative.
 
@@
 
-The documentation has mainly been changed to correspond with the changes to the API itself
-LaTeX support has been removed
+As the API changed versions, so too did the documentation.
+While there were no substantial changes, we did notice that the documentation is no longer offered as a PDF via latex but is instead only offered via HTML.
 
-%%Relate it to Categories
-One of the main “requests” was to increase functionality (such as ptz) - and the documentation had to be updated accordingly.
+We categorised this change as being updative with a reformative subcategory for the reasons that the change only updated the documentation to reflect the recent changes in the API.
+
+This sentiment was supported by the interview.
+The interviewee agreed with our assessment that the documentation was only changed to be up to date with the current workings of the API and how the new systems interact with each other.
+
+As there was no information to contradict our categorisations we have concluded we were correct in our assumptions.
 
@@
 %%Describe the change 
-They have gone from having direct access to the headers, to having a facade to access each module
+The API interfaces experienced the most change between the two versions.
+Three of the older interfaces were deprecated in favour of the new API architecture and the rest of the API is now comprised of brand new interfaces.
+The exception to this appears to be the image capture interface which only experienced a deprecation of a single feature.
+Each new feature is either accessed directly or via an interface which acts as a facade.
 
-The new interfaces are all based on callbacks. 
-One interface that was not touched was capture.h (Except for the deprecated burst method).
-She thinks that it probably should have been re-implemented to bring it in line and to be consistent they should bring it into line at some point.
-It wasn’t required as the implementation didn’t actually change.
+We therefore concluded that this change would be best described as being mainly groomative as the changes affected the overall design and not the implementation of the API.
+A subcategory of preventive was also chosen as this could be seen as a method for preventing future maintenance.
 
-%%Relate it to Categories
-Improvements related to coding standard. (cosmetic)
-These decisions were based on internal discussion.
-Wanted an event driven system
-Driven by internal struggles with using the API to create applications
+The interview provided further insight into the reasoning behind this change.
+Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all reasons for changing the interfaces of the API.
+Internal and external discussions about the use of the API also lead to the change in architecture of the API.
+For example, the interviewee mentioned how internal struggles with using the API highlighted the issue that the APIs were not simple to use and that they needed to be revised.
 
-The need for change was identified through discussions with API users which asked why “it isn’t possible to do it this way instead etc”
-
-Re-written because of the other changes to the API (to conform with the new standards)
-They were hard to use
-They were marked as deprecated so that it would not break existing applications using them. 
-They were however not included in the new SDK, so that it would encourage users to use the new, rewritten code
+Taking this information into account, we concluded that our categorisation was incorrect.
+The primary change seemed to be preventive given the strong emphasis on ease of use and could be seen as a way of avoiding future maintenance.
+We further concluded that the subcategory should be groomative to still reflect the intent to make the API more maintainable overall.
 
@@
 %%Describe the change 
-They now store errors in enums in separate header files
-This suggests that changed their error handling to use exceptions
+One interesting addition to version 2.0 of the API was many specific error header files, containing enums of error codes.
+While we were not aware of what error handling was utilised prior to this version, we assumed it had changed given the inclusion of these new files.
+For example, one might assume that they have perhaps switched to using C++ exceptions.
 
-%%Relate it to Categories
-The error handling was changed to correspond with how glib handles errors. 
-The error handling should be more informative + increase usability
-The change would have happened even if glib wasn’t added (but with glib made it “more obvious”)
+We therefore decided to categorise this change primarily as preventive.
+This was on the basis that error handling is preventive in nature.
+Groomative was decided as an appropriate subcategory of change as the changing, or introduction of error handling could be seen as a means to make code more maintainable.
+
+Following the discussions in the interview, it became clear that the error handling was indeed changed but not for the reasons we assumed.
+A reason given was that the previous error handling implementations lacked information and usability.
+Glib, a common C library was also introduced to the new API.
+The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API.
+However, it was expressed to us that the error handling would have changed between versions regardless of whether or not Glib was included.
+
+We therefore concluded that our categorisation for this change was correct.
+Indeed, the primary reason for the change was to improve the existing error handling while improving the overall maintainability of the API as a whole.
 
@@
 
+The advent of the new API saw the inclusion of new 3\textsuperscript{rd} party libraries.
+For example, axsound utilises a library called Alsa, all interfaces use Glib and daemons have been provided for using D-Bus.
+These changes potentially make the library much more flexible both for the API designers in terms of features they can provide and for the application developers in terms of applications they can develop.
+
+We therefore gave this change the main categorisation of adaptive with no suitable subcategories being found.
+
+(!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
+
+The architects creating the API decided they wished to use Glib which came about primarily from internal discussions at the company.
 %%Relate it to Categories

### 2015-04-30 thesis/acm/paper.tex
Added note to conclusion
Added note to 3rd party section

@@
 \subsubsection{3\textsuperscript{rd} Party}
+ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
 
@@
 We therefore gave this change the main categorisation of adaptive with no suitable subcategories being found.
-
-(!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
 
@@
 
-\section{Conclusion RQ2} \label{conclusion}
+\section{Conclusion} \label{conclusion}
+ATTN: This section has not been started.
 

### 2015-04-30 thesis/acm/paper.tex
Removed a note
Removed a note that was mistakenly left in place
law 7

@@
 %%Describe the change 
-Adds functionality which allows to connect with other hardware through serial communication
-Allows the possibility to integrate other systems with the camera (such as a ticket dispenser (i guess))
-
 The final new feature of the API was the inclusion of axserialport.
@@
 
-\subsubsection{3\textsuperscript{rd} Party}
+\subsubsection{3\textsuperscript{rd} Party}y e
 ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
@@
 
-\subsection{Increasing Complexity}
+\subsection{Increasing Complexity} \label{law2}
 A large part of the changes made to the API were made to improve the structure and the way that the API is used.
@@
 
-\subsection{Declining Quality — the quality will appear to decline unless it is rigorously maintained and adapted}
-Updates to documentation
-Updates to interfaces and error handling
-
-It's not 100\% true for APIs, because updating it too often will cause other problems --> ``rigorously''
+\subsection{Declining Quality}
+The interviews established that a groomative motive was not the most major reason for implementing any change.
+The changes to the example code and the SDK, as well as the re-structured modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content.
+These changes did, however, increase the quality and was a substantial part of the changes, which could have been left out.
+A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{law2}.
+We therefore settle that the law of declining quality can be applied to APIs.
 
 \subsection{Feedback System — multi-level, multi-loop, multi-agent feedback systems}
+One of the 
 She would like to get more feedback from the API users and the end-users - to better include this in the feedback loop and in turn use it to form change decisions

### 2015-04-30 thesis/acm/paper.tex
law 8

@@
 \alignauthor
-John Burchell\titlenote{I am da main author}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
+John Burchell\titlenote{Main author}\\
+       \affaddr{Computer Science and Engineering}\\
+       \affaddr{University of Gothenburg}\\
+       \affaddr{Gothenburg, Sweden}\\
+       \email{john.a.burchell@gmail.com}
 % 2nd. author
 \alignauthor
-William Granli\titlenote{I am da main author}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
+William Granli\titlenote{Main author}\\
+       \affaddr{Computer Science and Engineering}\\
+       \affaddr{University of Gothenburg}\\
+       \affaddr{Gothenburg, Sweden}\\
+       \email{william.granli@gmail.com}
 % 3rd. author
-\alignauthor Imed Hammouda\titlenote{I am da co-author}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
+\alignauthor Imed Hammouda\titlenote{Co-author}\\
+       \affaddr{Computer Science and Engineering}\\
+       \affaddr{University of Gothenburg}\\
+       \affaddr{Gothenburg, Sweden}\\
+       \email{imed.hammouda@gu.se}
 }
@@
 \item[\textbf{RQ1:}] How do companies actively drive API evolution?
-\item[\textbf{RQ2:}] How do APIs evolve?
-\item[\textbf{RQ3:}] To what extent can we reverse engineer API change decisions?
+\item[\textbf{RQ1.1:}] To what extent can we reverse engineer API change decisions?
+\item[\textbf{RQ2:}] How do APIs ``passively'' evolve?
 
@@
 
- \newpage
 \section{RQ1} \label{results}
@@
 
-\newpage
 \section{RQ2 Lehman}
@@
 
-\subsection{Feedback System — multi-level, multi-loop, multi-agent feedback systems}
-One of the 
-She would like to get more feedback from the API users and the end-users - to better include this in the feedback loop and in turn use it to form change decisions
-
-No “scientific” theories have been used when creating the APIs - most decisions have been based on experience (expertise) and previous experience
-
-There hasn’t been anything created by the users which has then been implemented into the API.
-However, there are partners who have created features which were then later included.
-i.e.
-Audio (This is not to say that they used the API that the partners had developed!)
-
-She is unaware of any metrics that they have.
-She would have to ask the ADP engineers for anything like this.
-She doesn’t personally know if there have been any issues or problems with the current API.
-She would like to have more feedback and input when things are working correctly, normally they only have feedback when things don’t work.
-Other than the feedback she mentioned previously, i.e.
-partners requesting features.
-
-They had some kind of validation testing whereby they had someone internally attempt to create an application using all parts of the API.
-It was during the development process and was successful but it also provided them with some key feedback.
-She suggested that this kind of testing should be increased and that they do need more of it.
-(This was only one application, as it differs a lot)
-
-Communication with users currently only really gives them bug reports, FAQs (Educational Issues) or queries about how to do something could indicate that there are missing features in the API.
-This is something that the product management deal with, rather than her.
-She focuses more on the how rather than the what.
-What it comes to decide what interface to do, PM decide and she then comes along and decides how it would look / be done.
+\subsection{Feedback System}
+One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
+Currently, the only the API users are included in this feedback loop, and the API architect expressed the desire to also include the end-users in this loop.
+The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users, and which leads to good applications being developed.
+One example of how the API users have been included in the feedback loop, was prior to version 2.0 being released, when API users implemented functionality related to sound, even though there was no interface for this in the API.
+The experiences of this API user, were later considered when developing the axsound module.
+One benefit of having a more structured feedback loop, would be that the API developers would be more and faster aware of potential errors in the implementation of the API.
+Another ambition which was mentioned, was to bring scientific theories and best practices from academia into consideration when developing the API.
+This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects.
+Because of these factors and clearly expressed ambitions, we conclude that the law of feedback system is true for APIs.
 

### 2015-04-30 thesis/acm/paper.tex
Changed author blocks + categories/keywords

@@
 
-\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+\conferenceinfo{14th International Workshop on Principles of Software Evolution}{2015 Bergamo, Italy}
 
-\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective
-\titlenote{(Produces the permission block, and
-copyright information). For use with
-SIG-ALTERNATE.CLS. Supported by ACM.}}
+\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
 \subtitle{[Extended Abstract]
-\titlenote{A full version of this paper is available as \textit{Author's Guide to Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.acm.org/eaddress.htm}}}
+}
 
@@
 
-\terms{Theory}
+\terms{Theory, Design or Verification maybe?}
 
-\keywords{ACM proceedings, \LaTeX, text tagging}
+\keywords{API Design, Software Evolution, Software Maintenance}
 

### 2015-04-30 thesis/acm/paper.tex
first page latex stuff
Added category, first page

@@
 
-\conferenceinfo{14th International Workshop on Principles of Software Evolution}{2015 Bergamo, Italy}
+\conferenceinfo{14th IWPSE} {'15 Bergamo, Italy}
+\CopyrightYear{2015}
+
+\crdata{1-23456-78-9/01/23}
 
 \title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
-\subtitle{[Extended Abstract]
-}
 
@@
 
-% A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+\category{K.6.3}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and reengineering]
 
-\terms{Theory, Design or Verification maybe?}
+\terms{Theory, Design or Verification/Documentation maybe?}
 

### 2015-04-30 thesis/acm/paper.tex
added note to acknowl

@@
 
+\section{Discussion}
+
 \section{Conclusion} \label{conclusion}
 ATTN: This section has not been started.
+
+Look up the papers from the conference (especially regarding the discussion/conclusion)
+discussion = revisiting research questions (and maybe structuring around industry/academia)
+conclusion = summary part, main final points and future work
+
+Stuff for the conclusion:
+Have a more structured feedback loop (include users) this can be future work too
+Include more scientific theories
 
@@
 \section{Acknowledgments}
+We would like to thank Axis and that project at GU.
 

### 2015-04-30 thesis/acm/paper.tex
Added 1 more category, first page

@@
 
-\category{K.6.3}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and reengineering]
+\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and reengineering]
+\category{K.6.3}{Computing Milieux}{Software Management}[Software Maintenance]
 

### 2015-05-01 thesis/acm/paper.tex
Added some comments to the conclusion

@@
 
-\subsubsection{3\textsuperscript{rd} Party}y e
+\subsubsection{3\textsuperscript{rd} Party}
 ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
@@
 %%John add conclusion ideas here
+We were correct with the majority of our categorisations.
+The ones we did get wrong were because we did not think of it from specific points of view.
+This probably means that it's possible to reverse engineer to some extent, but not completely (Which is probably the answer most people would expect).
+
+Interesting that the majority of the changes seem to be driven either by management (Suggested that it comes from partners) or the partners directly.
+There was also internal pressure to improve the API which came about from Axis developers trying to create their own applications.
+
+Potential ordering:
+
+RQ1
+RQ1.1
+RQ2
+What this means for industry:
+	Greater emphasis should be placed upon communicating with the end users / application developers
+What this means for academia
 

### 2015-05-01 thesis/acm/paper.tex
Removed more comments
Current Draft stuff
More discussiony things!

@@
 Each change was given a main category of maintenance and a subcategory if appropriate.
+This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.
+
+%%Does this paragraph below belong here or somewhere else? Feels a bit odd!
+The API itself consisted of two major versions; 1.4 and 2.0.
+There were no intermediate versions between 1.4 and 2.0.
+Version 1.4 was actually the same version as 1.0, just with added build options for other hardware platforms.
+The changes therefore come from the changes between the two major versions.
+Given that there was an apparent "big bang" implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.
 
@@
 %%Describe the change 
-
-Increased commenting and explanations
-Improved examples that cover more functionality
-
 As with many APIs, Axis included a selection of example programs to assist developers in creating applications by giving explicit examples of their usage.
@@
 %%Describe the change 
-
 As the API changed versions, so too did the documentation.
@@
 4 of the 13 changes were additions of new modules, and in the re-implemented modules a lot of functional content was added, too.
-It was also mentioned that the API users had previously reqeusted more frequent updates to the API, despite the drawbacks this could have.
+It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could have.
 One of the main reasons for continuously adapting the API is also to force (!!!wording) the API users to use the API in the way that it is intended.
@@
 One example of where this is evident in the evolution of the API, is in the module that handles the video capturing and video stream.
-It was decided that this module would not be re-written to conform with the new interface standard, as there was not much functional content that would change in this module, anyways (!!!reword).
+It was decided that this module would not be re-written to conform with the new interface standard, as there was not much functional content that would change in this module, anyway (!!!reword).
 Thus, the law of increasing complexity holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.
@@
 The future updates to the API will also be made incrementally, and there will not be a big bang update similar to the one of 2.0.
-This supports that the law of self regulation applies to APIs, assuming that the current stage of the life-cycle of the API can be considered as the center of the normal distribution curve of the APIs growth.
+This supports that the law of self regulation applies to APIs, assuming that the current stage of the life-cycle of the API can be considered as the centre of the normal distribution curve of the APIs growth.
 
@@
 The SDK that is included with the API was rigorously updated with the introduction of version 2.0.
-All functionality which was added or modified in version 2.0 was updated accordlingly in the SDK.
+All functionality which was added or modified in version 2.0 was updated accordingly in the SDK.
 The same pattern can be seen for the example code, which went through major changes as a result of the changes to the API code.
@@
 This also ties in with the ambition of controlling the way the API users use the API, as mentioned previously.
-It was also mentioned that the case company had recieved feedback from the API users that more frequent updates to the functional content was desirable, even though this may require them to update their application code.
+It was also mentioned that the case company had received feedback from the API users that more frequent updates to the functional content was desirable, even though this may require them to update their application code.
 Because of this, we conclude that the law of continuing growth applies to APIs.
@@
 
+Potential ordering:
+
+RQ1 - How do companies actively drive API evolution?
+%%Intro to this particular quesiton
+
+Overwhelmingly, the primary driving factor behind API evolution appears to have been the desire for new API functionality.
+We found strong evidence to suggest that most, if not all of the additions, re-implementations and functional changes were undertaken to include functionality that the partners desired.
+Specifically we found that 53.8\% of the changes were enhancive changes, 7.7\% were adaptive and the remaining 38.5\% were changes specifically aimed at improving the maintainability of the API.
+
+These data seem to align with the comments made during the interview.
+For example, the interviewee expressed a desire to have features be added to the API more rapidly and more quickly than they have previously.
+This sentiment was also expressed to the interviewee by certain partners who suggested that the API was too stable and citing their wish for more features and more frequent updates to the API.
+
+This leads to the conclusion that the inclusion of new features and the maintainability of an API are two very strong drivers of API evolution.
+
+%%% Notes and thoughts
+Consistent with Lehmans Laws - Continuing growth, feedback systems seem to be very important.
+Desire from some partners to have more have even more additional features etc
+
+Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!
+
+See if our numbers match up with previous studies who said roughly 70\% of changes to an API were refactorings. That number is a little high in our case, but it's close!
+
+RQ1.1
+RQ2
+What this means for industry:
+	Greater emphasis should be placed upon communicating with the end users / application developers.
+APIs should be made with maintainability and extendibility in mind as they seem to be what changes the most between versions.
+
+	Obvious benefit for Axis is that the more features == higher value for their camera.
+If they have many applications being developed by parters (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase.
+This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
+
+What this means for academia
+
 \section{Conclusion} \label{conclusion}
 ATTN: This section has not been started.
+
+Summarise the findings of the discussion
+Summarise what the next steps could be.
 
@@
 There was also internal pressure to improve the API which came about from Axis developers trying to create their own applications.
-
-Potential ordering:
-
-RQ1
-RQ1.1
-RQ2
-What this means for industry:
-	Greater emphasis should be placed upon communicating with the end users / application developers
-What this means for academia
 

### 2015-05-02 thesis/acm/paper.tex
Moar changes

@@
 Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection.
-The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API.
+The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API and how their decisions, needs and requirements have affected the development of the API.
 
@@
 
+%Another threat was we were reliant upon being given documentation and code. I.e. they might not give us everything, leave stuff out, ignore things etc.
+
 \section{RQ1} \label{results}
 
-Each change between versions has been identified and grouped into three particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
+Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
 Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories.
@@
 
-See if our numbers match up with previous studies who said roughly 70\% of changes to an API were refactorings. That number is a little high in our case, but it's close!
+%See if our numbers match up with previous studies who said roughly 70\% of changes to an API were refactorings. That number is a little high in our case, but it's close!
 
-RQ1.1
+RQ1.1 - To what extent can we reverse engineer API change decisions?
+Roughly 78\% of our categorisation matched the actual categorisation of the changes.
+While it is true that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.
+
+For future studies, this technique could be improved by performing more actions along side the code review.
+For example, having access to commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be performed.
+
 RQ2
@@
 
-	Obvious benefit for Axis is that the more features == higher value for their camera.
-If they have many applications being developed by parters (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase.
+	Obvious benefit for Axis is that the more features == more applications == higher value for their camera.
+If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase.
 This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
 
-What this means for academia
+What this means for academia:
 

### 2015-05-02 thesis/acm/paper.tex
Added information to data collection

@@
 A description of our methodology is introduced in Section \ref{methodology}.
-In Section \ref{results}, the results of our study are presented, and in Section \ref{conclusion}, we discuss the findings of our study.
+In Section \ref{results}, the results of our study are presented and in Section \ref{conclusion}, we discuss the findings of our study.
 
@@
 The data were collected primarily through inspections of the source code and the archival analysis of accompanying  documentation.
-The source code was comprised of two versions of the same API which the company had developed.
-An older version which is currently released and a newer version which is soon to be deployed.
+The source code was comprised of two versions of an API which the company had developed.
+An older version (1.4) which is currently released and a newer version which has recently been deployed (2.0).
 Each version of the API had its own respective documentation.
@@
 Maybe put it in a table?) The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
+<-- do we still want to mention exactly what kinds of data we looked for?
+i.e.
+return types, enums, typedefs etc etc.
+
+The APIs were inspected to determine where the changes had occurred.
+We used the Git Diff tool to find differences between two versions of files that existed in both versions of the API.
+Once we had identified the changes, we inspected the documentation and the code itself to determine if there was a reason for the change, for example, if a given function had been labelled deprecated between versions.
+These changes were then categorised by new changes, updates or re-implementations, removals and general trends.
 The collected data were input into tables and spreadsheets, according to the API version.
-From the documentation we collected data regarding the motive behind the functionality in API calls.
-Data gathered from the documentation was also stored in tables and spreadsheets and was organised together with its corresponding method.
 
@@
 Both phases were performed iteratively, together with the data collection.
-The reason for this created the opportunity to improve the process of analysis as the study progressed, as well as to be able to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
+This created the opportunity to improve the process of analysis as the study progressed, as well as allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
 The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.

### 2015-05-02 thesis/acm/paper.tex
Other changes

@@
 
-\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and reengineering]
+\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering and reengineering]
 \category{K.6.3}{Computing Milieux}{Software Management}[Software Maintenance]
@@
 \section{Introduction} \label{introduction}
-%API Design (and a little bit of ecosystems, and a bit of problem statement)
+%API Design (and a little bit of ecosystems and a bit of problem statement)
 As the software industry and the open-source movement steadily grow, the number of public APIs is increasing.
@@
 To the best of our knowledge, no studies that explore the motives behind or the effects of API evolution have previously been performed on embedded platform APIs.
+Reverse engineering design decisions is a challenging yet interesting problem.
+The better we can understand why changes occur and what problems they are trying to solve, the better we can design around these problems to avoid them cropping up in the future.
 
@@
 \section{Existing Literature} \label{existing_literature}
-This section will introduce the topics of API design and software evolution, and provide a review of studies that are directly related to our study.
+This section will introduce the topics of API design and software evolution and provide a brief review of studies that are directly related to our study.
 
@@
 %%Categories of maintenance and types of maintenance
-Software evolution is a field which studies the application of software maintenance activities and processes on software, and the resulting, evolved versions of the software.
+Software evolution is a field which studies the application of software maintenance activities and processes on software and the resulting, evolved versions of the software.
 The concept of software maintenance has existed since the 1960s.
@@
 The company is the global market leader in the markets of network cameras and video encoders.
-The company develops embedded software for the security cameras, and some of their products are designed to be accessible through APIs that are also developed by the company.
+The company develops embedded software for the security cameras and some of their products are designed to be accessible through APIs that are also developed by the company.
 
@@
 
-The case was selected using convenience sampling \cite{flyvbjerg2006five}, and a maximum variation strategy was used \cite{benbasat1987case}.
+The case was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}.
 As such, the goal was to include as many companies as possible in this study.
@@
 The goal of the study was twofold.
-Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs, and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's explanation of their motives.
+Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's explanation of their motives.
 Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.
@@
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to answer \textbf{RQ2}.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research; especially to be able to answer \textbf{RQ2}.
 
@@
 The codes were then analysed from a high-level point of view, the main goal of which was to identify trends in the codes.
-The final step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.
+The final step involved analysis of these trends and it was during this stage the hypotheses were generated and formulated.
 The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.
@@
 This is supported by the characteristic of the changes identified in this study.
-4 of the 13 changes were additions of new modules, and in the re-implemented modules a lot of functional content was added, too.
+4 of the 13 changes were additions of new modules and in the re-implemented modules a lot of functional content was added, too.
 It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could have.
@@
 When comparing the changes introduced in 2.0 to the ones previously introduced, it is clear that the growth of the API has increased gradually.
-During the interview it was also mentioned that the future plans for the API did not include any major changes, and that only a few minor changes were planned in the near future.
-The future updates to the API will also be made incrementally, and there will not be a big bang update similar to the one of 2.0.
+During the interview it was also mentioned that the future plans for the API did not include any major changes and that only a few minor changes were planned in the near future.
+The future updates to the API will also be made incrementally and there will not be a big bang update similar to the one of 2.0.
 This supports that the law of self regulation applies to APIs, assuming that the current stage of the life-cycle of the API can be considered as the centre of the normal distribution curve of the APIs growth.
@@
 Consequently, the only significant update to the API was made in the transition to version 2.0.
-The internal development of the API has also been made sporadically, and there have been periods where the API has not been actively developed.
+The internal development of the API has also been made sporadically and there have been periods where the API has not been actively developed.
 This suggests that the law of conservation of organisational stability does not apply to APIs.
@@
 Large parts of the changes between the versions were strictly additions of new functional content.
-4 new modules were added, and significant additions of new functionality were added to the modules which were re-structured from version 1.4.
+4 new modules were added and significant additions of new functionality were added to the modules which were re-structured from version 1.4.
 The interviewee also made it clear that increasing the functionality was one of the major goals with the 2.0 update.
@@
 One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
-Currently, the only the API users are included in this feedback loop, and the API architect expressed the desire to also include the end-users in this loop.
-The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users, and which leads to good applications being developed.
+Currently, the only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users in this loop.
+The reasoning for this was to increase the quality and to be able to deliver content which is useful for the users and which leads to good applications being developed.
 One example of how the API users have been included in the feedback loop, was prior to version 2.0 being released, when API users implemented functionality related to sound, even though there was no interface for this in the API.
@@
 RQ1.1 - To what extent can we reverse engineer API change decisions?
-Roughly 78\% of our categorisation matched the actual categorisation of the changes.
-While it is true that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.
+
+After cross examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.
+While it is obvious that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.
 
 For future studies, this technique could be improved by performing more actions along side the code review.
-For example, having access to commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be performed.
+For example, having access to and analysing commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be collected and analysed.
 
@@
 APIs should be made with maintainability and extendibility in mind as they seem to be what changes the most between versions.
+They should probably improve their feedback system to get more feedback from the API users.
 
@@
 What this means for academia:
+	Academia could benefit from the results as a means for further research - We have found that it's possible to reverse engineer these design decisions from a simple study, so perhaps more advanced studies should be conduct at a larger scale?
+-- Why though?
 

### 2015-05-02 thesis/acm/paper.tex
notes in discussion + commas revert

@@
 \begin{abstract}
-\blindtext
+
+Previous research and/or rationale for performing the study.
+Background: Exploration of the motives and drivers behind changes to APIs has
+
+Aims: Hypotheses/propositions to be tested, or goal of the study.
+
+Method: Description of the type of study, treatments, number and nature of experimental units (people, teams, algorithms, programs, tasks etc.), experimental design, outcome being measured.
+
+Results: Treatment outcome values, level of significance.
+
+Conclusions: Limitations of the study, implications of the results, and further work.
+
 \end{abstract}
 
-\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering and reengineering]
+\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and reengineering]
 \category{K.6.3}{Computing Milieux}{Software Management}[Software Maintenance]
@@
 One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
-Currently, the only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users in this loop.
-The reasoning for this was to increase the quality and to be able to deliver content which is useful for the users and which leads to good applications being developed.
+Currently, only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users in this loop.
+The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users and which leads to good applications being developed.
 One example of how the API users have been included in the feedback loop, was prior to version 2.0 being released, when API users implemented functionality related to sound, even though there was no interface for this in the API.
@@
 
+\subsection{RQ1}
 Potential ordering:
@@
 
+\subsection{RQ1.1}
+
 RQ1.1 - To what extent can we reverse engineer API change decisions?
@@
 
-RQ2
+This should probably be in conclusion, right? /Willy
        What this means for industry:
@@
 -- Why though?
+
+\subsection{RQ2}
+The general conclusion: 
+5 laws clearly apply
+2 laws probably apply (not significant)
+1 law clearly doesn't apply
+
+Have a table which relates each theory to each change (after we have re-analysed the one on docs. )
 
@@
 It's interesting that the partners have mentioned that they want more frequent updates... maybe API developers should be less afraid of updating them? 
+That the part about controlling how the API users use the API was such an important thing is interesting. (Not something we expected).
 

### 2015-05-02 thesis/acm/paper.tex
Abstract v0.7

@@
 \usepackage{blindtext}
+\usepackage[english]{babel}
 
@@
 \alignauthor
-John Burchell\titlenote{Main author}\\
+John Burchell\\
        \affaddr{Computer Science and Engineering}\\
@@
 \alignauthor
-William Granli\titlenote{Main author}\\
+William Granli\\
        \affaddr{Computer Science and Engineering}\\
@@
 \maketitle
+
 \begin{abstract}
 
-Previous research and/or rationale for performing the study.
-Background: Exploration of the motives and drivers behind changes to APIs has
+\textbf{Background } 
+Studies of the motives and drivers behind modifications to APIs have been done before, but platform APIs are, so far, unexplored.
+Previous work has also not studied APIs from the perspective of widely recognised software evolution theories, such as the Categories of Software Maintenance and Lehman's laws of software evolution.
 
-Aims: Hypotheses/propositions to be tested, or goal of the study.
+\smallskip \noindent
+\textbf{Objective } This study explored how companies actively drive changes to APIs and how APIs evolve from a passive point of view.
+The aim was also to test how well we could reverse engineer these change decisions.
+The goal was to study these factors by relating them to existing software evolution theories.
 
-Method: Description of the type of study, treatments, number and nature of experimental units (people, teams, algorithms, programs, tasks etc.), experimental design, outcome being measured.
+\smallskip \noindent
+\textbf{Method }
+This case study was conducted by investigating the changes between two versions in a platform API and its documentation, and by interview the architects of the API.
+The changes were analysed from a qualitative and investigative point of view.
 
-Results: Treatment outcome values, level of significance.
+\smallskip \noindent
+\textbf{Results  }
+This study identified 13 majors changes to the API.
+The study concluded that the most major driving force for the evolution of APIs is the drive for new functionality and that change decisions to a large extent can be reverse engineered.
+It was also found that 7 out of 8 of Lehman's laws were applicable to APIs.
 
-Conclusions: Limitations of the study, implications of the results, and further work.
+\smallskip \noindent
+\textbf{Conclusion  }
+This study has provided valuable insight into the evolution of platform APIs.
+The qualitative analysis can help other companies to improve their API maintenance process.
+The successful attempt to reverse engineer the change decisions should encourage similar studies to be conducted.
+The investigation of Lehman's laws show that APIs cannot be generalised and be compared to any type of system.
 

### 2015-05-02 thesis/acm/paper.tex
notes

@@
 Studies of the motives and drivers behind modifications to APIs have been done before, but platform APIs are, so far, unexplored.
-Previous work has also not studied APIs from the perspective of widely recognised software evolution theories, such as the Categories of Software Maintenance and Lehman's laws of software evolution.
+Previous work has also not studied APIs from the perspective of widely recognised software evolution theories, such as the Types of Software Evolution and Software Maintenance and Lehman's laws of software evolution.
 
@@
 
+%This should probably go in Methodology... parts of it at least /W
 Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
@@
 
-%%Does this paragraph below belong here or somewhere else? Feels a bit odd!
+%%Does this paragraph below belong here or somewhere else? Feels a bit odd!    W: Case Company Description I think
 The API itself consisted of two major versions; 1.4 and 2.0.
@@
 For example, having access to and analysing commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be collected and analysed.
+%%Conclusion stuff /Willy
 
-This should probably be in conclusion, right? /Willy
+%%The following should probably be in conclusion, right? /Willy
        What this means for industry:

### 2015-05-02 thesis/acm/paper.tex
Stuff

@@
 
-\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and reengineering]
+\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and re-engineering]
 \category{K.6.3}{Computing Milieux}{Software Management}[Software Maintenance]
@@
 \begin{description}
-\item[\textbf{RQ1:}] How do companies actively drive API evolution?
-\item[\textbf{RQ1.1:}] To what extent can we reverse engineer API change decisions?
-\item[\textbf{RQ2:}] How do APIs ``passively'' evolve?
+\item[\textbf{RQ1}] How do companies actively drive API evolution?
+\item[\textbf{RQ1.1}] To what extent can we reverse engineer API change decisions?
+\item[\textbf{RQ2}] How do APIs ``passively'' evolve?
 
@@
 %Info from the interview, add to this section
-Has been released, in the form we looked at (supports that we’re doing a ‘real’ case study)
-They have “partners” which develop applications using their API. These applications are then used by the end-users of the camera.
+Has been released, in the form we looked at (supports that we’re doing a ``real'' case study)
+They have partners which develop applications using their API. These applications are then used by the end-users of the camera.
 
@@
 %Intro and summary
-This study has been conducted using the case study methodology \cite{runeson2009guidelines}.
+This study has been conducted using the case study meth-odology \cite{runeson2009guidelines}.
 The goal of the study was twofold.
@@
 
-\section{RQ1} \label{results}
+\section{Results RQ1} \label{results}
 
@@
 The changes therefore come from the changes between the two major versions.
-Given that there was an apparent "big bang" implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.
+Given that there was an apparent ``big bang'' implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.
 
@@
 %%Relate it to Categories
-The information gathered from the interview suggests (!!!Better word than this?) that were correct in our choice of enhancive for this change.
-Once more there was no inclusion of an appropriate subcategory.
+The information gathered from the interview supported that were correct in our choice of enhancive for this change. Once more there was no inclusion of an appropriate subcategory.
 
@@
 
-In regards to re-implementations, during the interview it was mentioned that one intent behind the re-implementations was to bring them in-line with the newly created functionality which take advantage of Glib, a new kind of error handling and extensive use of callbacks.
+During the interview it was mentioned that one intent behind the re-implementations was to bring them in line with the newly created functionality which takes advantage of Glib, a new kind of error handling and extensive use of callbacks.
 
@@
 \section{RQ2 Lehman}
-This section will present results related to \textbf{RQ2}. The information introduced was collected during the interview with the case company.
+This section will present results related to \textbf{RQ2}. The results are structured around how much our results indicate that each of Lehman's laws apply to platform APIs.
 
@@
 \section{Discussion}
+In this section we will discuss the results of our study.
 
@@
 \subsection{RQ2}
+The 
 The general conclusion: 

### 2015-05-02 thesis/acm/paper.tex
Added lehman table

@@
 An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}.
-The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
+The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
 The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.
@@
 \section{RQ2 Lehman}
-This section will present results related to \textbf{RQ2}. The results are structured around how much our results indicate that each of Lehman's laws apply to platform APIs.
+The results related to \textbf{RQ2} are structured around each of Lehman's laws and to what extent our findings show that the laws apply to platform APIs.
+The summary of our findings can be seen in Table \ref{table:lehman}.
+
+\begin{table}
+       \centering
+       \begin{tabular}[Ht]{|l|c|}
+       \hline
+       \textbf{Law} & \textbf{Applicability} \\
+       \hline
+       Continuing Change & True \\
+       \hline
+       Increasing Complexity & Kinda \\
+       \hline
+       Self Regulation & True \\
+       \hline
+       Conservation of Organisational Stability & False \\
+       \hline
+       Conservation of Familiarity & True \\
+       \hline
+       Continuing Growth & True \\
+       \hline
+       Declining Quality & Kinda \\
+       \hline
+       Feedback System & True \\
+       \hline
+       \end{tabular}
+       \caption{The applicability of Lehman's laws}
+       \label{table:lehman}
+\end{table}
 
@@
 
-\subsection{Increasing Complexity} \label{law2}
+\subsection{Increasing Complexity} \label{sec:law2}
 A large part of the changes made to the API were made to improve the structure and the way that the API is used.
@@
 
-\subsection{Self Regulation} \label{law3}
+\subsection{Self Regulation} \label{sec:law3}
 When version 1.4 was introduced, no new functionality or re-structuring was introduced.
@@
 The changes to the ACAP API has been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
-As mentioned in Section \ref{law3} the changes introduced in version 1.4 did not involve any changes to the existing API functions.
+As mentioned in Section \ref{law3}, the changes introduced in version 1.4 did not involve any changes to the existing API functions.
 Consequently, the only significant update to the API was made in the transition to version 2.0.
@@
 A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{law2}.
-We therefore settle that the law of declining quality can be applied to APIs.
+We therefore settle that the law of declining quality can be applied to APIs, but that there is data that implies that reducing quality is not of high importance.
 
@@
 \subsection{RQ1}
-Potential ordering:
-
-RQ1 - How do companies actively drive API evolution?
-%%Intro to this particular quesiton
 
@@
 
-This leads to the conclusion that the inclusion of new features and the maintainability of an API are two very strong drivers of API evolution.
+This leads to the conclusion (!!probably avoid that word in discussion) that the inclusion of new features and the maintainability of an API are two very strong drivers of API evolution.
 
@@
 Desire from some partners to have more have even more additional features etc
-
 Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!
-
-%See if our numbers match up with previous studies who said roughly 70\% of changes to an API were refactorings. That number is a little high in our case, but it's close!
 
@@
 While it is obvious that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.
-
-For future studies, this technique could be improved by performing more actions along side the code review.
-For example, having access to and analysing commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be collected and analysed.
-%%Conclusion stuff /Willy
-
-%%The following should probably be in conclusion, right? /Willy
-       What this means for industry:
-       	Greater emphasis should be placed upon communicating with the end users / application developers.
-APIs should be made with maintainability and extendibility in mind as they seem to be what changes the most between versions.
-They should probably improve their feedback system to get more feedback from the API users.
-
-       	Obvious benefit for Axis is that the more features == more applications == higher value for their camera.
-If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase.
-This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
-
-       What this means for academia:
-       	Academia could benefit from the results as a means for further research - We have found that it's possible to reverse engineer these design decisions from a simple study, so perhaps more advanced studies should be conduct at a larger scale?
--- Why though?
 
@@
 
+For future studies, this technique could be improved by performing more actions along side the code review.
+For example, having access to and analysing commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be collected and analysed.
+%%Conclusion stuff /Willy
+
+%%The following should probably be in conclusion, right? /Willy
+       What this means for industry:
+              Greater emphasis should be placed upon communicating with the end users / application developers.
+APIs should be made with maintainability and extendibility in mind as they seem to be what changes the most between versions.
+They should probably improve their feedback system to get more feedback from the API users.
+
+              Obvious benefit for Axis is that the more features == more applications == higher value for their camera.
+If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase.
+This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
+
+       What this means for academia:
+              Academia could benefit from the results as a means for further research - We have found that it's possible to reverse engineer these design decisions from a simple study, so perhaps more advanced studies should be conduct at a larger scale?
+-- Why though?
+
 %%John add conclusion ideas here
@@
 
+%See if our numbers match up with previous studies who said roughly 70\% of changes to an API were refactorings.
+That number is a little high in our case, but it's close!
+<---- This could be done in conclusion when we discuss how it contribues to academia (i.e.
+say it enforces previous studies blabla)
+
 %%William add conclusion ideas here

### 2015-05-02 thesis/acm/paper.tex
Re-structured results and moved around stuff in discussion

@@
 
-\section{Results RQ1} \label{results}
+\section{Results} \label{results}
+Introduction.
 
+\subsection{RQ1 Results}
 %This should probably go in Methodology... parts of it at least /W
@@
 
-\subsection{New}
-
-%%TODO Finish this off
-New additions to the API were the most frequent change that we observed.
+%%TODO Finish this off XXX
+%New additions to the API were the most frequent change that we observed.
 Each addition added new functionality to the API, ranging from controlling the camera, enabling audio analysis, allowing external storage connections and providing a serial port to interface with other devices.
@@
 
-\subsection{Modified}
-These changes were deemed to be modifications or re-implementations of existing functionality of the API.
-
+%XXX
+%These changes were deemed to be modifications or re-implementations of existing functionality of the API.
 During the interview it was mentioned that one intent behind the re-implementations was to bring them in line with the newly created functionality which takes advantage of Glib, a new kind of error handling and extensive use of callbacks.
@@
 
-\subsection{Removed}
+%XXX
+%While the changes between versions 1.4 and 2.0 included many deprecations, only one of them was not re-implemented in a new part of the API.
 
-While the changes between versions 1.4 and 2.0 included many deprecations, only one of them was not re-implemented in a new part of the API. 
 \subsubsection{Burst Mode}
@@
 
-\subsection{General Trends}
-
-While the main focus of our investigation of the source code and documentation was to identify changes between the versions, it was also to discover differences larger trends of the API.
+%XXX
+%While the main focus of our investigation of the source code and documentation was to identify changes between the versions, it was also to discover differences larger trends of the API.
 The trends were also analysed and given an appropriate maintenance category.
@@
 
-\section{RQ2 Lehman}
+\subsection{RQ2 Results}
 The results related to \textbf{RQ2} are structured around each of Lehman's laws and to what extent our findings show that the laws apply to platform APIs.
@@
 
-\subsection{Continuing Change}
+\subsubsection{Continuing Change}
 The case company described that including new functional content was one of the top priorities for the 2.0 release.
@@
 
-\subsection{Increasing Complexity} \label{sec:law2}
+\subsubsection{Increasing Complexity} \label{sec:law2}
 A large part of the changes made to the API were made to improve the structure and the way that the API is used.
@@
 
-\subsection{Self Regulation} \label{sec:law3}
+\subsubsection{Self Regulation} \label{sec:law3}
 When version 1.4 was introduced, no new functionality or re-structuring was introduced.
@@
 
-\subsection{Conservation of Organisational Stability}
+\subsubsection{Conservation of Organisational Stability}
 The changes to the ACAP API has been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
@@
 
-\subsection{Conservation of Familiarity}
+\subsubsection{Conservation of Familiarity}
 The SDK that is included with the API was rigorously updated with the introduction of version 2.0.
@@
 
-\subsection{Continuing Growth}
+\subsubsection{Continuing Growth}
 Large parts of the changes between the versions were strictly additions of new functional content.
@@
 
-\subsection{Declining Quality}
+\subsubsection{Declining Quality}
 The interviews established that a groomative motive was not the most major reason for implementing any change.
@@
 
-\subsection{Feedback System}
+\subsubsection{Feedback System}
 One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
@@
 
-\subsection{Law 1}
-
-Problem: Leads to potentially unsafe implementations to get around shortcomings of the API
-
 \section{Acknowledgments}

### 2015-05-04 thesis/acm/paper.tex
Notes in disc

@@
 
-\numberofauthors{3}
+\numberofauthors{4}
 
@@
        \email{william.granli@gmail.com}
+\and
 % 3rd. author
 \alignauthor Imed Hammouda\titlenote{Co-author}\\
+       \affaddr{Computer Science and Engineering}\\
+       \affaddr{University of Gothenburg}\\
+       \affaddr{Gothenburg, Sweden}\\
+       \email{imed.hammouda@gu.se}
+% 4th 
+\alignauthor Eric Knauss\titlenote{Co-author}\\
        \affaddr{Computer Science and Engineering}\\
@@
 
+%Summary of the results (overview)
+
 Overwhelmingly, the primary driving factor behind API evolution appears to have been the desire for new API functionality.
@@
 
+%The most interesting parts (and reflections + more information about these "trends")
 This leads to the conclusion (!!probably avoid that word in discussion) that the inclusion of new features and the maintainability of an API are two very strong drivers of API evolution.
 
+%
+
 %%% Notes and thoughts
-Consistent with Lehmans Laws - Continuing growth, feedback systems seem to be very important.
-Desire from some partners to have more have even more additional features etc
-Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!
+%Consistent with Lehmans Laws - Continuing growth, feedback systems seem to be very important.
+%Desire from some partners to have more have even more additional features etc
+%Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!
 
 \subsection{RQ1.1}
+
+%Summary of the results (overview)
 
@@
 \subsection{RQ2}
-The 
-The general conclusion: 
-5 laws clearly apply
-2 laws probably apply (not significant)
-1 law clearly doesn't apply
-
-Have a table which relates each theory to each change (after we have re-analysed the one on docs. )
+You can't assume
 

### 2015-05-04 thesis/paper.tex
Changed folder structure, removed unwanted course folders and made changes to the paper.

--- 2015-05-04 thesis/acm/paper.tex
@@
 
+%%Does this paragraph below belong here or somewhere else? Feels a bit odd!    W: Case Company Description I think
+The API itself consisted of two major versions; 1.4 and 2.0.
+There were no intermediate versions between 1.4 and 2.0.
+Version 1.4 was actually the same version as 1.0, just with added build options for other hardware platforms.
+The changes therefore come from the changes between the two major versions.
+Given that there was an apparent ``big bang'' implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.
+
 \section{Methodology} \label{methodology}
@@
 
+%This should probably go in Methodology... parts of it at least /W
+Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
+Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories.
+Each change was given a main category of maintenance and a subcategory if appropriate.
+This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.
+
 \subsection{Validity Threats} \label{validity_threats}
@@
 
+%%Intoduce the four sections added, removed, modified & general trends.
+
 \subsection{RQ1 Results}
-%This should probably go in Methodology... parts of it at least /W
-Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
-Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories.
-Each change was given a main category of maintenance and a subcategory if appropriate.
-This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.
 
-%%Does this paragraph below belong here or somewhere else? Feels a bit odd!    W: Case Company Description I think
-The API itself consisted of two major versions; 1.4 and 2.0.
-There were no intermediate versions between 1.4 and 2.0.
-Version 1.4 was actually the same version as 1.0, just with added build options for other hardware platforms.
-The changes therefore come from the changes between the two major versions.
-Given that there was an apparent ``big bang'' implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.
+%% Check what willy wrote.
+%%Explain structure of this section around the RQ and a summary of it. Table with the percentages from both us and her.
+
+Specifically we found that 53.8\% of the changes were enhancive changes, 7.7\% were adaptive and the remaining 38.5\% were changes specifically aimed at improving the maintainability of the API.
 
@@
 Each addition added new functionality to the API, ranging from controlling the camera, enabling audio analysis, allowing external storage connections and providing a serial port to interface with other devices.
+
+%XXX
+%These changes were deemed to be modifications or re-implementations of existing functionality of the API.
+During the interview it was mentioned that one intent behind the re-implementations was to bring them in line with the newly created functionality which takes advantage of Glib, a new kind of error handling and extensive use of callbacks.
+
+%XXX
+%While the main focus of our investigation of the source code and documentation was to identify changes between the versions, it was also to discover differences larger trends of the API.
+The trends were also analysed and given an appropriate maintenance category.
+
+%XXX
+%While the changes between versions 1.4 and 2.0 included many deprecations, only one of them was not re-implemented in a new part of the API.
+
+%Discuss how there were many modifications but we've classified them as re-implementations.
+Includes a deprecation and a replacement of that deprecation.
+Alternative was to analyse modify them as both an addition and a deprecation.
 
@@
 
-We concluded that this change was enhancive as it is a brand-new feature of the API. No sub categories were found to be suitable.
+We concluded that this change was enhancive as it is a brand-new feature of the API. No sub-categories were found to be suitable.
 
@@
 Based on the interviewees comments, we concluded that we had correctly identified the change as being enhancive.
-Furthermore, we were also correct in our assumption that there were no suitable subcategories as there was no additional insight into other motivations for the inclusion of this feature.
+Furthermore, we were also correct in our assumption that there were no suitable sub-categories as there was no additional insight into other motivations for the inclusion of this feature.
 
@@
 This change was also determined to be enhancive as it was an inclusion of a brand-new feature to the API.
-Similarly to the axptz, there were no suitable sub categories that could be found to apply to this change.
+Similarly to the axptz, there were no suitable sub-categories that could be found to apply to this change.
 
@@
 Based on the information available, we concluded that we had successfully determined that the change was enhancive.
-Once more, there was no supporting evidence to suggest any suitable subcategories for this change.
+Once more, there was no supporting evidence to suggest any suitable sub-categories for this change.
 
@@
 Enhancive was once again chosen to be the most applicable category of change given that axstorage was a brand-new inclusion in the newest version of the API.
-Similarly, there were no appropriate subcategories for this change.
+Similarly, there were no appropriate sub-categories for this change.
 
@@
 %%Relate it to Categories
-The inclusion of this new feature was once again determined to be an enhancive change as it involved the addition of a brand new feature. No relevant subcategories were found.
+The inclusion of this new feature was once again determined to be an enhancive change as it involved the addition of a brand new feature. No relevant sub-categories were found.
 
@@
 Given this information, we concluded that we were correct in deciding that this change was also enhancive.
-Again, we were also correct in the assumption that there were no suitable subcategories for this change.
-
-%XXX
-%These changes were deemed to be modifications or re-implementations of existing functionality of the API.
-During the interview it was mentioned that one intent behind the re-implementations was to bring them in line with the newly created functionality which takes advantage of Glib, a new kind of error handling and extensive use of callbacks.
+Again, we were also correct in the assumption that there were no suitable sub-categories for this change.
 
@@
 
-%XXX
-%While the changes between versions 1.4 and 2.0 included many deprecations, only one of them was not re-implemented in a new part of the API.
-
 \subsubsection{Burst Mode}
@@
 
-Given this information we can safely say that we correctly concluded that this was a reductive maintenance task and that there are indeed no other subcategories which are applicable to describe this change.
-
-%XXX
-%While the main focus of our investigation of the source code and documentation was to identify changes between the versions, it was also to discover differences larger trends of the API.
-The trends were also analysed and given an appropriate maintenance category.
+Given this information we can safely say that we correctly concluded that this was a reductive maintenance task and that there are indeed no other sub-categories which are applicable to describe this change.
 
@@
 
-We therefore gave this change the main categorisation of adaptive with no suitable subcategories being found.
+We therefore gave this change the main categorisation of adaptive with no suitable sub-categories being found.
 
@@
 The results related to \textbf{RQ2} are structured around each of Lehman's laws and to what extent our findings show that the laws apply to platform APIs.
-The summary of our findings can be seen in Table \ref{table:lehman}.
+A summary of our findings can be seen in Table \ref{table:lehman}.
 
@@
 We found strong evidence to suggest that most, if not all of the additions, re-implementations and functional changes were undertaken to include functionality that the partners desired.
-Specifically we found that 53.8\% of the changes were enhancive changes, 7.7\% were adaptive and the remaining 38.5\% were changes specifically aimed at improving the maintainability of the API.
 
@@
 This leads to the conclusion (!!probably avoid that word in discussion) that the inclusion of new features and the maintainability of an API are two very strong drivers of API evolution.
+
+% 1 - Desire for new functionality
+% 2 - Push for new functionality from partners
+% 3 - Desire for a well designed API, interface improvements
+% 4 - Desire to have a more maintainable API
+%
 
@@
 
-Interesting that the majority of the changes seem to be driven either by management (Suggested that it comes from partners) or the partners directly.
-There was also internal pressure to improve the API which came about from Axis developers trying to create their own applications.
-
 Considering the Ecosystem and considering it as a whole when designing the API.

### 2015-05-04 rmtw/a4/stat/first.R

@@ -1,46 +1,0 @@
-uc_eff <- c(1.3, 8.0, 2.7, 2.7, 6.7, 9.3, 2.7, 5.3, 2.7, 16.0, 4.0, 
-          2.7, 4.0, 14.7, 5.3, 6.7, 4.0, 2.7, 4.0, 13.3, 2.7, 6.7, 
-          13.3, 5.3, 2.7, 10.7)
-
-cl_eff <- c(2.7, 1.3, 10.7, 13.3, 8.0, 10.7, 8.0, 13.3, 9.3, 8.0, 
-            9.3, 8.0, 4.0, 10.7, 6.7, 6.7, 5.3, 5.3, 4.0, 5.3, 
-            2.7, 5.3, 5.3, 5.3, 13.3, 7.3)
-
-uc_rate <- c(0.03, 0.16, 0.05, 0.05, 0.13, 0.18, 0.05, 0.11, 0.05, 
-             0.32, 0.08, 0.05, 0.08, 0.29, 0.11, 0.13, 0.08, 0.05, 
-             0.08, 0.26, 0.05, 0.13, 0.26, 0.11, 0.05, 0.21)
-
-cl_rate <- c(0.05, 0.03, 0.21, 0.26, 0.16, 0.21, 0.16, 0.26, 0.18,
-             0.16, 0.18, 0.16, 0.08, 0.21, 0.13, 0.13, 0.11, 0.11, 
-             0.08, 0.11, 0.05, 0.11, 0.11, 0.11, 0.26, 0.1448)
-
-
-UC = c(1, 6, 2, 2, 5, 7, 2, 4, 2, 12, 3, 2, 3, 11, 4, 5, 3, 2, 3, 10, 2, 5, 10, 4, 2, 8)
-CL = c(2, 1, 8, 10, 6, 8, 6, 10, 7, 6, 7, 6, 3, 8, 5, 5, 4, 4, 3, 4, 2, 4, 4, 4, 10, 5.48)
-m = mean(CL)
-m2 =mean(UC)
-
-
-
-#box_data <- data.frame(UC, CL)
-#boxplot(box_data)
-#boxplot(UC, main = "UC Boxplot")
-#boxplot(CL, main = "CL Boxplot")
-
-
-#ks.test(UC, "pnorm")
-#shapiro.test(UC)
-#ks.test(CL, "pnorm")
-#shapiro.test(CL)
[…]

### 2015-05-04 rmtw/a4/stat/script.R

@@ -1,56 +1,0 @@
-uc_eff <- c(1.3, 8.0, 2.7, 2.7, 6.7, 9.3, 2.7, 5.3, 2.7, 16.0, 4.0, 
-          2.7, 4.0, 14.7, 5.3, 6.7, 4.0, 2.7, 4.0, 13.3, 2.7, 6.7, 
-          13.3, 5.3, 2.7, 10.7)
-
-uc_rate <- c(0.03, 0.16, 0.05, 0.05, 0.13, 0.18, 0.05, 0.11, 0.05, 
-             0.32, 0.08, 0.05, 0.08, 0.29, 0.11, 0.13, 0.08, 0.05, 
-             0.08, 0.26, 0.05, 0.13, 0.26, 0.11, 0.05, 0.21)
-
-cl_eff <- c(2.7, 1.3, 10.7, 13.3, 8.0, 10.7, 8.0, 13.3, 9.3, 8.0, 
-            9.3, 8.0, 4.0, 10.7, 6.7, 6.7, 5.3, 5.3, 4.0, 5.3, 
-            2.7, 5.3, 5.3, 5.3, 13.3, 7.3)
-cl_eff_mean = mean(cl_eff)
-
-
-cl_rate <- c(0.05, 0.03, 0.21, 0.26, 0.16, 0.21, 0.16, 0.26, 0.18,
-             0.16, 0.18, 0.16, 0.08, 0.21, 0.13, 0.13, 0.11, 0.11, 
-             0.08, 0.11, 0.05, 0.11, 0.11, 0.11, 0.26, 0.1448)
-cl_rate_mean = mean(cl_rate)
-
-
-
-eff_data <- data.frame(uc_eff, cl_eff)
-rate_data <- data.frame(uc_rate, cl_rate)
-
-rate_box <- boxplot(rate_data)
-eff_box <- boxplot(eff_data)
-
-
-
-
-
-var.test(uc_eff, cl_eff)
-
-t.test(uc_eff, cl_eff, var.equal=TRUE)
-
-var.test(uc_rate, cl_rate)
-
-t.test(uc_rate, cl_rate, var.equal=TRUE)
-
-
-
-
-
-
-ct <- table(data$result)
-
-chisq.test(ct, correct=FALSE)
-
-
-qqnorm(uc_eff); qqline(uc_eff, col = 2,lwd=2,lty=2)
-
[…]

### 2015-05-04 thesis/paper.tex
added table and other changes

@@
 
+\begin{table}
+       \centering
+       \begin{tabular}[Ht]{|l|c|c|}
+       \hline
+       \textbf{Category} & \textbf{Prediction} & \textbf{Actual} \\
+       \hline
+       Updative & 15.4\% & 7.7\% \\
+       \hline
+       Groomative & 7.7\% & 0.0\% \\
+       \hline
+       Preventive & 7.7\% & 15.4\% \\
+       \hline
+       Enhancive & 53.8\% & 53.8\% \\
+       \hline
+       Reductive & 7.7\% & 7.7\% \\
+       \hline
+       Adaptive & 15.4\% & 7.7\% \\
+       \hline
+       \end{tabular}
+       \caption{Category Distribution}
+       \label{table:Categories}
+\end{table}
+
 %%TODO Finish this off XXX
@@
 
-\subsubsection{axparameter}
+\subsubsection{ax\_parameter}
 
@@
 For example, the interviewee expressed a desire to have features be added to the API more rapidly and more quickly than they have previously.
-This sentiment was also expressed to the interviewee by certain partners who suggested that the API was too stable and citing their wish for more features and more frequent updates to the API.
+This sentiment was also expressed to the interviewee by certain partners who suggested that the API was too stable, citing their wish for additional features and more frequent updates to the API.
 
@@
 % 3 - Desire for a well designed API, interface improvements
-% 4 - Desire to have a more maintainable API
-%
-
+% 4 - Desire to have a maintainable API
+% 5 - The majority of changes added to the API, rather than removed - Seems to support the paper which said most changes are refactorings?
 %

### 2015-05-04 thesis/paper.tex
Added structure for RQ1

@@
 
-%Summary of the results (overview)
+1. 
+Added functionality is a major factor
+-Requests from partners
+-Business motive related to more functionality = more sold cameras
 
@@
 
-These data seem to align with the comments made during the interview.
-For example, the interviewee expressed a desire to have features be added to the API more rapidly and more quickly than they have previously.
-This sentiment was also expressed to the interviewee by certain partners who suggested that the API was too stable, citing their wish for additional features and more frequent updates to the API.
+2. 
+Maintainablity is important, but where that was changed; funcitoanlity changes were alos made
+While are important and while it was mentioend during the interview that the groomative changes would hav ehappend in any case, there is not clear evidence for that allows us to make this concrete/bold claim.
+*Maintianabikltuy/groomative changes usually affect many places (i.e. standardization is very important) (relate it to ripple effects paper)
 
-%The most interesting parts (and reflections + more information about these "trends")
-This leads to the conclusion (!!probably avoid that word in discussion) that the inclusion of new features and the maintainability of an API are two very strong drivers of API evolution.
+3. 
+Controlling the way the users use the applicaitons is very important (error handling, example code, interfaces)
 
-% 1 - Desire for new functionality 
-% 2 - Push for new functionality from partners
-% 3 - Desire for a well designed API, interface improvements
-% 4 - Desire to have a maintainable API
-% 5 - The majority of changes added to the API, rather than removed - Seems to support the paper which said most changes are refactorings?
-%
+4. 
+Relate back to other literature and say that deprecations are preferred before removing, but that removing is recommended in certain cases (i.e when they really dont want ppl to use the function)
+*Dont do it without investigating the possible effects of removing something
+*Dont remove too much at once
 
-%%% Notes and thoughts
-%Consistent with Lehmans Laws - Continuing growth, feedback systems seem to be very important.
-%Desire from some partners to have more have even more additional features etc
-%Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!
+5. 
+Changes to documentation/example code are not important enough to drive changes to API, but they make up a large part of the change (although it's strictly updative (change cuz something else was changed))
+
+6. Hardware was not a driving factor (is this mentioned enough in the prev secitons?)
+Hardware hasn't direclty cotnributed to driving the evolution
 
 \subsection{RQ1.1}
-
-%Summary of the results (overview)
 
@@
 That the part about controlling how the API users use the API was such an important thing is interesting. (Not something we expected). 
+-Relate to 80% refactorings paper and say that we found different results
+*This is an intersting note if we want to compare platform apis and library apis to say that functionality changes more often in platform apis for example
+
+%Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!
 

### 2015-05-04 thesis/paper.tex
Moved a paragraph

@@
 
+After cross examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.
+
 %%TODO Finish this off XXX
@@
 With this information we concluded that our categorisation was incorrect.
-It became clear that this change was in actual fact primarily reformative, given that the changes to the documentation we being performed to meet the needs of the API users.
+It became clear that this change was in actual fact primarily reformative, given that the changes to the documentation were being performed to meet the needs of the API users.
 It was also clear that the subcategory should therefore be updative.
@@
 
-After cross examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.
 While it is obvious that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.

### 2015-05-04 thesis/paper.tex
added structure for disc rq1.1

@@
 
-RQ1.1 - To what extent can we reverse engineer API change decisions?
+1. Added functionality or similar is easy to reverse engineer
 
-While it is obvious that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.
+2. It's hard to distinguish between maintainability/quality-related changes and refactoring/groomative-related changes
+
+Bottom line: It is possible to reverse engineer to some extent
+-While it is obvious that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.
 

### 2015-05-04 thesis/paper.tex
Added structure for disc RQ2

@@
 The changes to the ACAP API has been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
-As mentioned in Section \ref{law3}, the changes introduced in version 1.4 did not involve any changes to the existing API functions.
+As mentioned in Section \ref{sec:law3}, the changes introduced in version 1.4 did not involve any changes to the existing API functions.
 Consequently, the only significant update to the API was made in the transition to version 2.0.
@@
 These changes did, however, increase the quality and was a substantial part of the changes, which could have been left out.
-A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{law2}.
+A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{sec:law2}.
 We therefore settle that the law of declining quality can be applied to APIs, but that there is data that implies that reducing quality is not of high importance.
@@
 The experiences of this API user, were later considered when developing the axsound module.
-One benefit of having a more structured feedback loop, would be that the API developers would be more and faster aware of potential errors in the implementation of the API.
+One benefit of having a more structured feedback loop, would be that the API developers would be more and faster (!!!re-phrase) aware of potential errors in the implementation of the API.
 Another ambition which was mentioned, was to bring scientific theories and best practices from academia into consideration when developing the API.
@@
 \subsection{RQ2}
-You can't assume
+1.
+Feedback system: 
+Something that is very important and might be overlooked in API development/evolution
+
+2. 
+Why don't all theories apply? 
+Try explain what the reason might be, by comparing APIs to normal systems. 
+(Complexity and quality) These apply, but it seems that they are not very important compared to for exmaple functionality. Maybe they are true to a lesser extent compared to normal systems. 
+This is interesting becaues it means one cannot assume that APIs are e-type systems and it cannot be compared to ``normal'' systems in some cases.
+
+3.
+The true ones 
+List the ones that we found a lot of evidence  (the most true: 6,7) (1, 3, 5) and explain why they are true by linking it to RQ1 results
 

### 2015-05-04 thesis/paper.tex
Added discussion RQ1.1

@@
 \smallskip \noindent
-\textbf{Objective } This study explored how companies actively drive changes to APIs and how APIs evolve from a passive point of view.
+\textbf{Objective  } 
+This study explored how companies actively drive changes to APIs and how APIs evolve from a passive point of view.
 The aim was also to test how well we could reverse engineer these change decisions.
@@
 \section{Discussion}
-In this section we will discuss the results of our study.
+Intro with a generic motivation for the study e.g. ``the results and insight into the API development suggest the following things'':
+
+``The results of our study allow us to formulate the following implications of our study:''
 
@@
 
-1. Added functionality or similar is easy to reverse engineer
+\noindent
+\textbf{Functionality is reverse engineerable  } 
+All changes which main motivation were to either add or remove functionality were accurately predicted.
+These changes were the most major ones, and it was expressed during the interview that these changes were the main motive behind the introduction of the new version.
+In summary, 11 out of a total 13 changes were correctly predicted.
+It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted.
+This supports that such changes have a clearer intent and are perhaps more well-defined.
 
-2. It's hard to distinguish between maintainability/quality-related changes and refactoring/groomative-related changes
-
-Bottom line: It is possible to reverse engineer to some extent
--While it is obvious that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.
+\smallskip \noindent
+\textbf{``Structural'' changes are not reverse engineerable  }
+3 out of 5 changes which did not add functionality, but rather were introduced to redcue complexity and increase quality were correctly predicted.
+The two changes which were not predicted correctly were wrong because the main-motivation was mixed up with the sub-intention (!!!re-phrase).
+This shows that although the prediction was incorrect, the general reasoning was correct.
+Our predictions were accurate enough to allow us to form a reliable conlusion which created a good means for discussion with the company (!!!re-phrase).
 
 \subsection{RQ2}
-1.
-Feedback system: 
+
+\noindent
+\textbf{Feedback system  }
 Something that is very important and might be overlooked in API development/evolution
 
-2. 
-Why don't all theories apply? 
+\smallskip \noindent
+\textbf{Why don't all theories apply?  }
 Try explain what the reason might be, by comparing APIs to normal systems. 
@@
 
-3.
-The true ones 
+\smallskip \noindent
+\textbf{The true ones  }
+
 List the ones that we found a lot of evidence  (the most true: 6,7) (1, 3, 5) and explain why they are true by linking it to RQ1 results

### 2015-05-04 thesis/paper.tex
Drafts of RQ1 discussion

@@
 %%Describe the change 
-Version 2.0 of the API has been designed around an event driven system, as such, it's not surprising that the old event system had to be re-implemented.
+Version 2.0 of the API has been designed around an event driven system, as such, it is not surprising that the old event system had to be re-implemented.
 The new event system is used by all features of the new API, for example events are sent when movement is detected by the camera.
@@
 The final re-implementation updated the parameter setting features of the API.
-This particular module had very few changes to it's functionality except for bringing into line, once again, with the new standard.
+This particular module had very few changes to its functionality except for bringing into line, once again, with the new standard.
 
@@
 We were informed that in order to continue using this feature in 2.0 and in newer versions of the camera hardware, it would have to be re-implemented from scratch.
-A cost analysis was performed on taking this action and it was deemed that the impact would be minimal resulting in it's removal from the API.
+A cost analysis was performed on taking this action and it was deemed that the impact would be minimal resulting in its removal from the API.
 
@@
 \section{Discussion}
+Our results have been valuable in exploring the motives behind API changes and the causes of API evolution. When Analysing these results, the following interesting topics came to light:
+
 Intro with a generic motivation for the study e.g. ``the results and insight into the API development suggest the following things'':
@@
 
-\subsection{RQ1}
+\subsection{How do companies actively drive API evolution?}
 
-1. 
-Added functionality is a major factor
--Requests from partners
--Business motive related to more functionality = more sold cameras
+\noindent
+\textbf{Adding functionality is a prime driver of API evolution  }
+Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
+We found strong evidence to suggest that most, if not all of the additions, re-implementations and functional changes were undertaken to include additional functionality requested both internally and by the API users.
+This focus upon functionality was also emphasised in part due to a business goal.
+The more features the API can provide, the more applications developers can create for the cameras.
+This has a knock-on effect of increasing the appeal and therefore value of the products.
 
-Overwhelmingly, the primary driving factor behind API evolution appears to have been the desire for new API functionality.
-We found strong evidence to suggest that most, if not all of the additions, re-implementations and functional changes were undertaken to include functionality that the partners desired.
+%API users should be included in the design process?
+\smallskip \noindent
+\textbf{Maintainability does not drive change  } 
+While maintainability is important, it is not a primary driving factor for change.
+We found that where maintainability changed, functionality was also altered.
+For example, we predicted that the main intents to be enhancive which was correct.
+Furthermore, of the changes identified, none were considered to be primarily groomative, groomative changes were only identified as sub-category changes.
+Changes to the example code is further evidence of this.
+The example code was updated purely to reflect the changes in functionality and not as a groomative effort.
 
-2. 
-Maintainablity is important, but where that was changed; funcitoanlity changes were alos made
-While are important and while it was mentioend during the interview that the groomative changes would hav ehappend in any case, there is not clear evidence for that allows us to make this concrete/bold claim.
-*Maintianabikltuy/groomative changes usually affect many places (i.e. standardization is very important) (relate it to ripple effects paper)
+\smallskip \noindent
+\textbf{Aiding development of applications  } 
+Aiding users of the API to create correct and robust applications is a very important evolution factor for Axis.
+Changes between the versions brought about improvements to error handling, the example code and the way in which the API utilises interfaces.
+This, coupled with removal of unwanted functionality and unsafe operations, has allowed the API to grow and become much more user friendly.
+As mentioned previously, this could increase the amount of applications being created for the camera and thus could increase its value.
 
-3. 
-Controlling the way the users use the applicaitons is very important (error handling, example code, interfaces)
+\smallskip \noindent
+\textbf{Removing functionality  }
+Previous literature has stated that deprecations should be favoured over removals from API for many reasons except in specific circumstances.
+The successful removal of the burst function seems to indicate that this advice is well worth following.
+Indeed, axis only removed this function from the API after an internal review found that the cost of removing it would outweigh potential drawbacks to keeping it in the API.
+It is therefore recommended to only remove something if the effects of removing it have been well investigated and that the removal is rather small in scale.
 
-4. 
-Relate back to other literature and say that deprecations are preferred before removing, but that removing is recommended in certain cases (i.e when they really dont want ppl to use the function)
-*Dont do it without investigating the possible effects of removing something
-*Dont remove too much at once
+\smallskip \noindent
+\textbf{Updative changes do not drive change  }
+Changes to documentation and example code are important, especially if the API is drastically changing between versions.
+However, these updative changes are drivers themselves, rather, they make up part of a larger change as a whole.
+%^Probably needs more to it?
 
-5. 
-Changes to documentation/example code are not important enough to drive changes to API, but they make up a large part of the change (although it's strictly updative (change cuz something else was changed))
-
-6. Hardware was not a driving factor (is this mentioned enough in the prev secitons?)
-Hardware hasn't direclty cotnributed to driving the evolution
+\smallskip \noindent
+\textbf{Hardware was not a driving factor  }
+Interestingly, we found that hardware was not a direct driver of change.
+Initially we had thought that it would be one of the strongest drivers of change, for example, new versions of hardware become available or new hardware is added to the camera requiring something in the API to access it.
+This does seem to suggest that the hardware for the camera is sufficiently stable such that it does not require changes and that those changes do not need to be reflected in new API versions.
 

### 2015-05-04 thesis/paper.tex
Started disc RQ2

--- 2015-05-04 thesis/paper.tex
@@
 
-\subsection{RQ1.1}
+\newpage
+
+\subsection{Discussion RQ1.1}
 
@@
 
-\subsection{RQ2}
+\newpage
+\subsection{Discussion RQ2}
 
 \noindent
+\textbf{A majority of the laws apply  }
+Sufficient evidence was found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System to establish that they apply to APIs.
+The most major explanation for this that a large part of the introduced changes were related to functionality.
+It is especially interesting to note that the laws of Self Regulation and Conservation of Familiarity perfectly match the API explored in this paper.
+
+\smallskip \noindent
+\textbf{Two laws kinda apply  }
+The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that the extent to which they apply might not be as significant for APIs compared to other types of systems.
+The reason that this doubt exists is that these motivations could were only secondary to the motivations of increased functionality.
+An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} might overshadow (!!!wording) the need to increase simplicity and quality.
+
+\smallskip \noindent
+\textbf{One law does not apply}
+Strong evidence was found which suggests that the law of Conservation of Organisational Stability does not apply to APIs.
+
+This is interesting becaues it means one cannot assume that APIs are e-type systems and it cannot be compared to ``normal'' systems in some cases. 
+\smallskip \noindent
 \textbf{Feedback system  }
@@
 
-\smallskip \noindent
-\textbf{Why don't all theories apply?  }
-Try explain what the reason might be, by comparing APIs to normal systems. 
-(Complexity and quality) These apply, but it seems that they are not very important compared to for exmaple functionality. Maybe they are true to a lesser extent compared to normal systems. 
-This is interesting becaues it means one cannot assume that APIs are e-type systems and it cannot be compared to ``normal'' systems in some cases.
-
-\smallskip \noindent
-\textbf{The true ones  }
-
-List the ones that we found a lot of evidence  (the most true: 6,7) (1, 3, 5) and explain why they are true by linking it to RQ1 results
+\newpage
 

### 2015-05-04 thesis/paper.tex

--- 2015-05-04 thesis/paper.tex
@@
 %%Describe the change 
-Version 2.0 of the API has been designed around an event driven system, as such, it is not surprising that the old event system had to be re-implemented.
+Version 2.0 of the API has been designed around an event driven system, as such, it's not surprising that the old event system had to be re-implemented.
 The new event system is used by all features of the new API, for example events are sent when movement is detected by the camera.
@@
 The final re-implementation updated the parameter setting features of the API.
-This particular module had very few changes to its functionality except for bringing into line, once again, with the new standard.
+This particular module had very few changes to it's functionality except for bringing into line, once again, with the new standard.
 
@@
 We were informed that in order to continue using this feature in 2.0 and in newer versions of the camera hardware, it would have to be re-implemented from scratch.
-A cost analysis was performed on taking this action and it was deemed that the impact would be minimal resulting in its removal from the API.
+A cost analysis was performed on taking this action and it was deemed that the impact would be minimal resulting in it's removal from the API.
 

### 2015-05-04 thesis/paper.tex
Discussion RQ2 done

@@
 
+\newpage
 \section{Discussion}
@@
 
-\subsection{How do companies actively drive API evolution?}
+\newpage
+\subsection{Discussion RQ1}
 
@@
 
-\subsection{RQ1.1}
+\newpage
+\subsection{Discussion RQ1.1}
 
@@
 \smallskip \noindent
-\textbf{One law does not apply}
+\textbf{One law does not apply  }
 Strong evidence was found which suggests that the law of Conservation of Organisational Stability does not apply to APIs.
+Our results not only show that the law is not true for APIs, but that the opposite of what the law states is true for APIs.
+This is supported by the consensus in literature of the negative effects caused by modifications to APIs \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
+The results from our study also showed that the reluctancy to change APIs causes the releases of new versions to be few and sporadic.
 
-This is interesting becaues it means one cannot assume that APIs are e-type systems and it cannot be compared to ``normal'' systems in some cases. 
 \smallskip \noindent
-\textbf{Feedback system  }
-Something that is very important and might be overlooked in API development/evolution
+\textbf{The importance of a Feedback System  }
+Especially interesting results were found in regards to the law of Feedback System.
+The importance of having a structured and developed feedback loop was stressed during the interview, and it was also expressed as one of the main points of improvement.
+This suggests that including feedback from more sources and making use of this feedback should be done more when developing an API.
 

### 2015-05-04 thesis/paper.tex
Intro to disc

@@
 
-\newpage
 \section{Discussion}
-Our results have been valuable in exploring the motives behind API changes and the causes of API evolution. When Analysing these results, the following interesting topics came to light:
+Our results have been provided valuable insight to the motives behind the evolution of an API.
+The results show that APIs definitely can be studied from the point of view of old evolution theories.
+Based on the result, we have formulated the subsequent outcomes.
 
-Intro with a generic motivation for the study e.g. ``the results and insight into the API development suggest the following things'':
-
-``The results of our study allow us to formulate the following implications of our study:''
-
-\newpage
 \subsection{Discussion RQ1}
@@
 
-\newpage
 \subsection{Discussion RQ1.1}
@@
 
-\newpage
 \subsection{Discussion RQ2}
@@
 This suggests that including feedback from more sources and making use of this feedback should be done more when developing an API.
-
-\newpage
 

### 2015-05-04 thesis/paper.tex
Removed Gothenburg, Sweden from auth block
Added missing fullstops in discussion

@@
        \affaddr{University of Gothenburg}\\
-       \affaddr{Gothenburg, Sweden}\\
        \email{john.a.burchell@gmail.com}
@@
        \affaddr{University of Gothenburg}\\
-       \affaddr{Gothenburg, Sweden}\\
        \email{william.granli@gmail.com}
@@
        \affaddr{University of Gothenburg}\\
-       \affaddr{Gothenburg, Sweden}\\
        \email{imed.hammouda@gu.se}
@@
 \noindent
-\textbf{Adding functionality is a prime driver of API evolution  }
+\textbf{Adding functionality is a prime driver of API evolution.  }
 Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
@@
 \smallskip \noindent
-\textbf{Maintainability does not drive change  } 
+\textbf{Maintainability does not drive change.  } 
 While maintainability is important, it is not a primary driving factor for change.
@@
 \smallskip \noindent
-\textbf{Aiding development of applications  } 
+\textbf{Aiding development of applications.  } 
 Aiding users of the API to create correct and robust applications is a very important evolution factor for Axis.
@@
 \smallskip \noindent
-\textbf{Removing functionality  }
+\textbf{Removing functionality.  }
 Previous literature has stated that deprecations should be favoured over removals from API for many reasons except in specific circumstances.
@@
 \smallskip \noindent
-\textbf{Updative changes do not drive change  }
+\textbf{Updative changes do not drive change.  }
 Changes to documentation and example code are important, especially if the API is drastically changing between versions.
@@
 \smallskip \noindent
-\textbf{Hardware was not a driving factor  }
+\textbf{Hardware was not a driving factor.  }
 Interestingly, we found that hardware was not a direct driver of change.

### 2015-05-04 thesis/paper.tex
Intro to results

@@
 \section{Results} \label{results}
-Introduction.
+This section will present the results of our study.
+The results related to \textbf{RQ1} and \textbf{RQ1.1} are introduced in Section \ref{results_rq1}, and the results of \textbf{RQ2} are presented in Section \ref{results_rq2}
 
-%%Intoduce the four sections added, removed, modified & general trends.
-
-\subsection{RQ1 Results}
+\subsection{RQ1 Results} \label{results_rq1}
 
@@
 
-\subsection{RQ2 Results}
+\subsection{RQ2 Results} \label{results_rq2}
 The results related to \textbf{RQ2} are structured around each of Lehman's laws and to what extent our findings show that the laws apply to platform APIs.

### 2015-05-04 thesis/paper.tex
updated results section

@@
 %%Explain structure of this section around the RQ and a summary of it. Table with the percentages from both us and her.
+In order to answer RQ1, we categorised the changes based on the 12 maintenance categories \cite{chapin2001types}.
+Initially we created predictions of the changes from inspecting the source code and accompanying documentation.
+Following the interview we compared our results with response from the interview to decide the actual maintenance categories of the changes.
+\ref{table:Categories} shows the predicted and actual maintenance categories.
 
-Specifically we found that 53.8\% of the changes were enhancive changes, 7.7\% were adaptive and the remaining 38.5\% were changes specifically aimed at improving the maintainability of the API.
+The changes have been divided up into four specific categories, namely: new, modified, removed and general trends.
+New and modified concern additions or modifications to modules, removed are features which have been removed entirely without deprecating and general trends are broad changes which do not directly affect functionality.
 
@@
 
-After cross examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.
+After cross-examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.
 

### 2015-05-04 thesis/paper.tex
RQ1 results intro

--- 2015-05-04 thesis/paper.tex
@@
 %%Explain structure of this section around the RQ and a summary of it. Table with the percentages from both us and her.
+In order to answer \textbf{RQ1}, we categorised the changes based on the 12 maintenance categories \cite{chapin2001types}.
+Initially, we created predictions of the changes from inspecting the source code and accompanying documentation.
+Following the interview, we compared our predictions with the actual motive which was deduced from the interviewee's reasoning.
+Table \ref{table:Categories} shows the predicted and actual maintenance categories.
 
-Specifically we found that 53.8\% of the changes were enhancive changes, 7.7\% were adaptive and the remaining 38.5\% were changes specifically aimed at improving the maintainability of the API.
+The changes have been divided up into four specific categories, namely: new, modified, removed and general trends.
+New and modified changes concern additions of or modifications to modules and removed changes is functionality which have been removed entirely without being deprecating or replaced by new implementations.
+General trends are broad changes which do not directly affect functionality.
 

### 2015-05-04 thesis/paper.tex
hi

@@
 \subsection{RQ2 Results} \label{results_rq2}
-The results related to \textbf{RQ2} are structured around each of Lehman's laws and to what extent our findings show that the laws apply to platform APIs.
+The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs.
 A summary of our findings can be seen in Table \ref{table:lehman}.
@@
 \noindent
-\textbf{Adding functionality is a prime driver of API evolution.  }
+\textbf{Adding functionality is a prime driver of API evolution  }
 Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
@@
 \smallskip \noindent
-\textbf{Maintainability does not drive change.  } 
+\textbf{Maintainability does not drive change  } 
 While maintainability is important, it is not a primary driving factor for change.
@@
 \smallskip \noindent
-\textbf{Aiding development of applications.  } 
+\textbf{Aiding development of applications  } 
 Aiding users of the API to create correct and robust applications is a very important evolution factor for Axis.
@@
 \smallskip \noindent
-\textbf{Removing functionality.  }
+\textbf{Removing functionality  }
 Previous literature has stated that deprecations should be favoured over removals from API for many reasons except in specific circumstances.
@@
 \smallskip \noindent
-\textbf{Updative changes do not drive change.  }
+\textbf{Updative changes do not drive change  }
 Changes to documentation and example code are important, especially if the API is drastically changing between versions.
@@
 \smallskip \noindent
-\textbf{Hardware was not a driving factor.  }
+\textbf{Hardware was not a driving factor  }
 Interestingly, we found that hardware was not a direct driver of change.

### 2015-05-04 thesis/paper.tex
fixed a typo

@@
 The changes have been divided up into four specific categories, namely: new, modified, removed and general trends.
-New and modified changes concern additions of or modifications to modules and removed changes is functionality which have been removed entirely without being deprecating or replaced by new implementations.
+New and modified changes concern additions of or modifications to modules.
+Removed changes are functionality which have been removed entirely without being deprecated or replaced by new implementations.
 General trends are broad changes which do not directly affect functionality.
@@
 \section{Discussion}
-Our results have been provided valuable insight to the motives behind the evolution of an API.
+Our results have provided valuable insight to the motives behind the evolution of an API.
 The results show that APIs definitely can be studied from the point of view of old evolution theories.

### 2015-05-04 thesis/paper.tex
added my email and affiliation to test setup of git.

--- 2015-05-04 thesis/paper.tex
@@
+\documentclass{sig-alternate}
+\usepackage{blindtext}
+\usepackage[english]{babel}
+
+\begin{document}
+
+\conferenceinfo{14th IWPSE} {'15 Bergamo, Italy}
+\CopyrightYear{2015}
+
+\crdata{1-23456-78-9/01/23}
+
+\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
+
+\numberofauthors{4}
+
+\author{
+% 1st. author
+\alignauthor
+John Burchell\\
+       \affaddr{Computer Science and Engineering}\\
+       \affaddr{University of Gothenburg}\\
+       \email{john.a.burchell@gmail.com}
+% 2nd. author
+\alignauthor
+William Granli\\
+       \affaddr{Computer Science and Engineering}\\
+       \affaddr{University of Gothenburg}\\
+       \email{william.granli@gmail.com}
+\and
+% 3rd. author
+\alignauthor Imed Hammouda\titlenote{Co-author}\\
+       \affaddr{Computer Science and Engineering}\\
+       \affaddr{University of Gothenburg}\\
+       \email{imed.hammouda@gu.se}
+% 4th 
+\alignauthor Eric Knauss\titlenote{Co-author}\\
+       \affaddr{Computer Science and Engineering}\\
+       \affaddr{Chalmers $\mid$ University of Gothenburg}\\
+       \email{eric.knauss@cse.gu.se}
+}
+
+\maketitle
+
+\begin{abstract}
+
+\textbf{Background  } 
+Studies of the motives and drivers behind modifications to APIs have been done before, but platform APIs are, so far, unexplored.
+Previous work has also not studied APIs from the perspective of widely recognised software evolution theories, such as the Types of Software Evolution and Software Maintenance and Lehman's laws of software evolution.
+
+\smallskip \noindent
+\textbf{Objective  } 
+This study explored how companies actively drive changes to APIs and how APIs evolve from a passive point of view.
+The aim was also to test how well we could reverse engineer these change decisions.
+The goal was to study these factors by relating them to existing software evolution theories.
+
+\smallskip \noindent
+\textbf{Method  }
+This case study was conducted by investigating the changes between two versions in a platform API and its documentation, and by interview the architects of the API.
+The changes were analysed from a qualitative and investigative point of view.
+
+\smallskip \noindent
+\textbf{Results  }
+This study identified 13 majors changes to the API.
+The study concluded that the most major driving force for the evolution of APIs is the drive for new functionality and that change decisions to a large extent can be reverse engineered.
+It was also found that 7 out of 8 of Lehman's laws were applicable to APIs.
+
+\smallskip \noindent
+\textbf{Conclusion  }
+This study has provided valuable insight into the evolution of platform APIs.
+The qualitative analysis can help other companies to improve their API maintenance process.
+The successful attempt to reverse engineer the change decisions should encourage similar studies to be conducted.
+The investigation of Lehman's laws show that APIs cannot be generalised and be compared to any type of system.
+
+\end{abstract}
+
+\category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and re-engineering]
+\category{K.6.3}{Computing Milieux}{Software Management}[Software Maintenance]
+
+\terms{Theory, Design or Verification/Documentation maybe?}
+
+\keywords{API Design, Software Evolution, Software Maintenance}
+
+\section{Introduction} \label{introduction}
+%API Design (and a little bit of ecosystems and a bit of problem statement)
+As the software industry and the open-source movement steadily grow, the number of public APIs is increasing.
+APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
+There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
+The main reason is that it will require the users to update the code, which is using the API, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
+The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}.
+%Software Evolution 
+In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint.
+Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software}.
+
+%Gap in Literature
+Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
+There are, however, no studies that attempt to map the motives behind changes to existing software evolution theories, such as the four categories of maintenance \cite{lientz1980software}.
+The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
+To the best of our knowledge, no studies that explore the motives behind or the effects of API evolution have previously been performed on embedded platform APIs.
+Reverse engineering design decisions is a challenging yet interesting problem.
+The better we can understand why changes occur and what problems they are trying to solve, the better we can design around these problems to avoid them cropping up in the future.
+
+%Purpose (and a bit of problem statement)
+%%****NEW*****
+Making changes to existing APIs can have a negative impact upon the users of those APIs.
+It is therefore important to understand why these changes occur.
+Understanding the motives behind the changes could help API designers prevent or avoid potential changes to their APIs.
+In order to achieve this and to provide immediate benefit to industry, an exploratory case study will be undertaken to investigate the underlying motives behind API changes of an existing API.
+Empirical analysis of changes between two major versions of an API will be undertaken, following which an interview with the architects will be used to verify the findings of our study.
+%%****^NEW^****
+
+%Old
+Due to the negative implications that modifications to APIs cause for its users, it is important to understand why changes to them occur.
+If most common pitfalls are known before the development of new APIs begin, these mistakes can be mitigated.
+Before the industry can make use of this information, we must also critically assess to what degree we can trace such motives.
+To achieve this, we will perform a case study which aims to investigate the underlying factors behind API changes.
+This will be achieved by empirically analysing the changes between two versions of an API.
+Subsequently, the designers of the API will be interviewed and asked to verify the accuracy of our findings.
+%Old
+
+\subsection{Research Questions} \label{rqs}
+\begin{description}
+\item[\textbf{RQ1}] How do companies actively drive API evolution?
+\item[\textbf{RQ1.1}] To what extent can we reverse engineer API change decisions?
+\item[\textbf{RQ2}] How do APIs ``passively'' evolve?
+
+\end{description}
+
+%Structure of the paper
+The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the background and previously published work that is related to our study.
+Section \ref{case_company_description} describes the case company and how it was selected.
+A description of our methodology is introduced in Section \ref{methodology}.
+In Section \ref{results}, the results of our study are presented and in Section \ref{conclusion}, we discuss the findings of our study.
+
+\section{Existing Literature} \label{existing_literature}
+This section will introduce the topics of API design and software evolution and provide a brief review of studies that are directly related to our study.
+
+\subsection{API Design} \label{api_design}
+API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{stylos2006comparing} \cite{afonso2012evaluating} \cite{bloch2008effective}.
+Examples of such decisions are whether to use the factory pattern or constructors to create objects, or if the API should display errors during compilation or runtime \cite{stylos2006comparing}.
+More trivial design problems, such as, assigning names to API features and difficulty in naming types also have a large impact on the usability of the API \cite{shi2011empirical}.
+When facing such design decisions, the following four factors are important to consider: a) The API  must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
+One of the most important qualities in an API is that the intent of the API is clear to the user when, for example, using design patterns, such as the concrete factory pattern \cite{stylos2006comparing} \cite{shi2011empirical}.
+The sum of all design decisions taken during the development of an API will decide the usability of the API.
+Measuring such a factor can be done by measuring the twelve cognitive dimensions which are factors that are impacted by the interaction between the API and the user of it \cite{clarke2004measuring}.
+
+\subsection{Software Evolution} \label{software_evolution}
+%%Categories of maintenance and types of maintenance
+Software evolution is a field which studies the application of software maintenance activities and processes on software and the resulting, evolved versions of the software.
+The concept of software maintenance has existed since the 1960s.
+Well-known studies from this era established the importance of software maintenance \cite{lientz1980software}.
+One study would go on to have a particularly profound effect on software maintenance by establishing a set of four categories which describe the intents behind change to software \cite{lientz1980software}.
+These categories were refined in a further study, in which the number of categories were increased from four to twelve \cite{chapin2001types}.
+The categories proposed were: Enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training \cite{chapin2001types}.
+Each category describes a type of software maintenance activity which relate to one of three particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}.
+This study also helped to further the distinction between software maintenance and software evolution.
+The study suggested that software maintenance is a part of software evolution and that the two are not interchangeable \cite{chapin2001types}.
+
+%%Lehman's laws (!!!improve later)
+An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}.
+The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
+The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.
+
+\subsection{Related Work} \label{related_work}
+Previous studies that have attempted analyse APIs in the context of software evolution have primarily focused on APIs that are a part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}.
+One study \cite{hou2011exploring} attempted to uncover the intents behind the changes made in the AWT and Swing Java libraries.
+They found that the use of a strong architecture was vital in ensuring a successful evolution of the API \cite{hou2011exploring}.
+In their study, the intents were categorised around programming related factors such as reducing coupling or conformance to naming conventions.
+
+One study \cite{dig2005role} investigated three frameworks and one library in which the study found that 80\% of refactoring changes to APIs negatively affected existing applications.
+Refactorings are not the only changes to APIs that can impact existing projects negatively.
+Another study was conducted regarding the changes, which the researchers refer to as ripple effects \cite{robbes2012developers}.
+They found that changes in APIs have an effect upon the entire ecosystem.
+This particular empirical study found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.
+
+\section{Case Company Description} \label{case_company_description}
+The case company is a medium-sized company in the domain of security cameras.
+The company has its headquarters in Lund, Sweden, but it operates worldwide.
+The company is the global market leader in the markets of network cameras and video encoders.
+The company develops embedded software for the security cameras and some of their products are designed to be accessible through APIs that are also developed by the company.
+
+%Try to get information about the users of the API. Either through Imed, or through the interviews.
+
+The case was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}.
+As such, the goal was to include as many companies as possible in this study.
+
+%Try to motivate why other sampling methods weren't used.
+
+%Info from the interview, add to this section
+Has been released, in the form we looked at (supports that we’re doing a ``real'' case study)
+They have partners which develop applications using their API. These applications are then used by the end-users of the camera.
+
+%%
+Hardware
+The API platform is developed for many different types of cameras. 
+Some have audio, some don’t, for example.
+
+%%Does this paragraph below belong here or somewhere else? Feels a bit odd!    W: Case Company Description I think
+The API itself consisted of two major versions; 1.4 and 2.0.
+There were no intermediate versions between 1.4 and 2.0.
+Version 1.4 was actually the same version as 1.0, just with added build options for other hardware platforms.
+The changes therefore come from the changes between the two major versions.
+Given that there was an apparent ``big bang'' implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.
+
+\section{Methodology} \label{methodology}
+%Intro and summary
+This study has been conducted using the case study meth-odology \cite{runeson2009guidelines}.
+The goal of the study was twofold.
+Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's explanation of their motives.
+Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.
+
+%Reasons for choosing case study
+The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
+The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}.
+An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research; especially to be able to answer \textbf{RQ2}.
+
+%Consider adding subsub for code+doc and interviews later
+\subsection{Data Collection} \label{data_collection}
+%Intro to code inspection
+The data were collected primarily through inspections of the source code and the archival analysis of accompanying  documentation.
+The source code was comprised of two versions of an API which the company had developed.
+An older version (1.4) which is currently released and a newer version which has recently been deployed (2.0).
+Each version of the API had its own respective documentation.
+The documentation was inspected and organised to find explanations of the features offered by the API.
+
+%Description of inspection
+From the APIs we collected method names, parameters and return types.
+(!!!Add more here.
+Maybe put it in a table?) The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
+<-- do we still want to mention exactly what kinds of data we looked for?
+i.e.
+return types, enums, typedefs etc etc.
+
+The APIs were inspected to determine where the changes had occurred.
+We used the Git Diff tool to find differences between two versions of files that existed in both versions of the API.
+Once we had identified the changes, we inspected the documentation and the code itself to determine if there was a reason for the change, for example, if a given function had been labelled deprecated between versions.
+These changes were then categorised by new changes, updates or re-implementations, removals and general trends.
+The collected data were input into tables and spreadsheets, according to the API version.
+
+%Reduce human error
+The data collection from code and documentation was performed independently by both researchers, to reduce the risk of human errors affecting the results.
+If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.
+
+%Interviews !!!improve later
+After the initial source code inspection had been performed, interviews were conducted.
+The main purpose of these was to validate our findings during the code inspection with the designers of the APIs.
+Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection.
+The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API and how their decisions, needs and requirements have affected the development of the API.
+
+\subsection{Data Analysis} \label{data_analysis}
+%Intro and summary
+The data analysis was conducted in two major phases \cite{andersson2007spiral}.
+During the first phase, a hypothesis generating approach \cite{seaman1999qualitative} was used to be able to fulfil the exploratory goal of the study.
+It was during this phase that the analysis of the API code and documentation was carried out.
+The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase.
+Both phases were performed iteratively, together with the data collection.
+This created the opportunity to improve the process of analysis as the study progressed, as well as allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
+The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
+
+%Description of code analysis
+More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{chapin2001types} the motive of the change corresponded to.
+The data were then mapped and coded to the laws presented by \cite{lehman1980programs}.
+The codes were then analysed from a high-level point of view, the main goal of which was to identify trends in the codes.
+The final step involved analysis of these trends and it was during this stage the hypotheses were generated and formulated.
+The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.
+
+%Description of interview analysis
+Following the analysis of the archival data, the results of the interviews were analysed.
+The interviews were analysed using the same approach taken for the archival data.
+The results of this analysis was then compared and correlated with the results of the code analysis, with the goal of confirming the hypotheses that had been formulated.
+This support also supported triangulation of our results.
+
+%Relate to RQs
+The software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer \textbf{RQ1}.
+The software evolution categories were used to map and explore motives behind changes and Lehman's laws were used to see what drives the natural evolution of APIs.
+Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, will serve as the basis for answering \textbf{RQ2}.
+
+%This should probably go in Methodology... parts of it at least /W
+Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
+Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories.
+Each change was given a main category of maintenance and a subcategory if appropriate.
+This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.
+
+\subsection{Validity Threats} \label{validity_threats}
+In this section we discuss possible threats to construct validity, internal validity, external validity and reliability \cite{runeson2009guidelines}.
+
+%We must add construct validity.
+
+%Internal Validity
+\textit{Internal validity} threats for our study have been greatly reduced by the methodologies we have employed.
+By performing an individual inspection of  the API source code, documentation and individual results analysis, internal validity is significantly reduced.
+Triangulation of the results with the use of interviewing the designers is a key step in reducing potential validity threats in our study.
+
+%External Validity
+Regarding \textit{external validity}, generalisability and the appropriateness of our results are at risk.
+In our study we have striven to ensure that our findings will be as useful as possible to others.
+Given that there are some similar studies to ours and that ours is an exploratory study, our results will be useful to others who perform similar studies in the future.
+Our results come from both APIs either in production or soon to be in production.
+As such, the results of this study will hopefully be of use to the company at which they were studied, be it now for their current API or in the future when they inevitably develop others.
+Likewise, other companies in similar positions could use the results of our study when creating their own APIs.
+
+%Reliability
+The largest \textit{reliability} threat facing our study was the reproducibility.
+To counter this threat, we have followed a well-proven method for analysing the collected data.
+Furthermore, as mentioned previously, we have attempted to limit bias and ambiguity in our interview questions where possible.
+To ensure clarity of the questions, we have field tested the interview with some of our peers, improving the questions based on their feedback.
+
+%Another threat was we were reliant upon being given documentation and code. I.e. they might not give us everything, leave stuff out, ignore things etc.
+
+\section{Results} \label{results}
+This section will present the results of our study.
+The results related to \textbf{RQ1} and \textbf{RQ1.1} are introduced in Section \ref{results_rq1}, and the results of \textbf{RQ2} are presented in Section \ref{results_rq2}
+
+\subsection{RQ1 Results} \label{results_rq1}
+
+%% Check what willy wrote.
+%%Explain structure of this section around the RQ and a summary of it. Table with the percentages from both us and her.
+In order to answer \textbf{RQ1}, we categorised the changes based on the 12 maintenance categories \cite{chapin2001types}.
+Initially, we created predictions of the changes from inspecting the source code and accompanying documentation.
+Following the interview, we compared our predictions with the actual motive which was deduced from the interviewee's reasoning.
+Table \ref{table:Categories} shows the predicted and actual maintenance categories.
+
+The changes have been divided up into four specific categories, namely: new, modified, removed and general trends.
+New and modified changes concern additions of or modifications to modules and removed changes is functionality which have been removed entirely without being deprecating or replaced by new implementations.
+General trends are broad changes which do not directly affect functionality.
+
+\begin{table}
+       \centering
+       \begin{tabular}[Ht]{|l|c|c|}
+       \hline
+       \textbf{Category} & \textbf{Prediction} & \textbf{Actual} \\
+       \hline
+       Updative & 15.4\% & 7.7\% \\
+       \hline
+       Groomative & 7.7\% & 0.0\% \\
+       \hline
+       Preventive & 7.7\% & 15.4\% \\
+       \hline
+       Enhancive & 53.8\% & 53.8\% \\
+       \hline
+       Reductive & 7.7\% & 7.7\% \\
+       \hline
+       Adaptive & 15.4\% & 7.7\% \\
+       \hline
+       \end{tabular}
+       \caption{Category Distribution}
+       \label{table:Categories}
+\end{table}
+
+After cross-examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.
+
+%%TODO Finish this off XXX
+%New additions to the API were the most frequent change that we observed.
+Each addition added new functionality to the API, ranging from controlling the camera, enabling audio analysis, allowing external storage connections and providing a serial port to interface with other devices.
+
+%XXX
+%These changes were deemed to be modifications or re-implementations of existing functionality of the API.
+During the interview it was mentioned that one intent behind the re-implementations was to bring them in line with the newly created functionality which takes advantage of Glib, a new kind of error handling and extensive use of callbacks.
+
+%XXX
+%While the main focus of our investigation of the source code and documentation was to identify changes between the versions, it was also to discover differences larger trends of the API.
+The trends were also analysed and given an appropriate maintenance category.
+
+%XXX
+%While the changes between versions 1.4 and 2.0 included many deprecations, only one of them was not re-implemented in a new part of the API.
+
+%Discuss how there were many modifications but we've classified them as re-implementations.
+Includes a deprecation and a replacement of that deprecation.
+Alternative was to analyse modify them as both an addition and a deprecation.
+
+\subsubsection{axptz}
+
+This change introduced the ability to perform Pan, Tilt and Zoom (ptz) manoeuvres both mechanically and digitally on the camera.
+For example, zooming in on a particular section of a large image, panning the camera to the left to view a certain area.
+
+We concluded that this change was enhancive as it is a brand-new feature of the API. No sub-categories were found to be suitable.
+
+%%Explain what she said
+The interviewee described how this change and the 3 following changes were all included in the new API at the request of both API users and product management.
+The feature was sought after by API users frequently, while they were able to control the camera, there was no official application for doing so and as such, it was a good candidate for inclusion in the new API.
+
+%%Explain how this relates to the category
+Based on the interviewees comments, we concluded that we had correctly identified the change as being enhancive.
+Furthermore, we were also correct in our assumption that there were no suitable sub-categories as there was no additional insight into other motivations for the inclusion of this feature.
+
+\subsubsection{axaudio}
+
+%%Describe the change 
+By and large the most common usage of the camera is to analyse video data, however some of the API users require audio data.
+The inclusion of axaudio allows these users to perform audio analysis upon audio streams captured by Axis devices.
+
+%%Relate it to Categories
+This change was also determined to be enhancive as it was an inclusion of a brand-new feature to the API.
+Similarly to the axptz, there were no suitable sub-categories that could be found to apply to this change.
+
+%%What she said
+Audio analysis had not previously been possible on Axis devices.
+However, the interviewer informed us that an API user had managed to create their own audio analysis using the current (1.4) API.
+Given the demand for audio analysis, it was a logical choice to include it as a new feature in the new version of the API.
+
+%%Category based on her information
+Based on the information available, we concluded that we had successfully determined that the change was enhancive.
+Once more, there was no supporting evidence to suggest any suitable sub-categories for this change.
+
+\subsubsection{axstorage}
+
+%%Describe the change 
+Prior to the newest version of the API, storage for the devices existed solely on the cameras or the Video Management System (VMS) itself.
+The release of version 2.0 saw the inclusion of alternative storage solutions.
+axstorage now allows Axis devices to interface with external storage devices, such as
+
+Enhancive was once again chosen to be the most applicable category of change given that axstorage was a brand-new inclusion in the newest version of the API.
+Similarly, there were no appropriate sub-categories for this change.
+
+%%Her information
+The limited storage options for the Axis devices meant that this feature was strongly requested by API users and as such was included in this new version of the API.
+
+%%Relate it to Categories
+The information gathered from the interview supported that were correct in our choice of enhancive for this change. Once more there was no inclusion of an appropriate subcategory.
+
+\subsubsection{axserialport}
+
+%%Describe the change 
+The final new feature of the API was the inclusion of axserialport.
+This part of the API allows API users to connect various devices to their cameras through the use of a serial port.
+This effectively allows users to integrate multiple kinds of devices to create their own unique solutions.
+In the previous version of the API there was no ability to connect to devices outside of the VMS.
+
+%%Relate it to Categories
+The inclusion of this new feature was once again determined to be an enhancive change as it involved the addition of a brand new feature. No relevant sub-categories were found.
+
+Our interviewee described scenarios whereby a camera could be used with external devices to create, for example, a ticketing system which reacts to users interacting with it in close proximity.
+This was just one scenario in which users might wish to use the camera with other devices.
+As such it was included in the new API to meet the demand of the API users.
+
+%%Real category
+Given this information, we concluded that we were correct in deciding that this change was also enhancive.
+Again, we were also correct in the assumption that there were no suitable sub-categories for this change.
+
+\subsubsection{axevent}
+
+%%Describe the change 
+Version 2.0 of the API has been designed around an event driven system, as such, it's not surprising that the old event system had to be re-implemented.
+The new event system is used by all features of the new API, for example events are sent when movement is detected by the camera.
+This event system is combined with the use of callbacks to create a robust event driven API.
+
+%%Relate it to Categories
+Given that this feature was a re-implementation, we concluded that it should be classified mainly as an enhancive change with the subcategory of change being classified as groomative.
+Groomative was chosen as a subcategory due to the alternate intention of bringing the new feature in line with the new interface.
+
+The interviewee mentioned that the previous version of axevent, event, was being deprecated in favour of this new implementation.
+The primary reason was to bring the implementation into line with the new way that the API handles events and interfaces as a whole.
+The interviewee mentioned that they realised that the API was hard to use previously and that improving it this way, through the use of re-implementations, could allow them to create an easier to use API.
+
+Groomative is therefore the obvious choice for the main category for this change with enhancive being the subcategory.
+This is the reverse of what we concluded and as such means that we incorrectly determined the intent for this change.
+
+\subsubsection{axhttp}
+
+%%Describe the change 
+axhttp was re-implemented from the previous version of the API to follow the new interface and callbacks standards while also including the event driven architecture of 2.0.
+Functionality remained similar in that it allowed the conversion of data into html in order to display on web pages.
+
+This change is very similar to the previously mentioned change and as such is classified in the same way; a main categorisation of enhancive with groomative as the subcategory of change.
+
+The interviewee again described how the main intent to changing this part of the API came about most to bring it into line with the new event driven and callback focused architecture.
+Similarly to the previous change, this feature was redesigned and re-implemented with added functionality.
+
+Our conclusion of enhancive and groomative was also backwards for this change.
+As per the previous change, the primary intent was to bring these parts of the API into line with the new standard; improving functionality was an added bonus.
+
+\subsubsection{ax\_parameter}
+
+%%Describe the change 
+The final re-implementation updated the parameter setting features of the API.
+This particular module had very few changes to it's functionality except for bringing into line, once again, with the new standard.
+
+This change was also deemed to be primarily enhancive with a subcategory of groomative.
+The reason being that this change was part of the broader re-implementation and while it did not purely add new functionality, it did change aid in changing the behaviour of this particular part of the API.
+
+The interviewee once again clarified how this change was indeed primarily concerned with meeting the new standards of version 2.0.
+They agreed that little had actually changed in terms of what functionality the API offered and gave the same reasoning suggested for the two prior changes.
+
+Once again our conclusion was incorrect for the categorisation of this change.
+Given the information from the interview, we deemed that this change was also primarily groomative with a subcategory of enhancive.
+
+\subsubsection{Burst Mode}
+
+The burst mode feature of the API allowed users to buffer a series of images for closer analysis. This feature was deprecated during the transition between 1.4 and 2.0 and was not re-implemented.
+
+This change presented itself as a clear example of a reductive category of maintenance as it was simply removed and not replaced anywhere else.
+We also concluded that this change had no suitable subcategory in which to classify the change.
+
+The interviewee did shed some light onto why this change occurred.
+We were informed that in order to continue using this feature in 2.0 and in newer versions of the camera hardware, it would have to be re-implemented from scratch.
+A cost analysis was performed on taking this action and it was deemed that the impact would be minimal resulting in it's removal from the API.
+
+Given this information we can safely say that we correctly concluded that this was a reductive maintenance task and that there are indeed no other sub-categories which are applicable to describe this change.
+
+\subsubsection{Example Code}
+
+%%Describe the change 
+As with many APIs, Axis included a selection of example programs to assist developers in creating applications by giving explicit examples of their usage.
+This trend continued in 2.0 but there were some significant improvements.
+The number of example programs increased, as did the amount of comments accompanying the code which lead to an overall more robust set of examples.
+
+We therefore concluded that this change was updative as the example code was updated to the new API and the new techniques which it utilises.
+We further decided that this change also had a subcategory of reformative.
+
+From the interview it became clear that the improvement of the example code was an important change between the two versions.
+The interviewee described to us how the examples were used frequently by their customers, however, the old examples varied significantly between how different and even similar tasks were implemented.
+This ultimately meant that the old examples were not good enough and new ones needed to be created, preferably conforming to a single standard of implementation techniques.
+The new examples made sure to cover the new functionality, specific new features and they to show how they can be combined to create applications.
+
+With this information we concluded that our categorisation was incorrect.
+It became clear that this change was in actual fact primarily reformative, given that the changes to the documentation were being performed to meet the needs of the API users.
+It was also clear that the subcategory should therefore be updative.
+
+\subsubsection{Documentation}
+
+%%Describe the change 
+As the API changed versions, so too did the documentation.
+While there were no substantial changes, we did notice that the documentation is no longer offered as a PDF via latex but is instead only offered via HTML.
+
+We categorised this change as being updative with a reformative subcategory for the reasons that the change only updated the documentation to reflect the recent changes in the API.
+
+This sentiment was supported by the interview.
+The interviewee agreed with our assessment that the documentation was only changed to be up to date with the current workings of the API and how the new systems interact with each other.
+
+As there was no information to contradict our categorisations we have concluded we were correct in our assumptions.
+
+\subsubsection{Interfaces}
+
+%%Describe the change 
+The API interfaces experienced the most change between the two versions.
+Three of the older interfaces were deprecated in favour of the new API architecture and the rest of the API is now comprised of brand new interfaces.
+The exception to this appears to be the image capture interface which only experienced a deprecation of a single feature.
+Each new feature is either accessed directly or via an interface which acts as a facade.
+
+We therefore concluded that this change would be best described as being mainly groomative as the changes affected the overall design and not the implementation of the API.
+A subcategory of preventive was also chosen as this could be seen as a method for preventing future maintenance.
+
+The interview provided further insight into the reasoning behind this change.
+Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all reasons for changing the interfaces of the API.
+Internal and external discussions about the use of the API also lead to the change in architecture of the API.
+For example, the interviewee mentioned how internal struggles with using the API highlighted the issue that the APIs were not simple to use and that they needed to be revised.
+
+Taking this information into account, we concluded that our categorisation was incorrect.
+The primary change seemed to be preventive given the strong emphasis on ease of use and could be seen as a way of avoiding future maintenance.
+We further concluded that the subcategory should be groomative to still reflect the intent to make the API more maintainable overall.
+
+\subsubsection{Error Handling}
+
+%%Describe the change 
+One interesting addition to version 2.0 of the API was many specific error header files, containing enums of error codes.
+While we were not aware of what error handling was utilised prior to this version, we assumed it had changed given the inclusion of these new files.
+For example, one might assume that they have perhaps switched to using C++ exceptions.
+
+We therefore decided to categorise this change primarily as preventive.
+This was on the basis that error handling is preventive in nature.
+Groomative was decided as an appropriate subcategory of change as the changing, or introduction of error handling could be seen as a means to make code more maintainable.
+
+Following the discussions in the interview, it became clear that the error handling was indeed changed but not for the reasons we assumed.
+A reason given was that the previous error handling implementations lacked information and usability.
+Glib, a common C library was also introduced to the new API.
+The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API.
+However, it was expressed to us that the error handling would have changed between versions regardless of whether or not Glib was included.
+
+We therefore concluded that our categorisation for this change was correct.
+Indeed, the primary reason for the change was to improve the existing error handling while improving the overall maintainability of the API as a whole.
+
+\subsubsection{3\textsuperscript{rd} Party}
+ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
+
+%%Describe the change 
+2.0 utilizes more 3rd party libraries
+axsound, for example, uses alsa
+All modules use glib
+
+The advent of the new API saw the inclusion of new 3\textsuperscript{rd} party libraries.
+For example, axsound utilises a library called Alsa, all interfaces use Glib and daemons have been provided for using D-Bus.
+These changes potentially make the library much more flexible both for the API designers in terms of features they can provide and for the application developers in terms of applications they can develop.
+
+We therefore gave this change the main categorisation of adaptive with no suitable sub-categories being found.
+
+The architects creating the API decided they wished to use Glib which came about primarily from internal discussions at the company.
+%%Relate it to Categories
+
+Architects decided to use glib, part of an internal decision.
+
+\subsection{RQ2 Results} \label{results_rq2}
+The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs.
+A summary of our findings can be seen in Table \ref{table:lehman}.
+
+\begin{table}
+       \centering
+       \begin{tabular}[Ht]{|l|c|}
+       \hline
+       \textbf{Law} & \textbf{Applicability} \\
+       \hline
+       Continuing Change & True \\
+       \hline
+       Increasing Complexity & Kinda \\
+       \hline
+       Self Regulation & True \\
+       \hline
+       Conservation of Organisational Stability & False \\
+       \hline
+       Conservation of Familiarity & True \\
+       \hline
+       Continuing Growth & True \\
+       \hline
+       Declining Quality & Kinda \\
+       \hline
+       Feedback System & True \\
+       \hline
+       \end{tabular}
+       \caption{The applicability of Lehman's laws}
+       \label{table:lehman}
+\end{table}
+
+\subsubsection{Continuing Change}
+The case company described that including new functional content was one of the top priorities for the 2.0 release.
+This is supported by the characteristic of the changes identified in this study.
+4 of the 13 changes were additions of new modules and in the re-implemented modules a lot of functional content was added, too.
+It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could have.
+One of the main reasons for continuously adapting the API is also to force (!!!wording) the API users to use the API in the way that it is intended.
+Previously, many applications which worked around the lacking (!!!negative wording) functionality had been developed.
+These applications were fully functional, but were developed very differently from user to user (!!!wording).
+We therefore conclude that the law of continuing change holds for APIs.
+
+\subsubsection{Increasing Complexity} \label{sec:law2}
+A large part of the changes made to the API were made to improve the structure and the way that the API is used.
+Many of these changes were related to the same design choices, which enforced a certain implementation style on the whole API.
+One example of this is the change to the interfaces which set a standard for the whole API.
+During the interview it was also concluded that consistency and following certain standards is an important factor to consider when designing APIs.
+It was also made clear a contributing factor for changing certain parts of the API was to bring it in line with the new interfaces.
+The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that the company currently did not make use of these.
+Even though the importance of maintaining the API to reduce complexity was stated, arguments which support that it is of lesser importance than releasing functional content was also presented.
+One example of where this is evident in the evolution of the API, is in the module that handles the video capturing and video stream.
+It was decided that this module would not be re-written to conform with the new interface standard, as there was not much functional content that would change in this module, anyway (!!!reword).
+Thus, the law of increasing complexity holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.
+
+\subsubsection{Self Regulation} \label{sec:law3}
+When version 1.4 was introduced, no new functionality or re-structuring was introduced.
+Version 1.4 only added support for additional build platforms.
+When comparing the changes introduced in 2.0 to the ones previously introduced, it is clear that the growth of the API has increased gradually.
+During the interview it was also mentioned that the future plans for the API did not include any major changes and that only a few minor changes were planned in the near future.
+The future updates to the API will also be made incrementally and there will not be a big bang update similar to the one of 2.0.
+This supports that the law of self regulation applies to APIs, assuming that the current stage of the life-cycle of the API can be considered as the centre of the normal distribution curve of the APIs growth.
+
+\subsubsection{Conservation of Organisational Stability}
+The changes to the ACAP API has been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
+As mentioned in Section \ref{sec:law3}, the changes introduced in version 1.4 did not involve any changes to the existing API functions.
+Consequently, the only significant update to the API was made in the transition to version 2.0.
+The internal development of the API has also been made sporadically and there have been periods where the API has not been actively developed.
+This suggests that the law of conservation of organisational stability does not apply to APIs.
+
+\subsubsection{Conservation of Familiarity}
+The SDK that is included with the API was rigorously updated with the introduction of version 2.0.
+All functionality which was added or modified in version 2.0 was updated accordingly in the SDK.
+The same pattern can be seen for the example code, which went through major changes as a result of the changes to the API code.
+The case company's intent to control the way that their API is used also suggests that the knowledge of how to use the API is of importance, since if the API is used in too many different ways, it will be more difficult for the case company to have relevant documentation and example code.
+It was also expressed during the interview that further transparency in how the API should be used could be achieved.
+One example of this is to improve the information to the user regarding which API functions are supported on which hardware types.
+These facts support that the law of conservation of familiarity is true for APIs.
+
+\subsubsection{Continuing Growth}
+Large parts of the changes between the versions were strictly additions of new functional content.
+4 new modules were added and significant additions of new functionality were added to the modules which were re-structured from version 1.4.
+The interviewee also made it clear that increasing the functionality was one of the major goals with the 2.0 update.
+This also ties in with the ambition of controlling the way the API users use the API, as mentioned previously.
+It was also mentioned that the case company had received feedback from the API users that more frequent updates to the functional content was desirable, even though this may require them to update their application code.
+Because of this, we conclude that the law of continuing growth applies to APIs.
+
+\subsubsection{Declining Quality}
+The interviews established that a groomative motive was not the most major reason for implementing any change.
+The changes to the example code and the SDK, as well as the re-structured modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content.
+These changes did, however, increase the quality and was a substantial part of the changes, which could have been left out.
+A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{sec:law2}.
+We therefore settle that the law of declining quality can be applied to APIs, but that there is data that implies that reducing quality is not of high importance.
+
+\subsubsection{Feedback System}
+One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
+Currently, only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users in this loop.
+The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users and which leads to good applications being developed.
+One example of how the API users have been included in the feedback loop, was prior to version 2.0 being released, when API users implemented functionality related to sound, even though there was no interface for this in the API.
+The experiences of this API user, were later considered when developing the axsound module.
+One benefit of having a more structured feedback loop, would be that the API developers would be more and faster (!!!re-phrase) aware of potential errors in the implementation of the API.
+Another ambition which was mentioned, was to bring scientific theories and best practices from academia into consideration when developing the API.
+This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects.
+Because of these factors and clearly expressed ambitions, we conclude that the law of feedback system is true for APIs.
+
+\section{Discussion}
+Our results have been provided valuable insight to the motives behind the evolution of an API.
+The results show that APIs definitely can be studied from the point of view of old evolution theories.
+Based on the result, we have formulated the subsequent outcomes.
+
+\subsection{Discussion RQ1}
+
+\noindent
+\textbf{Adding functionality is a prime driver of API evolution  }
+Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
+We found strong evidence to suggest that most, if not all of the additions, re-implementations and functional changes were undertaken to include additional functionality requested both internally and by the API users.
+This focus upon functionality was also emphasised in part due to a business goal.
+The more features the API can provide, the more applications developers can create for the cameras.
+This has a knock-on effect of increasing the appeal and therefore value of the products.
+
+%API users should be included in the design process?
+\smallskip \noindent
+\textbf{Maintainability does not drive change  } 
+While maintainability is important, it is not a primary driving factor for change.
+We found that where maintainability changed, functionality was also altered.
+For example, we predicted that the main intents to be enhancive which was correct.
+Furthermore, of the changes identified, none were considered to be primarily groomative, groomative changes were only identified as sub-category changes.
+Changes to the example code is further evidence of this.
+The example code was updated purely to reflect the changes in functionality and not as a groomative effort.
+
+\smallskip \noindent
+\textbf{Aiding development of applications  } 
+Aiding users of the API to create correct and robust applications is a very important evolution factor for Axis.
+Changes between the versions brought about improvements to error handling, the example code and the way in which the API utilises interfaces.
+This, coupled with removal of unwanted functionality and unsafe operations, has allowed the API to grow and become much more user friendly.
+As mentioned previously, this could increase the amount of applications being created for the camera and thus could increase its value.
+
+\smallskip \noindent
+\textbf{Removing functionality  }
+Previous literature has stated that deprecations should be favoured over removals from API for many reasons except in specific circumstances.
+The successful removal of the burst function seems to indicate that this advice is well worth following.
+Indeed, axis only removed this function from the API after an internal review found that the cost of removing it would outweigh potential drawbacks to keeping it in the API.
+It is therefore recommended to only remove something if the effects of removing it have been well investigated and that the removal is rather small in scale.
+
+\smallskip \noindent
+\textbf{Updative changes do not drive change  }
+Changes to documentation and example code are important, especially if the API is drastically changing between versions.
+However, these updative changes are drivers themselves, rather, they make up part of a larger change as a whole.
+%^Probably needs more to it?
+
+\smallskip \noindent
+\textbf{Hardware was not a driving factor  }
+Interestingly, we found that hardware was not a direct driver of change.
+Initially we had thought that it would be one of the strongest drivers of change, for example, new versions of hardware become available or new hardware is added to the camera requiring something in the API to access it.
+This does seem to suggest that the hardware for the camera is sufficiently stable such that it does not require changes and that those changes do not need to be reflected in new API versions.
+
+\subsection{Discussion RQ1.1}
+
+\noindent
+\textbf{Functionality is reverse engineerable  } 
+All changes which main motivation were to either add or remove functionality were accurately predicted.
+These changes were the most major ones, and it was expressed during the interview that these changes were the main motive behind the introduction of the new version.
+In summary, 11 out of a total 13 changes were correctly predicted.
+It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted.
+This supports that such changes have a clearer intent and are perhaps more well-defined.
+
+\smallskip \noindent
+\textbf{``Structural'' changes are not reverse engineerable  }
+3 out of 5 changes which did not add functionality, but rather were introduced to redcue complexity and increase quality were correctly predicted.
+The two changes which were not predicted correctly were wrong because the main-motivation was mixed up with the sub-intention (!!!re-phrase).
+This shows that although the prediction was incorrect, the general reasoning was correct.
+Our predictions were accurate enough to allow us to form a reliable conlusion which created a good means for discussion with the company (!!!re-phrase).
+
+\subsection{Discussion RQ2}
+
+\noindent
+\textbf{A majority of the laws apply  }
+Sufficient evidence was found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System to establish that they apply to APIs.
+The most major explanation for this that a large part of the introduced changes were related to functionality.
+It is especially interesting to note that the laws of Self Regulation and Conservation of Familiarity perfectly match the API explored in this paper.
+
+\smallskip \noindent
+\textbf{Two laws kinda apply  }
+The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that the extent to which they apply might not be as significant for APIs compared to other types of systems.
+The reason that this doubt exists is that these motivations could were only secondary to the motivations of increased functionality.
+An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} might overshadow (!!!wording) the need to increase simplicity and quality.
+
+\smallskip \noindent
+\textbf{One law does not apply  }
+Strong evidence was found which suggests that the law of Conservation of Organisational Stability does not apply to APIs.
+Our results not only show that the law is not true for APIs, but that the opposite of what the law states is true for APIs.
+This is supported by the consensus in literature of the negative effects caused by modifications to APIs \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
+The results from our study also showed that the reluctancy to change APIs causes the releases of new versions to be few and sporadic.
+
+\smallskip \noindent
+\textbf{The importance of a Feedback System  }
+Especially interesting results were found in regards to the law of Feedback System.
+The importance of having a structured and developed feedback loop was stressed during the interview, and it was also expressed as one of the main points of improvement.
+This suggests that including feedback from more sources and making use of this feedback should be done more when developing an API.
+
+\section{Conclusion} \label{conclusion}
+ATTN: This section has not been started.
+
+Summarise the findings of the discussion
+Summarise what the next steps could be.
+
+Look up the papers from the conference (especially regarding the discussion/conclusion)
+discussion = revisiting research questions (and maybe structuring around industry/academia)
+conclusion = summary part, main final points and future work
+
+Stuff for the conclusion:
+Have a more structured feedback loop (include users) this can be future work too
+Include more scientific theories
+
+For future studies, this technique could be improved by performing more actions along side the code review.
+For example, having access to and analysing commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be collected and analysed.
+%%Conclusion stuff /Willy
+
+%%The following should probably be in conclusion, right? /Willy
+       What this means for industry:
+              Greater emphasis should be placed upon communicating with the end users / application developers.
+APIs should be made with maintainability and extendibility in mind as they seem to be what changes the most between versions.
+They should probably improve their feedback system to get more feedback from the API users.
+
+              Obvious benefit for Axis is that the more features == more applications == higher value for their camera.
+If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase.
+This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
+
+       What this means for academia:
+              Academia could benefit from the results as a means for further research - We have found that it's possible to reverse engineer these design decisions from a simple study, so perhaps more advanced studies should be conduct at a larger scale?
+-- Why though?
+
+%%John add conclusion ideas here
+We were correct with the majority of our categorisations.
+The ones we did get wrong were because we did not think of it from specific points of view.
+This probably means that it's possible to reverse engineer to some extent, but not completely (Which is probably the answer most people would expect).
+
+Considering the Ecosystem and considering it as a whole when designing the API.
+She does not think that they did take it into consideration at all.
+They had not thought about them when designing the APIs.
+She does think about who is going to use it and how but nothing in regards to how it affects an ecosystem as a whole.
+Things like allowing embedded webpages for the ACAP allows users to get more information from their system meaning they don’t need to ask for as much help and assistance.
+They usually integrate this with the VMS.
+Overall there was not much thought about ecosystem when the API was designed.
+She’s unsure if it’s one ecosystem or two.
+The network APIs and their API.
+Perhaps it is one ecosystem.
+(this is something Imed is looking at).
+It seems that a focus on ecosystems might be starting to come through but that they already thought about them without calling them ecosystems.
+For example, her mentioning that they already did think about the users of the API and how they would be using it gives a slight clue that they do already think about the wider audience of their API.
+
+%See if our numbers match up with previous studies who said roughly 70\% of changes to an API were refactorings.
+That number is a little high in our case, but it's close!
+<---- This could be done in conclusion when we discuss how it contribues to academia (i.e.
+say it enforces previous studies blabla)
+
+%%William add conclusion ideas here
+It's interesting that the partners have mentioned that they want more frequent updates... maybe API developers should be less afraid of updating them? 
+That the part about controlling how the API users use the API was such an important thing is interesting. (Not something we expected). 
+-Relate to 80% refactorings paper and say that we found different results
+*This is an intersting note if we want to compare platform apis and library apis to say that functionality changes more often in platform apis for example
+
+%Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!
+
+\section{Acknowledgments}
+We would like to thank Axis and that project at GU.
+
+\bibliographystyle{abbrv}
+\bibliography{bib}
+
+\end{document}
+=======
+
 \documentclass{sig-alternate}
@@
 \end{document}
+>>>>>>> d390a4497e7e76430c2b9cdf1432c4a1597dcfd1

### 2015-05-05 thesis/paper.tex
cool_table
improved cat table a bit... still bad
review ptz

--- 2015-05-04 thesis/paper.tex
@@
 
+%Used to create Macro 1
+\usepackage{array}
+
+%Used for \textsubscript
+\usepackage{fixltx2e}
+
 \begin{document}
+
+%Macro 1, used to create thick vertical line in Table 1: Category 
+\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
+\makeatother
 
@@
 \textbf{Method  }
-This case study was conducted by investigating the changes between two versions in a platform API and its documentation, and by interview the architects of the API.
+This case study was conducted by investigating the changes between two versions in a platform API and its documentation, and by interviewing the architects of the API.
 The changes were analysed from a qualitative and investigative point of view.
@@
 There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
-The main reason is that it will require the users to update the code, which is using the API, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
+The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
 The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}.
@@
 
-%% Check what willy wrote.
-%%Explain structure of this section around the RQ and a summary of it. Table with the percentages from both us and her.
-In order to answer \textbf{RQ1}, we categorised the changes based on the 12 maintenance categories \cite{chapin2001types}.
-Initially, we created predictions of the changes from inspecting the source code and accompanying documentation.
-Following the interview, we compared our predictions with the actual motive which was deduced from the interviewee's reasoning.
-Table \ref{table:Categories} shows the predicted and actual maintenance categories.
+%This paragraph should be moved to Methodology
+In order to answer \textbf{RQ1}, we categorised the changes based on the 12 maintenance categories \cite{chapin2001types}, by inspecting the source code and the accompanying documentation.
+Following the interview, we compared our categorisations to the actual motive which was gathered from the interview.
 
+%Add a small introductory sentence to this paragraph and have it as the first paragraph of this section (Don't forget to ref the table)
 The changes have been divided up into four specific categories, namely: new, modified, removed and general trends.
-New and modified changes concern additions of or modifications to modules and removed changes is functionality which have been removed entirely without being deprecating or replaced by new implementations.
-General trends are broad changes which do not directly affect functionality.
+The category new concerns additions of modules, modified concerns modifications to modules that existed in version 1.4 and removed are changes where functionality was removed being deprecated or replaced by functionality.
+General trends are broad changes that do not directly affect functionality.
 
@@
        \centering
-       \begin{tabular}[Ht]{|l|c|c|}
+       \begin{tabular}[Ht]{|c"c|c|c|c|}
        \hline
-       \textbf{Category} & \textbf{Prediction} & \textbf{Actual} \\
+       Mode &  \multicolumn{2}{c}{Main} & \multicolumn{2}{c}{Sub} \\
+
        \hline
-       Updative & 15.4\% & 7.7\% \\
+       \textbf{Change} & \textbf{Prediction} & \textbf{Actual} & \textbf{Prediction} & \textbf{Actual} \\
        \hline    
-       Groomative & 7.7\% & 0.0\% \\
+       Example Code & U &      R\textsubscript{ef} &   R\textsubscript{ef} &   U \\
        \hline
-       Preventive & 7.7\% & 15.4\% \\
+       Documentation & U &      U &      Ref &   Ref \\
        \hline
-       Enhancive & 53.8\% & 53.8\% \\
+       Interfaces & G &    P &    P &    G \\
        \hline
-       Reductive & 7.7\% & 7.7\% \\
+       Error Handling & P &    P &    G &    G \\
        \hline
-       Adaptive & 15.4\% & 7.7\% \\
+       3rd Party & A &      A &      N/A &           N/A \\
        \hline
+       axaudio & E &     E &     N/A &           N/A \\
+       \hline
+       axptz & E &     E &     N/A &           N/A \\
+       \hline
+       axstorage & E &     E &     N/A &           N/A \\
+       \hline
+       axserialport & E &     E &     N/A &           N/A \\
+       \hline
+       axevent & E &     E &     G &    G \\
+       \hline
+       axhttp & E &     E &     G &    G \\
+       \hline
+       ax\_parameter & E &     E &     G &    G \\
+       \hline
+       Burst Mode & R\textsubscript{ed} &     R\textsubscript{ed} &     N/A &           N/A \\
+       \hline
+
        \end{tabular}
-       \caption{Category Distribution}
+       \caption{Category }
        \label{table:Categories}
@@
 \subsubsection{axptz}
+%Add info about this is one of the added changes
+The Pan, Tilt and Zoom (ptz) module concerns functionality related to manoeuvring the camera, both mechanically and digitally.
 
-This change introduced the ability to perform Pan, Tilt and Zoom (ptz) manoeuvres both mechanically and digitally on the camera.
-For example, zooming in on a particular section of a large image, panning the camera to the left to view a certain area.
-
-We concluded that this change was enhancive as it is a brand-new feature of the API. No sub-categories were found to be suitable.
+We concluded that this change was enhancive as it is a brand-new feature of the API. There was no secondary motive behind this change, as the change was purely enhancive.
 
 %%Explain what she said
-The interviewee described how this change and the 3 following changes were all included in the new API at the request of both API users and product management.
-The feature was sought after by API users frequently, while they were able to control the camera, there was no official application for doing so and as such, it was a good candidate for inclusion in the new API.
+The interviewee described how this change and the other changes classified as additions were all included in the new API at the request of API users.
+Prior to the change being introduced, there was no API functionality for controlling the camera and as such, it was a high priority addition to the new API.
 
 %%Explain how this relates to the category
-Based on the interviewees comments, we concluded that we had correctly identified the change as being enhancive.
-Furthermore, we were also correct in our assumption that there were no suitable sub-categories as there was no additional insight into other motivations for the inclusion of this feature.
+Based on the interviewees' comments, we concluded that we had correctly identified the change as being enhancive.
+Furthermore, we were also correct in our prediction that there was no secondary category.
 

### 2015-05-05 thesis/paper.tex
Review serialport

@@
 
+%%Relate it to Categories
 We concluded that this change was enhancive as it is a brand-new feature of the API. There was no secondary motive behind this change, as the change was purely enhancive.
 
-%%Explain what she said
+%%What she said
 The interviewee described how this change and the other changes classified as additions were all included in the new API at the request of API users.
@@
 
-%%Explain how this relates to the category
+%%Category based on her information
 Based on the interviewees' comments, we concluded that we had correctly identified the change as being enhancive.
@@
 %%Describe the change 
-By and large the most common usage of the camera is to analyse video data, however some of the API users require audio data.
-The inclusion of axaudio allows these users to perform audio analysis upon audio streams captured by Axis devices.
+The most important functionality of the camera is to capture and analyse video data, however, some the API users require the possibility to perform analysis upon audio data.
+The addition of axaudio allows API users to perform audio analysis upon audio streams captured by cameras.
 
 %%Relate it to Categories
-This change was also determined to be enhancive as it was an inclusion of a brand-new feature to the API.
-Similarly to the axptz, there were no suitable sub-categories that could be found to apply to this change.
+This change was determined to be enhancive, as it was an addition of a new feature to the API. We found no secondary motive of the change.
 
@@
 Audio analysis had not previously been possible on Axis devices.
-However, the interviewer informed us that an API user had managed to create their own audio analysis using the current (1.4) API.
-Given the demand for audio analysis, it was a logical choice to include it as a new feature in the new version of the API.
+During the interview, it was revealed that an API user had managed to implement their own audio analysis using version 1.4 of the API.
+Given the demand for audio analysis, it was included in version 2.0 of the API.
 
 %%Category based on her information
-Based on the information available, we concluded that we had successfully determined that the change was enhancive.
-Once more, there was no supporting evidence to suggest any suitable sub-categories for this change.
+Based on the the interviewee's reasoning, we concluded that we had successfully determined that the change was enhancive. The addition of axaudio had no secondary motive.
 
@@
 %%Describe the change 
-Prior to the newest version of the API, storage for the devices existed solely on the cameras or the Video Management System (VMS) itself.
-The release of version 2.0 saw the inclusion of alternative storage solutions.
-axstorage now allows Axis devices to interface with external storage devices, such as
+Prior to the newest version of the API being released, the sole alternative for storage was to use the Video Management System.
+Version 2.0 included the possibility of alternative storage solutions, by allowing to the camera to interface with external storage devices, such as SD cards.
 
-Enhancive was once again chosen to be the most applicable category of change given that axstorage was a brand-new inclusion in the newest version of the API.
-Similarly, there were no appropriate sub-categories for this change.
+%Relate it to categories
+Enhancive was chosen to be the most applicable category of change, given that axstorage was a new addition in version 2.0. No secondary motive was identifed.
 
-%%Her information
-The limited storage options for the Axis devices meant that this feature was strongly requested by API users and as such was included in this new version of the API.
+%%What she said
+The limited storage options for the cameras was the reason that increased functionality was strongly requested by API users and as such axstorage was included in version 2.0 of the API.
 
-%%Relate it to Categories
-The information gathered from the interview supported that were correct in our choice of enhancive for this change. Once more there was no inclusion of an appropriate subcategory.
+%%Category based on her information
+The information gathered from the interview supported that we were correct in our categorisation of this change. No secondary category was established.
 

### 2015-05-05 thesis/paper.tex
Review serialport

@@
 %%Describe the change 
-The final new feature of the API was the inclusion of axserialport.
-This part of the API allows API users to connect various devices to their cameras through the use of a serial port.
-This effectively allows users to integrate multiple kinds of devices to create their own unique solutions.
-In the previous version of the API there was no ability to connect to devices outside of the VMS.
+The addition of axserialport allows API users to connect various devices to their cameras by through the serial port.
+This allows users to integrate multiple devices to create their own unique solutions.
+In version 1.4 of the API, there was no possibility to connect external devices to the camera.
 
 %%Relate it to Categories
-The inclusion of this new feature was once again determined to be an enhancive change as it involved the addition of a brand new feature. No relevant sub-categories were found.
+The addition of this module was determined to be an enhancive change, as it involved the addition of a new feature. No relevant secondary category were identified.
 
-Our interviewee described scenarios whereby a camera could be used with external devices to create, for example, a ticketing system which reacts to users interacting with it in close proximity.
-This was just one scenario in which users might wish to use the camera with other devices.
-As such it was included in the new API to meet the demand of the API users.
+%%What she said
+The addition of axserialport was requested by API users.
+A possible use case, which was given during the interiew involved a ticketing system which allows for joint analysis of data from both devices.
+As such it was included in version 2.0, to meet the demand of the API users.
 
 %%Real category
-Given this information, we concluded that we were correct in deciding that this change was also enhancive.
-Again, we were also correct in the assumption that there were no suitable sub-categories for this change.
+Given this information, we concluded that we were correct in predicting that this change was enhancive. The prediction of the secondary category was also correct.
 

### 2015-05-05 thesis/paper.tex
Review axevent

@@
 \subsubsection{axptz}
-%Add info about this is one of the added changes
+%Add info about this is one of the added changes XXX (do that for all)
 The Pan, Tilt and Zoom (ptz) module concerns functionality related to manoeuvring the camera, both mechanically and digitally.
@@
 
-%%Real category
+%%Category based on her information
 Given this information, we concluded that we were correct in predicting that this change was enhancive. The prediction of the secondary category was also correct.
@@
 %%Describe the change 
-Version 2.0 of the API has been designed around an event driven system, as such, it's not surprising that the old event system had to be re-implemented.
-The new event system is used by all features of the new API, for example events are sent when movement is detected by the camera.
-This event system is combined with the use of callbacks to create a robust event driven API.
+Version 2.0 of the API was designed to be event-driven system which makes use of callbacks.
+To achieve this, the old event system had to be re-designed.
+The new event system is used by all features of version 2.0.
+An example of when an event is generated is when movement is detected by the camera.
 
 %%Relate it to Categories
-Given that this feature was a re-implementation, we concluded that it should be classified mainly as an enhancive change with the subcategory of change being classified as groomative.
-Groomative was chosen as a subcategory due to the alternate intention of bringing the new feature in line with the new interface.
+Given that this module was a re-implementation previous event system, we concluded that it should be classified mainly as an enhancive change with the secondary category being classified as groomative.
+Groomative was chosen as the secondary category due to the additional motive of bringing the new feature in line with the new interface.
 
-The interviewee mentioned that the previous version of axevent, event, was being deprecated in favour of this new implementation.
-The primary reason was to bring the implementation into line with the new way that the API handles events and interfaces as a whole.
-The interviewee mentioned that they realised that the API was hard to use previously and that improving it this way, through the use of re-implementations, could allow them to create an easier to use API.
+%%What she said 
+%%Re-write this... the main reason was functioanlity and not usability stuff XXX
+The interviewee outlined that the previous version of axevent, event, was deprecated in favour.
+The primary reason for this was to bring the implementation into line with the new design of the event system and interfaces.
+The interviewee expressed that they were unsatisfied with certain usability aspects of the API.
 
+%%Category based on her information
 Groomative is therefore the obvious choice for the main category for this change with enhancive being the subcategory.

### 2015-05-05 thesis/paper.tex
review error handling

@@
 
+%%Relate it to Categories
 %%What she said
@@
 
+%%Relate it to Categories
 We therefore concluded that this change would be best described as being mainly groomative as the changes affected the overall design and not the implementation of the API.
@@
 
+%%What she said
 The interview provided further insight into the reasoning behind this change.
@@
 
+%%Category based on her information
 Taking this information into account, we concluded that our categorisation was incorrect.
-The primary change seemed to be preventive given the strong emphasis on ease of use and could be seen as a way of avoiding future maintenance.
+The primary change seemed to be preventive given the strong emphasis on ease of use and could be regarded as a way of avoiding future maintenance.
 We further concluded that the subcategory should be groomative to still reflect the intent to make the API more maintainable overall.
@@
 %%Describe the change 
-One interesting addition to version 2.0 of the API was many specific error header files, containing enums of error codes.
+A substantial change included in version 2.0 was the addition of specific error header files, containing enums of error codes.
 While we were not aware of what error handling was utilised prior to this version, we assumed it had changed given the inclusion of these new files.
 For example, one might assume that they have perhaps switched to using C++ exceptions.
+(!!!This is way too assume-y)
 
-We therefore decided to categorise this change primarily as preventive.
-This was on the basis that error handling is preventive in nature.
-Groomative was decided as an appropriate subcategory of change as the changing, or introduction of error handling could be seen as a means to make code more maintainable.
+%%Relate it to Categories
+Based on this, we categorise this change as being primarily preventive.
+The reasoning for this was that error handling is preventive in nature.
+Groomative was decided as the secondary category of maintenance as improvement of error handling could be regarded as a means to make the code more maintainable.
 
+%%What she said
 Following the discussions in the interview, it became clear that the error handling was indeed changed but not for the reasons we assumed.
@@
 
+%%Category based on her information
 We therefore concluded that our categorisation for this change was correct.

### 2015-05-05 thesis/paper.tex
Updated the incorrect endings to the three re-implementations

@@
 %Relate it to categories
-Enhancive was chosen to be the most applicable category of change, given that axstorage was a new addition in version 2.0. No secondary motive was identifed.
+Enhancive was chosen to be the most applicable category of change, given that axstorage was a new addition in version 2.0. No secondary motive was identified.
 
@@
 The addition of axserialport was requested by API users.
-A possible use case, which was given during the interiew involved a ticketing system which allows for joint analysis of data from both devices.
+A possible use case, which was given during the interview involved a ticketing system which allows for joint analysis of data from both devices.
 As such it was included in version 2.0, to meet the demand of the API users.
@@
 
+The interviewee outline that the previous version of axevent, event, was deprecated in favour of a redesigned event system.
+This redesign was also a good opportunity to implement the new interface design.
+
 %%Category based on her information
@@
 This is the reverse of what we concluded and as such means that we incorrectly determined the intent for this change.
+
+From the discussion in the interview, it clear that both of our categorisations were correct; this change was primarily enhancive and secondarily groomative.
 
@@
 
-The interviewee again described how the main intent to changing this part of the API came about most to bring it into line with the new event driven and callback focused architecture.
-Similarly to the previous change, this feature was redesigned and re-implemented with added functionality.
+The main driving force for this change was the re-implementation and addition of functionality to the axhttp module. Redesigning the module to take advantage of the design was an added bonus.
 
-Our conclusion of enhancive and groomative was also backwards for this change.
-As per the previous change, the primary intent was to bring these parts of the API into line with the new standard; improving functionality was an added bonus.
+Our categorisation of enhancive and groomative was therefore correct for this change. The primary intent was to add functionality while also allowing the re-implementation accommodate the new design.
 
@@
 
-The interviewee once again clarified how this change was indeed primarily concerned with meeting the new standards of version 2.0.
-They agreed that little had actually changed in terms of what functionality the API offered and gave the same reasoning suggested for the two prior changes.
+The interviewee clarified that this change was mainly concerned with implementing new functionality and re-implementing old functionality while simultaneously adopting the new standards of version 2.0.
 
-Once again our conclusion was incorrect for the categorisation of this change.
-Given the information from the interview, we deemed that this change was also primarily groomative with a subcategory of enhancive.
+Given the information from the interview, we concluded that this change was correctly categorised; the primary intent was enhancive and the secondary intent was groomative.
 

### 2015-05-05 thesis/paper.tex
review error handl

@@
 %%What she said
-Following the discussions in the interview, it became clear that the error handling was indeed changed but not for the reasons we assumed.
-A reason given was that the previous error handling implementations lacked information and usability.
+During the interview, it was made clear that the previous error handling implementations lacked information and usability.
 Glib, a common C library was also introduced to the new API.

### 2015-05-05 thesis/paper.tex
blabla
Re-updated event

@@
 
-%%Relate it to Categories
 %%What she said
@@
 %%What she said 
-%%Re-write this... the main reason was functioanlity and not usability stuff XXX
-The interviewee outlined that the previous version of axevent, event, was deprecated in favour.
-The primary reason for this was to bring the implementation into line with the new design of the event system and interfaces.
+The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implemention of the new event system.
 The interviewee expressed that they were unsatisfied with certain usability aspects of the API.
-
-The interviewee outline that the previous version of axevent, event, was deprecated in favour of a redesigned event system.
-This redesign was also a good opportunity to implement the new interface design.
+event was then completely re-implemented and as a secondary concern, adopted the new system design being used in version 2.0
 
 %%Category based on her information
-Groomative is therefore the obvious choice for the main category for this change with enhancive being the subcategory.
-This is the reverse of what we concluded and as such means that we incorrectly determined the intent for this change.
-
 From the discussion in the interview, it clear that both of our categorisations were correct; this change was primarily enhancive and secondarily groomative.
@@
 
+%%Relate it to Categories
 This change is very similar to the previously mentioned change and as such is classified in the same way; a main categorisation of enhancive with groomative as the subcategory of change.
 
+%%What she said 
 The main driving force for this change was the re-implementation and addition of functionality to the axhttp module. Redesigning the module to take advantage of the design was an added bonus.
 
+%%Category based on her information
 Our categorisation of enhancive and groomative was therefore correct for this change. The primary intent was to add functionality while also allowing the re-implementation accommodate the new design.

### 2015-05-05 thesis/paper.tex
Cleaned up table

@@
        \hline
-       Mode &  \multicolumn{2}{c}{Main} & \multicolumn{2}{c}{Sub} \\
 
-       \hline
-       \textbf{Change} & \textbf{Prediction} & \textbf{Actual} & \textbf{Prediction} & \textbf{Actual} \\
-       \hline    
-       Example Code & U &      R\textsubscript{ef} &   R\textsubscript{ef} &   U \\
-       \hline
-       Documentation & U &      U &      Ref &   Ref \\
-       \hline
-       Interfaces & G &    P &    P &    G \\
-       \hline
-       Error Handling & P &    P &    G &    G \\
-       \hline
-       3rd Party & A &      A &      N/A &           N/A \\
-       \hline
-       axaudio & E &     E &     N/A &           N/A \\
-       \hline
-       axptz & E &     E &     N/A &           N/A \\
-       \hline
-       axstorage & E &     E &     N/A &           N/A \\
-       \hline
-       axserialport & E &     E &     N/A &           N/A \\
-       \hline
-       axevent & E &     E &     G &    G \\
-       \hline
-       axhttp & E &     E &     G &    G \\
-       \hline
-       ax\_parameter & E &     E &     G &    G \\
-       \hline
-       Burst Mode & R\textsubscript{ed} &     R\textsubscript{ed} &     N/A &           N/A \\
-       \hline
+       Mode                        & \multicolumn{2}{c}{Main}                              & \multicolumn{2}{c}{Sub}                 \\ \hline
+
+       \textbf{Change}      & \textbf{Prediction}       & \textbf{Actual}           & \textbf{Prediction}       & \textbf{Actual}    \\ \hline    
+       Example Code         & U                         & R\textsubscript{ef}       & R\textsubscript{ef}       & U                  \\ \hline
+       Documentation        & U                         & U                         & Ref                       & Ref                \\ \hline
+       Interfaces           & G                         & P                         & P                         & G                  \\ \hline
+       Error Handling       & P                         & P                         & G                         & G                  \\ \hline
+       3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
+       axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
+       axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
+       axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
+       axserialport         & E                         & E                         & N/A                       & N/A                \\ \hline
+       axevent              & E                         & E                         & G                         & G                  \\ \hline
+       axhttp               & E                         & E                         & G                         & G                  \\ \hline
+       ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
+       Burst Mode           & R\textsubscript{ed}       & R\textsubscript{ed} &     N/A                         & N/A                \\ \hline
 

### 2015-05-05 thesis/paper.tex
Table stuff

--- 2015-05-05 thesis/paper.tex
@@
 \usepackage{array}
+
+%
+\usepackage{multirow}
 
@@
        \centering
-       \begin{tabular}[Ht]{|c"c|c|c|c|}
+       \begin{tabular}[ht]{|c"c|c|c|c|}
        \hline
-       Mode &  \multicolumn{2}{c}{Main} & \multicolumn{2}{c}{Sub} \\
 
-       \hline
-       \textbf{Change} & \textbf{Prediction} & \textbf{Actual} & \textbf{Prediction} & \textbf{Actual} \\
-       \hline    
-       Example Code & U &      R\textsubscript{ef} &   R\textsubscript{ef} &   U \\
-       \hline
-       Documentation & U &      U &      Ref &   Ref \\
-       \hline
-       Interfaces & G &    P &    P &    G \\
-       \hline
-       Error Handling & P &    P &    G &    G \\
-       \hline
-       3rd Party & A &      A &      N/A &           N/A \\
-       \hline
-       axaudio & E &     E &     N/A &           N/A \\
-       \hline
-       axptz & E &     E &     N/A &           N/A \\
-       \hline
-       axstorage & E &     E &     N/A &           N/A \\
-       \hline
-       axserialport & E &     E &     N/A &           N/A \\
-       \hline
-       axevent & E &     E &     G &    G \\
-       \hline
-       axhttp & E &     E &     G &    G \\
-       \hline
-       ax\_parameter & E &     E &     G &    G \\
-       \hline
-       Burst Mode & R\textsubscript{ed} &     R\textsubscript{ed} &     N/A &           N/A \\
-       \hline
+       \multirow{2}{*}{\textbf{Change}}          & \multicolumn{2}{c}{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Sub}}        \\ \cline{2-5}
+
+                            & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \hline    
+       Example Code         & U                         & R\textsubscript{ef}       & R\textsubscript{ef}       & U                  \\ \hline
+       Documentation        & U                         & U                         & R\textsubscript{ef}       & R\textsubscript{ef} \\ \hline
+       Interfaces           & G                         & P                         & P                         & G                  \\ \hline
+       Error Handling       & P                         & P                         & G                         & G                  \\ \hline
+       3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
+       axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
+       axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
+       axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
+       axserialport         & E                         & E                         & N/A                       & N/A                \\ \hline
+       axevent              & E                         & E                         & G                         & G                  \\ \hline
+       axhttp               & E                         & E                         & G                         & G                  \\ \hline
+       ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
+       Burst Mode           & R\textsubscript{ed}       & R\textsubscript{ed} &     N/A                         & N/A                \\ \hline
 
@@
        \centering
-       \begin{tabular}[Ht]{|l|c|}
+       \begin{tabular}[ht]{|l|c|}
        \hline

### 2015-05-05 thesis/paper.tex
review axhttp

@@
 %%Describe the change 
-Version 2.0 of the API was designed to be event-driven system which makes use of callbacks.
+Version 2.0 of the API was designed to be an event-driven system which makes use of callbacks.
 To achieve this, the old event system had to be re-designed.
-The new event system is used by all features of version 2.0.
+The new design is used by all features of API version 2.0.
 An example of when an event is generated is when movement is detected by the camera.
@@
 %%Relate it to Categories
-Given that this module was a re-implementation previous event system, we concluded that it should be classified mainly as an enhancive change with the secondary category being classified as groomative.
-Groomative was chosen as the secondary category due to the additional motive of bringing the new feature in line with the new interface.
+Given that this module was a re-implementation of the previous event system, we concluded that it should be classified mainly as an enhancive change with the secondary category being classified as groomative.
+Groomative was chosen as the secondary category due to the additional motive of bringing the new functionality into line with the new design.
 
@@
 The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implemention of the new event system.
-The interviewee expressed that they were unsatisfied with certain usability aspects of the API.
-event was then completely re-implemented and as a secondary concern, adopted the new system design being used in version 2.0
+One reason being that the case company were dissatisfied with certain usability aspects of the API.
+The module was then completely re-implemented and according to the new system design of version 2.0.
 
 %%Category based on her information
-From the discussion in the interview, it clear that both of our categorisations were correct; this change was primarily enhancive and secondarily groomative.
+From the discussion in the interview, it was clear that both of our categorisations were correct. The change was primarily enhancive and secondarily groomative.
 
@@
 %%Describe the change 
-axhttp was re-implemented from the previous version of the API to follow the new interface and callbacks standards while also including the event driven architecture of 2.0.
-Functionality remained similar in that it allowed the conversion of data into html in order to display on web pages.
+The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynically load data to web pages.
+The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards.
+Additional functionality was also added to the module.
 

### 2015-05-05 thesis/paper.tex
asd

@@
 The API interfaces experienced the most change between the two versions.
-Three of the older interfaces were deprecated in favour of the new API architecture and the rest of the API is now comprised of brand new interfaces.
+(<-what do you mean by this?) Three of the older interfaces were deprecated in favour of the API architecture (<-what do you mean?) and the rest of the API is now comprised of new interfaces.
+
 The exception to this appears to be the image capture interface which only experienced a deprecation of a single feature.
@@
 %%Relate it to Categories
-Based on this, we categorise this change as being primarily preventive.
+Based on this, we categorised this change as being primarily preventive.
 The reasoning for this was that error handling is preventive in nature.
@@
 %%What she said
-During the interview, it was made clear that the previous error handling implementations lacked information and usability.
-Glib, a common C library was also introduced to the new API.
+During the interview, it was made clear that the previous error handling was not expressive and usable enough.
+Glib (!!!ref to website) was also introduced to the new API.
 The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API.
 However, it was expressed to us that the error handling would have changed between versions regardless of whether or not Glib was included.
+(!!!This is also too assume-y)
 

### 2015-05-05 thesis/paper.tex
Reviewed RQ2 results

@@
 
-\subsubsection{Continuing Change}
-The case company described that including new functional content was one of the top priorities for the 2.0 release.
+\subsubsection{Continuing Change} %Reviewed by W
+The case company described that including new functional content was one of the top priorities for the release of vesrion 2.0.
 This is supported by the characteristic of the changes identified in this study.
-4 of the 13 changes were additions of new modules and in the re-implemented modules a lot of functional content was added, too.
-It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could have.
+4 of the 13 changes were additions of new modules, and additional functionality was also added to re-implemented modules.
+It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could have (!!!mean, imply?).
 One of the main reasons for continuously adapting the API is also to force (!!!wording) the API users to use the API in the way that it is intended.
-Previously, many applications which worked around the lacking (!!!negative wording) functionality had been developed.
-These applications were fully functional, but were developed very differently from user to user (!!!wording).
+Prior to version 2.0 being released, a number of API users used workarounds to implement applications which contained functionality which was not yet offered from the API.
+These applications were fully functional, but were developed were incongruent.
 We therefore conclude that the law of continuing change holds for APIs.
 
-\subsubsection{Increasing Complexity} \label{sec:law2}
-A large part of the changes made to the API were made to improve the structure and the way that the API is used.
+\subsubsection{Increasing Complexity} \label{sec:law2} %Reviewed by W
+A majority of the changes introduced in version 2.0 aimed to improve the structure and the way that the API was used.
 Many of these changes were related to the same design choices, which enforced a certain implementation style on the whole API.
@@
 During the interview it was also concluded that consistency and following certain standards is an important factor to consider when designing APIs.
-It was also made clear a contributing factor for changing certain parts of the API was to bring it in line with the new interfaces.
+It was also made clear that a contributing factor for changing certain parts of the API was to bring it into line with the new interface structure.
 The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that the company currently did not make use of these.
-Even though the importance of maintaining the API to reduce complexity was stated, arguments which support that it is of lesser importance than releasing functional content was also presented.
+Even though the importance of maintaining the API in order to reduce complexity was stated, arguments which support that it is of lesser importance than releasing functional content was also presented.
 One example of where this is evident in the evolution of the API, is in the module that handles the video capturing and video stream.
-It was decided that this module would not be re-written to conform with the new interface standard, as there was not much functional content that would change in this module, anyway (!!!reword).
+It was decided that this module would not be re-designed to conform with the new interface standard, as the changes to functionality in this module were very minor.
 Thus, the law of increasing complexity holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.
 
-\subsubsection{Self Regulation} \label{sec:law3}
-When version 1.4 was introduced, no new functionality or re-structuring was introduced.
-Version 1.4 only added support for additional build platforms.
-When comparing the changes introduced in 2.0 to the ones previously introduced, it is clear that the growth of the API has increased gradually.
+\subsubsection{Self Regulation} \label{sec:law3} %Reviewed by W
+The release of version 1.4 did not include any changes related to the API interface.
+Version 1.4 strictly added support for additional build platforms (!!change this to more technical lingo).
+When comparing the changes introduced in version 2.0 to the ones in previous versions, it is clear that the growth of the API has gradually increased.
 During the interview it was also mentioned that the future plans for the API did not include any major changes and that only a few minor changes were planned in the near future.
-The future updates to the API will also be made incrementally and there will not be a big bang update similar to the one of 2.0.
+The future updates to the API will also be made incrementally and there will not be a big bang update similar to the one of version 2.0.
 This supports that the law of self regulation applies to APIs, assuming that the current stage of the life-cycle of the API can be considered as the centre of the normal distribution curve of the APIs growth.
 
-\subsubsection{Conservation of Organisational Stability}
-The changes to the ACAP API has been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
+\subsubsection{Conservation of Organisational Stability} %Reviewed by W
+The changes to the API have been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
 As mentioned in Section \ref{sec:law3}, the changes introduced in version 1.4 did not involve any changes to the existing API functions.
@@
 
-\subsubsection{Conservation of Familiarity}
-The SDK that is included with the API was rigorously updated with the introduction of version 2.0.
-All functionality which was added or modified in version 2.0 was updated accordingly in the SDK.
+\subsubsection{Conservation of Familiarity} %Reviewed by W
+The documentation that is included with the API was rigorously updated with the introduction of version 2.0.
+All functionality which was added or modified in version 2.0 was updated accordingly in the documentation.
 The same pattern can be seen for the example code, which went through major changes as a result of the changes to the API code.
@@
 
-\subsubsection{Continuing Growth}
-Large parts of the changes between the versions were strictly additions of new functional content.
+\subsubsection{Continuing Growth} %Reviewed by W
+Large parts of the changes between the versions were strict (!!!word) additions of new functional content.
 4 new modules were added and significant additions of new functionality were added to the modules which were re-structured from version 1.4.
-The interviewee also made it clear that increasing the functionality was one of the major goals with the 2.0 update.
+The interviewee also made it clear that increasing the functionality was one of the main goals with the 2.0 update.
 This also ties in with the ambition of controlling the way the API users use the API, as mentioned previously.
@@
 
-\subsubsection{Declining Quality}
-The interviews established that a groomative motive was not the most major reason for implementing any change.
-The changes to the example code and the SDK, as well as the re-structured modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content.
-These changes did, however, increase the quality and was a substantial part of the changes, which could have been left out.
+\subsubsection{Declining Quality} %Reviewed by W
+The interviews established that a groomative motive was not the primary reason for implementing any change.
+The changes to the example code and the documentation, as well as the re-structured modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content.
+These changes did, however, increase the quality and were a substantial part of the update.
 A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{sec:law2}.
@@
 
-\subsubsection{Feedback System}
+\subsubsection{Feedback System} %Reviewed by W
 One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
-Currently, only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users in this loop.
+Currently, only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users.
 The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users and which leads to good applications being developed.
@@
 The experiences of this API user, were later considered when developing the axsound module.
-One benefit of having a more structured feedback loop, would be that the API developers would be more and faster (!!!re-phrase) aware of potential errors in the implementation of the API.
+One benefit of having a more structured feedback loop, would be that the API developers would better aware of potential errors in the implementation of the API.
 Another ambition which was mentioned, was to bring scientific theories and best practices from academia into consideration when developing the API.

### 2015-05-05 thesis/paper.tex
Updated results for axevent and below

@@
 %%Describe the change 
-The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynically load data to web pages.
+The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically load data to web pages.
 The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards.
@@
 %%Relate it to Categories
-This change is very similar to the previously mentioned change and as such is classified in the same way; a main categorisation of enhancive with groomative as the subcategory of change.
+This change re-implemented an existing module while adhering to the new design of API version 2.0. The main categorisation was chosen to be enhancive with groomative as the secondary change.
 
 %%What she said 
-The main driving force for this change was the re-implementation and addition of functionality to the axhttp module. Redesigning the module to take advantage of the design was an added bonus.
+The interviewee expressed to us that the main driving force behind this change was to re-implement and add new functionality to the axhttp module.
+Redesigning the module to take advantage of the new design was an added bonus.
 
 %%Category based on her information
-Our categorisation of enhancive and groomative was therefore correct for this change. The primary intent was to add functionality while also allowing the re-implementation accommodate the new design.
+Our categorisation of enhancive and groomative was therefore correct for this change.
+The primary intent was to add functionality while also allowing the re-implementation accommodate the new API design.
 
@@
 %%Describe the change 
-The final re-implementation updated the parameter setting features of the API.
-This particular module had very few changes to it's functionality except for bringing into line, once again, with the new standard.
+The parameter setting module of the API allows data and application settings to be saved so that they are not lost when the device is not running.
+This module was re-implemented as ax\_parameter with added functionality and conformance to the new design standards of API version 2.0.
 
-This change was also deemed to be primarily enhancive with a subcategory of groomative.
-The reason being that this change was part of the broader re-implementation and while it did not purely add new functionality, it did change aid in changing the behaviour of this particular part of the API.
+Given that this change re-implemented an existing module while also incorporating the new design standards, it has been categorised as being primarily enhancive with a secondary category of groomative.
 
-The interviewee clarified that this change was mainly concerned with implementing new functionality and re-implementing old functionality while simultaneously adopting the new standards of version 2.0.
+The interviewee clarified that this change was mainly concerned with re-implementing existing functionality while simultaneously adopting the new standards of version 2.0.
 
@@
 
+%%Describe the change 
 The burst mode feature of the API allowed users to buffer a series of images for closer analysis. This feature was deprecated during the transition between 1.4 and 2.0 and was not re-implemented.
 
-This change presented itself as a clear example of a reductive category of maintenance as it was simply removed and not replaced anywhere else.
-We also concluded that this change had no suitable subcategory in which to classify the change.
+%%Relate it to Categories
+This change presented itself as a clear example of a reductive category of maintenance as it was simply removed and not replaced within the API.
+We also concluded that this change had no secondary category.
 
+%%What she said
 The interviewee did shed some light onto why this change occurred.
 We were informed that in order to continue using this feature in 2.0 and in newer versions of the camera hardware, it would have to be re-implemented from scratch.
-A cost analysis was performed on taking this action and it was deemed that the impact would be minimal resulting in it's removal from the API.
+An impact assessment was undertaken to determine if the removal of the function would cost significant time and money.
+Ultimately it was deemed appropriate and the function was removed from the API.
 
-Given this information we can safely say that we correctly concluded that this was a reductive maintenance task and that there are indeed no other sub-categories which are applicable to describe this change.
+%%Category based on her information
+Given this information we can safely say that we correctly categorised this as reductive that there are indeed no other secondary categories to describe this change.
 
@@
 %%Describe the change 
-As with many APIs, Axis included a selection of example programs to assist developers in creating applications by giving explicit examples of their usage.
-This trend continued in 2.0 but there were some significant improvements.
-The number of example programs increased, as did the amount of comments accompanying the code which lead to an overall more robust set of examples.
+As with many APIs, Axis included a selection of example programs to assist developers with creating applications.
+This trend continued in 2.0, but there were some significant improvements.
+The number of example programs increased, as did the amount of comments accompanying the code which has lead to an overall more robust set of examples.
 
-We therefore concluded that this change was updative as the example code was updated to the new API and the new techniques which it utilises.
-We further decided that this change also had a subcategory of reformative.
+%%Relate it to Categories
+We therefore concluded that this change was updative as the example code was updated to the new API and the new techniques that it utilises.
+We further decided that this change also had a secondary category of reformative.
 
+%%What she said
 From the interview it became clear that the improvement of the example code was an important change between the two versions.
-The interviewee described to us how the examples were used frequently by their customers, however, the old examples varied significantly between how different and even similar tasks were implemented.
-This ultimately meant that the old examples were not good enough and new ones needed to be created, preferably conforming to a single standard of implementation techniques.
-The new examples made sure to cover the new functionality, specific new features and they to show how they can be combined to create applications.
+The interviewee described to us how the examples were used frequently by their customers, however, the old examples varied significantly, even between similar tasks.
+This ultimately meant that the old examples were not good enough and new ones needed to be created, preferably conforming to a standard.
+The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.
 
+%%Category based on her information
 With this information we concluded that our categorisation was incorrect.
 It became clear that this change was in actual fact primarily reformative, given that the changes to the documentation were being performed to meet the needs of the API users.
-It was also clear that the subcategory should therefore be updative.
+It was also clear that the subcategory should therefore have been updative.
 
@@
 
-We categorised this change as being updative with a reformative subcategory for the reasons that the change only updated the documentation to reflect the recent changes in the API.
+%%Relate it to Categories
+We categorised this change as being updative with a reformative secondary category for the reasons that the change only updated the documentation to reflect the recent changes in version 2.0.
 
+%%What she said
 This sentiment was supported by the interview.
@@
 
-As there was no information to contradict our categorisations we have concluded we were correct in our assumptions.
+%%Category based on her information
+As there was no information to contradict our categorisations we have concluded we were correct in our predictions.
 
@@
 %%Describe the change 
-The API interfaces experienced the most change between the two versions.
-(<-what do you mean by this?) Three of the older interfaces were deprecated in favour of the API architecture (<-what do you mean?) and the rest of the API is now comprised of new interfaces.
-
-The exception to this appears to be the image capture interface which only experienced a deprecation of a single feature.
-Each new feature is either accessed directly or via an interface which acts as a facade.
+Version 1.4 of the API allowed direct access to the headers of each module available in the API.
+Version 2.0 changed this by including interfaces from which users can now access functionality.
+This design change has had an overall affect on the whole API as it has changed the structure of modules, but not their functionality.
 
 %%Relate it to Categories
-We therefore concluded that this change would be best described as being mainly groomative as the changes affected the overall design and not the implementation of the API.
-A subcategory of preventive was also chosen as this could be seen as a method for preventing future maintenance.
+We therefore concluded that this change would be best categorised as  groomative.
+The secondary category of preventive was also chosen as this change could be seen as an attempt to reduce future maintenance.
 
 %%What she said
-The interview provided further insight into the reasoning behind this change.
-Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all reasons for changing the interfaces of the API.
-Internal and external discussions about the use of the API also lead to the change in architecture of the API.
-For example, the interviewee mentioned how internal struggles with using the API highlighted the issue that the APIs were not simple to use and that they needed to be revised.
+The interview provided further insight into the reasoning behind this design change.
+Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to change the interfaces of the API.
+Furthermore, the redesign would hopefully avoid future maintenance while allowing the system to be easily extended.
 
@@
 Taking this information into account, we concluded that our categorisation was incorrect.
-The primary change seemed to be preventive given the strong emphasis on ease of use and could be regarded as a way of avoiding future maintenance.
-We further concluded that the subcategory should be groomative to still reflect the intent to make the API more maintainable overall.
+The primary change seemed to be preventive given the strong emphasis on avoiding future maintenance and improving ease of use.
+We further concluded that the secondary change should be groomative reflect the intent to make the API more maintainable overall.
 
@@
 While we were not aware of what error handling was utilised prior to this version, we assumed it had changed given the inclusion of these new files.
-For example, one might assume that they have perhaps switched to using C++ exceptions.
-(!!!This is way too assume-y)
 
 %%Relate it to Categories
-Based on this, we categorised this change as being primarily preventive.
-The reasoning for this was that error handling is preventive in nature.
-Groomative was decided as the secondary category of maintenance as improvement of error handling could be regarded as a means to make the code more maintainable.
+Based on this, we categorised this change as being primarily preventive as error handling is preventive by nature.
+Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability.
 
 %%What she said
-During the interview, it was made clear that the previous error handling was not expressive and usable enough.
-Glib (!!!ref to website) was also introduced to the new API.
-The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API.
-However, it was expressed to us that the error handling would have changed between versions regardless of whether or not Glib was included.
-(!!!This is also too assume-y)
+%% Glib - https://developer.gnome.org/glib/
+During the interview, it was made clear that the previous error handling was lacking in expressiveness and usability.
+Glib was added to version 2.0 and the error handling functionality that Glib provides, was incorporated into the new API design.
 
@@
 We therefore concluded that our categorisation for this change was correct.
-Indeed, the primary reason for the change was to improve the existing error handling while improving the overall maintainability of the API as a whole.
+Indeed, the primary reason for the change was to improve the existing error handling while conforming to the new API standard.
 
@@
 Architects decided to use glib, part of an internal decision. 
+Glib (!!!ref to website) was therefore introduced to the new API to help alleviate this
+
+The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API.
+However, it was expressed to us that the error handling would have changed between versions regardless of whether or not Glib was included.
+(!!!This is also too assume-y)
 

### 2015-05-05 thesis/paper.tex
saddsf

@@
 \subsection{API Design} \label{api_design}
-API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{stylos2006comparing} \cite{afonso2012evaluating} \cite{bloch2008effective}.
+API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}.
 Examples of such decisions are whether to use the factory pattern or constructors to create objects, or if the API should display errors during compilation or runtime \cite{stylos2006comparing}.
@@
        \begin{tabular}[ht]{|c"c|c|c|c|}
+
               \hline
@@
               \hline
-       \textbf{Law} & \textbf{Applicability} \\
-       \hline
-       Continuing Change & True \\
-       \hline
-       Increasing Complexity & Kinda \\
-       \hline
-       Self Regulation & True \\
-       \hline
-       Conservation of Organisational Stability & False \\
-       \hline
-       Conservation of Familiarity & True \\
-       \hline
-       Continuing Growth & True \\
-       \hline
-       Declining Quality & Kinda \\
-       \hline
-       Feedback System & True \\
-       \hline
+
+              \textbf{Law}                              & \textbf{Applicability}    \\ \hline
+              Continuing Change                         & True                      \\ \hline
+              Increasing Complexity                     & Kinda                     \\ \hline
+              Self Regulation                           & True                      \\ \hline
+              Conservation of Organisational Stability  & False                     \\ \hline
+              Conservation of Familiarity               & True                      \\ \hline
+              Continuing Growth                         & True                      \\ \hline
+              Declining Quality                         & Kinda                     \\ \hline
+              Feedback System                           & True                      \\ \hline
+
        \end{tabular}

### 2015-05-05 thesis/paper.tex
john review RQ2 results

@@
 The interviewee expressed to us that the main driving force behind this change was to re-implement and add new functionality to the axhttp module.
-Redesigning the module to take advantage of the new design was an added bonus.
+Re-designing the module to take advantage of the new design was an added bonus.
 
@@
 %%What she said
-The interviewee did shed some light onto why this change occurred.
+The interviewee did shed some light on why this change occurred.
 We were informed that in order to continue using this feature in 2.0 and in newer versions of the camera hardware, it would have to be re-implemented from scratch.
@@
 As with many APIs, Axis included a selection of example programs to assist developers with creating applications.
-This trend continued in 2.0, but there were some significant improvements.
+This trend continued in version 2.0, but there were some significant improvements.
 The number of example programs increased, as did the amount of comments accompanying the code which has lead to an overall more robust set of examples.
@@
 %%Relate it to Categories
-We therefore concluded that this change was updative as the example code was updated to the new API and the new techniques that it utilises.
+We therefore concluded that this change was updative, as the example code was updated to the new API and the new techniques that it utilises.
 We further decided that this change also had a secondary category of reformative.
@@
 Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to change the interfaces of the API.
-Furthermore, the redesign would hopefully avoid future maintenance while allowing the system to be easily extended.
+Furthermore, the re-design would hopefully avoid future maintenance while allowing the system to be easily extended.
 
@@
 4 of the 13 changes were additions of new modules, and additional functionality was also added to re-implemented modules.
-It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could have (!!!mean, imply?).
-One of the main reasons for continuously adapting the API is also to force (!!!wording) the API users to use the API in the way that it is intended.
+It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could cause.
+One of the main reasons for continuously adapting the API is also to control the way API users use the API.
 Prior to version 2.0 being released, a number of API users used workarounds to implement applications which contained functionality which was not yet offered from the API.
-These applications were fully functional, but were developed were incongruent.
+These applications were fully functional, but there existed no standard method of implementation.
 We therefore conclude that the law of continuing change holds for APIs.
@@
 During the interview it was also concluded that consistency and following certain standards is an important factor to consider when designing APIs.
-It was also made clear that a contributing factor for changing certain parts of the API was to bring it into line with the new interface structure.
+It was also made clear that a contributing factor for changing certain parts of the API was to bring it into line with the new interface design.
 The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that the company currently did not make use of these.
@@
 The release of version 1.4 did not include any changes related to the API interface.
-Version 1.4 strictly added support for additional build platforms (!!change this to more technical lingo).
+Version 1.0 through to 1.4 strictly added support for additional build target platforms.
 When comparing the changes introduced in version 2.0 to the ones in previous versions, it is clear that the growth of the API has gradually increased.
 During the interview it was also mentioned that the future plans for the API did not include any major changes and that only a few minor changes were planned in the near future.
-The future updates to the API will also be made incrementally and there will not be a big bang update similar to the one of version 2.0.
-This supports that the law of self regulation applies to APIs, assuming that the current stage of the life-cycle of the API can be considered as the centre of the normal distribution curve of the APIs growth.
+The future updates to the API will also be made incrementally and there will not be a big bang update similar to that of version 2.0.
+This supports that the law of self regulation applies to APIs, assuming that version 2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
 
@@
 It was also expressed during the interview that further transparency in how the API should be used could be achieved.
-One example of this is to improve the information to the user regarding which API functions are supported on which hardware types.
+One example mentioned of how this could be achieved is by improving the expressiveness regarding which API functions are supported on which hardware types.
 These facts support that the law of conservation of familiarity is true for APIs.
@@
 \subsubsection{Continuing Growth} %Reviewed by W
-Large parts of the changes between the versions were strict (!!!word) additions of new functional content.
-4 new modules were added and significant additions of new functionality were added to the modules which were re-structured from version 1.4.
+Large parts of the changes between the versions were strictly additions of new functional content.
+4 new modules were added and significant additions of new functionality were added to the modules which were re-designed from version 1.4.
 The interviewee also made it clear that increasing the functionality was one of the main goals with the 2.0 update.
-This also ties in with the ambition of controlling the way the API users use the API, as mentioned previously.
+This also ties in with the ambition of controlling the way that the API is used, as mentioned previously.
 It was also mentioned that the case company had received feedback from the API users that more frequent updates to the functional content was desirable, even though this may require them to update their application code.
-Because of this, we conclude that the law of continuing growth applies to APIs.
+We therefore conclude that the law of continuing growth applies to APIs.
 
@@
 The interviews established that a groomative motive was not the primary reason for implementing any change.
-The changes to the example code and the documentation, as well as the re-structured modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content.
-These changes did, however, increase the quality and were a substantial part of the update.
+The changes to the example code and the documentation, as well as the re-designed modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content.
+These changes did, however, also increase the quality and were a substantial part of the update.
 A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{sec:law2}.
@@
 The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users and which leads to good applications being developed.
-One example of how the API users have been included in the feedback loop, was prior to version 2.0 being released, when API users implemented functionality related to sound, even though there was no interface for this in the API.
+Prior to version 2.0 being released, an example of how the API users were included in the feedback loop was when they implemented functionality related to sound, despite the fact there was no interface for this.
 The experiences of this API user, were later considered when developing the axsound module.
-One benefit of having a more structured feedback loop, would be that the API developers would better aware of potential errors in the implementation of the API.
+One benefit of having a more structured feedback loop, would be that the API developers would have greater awareness of potential errors in the implementation of the API.
 Another ambition which was mentioned, was to bring scientific theories and best practices from academia into consideration when developing the API.
 This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects.
-Because of these factors and clearly expressed ambitions, we conclude that the law of feedback system is true for APIs.
+Based on these factors and clearly expressed ambitions, we conclude that the law of feedback system is true for APIs.
 

### 2015-05-05 thesis/paper.tex
Updates to RQ1 results

--- 2015-05-05 thesis/paper.tex
@@
 %%What she said 
-The interviewee expressed to us that the main driving force behind this change was to re-implement and add new functionality to the axhttp module.
-Redesigning the module to take advantage of the new design was an added bonus.
+The interviewee expressed that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, while at the same time, allowing them to the module according to the new design.
 
@@
 %%Describe the change 
-The burst mode feature of the API allowed users to buffer a series of images for closer analysis. This feature was deprecated during the transition between 1.4 and 2.0 and was not re-implemented.
+The burst mode feature of the API allowed users to buffer a series of images for more exact analysis.
+This feature was deprecated during the transition between version 1.4 and 2.0 and was not re-implemented.
 
 %%Relate it to Categories
-This change presented itself as a clear example of a reductive category of maintenance as it was simply removed and not replaced within the API.
-We also concluded that this change had no secondary category.
+This change presented itself as a clear example of a reductive category of maintenance, as it was simply removed and was not replaced. We also concluded that this change had no secondary category.
 
@@
 The interviewee did shed some light onto why this change occurred.
-We were informed that in order to continue using this feature in 2.0 and in newer versions of the camera hardware, it would have to be re-implemented from scratch.
-An impact assessment was undertaken to determine if the removal of the function would cost significant time and money.
+In order to continue using this feature in version 2.0 and in newer versions of the camera hardware, it would have to be re-implemented.
+An impact assessment was undertaken to determine if the removal of the function would be costly.
 Ultimately it was deemed appropriate and the function was removed from the API.
@@
 %%Category based on her information
-Given this information we can safely say that we correctly categorised this as reductive that there are indeed no other secondary categories to describe this change.
+Given this information, we can conclude that we correctly categorised this as reductive and that there are indeed no other secondary categories to describe this change.
 
@@
 %%Describe the change 
-As with many APIs, Axis included a selection of example programs to assist developers with creating applications.
+The case company included a selection of example programs to assist developers with creating applications.
 This trend continued in 2.0, but there were some significant improvements.
-The number of example programs increased, as did the amount of comments accompanying the code which has lead to an overall more robust set of examples.
+The number of example programs increased, as did the amount of comments accompanying the code which has lead to an more robust set of examples.
 
@@
 From the interview it became clear that the improvement of the example code was an important change between the two versions.
-The interviewee described to us how the examples were used frequently by their customers, however, the old examples varied significantly, even between similar tasks.
-This ultimately meant that the old examples were not good enough and new ones needed to be created, preferably conforming to a standard.
+The interviewee described how the examples were used frequently by their customers, however, the old examples varied significantly, even between similar tasks.
+This ultimately meant that the old examples were not satisfactory and new ones needed to be created, preferably conforming to a standard.
 The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.
@@
 %%Describe the change 
-As the API changed versions, so too did the documentation.
-While there were no substantial changes, we did notice that the documentation is no longer offered as a PDF via latex but is instead only offered via HTML.
+As the API code was updated in version 2.0, the API documentation was updated to correspond with the new code.
+While there were no substantial changes, we found that the documentation is no longer offered as a PDF but is instead only offered as HTML.
 
@@
 
+%Re-write this, don't say no information etc
+
 \subsubsection{Interfaces}
@@
 Version 1.4 of the API allowed direct access to the headers of each module available in the API.
-Version 2.0 changed this by including interfaces from which users can now access functionality.
-This design change has had an overall affect on the whole API as it has changed the structure of modules, but not their functionality.
+Version 2.0 changed this by including interfaces through which functionality is accessed.
+This design change has had an effect on the whole API, as it has changed the structure of modules, but not the functionality of them.
 
@@
 We therefore concluded that this change would be best categorised as  groomative.
-The secondary category of preventive was also chosen as this change could be seen as an attempt to reduce future maintenance.
+The secondary category was categorised as preventive, as this change could be seen as an attempt to reduce future maintenance.
 
@@
 Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to change the interfaces of the API.
-Furthermore, the redesign would hopefully avoid future maintenance while allowing the system to be easily extended.
+Furthermore, the redesign would hopefully avoid future maintenance while allowing the system to be more extensible.
 
@@
 Taking this information into account, we concluded that our categorisation was incorrect.
-The primary change seemed to be preventive given the strong emphasis on avoiding future maintenance and improving ease of use.
-We further concluded that the secondary change should be groomative reflect the intent to make the API more maintainable overall.
+The interview showed that the primary categorisation should have been preventive, given the strong emphasis on avoiding future maintenance and improving ease of use.
+We further concluded that the secondary change should have been groomative to reflect the intent to make the API more maintainable.
 
@@
 %%Describe the change 
-A substantial change included in version 2.0 was the addition of specific error header files, containing enums of error codes.
-While we were not aware of what error handling was utilised prior to this version, we assumed it had changed given the inclusion of these new files.
+A substantial change included in version 2.0 was the addition of header files, containing enums of error codes.
+While we were not aware of what error handling was utilised prior to this version, we assumed it had changed, given the inclusion of these new files.
 

### 2015-05-05 thesis/paper.tex

@@
 %%What she said
-The interviewee did shed some light onto why this change occurred.
-In order to continue using this feature in version 2.0 and in newer versions of the camera hardware, it would have to be re-implemented.
+The interviewee described that in order to continue using this feature in version 2.0 and in newer versions of the camera hardware, it would have to be re-implemented.
 An impact assessment was undertaken to determine if the removal of the function would be costly.
@@
 %%Describe the change
+
 The case company included a selection of example programs to assist developers with creating applications.
@@
 Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to change the interfaces of the API.
-Furthermore, the redesign would hopefully avoid future maintenance while allowing the system to be more extensible.
+Furthermore, the re-design would hopefully avoid future maintenance while allowing the system to be easily extended.
 

### 2015-05-06 thesis/paper.tex
removed comments
Reviewed disc rq1, added comments

@@
 
+%%Add percentages for both main and sub and specify which is for which
+After cross-examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.
+
+%Discuss how there were many modifications but we've classified them as re-implementations.
+Includes a deprecation and a replacement of that deprecation.
+Alternative was to analyse modify them as both an addition and a deprecation.
+
 \begin{table}
@@
 
-After cross-examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.
-
-%%TODO Finish this off XXX
-%New additions to the API were the most frequent change that we observed.
-Each addition added new functionality to the API, ranging from controlling the camera, enabling audio analysis, allowing external storage connections and providing a serial port to interface with other devices.
-
-%XXX
-%These changes were deemed to be modifications or re-implementations of existing functionality of the API.
-During the interview it was mentioned that one intent behind the re-implementations was to bring them in line with the newly created functionality which takes advantage of Glib, a new kind of error handling and extensive use of callbacks.
-
-%XXX
-%While the main focus of our investigation of the source code and documentation was to identify changes between the versions, it was also to discover differences larger trends of the API.
-The trends were also analysed and given an appropriate maintenance category.
-
-%XXX
-%While the changes between versions 1.4 and 2.0 included many deprecations, only one of them was not re-implemented in a new part of the API.
-
-%Discuss how there were many modifications but we've classified them as re-implementations.
-Includes a deprecation and a replacement of that deprecation.
-Alternative was to analyse modify them as both an addition and a deprecation.
-
 \subsubsection{axptz}
@@
 The Pan, Tilt and Zoom (ptz) module concerns functionality related to manoeuvring the camera, both mechanically and digitally. 
-
 %%Relate it to Categories
 We concluded that this change was enhancive as it is a brand-new feature of the API. There was no secondary motive behind this change, as the change was purely enhancive. 
-
 %%What she said
@@
 Prior to the change being introduced, there was no API functionality for controlling the camera and as such, it was a high priority addition to the new API.
-
 %%Category based on her information
@@
 \subsubsection{axaudio}
-
 %%Describe the change 
@@
 The addition of axaudio allows API users to perform audio analysis upon audio streams captured by cameras.
-
 %%Relate it to Categories
 This change was determined to be enhancive, as it was an addition of a new feature to the API. We found no secondary motive of the change. 
-
 %%What she said
@@
 Given the demand for audio analysis, it was included in version 2.0 of the API.
-
 %%Category based on her information
@@
 Version 2.0 included the possibility of alternative storage solutions, by allowing to the camera to interface with external storage devices, such as SD cards.
-
 %Relate it to categories
 Enhancive was chosen to be the most applicable category of change, given that axstorage was a new addition in version 2.0. No secondary motive was identified. 
-
 %%What she said
 The limited storage options for the cameras was the reason that increased functionality was strongly requested by API users and as such axstorage was included in version 2.0 of the API.
-
 %%Category based on her information
@@
 In version 1.4 of the API, there was no possibility to connect external devices to the camera.
-
 %%Relate it to Categories
 The addition of this module was determined to be an enhancive change, as it involved the addition of a new feature. No relevant secondary category were identified.
-
 %%What she said
@@
 As such it was included in version 2.0, to meet the demand of the API users.
-
 %%Category based on her information
@@
 An example of when an event is generated is when movement is detected by the camera.
-
 %%Relate it to Categories
@@
 Groomative was chosen as the secondary category due to the additional motive of bringing the new functionality into line with the new design.
-
 %%What she said 
@@
 The module was then completely re-implemented and according to the new system design of version 2.0.
-
 %%Category based on her information
@@
 Additional functionality was also added to the module.
-
 %%Relate it to Categories
 This change re-implemented an existing module while adhering to the new design of API version 2.0. The main categorisation was chosen to be enhancive with groomative as the secondary change.
-
 %%What she said 
 The interviewee expressed that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, while at the same time, allowing them to the module according to the new design.
-
 %%Category based on her information
@@
 This module was re-implemented as ax\_parameter with added functionality and conformance to the new design standards of API version 2.0.
-
+%2
 Given that this change re-implemented an existing module while also incorporating the new design standards, it has been categorised as being primarily enhancive with a secondary category of groomative.
-
+%3
 The interviewee clarified that this change was mainly concerned with re-implementing existing functionality while simultaneously adopting the new standards of version 2.0. 
-
+%4
 Given the information from the interview, we concluded that this change was correctly categorised; the primary intent was enhancive and the secondary intent was groomative.
@@
 This feature was deprecated during the transition between version 1.4 and 2.0 and was not re-implemented.
-
 %%Relate it to Categories
 This change presented itself as a clear example of a reductive category of maintenance, as it was simply removed and was not replaced. We also concluded that this change had no secondary category.
-
 %%What she said
@@
 Ultimately it was deemed appropriate and the function was removed from the API.
-
 %%Category based on her information
@@
 %%Describe the change 
-
 The case company included a selection of example programs to assist developers with creating applications.
@@
 The number of example programs increased, as did the amount of comments accompanying the code which has lead to an more robust set of examples.
-
 %%Relate it to Categories
@@
 We further decided that this change also had a secondary category of reformative.
-
 %%What she said
@@
 The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.
-
 %%Category based on her information
@@
 While there were no substantial changes, we found that the documentation is no longer offered as a PDF but is instead only offered as HTML.
-
 %%Relate it to Categories
 We categorised this change as being updative with a reformative secondary category for the reasons that the change only updated the documentation to reflect the recent changes in version 2.0.
-
 %%What she said
@@
 The interviewee agreed with our assessment that the documentation was only changed to be up to date with the current workings of the API and how the new systems interact with each other.
-
 %%Category based on her information
@@
 
-%Re-write this, don't say no information etc
+%!!!Re-write this, don't say no information etc
 
@@
 This design change has had an effect on the whole API, as it has changed the structure of modules, but not the functionality of them.
-
 %%Relate it to Categories
@@
 The secondary category was categorised as preventive, as this change could be seen as an attempt to reduce future maintenance.
-
 %%What she said
@@
 Furthermore, the re-design would hopefully avoid future maintenance while allowing the system to be easily extended.
-
 %%Category based on her information
@@
 While we were not aware of what error handling was utilised prior to this version, we assumed it had changed, given the inclusion of these new files.
-
 %%Relate it to Categories
@@
 Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability.
-
 %%What she said
@@
 Glib was added to version 2.0 and the error handling functionality that Glib provides, was incorporated into the new API design.
-
 %%Category based on her information
@@
 
-\subsubsection{Continuing Change} %Reviewed by W
+\subsubsection{Continuing Change} %Reviewed by WJ
 The case company described that including new functional content was one of the top priorities for the release of vesrion 2.0.
@@
 
-\subsubsection{Increasing Complexity} \label{sec:law2} %Reviewed by W
+\subsubsection{Increasing Complexity} \label{sec:law2} %Reviewed by WJ
 A majority of the changes introduced in version 2.0 aimed to improve the structure and the way that the API was used.
@@
 
-\subsubsection{Self Regulation} \label{sec:law3} %Reviewed by W
+\subsubsection{Self Regulation} \label{sec:law3} %Reviewed by WJ
 The release of version 1.4 did not include any changes related to the API interface.
@@
 
-\subsubsection{Conservation of Organisational Stability} %Reviewed by W
+\subsubsection{Conservation of Organisational Stability} %Reviewed by WJ
 The changes to the API have been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
@@
 
-\subsubsection{Conservation of Familiarity} %Reviewed by W
+\subsubsection{Conservation of Familiarity} %Reviewed by WJ
 The documentation that is included with the API was rigorously updated with the introduction of version 2.0.
@@
 
-\subsubsection{Continuing Growth} %Reviewed by W
+\subsubsection{Continuing Growth} %Reviewed by WJ
 Large parts of the changes between the versions were strictly additions of new functional content.
@@
 
-\subsubsection{Declining Quality} %Reviewed by W
+\subsubsection{Declining Quality} %Reviewed by WJ
 The interviews established that a groomative motive was not the primary reason for implementing any change.
@@
 
-\subsubsection{Feedback System} %Reviewed by W
+\subsubsection{Feedback System} %Reviewed by WJ
 One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
@@
 
-\section{Discussion}
+\section{Discussion} %Reviewed by W
 Our results have been provided valuable insight to the motives behind the evolution of an API.
-The results show that APIs definitely can be studied from the point of view of old evolution theories.
+The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
 Based on the result, we have formulated the subsequent outcomes.
@@
 \noindent
-\textbf{Adding functionality is a prime driver of API evolution  }
+\textbf{Adding functionality is a prime driver of API evolution  } %Reviewed by W
 Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
-We found strong evidence to suggest that most, if not all of the additions, re-implementations and functional changes were undertaken to include additional functionality requested both internally and by the API users.
-This focus upon functionality was also emphasised in part due to a business goal.
+We found that a vast majority of the changes either added functionality or were direct effects of functionality being added.
+The main driver for these changes was the pressure from the API users, but pressure from the case company developers which utilised the API also contributed.
+This focus upon functionality was also emphasised in part due to a business goal ( "in part due to, sounds weird to me") .
 The more features the API can provide, the more applications developers can create for the cameras.
-This has a knock-on effect of increasing the appeal and therefore value of the products.
+This has a domino effect of increasing the appeal and therefore value of the products.
 
@@
 \smallskip \noindent 
-\textbf{Maintainability does not drive change  } 
+\textbf{Maintainability does not drive change  } %Reviewed by W 
 While maintainability is important, it is not a primary driving factor for change.
@@
 For example, we predicted that the main intents to be enhancive which was correct.
-Furthermore, of the changes identified, none were considered to be primarily groomative, groomative changes were only identified as sub-category changes.
+( " Need to explain what was enhancive") Furthermore, of the changes identified, none were considered to be primarily groomative.
+Groomative motives were only found to be secondary, and never drove the change.
 Changes to the example code is further evidence of this.
@@
 \smallskip \noindent
-\textbf{Aiding development of applications  } 
-Aiding users of the API to create correct and robust applications is a very important evolution factor for Axis.
-Changes between the versions brought about improvements to error handling, the example code and the way in which the API utilises interfaces.
-This, coupled with removal of unwanted functionality and unsafe operations, has allowed the API to grow and become much more user friendly.
-As mentioned previously, this could increase the amount of applications being created for the camera and thus could increase its value.
+\textbf{Aiding development of applications  } %Reviewed by W
+Aiding ( "minor detail: is supporting better here?") users of the API to create correct and robust applications is a very important evolution factor for the case company.
+Changes between the versions brought about ( 're-word'?) improvements to error handling, the example code and the way in which the API utilises interfaces.
+This, coupled with removal of unwanted functionality and unsafe operations, has allowed the API to grow and become much more user-friendly.
+As mentioned previously, this could increase the amount of applications being created for the camera and in turn could increase its value ( "change to' : increase the value of them ?").
 
 \smallskip \noindent
-\textbf{Removing functionality  }
-Previous literature has stated that deprecations should be favoured over removals from API for many reasons except in specific circumstances.
-The successful removal of the burst function seems to indicate that this advice is well worth following.
-Indeed, axis only removed this function from the API after an internal review found that the cost of removing it would outweigh potential drawbacks to keeping it in the API.
-It is therefore recommended to only remove something if the effects of removing it have been well investigated and that the removal is rather small in scale.
+\textbf{Removing functionality  } %Reviewed by W
+Previous literature has stated that deprecations should be favoured over removals from API for many reasons, except in specific circumstances.
+The successful removal of the burst function seems to indicate that this advice is well worth following ( "well worth following reads weirdly") ( 'this sentence also contradicts the previous one').
+Indeed, Axis only removed this function from the API after an internal review found that the cost of removing it would outweigh potential drawbacks to ( 'of???') keeping it in the API.
+( 'this sentence is weird', "and remove the indeed") It is ( 'change to We therefore recommend') therefore recommended to only remove something if the effects of removing it have been well investigated and that the removal is rather small in scale.
+( "instead of saying  small in scale i think we should explain that they should be made in increments and only a few at once")
 
 \smallskip \noindent
-\textbf{Updative changes do not drive change  }
+\textbf{Updative changes do not drive change  } %Reviewed by W
 Changes to documentation and example code are important, especially if the API is drastically changing between versions.
 However, these updative changes are drivers themselves, rather, they make up part of a larger change as a whole.
+( "this whole section has to be re-written.
+We can't refer to them as updative changes since the nature of updative changes are reactive.
+instead refer to them as changes to !code e.g.
+documentation, example code etc.")
 %^Probably needs more to it?
@@
 \smallskip \noindent
-\textbf{Hardware was not a driving factor  }
-Interestingly, we found that hardware was not a direct driver of change.
-Initially we had thought that it would be one of the strongest drivers of change, for example, new versions of hardware become available or new hardware is added to the camera requiring something in the API to access it.
-This does seem to suggest that the hardware for the camera is sufficiently stable such that it does not require changes and that those changes do not need to be reflected in new API versions.
+\textbf{Hardware was not a driving factor  } %Reviewed by W
+Interestingly ( "remove interestingly") , we found that hardware ( "have to explain in what regard we 'expected' hardware to be a driver e.g.
+updates to hardware, the release of new cameras")) was not a direct driver of change.
+Initially, we had thought ( "rephrase had thought...
+anticipated?
+thought sounds like we guessed" (or maybe say "Our initial expectaitions were")) that it would be one of the strongest drivers of change ( "new sentence here"), for example, new versions of hardware become available or new hardware is added to the camera requiring something in the API to access it.
+This does seem to suggest that the hardware for the camera is sufficiently stable such that it does not require changes and that those changes do not need to be ( "change 'not need to be' to 'are not'?") reflected in new API versions.
 
@@
 The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that the extent to which they apply might not be as significant for APIs compared to other types of systems.
-The reason that this doubt exists is that these motivations could were only secondary to the motivations of increased functionality.
+The reason that this doubt exists is that these motivations were only secondary to the motivations of increased functionality.
 An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} might overshadow (!!!wording) the need to increase simplicity and quality.

### 2015-05-06 thesis/paper.tex
Updates to RQ1

@@
 %This should probably go in Methodology... parts of it at least /W
+In order to answer \textbf{RQ1}, we categorised the changes based on the 12 maintenance categories \cite{chapin2001types}, by inspecting the source code and the accompanying documentation.
+Following the interview, we compared our categorisations to the actual motive which was gathered from the interview.
+
 Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
+
 Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories.
@@
 This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.
+%This paragraph should be moved to Methodology
 
@@
 \subsection{RQ1 Results} \label{results_rq1}
-
-%This paragraph should be moved to Methodology
-In order to answer \textbf{RQ1}, we categorised the changes based on the 12 maintenance categories \cite{chapin2001types}, by inspecting the source code and the accompanying documentation.
-Following the interview, we compared our categorisations to the actual motive which was gathered from the interview.
-
 %Add a small introductory sentence to this paragraph and have it as the first paragraph of this section (Don't forget to ref the table)
+Many changes were found between version 1.4 and version 2.0.
+Initial inspection revealed there to be many deprecations which were later re-implemented as new modules.
+We have considered these changes as a single change instead of a deprecation and a re-implementation.
+In total, thirteen unique changes were found.
+These changes are show in table \ref{table:Categories}.
+%
 The changes have been divided up into four specific categories, namely: new, modified, removed and general trends.
@@
 General trends are broad changes that do not directly affect functionality.
-
 %%Add percentages for both main and sub and specify which is for which
-After cross-examining our results with the interviewee and their responses, we found that roughly 78\% of our categorisation matched the actual categorisation of the changes.
-
-%Discuss how there were many modifications but we've classified them as re-implementations.
-Includes a deprecation and a replacement of that deprecation.
-Alternative was to analyse modify them as both an addition and a deprecation.
+After cross-examining our results with the interviewee and their responses, we found that 78\% of our main categorisation predictions matched the actual intent of the changes and that 78\% of our sub categorisations predictions matched the actual intents.
 
@@
 %%Relate it to Categories
-We concluded that this change was enhancive as it is a brand-new feature of the API. There was no secondary motive behind this change, as the change was purely enhancive. 
+We concluded that this change was enhancive, because it is a new feature of the API. There was no secondary motive behind this change, as the change was purely enhancive. 
 %%What she said
-The interviewee described how this change and the other changes classified as additions were all included in the new API at the request of API users.
+The interviewee described how this change, as well as the other changes classified as additions, were all included in the new API at the request of API users.
 Prior to the change being introduced, there was no API functionality for controlling the camera and as such, it was a high priority addition to the new API.
 %%Category based on her information
-Based on the interviewees' comments, we concluded that we had correctly identified the change as being enhancive.
-Furthermore, we were also correct in our prediction that there was no secondary category.
+The interviewees' comments allowed us to concluded that we had correctly identified the change as being enhancive.
+Furthermore, we were also correct in our prediction that there was no secondary change category.
 
@@
 %%Describe the change 
-The most important functionality of the camera is to capture and analyse video data, however, some the API users require the possibility to perform analysis upon audio data.
+The most important functionality of the camera is to capture and analyse video data, however, some API users require the ability to analyse audio data.
 The addition of axaudio allows API users to perform audio analysis upon audio streams captured by cameras.
 %%Relate it to Categories
-This change was determined to be enhancive, as it was an addition of a new feature to the API. We found no secondary motive of the change. 
+This change was determined to be enhancive, as it was an addition of a new feature to the API. We found no secondary motive for the change. 
 %%What she said
-Audio analysis had not previously been possible on Axis devices.
-During the interview, it was revealed that an API user had managed to implement their own audio analysis using version 1.4 of the API.
-Given the demand for audio analysis, it was included in version 2.0 of the API.
+Audio analysis had previously not been supported in version 1.4 of the API.
+However, during the interview, it was revealed that an API user had managed to implement their own audio analysis application using version 1.4 of the API.
+Given the apparent demand for audio analysis, it was included in version 2.0 of the API.
 %%Category based on her information
-Based on the the interviewee's reasoning, we concluded that we had successfully determined that the change was enhancive. The addition of axaudio had no secondary motive.
+Taking into account the interviewee's reasoning, we concluded that we had successfully determined that the change was enhancive. The addition of axaudio had no secondary motive.
 
@@
 %%Describe the change 
-Prior to the newest version of the API being released, the sole alternative for storage was to use the Video Management System.
-Version 2.0 included the possibility of alternative storage solutions, by allowing to the camera to interface with external storage devices, such as SD cards.
+Prior to the newest version of the API being released, the sole alternative for storing data was to use the Video Management System.
+Version 2.0 added the possibility of alternative storage solutions, by allowing to the camera to interface with external storage devices, such as SD cards.
 %Relate it to categories
-Enhancive was chosen to be the most applicable category of change, given that axstorage was a new addition in version 2.0. No secondary motive was identified. 
+Enhancive was chosen to be the primary category of change, given that axstorage was a new addition in version 2.0. No secondary motive was identified. 
 %%What she said
-The limited storage options for the cameras was the reason that increased functionality was strongly requested by API users and as such axstorage was included in version 2.0 of the API.
+The interviewee described how limited storage options for the cameras, in version 1.4, was the reason that increased functionality was strongly requested by API users.
+As such, axstorage was included in version 2.0 of the API.
 %%Category based on her information
-The information gathered from the interview supported that we were correct in our categorisation of this change. No secondary category was established.
+The information gathered from the interview therefore supported our original categorisation; it was an enhancive change. No secondary category was established.
 
@@
 %%Describe the change 
-The addition of axserialport allows API users to connect various devices to their cameras by through the serial port.
+The addition of axserialport allows API users to connect various devices to their cameras through the use of a serial port.
 This allows users to integrate multiple devices to create their own unique solutions.
-In version 1.4 of the API, there was no possibility to connect external devices to the camera.
+This was not possible in version 1.4 of the API.
 %%Relate it to Categories
-The addition of this module was determined to be an enhancive change, as it involved the addition of a new feature. No relevant secondary category were identified.
+The addition of this module was determined to be an enhancive change, as it involved the addition of a new feature. No relevant secondary category was identified.
 %%What she said
-The addition of axserialport was requested by API users.
-A possible use case, which was given during the interview involved a ticketing system which allows for joint analysis of data from both devices.
+The addition of axserialport was requested by API users to allow them to connect their cameras with other devices.
+A possible use case, that was given during the interview, involved a ticketing system which allows for joint analysis of data from multiple devices.
 As such it was included in version 2.0, to meet the demand of the API users.
 %%Category based on her information
-Given this information, we concluded that we were correct in predicting that this change was enhancive. The prediction of the secondary category was also correct.
+Given this information, we concluded that we were correct categorising this change as enhancive. The categorisation of the secondary category was also correct.
 
@@
 %%Describe the change 
-Version 2.0 of the API was designed to be an event-driven system which makes use of callbacks.
+Version 2.0 of the API was designed to be an event-driven system that makes use of callbacks.
 To achieve this, the old event system had to be re-designed.
-The new design is used by all features of API version 2.0.
-An example of when an event is generated is when movement is detected by the camera.
+The new design is used by all features of version 2.0 of the API.
+An example of when an event is generated, would be when movement is detected by the camera.
 %%Relate it to Categories
-Given that this module was a re-implementation of the previous event system, we concluded that it should be classified mainly as an enhancive change with the secondary category being classified as groomative.
+Given that this module was a re-implementation of the previous event system, we concluded that it should be categorised mainly as an enhancive change with the secondary change as groomative.
 Groomative was chosen as the secondary category due to the additional motive of bringing the new functionality into line with the new design.
@@
 The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implemention of the new event system.
-One reason being that the case company were dissatisfied with certain usability aspects of the API.
-The module was then completely re-implemented and according to the new system design of version 2.0.
+One reason being, that the case company was dissatisfied with certain usability aspects of API version 1.4.
+The module was then completely re-implemented and re-designed according to the new system design of version 2.0.
 %%Category based on her information
@@
 %%Describe the change 
-The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically load data to web pages.
+The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically send data to web pages.
 The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards.

### 2015-05-06 thesis/paper.tex
Added rqs to results

@@
 \subsection{RQ1 Results} \label{results_rq1}
-%Add a small introductory sentence to this paragraph and have it as the first paragraph of this section (Don't forget to ref the table)
+\noindent
+RQ1: \textbf{How do companies actively drive API evolution?}
+
+\noindent
+RQ1.1: \textbf{To what extent can we reverse engineer API change decisions?}
+\smallskip
+
 Many changes were found between version 1.4 and version 2.0.
@@
 \subsection{RQ2 Results} \label{results_rq2}
+\noindent
+RQ2: \textbf{How do APIs ``passively'' evolve?}
+\smallskip
+
 The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs.

### 2015-05-06 thesis/paper.tex
Review disc RQ1.1

@@
 \noindent
-\textbf{Functionality is reverse engineerable  } 
-All changes which main motivation were to either add or remove functionality were accurately predicted.
-These changes were the most major ones, and it was expressed during the interview that these changes were the main motive behind the introduction of the new version.
+\textbf{Functionality is reverse engineerable  } %Reviewed by W
+All changes which main motive were to either add or remove functionality were accurately predicted.
+These changes were the most major ones, and it was expressed during the interview that these types of changes main driving factor behind the development of the new version.
 In summary, 11 out of a total 13 changes were correctly predicted.
@@
 \smallskip \noindent
-\textbf{``Structural'' changes are not reverse engineerable  }
+\textbf{``Structural'' reverse engineerable to a lesser extent} %Reviewed by W
 3 out of 5 changes which did not add functionality, but rather were introduced to redcue complexity and increase quality were correctly predicted.
-The two changes which were not predicted correctly were wrong because the main-motivation was mixed up with the sub-intention (!!!re-phrase).
+The two changes which were incorrectly predicted were wrong because the main motivation was mixed up with the secondary intent ( "re-phrase").
 This shows that although the prediction was incorrect, the general reasoning was correct.
-Our predictions were accurate enough to allow us to form a reliable conlusion which created a good means for discussion with the company (!!!re-phrase).
+Our predictions were accurate enough to allow us to form a reliable conlusion which created a good means for discussion with the company ( "re-phrase").
 

### 2015-05-06 thesis/paper.tex
Finished review of RQ1 results

@@
 The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically send data to web pages.
-The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards.
-Additional functionality was also added to the module.
+The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards and at the same time, additional functionality was added to the module.
 %%Relate it to Categories
-This change re-implemented an existing module while adhering to the new design of API version 2.0. The main categorisation was chosen to be enhancive with groomative as the secondary change.
+This change re-implemented an existing module while adhering to the new design of API version 2.0. The main categorisation therefore was chosen to be enhancive with groomative as the secondary change.
 %%What she said 
-The interviewee expressed that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, while at the same time, allowing them to the module according to the new design.
+The interviewee described that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, while at the same time, following the new design.
 %%Category based on her information
 Our categorisation of enhancive and groomative was therefore correct for this change.
-The primary intent was to add functionality while also allowing the re-implementation accommodate the new API design.
+The primary intent was to add functionality while also allowing the re-implementation to make use of the new API design.
 
@@
 %%Describe the change 
-The parameter setting module of the API allows data and application settings to be saved so that they are not lost when the device is not running.
+The parameter setting module of the API allowed data and application settings to be saved so that they are not lost if the device is not running.
 This module was re-implemented as ax\_parameter with added functionality and conformance to the new design standards of API version 2.0.
@@
 %3
-The interviewee clarified that this change was mainly concerned with re-implementing existing functionality while simultaneously adopting the new standards of version 2.0. 
+The interviewee clarified that this change was mainly concerned with re-implementing existing functionality, while simultaneously adopting the new standards of version 2.0. 
 %4
@@
 %%Describe the change 
-The burst mode feature of the API allowed users to buffer a series of images for more exact analysis.
+The burst mode feature of the API allowed users to buffer a series of images for greater analysis.
 This feature was deprecated during the transition between version 1.4 and 2.0 and was not re-implemented.
 %%Relate it to Categories
-This change presented itself as a clear example of a reductive category of maintenance, as it was simply removed and was not replaced. We also concluded that this change had no secondary category.
+This change presented itself as a clear example of a reductive category of maintenance, as it was simply removed and was not replaced. We therefore gave no secondary categorisation for this change.
 %%What she said
-The interviewee described that in order to continue using this feature in version 2.0 and in newer versions of the camera hardware, it would have to be re-implemented.
+The interviewee described, that in order to continue using this feature, it would have to be re-implemented.
 An impact assessment was undertaken to determine if the removal of the function would be costly.
-Ultimately it was deemed appropriate and the function was removed from the API.
+Ultimately it was deemed appropriate to remove and the function was take out of the API.
 %%Category based on her information
-Given this information, we can conclude that we correctly categorised this as reductive and that there are indeed no other secondary categories to describe this change.
+We can therefore conclude that we correctly categorised this change as reductive and that there are indeed, no secondary categories to describe this change.
 
@@
 The case company included a selection of example programs to assist developers with creating applications.
-This trend continued in 2.0, but there were some significant improvements.
-The number of example programs increased, as did the amount of comments accompanying the code which has lead to an more robust set of examples.
+This trend continued in version 2.0, but there were some significant improvements.
+The number of example programs and the amount of comments accompanying the code increased, thus improving quality of the examples.
 %%Relate it to Categories
@@
 %%What she said
-From the interview it became clear that the improvement of the example code was an important change between the two versions.
-The interviewee described how the examples were used frequently by their customers, however, the old examples varied significantly, even between similar tasks.
-This ultimately meant that the old examples were not satisfactory and new ones needed to be created, preferably conforming to a standard.
+During the interview, it became clear that the improvement of the example code was an important change between the two versions.
+The interviewee described how the examples were used frequently by their customers, however, the old examples had many varied implementation techniques even for similar tasks.
+This ultimately meant that the old examples were not satisfactory and that new examples would have to be written, preferably conforming to the same standards.
 The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.
 %%Category based on her information
-With this information we concluded that our categorisation was incorrect.
-It became clear that this change was in actual fact primarily reformative, given that the changes to the documentation were being performed to meet the needs of the API users.
+With this information, we concluded that our categorisation was incorrect.
+It became clear that this change was, in actual fact, primarily reformative.
 It was also clear that the subcategory should therefore have been updative.
@@
 %%What she said
-This sentiment was supported by the interview.
-The interviewee agreed with our assessment that the documentation was only changed to be up to date with the current workings of the API and how the new systems interact with each other.
+This sentiment was shared by the interviewee.
+They agreed with our assessment, that the documentation was only changed to keep it up to date with the current workings of the API and how the new systems interact with each other.
 %%Category based on her information
-As there was no information to contradict our categorisations we have concluded we were correct in our predictions.
+We can therefore say that our categorisations were correct, the change was updative and reformative.
 
@@
 We therefore concluded that this change would be best categorised as  groomative.
-The secondary category was categorised as preventive, as this change could be seen as an attempt to reduce future maintenance.
+The secondary category was categorised as preventive, as the change could be seen as an attempt to reduce future maintenance.
 %%What she said
 The interview provided further insight into the reasoning behind this design change.
-Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to change the interfaces of the API.
-Furthermore, the re-design would hopefully avoid future maintenance while allowing the system to be easily extended.
+Improvements to coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to use interfaces in versions 2.0 of the API.
+Furthermore, the re-design would hopefully avoid future maintenance, while also allowing the system to be easily extended.
 %%Category based on her information
 Taking this information into account, we concluded that our categorisation was incorrect.
-The interview showed that the primary categorisation should have been preventive, given the strong emphasis on avoiding future maintenance and improving ease of use.
-We further concluded that the secondary change should have been groomative to reflect the intent to make the API more maintainable.
+The interview showed that the primary categorisation should have been preventive, given the strong emphasis on avoiding future maintenance and improving usability.
+We further concluded that the secondary change should have been groomative, to better reflect the intent of improving the APIs maintainability.
 
@@
 %%Relate it to Categories
-Based on this, we categorised this change as being primarily preventive as error handling is preventive by nature.
+We therefore categorised this change as being primarily preventive, as error handling is preventive by nature.
 Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability.
@@
 During the interview, it was made clear that the previous error handling was lacking in expressiveness and usability.
-Glib was added to version 2.0 and the error handling functionality that Glib provides, was incorporated into the new API design.
+Glib was added to version 2.0 and the error handling functionality that Glib provides was incorporated into the new API design.
 %%Category based on her information

### 2015-05-06 thesis/paper.tex
Changes to table
Review results rq1

@@
 \usepackage[english]{babel}
-
-%Used to create Macro 1
-\usepackage{array}
 
@@
 \begin{document}
-
-%Macro 1, used to create thick vertical line in Table 1: Category 
-\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
-\makeatother
 
@@
 \section{Results} \label{results}
-This section will present the results of our study.
+This section will present the findings of our study.
 The results related to \textbf{RQ1} and \textbf{RQ1.1} are introduced in Section \ref{results_rq1}, and the results of \textbf{RQ2} are presented in Section \ref{results_rq2}
@@
 Many changes were found between version 1.4 and version 2.0.
-Initial inspection revealed there to be many deprecations which were later re-implemented as new modules.
-We have considered these changes as a single change instead of a deprecation and a re-implementation.
+The initial inspection revealed there to be many deprecations which were later re-implemented as new modules.
+We have group these changes into a single change instead of a deprecation and a re-implementation.
 In total, thirteen unique changes were found.
-These changes are show in table \ref{table:Categories}.
-%
-The changes have been divided up into four specific categories, namely: new, modified, removed and general trends.
-The category new concerns additions of modules, modified concerns modifications to modules that existed in version 1.4 and removed are changes where functionality was removed being deprecated or replaced by functionality.
-General trends are broad changes that do not directly affect functionality.
-%%Add percentages for both main and sub and specify which is for which
-After cross-examining our results with the interviewee and their responses, we found that 78\% of our main categorisation predictions matched the actual intent of the changes and that 78\% of our sub categorisations predictions matched the actual intents.
+These changes are shown in Table \ref{table:categories}.
+
+The changes have been divided up into four specific categories, namely: \textit{new}, \textit{modified}, \textit{removed} and \textit{general trends}.
+The category \textit{new} concerns additions of modules, \textit{modified} concerns modifications to modules that existed in version 1.4 and \textit{removed} are changes where functionality was removed being deprecated or replaced by functionality.
+\textit{General trends} are broad changes that are mainly related to design.
+
+After cross-examining our results with the interviewee and their responses, we found that 78\% of our main category predictions matched the actual motive of the changes and that 78\% of our secondary categorisations matched the actual motives.
 
@@
        \centering
-       \begin{tabular}[ht]{|c"c|c|c|c|}
+       \begin{tabular}[ht]{|c|c|c|c|c|}
 
@@
 
-              \multirow{2}{*}{\textbf{Change}}          & \multicolumn{2}{c}{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Sub}}        \\ \cline{2-5}
+              \multirow{2}{*}{\textbf{Change}}          & \multicolumn{2}{c|}{\textbf{Main}}       & \multicolumn{2}{c|}{\textbf{Sub}}        \\ \cline{2-5}
 
@@
        \caption{Category }
-       \label{table:Categories}
+       \label{table:categories}
 \end{table}
@@
 %%Category based on her information
-The interviewees' comments allowed us to concluded that we had correctly identified the change as being enhancive.
+The interviewees' comments allowed us to conclude that we had correctly identified the change as being enhancive.
 Furthermore, we were also correct in our prediction that there was no secondary change category.
@@
 The most important functionality of the camera is to capture and analyse video data, however, some API users require the ability to analyse audio data.
-The addition of axaudio allows API users to perform audio analysis upon audio streams captured by cameras.
+The addition of axaudio allows API users to perform audio analysis of audio streams captured by cameras.
 %%Relate it to Categories
@@
 Prior to the newest version of the API being released, the sole alternative for storing data was to use the Video Management System.
-Version 2.0 added the possibility of alternative storage solutions, by allowing to the camera to interface with external storage devices, such as SD cards.
+Version 2.0 added the possibility of alternative storage solutions, by allowing the camera to interface with external storage devices, such as SD cards.
 %Relate it to categories
-Enhancive was chosen to be the primary category of change, given that axstorage was a new addition in version 2.0. No secondary motive was identified. 
+Enhancive was chosen to be the primary category of change, given that axstorage was a new addition to version 2.0. No secondary motive was identified. 
 %%What she said
@@
 %%Describe the change 
-The addition of axserialport allows API users to connect various devices to their cameras through the use of a serial port.
+The addition of axserialport allows API users to connect various devices to the cameras through the use of a serial port.
 This allows users to integrate multiple devices to create their own unique solutions.
@@
 %%What she said
-The addition of axserialport was requested by API users to allow them to connect their cameras with other devices.
+The addition of axserialport was requested by API users to allow them to connect the cameras to other devices.
 A possible use case, that was given during the interview, involved a ticketing system which allows for joint analysis of data from multiple devices.
-As such it was included in version 2.0, to meet the demand of the API users.
+As such, it was included in version 2.0, to meet the demand of the API users.
 %%Category based on her information
-Given this information, we concluded that we were correct categorising this change as enhancive. The categorisation of the secondary category was also correct.
+Given this information, we concluded that we were correct in categorising this change as enhancive. The categorisation of the secondary category was also correct.
 
@@
 The new design is used by all features of version 2.0 of the API.
-An example of when an event is generated, would be when movement is detected by the camera.
+An example of when an event would be generated, is when the camera detects movement.
 %%Relate it to Categories
@@
 The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implemention of the new event system.
-One reason being, that the case company was dissatisfied with certain usability aspects of API version 1.4.
+One reason was that the case company was dissatisfied with certain usability aspects of API version 1.4.
 The module was then completely re-implemented and re-designed according to the new system design of version 2.0.
@@
 The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically send data to web pages.
-The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards and at the same time, additional functionality was added to the module.
+The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards, and at the same time, additional functionality was added to the module.
 %%Relate it to Categories
-This change re-implemented an existing module while adhering to the new design of API version 2.0. The main categorisation therefore was chosen to be enhancive with groomative as the secondary change.
+This change re-implemented an existing module while adhering to the new design of API version 2.0.
+The main categorisation therefore was chosen to be enhancive with groomative as the secondary category.
 %%What she said 
-The interviewee described that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, while at the same time, following the new design.
+The interviewee described that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, within the standards of the new design. 
 %%Category based on her information
@@
 %%Relate it to Categories
-This change presented itself as a clear example of a reductive category of maintenance, as it was simply removed and was not replaced. We therefore gave no secondary categorisation for this change.
+This change presented itself as a clear example of reductive maintenance, as it was simply removed and without being replaced. We therefore gave no secondary categorisation for this change.
 %%What she said
@@
 An impact assessment was undertaken to determine if the removal of the function would be costly.
-Ultimately it was deemed appropriate to remove and the function was take out of the API.
+Ultimately, the negative effects were not deemed significant enough and thus the function was removed of the API.
 %%Category based on her information
@@
 %%Relate it to Categories
-We therefore concluded that this change was updative, as the example code was updated to the new API and the new techniques that it utilises.
+We therefore concluded that this change was updative, as the example code was updated according to the new API and the new techniques that it utilises.
 We further decided that this change also had a secondary category of reformative.
@@
 During the interview, it became clear that the improvement of the example code was an important change between the two versions.
-The interviewee described how the examples were used frequently by their customers, however, the old examples had many varied implementation techniques even for similar tasks.
+The interviewee described how the examples were used frequently by their customers, however, the old examples had many varied implementation techniques, even for similar tasks.
 This ultimately meant that the old examples were not satisfactory and that new examples would have to be written, preferably conforming to the same standards.
@@
 %%What she said
-This sentiment was shared by the interviewee.
-They agreed with our assessment, that the documentation was only changed to keep it up to date with the current workings of the API and how the new systems interact with each other.
+This sentiment was shared by the interviewee; the documentation was only changed according to the current workings of the API and how the new modules interact with each other.
 %%Category based on her information
@@
 
-\subsubsection{Error Handling}
-
-%%Describe the change 
-A substantial change included in version 2.0 was the addition of header files, containing enums of error codes.
-While we were not aware of what error handling was utilised prior to this version, we assumed it had changed, given the inclusion of these new files.
-%%Relate it to Categories
-We therefore categorised this change as being primarily preventive, as error handling is preventive by nature.
-Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability.
-%%What she said
-%% Glib - https://developer.gnome.org/glib/
-During the interview, it was made clear that the previous error handling was lacking in expressiveness and usability.
-Glib was added to version 2.0 and the error handling functionality that Glib provides was incorporated into the new API design.
-%%Category based on her information
-We therefore concluded that our categorisation for this change was correct.
-Indeed, the primary reason for the change was to improve the existing error handling while conforming to the new API standard.
-
 \subsubsection{3\textsuperscript{rd} Party}
 ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
+%% REMEMBER TO PROVIDE LINK TO GLIB:::: - https://developer.gnome.org/glib/
 
@@
 (!!!This is also too assume-y)
+
+\subsubsection{Error Handling}
+
+%%Describe the change 
+A substantial change included in version 2.0 was the addition of header files, containing enums of error codes.
+While it was not evident how the error handling was implemented prior to version 2.0, we concluded that it had changed, given the addition of the new header files.
+%%Relate it to Categories
+We therefore categorised this change as being primarily preventive, as error handling is preventive by nature.
+Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability.
+%%What she said
+During the interview, it was made clear that the previous error handling was lacking in expressiveness and usability.
+Glib was added to version 2.0 and the error handling functionality that Glib provides was incorporated into the new API design.
+%%Category based on her information
+We therefore concluded that our categorisation for this change was correct. The primary reason for the change was to improve the existing error handling while conforming to the new API standard.
 

### 2015-05-06 thesis/paper.tex
Removed comments from results rq1

@@
 \subsubsection{axptz}
-%Add info about this is one of the added changes XXX (do that for all)
 The Pan, Tilt and Zoom (ptz) module concerns functionality related to manoeuvring the camera, both mechanically and digitally.
-%%Relate it to Categories
-We concluded that this change was enhancive, because it is a new feature of the API. There was no secondary motive behind this change, as the change was purely enhancive. 
-%%What she said
+We concluded that this change was enhancive, because it is a new feature of the API.
+There was no secondary motive behind this change, as the change was purely enhancive.
 The interviewee described how this change, as well as the other changes classified as additions, were all included in the new API at the request of API users.
 Prior to the change being introduced, there was no API functionality for controlling the camera and as such, it was a high priority addition to the new API.
-%%Category based on her information
 The interviewees' comments allowed us to conclude that we had correctly identified the change as being enhancive.
@@
 \subsubsection{axaudio}
-%%Describe the change 
 The most important functionality of the camera is to capture and analyse video data, however, some API users require the ability to analyse audio data.
 The addition of axaudio allows API users to perform audio analysis of audio streams captured by cameras.
-%%Relate it to Categories
-This change was determined to be enhancive, as it was an addition of a new feature to the API. We found no secondary motive for the change. 
-%%What she said
+This change was determined to be enhancive, as it was an addition of a new feature to the API.
+We found no secondary motive for the change.
 Audio analysis had previously not been supported in version 1.4 of the API.
 However, during the interview, it was revealed that an API user had managed to implement their own audio analysis application using version 1.4 of the API.
-Given the apparent demand for audio analysis, it was included in version 2.0 of the API.
-%%Category based on her information
-Taking into account the interviewee's reasoning, we concluded that we had successfully determined that the change was enhancive. The addition of axaudio had no secondary motive.
+Given the apparent demand for audio analysis, it was included in version 2.0 of the API.Taking into account the interviewee's reasoning, we concluded that we had successfully determined that the change was enhancive.
+The addition of axaudio had no secondary motive.
 
 \subsubsection{axstorage}
-
-%%Describe the change 
 Prior to the newest version of the API being released, the sole alternative for storing data was to use the Video Management System.
 Version 2.0 added the possibility of alternative storage solutions, by allowing the camera to interface with external storage devices, such as SD cards.
-%Relate it to categories
-Enhancive was chosen to be the primary category of change, given that axstorage was a new addition to version 2.0. No secondary motive was identified. 
-%%What she said
+Enhancive was chosen to be the primary category of change, given that axstorage was a new addition to version 2.0.
+No secondary motive was identified.
 The interviewee described how limited storage options for the cameras, in version 1.4, was the reason that increased functionality was strongly requested by API users.
-As such, axstorage was included in version 2.0 of the API.
-%%Category based on her information
-The information gathered from the interview therefore supported our original categorisation; it was an enhancive change. No secondary category was established.
+As such, axstorage was included in version 2.0 of the API.The information gathered from the interview therefore supported our original categorisation; it was an enhancive change.
+No secondary category was established.
 
 \subsubsection{axserialport}
-
-%%Describe the change 
 The addition of axserialport allows API users to connect various devices to the cameras through the use of a serial port.
@@
 This was not possible in version 1.4 of the API.
-%%Relate it to Categories
-The addition of this module was determined to be an enhancive change, as it involved the addition of a new feature. No relevant secondary category was identified.
-%%What she said
+The addition of this module was determined to be an enhancive change, as it involved the addition of a new feature.
+No relevant secondary category was identified.
 The addition of axserialport was requested by API users to allow them to connect the cameras to other devices.
@@
 As such, it was included in version 2.0, to meet the demand of the API users.
-%%Category based on her information
-Given this information, we concluded that we were correct in categorising this change as enhancive. The categorisation of the secondary category was also correct.
+Given this information, we concluded that we were correct in categorising this change as enhancive.
+The categorisation of the secondary category was also correct.
 
 \subsubsection{axevent}
-
-%%Describe the change 
 Version 2.0 of the API was designed to be an event-driven system that makes use of callbacks.
@@
 An example of when an event would be generated, is when the camera detects movement.
-%%Relate it to Categories
 Given that this module was a re-implementation of the previous event system, we concluded that it should be categorised mainly as an enhancive change with the secondary change as groomative.
 Groomative was chosen as the secondary category due to the additional motive of bringing the new functionality into line with the new design.
-%%What she said 
 The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implemention of the new event system.
@@
 The module was then completely re-implemented and re-designed according to the new system design of version 2.0.
-%%Category based on her information
-From the discussion in the interview, it was clear that both of our categorisations were correct. The change was primarily enhancive and secondarily groomative.
+From the discussion in the interview, it was clear that both of our categorisations were correct.
+The change was primarily enhancive and secondarily groomative.
 
 \subsubsection{axhttp}
-
-%%Describe the change 
 The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically send data to web pages.
 The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards, and at the same time, additional functionality was added to the module.
-%%Relate it to Categories
 This change re-implemented an existing module while adhering to the new design of API version 2.0.
 The main categorisation therefore was chosen to be enhancive with groomative as the secondary category.
-%%What she said 
 The interviewee described that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, within the standards of the new design.
-%%Category based on her information
 Our categorisation of enhancive and groomative was therefore correct for this change.
@@
 \subsubsection{ax\_parameter}
-
-%%Describe the change 
 The parameter setting module of the API allowed data and application settings to be saved so that they are not lost if the device is not running.
 This module was re-implemented as ax\_parameter with added functionality and conformance to the new design standards of API version 2.0.
-%2
 Given that this change re-implemented an existing module while also incorporating the new design standards, it has been categorised as being primarily enhancive with a secondary category of groomative.
-%3
 The interviewee clarified that this change was mainly concerned with re-implementing existing functionality, while simultaneously adopting the new standards of version 2.0.
-%4
 Given the information from the interview, we concluded that this change was correctly categorised; the primary intent was enhancive and the secondary intent was groomative.
@@
 \subsubsection{Burst Mode}
-
-%%Describe the change 
 The burst mode feature of the API allowed users to buffer a series of images for greater analysis.
 This feature was deprecated during the transition between version 1.4 and 2.0 and was not re-implemented.
-%%Relate it to Categories
-This change presented itself as a clear example of reductive maintenance, as it was simply removed and without being replaced. We therefore gave no secondary categorisation for this change.
-%%What she said
+This change presented itself as a clear example of reductive maintenance, as it was simply removed and without being replaced.
+We therefore gave no secondary categorisation for this change.
 The interviewee described, that in order to continue using this feature, it would have to be re-implemented.
@@
 Ultimately, the negative effects were not deemed significant enough and thus the function was removed of the API.
-%%Category based on her information
 We can therefore conclude that we correctly categorised this change as reductive and that there are indeed, no secondary categories to describe this change.
@@
 \subsubsection{Example Code}
-
-%%Describe the change 
 The case company included a selection of example programs to assist developers with creating applications.
@@
 The number of example programs and the amount of comments accompanying the code increased, thus improving quality of the examples.
-%%Relate it to Categories
 We therefore concluded that this change was updative, as the example code was updated according to the new API and the new techniques that it utilises.
 We further decided that this change also had a secondary category of reformative.
-%%What she said
 During the interview, it became clear that the improvement of the example code was an important change between the two versions.
@@
 The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.
-%%Category based on her information
 With this information, we concluded that our categorisation was incorrect.
@@
 \subsubsection{Documentation}
-
-%%Describe the change 
 As the API code was updated in version 2.0, the API documentation was updated to correspond with the new code.
 While there were no substantial changes, we found that the documentation is no longer offered as a PDF but is instead only offered as HTML.
-%%Relate it to Categories
 We categorised this change as being updative with a reformative secondary category for the reasons that the change only updated the documentation to reflect the recent changes in version 2.0.
-%%What she said
 This sentiment was shared by the interviewee; the documentation was only changed according to the current workings of the API and how the new modules interact with each other.
-%%Category based on her information
 We can therefore say that our categorisations were correct, the change was updative and reformative.
 
-%!!!Re-write this, don't say no information etc
-
 \subsubsection{Interfaces}
-
-%%Describe the change 
 Version 1.4 of the API allowed direct access to the headers of each module available in the API.
 Version 2.0 changed this by including interfaces through which functionality is accessed.
-This design change has had an effect on the whole API, as it has changed the structure of modules, but not the functionality of them.
-%%Relate it to Categories
-We therefore concluded that this change would be best categorised as  groomative.
+This design change has had an effect on the whole API, as it has changed the structure of modules, but not the functionality of them.We therefore concluded that this change would be best categorised as  groomative.
 The secondary category was categorised as preventive, as the change could be seen as an attempt to reduce future maintenance.
-%%What she said
 The interview provided further insight into the reasoning behind this design change.
@@
 Furthermore, the re-design would hopefully avoid future maintenance, while also allowing the system to be easily extended.
-%%Category based on her information
 Taking this information into account, we concluded that our categorisation was incorrect.
@@
 \subsubsection{Error Handling}
-
-%%Describe the change 
 A substantial change included in version 2.0 was the addition of header files, containing enums of error codes.
 While it was not evident how the error handling was implemented prior to version 2.0, we concluded that it had changed, given the addition of the new header files.
-%%Relate it to Categories
 We therefore categorised this change as being primarily preventive, as error handling is preventive by nature.
 Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability.
-%%What she said
 During the interview, it was made clear that the previous error handling was lacking in expressiveness and usability.
 Glib was added to version 2.0 and the error handling functionality that Glib provides was incorporated into the new API design.
-%%Category based on her information
-We therefore concluded that our categorisation for this change was correct. The primary reason for the change was to improve the existing error handling while conforming to the new API standard.
+We therefore concluded that our categorisation for this change was correct.
+The primary reason for the change was to improve the existing error handling while conforming to the new API standard.
 

### 2015-05-06 thesis/paper.tex
Added note to reviewed sections

@@
 
-\section{Results} \label{results}
+\section{Results} \label{results} %Reviewed by JW
 This section will present the findings of our study.
@@
 
-\subsection{RQ1 Results} \label{results_rq1}
+\subsection{RQ1 Results} \label{results_rq1} %Reviewed by JW
 \noindent
@@
 
-\subsubsection{axptz}
+\subsubsection{axptz} %Reviewed by JW
 The Pan, Tilt and Zoom (ptz) module concerns functionality related to manoeuvring the camera, both mechanically and digitally.
@@
 
-\subsubsection{axaudio}
+\subsubsection{axaudio} %Reviewed by JW
 The most important functionality of the camera is to capture and analyse video data, however, some API users require the ability to analyse audio data.
@@
 
-\subsubsection{axstorage}
+\subsubsection{axstorage} %Reviewed by JW
 Prior to the newest version of the API being released, the sole alternative for storing data was to use the Video Management System.
@@
 
-\subsubsection{axserialport}
+\subsubsection{axserialport} %Reviewed by JW
 The addition of axserialport allows API users to connect various devices to the cameras through the use of a serial port.
@@
 
-\subsubsection{axevent}
+\subsubsection{axevent} %Reviewed by JW
 Version 2.0 of the API was designed to be an event-driven system that makes use of callbacks.
@@
 
-\subsubsection{axhttp}
+\subsubsection{axhttp} %Reviewed by JW
 The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically send data to web pages.
@@
 
-\subsubsection{ax\_parameter}
+\subsubsection{ax\_parameter} %Reviewed by JW
 The parameter setting module of the API allowed data and application settings to be saved so that they are not lost if the device is not running.
@@
 
-\subsubsection{Burst Mode}
+\subsubsection{Burst Mode} %Reviewed by JW
 The burst mode feature of the API allowed users to buffer a series of images for greater analysis.
@@
 
-\subsubsection{Example Code}
+\subsubsection{Example Code} %Reviewed by JW
 The case company included a selection of example programs to assist developers with creating applications.
@@
 
-\subsubsection{Documentation}
+\subsubsection{Documentation} %Reviewed by JW
 As the API code was updated in version 2.0, the API documentation was updated to correspond with the new code.
@@
 
-\subsubsection{Interfaces}
+\subsubsection{Interfaces} %Reviewed by JW
 Version 1.4 of the API allowed direct access to the headers of each module available in the API.
@@
 \subsubsection{3\textsuperscript{rd} Party}
+%% REMEMBER TO PROVIDE LINK TO GLIB:::: - https://developer.gnome.org/glib/
 ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
-%% REMEMBER TO PROVIDE LINK TO GLIB:::: - https://developer.gnome.org/glib/
-
 %%Describe the change 
@@
 All modules use glib
-
 The advent of the new API saw the inclusion of new 3\textsuperscript{rd} party libraries.
@@
 These changes potentially make the library much more flexible both for the API designers in terms of features they can provide and for the application developers in terms of applications they can develop.
-
 We therefore gave this change the main categorisation of adaptive with no suitable sub-categories being found.
-
 The architects creating the API decided they wished to use Glib which came about primarily from internal discussions at the company.
 %%Relate it to Categories
-
 Architects decided to use glib, part of an internal decision. 
 Glib (!!!ref to website) was therefore introduced to the new API to help alleviate this 
-
 The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API.
@@
 
-\subsubsection{Error Handling}
+\subsubsection{Error Handling} %Reviewed by JW
 A substantial change included in version 2.0 was the addition of header files, containing enums of error codes.

### 2015-05-06 thesis/paper.tex
Table..... again

@@
 %
+\usepackage{array}
 \usepackage{multirow}
+\usepackage{makecell}
 
@@
 
+  %\begin{tabular}{!{\vrule width 2pt}c|c|c!{\vrule width 2pt}c|c|c%
+
 \begin{table}
        \centering
-       \begin{tabular}[ht]{|c|c|c|c|c|}
-
+       \begin{tabular}[ht]{|c !{\vrule width 1.5pt} c|c|c|c|} 
               \hline
@@
 
-                                   & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \hline    
+                                   & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \Xhline{2\arrayrulewidth}
               Example Code         & U                         & R\textsubscript{ef}       & R\textsubscript{ef}       & U                  \\ \hline

### 2015-05-06 thesis/paper.tex
Review of Discussion

@@
 
-\section{Discussion} %Reviewed by W
-Our results have been provided valuable insight to the motives behind the evolution of an API.
+\section{Discussion} %Reviewed by WJ
+Our results have been provided valuable insight into the motives behind the evolution of an API.
 The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
-Based on the result, we have formulated the subsequent outcomes.
+Based on the results, we have formulated the subsequent outcomes.
 
@@
 \noindent
-\textbf{Adding functionality is a prime driver of API evolution  } %Reviewed by W
+\textbf{Adding functionality is a prime driver of API evolution  } %Reviewed by WJ
 Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
-We found that a vast majority of the changes either added functionality or were direct effects of functionality being added.
-The main driver for these changes was the pressure from the API users, but pressure from the case company developers which utilised the API also contributed.
-This focus upon functionality was also emphasised in part due to a business goal ( "in part due to, sounds weird to me") .
+We found that a vast majority of the changes either added functionality or were direct a direct consequence of functionality being added.
+The main driver for these changes was the pressure from API users, but pressure from the case company developers who utilise the API also contributed.
+This focus upon functionality was also emphasised partially due to a business goal.
 The more features the API can provide, the more applications developers can create for the cameras.
@@
 While maintainability is important, it is not a primary driving factor for change.
-We found that where maintainability changed, functionality was also altered.
-For example, we predicted that the main intents to be enhancive which was correct.
-( " Need to explain what was enhancive") Furthermore, of the changes identified, none were considered to be primarily groomative.
-Groomative motives were only found to be secondary, and never drove the change.
-Changes to the example code is further evidence of this.
+We found that where maintainability changed, functionality had also been added or modified.
+Of the changes identified, none were considered to be primarily groomative.
+Groomative motives were only found to be secondary, and were never the main motive for a change.
+Changes to the example code are an instance of this.
 The example code was updated purely to reflect the changes in functionality and not as a groomative effort.
@@
 \smallskip \noindent
-\textbf{Aiding development of applications  } %Reviewed by W
-Aiding ( "minor detail: is supporting better here?") users of the API to create correct and robust applications is a very important evolution factor for the case company.
-Changes between the versions brought about ( 're-word'?) improvements to error handling, the example code and the way in which the API utilises interfaces.
+\textbf{Aiding development of applications  } %Reviewed by WJ
+Supporting users of the API in creating correct and robust applications is a very important evolution factor for the case company.
+Changes between the versions introduced improvements to error handling, the example code and the way in which the API utilises interfaces.
 This, coupled with removal of unwanted functionality and unsafe operations, has allowed the API to grow and become much more user-friendly.
-As mentioned previously, this could increase the amount of applications being created for the camera and in turn could increase its value ( "change to' : increase the value of them ?").
+As mentioned previously, this could increase the amount of applications being created for the camera and as a consequence, could potentially increase the value of them.
 
 \smallskip \noindent
-\textbf{Removing functionality  } %Reviewed by W
-Previous literature has stated that deprecations should be favoured over removals from API for many reasons, except in specific circumstances.
-The successful removal of the burst function seems to indicate that this advice is well worth following ( "well worth following reads weirdly") ( 'this sentence also contradicts the previous one').
-Indeed, Axis only removed this function from the API after an internal review found that the cost of removing it would outweigh potential drawbacks to ( 'of???') keeping it in the API.
-( 'this sentence is weird', "and remove the indeed") It is ( 'change to We therefore recommend') therefore recommended to only remove something if the effects of removing it have been well investigated and that the removal is rather small in scale.
-( "instead of saying  small in scale i think we should explain that they should be made in increments and only a few at once")
+\textbf{Removing functionality  } %Reviewed by WJ
+Previous literature has stated that deprecations are the most common technique to used remove support for specific functionality.
+Removals are only suggested in specific circumstances.
+The successful removal of the burst function seems to indicate that under the correct circumstances, removing small unwanted functionality is a good alternative to deprecation.
+The case company only removed this function from the API after an internal review found that the cost of removing it would outweigh potential drawbacks of keeping it in the API.
+We therefore recommended to only remove parts of an API if the effect of the removal has been thoroughly investigated and that the removals happen incrementally and slowly.
 
 \smallskip \noindent
-\textbf{Updative changes do not drive change  } %Reviewed by W
-Changes to documentation and example code are important, especially if the API is drastically changing between versions.
-However, these updative changes are drivers themselves, rather, they make up part of a larger change as a whole.
-( "this whole section has to be re-written.
-We can't refer to them as updative changes since the nature of updative changes are reactive.
-instead refer to them as changes to !code e.g.
-documentation, example code etc.")
-%^Probably needs more to it?
+\textbf{Updative changes do not drive change  } %Reviewed by WJ
+The intent to update example code and documentation was described by the interviewee to be an important change between version 1.4 and 2.0.
+While important for the APIs usability, it was not a driving factor of change itself.
+The changes to the APIs design and functionality caused the need to update the documentation and example code.
 
 \smallskip \noindent
-\textbf{Hardware was not a driving factor  } %Reviewed by W
-Interestingly ( "remove interestingly") , we found that hardware ( "have to explain in what regard we 'expected' hardware to be a driver e.g.
-updates to hardware, the release of new cameras")) was not a direct driver of change.
-Initially, we had thought ( "rephrase had thought...
-anticipated?
-thought sounds like we guessed" (or maybe say "Our initial expectaitions were")) that it would be one of the strongest drivers of change ( "new sentence here"), for example, new versions of hardware become available or new hardware is added to the camera requiring something in the API to access it.
-This does seem to suggest that the hardware for the camera is sufficiently stable such that it does not require changes and that those changes do not need to be ( "change 'not need to be' to 'are not'?") reflected in new API versions.
+\textbf{Hardware was not a driving factor  } %Reviewed by WJ
+Our initial expectations included the view that changes to hardware would be one of the strongest driving factors of API evolution.
+For example, new cameras are created or new hardware is added to an existing camera, requiring updates to the API to allow use of the new features.
+However, after analysing the changes and from the information gathered in the interview, we discovered that hardware has played a minimal role in the evolution of the API.
+
+%Save this for conclusion? Or leave it here?
+%While out of the scope of our research, it might be interesting to investigate if this trend occurs in other platform specific APIs.
 
@@
 \noindent
-\textbf{Functionality is reverse engineerable  } %Reviewed by W
-All changes which main motive were to either add or remove functionality were accurately predicted.
+\textbf{Functionality is reverse engineerable  } %Reviewed by WJ
+All changes which main motive were to either (``all changes whose main motive was to - Or something similar'') add or remove functionality were accurately predicted.
 These changes were the most major ones, and it was expressed during the interview that these types of changes main driving factor behind the development of the new version.
-In summary, 11 out of a total 13 changes were correctly predicted.
+In summary, 11 out of a total 13 (``Write out eleven and thirteen?'') changes were correctly predicted.
 It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted.
-This supports that such changes have a clearer intent and are perhaps more well-defined.
+This supports (``Meant to add something here?'') that such changes have a clearer intent and are perhaps more well-defined.
 
@@
 \textbf{``Structural'' reverse engineerable to a lesser extent} %Reviewed by W
-3 out of 5 changes which did not add functionality, but rather were introduced to redcue complexity and increase quality were correctly predicted.
-The two changes which were incorrectly predicted were wrong because the main motivation was mixed up with the secondary intent ( "re-phrase").
+3 out of 5 (``Three out of five'') changes which did not add functionality, but rather were introduced to reduce complexity and increase quality were correctly predicted.
+The two changes which were incorrectly predicted were wrong because the main motivation was mixed up (``confused'') with the secondary intent ( "re-phrase").
 This shows that although the prediction was incorrect, the general reasoning was correct.
-Our predictions were accurate enough to allow us to form a reliable conlusion which created a good means for discussion with the company ( "re-phrase").
+Our predictions were accurate enough to allow us to form a reliable conclusion which created a good means for discussion with the company (``which provided valuable discussion with the company ''( "re-phrase").
 
@@
 Sufficient evidence was found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System to establish that they apply to APIs.
-The most major explanation for this that a large part of the introduced changes were related to functionality.
+The most major (``the most prominent?
+the most important'') explanation for this (``is'') that a large part of the introduced changes were related to functionality.
 It is especially interesting to note that the laws of Self Regulation and Conservation of Familiarity perfectly match the API explored in this paper.
+(``in what way do they match?
+Maybe explain this a little'')
 
@@
 The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that the extent to which they apply might not be as significant for APIs compared to other types of systems.
-The reason that this doubt exists is that these motivations were only secondary to the motivations of increased functionality.
-An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} might overshadow (!!!wording) the need to increase simplicity and quality.
+The reason that this doubt exists is (``because'')that these motivations were only secondary to the motivations of increased functionality.
+An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} might overshadow (``outweigh, dwarfs, rules out'') (!!!wording) the need to increase(``Improve'') simplicity and quality.
 
@@
 \textbf{One law does not apply  }
-Strong evidence was found which suggests that the law of Conservation of Organisational Stability does not apply to APIs.
+Strong evidence was found which suggests (``to suggest'') that the law of Conservation of Organisational Stability does not apply to APIs.
 Our results not only show that the law is not true for APIs, but that the opposite of what the law states is true for APIs.
 This is supported by the consensus in literature of the negative effects caused by modifications to APIs \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
-The results from our study also showed that the reluctancy to change APIs causes the releases of new versions to be few and sporadic.
+The results from our study also showed that the reluctancy (``that reluctance'') to change APIs causes the releases of new versions to be few and sporadic.
 
@@
 Especially interesting results were found in regards to the law of Feedback System.
-The importance of having a structured and developed feedback loop was stressed during the interview, and it was also expressed as one of the main points of improvement.
-This suggests that including feedback from more sources and making use of this feedback should be done more when developing an API.
+The importance of having a structured and developed feedback loop was stressed during the interview and it was also expressed as one of the main points of improvement.
+This suggests that including feedback from more sources and making use of this feedback (``when / where?
+if we want to be specific'') should be done (``performed or something other than done'') more when developing an API.
 

### 2015-05-06 thesis/paper.tex
Review disc rq2

@@
 
-  %\begin{tabular}{!{\vrule width 2pt}c|c|c!{\vrule width 2pt}c|c|c%
-
 \begin{table}
@@
 
-\section{Discussion} %Reviewed by WJ
-Our results have been provided valuable insight into the motives behind the evolution of an API.
+\section{Discussion}  have been provided valuable insight into the motives behind the evolution of an API.
 The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
@@
 \noindent
-\textbf{Adding functionality is a prime driver of API evolution  } %Reviewed by WJ
+\textbf{Adding functionality is a prime driver of API evolution  } 
 Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
@@
 \smallskip \noindent 
-\textbf{Maintainability does not drive change  } %Reviewed by W 
+\textbf{Maintainability does not drive change  }  
 While maintainability is important, it is not a primary driving factor for change.
@@
 \smallskip \noindent
-\textbf{Aiding development of applications  } %Reviewed by WJ
+\textbf{Aiding development of applications  } 
 Supporting users of the API in creating correct and robust applications is a very important evolution factor for the case company.
@@
 \smallskip \noindent
-\textbf{Removing functionality  } %Reviewed by WJ
+\textbf{Removing functionality  } 
 Previous literature has stated that deprecations are the most common technique to used remove support for specific functionality.
@@
 \smallskip \noindent
-\textbf{Updative changes do not drive change  } %Reviewed by WJ
+\textbf{ "Updative" changes do not drive change  } 
 The intent to update example code and documentation was described by the interviewee to be an important change between version 1.4 and 2.0.
@@
 \smallskip \noindent
-\textbf{Hardware was not a driving factor  } %Reviewed by WJ
+\textbf{Hardware was not a driving factor  } 
 Our initial expectations included the view that changes to hardware would be one of the strongest driving factors of API evolution.
@@
 \noindent
-\textbf{Functionality is reverse engineerable  } %Reviewed by WJ
-All changes which main motive were to either (``all changes whose main motive was to - Or something similar'') add or remove functionality were accurately predicted.
+\textbf{Functionality is reverse engineerable  } 
+All changes whose main motive was to either add or remove functionality were accurately predicted.
 These changes were the most major ones, and it was expressed during the interview that these types of changes main driving factor behind the development of the new version.
-In summary, 11 out of a total 13 (``Write out eleven and thirteen?'') changes were correctly predicted.
+In summary, eleven out of a total thirteen changes were correctly predicted.
 It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted.
-This supports (``Meant to add something here?'') that such changes have a clearer intent and are perhaps more well-defined.
+This supports the fact that such changes have a clearer intent and are perhaps more well-defined.
 
 \smallskip \noindent
-\textbf{``Structural'' reverse engineerable to a lesser extent} %Reviewed by W
-3 out of 5 (``Three out of five'') changes which did not add functionality, but rather were introduced to reduce complexity and increase quality were correctly predicted.
-The two changes which were incorrectly predicted were wrong because the main motivation was mixed up (``confused'') with the secondary intent ( "re-phrase").
-This shows that although the prediction was incorrect, the general reasoning was correct.
-Our predictions were accurate enough to allow us to form a reliable conclusion which created a good means for discussion with the company (``which provided valuable discussion with the company ''( "re-phrase").
+\textbf{``Structural'' reverse engineerable to a lesser extent} 
+Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality were correctly predicted.
+The two changes which were incorrectly predicted were wrong because the main motivation was confused with the secondary intent.
+This shows that, although the prediction was incorrect, the general reasoning was correct.
+Our predictions were accurate enough to allow us to form a reliable conclusion which provided valuable discussion with the case company.
 
@@
 Sufficient evidence was found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System to establish that they apply to APIs.
-The most major (``the most prominent?
-the most important'') explanation for this (``is'') that a large part of the introduced changes were related to functionality.
-It is especially interesting to note that the laws of Self Regulation and Conservation of Familiarity perfectly match the API explored in this paper.
-(``in what way do they match?
-Maybe explain this a little'')
+The most prominent explanation for this is that a large part of the introduced changes were related to functionality.
+It is especially interesting to note that the laws of Self Regulation and Conservation of Familiarity accurately match the API explored in this paper.
 
@@
 The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that the extent to which they apply might not be as significant for APIs compared to other types of systems.
-The reason that this doubt exists is (``because'')that these motivations were only secondary to the motivations of increased functionality.
-An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} might overshadow (``outweigh, dwarfs, rules out'') (!!!wording) the need to increase(``Improve'') simplicity and quality.
+The reason that this doubt exists is because these motives were only secondary to the motives of increased functionality.
+An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} might dominate the need to improve simplicity and quality.
 
@@
 \textbf{One law does not apply  }
-Strong evidence was found which suggests (``to suggest'') that the law of Conservation of Organisational Stability does not apply to APIs.
+Strong evidence was found to suggest that the law of Conservation of Organisational Stability does not apply to APIs.
 Our results not only show that the law is not true for APIs, but that the opposite of what the law states is true for APIs.
 This is supported by the consensus in literature of the negative effects caused by modifications to APIs \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
-The results from our study also showed that the reluctancy (``that reluctance'') to change APIs causes the releases of new versions to be few and sporadic.
+The results from our study also revealed that reluctance to change APIs causes the releases of new versions to be few and sporadic.
 
@@
 The importance of having a structured and developed feedback loop was stressed during the interview and it was also expressed as one of the main points of improvement.
-This suggests that including feedback from more sources and making use of this feedback (``when / where?
-if we want to be specific'') should be done (``performed or something other than done'') more when developing an API.
+This suggests that including feedback from more sources and using this feedback to improve the evolution process should be a consideration for APIs.
 

### 2015-05-06 thesis/paper.tex
Removed comment
Changes to meth and comment in discussion

@@
 %Intro to code inspection
-The data were collected primarily through inspections of the source code and the archival analysis of accompanying  documentation.
+The data were collected primarily through inspections of the source code and the archival analysis of the accompanying documentation.
 The source code was comprised of two versions of an API which the company had developed.
-An older version (1.4) which is currently released and a newer version which has recently been deployed (2.0).
+An older version, 1.4, which is currently released and a newer version, 2.0, which has recently been deployed.
 Each version of the API had its own respective documentation.
@@
 Once we had identified the changes, we inspected the documentation and the code itself to determine if there was a reason for the change, for example, if a given function had been labelled deprecated between versions.
-These changes were then categorised by new changes, updates or re-implementations, removals and general trends.
-The collected data were input into tables and spreadsheets, according to the API version.
+Similar changes will be grouped together based on commonalities between them.
+(!!!reword nicely)
 
@@
 After the initial source code inspection had been performed, interviews were conducted.
-The main purpose of these was to validate our findings during the code inspection with the designers of the APIs.
+The main purpose of the interviews was to validate our findings during the code inspection with the designers of the APIs.
 Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection.
@@
 %Description of code analysis
-More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{chapin2001types} the motive of the change corresponded to.
-The data were then mapped and coded to the laws presented by \cite{lehman1980programs}.
-The codes were then analysed from a high-level point of view, the main goal of which was to identify trends in the codes.
-The final step involved analysis of these trends and it was during this stage the hypotheses were generated and formulated.
-The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.
+More specifically, the approach undertaken was divided into three steps where the changes were first categorised based by following the decision tree for types \cite{chapin2001types}.
+The changes were then mapped according to the laws presented by \cite{lehman1980programs}.
+The changes were then analysed from a high-level point of view, the main goal of which was to identify trends in the changes.
+The final step involved analysis of both the trends and the changes.
+During this stage the hypotheses were generated and formulated.
+The same approach was taken to reduce the risks of research bias and human error in the data collection was also performed during results analysis.
 
@@
 
-%Save this for conclusion? Or leave it here?
-%While out of the scope of our research, it might be interesting to investigate if this trend occurs in other platform specific APIs.
-
 \subsection{Discussion RQ1.1}
@@
 
+              Interesting that hardware did not drive change. Could be studied further in a new study to see if this applies to platform specific APIs in general?
+
               Obvious benefit for Axis is that the more features == more applications == higher value for their camera.

### 2015-05-06 thesis/paper.tex
beef titles

@@
 
-\section{Discussion}  have been provided valuable insight into the motives behind the evolution of an API.
+\section{Discussion}
+Our results have provided valuable insight into the motives behind the evolution of an API.
 The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
@@
 \noindent
-\textbf{Adding functionality is a prime driver of API evolution  } 
+\textbf{Functionality is a prime driver of API evolution  } 
 Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
@@
 \smallskip \noindent
-\textbf{Aiding development of applications  } 
+\textbf{Standardising application development  } 
 Supporting users of the API in creating correct and robust applications is a very important evolution factor for the case company.
@@
 \smallskip \noindent
-\textbf{ "Updative" changes do not drive change  } 
+\textbf{Documentation does not drive change  } 
 The intent to update example code and documentation was described by the interviewee to be an important change between version 1.4 and 2.0.
@@
 \smallskip \noindent
-\textbf{Hardware was not a driving factor  } 
+\textbf{Hardware is not a driving factor  } 
 Our initial expectations included the view that changes to hardware would be one of the strongest driving factors of API evolution.
@@
 \smallskip \noindent
-\textbf{``Structural'' reverse engineerable to a lesser extent} 
+\textbf{Design changes are reverse engineerable to some extent} 
 Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality were correctly predicted.
@@
 \smallskip \noindent
-\textbf{Two laws kinda apply  }
+\textbf{Two laws apply to a certain extent  }
 The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that the extent to which they apply might not be as significant for APIs compared to other types of systems.
 The reason that this doubt exists is because these motives were only secondary to the motives of increased functionality.
-An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} might dominate the need to improve simplicity and quality.
+An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{henning2007api} \cite{mcdonnell2013empirical} \cite{robbes2012developers} might dominate the need to improve simplicity and quality.
 
 \smallskip \noindent
-\textbf{One law does not apply  }
+\textbf{One law is not applicable  }
 Strong evidence was found to suggest that the law of Conservation of Organisational Stability does not apply to APIs.
 Our results not only show that the law is not true for APIs, but that the opposite of what the law states is true for APIs.
-This is supported by the consensus in literature of the negative effects caused by modifications to APIs \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
+This is supported by the consensus in literature of the negative effects caused by modifications to APIs \cite{google_talk} \cite{henning2007api} \cite{mcdonnell2013empirical} \cite{robbes2012developers}.
 The results from our study also revealed that reluctance to change APIs causes the releases of new versions to be few and sporadic.

### 2015-05-06 thesis/paper.tex
Review disc

@@
 \section{Discussion}
-Our results have provided valuable insight into the motives behind the evolution of an API.
+Our results have provided valuable insight into the motives behind the evolution of APIs.
 The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
@@
 Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
-We found that a vast majority of the changes either added functionality or were direct a direct consequence of functionality being added.
+We found that a vast majority of the changes either added functionality or were a direct consequence of increased functionality.
 The main driver for these changes was the pressure from API users, but pressure from the case company developers who utilise the API also contributed.
@@
 While maintainability is important, it is not a primary driving factor for change.
-We found that where maintainability changed, functionality had also been added or modified.
+We found that where maintainability changed ( 'maintainability doesnt change'), functionality had also been added or modified.
 Of the changes identified, none were considered to be primarily groomative.
@@
 \textbf{Removing functionality  } 
-Previous literature has stated that deprecations are the most common technique to used remove support for specific functionality.
+Previous literature has suggested that deprecating functionality is the most common technique used to remove support for specific functionality.
 Removals are only suggested in specific circumstances.
-The successful removal of the burst function seems to indicate that under the correct circumstances, removing small unwanted functionality is a good alternative to deprecation.
-The case company only removed this function from the API after an internal review found that the cost of removing it would outweigh potential drawbacks of keeping it in the API.
-We therefore recommended to only remove parts of an API if the effect of the removal has been thoroughly investigated and that the removals happen incrementally and slowly.
+The successful removal of the burst function seems to indicate that under the correct circumstances, removing specific functionality is an alternative that should be considered.
+The case company removed this function from the API, after an internal review found that the potential negative effect the removal could have, would be less impactful than further maintenance of the function.
+We therefore recommend to remove functionality of an API if the effect of the removal has been thoroughly investigated and that the removals happen incrementally.
 
@@
 While important for the APIs usability, it was not a driving factor of change itself.
-The changes to the APIs design and functionality caused the need to update the documentation and example code.
+The changes to the APIs' design and functionality caused the need to update the documentation and example code.
 
@@
 Our initial expectations included the view that changes to hardware would be one of the strongest driving factors of API evolution.
-For example, new cameras are created or new hardware is added to an existing camera, requiring updates to the API to allow use of the new features.
+One example could be if new cameras are created or new hardware is added to an existing camera, which would require updates to the API to allow use of the new features.
 However, after analysing the changes and from the information gathered in the interview, we discovered that hardware has played a minimal role in the evolution of the API.
@@
 All changes whose main motive was to either add or remove functionality were accurately predicted.
-These changes were the most major ones, and it was expressed during the interview that these types of changes main driving factor behind the development of the new version.
-In summary, eleven out of a total thirteen changes were correctly predicted.
+These changes were the most significant and it was expressed during the interview that these types of changes (``were the?'') main driving factor(``s'') behind the development of the new version.
+In summary, eleven out of a total (``of'') thirteen changes were correctly predicted.
 It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted.
@@
 \textbf{Design changes are reverse engineerable to some extent} 
-Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality were correctly predicted.
-The two changes which were incorrectly predicted were wrong because the main motivation was confused with the secondary intent.
+Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality, were correctly predicted.
+The two changes which were incorrectly predicted were wrong (``inaccurate?'') because the main motivation was confused with the secondary intent.
 This shows that, although the prediction was incorrect, the general reasoning was correct.
@@
 \textbf{Two laws apply to a certain extent  }
-The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that the extent to which they apply might not be as significant for APIs compared to other types of systems.
-The reason that this doubt exists is because these motives were only secondary to the motives of increased functionality.
+The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that (``don't need that'') the extent to which they apply might not be as significant for APIs compared to other types of systems.
+The reason that this doubt exists is because these motives were only (``do you need only?'') secondary to the motives of increased functionality.
 An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{henning2007api} \cite{mcdonnell2013empirical} \cite{robbes2012developers} might dominate the need to improve simplicity and quality.

### 2015-05-06 thesis/paper.tex
More reviewing of discussion

@@
 \section{Discussion}
-Our results have provided valuable insight into the motives behind the evolution of APIs.
+Our results have provided valuable insight into the motives behind the evolution of an API.
 The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
@@
 Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
-We found that a vast majority of the changes either added functionality or were a direct consequence of increased functionality.
+We found that a vast majority of the changes either added functionality or were direct a direct consequence of functionality being added.
 The main driver for these changes was the pressure from API users, but pressure from the case company developers who utilise the API also contributed.
@@
 While maintainability is important, it is not a primary driving factor for change.
-We found that where maintainability changed ( 'maintainability doesnt change'), functionality had also been added or modified.
+We found that where maintainability changed, functionality had also been added or modified.
 Of the changes identified, none were considered to be primarily groomative.

### 2015-05-06 thesis/paper.tex
Fixed suggestions

--- 2015-05-06 thesis/paper.tex
@@
 While maintainability is important, it is not a primary driving factor for change.
-We found that where maintainability changed ( 'maintainability doesnt change'), functionality had also been added or modified.
+We found that where changes that effected maintainability, functionality had also been added or modified.
 Of the changes identified, none were considered to be primarily groomative.
@@
 All changes whose main motive was to either add or remove functionality were accurately predicted.
-These changes were the most significant and it was expressed during the interview that these types of changes (``were the?'') main driving factor(``s'') behind the development of the new version.
-In summary, eleven out of a total (``of'') thirteen changes were correctly predicted.
+These changes were the most significant and it was expressed during the interview that these types of changes were the main driving factors behind the development of the new version.
+In summary, eleven out of a total of thirteen changes were correctly predicted.
 It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted.
@@
 Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality, were correctly predicted.
-The two changes which were incorrectly predicted were wrong (``inaccurate?'') because the main motivation was confused with the secondary intent.
+The two changes which were incorrectly predicted were inaccurate because the main motivation was confused with the secondary intent.
 This shows that, although the prediction was incorrect, the general reasoning was correct.
@@
 \textbf{Two laws apply to a certain extent  }
-The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but that (``don't need that'') the extent to which they apply might not be as significant for APIs compared to other types of systems.
-The reason that this doubt exists is because these motives were only (``do you need only?'') secondary to the motives of increased functionality.
+The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but the extent to which they apply might not be as significant for APIs compared to other types of systems.
+The reason that this doubt exists is because these motives were secondary to the motives of increased functionality.
 An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{henning2007api} \cite{mcdonnell2013empirical} \cite{robbes2012developers} might dominate the need to improve simplicity and quality.

### 2015-05-06 thesis/paper.tex
reivew disc
Further fixes

@@
 \subsubsection{Continuing Change} %Reviewed by WJ
-The case company described that including new functional content was one of the top priorities for the release of vesrion 2.0.
+The case company described that including new functional content was one of the top priorities for the release of version 2.0.
 This is supported by the characteristic of the changes identified in this study.
@@
 
-%API users should be included in the design process? 
 \smallskip \noindent 

### 2015-05-06 thesis/paper.tex
Notes

@@
 
-\subsection{RQ2 Results} \label{results_rq2}
+\subsection{RQ2 Results} \label{results_rq2} %Reviewed by JW
 \noindent
@@
 
-\section{Discussion}
+\section{Discussion} %Reviewed by JW
 Our results have provided valuable insight into the motives behind the evolution of APIs.
@@
 
-\subsection{Discussion RQ1}
+\subsection{Discussion RQ1} %Reviewed by JW
 
 \noindent
-\textbf{Functionality is a prime driver of API evolution  } 
+\textbf{Functionality is a prime driver of API evolution  }  %Reviewed by JW
 Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
@@
 \smallskip \noindent 
-\textbf{Maintainability does not drive change  }  
+\textbf{Maintainability does not drive change  }  %Reviewed by JW
 While maintainability is important, it is not a primary driving factor for change.
@@
 \smallskip \noindent
-\textbf{Standardising application development  } 
+\textbf{Standardising application development  } %Reviewed by JW%Reviewed by JW
 Supporting users of the API in creating correct and robust applications is a very important evolution factor for the case company.
@@
 \smallskip \noindent
-\textbf{Removing functionality  } 
+\textbf{Removing functionality  } %Reviewed by JW
 Previous literature has suggested that deprecating functionality is the most common technique used to remove support for specific functionality.
@@
 \smallskip \noindent
-\textbf{Documentation does not drive change  } 
+\textbf{Documentation does not drive change  } %Reviewed by JW
 The intent to update example code and documentation was described by the interviewee to be an important change between version 1.4 and 2.0.
@@
 \smallskip \noindent
-\textbf{Hardware is not a driving factor  } 
+\textbf{Hardware is not a driving factor  } %Reviewed by JW
 Our initial expectations included the view that changes to hardware would be one of the strongest driving factors of API evolution.
@@
 \noindent
-\textbf{Functionality is reverse engineerable  } 
+\textbf{Functionality is reverse engineerable  } %Reviewed by JW
 All changes whose main motive was to either add or remove functionality were accurately predicted.
@@
 \smallskip \noindent
-\textbf{Design changes are reverse engineerable to some extent} 
+\textbf{Design changes are reverse engineerable to some extent  }  %Reviewed by JW
 Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality, were correctly predicted.
@@
 \noindent
-\textbf{A majority of the laws apply  }
+\textbf{A majority of the laws apply  } %Reviewed by JW
 Sufficient evidence was found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System to establish that they apply to APIs.
@@
 \smallskip \noindent
-\textbf{Two laws apply to a certain extent  }
+\textbf{Two laws apply to a certain extent  } %Reviewed by JW
 The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but the extent to which they apply might not be as significant for APIs compared to other types of systems.
@@
 \smallskip \noindent
-\textbf{One law is not applicable  }
+\textbf{One law is not applicable  } %Reviewed by JW
 Strong evidence was found to suggest that the law of Conservation of Organisational Stability does not apply to APIs.
@@
 \smallskip \noindent
-\textbf{The importance of a Feedback System  }
+\textbf{The importance of a Feedback System  } %Reviewed by JW
 Especially interesting results were found in regards to the law of Feedback System.

### 2015-05-06 thesis/paper.tex
tebul

@@
 \usepackage{makecell}
+\usepackage{booktabs}
 
@@
        \centering
-       \begin{tabular}[ht]{|c !{\vrule width 1.5pt} c|c|c|c|} 
-              \hline
+       \begin{tabular}[ht]{c !{\vrule width 1.5pt} c|c !{\vrule width 1.5pt} c|c} 
+              \toprule
 
-              \multirow{2}{*}{\textbf{Change}}          & \multicolumn{2}{c|}{\textbf{Main}}       & \multicolumn{2}{c|}{\textbf{Sub}}        \\ \cline{2-5}
+              \multirow{2}{*}{\textbf{Change}}          & \multicolumn{2}{c !{\vrule width 1.5pt} }{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Sub}}        \\ \cline{2-5}
 
                                    & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \Xhline{2\arrayrulewidth}
-              Example Code         & U                         & R\textsubscript{ef}       & R\textsubscript{ef}       & U                  \\ \hline
-              Documentation        & U                         & U                         & R\textsubscript{ef}       & R\textsubscript{ef} \\ \hline
+              Example Code         & U                         & R\textsubscript{f}        & R\textsubscript{f}        & U                  \\ \hline
+              Documentation        & U                         & U                         & R\textsubscript{f}        & R\textsubscript{f} \\ \hline
               Interfaces           & G                         & P                         & P                         & G                  \\ \hline
@@
               ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
-              Burst Mode           & R\textsubscript{ed}       & R\textsubscript{ed} &     N/A                         & N/A                \\ \hline
+              Burst Mode           & R\textsubscript{d}        & R\textsubscript{d}        & N/A                       & N/A                \\
 
+              \bottomrule
        \end{tabular}

### 2015-05-06 thesis/paper.tex
table

@@
                                    & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \Xhline{2\arrayrulewidth}
-              Example Code         & U                         & R\textsubscript{f}        & R\textsubscript{f}        & U                  \\ \hline
-              Documentation        & U                         & U                         & R\textsubscript{f}        & R\textsubscript{f} \\ \hline
-              Interfaces           & G                         & P                         & P                         & G                  \\ \hline
-              Error Handling       & P                         & P                         & G                         & G                  \\ \hline
-              3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
+              axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
               axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
-              axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
               axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
@@
               ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
-              Burst Mode           & R\textsubscript{d}        & R\textsubscript{d}        & N/A                       & N/A                \\
+              Burst Mode           & R\textsubscript{d}        & R\textsubscript{d}        & N/A                       & N/A                \\ \hline
+              Example Code         & U                         & R\textsubscript{f}        & R\textsubscript{f}        & U                  \\ \hline
+              Documentation        & U                         & U                         & R\textsubscript{f}        & R\textsubscript{f} \\ \hline
+              Interfaces           & G                         & P                         & P                         & G                  \\ \hline
+              3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
+              Error Handling       & P                         & P                         & G                         & G                  \\
 
@@
        \end{tabular}
-       \caption{Category }
+       \caption{Categorisation of Changes }
        \label{table:categories}

### 2015-05-07 thesis/paper.tex
Review abstract -conclusion

@@
 John Burchell\\
-       \affaddr{Computer Science and Engineering}\\
+%       \affaddr{Computer Science and Engineering}\\
        \affaddr{University of Gothenburg}\\
@@
 William Granli\\
-       \affaddr{Computer Science and Engineering}\\
+%       \affaddr{Computer Science and Engineering}\\
        \affaddr{University of Gothenburg}\\
@@
 \alignauthor Imed Hammouda\titlenote{Co-author}\\
-       \affaddr{Computer Science and Engineering}\\
+%       \affaddr{Computer Science and Engineering}\\
        \affaddr{University of Gothenburg}\\
@@
 % 4th 
-\alignauthor Eric Knauss\titlenote{Co-author}\\
-       \affaddr{Computer Science and Engineering}\\
+\alignauthor Er ic Knauss\titlenote{Co-author}\\
+%       \affaddr{Computer Science and Engineering}\\
        \affaddr{University of Gothenburg}\\
@@
 
-\textbf{Background  } 
-Studies of the motives and drivers behind modifications to APIs have been done before, but platform APIs are, so far, unexplored.
-Previous work has also not studied APIs from the perspective of widely recognised software evolution theories, such as the Types of Software Evolution and Software Maintenance and Lehman's laws of software evolution.
+\textbf{Background  } %Done
+The driving forces of modifications to APIs have been investigated before, however, platform APIs are, until now, unexplored.
+Previous studies have not considered APIs from the perspective of well-established software evolution theories.
 
 \smallskip \noindent
-\textbf{Objective  } 
-This study explored how companies actively drive changes to APIs and how APIs evolve from a passive point of view.
-The aim was also to test how well we could reverse engineer these change decisions.
-The goal was to study these factors by relating them to existing software evolution theories.
+\textbf{Objective  } %Done
+In this study, we explore how companies actively evolve their APIs and 'how APIs evolve from a passive point of view'.
+We also aim to evaluate to what extent we are able to reverse engineer these evolutionary change decisions.
+The goal is to study these factors by evaluating them against existing software evolution theories.
 
 \smallskip \noindent
-\textbf{Method  }
-This case study was conducted by investigating the changes between two versions in a platform API and its documentation, and by interviewing the architects of the API.
-The changes were analysed from a qualitative and investigative point of view.
+\textbf{Method  } %Done
+This case study was conducted by analysing the changes between two versions of a platform API and its documentation.
+The results were analysed from a qualitative and investigative perspective, and were then reviewed and validated with the architects of the API.
 
 \smallskip \noindent
-\textbf{Results  }
-This study identified 13 majors changes to the API.
-The study concluded that the most major driving force for the evolution of APIs is the drive for new functionality and that change decisions to a large extent can be reverse engineered.
-It was also found that 7 out of 8 of Lehman's laws were applicable to APIs.
+\textbf{Results  } %Done
+We identified thirteen major changes which were introduced in the new version of the API.
+We concluded that the dominant driving force of the API evolution is demand for new functionality and that change decisions, to a large extent, are reverse engineerable.
+We also found that long-established software evolution laws were largely applicable to APIs.
 

### 2015-05-07 thesis/paper.tex
intro review

@@
 The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
-The most common changes to APIs occur from refactoring \cite{dig2005role} \cite{xing2006refactoring}.
+Refactoring is the most common change that APIs undergo \cite{dig2005role} \cite{xing2006refactoring}.
 %Software Evolution 
@@
 Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
-There are, however, no studies that attempt to map the motives behind changes to existing software evolution theories, such as the four categories of maintenance \cite{lientz1980software}.
+There are, however, no studies that attempt to map the motives behind changes to existing software evolution theories, such as the types of software evolution and software maintenance activities \cite{chapin2001types}.
 The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
-To the best of our knowledge, no studies that explore the motives behind or the effects of API evolution have previously been performed on embedded platform APIs.
-Reverse engineering design decisions is a challenging yet interesting problem.
+To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.
+
+%Purpose
+Modifications to deployed APIs may negatively impact its users.
+It is therefore important to investigate why these changes occur.
+Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs.
+Before the industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.
+
+%Method
+In order to achieve this, an exploratory case study will be undertaken to investigate the underlying motives behind changes to APIs.
+Empirical analysis of the changes between two major versions of an API will be undertaken, following which, an interview with the achitects will be used to validate the findings of our analysis.
+
+%Can't find a place for this - it's repeated in the Purpose
+%Reverse engineering design decisions is a challenging yet interesting problem.
 The better we can understand why changes occur and what problems they are trying to solve, the better we can design around these problems to avoid them cropping up in the future.
-
-%Purpose (and a bit of problem statement)
-%%****NEW*****
-Making changes to existing APIs can have a negative impact upon the users of those APIs.
-It is therefore important to understand why these changes occur.
-Understanding the motives behind the changes could help API designers prevent or avoid potential changes to their APIs.
-In order to achieve this and to provide immediate benefit to industry, an exploratory case study will be undertaken to investigate the underlying motives behind API changes of an existing API.
-Empirical analysis of changes between two major versions of an API will be undertaken, following which an interview with the architects will be used to verify the findings of our study.
-%%****^NEW^****
-
-%Old
-Due to the negative implications that modifications to APIs cause for its users, it is important to understand why changes to them occur.
-If most common pitfalls are known before the development of new APIs begin, these mistakes can be mitigated.
-Before the industry can make use of this information, we must also critically assess to what degree we can trace such motives.
-To achieve this, we will perform a case study which aims to investigate the underlying factors behind API changes.
-This will be achieved by empirically analysing the changes between two versions of an API.
-Subsequently, the designers of the API will be interviewed and asked to verify the accuracy of our findings.
-%Old
 
@@
 The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the background and previously published work that is related to our study.
-Section \ref{case_company_description} describes the case company and how it was selected.
+Section \ref{case_company_description} describes the case company and the API which was studied.
 A description of our methodology is introduced in Section \ref{methodology}.
-In Section \ref{results}, the results of our study are presented and in Section \ref{conclusion}, we discuss the findings of our study.
+In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the findings of our study.
+In Secton \ref{conclusion} we suggest the potential impact of our work and advise future work.
 
@@
 
-\section{Discussion} %Reviewed by JW
+\section{Discussion} \label{discussion}%Reviewed by JW
 Our results have provided valuable insight into the motives behind the evolution of APIs.

### 2015-05-07 thesis/paper.tex
Updated related work etc

--- 2015-05-07 thesis/paper.tex
@@
 %Structure of the paper
-The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the background and previously published work that is related to our study.
+The sections following the Introduction are structured thusly: In Section \ref{existing_literature}, we present the background and previously published work that is related to our study.
 Section \ref{case_company_description} describes the case company and how it was selected.
@@
 \subsection{API Design} \label{api_design}
-API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}.
-Examples of such decisions are whether to use the factory pattern or constructors to create objects, or if the API should display errors during compilation or runtime \cite{stylos2006comparing}.
-More trivial design problems, such as, assigning names to API features and difficulty in naming types also have a large impact on the usability of the API \cite{shi2011empirical}.
+API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}.
+Examples of such decisions include whether or not to make use of the factory pattern or if an API should display errors only at compilation or only at runtime \cite{stylos2006comparing}.
+More trivial design problems, such as assigning names to API features or correctly naming user defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}.
 When facing such design decisions, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
-One of the most important qualities in an API is that the intent of the API is clear to the user when, for example, using design patterns, such as the concrete factory pattern \cite{stylos2006comparing} \cite{shi2011empirical}.
-The sum of all design decisions taken during the development of an API will decide the usability of the API.
-Measuring such a factor can be done by measuring the twelve cognitive dimensions which are factors that are impacted by the interaction between the API and the user of it \cite{clarke2004measuring}.
+One of the most important qualities in an API is that the intent of the API is clear to the user, for example, using design patterns \cite{stylos2006comparing} \cite{shi2011empirical}.
+The design decisions reached during development of an API will effect the overall usability of the API, for better or worse.
+Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and the API's user \cite{clarke2004measuring}.
 
@@
 %%Categories of maintenance and types of maintenance
-Software evolution is a field which studies the application of software maintenance activities and processes on software and the resulting, evolved versions of the software.
-The concept of software maintenance has existed since the 1960s.
-Well-known studies from this era established the importance of software maintenance \cite{lientz1980software}.
-One study would go on to have a particularly profound effect on software maintenance by establishing a set of four categories which describe the intents behind change to software \cite{lientz1980software}.
-These categories were refined in a further study, in which the number of categories were increased from four to twelve \cite{chapin2001types}.
-The categories proposed were: Enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training \cite{chapin2001types}.
-Each category describes a type of software maintenance activity which relate to one of three particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}.
-This study also helped to further the distinction between software maintenance and software evolution.
-The study suggested that software maintenance is a part of software evolution and that the two are not interchangeable \cite{chapin2001types}.
+Software evolution is a field that studies the application of software maintenance activities, changes in software processes and the resulting, evolved versions of the software.
+The concept of software maintenance has existed since the 1960s when it was first introduced to the software development community \cite{lientz1980software}.
+A set of four categories describing software maintenance categories \cite{lientz1980software} became the basis upon which twelve new categories were created \cite{chapin2001types}.
+The tweleve categories are: enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training \cite{chapin2001types}.
+Each category describes a software maintenance activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}.
+It has been suggested that software maintenance is a part of software evolution and that the two terms are not interchangeable \cite{chapin2001types}.
 
 %%Lehman's laws (!!!improve later)
-An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}.
-The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
-The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.
+Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman1980programs}.
+The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
+The laws are said to only apply to E-type systems, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.
 
 \subsection{Related Work} \label{related_work}
-Previous studies that have attempted analyse APIs in the context of software evolution have primarily focused on APIs that are a part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}.
-One study \cite{hou2011exploring} attempted to uncover the intents behind the changes made in the AWT and Swing Java libraries.
-They found that the use of a strong architecture was vital in ensuring a successful evolution of the API \cite{hou2011exploring}.
-In their study, the intents were categorised around programming related factors such as reducing coupling or conformance to naming conventions.
+The analysis of APIs in the context of software evolution has primarily focused on APIs that are a part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}.
+Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
 
-One study \cite{dig2005role} investigated three frameworks and one library in which the study found that 80\% of refactoring changes to APIs negatively affected existing applications.
-Refactorings are not the only changes to APIs that can impact existing projects negatively.
-Another study was conducted regarding the changes, which the researchers refer to as ripple effects \cite{robbes2012developers}.
-They found that changes in APIs have an effect upon the entire ecosystem.
-This particular empirical study found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.
+Investigations of three frameworks and one library indicated that 80\% of refactoring changes to APIs negatively affected existing applications \cite{dig2005role}.
+The changes, sometimes referred to as ripple effects \cite{robbes2012developers} indicate that negative effects of changes can propagate throughout a software ecosystem.
+It was found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.
+
+%%Possibly add a paragraph here to
 

### 2015-05-07 thesis/paper.tex

@@
 %Structure of the paper
-The sections following the Introduction are structured thusly: In Section \ref{existing_literature}, we present the background and previously published work that is related to our study.
-Section \ref{case_company_description} describes the case company and how it was selected.
+The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the background and previously published work that is related to our study.
+Section \ref{case_company_description} describes the case company and the API which was studied.
 A description of our methodology is introduced in Section \ref{methodology}.
-In Section \ref{results}, the results of our study are presented and in Section \ref{conclusion}, we discuss the findings of our study.
+In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the findings of our study.
+In Secton \ref{conclusion} we suggest the potential impact of our work and advise future work.
 

### 2015-05-07 thesis/paper.tex
case descr

@@
 \section{Case Company Description} \label{case_company_description}
-The case company is a medium-sized company in the domain of security cameras.
-The company has its headquarters in Lund, Sweden, but it operates worldwide.
+The case company is a company operating in the domain of video surveillance.
+The company has its headquarters in Lund, Sweden with offices in 49 countries worldwide.
 The company is the global market leader in the markets of network cameras and video encoders.
-The company develops embedded software for the security cameras and some of their products are designed to be accessible through APIs that are also developed by the company.
+The develops embedded software for the security cameras.
+The cameras are designed to be accessible through APIs that are developed and maintained by the company.
 
-%Try to get information about the users of the API. Either through Imed, or through the interviews.
+The API analysed in this study has been deployed for several years.
+It was recently updated from version 1.4 to version 2.0, which is the current active version.
+The changes between these two versions is what has been analysed in this study.
+Between the release of 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms.
+The API is used by company partners, which are companies who develop applications for the cameras.
+These applications are, in turn, used by the end-users of the cameras.
+The API is developed for a wide range of camera types that offer different functionality and are used for different purposes.
 
@@
 As such, the goal was to include as many companies as possible in this study.
-
-%Try to motivate why other sampling methods weren't used.
-
-%Info from the interview, add to this section
-Has been released, in the form we looked at (supports that we’re doing a ``real'' case study)
-They have partners which develop applications using their API. These applications are then used by the end-users of the camera.
-
-%%
-Hardware
-The API platform is developed for many different types of cameras. 
-Some have audio, some don’t, for example.
-
-%%Does this paragraph below belong here or somewhere else? Feels a bit odd!    W: Case Company Description I think
-The API itself consisted of two major versions; 1.4 and 2.0.
-There were no intermediate versions between 1.4 and 2.0.
-Version 1.4 was actually the same version as 1.0, just with added build options for other hardware platforms.
-The changes therefore come from the changes between the two major versions.
-Given that there was an apparent ``big bang'' implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.
 

### 2015-05-07 thesis/paper.tex
Spellcheck

@@
 % 4th 
-\alignauthor Er ic Knauss\titlenote{Co-author}\\
+\alignauthor Eric Knauss\titlenote{Co-author}\\
 %       \affaddr{Computer Science and Engineering}\\
@@
 In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the findings of our study.
-In Secton \ref{conclusion} we suggest the potential impact of our work and advise future work.
+In Section \ref{conclusion} we suggest the potential impact of our work and advise future work.
 
@@
 The design decisions reached during development of an API will effect the overall usability of the API, for better or worse.
-Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and the API's user \cite{clarke2004measuring}.
+Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and the user of it \cite{clarke2004measuring}.
 
@@
 A set of four categories describing software maintenance categories \cite{lientz1980software} became the basis upon which twelve new categories were created \cite{chapin2001types}.
-The tweleve categories are: enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training \cite{chapin2001types}.
+The twelve categories are: enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training \cite{chapin2001types}.
 Each category describes a software maintenance activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}.
@@
 Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman1980programs}.
-The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
+The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
 The laws are said to only apply to E-type systems, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.
@@
 %Intro and summary
-This study has been conducted using the case study meth-odology \cite{runeson2009guidelines}.
+This study has been conducted using the case study methodology \cite{runeson2009guidelines}.
 The goal of the study was twofold.
@@
 Groomative was chosen as the secondary category due to the additional motive of bringing the new functionality into line with the new design.
-The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implemention of the new event system.
+The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implementation of the new event system.
 One reason was that the case company was dissatisfied with certain usability aspects of API version 1.4.
@@
 %%Describe the change 
-2.0 utilizes more 3rd party libraries
+2.0 utilises more 3rd party libraries
 axsound, for example, uses alsa
@@
               Greater emphasis should be placed upon communicating with the end users / application developers.
-APIs should be made with maintainability and extendibility in mind as they seem to be what changes the most between versions.
+APIs should be made with maintainability and extensibility in mind as they seem to be what changes the most between versions.
 They should probably improve their feedback system to get more feedback from the API users.
@@
 She does think about who is going to use it and how but nothing in regards to how it affects an ecosystem as a whole.
-Things like allowing embedded webpages for the ACAP allows users to get more information from their system meaning they don’t need to ask for as much help and assistance.
+Things like allowing embedded web pages for the ACAP allows users to get more information from their system meaning they don’t need to ask for as much help and assistance.
 They usually integrate this with the VMS.
@@
 -Relate to 80% refactorings paper and say that we found different results
-*This is an intersting note if we want to compare platform apis and library apis to say that functionality changes more often in platform apis for example
+*This is an interesting note if we want to compare platform APIs and library APIs to say that functionality changes more often in platform APIs for example
 
@@
 
-\section{Acknowledgments}
+\section{Acknowledgements}
 We would like to thank Axis and that project at GU.

### 2015-05-07 thesis/paper.tex
Case description review

@@
 The case company is a company operating in the domain of video surveillance.
-The company has its headquarters in Lund, Sweden with offices in 49 countries worldwide.
+The company has its headquarters located in Lund, Sweden, with offices in 49 countries worldwide.
 The company is the global market leader in the markets of network cameras and video encoders.
-The develops embedded software for the security cameras.
+They develop embedded software for security cameras.
 The cameras are designed to be accessible through APIs that are developed and maintained by the company.
@@
 The changes between these two versions is what has been analysed in this study.
-Between the release of 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms.
+Between the release of 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms (``Bit odd the end of this sentence'')(``version 1.0 to 1.4 only included additional build options and did not include the addition of new functionality'').
 The API is used by company partners, which are companies who develop applications for the cameras.

### 2015-05-07 thesis/paper.tex
review existing lit

@@
 \section{Existing Literature} \label{existing_literature}
-This section will introduce the topics of API design and software evolution and provide a brief review of studies that are directly related to our study.
+This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.
 
 \subsection{API Design} \label{api_design}
-API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}.
+API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}.
 Examples of such decisions include whether or not to make use of the factory pattern or if an API should display errors only at compilation or only at runtime \cite{stylos2006comparing}.
@@
 When facing such design decisions, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
-One of the most important qualities in an API is that the intent of the API is clear to the user, for example, using design patterns \cite{stylos2006comparing} \cite{shi2011empirical}.
-The design decisions reached during development of an API will effect the overall usability of the API, for better or worse.
-Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and the user of it \cite{clarke2004measuring}.
+One of the most important qualities in an API is that the intent of the API is clear to the user, for example, ( "something is missing here") using design patterns \cite{stylos2006comparing} \cite{shi2011empirical}.
+The design decisions reached during development of an API will affect the overall usability of the API, for better or worse ( "too informal?").
+Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.
 
@@
 \subsection{Related Work} \label{related_work}
-The analysis of APIs in the context of software evolution has primarily focused on APIs that are a part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}.
+The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}.
 Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.

### 2015-05-07 thesis/paper.tex
Replaced intro with willy's new intro, added a comment to case company description

@@
 Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
-There are, however, no studies that attempt to map the motives behind changes to existing software evolution theories, such as the four categories of maintenance \cite{lientz1980software}.
+There are, however, no studies that attempt to map the motives behind changes to existing software evolution theories, such as the types of software evolution and software maintenance activities \cite{chapin2001types}.
 The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
-To the best of our knowledge, no studies that explore the motives behind or the effects of API evolution have previously been performed on embedded platform APIs.
-Reverse engineering design decisions is a challenging yet interesting problem.
+To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.
+
+%Purpose
+Modifications to deployed APIs may negatively impact its users.
+It is therefore important to investigate why these changes occur.
+Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs.
+Before the industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.
+
+%Method
+In order to achieve this, an exploratory case study will be undertaken to investigate the underlying motives behind changes to APIs.
+Empirical analysis of the changes between two major versions of an API will be undertaken, following which, an interview with the architects will be used to validate the findings of our analysis.
+
+%Can't find a place for this - it's repeated in the Purpose
+%Reverse engineering design decisions is a challenging yet interesting problem.
 The better we can understand why changes occur and what problems they are trying to solve, the better we can design around these problems to avoid them cropping up in the future.
-
-%Purpose (and a bit of problem statement)
-%%****NEW*****
-Making changes to existing APIs can have a negative impact upon the users of those APIs.
-It is therefore important to understand why these changes occur.
-Understanding the motives behind the changes could help API designers prevent or avoid potential changes to their APIs.
-In order to achieve this and to provide immediate benefit to industry, an exploratory case study will be undertaken to investigate the underlying motives behind API changes of an existing API.
-Empirical analysis of changes between two major versions of an API will be undertaken, following which an interview with the architects will be used to verify the findings of our study.
-%%****^NEW^****
-
-%Old
-Due to the negative implications that modifications to APIs cause for its users, it is important to understand why changes to them occur.
-If most common pitfalls are known before the development of new APIs begin, these mistakes can be mitigated.
-Before the industry can make use of this information, we must also critically assess to what degree we can trace such motives.
-To achieve this, we will perform a case study which aims to investigate the underlying factors behind API changes.
-This will be achieved by empirically analysing the changes between two versions of an API.
-Subsequently, the designers of the API will be interviewed and asked to verify the accuracy of our findings.
-%Old
 

### 2015-05-07 thesis/paper.tex
Case company review

@@
 The case company is a company operating in the domain of video surveillance.
-The company has its headquarters located in Lund, Sweden, with offices in 49 countries worldwide.
+The company's headquarters are located in Lund, Sweden, with offices in 49 countries worldwide.
 The company is the global market leader in the markets of network cameras and video encoders.
@@
 The changes between these two versions is what has been analysed in this study.
-Between the release of 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms (``Bit odd the end of this sentence'')(``version 1.0 to 1.4 only included additional build options and did not include the addition of new functionality'').
+Between the release of 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms.
+Prior to version 1.4 being released, updates were only made to include additional built options and did not include any additional functionality.
 The API is used by company partners, which are companies who develop applications for the cameras.
@@
 
-The case was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}.
+The case company was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}.
 As such, the goal was to include as many companies as possible in this study.

### 2015-05-07 thesis/paper.tex
Fixed related work

@@
 When facing such design decisions, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
-One of the most important qualities in an API is that the intent of the API is clear to the user, for example, ( "something is missing here") using design patterns \cite{stylos2006comparing} \cite{shi2011empirical}.
-The design decisions reached during development of an API will affect the overall usability of the API, for better or worse ( "too informal?").
+One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{stylos2006comparing} \cite{shi2011empirical}.
+The design decisions reached during development of an API will affect the overall usability of the API.
 Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.

### 2015-05-07 thesis/paper.tex
review

@@
 %API Design (and a little bit of ecosystems and a bit of problem statement)
-As the software industry and the open-source movement steadily grow, the number of public APIs is increasing.
+As the software industry and the open-source movement continue to grow, the number of public APIs is steadily increasing.
 APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
@@
 In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the findings of our study.
-In Section \ref{conclusion} we suggest the potential impact of our work and advise future work.
+In Section \ref{conclusion} we propose the potential impact of our work and give suggestions for future work that builds on our research.
 
@@
 More trivial design problems, such as assigning names to API features or correctly naming user defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}.
-When facing such design decisions, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
+When facing such design challanges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
 One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{stylos2006comparing} \cite{shi2011empirical}.

### 2015-05-07 thesis/paper.tex
construct validity

@@
 
-%We must add construct validity.
+\noindent
+\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the research questions around already established and accepted theories \cite{chapin2001types} \cite{lehman1980programs}.
+Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis.
+This means that the evolution of the API was studied during a rather short part of its lifetime ( "rephrase").
+It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes.
+We consider this to be remaining threats to construct validity.
+
+\smallskip \noindent
+\textbf{Internal validity  }
+
+\smallskip \noindent
+\textbf{External validity  }
+
+\smallskip \noindent
+\textbf{Reliability  }
+
+1
+Theories not applying
+Only analysing changes between two version
+Not investigating the implementation of the code (i.e. only headers were analysed)
+
+2
+Counteracted: 
+Triangulation by checking both code, documentation and interviewing.
+
+Remaining: 
+Only interviewing architects. Maybe business ppl need to be invited to find intents.
+Not interviewing partners
+
+3
+The results should be generalisable to a large extent to any API designers
+Should be especially useful for platform/embedded APIs
+
+4
+This threat has bene counteracted by following a well-reputed guide to case studies \cite{runeson}, and by using analysis methods \cite{grounded} which are conventional. 
+The analysis of the data is based around existing theories which should also help reproducability.
+The inteview was semi-structured and largely based around the categories of software maintenance and Lehman's laws, which should help reproducability.
 
@@
        \centering
-       \begin{tabular}[ht]{|l|c|}
-              \hline
+       \begin{tabular}[ht]{l|c}
+              \toprule
 
-              \textbf{Law}                              & \textbf{Applicability}    \\ \hline
+              \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
               Continuing Change                         & True                      \\ \hline
@@
               Declining Quality                         & Kinda                     \\ \hline
-              Feedback System                           & True                      \\ \hline
+              Feedback System                           & True                      \\
+
+              \bottomrule
 

### 2015-05-07 thesis/paper.tex
internal validiyt

@@
 More trivial design problems, such as assigning names to API features or correctly naming user defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}.
-When facing such design challanges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
+When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
 One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{stylos2006comparing} \cite{shi2011empirical}.
@@
 \noindent
-\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the research questions around already established and accepted theories \cite{chapin2001types} \cite{lehman1980programs}.
+\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results the study around already established and accepted theories \cite{chapin2001types} \cite{lehman1980programs}.
 Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis.
@@
 \smallskip \noindent
-\textbf{Internal validity  }
+\textbf{Internal validity  } Internal validity has been acknowledged by analysing the the code and documentation jointly.
+This has contributed to triangulating the results and discovering possible inconsistencies.
+Further triangulation of the results was performed by interviewing the API architect.
+Business-related factors might have had an impact on the evolution of the API, and these were not closely investigated.
+This was not in the scope of the study and would best be investigated in a study complementary to ours.
+The study revealed that the API users were significant to the evolution of the API.
+Since API users were not interviewed, it might be a affecting factor which was left unexplored.
 
@@
 \textbf{Reliability  }
-
-1
-Theories not applying
-Only analysing changes between two version
-Not investigating the implementation of the code (i.e. only headers were analysed)
 
@@
 4
-This threat has bene counteracted by following a well-reputed guide to case studies \cite{runeson}, and by using analysis methods \cite{grounded} which are conventional. 
-The analysis of the data is based around existing theories which should also help reproducability.
-The inteview was semi-structured and largely based around the categories of software maintenance and Lehman's laws, which should help reproducability.
+This threat has been counteracted by following a well-reputed guide to case studies \cite{runeson}, and by using analysis methods \cite{grounded} which are conventional. 
+The analysis of the data is based around existing theories which should also help reproducibility.
+The interview was semi-structured and largely based around the categories of software maintenance and Lehman's laws, which should help reproducibility.
 

### 2015-05-07 thesis/paper.tex
external val

@@
 \smallskip \noindent
-\textbf{External validity  }
+\textbf{External validity  } The results of our study should be highly generalisable similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors.
+Our study should be of special interest to researchers studying platform or embedded APIs.
+The fact that the results of the study are presented in a structured way, by relating them to existing software evolution theories, should further increase the generalisability of our study.
 
@@
 \textbf{Reliability  }
-
-2
-Counteracted: 
-Triangulation by checking both code, documentation and interviewing.
-
-Remaining: 
-Only interviewing architects. Maybe business ppl need to be invited to find intents.
-Not interviewing partners
 

### 2015-05-07 thesis/paper.tex
reliability

@@
 \smallskip \noindent
-\textbf{Reliability  }
-
-3
-The results should be generalisable to a large extent to any API designers
-Should be especially useful for platform/embedded APIs
-
-4
-This threat has been counteracted by following a well-reputed guide to case studies \cite{runeson}, and by using analysis methods \cite{grounded} which are conventional. 
-The analysis of the data is based around existing theories which should also help reproducibility.
-The interview was semi-structured and largely based around the categories of software maintenance and Lehman's laws, which should help reproducibility.
-
-%Internal Validity
-\textit{Internal validity} threats for our study have been greatly reduced by the methodologies we have employed.
-By performing an individual inspection of the API source code, documentation and individual results analysis, internal validity is significantly reduced.
-Triangulation of the results with the use of interviewing the designers is a key step in reducing potential validity threats in our study.
-
-%External Validity
-Regarding \textit{external validity}, generalisability and the appropriateness of our results are at risk.
-In our study we have striven to ensure that our findings will be as useful as possible to others.
-Given that there are some similar studies to ours and that ours is an exploratory study, our results will be useful to others who perform similar studies in the future.
-Our results come from both APIs either in production or soon to be in production.
-As such, the results of this study will hopefully be of use to the company at which they were studied, be it now for their current API or in the future when they inevitably develop others.
-Likewise, other companies in similar positions could use the results of our study when creating their own APIs.
-
-%Reliability
-The largest \textit{reliability} threat facing our study was the reproducibility.
-To counter this threat, we have followed a well-proven method for analysing the collected data.
-Furthermore, as mentioned previously, we have attempted to limit bias and ambiguity in our interview questions where possible.
-To ensure clarity of the questions, we have field tested the interview with some of our peers, improving the questions based on their feedback.
-
-%Another threat was we were reliant upon being given documentation and code. I.e. they might not give us everything, leave stuff out, ignore things etc.
+\textbf{Reliability  } Potential threats to the reliability of our study have to a great extent been reduced by conducting the study according to a well-reputed guide to case studies \cite{runeson2009guidelines}.
+In addition to that, fragments ( "werd") from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} have been used to increase the trustworthiness of the data gathering and data analysis.
+The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study.
+The semi-structured nature of the interiew, might threaten the reproducibility; but large parts of it were also structured around existing theories.
 

### 2015-05-07 thesis/paper.tex
review threats

@@
 
+%Diffs / Excel documents - This was data collection
+
 %Description of inspection
-From the APIs we collected method names, parameters and return types.
-(!!!Add more here.
-Maybe put it in a table?) The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest.
-<-- do we still want to mention exactly what kinds of data we looked for?
-i.e.
-return types, enums, typedefs etc etc.
+%Description of code analysis - Needs more emphasis on the qualitative grouping
 
-The APIs were inspected to determine where the changes had occurred.
-We used the Git Diff tool to find differences between two versions of files that existed in both versions of the API.
-Once we had identified the changes, we inspected the documentation and the code itself to determine if there was a reason for the change, for example, if a given function had been labelled deprecated between versions.
-Similar changes will be grouped together based on commonalities between them.
-(!!!reword nicely)
+%Identify the changes
+The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
+
+The API code was inspected sequentially, starting with version 1.4.
+Both versions of the API underwent the same inspection.
+This involved extracting methods names, enums, data structures which were then subsequently stored in excel spreadsheets.
+Crosscase analysis was then performed on both sets of data retrieved from different versions of the API \cite{seaman1999qualitative}.
+Changes were grouped into categories that best represented what the change achieved and were added to the data tables (``Use excel?
+Is it ok?'').
+For example, additions, modifications and removals.
+After a change was found in the code, we found related documentation changes, or explanations that were relevant to that change and added them along side their corresponding changes in the excel sheets.
 
@@
 %Interviews !!!improve later
-After the initial source code inspection had been performed, interviews were conducted.
+After the initial source code inspection and preliminary analysis had been performed, interviews were conducted.
 The main purpose of the interviews was to validate our findings during the code inspection with the designers of the APIs.
-Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection.
+Ideally, the interviews would provide additional insight into decisions and motives behind changes that were not evident from the code inspection.
 The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API and how their decisions, needs and requirements have affected the development of the API.
@@
 This created the opportunity to improve the process of analysis as the study progressed, as well as allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
-The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
 
-%Description of code analysis
-More specifically, the approach undertaken was divided into three steps where the changes were first categorised based by following the decision tree for types \cite{chapin2001types}.
-The changes were then mapped according to the laws presented by \cite{lehman1980programs}.
-The changes were then analysed from a high-level point of view, the main goal of which was to identify trends in the changes.
-The final step involved analysis of both the trends and the changes.
-During this stage the hypotheses were generated and formulated.
-The same approach was taken to reduce the risks of research bias and human error in the data collection was also performed during results analysis.
+%Initial state with the data - It's in tables as raw changes here
+Once the preliminary groups of changes were identified, we had to identify what was different between the two versions.
+
+%Grouped into the broader changes by now, new, added, modified and removed.
+Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
+
+%Determining what kind of change it was
+To determine if a change was new, we checked if it had existed in version 1.4 and then existed in version 2.0.
+For those files that did exist, we inspected using the Git Diff tool.
+This allowed us to find differences between files to determine if anything was changed.
+If we found a difference between two files where a function was removed, then it would be categorised as accordingly.
+Finally, for finding removals, we check if any files existed in version 1.4 and were no longer present in version 2.0.
+
+%Documentation's role & trends
+During the data collection stage, appropriate documentation was collected along side each change and was used to also determine what kind of change had occurred.
+Specifically, the documentation included a list of deprecated functions and files which allowed us to identify many changes easily.
+A high level analysis of the changes allowed us to identify general trends of the evolution.
+
+%We have all the changes and our suggested theories. Categorise them now
+Changes identified at this point were further categorised by following the decision tree for types \cite{chapin2001types}.
+Each change was given a main category of maintenance and a subcategory if appropriate.
+This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.
 
 %Description of interview analysis
-Following the analysis of the archival data, the results of the interviews were analysed.
-The interviews were analysed using the same approach taken for the archival data.
-The results of this analysis was then compared and correlated with the results of the code analysis, with the goal of confirming the hypotheses that had been formulated.
-This support also supported triangulation of our results.
+The results of the interviews were analysed and categorised in the same way that our identified changes had been.
+The actual categorisations of the were tabulated and compared with our initial findings.
+
+%Lehman's
+The final step involved analysis of both the trends and the changes, combined with information gathered during the interview.
+These trends, combined with the information gathered in the interviews, allowed us to determine if Lehman's laws are applicable to APIs and therefore the answer to \textbf{RQ2} \cite{lehman1980programs}.
 
@@
 
-Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
-
+%Where does this go?
 Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories.
-Each change was given a main category of maintenance and a subcategory if appropriate.
-This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.
 %This paragraph should be moved to Methodology
@@
 
-\noindent
-\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results the study around already established and accepted theories \cite{chapin2001types} \cite{lehman1980programs}.
+\smallskip \noindent
+\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types} \cite{lehman1980programs}.
 Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis.
@@
 \smallskip \noindent
-\textbf{Internal validity  } Internal validity has been acknowledged by analysing the the code and documentation jointly.
+\textbf{Internal validity  } Internal validity has been acknowledged by analysing the code and documentation jointly.
 This has contributed to triangulating the results and discovering possible inconsistencies.
@@
 The study revealed that the API users were significant to the evolution of the API.
-Since API users were not interviewed, it might be a affecting factor which was left unexplored.
+Since API users were not interviewed, it might be an affecting factor which was left unexplored.
 
 \smallskip \noindent
-\textbf{External validity  } The results of our study should be highly generalisable similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors.
+\textbf{External validity  } The results of our study should be highly generalisable to similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors.
 Our study should be of special interest to researchers studying platform or embedded APIs.

### 2015-05-07 thesis/paper.tex
Methodology re-write

@@
 
-\smallskip \noindent
-\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types} \cite{lehman1980programs}.
+\noindent
+\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results the study around already established and accepted theories \cite{chapin2001types} \cite{lehman1980programs}.
 Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis.
@@
 \smallskip \noindent
-\textbf{Internal validity  } Internal validity has been acknowledged by analysing the code and documentation jointly.
+\textbf{Internal validity  } Internal validity has been acknowledged by analysing the the code and documentation jointly.
 This has contributed to triangulating the results and discovering possible inconsistencies.
@@
 The study revealed that the API users were significant to the evolution of the API.
-Since API users were not interviewed, it might be an affecting factor which was left unexplored.
+Since API users were not interviewed, it might be a affecting factor which was left unexplored.
 
 \smallskip \noindent
-\textbf{External validity  } The results of our study should be highly generalisable to similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors.
+\textbf{External validity  } The results of our study should be highly generalisable similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors.
 Our study should be of special interest to researchers studying platform or embedded APIs.

### 2015-05-07 thesis/paper.tex
removed some comments
review meth

--- 2015-05-07 thesis/paper.tex
@@
 The data were collected primarily through inspections of the source code and the archival analysis of the accompanying documentation.
-The source code was comprised of two versions of an API which the company had developed.
-An older version, 1.4, which is currently released and a newer version, 2.0, which has recently been deployed.
-Each version of the API had its own respective documentation.
+The source code was comprised of API versions.
+Each version of the API also had its own respective documentation.
 The documentation was inspected and organised to find explanations of the features offered by the API.
-
-%Diffs / Excel documents - This was data collection
-
-%Description of inspection
-%Description of code analysis - Needs more emphasis on the qualitative grouping
+( "Not sure if this sentence fits here")
 
@@
 The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
-
+%How the initial inspection was performed
 The API code was inspected sequentially, starting with version 1.4.
 Both versions of the API underwent the same inspection.
-This involved extracting methods names, enums, data structures which were then subsequently stored in excel spreadsheets.
-Crosscase analysis was then performed on both sets of data retrieved from different versions of the API \cite{seaman1999qualitative}.
-Changes were grouped into categories that best represented what the change achieved and were added to the data tables (``Use excel?
-Is it ok?'').
-For example, additions, modifications and removals.
-After a change was found in the code, we found related documentation changes, or explanations that were relevant to that change and added them along side their corresponding changes in the excel sheets.
+This involved extracting methods names, enums, data structures which were then subsequently stored in spreadsheets.
+Crosscase ( "Cross") analysis was then performed on both sets of data retrieved from different versions of the API \cite{seaman1999qualitative}.
+Changes were grouped into categories that best represented what the change achieved and were added to the spreadsheet.
+( "add something here, following is not a full sentence") For example, additions, modifications and removals.
+After a change was found in the code, we identified the related documentation changes, or explanations that were relevant to that change and added them alongside their corresponding changes in the spreadsheets.
+
+%William has reviewed this far!!!!!!!!!!
 
@@
 
-%Interviews !!!improve later
+%Interviews
 After the initial source code inspection and preliminary analysis had been performed, interviews were conducted.
@@
 The final step involved analysis of both the trends and the changes, combined with information gathered during the interview.
-These trends, combined with the information gathered in the interviews, allowed us to determine if Lehman's laws are applicable to APIs and therefore the answer to \textbf{RQ2} \cite{lehman1980programs}.
+These trends, combined with the information gathered in the interviews, allowed us to determine if Lehman's laws are applicable to APIs and therefore the answer to \textbf{RQ1.1} \cite{lehman1980programs}.
 
@@
 
+%%%%****** This stuff is not part of the section, but we might want to use it somewhere, if we don't, remove it! ********
 %This should probably go in Methodology... parts of it at least /W
@@
 
-%Where does this go?
+%Where does this go -- Do we want to put this in anywhere?
 Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories.
-%This paragraph should be moved to Methodology
 

### 2015-05-07 thesis/paper.tex
Updated comments for validity threats

@@
 Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis.
-This means that the evolution of the API was studied during a rather short part of its lifetime ( "rephrase").
+This means that the evolution of the API was studied during a rather short period of its lifetime ( "Is that better?").
 It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes.
 We consider this to be remaining threats to construct validity.
+(``not sure about that last sentence'')
 
@@
 \smallskip \noindent
-\textbf{Reliability  } Potential threats to the reliability of our study have to a great extent been reduced by conducting the study according to a well-reputed guide to case studies \cite{runeson2009guidelines}.
-In addition to that, fragments ( "werd") from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} have been used to increase the trustworthiness of the data gathering and data analysis.
+\textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to a well-reputed guide to case studies \cite{runeson2009guidelines}.
+In addition to that, (``Concepts, strategies, ideas, techniques'') from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} have been used to increase the trustworthiness of the data gathering and data analysis.
 The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study.
-The semi-structured nature of the interiew, might threaten the reproducibility; but large parts of it were also structured around existing theories.
+The semi-structured nature of the interview, might threaten the reproducibility; however, large parts of it were structured around existing theories.
 

### 2015-05-08 thesis/paper.tex
notes to data analysis

@@
 %Reduce human error
+%We could consider joining this sentence with the previous paragraph. WWW
 The data collection from code and documentation was performed independently by both researchers, to reduce the risk of human errors affecting the results.
@@
 %Interviews 
-After the initial source code inspection and preliminary analysis had been performed, interviews were conducted.
-The main purpose of the interviews was to validate our findings during the code inspection with the designers of the APIs.
-Ideally, the interviews would provide additional insight into decisions and motives behind changes that were not evident from the code inspection.
-The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API and how their decisions, needs and requirements have affected the development of the API.
+%I changed stuff in here WWW
+After the initial source code inspection and preliminary analysis had been performed, an interview was conducted.
+The main purpose of the interview was to validate our findings during the code inspection with the API architect.
+The interview also served the purpose of providing additional insight into what drives the API evolution, by complementing what was found from the code inspection.
+The final reason for interviewing the API architects was to gather information about the API users and how their decisions, needs and requirements have affected the development of the API.
 
 \subsection{Data Analysis} \label{data_analysis}
+
+1. Grounded theory
+
+2. RQ1
+
+3. RQ2
+
+4. Interviews
+
+5. RQ1.1
+
 %Intro and summary
@@
 %Initial state with the data - It's in tables as raw changes here
-Once the preliminary groups of changes were identified, we had to identify what was different between the two versions.
+Once the preliminary groups of changes were identified, we had to identify what was different between the two versions. %%Preliminary groups=?, "had to", what was different"=not descriptive enough
 

### 2015-05-08 thesis/paper.tex
Data col

@@
 %Intro to code inspection
-The data were collected primarily through inspections of the source code and the archival analysis of the accompanying documentation.
-The source code was comprised of API versions.
-Each version of the API also had its own respective documentation.
-The documentation was inspected and organised to find explanations of the features offered by the API.
-( "Not sure if this sentence fits here")
+The data were collected primarily through inspections of the source code and the analysis of accompanying documentation.
+The source code was comprised of the two API versions previously mentioned.
+Each version of the API had its own respective documentation, including example code, a library description and a basic development manual.
 
@@
 This involved extracting methods names, enums, data structures which were then subsequently stored in spreadsheets.
-Crosscase ( "Cross") analysis was then performed on both sets of data retrieved from different versions of the API \cite{seaman1999qualitative}.
+Cross analysis was then performed on both sets of data retrieved from different versions of the API \cite{seaman1999qualitative}.
 Changes were grouped into categories that best represented what the change achieved and were added to the spreadsheet.
-( "add something here, following is not a full sentence") For example, additions, modifications and removals.
-After a change was found in the code, we identified the related documentation changes, or explanations that were relevant to that change and added them alongside their corresponding changes in the spreadsheets.
+After a change was found in the code, we identified the related documentation that offered explanations or descriptions relevant to that change that had occurred.
+Both the changes and the code were input into spreadsheets for further analysis.
 

### 2015-05-08 thesis/paper.tex
Moved grounded theory
Data analysis

@@
 Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
-
+enu
 Investigations of three frameworks and one library indicated that 80\% of refactoring changes to APIs negatively affected existing applications \cite{dig2005role}.
@@
 
-The API analysed in this study has been deployed for several years.
+The API analysed in this study is written in the programming language C and has been deployed for several years.
 It was recently updated from version 1.4 to version 2.0, which is the current active version.
 The changes between these two versions is what has been analysed in this study.
-Between the release of 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms.
+Between the release of version 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms.
 Prior to version 1.4 being released, updates were only made to include additional built options and did not include any additional functionality.
@@
 The goal of the study was twofold.
-Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's explanation of their motives.
+Firstly, the aim was to empirically explore the motives behind changes to APIs and secondly, our ambition was to validate the results' level of correctness by comparing our findings with the case company's explanation of their motives.
 Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.
@@
 
-%Identify the changes
-The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
 %How the initial inspection was performed
@@
 Both versions of the API underwent the same inspection.
-This involved extracting methods names, enums, data structures which were then subsequently stored in spreadsheets.
-Cross analysis was then performed on both sets of data retrieved from different versions of the API \cite{seaman1999qualitative}.
-Changes were grouped into categories that best represented what the change achieved and were added to the spreadsheet.
-After a change was found in the code, we identified the related documentation that offered explanations or descriptions relevant to that change that had occurred.
-Both the changes and the code were input into spreadsheets for further analysis.
-
-%William has reviewed this far!!!!!!!!!!
-
-%Reduce human error
-%We could consider joining this sentence with the previous paragraph. WWW
+This involved extracting methods signatures, enums, structs, typedefs and macros, which were then subsequently stored in spreadsheets.
+The extraction involved a lot of manual work, but Git's \cite{git} diff command was used to identify changes in files which exist in both versions.
+After a change was identified in the code, a description of the corresponding change in the documentation was added to the spreadsheet.
+The ID, module, file and description was logged for each change stored in the spreadsheet.
 The data collection from code and documentation was performed independently by both researchers, to reduce the risk of human errors affecting the results.
@@
 
-%Interviews 
-%I changed stuff in here WWW
+%Purpose of the interview
 After the initial source code inspection and preliminary analysis had been performed, an interview was conducted.
@@
 The interview also served the purpose of providing additional insight into what drives the API evolution, by complementing what was found from the code inspection.
-The final reason for interviewing the API architects was to gather information about the API users and how their decisions, needs and requirements have affected the development of the API.
+The final reason for interviewing the API architect was to gather information about the API users and how their decisions, needs and requirements have affected the development of the API.
+
+%Structure of the interview
+The interview was conducted using a semi-structured approach \cite{robson2002real}.
+Structure to the interview was provided by organising it around the theories \cite{chapin2001types} \cite{lehman1980programs}.
+Investigative and open-ended questions related to each category and law were asked to provide a basis for comparison between the answers and our initial analysis.
+The interviewee was encouraged to speak freely, even if it required a change in direction or topic.
+This was allowed to fulfil our exploratory
+goal of the study.
 
 \subsection{Data Analysis} \label{data_analysis}
+%Intro and summary
+The data analysis was conducted in two major phases \cite{andersson2007spiral}.
+During the first phase, a hypothesis generating approach \cite{seaman1999qualitative} was used to be able to fulfil the exploratory goal of the study.
+It was during this phase that the analysis of the API code and documentation was carried out.
+The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase.
+Both phases were performed iteratively, together with the data collection.
+This created the opportunity to improve the process of analysis as the study progressed, as well as allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
 
 1. Grounded theory
+
+%Identify the changes
+The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
 
@@
 5. RQ1.1
-
-%Intro and summary
-The data analysis was conducted in two major phases \cite{andersson2007spiral}.
-During the first phase, a hypothesis generating approach \cite{seaman1999qualitative} was used to be able to fulfil the exploratory goal of the study.
-It was during this phase that the analysis of the API code and documentation was carried out.
-The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase.
-Both phases were performed iteratively, together with the data collection.
-This created the opportunity to improve the process of analysis as the study progressed, as well as allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
 

### 2015-05-08 thesis/paper.tex
collection+threats review

@@
 
-%Consider adding subsub for code+doc and interviews later
-\subsection{Data Collection} \label{data_collection}
+\subsection{Data Collection} \label{data_collection}  %Review 1 or 2 more times (John first)
 %Intro to code inspection
@@
 
-\subsection{Validity Threats} \label{validity_threats}
+\subsection{Validity Threats} \label{validity_threats} %Review 1 or 2 more times (John first)
 In this section we discuss possible threats to construct validity, internal validity, external validity and reliability \cite{runeson2009guidelines}.
@@
 Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis.
-This means that the evolution of the API was studied during a rather short period of its lifetime ( "Is that better?").
+This means that the evolution of the API was studied during a rather short period of its lifetime.
 It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes.
-We consider this to be remaining threats to construct validity.
-(``not sure about that last sentence'')
+We consider these factors to be the remaining threats to construct validity.
 
 \smallskip \noindent
-\textbf{Internal validity  } Internal validity has been acknowledged by analysing the code and documentation jointly.
+\textbf{Internal validity  } Limitations related to internal validity have been acknowledged by analysing the code and documentation jointly.
 This has contributed to triangulating the results and discovering possible inconsistencies.
@@
 \textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to a well-reputed guide to case studies \cite{runeson2009guidelines}.
-In addition to that, (``Concepts, strategies, ideas, techniques'') from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} have been used to increase the trustworthiness of the data gathering and data analysis.
+In addition to that, strategies from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} \cite{robson2002real} have been used to increase the trustworthiness of the data gathering and data analysis.
 The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study.

### 2015-05-08 thesis/paper.tex
Analysis

@@
 
-1. Grounded theory
-
-%Identify the changes
+%Grounded Theory
 The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
 
-2. RQ1
+%Codes
+Each change identified in the spreadsheet was coded based on what module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, or b) if the change was a cosmetic change.
+%Concepts
+Grouping the codes by module allowed us to form general concepts of change. However, changes that affected the whole API were categorised on their own.
+%Categories
+These concepts were then grouped into categories based on common patterns between the concepts.
+%Theory
+These categories were then used to identify the most interesting trends in the evolution of the API. These trends were later used as a discussion point during the interview.
 
-3. RQ2
+%RQ1
+%We have all the changes and our suggested theories. Categorise them now
+The categories identified previously were then coded according to the software maintenance categories \cite{chapin2001types}.
+The process used followed the decision tree for types \cite{chapin2001types}.
+Each of the previously identified categories was given a main category of maintenance and a subcategory if appropriate.
+This was then used to answer \textbf{RQ1}.
 
-4. Interviews
-
-5. RQ1.1
-
-%Initial state with the data - It's in tables as raw changes here
-Once the preliminary groups of changes were identified, we had to identify what was different between the two versions. %%Preliminary groups=?, "had to", what was different"=not descriptive enough
-
-%Grouped into the broader changes by now, new, added, modified and removed.
-Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends.
-
-%Determining what kind of change it was
-To determine if a change was new, we checked if it had existed in version 1.4 and then existed in version 2.0.
-For those files that did exist, we inspected using the Git Diff tool.
-This allowed us to find differences between files to determine if anything was changed.
-If we found a difference between two files where a function was removed, then it would be categorised as accordingly.
-Finally, for finding removals, we check if any files existed in version 1.4 and were no longer present in version 2.0.
-
-%Documentation's role & trends
-During the data collection stage, appropriate documentation was collected along side each change and was used to also determine what kind of change had occurred.
-Specifically, the documentation included a list of deprecated functions and files which allowed us to identify many changes easily.
-A high level analysis of the changes allowed us to identify general trends of the evolution.
-
-%We have all the changes and our suggested theories. Categorise them now
-Changes identified at this point were further categorised by following the decision tree for types \cite{chapin2001types}.
-Each change was given a main category of maintenance and a subcategory if appropriate.
-This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.
+Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, will serve as the basis for answering \textbf{RQ1.1}.
 
 %Description of interview analysis
-The results of the interviews were analysed and categorised in the same way that our identified changes had been.
-The actual categorisations of the were tabulated and compared with our initial findings.
+The results of the interview were analysed and categorised in the same way that our identified changes had been.
+Validation of our findings, by comparing our categorisation against the interviewee's categorisation, was performed at this point.
+The results of which are used to answer \textbf{RQ1}, \textbf{RQ1.1} and \textbf{RQ2}.
 
-%Lehman's
-The final step involved analysis of both the trends and the changes, combined with information gathered during the interview.
-These trends, combined with the information gathered in the interviews, allowed us to determine if Lehman's laws are applicable to APIs and therefore the answer to \textbf{RQ1.1} \cite{lehman1980programs}.
+%Lehman's - RQ2
+The analysis of both the trends and the changes, combined with information gathered during the interview allowed us to answer \textbf{RQ2} by determining if Lehman's laws are applicable to APIs \cite{lehman1980programs}.
 
-%Relate to RQs
-The software evolution categories \cite{chapin2001types} and Lehman's laws \cite{lehman1980programs} were analysed to allow us to be able to answer \textbf{RQ1}.
-The software evolution categories were used to map and explore motives behind changes and Lehman's laws were used to see what drives the natural evolution of APIs.
-Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, will serve as the basis for answering \textbf{RQ2}.
-
-%%%%****** This stuff is not part of the section, but we might want to use it somewhere, if we don't, remove it! ********
-%This should probably go in Methodology... parts of it at least /W
-In order to answer \textbf{RQ1}, we categorised the changes based on the 12 maintenance categories \cite{chapin2001types}, by inspecting the source code and the accompanying documentation.
-Following the interview, we compared our categorisations to the actual motive which was gathered from the interview.
-
-%Where does this go -- Do we want to put this in anywhere?
-Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories.
+%RQ1.1
+The final stage of analysis was conducted once all the data had been analysed.
+To answer \textbf{RQ1.1}, we compared our analysis and interpretation of the change intents against the opinions expressed during the interview.
+Success was determined based on the amount of correct interpretations made about the intent behind the changes.
 

### 2015-05-08 thesis/paper.tex
Changed lehman ref

@@
 enu
+
 Investigations of three frameworks and one library indicated that 80\% of refactoring changes to APIs negatively affected existing applications \cite{dig2005role}.

### 2015-05-08 thesis/paper.tex
Review Changes

@@
 Both versions of the API underwent the same inspection.
-This involved extracting methods signatures, enums, structs, typedefs and macros, which were then subsequently stored in spreadsheets.
+This involved extracting method signatures, enums, structs, typedefs and macros, which were then subsequently stored in spreadsheets.
 The extraction involved a lot of manual work, but Git's \cite{git} diff command was used to identify changes in files which exist in both versions.
@@
 The main purpose of the interview was to validate our findings during the code inspection with the API architect.
-The interview also served the purpose of providing additional insight into what drives the API evolution, by complementing what was found from the code inspection.
+The interview also served the purpose of providing additional insight into what drove the evolution of the API, by complementing what was found from the code inspection.
 The final reason for interviewing the API architect was to gather information about the API users and how their decisions, needs and requirements have affected the development of the API.
@@
 The interview was conducted using a semi-structured approach \cite{robson2002real}.
-Structure to the interview was provided by organising it around the theories \cite{chapin2001types} \cite{lehman1980programs}.
+Structure to the interview was provided by organising it around the software evolution theories \cite{chapin2001types} \cite{lehman1980programs}.
 Investigative and open-ended questions related to each category and law were asked to provide a basis for comparison between the answers and our initial analysis.
 The interviewee was encouraged to speak freely, even if it required a change in direction or topic.
-This was allowed to fulfil our exploratory
-goal of the study.
+This was allowed in order to fulfil our exploratory goal of the study.
 

### 2015-05-08 thesis/paper.tex
review analysis

--- 2015-05-08 thesis/paper.tex
@@
 Both phases were performed iteratively, together with the data collection.
-This created the opportunity to improve the process of analysis as the study progressed, as well as allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
+This created the opportunity to improve the process of analysis as the study progressed, as well as, allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
 
@@
 The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
-
 %Codes
-Each change identified in the spreadsheet was coded based on what module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, or b) if the change was a cosmetic change.
+Each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
 %Concepts
@@
 %Theory
-These categories were then used to identify the most interesting trends in the evolution of the API. These trends were later used as a discussion point during the interview.
+These categories were then used to identify the most interesting trends in the evolution of the API. These trends were later used as a basis for discussion during the interview.
 
@@
 %We have all the changes and our suggested theories. Categorise them now
-The categories identified previously were then coded according to the software maintenance categories \cite{chapin2001types}.
-The process used followed the decision tree for types \cite{chapin2001types}.
-Each of the previously identified categories was given a main category of maintenance and a subcategory if appropriate.
-This was then used to answer \textbf{RQ1}.
-
-Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, will serve as the basis for answering \textbf{RQ1.1}.
+The categories identified previously were then classified according to the software maintenance categories \cite{chapin2001types}.
+The process used followed the decision tree used for the types of software evolution and software maintenance \cite{chapin2001types}.
+Each of the previously identified categories were given a main category of maintenance and a secondary category, if appropriate.
+This material was then used as a basis for answering \textbf{RQ1}.
 
@@
 %Lehman's - RQ2
-The analysis of both the trends and the changes, combined with information gathered during the interview allowed us to answer \textbf{RQ2} by determining if Lehman's laws are applicable to APIs \cite{lehman1980programs}.
+The analysis of the trends and the changes, combined with information gathered during the interview allowed us to answer \textbf{RQ2} by determining if Lehman's laws are applicable to the changes to the API \cite{lehman1980programs}.
 
@@
 Success was determined based on the amount of correct interpretations made about the intent behind the changes.
+Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, served as the basis for answering \textbf{RQ1.1}.
 

### 2015-05-08 thesis/paper.tex
first page
Review meth

@@
 
-\numberofauthors{4}
+\numberofauthors{2}
 
@@
        \email{william.granli@gmail.com}
-\and
+%\and
 % 3rd. author
-\alignauthor Imed Hammouda\titlenote{Co-author}\\
+%\alignauthor Imed Hammouda\titlenote{Co-author}\\
 %       \affaddr{Computer Science and Engineering}\\
-       \affaddr{University of Gothenburg}\\
-       \email{imed.hammouda@gu.se}
+%       \affaddr{University of Gothenburg}\\
+%       \email{imed.hammouda@gu.se}
 % 4th 
-\alignauthor Eric Knauss\titlenote{Co-author}\\
+%\alignauthor Eric Knauss\titlenote{Co-author}\\
 %       \affaddr{Computer Science and Engineering}\\
-       \affaddr{University of Gothenburg}\\
-       \email{imed.hammouda@gu.se}
+%       \affaddr{University of Gothenburg}\\
+%       \email{imed.hammouda@gu.se}
 }
@@
 Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
-enu
 
@@
 The goal of the study was twofold.
-Firstly, the aim was to empirically explore the motives behind changes to APIs and secondly, our ambition was to validate the results' level of correctness by comparing our findings with the case company's explanation of their motives.
+Firstly, the aim was to empirically explore the motives behind changes to APIs and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of their motives.
 Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.
@@
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research; especially to be able to answer \textbf{RQ2}.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ1.1}.
 
@@
 Both versions of the API underwent the same inspection.
-This involved extracting method signatures, enums, structs, typedefs and macros, which were then subsequently stored in spreadsheets.
+This involved extracting method signatures, enums, structs, typedefs and macros, which were subsequently stored in spreadsheets.
 The extraction involved a lot of manual work, but Git's \cite{git} diff command was used to identify changes in files which exist in both versions.
 After a change was identified in the code, a description of the corresponding change in the documentation was added to the spreadsheet.
-The ID, module, file and description was logged for each change stored in the spreadsheet.
+The module and file in which the change was identified was then logged together with an ID and a description of the change.
 The data collection from code and documentation was performed independently by both researchers, to reduce the risk of human errors affecting the results.
@@
 After the initial source code inspection and preliminary analysis had been performed, an interview was conducted.
-The main purpose of the interview was to validate our findings during the code inspection with the API architect.
+The main purpose of the interview was to validate our findings from the code inspection with the API architect.
 The interview also served the purpose of providing additional insight into what drove the evolution of the API, by complementing what was found from the code inspection.
@@
 %Theory
-These categories were then used to identify the most interesting trends in the evolution of the API. These trends were later used as a basis for discussion during the interview.
+These categories were then used to identify the most notable trends in the evolution of the API. These trends were later used as a basis for discussion during the interview.
 
 %RQ1
-%We have all the changes and our suggested theories. Categorise them now
 The categories identified previously were then classified according to the software maintenance categories \cite{chapin2001types}.
-The process used followed the decision tree used for the types of software evolution and software maintenance \cite{chapin2001types}.
+The process followed the decision tree used for the types of software evolution and software maintenance \cite{chapin2001types}.
 Each of the previously identified categories were given a main category of maintenance and a secondary category, if appropriate.
@@
 Validation of our findings, by comparing our categorisation against the interviewee's categorisation, was performed at this point.
-The results of which are used to answer \textbf{RQ1}, \textbf{RQ1.1} and \textbf{RQ2}.
 
 %Lehman's - RQ2
-The analysis of the trends and the changes, combined with information gathered during the interview allowed us to answer \textbf{RQ2} by determining if Lehman's laws are applicable to the changes to the API \cite{lehman1980programs}.
+The analysis of the trends and the changes, combined with information gathered during the interview, allowed us to answer \textbf{RQ2} by determining if Lehman's laws are applicable to the changes to the API \cite{lehman1980programs}.
 
 %RQ1.1
-The final stage of analysis was conducted once all the data had been analysed.
-To answer \textbf{RQ1.1}, we compared our analysis and interpretation of the change intents against the opinions expressed during the interview.
-Success was determined based on the amount of correct interpretations made about the intent behind the changes.
-Our ability to correctly predict the motives compared to the actual motives of the designers which were made clear during the interviews, served as the basis for answering \textbf{RQ1.1}.
+The final stage of analysis was conducted once all the data had been analysed, which allowed us to answer \textbf{RQ1.1}.
+This was accomplished by comparing our analysis and interpretation of the change motives against the opinions expressed during the interview.
+Success was determined by the amount of correct interpretations made about the motives of the changes.
+Our ability to correctly predict the motives, compared to the designers' actual motives which were made clear during the interviews, served as the basis for answering \textbf{RQ1.1}.
 
@@
 \textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types} \cite{lehman1980programs}.
-Due to restricted access to the company's source code, we were not able to include versions previous to version 1.4 in our analysis.
+Due to restricted access to the company's source code, we were not able to include versions prior to version 1.4 in our analysis.
 This means that the evolution of the API was studied during a rather short period of its lifetime.

### 2015-05-08 thesis/paper.tex
concl comments

@@
 
-Summarise the findings of the discussion
-Summarise what the next steps could be.
+1. Small intro which: Summarises the findings of the discussion
 
+2. Conclusions/outcomes:
+Industry
+Have a more structured feedback loop (include users) this can be future work too
+              Greater emphasis should be placed upon communicating with the end users / application developers.
+They should probably improve their feedback system to get more feedback from the API users.
+              Include more scientific theories
+              --> consider ecosystem stuff
+
+Academia
+Some laws dont apply. Propose a new version of the law.
+Interesting that hardware did not drive change. This is cool cuz it means hardware apis can be generalised to any type of api.
+Since motives are reverse engineerable, it hsould encourage more ppl to do similar studies
+%%William add conclusion ideas here
+That the part about controlling how the API users use the API was such an important thing is interesting. (Not something we expected). 
+       MAke a study which looks the quality of applications before and after api changes have been introduced
+
+3. Future work: Summarise what the next steps could be.
+Obvious benefit for Axis is that the more features == more applications == higher value for their camera.
+If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase.
+This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
+       -->Suggest a similar study which looks at business factors
+
+Random tips n trickz:
        Look up the papers from the conference (especially regarding the discussion/conclusion)
@@
        conclusion = summary part, main final points and future work
-
-Stuff for the conclusion:
-Have a more structured feedback loop (include users) this can be future work too
-Include more scientific theories
-
-For future studies, this technique could be improved by performing more actions along side the code review.
-For example, having access to and analysing commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be collected and analysed.
-%%Conclusion stuff /Willy
-
-%%The following should probably be in conclusion, right? /Willy
-       What this means for industry:
-              Greater emphasis should be placed upon communicating with the end users / application developers.
-APIs should be made with maintainability and extensibility in mind as they seem to be what changes the most between versions.
-They should probably improve their feedback system to get more feedback from the API users.
-
-              Interesting that hardware did not drive change. Could be studied further in a new study to see if this applies to platform specific APIs in general?
-
-              Obvious benefit for Axis is that the more features == more applications == higher value for their camera.
-If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase.
-This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
-
-       What this means for academia:
-              Academia could benefit from the results as a means for further research - We have found that it's possible to reverse engineer these design decisions from a simple study, so perhaps more advanced studies should be conduct at a larger scale?
--- Why though?
-
-%%John add conclusion ideas here
-We were correct with the majority of our categorisations.
-The ones we did get wrong were because we did not think of it from specific points of view.
-This probably means that it's possible to reverse engineer to some extent, but not completely (Which is probably the answer most people would expect).
-
-Considering the Ecosystem and considering it as a whole when designing the API.
-She does not think that they did take it into consideration at all.
-They had not thought about them when designing the APIs.
-She does think about who is going to use it and how but nothing in regards to how it affects an ecosystem as a whole.
-Things like allowing embedded web pages for the ACAP allows users to get more information from their system meaning they don’t need to ask for as much help and assistance.
-They usually integrate this with the VMS.
-Overall there was not much thought about ecosystem when the API was designed.
-She’s unsure if it’s one ecosystem or two.
-The network APIs and their API.
-Perhaps it is one ecosystem.
-(this is something Imed is looking at).
-It seems that a focus on ecosystems might be starting to come through but that they already thought about them without calling them ecosystems.
-For example, her mentioning that they already did think about the users of the API and how they would be using it gives a slight clue that they do already think about the wider audience of their API.
-
-%See if our numbers match up with previous studies who said roughly 70\% of changes to an API were refactorings.
-That number is a little high in our case, but it's close!
-<---- This could be done in conclusion when we discuss how it contribues to academia (i.e.
-say it enforces previous studies blabla)
-
-%%William add conclusion ideas here
-It's interesting that the partners have mentioned that they want more frequent updates... maybe API developers should be less afraid of updating them? 
-That the part about controlling how the API users use the API was such an important thing is interesting. (Not something we expected). 
--Relate to 80% refactorings paper and say that we found different results
-*This is an interesting note if we want to compare platform APIs and library APIs to say that functionality changes more often in platform APIs for example
-
-%Business rules and motives are not taken into consideration apparently when creating these APIs. They probably should be!
 

### 2015-05-11 thesis/paper.tex
Added notes from meeting

@@
 
-\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
+\title{Exploring the Types and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
 
@@
 
-\textbf{Background  } %Done
+\textbf{Background  } %Give a feeling of the need of this study, answer why Axis needs what is in the Objective (+Context)
 The driving forces of modifications to APIs have been investigated before, however, platform APIs are, until now, unexplored.
@@
 
+%switch places between ^ and v
+
 %Purpose
@@
 
-%Method
+%Method %wrong tense %include RQs in here %include clear contribution (to johanna)
 In order to achieve this, an exploratory case study will be undertaken to investigate the underlying motives behind changes to APIs.
@@
 
-\section{Existing Literature} \label{existing_literature}
+\section{Background} \label{existing_literature}
 This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.
@@
 
-\subsection{Related Work} \label{related_work}
+\subsection{API Evolution} \label{related_work}
 The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}.
@@
 
-\section{Case Company Description} \label{case_company_description}
+\subsection{Case Company Description} \label{case_company_description}
 The case company is a company operating in the domain of video surveillance.
@@
 
-The case company was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}.
+%The case company was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}.
 As such, the goal was to include as many companies as possible in this study.
@@
 The categories identified previously were then classified according to the software maintenance categories \cite{chapin2001types}.
-The process followed the decision tree used for the types of software evolution and software maintenance \cite{chapin2001types}.
+The process followed the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}.
 Each of the previously identified categories were given a main category of maintenance and a secondary category, if appropriate.
@@
 
+\newpage
+\newpage
 \subsection{RQ1 Results} \label{results_rq1} %Reviewed by JW

### 2015-05-11 thesis/paper.tex
Re-structured Results

@@
 
-\section{Results} \label{results} %Reviewed by JW
+\section{Results} \label{results} 
 This section will present the findings of our study.
@@
 
-\newpage
-\newpage
-\subsection{RQ1 Results} \label{results_rq1} %Reviewed by JW
-\noindent
-RQ1: \textbf{How do companies actively drive API evolution?}
+\subsection{RQ1 Results} \label{results_rq1}
 
-\noindent
-RQ1.1: \textbf{To what extent can we reverse engineer API change decisions?}
-\smallskip
+\subsubsection{Categories of Maintenance}
 
-Many changes were found between version 1.4 and version 2.0.
-The initial inspection revealed there to be many deprecations which were later re-implemented as new modules.
-We have group these changes into a single change instead of a deprecation and a re-implementation.
-In total, thirteen unique changes were found.
-These changes are shown in Table \ref{table:categories}.
+\smallskip \noindent
+\textbf{Enhancive  }
 
-The changes have been divided up into four specific categories, namely: \textit{new}, \textit{modified}, \textit{removed} and \textit{general trends}.
-The category \textit{new} concerns additions of modules, \textit{modified} concerns modifications to modules that existed in version 1.4 and \textit{removed} are changes where functionality was removed being deprecated or replaced by functionality.
-\textit{General trends} are broad changes that are mainly related to design.
+\smallskip \noindent
+\textbf{Corrective  }
 
-After cross-examining our results with the interviewee and their responses, we found that 78\% of our main category predictions matched the actual motive of the changes and that 78\% of our secondary categorisations matched the actual motives.
+\smallskip \noindent
+\textbf{Reductive  }
 
-\begin{table}
-       \centering
-       \begin{tabular}[ht]{c !{\vrule width 1.5pt} c|c !{\vrule width 1.5pt} c|c} 
-              \toprule
+\smallskip \noindent
+\textbf{Adaptive  }
 
-              \multirow{2}{*}{\textbf{Change}}          & \multicolumn{2}{c !{\vrule width 1.5pt} }{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Sub}}        \\ \cline{2-5}
+\smallskip \noindent
+\textbf{Performance  }
 
-                                   & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \Xhline{2\arrayrulewidth}
-              axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
-              axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
-              axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
-              axserialport         & E                         & E                         & N/A                       & N/A                \\ \hline
-              axevent              & E                         & E                         & G                         & G                  \\ \hline
-              axhttp               & E                         & E                         & G                         & G                  \\ \hline
-              ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
-              Burst Mode           & R\textsubscript{d}        & R\textsubscript{d}        & N/A                       & N/A                \\ \hline
-              Example Code         & U                         & R\textsubscript{f}        & R\textsubscript{f}        & U                  \\ \hline
-              Documentation        & U                         & U                         & R\textsubscript{f}        & R\textsubscript{f} \\ \hline
-              Interfaces           & G                         & P                         & P                         & G                  \\ \hline
-              3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
-              Error Handling       & P                         & P                         & G                         & G                  \\
+\smallskip \noindent
+\textbf{Preventive  }
 
-              \bottomrule
-       \end{tabular}
-       \caption{Categorisation of Changes }
-       \label{table:categories}
-\end{table}
+\smallskip \noindent
+\textbf{Groomative  }
 
-\subsubsection{axptz} %Reviewed by JW
-The Pan, Tilt and Zoom (ptz) module concerns functionality related to manoeuvring the camera, both mechanically and digitally.
-We concluded that this change was enhancive, because it is a new feature of the API.
-There was no secondary motive behind this change, as the change was purely enhancive.
-The interviewee described how this change, as well as the other changes classified as additions, were all included in the new API at the request of API users.
-Prior to the change being introduced, there was no API functionality for controlling the camera and as such, it was a high priority addition to the new API.
-The interviewees' comments allowed us to conclude that we had correctly identified the change as being enhancive.
-Furthermore, we were also correct in our prediction that there was no secondary change category.
+\smallskip \noindent
+\textbf{Updative  }
 
-\subsubsection{axaudio} %Reviewed by JW
-The most important functionality of the camera is to capture and analyse video data, however, some API users require the ability to analyse audio data.
-The addition of axaudio allows API users to perform audio analysis of audio streams captured by cameras.
-This change was determined to be enhancive, as it was an addition of a new feature to the API.
-We found no secondary motive for the change.
-Audio analysis had previously not been supported in version 1.4 of the API.
-However, during the interview, it was revealed that an API user had managed to implement their own audio analysis application using version 1.4 of the API.
-Given the apparent demand for audio analysis, it was included in version 2.0 of the API.Taking into account the interviewee's reasoning, we concluded that we had successfully determined that the change was enhancive.
-The addition of axaudio had no secondary motive.
+\smallskip \noindent
+\textbf{Reformative  }
 
-\subsubsection{axstorage} %Reviewed by JW
-Prior to the newest version of the API being released, the sole alternative for storing data was to use the Video Management System.
-Version 2.0 added the possibility of alternative storage solutions, by allowing the camera to interface with external storage devices, such as SD cards.
-Enhancive was chosen to be the primary category of change, given that axstorage was a new addition to version 2.0.
-No secondary motive was identified.
-The interviewee described how limited storage options for the cameras, in version 1.4, was the reason that increased functionality was strongly requested by API users.
-As such, axstorage was included in version 2.0 of the API.The information gathered from the interview therefore supported our original categorisation; it was an enhancive change.
-No secondary category was established.
+\smallskip \noindent
+\textbf{Evaluative  }
 
-\subsubsection{axserialport} %Reviewed by JW
-The addition of axserialport allows API users to connect various devices to the cameras through the use of a serial port.
-This allows users to integrate multiple devices to create their own unique solutions.
-This was not possible in version 1.4 of the API.
-The addition of this module was determined to be an enhancive change, as it involved the addition of a new feature.
-No relevant secondary category was identified.
-The addition of axserialport was requested by API users to allow them to connect the cameras to other devices.
-A possible use case, that was given during the interview, involved a ticketing system which allows for joint analysis of data from multiple devices.
-As such, it was included in version 2.0, to meet the demand of the API users.
-Given this information, we concluded that we were correct in categorising this change as enhancive.
-The categorisation of the secondary category was also correct.
+\smallskip \noindent
+\textbf{Consultive  }
 
-\subsubsection{axevent} %Reviewed by JW
-Version 2.0 of the API was designed to be an event-driven system that makes use of callbacks.
-To achieve this, the old event system had to be re-designed.
-The new design is used by all features of version 2.0 of the API.
-An example of when an event would be generated, is when the camera detects movement.
-Given that this module was a re-implementation of the previous event system, we concluded that it should be categorised mainly as an enhancive change with the secondary change as groomative.
-Groomative was chosen as the secondary category due to the additional motive of bringing the new functionality into line with the new design.
-The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implementation of the new event system.
-One reason was that the case company was dissatisfied with certain usability aspects of API version 1.4.
-The module was then completely re-implemented and re-designed according to the new system design of version 2.0.
-From the discussion in the interview, it was clear that both of our categorisations were correct.
-The change was primarily enhancive and secondarily groomative.
+\smallskip \noindent
+\textbf{Training  }
 
-\subsubsection{axhttp} %Reviewed by JW
-The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically send data to web pages.
-The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards, and at the same time, additional functionality was added to the module.
-This change re-implemented an existing module while adhering to the new design of API version 2.0.
-The main categorisation therefore was chosen to be enhancive with groomative as the secondary category.
-The interviewee described that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, within the standards of the new design.
-Our categorisation of enhancive and groomative was therefore correct for this change.
-The primary intent was to add functionality while also allowing the re-implementation to make use of the new API design.
-
-\subsubsection{ax\_parameter} %Reviewed by JW
-The parameter setting module of the API allowed data and application settings to be saved so that they are not lost if the device is not running.
-This module was re-implemented as ax\_parameter with added functionality and conformance to the new design standards of API version 2.0.
-Given that this change re-implemented an existing module while also incorporating the new design standards, it has been categorised as being primarily enhancive with a secondary category of groomative.
-The interviewee clarified that this change was mainly concerned with re-implementing existing functionality, while simultaneously adopting the new standards of version 2.0.
-Given the information from the interview, we concluded that this change was correctly categorised; the primary intent was enhancive and the secondary intent was groomative.
-
-\subsubsection{Burst Mode} %Reviewed by JW
-The burst mode feature of the API allowed users to buffer a series of images for greater analysis.
-This feature was deprecated during the transition between version 1.4 and 2.0 and was not re-implemented.
-This change presented itself as a clear example of reductive maintenance, as it was simply removed and without being replaced.
-We therefore gave no secondary categorisation for this change.
-The interviewee described, that in order to continue using this feature, it would have to be re-implemented.
-An impact assessment was undertaken to determine if the removal of the function would be costly.
-Ultimately, the negative effects were not deemed significant enough and thus the function was removed of the API.
-We can therefore conclude that we correctly categorised this change as reductive and that there are indeed, no secondary categories to describe this change.
-
-\subsubsection{Example Code} %Reviewed by JW
-The case company included a selection of example programs to assist developers with creating applications.
-This trend continued in version 2.0, but there were some significant improvements.
-The number of example programs and the amount of comments accompanying the code increased, thus improving quality of the examples.
-We therefore concluded that this change was updative, as the example code was updated according to the new API and the new techniques that it utilises.
-We further decided that this change also had a secondary category of reformative.
-During the interview, it became clear that the improvement of the example code was an important change between the two versions.
-The interviewee described how the examples were used frequently by their customers, however, the old examples had many varied implementation techniques, even for similar tasks.
-This ultimately meant that the old examples were not satisfactory and that new examples would have to be written, preferably conforming to the same standards.
-The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.
-With this information, we concluded that our categorisation was incorrect.
-It became clear that this change was, in actual fact, primarily reformative.
-It was also clear that the subcategory should therefore have been updative.
-
-\subsubsection{Documentation} %Reviewed by JW
-As the API code was updated in version 2.0, the API documentation was updated to correspond with the new code.
-While there were no substantial changes, we found that the documentation is no longer offered as a PDF but is instead only offered as HTML.
-We categorised this change as being updative with a reformative secondary category for the reasons that the change only updated the documentation to reflect the recent changes in version 2.0.
-This sentiment was shared by the interviewee; the documentation was only changed according to the current workings of the API and how the new modules interact with each other.
-We can therefore say that our categorisations were correct, the change was updative and reformative.
-
-\subsubsection{Interfaces} %Reviewed by JW
-Version 1.4 of the API allowed direct access to the headers of each module available in the API.
-Version 2.0 changed this by including interfaces through which functionality is accessed.
-This design change has had an effect on the whole API, as it has changed the structure of modules, but not the functionality of them.We therefore concluded that this change would be best categorised as  groomative.
-The secondary category was categorised as preventive, as the change could be seen as an attempt to reduce future maintenance.
-The interview provided further insight into the reasoning behind this design change.
-Improvements to coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to use interfaces in versions 2.0 of the API.
-Furthermore, the re-design would hopefully avoid future maintenance, while also allowing the system to be easily extended.
-Taking this information into account, we concluded that our categorisation was incorrect.
-The interview showed that the primary categorisation should have been preventive, given the strong emphasis on avoiding future maintenance and improving usability.
-We further concluded that the secondary change should have been groomative, to better reflect the intent of improving the APIs maintainability.
-
-\subsubsection{3\textsuperscript{rd} Party}
-%% REMEMBER TO PROVIDE LINK TO GLIB:::: - https://developer.gnome.org/glib/
-ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
-%%Describe the change 
-2.0 utilises more 3rd party libraries
-axsound, for example, uses alsa
-All modules use glib
-The advent of the new API saw the inclusion of new 3\textsuperscript{rd} party libraries.
-For example, axsound utilises a library called Alsa, all interfaces use Glib and daemons have been provided for using D-Bus.
-These changes potentially make the library much more flexible both for the API designers in terms of features they can provide and for the application developers in terms of applications they can develop.
-We therefore gave this change the main categorisation of adaptive with no suitable sub-categories being found.
-The architects creating the API decided they wished to use Glib which came about primarily from internal discussions at the company.
-%%Relate it to Categories
-Architects decided to use glib, part of an internal decision. 
-Glib (!!!ref to website) was therefore introduced to the new API to help alleviate this 
-The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API.
-However, it was expressed to us that the error handling would have changed between versions regardless of whether or not Glib was included.
-(!!!This is also too assume-y)
-
-\subsubsection{Error Handling} %Reviewed by JW
-A substantial change included in version 2.0 was the addition of header files, containing enums of error codes.
-While it was not evident how the error handling was implemented prior to version 2.0, we concluded that it had changed, given the addition of the new header files.
-We therefore categorised this change as being primarily preventive, as error handling is preventive by nature.
-Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability.
-During the interview, it was made clear that the previous error handling was lacking in expressiveness and usability.
-Glib was added to version 2.0 and the error handling functionality that Glib provides was incorporated into the new API design.
-We therefore concluded that our categorisation for this change was correct.
-The primary reason for the change was to improve the existing error handling while conforming to the new API standard.
-
-\subsection{RQ2 Results} \label{results_rq2} %Reviewed by JW
-\noindent
-RQ2: \textbf{How do APIs ``passively'' evolve?}
-\smallskip
-
-The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs.
-A summary of our findings can be seen in Table \ref{table:lehman}.
-
-\begin{table}
-       \centering
-       \begin{tabular}[ht]{l|c}
-              \toprule
-
-              \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
-              Continuing Change                         & True                      \\ \hline
-              Increasing Complexity                     & Kinda                     \\ \hline
-              Self Regulation                           & True                      \\ \hline
-              Conservation of Organisational Stability  & False                     \\ \hline
-              Conservation of Familiarity               & True                      \\ \hline
-              Continuing Growth                         & True                      \\ \hline
-              Declining Quality                         & Kinda                     \\ \hline
-              Feedback System                           & True                      \\
-
-              \bottomrule
-
-       \end{tabular}
-       \caption{The applicability of Lehman's laws}
-       \label{table:lehman}
-\end{table}
-
-\subsubsection{Continuing Change} %Reviewed by WJ
-The case company described that including new functional content was one of the top priorities for the release of version 2.0.
-This is supported by the characteristic of the changes identified in this study.
-4 of the 13 changes were additions of new modules, and additional functionality was also added to re-implemented modules.
-It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could cause.
-One of the main reasons for continuously adapting the API is also to control the way API users use the API.
-Prior to version 2.0 being released, a number of API users used workarounds to implement applications which contained functionality which was not yet offered from the API.
-These applications were fully functional, but there existed no standard method of implementation.
-We therefore conclude that the law of continuing change holds for APIs.
-
-\subsubsection{Increasing Complexity} \label{sec:law2} %Reviewed by WJ
-A majority of the changes introduced in version 2.0 aimed to improve the structure and the way that the API was used.
-Many of these changes were related to the same design choices, which enforced a certain implementation style on the whole API.
-One example of this is the change to the interfaces which set a standard for the whole API.
-During the interview it was also concluded that consistency and following certain standards is an important factor to consider when designing APIs.
-It was also made clear that a contributing factor for changing certain parts of the API was to bring it into line with the new interface design.
-The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that the company currently did not make use of these.
-Even though the importance of maintaining the API in order to reduce complexity was stated, arguments which support that it is of lesser importance than releasing functional content was also presented.
-One example of where this is evident in the evolution of the API, is in the module that handles the video capturing and video stream.
-It was decided that this module would not be re-designed to conform with the new interface standard, as the changes to functionality in this module were very minor.
-Thus, the law of increasing complexity holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.
-
-\subsubsection{Self Regulation} \label{sec:law3} %Reviewed by WJ
-The release of version 1.4 did not include any changes related to the API interface.
-Version 1.0 through to 1.4 strictly added support for additional build target platforms.
-When comparing the changes introduced in version 2.0 to the ones in previous versions, it is clear that the growth of the API has gradually increased.
-During the interview it was also mentioned that the future plans for the API did not include any major changes and that only a few minor changes were planned in the near future.
-The future updates to the API will also be made incrementally and there will not be a big bang update similar to that of version 2.0.
-This supports that the law of self regulation applies to APIs, assuming that version 2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
-
-\subsubsection{Conservation of Organisational Stability} %Reviewed by WJ
-The changes to the API have been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
-As mentioned in Section \ref{sec:law3}, the changes introduced in version 1.4 did not involve any changes to the existing API functions.
-Consequently, the only significant update to the API was made in the transition to version 2.0.
-The internal development of the API has also been made sporadically and there have been periods where the API has not been actively developed.
-This suggests that the law of conservation of organisational stability does not apply to APIs.
-
-\subsubsection{Conservation of Familiarity} %Reviewed by WJ
-The documentation that is included with the API was rigorously updated with the introduction of version 2.0.
-All functionality which was added or modified in version 2.0 was updated accordingly in the documentation.
-The same pattern can be seen for the example code, which went through major changes as a result of the changes to the API code.
-The case company's intent to control the way that their API is used also suggests that the knowledge of how to use the API is of importance, since if the API is used in too many different ways, it will be more difficult for the case company to have relevant documentation and example code.
-It was also expressed during the interview that further transparency in how the API should be used could be achieved.
-One example mentioned of how this could be achieved is by improving the expressiveness regarding which API functions are supported on which hardware types.
-These facts support that the law of conservation of familiarity is true for APIs.
-
-\subsubsection{Continuing Growth} %Reviewed by WJ
-Large parts of the changes between the versions were strictly additions of new functional content.
-4 new modules were added and significant additions of new functionality were added to the modules which were re-designed from version 1.4.
-The interviewee also made it clear that increasing the functionality was one of the main goals with the 2.0 update.
-This also ties in with the ambition of controlling the way that the API is used, as mentioned previously.
-It was also mentioned that the case company had received feedback from the API users that more frequent updates to the functional content was desirable, even though this may require them to update their application code.
-We therefore conclude that the law of continuing growth applies to APIs.
-
-\subsubsection{Declining Quality} %Reviewed by WJ
-The interviews established that a groomative motive was not the primary reason for implementing any change.
-The changes to the example code and the documentation, as well as the re-designed modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content.
-These changes did, however, also increase the quality and were a substantial part of the update.
-A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{sec:law2}.
-We therefore settle that the law of declining quality can be applied to APIs, but that there is data that implies that reducing quality is not of high importance.
-
-\subsubsection{Feedback System} %Reviewed by WJ
-One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
-Currently, only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users.
-The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users and which leads to good applications being developed.
-Prior to version 2.0 being released, an example of how the API users were included in the feedback loop was when they implemented functionality related to sound, despite the fact there was no interface for this.
-The experiences of this API user, were later considered when developing the axsound module.
-One benefit of having a more structured feedback loop, would be that the API developers would have greater awareness of potential errors in the implementation of the API.
-Another ambition which was mentioned, was to bring scientific theories and best practices from academia into consideration when developing the API.
-This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects.
-Based on these factors and clearly expressed ambitions, we conclude that the law of feedback system is true for APIs.
-
-\section{Discussion} \label{discussion}%Reviewed by JW
-Our results have provided valuable insight into the motives behind the evolution of APIs.
-The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
-Based on the results, we have formulated the subsequent outcomes.
-
-\subsection{Discussion RQ1}  %Reviewed by JW
+\subsubsection{Summary}
 
@@
 
-\subsection{Discussion RQ1.1}
+\subsection{Reverse Results}
 
@@
 Our predictions were accurate enough to allow us to form a reliable conclusion which provided valuable discussion with the case company.
+
+\subsection{RQ2 Results} \label{results_rq2} 
+\noindent
+RQ2: \textbf{How do APIs ``passively'' evolve?}
+\smallskip
+
+The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs.
+A summary of our findings can be seen in Table \ref{table:lehman}.
+
+\begin{table}
+       \centering
+       \begin{tabular}[ht]{l|c}
+              \toprule
+
+              \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
+              Continuing Change                         & True                      \\ \hline
+              Increasing Complexity                     & Kinda                     \\ \hline
+              Self Regulation                           & True                      \\ \hline
+              Conservation of Organisational Stability  & False                     \\ \hline
+              Conservation of Familiarity               & True                      \\ \hline
+              Continuing Growth                         & True                      \\ \hline
+              Declining Quality                         & Kinda                     \\ \hline
+              Feedback System                           & True                      \\
+
+              \bottomrule
+
+       \end{tabular}
+       \caption{The applicability of Lehman's laws}
+       \label{table:lehman}
+\end{table}
+
+\smallskip \noindent
+\textbf{Continuing Change} 
+The case company described that including new functional content was one of the top priorities for the release of version 2.0.
+This is supported by the characteristic of the changes identified in this study.
+4 of the 13 changes were additions of new modules, and additional functionality was also added to re-implemented modules.
+It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could cause.
+One of the main reasons for continuously adapting the API is also to control the way API users use the API.
+Prior to version 2.0 being released, a number of API users used workarounds to implement applications which contained functionality which was not yet offered from the API.
+These applications were fully functional, but there existed no standard method of implementation.
+We therefore conclude that the law of continuing change holds for APIs.
+
+\smallskip \noindent
+\textbf{Increasing Complexity} \label{sec:law2} 
+A majority of the changes introduced in version 2.0 aimed to improve the structure and the way that the API was used.
+Many of these changes were related to the same design choices, which enforced a certain implementation style on the whole API.
+One example of this is the change to the interfaces which set a standard for the whole API.
+During the interview it was also concluded that consistency and following certain standards is an important factor to consider when designing APIs.
+It was also made clear that a contributing factor for changing certain parts of the API was to bring it into line with the new interface design.
+The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that the company currently did not make use of these.
+Even though the importance of maintaining the API in order to reduce complexity was stated, arguments which support that it is of lesser importance than releasing functional content was also presented.
+One example of where this is evident in the evolution of the API, is in the module that handles the video capturing and video stream.
+It was decided that this module would not be re-designed to conform with the new interface standard, as the changes to functionality in this module were very minor.
+Thus, the law of increasing complexity holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.
+
+\smallskip \noindent
+\textbf{Self Regulation} \label{sec:law3} 
+The release of version 1.4 did not include any changes related to the API interface.
+Version 1.0 through to 1.4 strictly added support for additional build target platforms.
+When comparing the changes introduced in version 2.0 to the ones in previous versions, it is clear that the growth of the API has gradually increased.
+During the interview it was also mentioned that the future plans for the API did not include any major changes and that only a few minor changes were planned in the near future.
+The future updates to the API will also be made incrementally and there will not be a big bang update similar to that of version 2.0.
+This supports that the law of self regulation applies to APIs, assuming that version 2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
+
+\smallskip \noindent
+\textbf{Conservation of Organisational Stability} 
+The changes to the API have been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
+As mentioned in Section \ref{sec:law3}, the changes introduced in version 1.4 did not involve any changes to the existing API functions.
+Consequently, the only significant update to the API was made in the transition to version 2.0.
+The internal development of the API has also been made sporadically and there have been periods where the API has not been actively developed.
+This suggests that the law of conservation of organisational stability does not apply to APIs.
+
+\smallskip \noindent
+\textbf{Conservation of Familiarity} 
+The documentation that is included with the API was rigorously updated with the introduction of version 2.0.
+All functionality which was added or modified in version 2.0 was updated accordingly in the documentation.
+The same pattern can be seen for the example code, which went through major changes as a result of the changes to the API code.
+The case company's intent to control the way that their API is used also suggests that the knowledge of how to use the API is of importance, since if the API is used in too many different ways, it will be more difficult for the case company to have relevant documentation and example code.
+It was also expressed during the interview that further transparency in how the API should be used could be achieved.
+One example mentioned of how this could be achieved is by improving the expressiveness regarding which API functions are supported on which hardware types.
+These facts support that the law of conservation of familiarity is true for APIs.
+
+\smallskip \noindent
+\textbf{Continuing Growth} 
+Large parts of the changes between the versions were strictly additions of new functional content.
+4 new modules were added and significant additions of new functionality were added to the modules which were re-designed from version 1.4.
+The interviewee also made it clear that increasing the functionality was one of the main goals with the 2.0 update.
+This also ties in with the ambition of controlling the way that the API is used, as mentioned previously.
+It was also mentioned that the case company had received feedback from the API users that more frequent updates to the functional content was desirable, even though this may require them to update their application code.
+We therefore conclude that the law of continuing growth applies to APIs.
+
+\smallskip \noindent
+\textbf{Declining Quality} 
+The interviews established that a groomative motive was not the primary reason for implementing any change.
+The changes to the example code and the documentation, as well as the re-designed modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content.
+These changes did, however, also increase the quality and were a substantial part of the update.
+A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{sec:law2}.
+We therefore settle that the law of declining quality can be applied to APIs, but that there is data that implies that reducing quality is not of high importance.
+
+\smallskip \noindent
+\textbf{Feedback System} 
+One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
+Currently, only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users.
+The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users and which leads to good applications being developed.
+Prior to version 2.0 being released, an example of how the API users were included in the feedback loop was when they implemented functionality related to sound, despite the fact there was no interface for this.
+The experiences of this API user, were later considered when developing the axsound module.
+One benefit of having a more structured feedback loop, would be that the API developers would have greater awareness of potential errors in the implementation of the API.
+Another ambition which was mentioned, was to bring scientific theories and best practices from academia into consideration when developing the API.
+This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects.
+Based on these factors and clearly expressed ambitions, we conclude that the law of feedback system is true for APIs.
+
+\section{Discussion} \label{discussion}
+Our results have provided valuable insight into the motives behind the evolution of APIs.
+The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
+Based on the results, we have formulated the subsequent outcomes.
+
+\subsection{Discussion RQ1}
+
+\subsection{Discussion RQ1.1}
 
@@
 \end{document}
+
+% \subsection{RQ1 Results} \label{results_rq1} %Reviewed by JW
+% \noindent
+% RQ1: \textbf{How do companies actively drive API evolution?}
+
+% \noindent
+% RQ1.1: \textbf{To what extent can we reverse engineer API change decisions?}
+% \smallskip
+
+% Many changes were found between version 1.4 and version 2.0.
+The initial inspection revealed there to be many deprecations which were later re-implemented as new modules.
+We have group these changes into a single change instead of a deprecation and a re-implementation.
+In total, thirteen unique changes were found.
+These changes are shown in Table \ref{table:categories}.
+
+% The changes have been divided up into four specific categories, namely: \textit{new}, \textit{modified}, \textit{removed} and \textit{general trends}.
+The category \textit{new} concerns additions of modules, \textit{modified} concerns modifications to modules that existed in version 1.4 and \textit{removed} are changes where functionality was removed being deprecated or replaced by functionality.
+\textit{General trends} are broad changes that are mainly related to design.
+
+% After cross-examining our results with the interviewee and their responses, we found that 78\% of our main category predictions matched the actual motive of the changes and that 78\% of our secondary categorisations matched the actual motives.
+
+% \begin{table}
+%        \centering
+%        \begin{tabular}[ht]{c !{\vrule width 1.5pt} c|c !{\vrule width 1.5pt} c|c} 
+%               \toprule
+
+%               \multirow{2}{*}{\textbf{Change}}          & \multicolumn{2}{c !{\vrule width 1.5pt} }{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Sub}}        \\ \cline{2-5}
+
+%                                    & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \Xhline{2\arrayrulewidth}
+%               axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
+%               axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
+%               axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
+%               axserialport         & E                         & E                         & N/A                       & N/A                \\ \hline
+%               axevent              & E                         & E                         & G                         & G                  \\ \hline
+%               axhttp               & E                         & E                         & G                         & G                  \\ \hline
+%               ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
+%               Burst Mode           & R\textsubscript{d}        & R\textsubscript{d}        & N/A                       & N/A                \\ \hline
+%               Example Code         & U                         & R\textsubscript{f}        & R\textsubscript{f}        & U                  \\ \hline
+%               Documentation        & U                         & U                         & R\textsubscript{f}        & R\textsubscript{f} \\ \hline
+%               Interfaces           & G                         & P                         & P                         & G                  \\ \hline
+%               3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
+%               Error Handling       & P                         & P                         & G                         & G                  \\
+
+%               \bottomrule
+%        \end{tabular}
+%        \caption{Categorisation of Changes }
+%        \label{table:categories}
+% \end{table}
+
+% \subsubsection{axptz} %Reviewed by JW
+% The Pan, Tilt and Zoom (ptz) module concerns functionality related to manoeuvring the camera, both mechanically and digitally.
+We concluded that this change was enhancive, because it is a new feature of the API.
+There was no secondary motive behind this change, as the change was purely enhancive.
+The interviewee described how this change, as well as the other changes classified as additions, were all included in the new API at the request of API users.
+Prior to the change being introduced, there was no API functionality for controlling the camera and as such, it was a high priority addition to the new API.
+The interviewees' comments allowed us to conclude that we had correctly identified the change as being enhancive.
+Furthermore, we were also correct in our prediction that there was no secondary change category.
+
+% \subsubsection{axaudio} %Reviewed by JW
+% The most important functionality of the camera is to capture and analyse video data, however, some API users require the ability to analyse audio data.
+The addition of axaudio allows API users to perform audio analysis of audio streams captured by cameras.
+This change was determined to be enhancive, as it was an addition of a new feature to the API.
+We found no secondary motive for the change.
+Audio analysis had previously not been supported in version 1.4 of the API.
+However, during the interview, it was revealed that an API user had managed to implement their own audio analysis application using version 1.4 of the API.
+Given the apparent demand for audio analysis, it was included in version 2.0 of the API.Taking into account the interviewee's reasoning, we concluded that we had successfully determined that the change was enhancive.
+The addition of axaudio had no secondary motive.
+
+% \subsubsection{axstorage} %Reviewed by JW
+% Prior to the newest version of the API being released, the sole alternative for storing data was to use the Video Management System.
+Version 2.0 added the possibility of alternative storage solutions, by allowing the camera to interface with external storage devices, such as SD cards.
+Enhancive was chosen to be the primary category of change, given that axstorage was a new addition to version 2.0.
+No secondary motive was identified.
+The interviewee described how limited storage options for the cameras, in version 1.4, was the reason that increased functionality was strongly requested by API users.
+As such, axstorage was included in version 2.0 of the API.The information gathered from the interview therefore supported our original categorisation; it was an enhancive change.
+No secondary category was established.
+
+% \subsubsection{axserialport} %Reviewed by JW
+% The addition of axserialport allows API users to connect various devices to the cameras through the use of a serial port.
+This allows users to integrate multiple devices to create their own unique solutions.
+This was not possible in version 1.4 of the API.
+The addition of this module was determined to be an enhancive change, as it involved the addition of a new feature.
+No relevant secondary category was identified.
+The addition of axserialport was requested by API users to allow them to connect the cameras to other devices.
+A possible use case, that was given during the interview, involved a ticketing system which allows for joint analysis of data from multiple devices.
+As such, it was included in version 2.0, to meet the demand of the API users.
+Given this information, we concluded that we were correct in categorising this change as enhancive.
+The categorisation of the secondary category was also correct.
+
+% \subsubsection{axevent} %Reviewed by JW
+% Version 2.0 of the API was designed to be an event-driven system that makes use of callbacks.
+To achieve this, the old event system had to be re-designed.
+The new design is used by all features of version 2.0 of the API.
+An example of when an event would be generated, is when the camera detects movement.
+Given that this module was a re-implementation of the previous event system, we concluded that it should be categorised mainly as an enhancive change with the secondary change as groomative.
+Groomative was chosen as the secondary category due to the additional motive of bringing the new functionality into line with the new design.
+The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implementation of the new event system.
+One reason was that the case company was dissatisfied with certain usability aspects of API version 1.4.
+The module was then completely re-implemented and re-designed according to the new system design of version 2.0.
+From the discussion in the interview, it was clear that both of our categorisations were correct.
+The change was primarily enhancive and secondarily groomative.
+
+% \subsubsection{axhttp} %Reviewed by JW
+% The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically send data to web pages.
+The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards, and at the same time, additional functionality was added to the module.
+This change re-implemented an existing module while adhering to the new design of API version 2.0.
+The main categorisation therefore was chosen to be enhancive with groomative as the secondary category.
+The interviewee described that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, within the standards of the new design.
+Our categorisation of enhancive and groomative was therefore correct for this change.
+The primary intent was to add functionality while also allowing the re-implementation to make use of the new API design.
+
+% \subsubsection{ax\_parameter} %Reviewed by JW
+% The parameter setting module of the API allowed data and application settings to be saved so that they are not lost if the device is not running.
+This module was re-implemented as ax\_parameter with added functionality and conformance to the new design standards of API version 2.0.
+Given that this change re-implemented an existing module while also incorporating the new design standards, it has been categorised as being primarily enhancive with a secondary category of groomative.
+The interviewee clarified that this change was mainly concerned with re-implementing existing functionality, while simultaneously adopting the new standards of version 2.0.
+Given the information from the interview, we concluded that this change was correctly categorised; the primary intent was enhancive and the secondary intent was groomative.
+
+% \subsubsection{Burst Mode} %Reviewed by JW
+% The burst mode feature of the API allowed users to buffer a series of images for greater analysis.
+This feature was deprecated during the transition between version 1.4 and 2.0 and was not re-implemented.
+This change presented itself as a clear example of reductive maintenance, as it was simply removed and without being replaced.
+We therefore gave no secondary categorisation for this change.
+The interviewee described, that in order to continue using this feature, it would have to be re-implemented.
+An impact assessment was undertaken to determine if the removal of the function would be costly.
+Ultimately, the negative effects were not deemed significant enough and thus the function was removed of the API.
+We can therefore conclude that we correctly categorised this change as reductive and that there are indeed, no secondary categories to describe this change.
+
+% \subsubsection{Example Code} %Reviewed by JW
+% The case company included a selection of example programs to assist developers with creating applications.
+This trend continued in version 2.0, but there were some significant improvements.
+The number of example programs and the amount of comments accompanying the code increased, thus improving quality of the examples.
+We therefore concluded that this change was updative, as the example code was updated according to the new API and the new techniques that it utilises.
+We further decided that this change also had a secondary category of reformative.
+During the interview, it became clear that the improvement of the example code was an important change between the two versions.
+The interviewee described how the examples were used frequently by their customers, however, the old examples had many varied implementation techniques, even for similar tasks.
+This ultimately meant that the old examples were not satisfactory and that new examples would have to be written, preferably conforming to the same standards.
+The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.
+With this information, we concluded that our categorisation was incorrect.
+It became clear that this change was, in actual fact, primarily reformative.
+It was also clear that the subcategory should therefore have been updative.
+
+% \subsubsection{Documentation} %Reviewed by JW
+% As the API code was updated in version 2.0, the API documentation was updated to correspond with the new code.
+While there were no substantial changes, we found that the documentation is no longer offered as a PDF but is instead only offered as HTML.
+We categorised this change as being updative with a reformative secondary category for the reasons that the change only updated the documentation to reflect the recent changes in version 2.0.
+This sentiment was shared by the interviewee; the documentation was only changed according to the current workings of the API and how the new modules interact with each other.
+We can therefore say that our categorisations were correct, the change was updative and reformative.
+
+% \subsubsection{Interfaces} %Reviewed by JW
+% Version 1.4 of the API allowed direct access to the headers of each module available in the API.
+Version 2.0 changed this by including interfaces through which functionality is accessed.
+This design change has had an effect on the whole API, as it has changed the structure of modules, but not the functionality of them.We therefore concluded that this change would be best categorised as  groomative.
+The secondary category was categorised as preventive, as the change could be seen as an attempt to reduce future maintenance.
+The interview provided further insight into the reasoning behind this design change.
+Improvements to coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to use interfaces in versions 2.0 of the API.
+Furthermore, the re-design would hopefully avoid future maintenance, while also allowing the system to be easily extended.
+Taking this information into account, we concluded that our categorisation was incorrect.
+The interview showed that the primary categorisation should have been preventive, given the strong emphasis on avoiding future maintenance and improving usability.
+We further concluded that the secondary change should have been groomative, to better reflect the intent of improving the APIs maintainability.
+
+% \subsubsection{3\textsuperscript{rd} Party}
+% %% REMEMBER TO PROVIDE LINK TO GLIB:::: - https://developer.gnome.org/glib/
+% ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
+% %%Describe the change 
+% 2.0 utilises more 3rd party libraries
+% axsound, for example, uses alsa
+% All modules use glib
+% The advent of the new API saw the inclusion of new 3\textsuperscript{rd} party libraries.
+For example, axsound utilises a library called Alsa, all interfaces use Glib and daemons have been provided for using D-Bus.
+These changes potentially make the library much more flexible both for the API designers in terms of features they can provide and for the application developers in terms of applications they can develop.
+% We therefore gave this change the main categorisation of adaptive with no suitable sub-categories being found.
+% The architects creating the API decided they wished to use Glib which came about primarily from internal discussions at the company.
+% %%Relate it to Categories
+% Architects decided to use glib, part of an internal decision. 
+% Glib (!!!ref to website) was therefore introduced to the new API to help alleviate this 
+% The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API.
+However, it was expressed to us that the error handling would have changed between versions regardless of whether or not Glib was included.
+(!!!This is also too assume-y)
+
+% \subsubsection{Error Handling} %Reviewed by JW
+% A substantial change included in version 2.0 was the addition of header files, containing enums of error codes.
+While it was not evident how the error handling was implemented prior to version 2.0, we concluded that it had changed, given the addition of the new header files.
+We therefore categorised this change as being primarily preventive, as error handling is preventive by nature.
+Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability.
+During the interview, it was made clear that the previous error handling was lacking in expressiveness and usability.
+Glib was added to version 2.0 and the error handling functionality that Glib provides was incorporated into the new API design.
+We therefore concluded that our categorisation for this change was correct.
+The primary reason for the change was to improve the existing error handling while conforming to the new API standard.

### 2015-05-11 thesis/paper.tex
More re-strucutring
Results structure

@@
 \item[\textbf{RQ1}] How do companies actively drive API evolution?
-\item[\textbf{RQ1.1}] To what extent can we reverse engineer API change decisions?
-\item[\textbf{RQ2}] How do APIs ``passively'' evolve?
+\item[\textbf{RQ2}] To what extent can we reverse engineer API change decisions?
+\item[\textbf{RQ3}] How do APIs ``passively'' evolve?
 
@@
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ1.1}.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ2}.
 
@@
 
-%Lehman's - RQ2
-The analysis of the trends and the changes, combined with information gathered during the interview, allowed us to answer \textbf{RQ2} by determining if Lehman's laws are applicable to the changes to the API \cite{lehman1980programs}.
+%Lehman's - RQ3
+The analysis of the trends and the changes, combined with information gathered during the interview, allowed us to answer \textbf{RQ3} by determining if Lehman's laws are applicable to the changes to the API \cite{lehman1980programs}.
 
-%RQ1.1
-The final stage of analysis was conducted once all the data had been analysed, which allowed us to answer \textbf{RQ1.1}.
+%RQ2
+The final stage of analysis was conducted once all the data had been analysed, which allowed us to answer \textbf{RQ2}.
 This was accomplished by comparing our analysis and interpretation of the change motives against the opinions expressed during the interview.
 Success was determined by the amount of correct interpretations made about the motives of the changes.
-Our ability to correctly predict the motives, compared to the designers' actual motives which were made clear during the interviews, served as the basis for answering \textbf{RQ1.1}.
+Our ability to correctly predict the motives, compared to the designers' actual motives which were made clear during the interviews, served as the basis for answering \textbf{RQ2}.
 
@@
 
+\newpage
+
 \section{Results} \label{results} 
 This section will present the findings of our study.
-The results related to \textbf{RQ1} and \textbf{RQ1.1} are introduced in Section \ref{results_rq1}, and the results of \textbf{RQ2} are presented in Section \ref{results_rq2}
+The results related to \textbf{RQ1} and \textbf{RQ2} are introduced in Section \ref{results_rq1}, and the results of \textbf{RQ3} are presented in Section \ref{results_RQ3}
 
@@
 \textbf{Enhancive  }
+We have found enhancive changes to be a large part of the API's evolution. Examples are...
 
@@
 \textbf{Corrective  }
+Corrective changes have been a driving force for the evolution of the API...
 
@@
 \textbf{Reductive  }
+Only one reductive change was found...
 
@@
 \textbf{Adaptive  }
+No adaptive changes were found
 
@@
 \textbf{Performance  }
+No identified changes could be related to performance...
 
@@
 \textbf{Preventive  }
+Preventive changes were...
 
@@
 \textbf{Groomative  }
+A couple of groomative changes were found...
 
@@
 \textbf{Updative  }
+Updative changes only affected documentation and not code...
 
@@
 \textbf{Reformative  }
+Blabla...
 
@@
 \textbf{Evaluative  }
+Blabla...
 
@@
 \textbf{Consultive  }
+Blabla...
 
@@
 \textbf{Training  }
+Blabla...
 
@@
 
-\subsection{Reverse Results}
+\newpage
+\subsection{RQ2 Results}
 
@@
 
-\subsection{RQ2 Results} \label{results_rq2} 
+\newpage
+
+\subsection{RQ3 Results} \label{results_RQ3} 
 \noindent
-RQ2: \textbf{How do APIs ``passively'' evolve?}
+RQ3: \textbf{How do APIs ``passively'' evolve?}
 \smallskip
 
-The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs.
+The results related to \textbf{RQ3} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs.
 A summary of our findings can be seen in Table \ref{table:lehman}.
@@
 \end{table}
+
+\subsubsection{Lehman's Laws}
 
@@
 
-\section{Discussion} \label{discussion}
-Our results have provided valuable insight into the motives behind the evolution of APIs.
-The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
-Based on the results, we have formulated the subsequent outcomes.
-
-\subsection{Discussion RQ1}
-
-\subsection{Discussion RQ1.1}
-
-\subsection{Discussion RQ2}
+\subsubsection{Summary}
 
@@
 This suggests that including feedback from more sources and using this feedback to improve the evolution process should be a consideration for APIs.
+
+\newpage
+
+\section{Discussion} \label{discussion}
+Our results have provided valuable insight into the motives behind the evolution of APIs.
+The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
+Based on the results, we have formulated the subsequent outcomes.
+
+\subsection{Discussion RQ1}
+
+\subsection{Discussion RQ2}
+
+\subsection{Discussion RQ3}
 
@@
 % \noindent
-% RQ1.1: \textbf{To what extent can we reverse engineer API change decisions?}
+% RQ2: \textbf{To what extent can we reverse engineer API change decisions?}
 % \smallskip

### 2015-05-11 thesis/paper.tex
Tables in BG+Title

@@
 
-\title{Exploring the Types and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
+\title{The Types and Driving Forces of Modifications in the Evolution of an API}
 
@@
 The laws are said to only apply to E-type systems, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.
+
+\begin{table}
+       \centering
+       \begin{tabular}[ht]{l|c}
+              \toprule
+
+              \textbf{Type}                              & \textbf{Explanation}    \\ \midrule
+              Corrective    & [Explanation]                      \\ \hline
+              Reductive     & [Explanation]                     \\ \hline
+              Adaptive      & [Explanation]                      \\ \hline
+              Performance   & [Explanation]                     \\ \hline
+              Preventive    & [Explanation]                      \\ \hline
+              Groomative    & [Explanation]                      \\ \hline
+              Updative      & [Explanation]                     \\ \hline
+              Reformative   & [Explanation]                     \\ \hline
+              Evaluative    & [Explanation]                     \\ \hline
+              Consultive    & [Explanation]                     \\ \hline
+              Training      & [Explanation]                     \\
+
+              \bottomrule
+
+       \end{tabular}
+       \caption{Explanation of Types of Software Maintenance}
+       \label{table:expl_types}
+\end{table}
+
+Adaptive
+
+\begin{table}
+       \centering
+       \begin{tabular}[ht]{l|c}
+              \toprule
+
+              \textbf{Law}                              & \textbf{Explanation}    \\ \midrule
+              Continuing Change                         & [Explanation]                      \\ \hline
+              Increasing Complexity                     & [Explanation]                     \\ \hline
+              Self Regulation                           & [Explanation]                      \\ \hline
+              Conservation of Organisational Stability  & [Explanation]                     \\ \hline
+              Conservation of Familiarity               & [Explanation]                      \\ \hline
+              Continuing Growth                         & [Explanation]                      \\ \hline
+              Declining Quality                         & [Explanation]                     \\ \hline
+              Feedback System                           & [Explanation]                      \\
+
+              \bottomrule
+
+       \end{tabular}
+       \caption{Explanation of Lehman's Laws}
+       \label{table:expl_laws}
+\end{table}
 

### 2015-05-12 thesis/paper.tex
First page
removed factory pattern example

@@
 \category{D.2.7}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and re-engineering]
-\category{K.6.3}{Computing Milieux}{Software Management}[Software Maintenance]
-
-\terms{Theory, Design or Verification/Documentation maybe?}
-
 \keywords{API Design, Software Evolution, Software Maintenance}
@@
 API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}.
-Examples of such decisions include whether or not to make use of the factory pattern or if an API should display errors only at compilation or only at runtime \cite{stylos2006comparing}.
-More trivial design problems, such as assigning names to API features or correctly naming user defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}.
+Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.
+More trivial design problems, such as assigning names to API features or correctly naming user-defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}.
 When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.

### 2015-05-12 thesis/paper.tex
Added kappa test, + review changes

@@
 The concept of software maintenance has existed since the 1960s when it was first introduced to the software development community \cite{lientz1980software}.
-A set of four categories describing software maintenance categories \cite{lientz1980software} became the basis upon which twelve new categories were created \cite{chapin2001types}.
-The twelve categories are: enhancive, corrective, reductive, adaptive, performance, preventive, groomative, updative, reformative, evaluative, consultive and training \cite{chapin2001types}.
-Each category describes a software maintenance activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality \cite{chapin2001types}.
-It has been suggested that software maintenance is a part of software evolution and that the two terms are not interchangeable \cite{chapin2001types}.
+A set of four categories describing different types of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}.
+The twelve types of software evolution and software maintenance, as seen in Table \ref{table:expl_types}, describe a software evolution activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality.
 
@@
 The module and file in which the change was identified was then logged together with an ID and a description of the change.
-The data collection from code and documentation was performed independently by both researchers, to reduce the risk of human errors affecting the results.
+The data collection from code and documentation was performed independently by both John Burchell and William Granli, to reduce the risk of human errors affecting the results.
 If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.
@@
 The data analysis was conducted in two major phases \cite{andersson2007spiral}.
-During the first phase, a hypothesis generating approach \cite{seaman1999qualitative} was used to be able to fulfil the exploratory goal of the study.
+The aim of the first phase was to generate hypotheses \cite{seaman1999qualitative} and to formulate clear research questions.
 It was during this phase that the analysis of the API code and documentation was carried out.
@@
 %Grounded Theory
-The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
+The process used for analysing the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
 %Codes
@@
 \textbf{External validity  } The results of our study should be highly generalisable to similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors.
-Our study should be of special interest to researchers studying platform or embedded APIs.
-The fact that the results of the study are presented in a structured way, by relating them to existing software evolution theories, should further increase the generalisability of our study.
+Our study can especially be compared to similar studies conducted on platform or embedded APIs.
+Further comparability to our study is offered through how the results are structured around established software evolution theories.
 
 \smallskip \noindent
-\textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to a well-reputed guide to case studies \cite{runeson2009guidelines}.
+\textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to an accredited guide to case studies \cite{runeson2009guidelines}.
 In addition to that, strategies from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} \cite{robson2002real} have been used to increase the trustworthiness of the data gathering and data analysis.

### 2015-05-12 kappa.r

@@ -1,0 +1,19 @@
+
+
+library(irr)
+
+
+ours=c("E", "E", "E", "E", "E", "E", "E", "Rd", "U", "U", "G", "A", "P",  "N", "N", "N", "N", "G", "G", "G", "N", "Rf", "Rf", "P", "N", "G")
+hers=c("E", "E", "E", "E", "E", "E", "E", "Rd", "Rf", "U", "P", "A", "P", "N", "N", "N", "N", "G", "G", "G", "N", "U", "Rf", "G", "N", "G")
+
+kappa2(cbind(ours, hers), "unweighted")
+
+
+#Cohen's Kappa for 2 Raters (Weights: unweighted)
+
+# Subjects = 26 
+#   Raters = 2 
+#    Kappa = 0.812 
+
+#        z = 9.15 
+#  p-value = 0 

### 2015-05-12 thesis/paper.tex
Comments

@@
 Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
-There are, however, no studies that attempt to map the motives behind changes to existing software evolution theories, such as the types of software evolution and software maintenance activities \cite{chapin2001types}.
 The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
@@
 Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs.
-Before the industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.
+Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.
 
@@
 This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.
+Follow that, we will introduce the company and API examined in this study.
 
@@
 \end{table}
-
-Adaptive
 
@@
 
+The majority of changes between version 1.4 and version 2.0 have been additions to functionality of the API.
+Such additions include added functionality to mechanically and digitally control the camera, to utilise additional storage devices, to allow serial connectivity and to allow audio analysis on the cameras.
+
+Many of the changes found many deprecations which were later re-implemented as new modules.
+We have grouped these kinds of changes into a single type instead of two.
+Such examples include the deprecation and re-implementation of an event system, dynamic web page generation and configuration utilities.
+
+The remainder of the changes were defined as general trends.
+These changes were not individual, but were instead larger changes that effected the whole API.
+Such examples include a shift towards using interfaces to access features, improved maintainability, a different error-handling approach and the inclusion of additional 3\textit{rd} party libraries.
+
+All of the identified changes have been given a type based the nature of the change according to the Types of Software Evolution and Software Maintenance decision tree \cite{chapin2001types}.
+In total, thirteen unique changes were found.
+These changes are shown in Table \ref{table:categories}.
+
 \smallskip \noindent
 \textbf{Enhancive  }
-We have found enhancive changes to be a large part of the API's evolution. Examples are...
+%Define how we identified the change type
+Additions or re-implementations of functionality are defined to be enhancive changes. In addition to this, we have included deprecations that have then been re-implemented to also be enhancive.
+%Some Data and little explanation
+53.8\% of the identified changes were given the type of enhancive.
+The majority of which were additions of new functionality to the API.
+Two examples of added functionality are the addition of camera movement module and an audio analysis module.
+One example of a deprecation that was re-implemented is the event system.
+%Conclusion
+Given that over half of the changes were identified to be enhancive, we conclude that the APIs evolution primary type of change was enhancive.
 
@@
 \textbf{Corrective  }
-Corrective changes have been a driving force for the evolution of the API...
-
+%Define what kinds of changes these are
+Corrective changes are identified as types of change that fix broken functionality.
+%Data and explanation
+No corrective changes were identified between V1.0 and V2.0.
+There are two main reasons that we did not find any changes of this type.
+Firstly, the majority of changes were additions or re-implementations of functionality.
+This meant that most of the existing code was either removed, replaced or deprecated resulting in little to no obvious fixes.
+Secondly, we only had access to the public facing API and not the implementation itself.
+We therefore could not inspect the inner workings of the functionality that has remained between versions to determine if any corrective change took place.
+%Conclusion
+We therefore conclude that the evolution of the API was not driven by corrective changes.
 \smallskip \noindent
 \textbf{Reductive  }
-Only one reductive change was found...
+%Definition
+Reductive changes are defined as changes that remove or reduce functionality. This is distinctive from a deprecation as reductive types of change remove functionality completely.
+%Data & Explanation
+Only a single reductive type of change was identified.
+This reductive change removed functionality that provided the ability to buffer individual images for closer analysis by a user.
+Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role} \cite{xing2006refactoring}, this was a surprising result.
+%Don't know if I should discuss the finding in this much depth here?
+%If OK - Talk more about the business side of things, and how we couldn't identify this change ourselves
+It was revealed during the interview that the functionality was removed because the case company no longer wished to support this feature, due to hardware constraints. 
+%Conclusion
+As this was the only reductive change found, we conclude that the evolution of the API was not primarily driven by reductive changes.
 
@@
 \subsection{RQ2 Results}
+
+% After cross-examining our results with the interviewee and their responses, we found that 78\% of our main category predictions matched the actual motive of the changes and that 78\% of our secondary categorisations matched the actual motives.
 
@@
        -->Suggest a similar study which looks at business factors
+ in-depth study on each of the laws (more exhaustive) (suggested by Imed during Friday review)
 
@@
        conclusion = summary part, main final points and future work 
+       look up implications for practitioners 
+       recommendations for the case company (need to put this somewhere)
 

### 2015-05-12 thesis/paper.tex
Added new RQ1 results sections. Included sections for Enhancive, Corrective and Reductive changes.

@@
 This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.
-Follow that, we will introduce the company and API examined in this study.
 
@@
 \end{table}
+
+Adaptive
 
@@
        -->Suggest a similar study which looks at business factors
- in-depth study on each of the laws (more exhaustive) (suggested by Imed during Friday review)
 
@@
        conclusion = summary part, main final points and future work
-       look up implications for practitioners 
-       recommendations for the case company (need to put this somewhere)
 

### 2015-05-12 thesis/paper.tex
Re-wrote meth

--- 2015-05-12 thesis/paper.tex
@@
 
+\newpage
+
 \section{Methodology} \label{methodology}
@@
 
-\subsection{Data Collection} \label{data_collection}  %Review 1 or 2 more times (John first)
+The study was conducted in two major phases \cite{andersson2007spiral}.
+The aim of the first phase was to generate hyptheses and to formulate clear research questions.
+This was achieved by using a data-driven approach to analysing the code and documentation.
+The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phsae.
+Both phases were performed iteratively.
+This created the opportunity to improve the data analysis as the study progressed, as well as allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.
+
+The process used for examining the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
+
+\subsection{Data Collection} \label{data_collection}  
 %Intro to code inspection
@@
 \subsection{Data Analysis} \label{data_analysis}
-%Intro and summary
-The data analysis was conducted in two major phases \cite{andersson2007spiral}.
-The aim of the first phase was to generate hypotheses \cite{seaman1999qualitative} and to formulate clear research questions.
-It was during this phase that the analysis of the API code and documentation was carried out.
-The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase.
-Both phases were performed iteratively, together with the data collection.
-This created the opportunity to improve the process of analysis as the study progressed, as well as, allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.
 
-%Grounded Theory
-The process used for analysing the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
 %Codes
-Each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
+To analyse the data each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
 %Concepts
@@
 %RQ1
-The categories identified previously were then classified according to the software maintenance categories \cite{chapin2001types}.
+The trends identified previously were then classified according to the software maintenance types \cite{chapin2001types}.
 The process followed the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}.
-Each of the previously identified categories were given a main category of maintenance and a secondary category, if appropriate.
-This material was then used as a basis for answering \textbf{RQ1}.
-
-%Description of interview analysis
-The results of the interview were analysed and categorised in the same way that our identified changes had been.
-Validation of our findings, by comparing our categorisation against the interviewee's categorisation, was performed at this point.
-
-%Lehman's - RQ3
-The analysis of the trends and the changes, combined with information gathered during the interview, allowed us to answer \textbf{RQ3} by determining if Lehman's laws are applicable to the changes to the API \cite{lehman1980programs}.
+Each of the previously identified trends were given a main type of maintenance and, if appropriate, a secondary type.
+This material, as well as the results of the interview, were then used as the basis for answering \textbf{RQ1}.
 
 %RQ2
-The final stage of analysis was conducted once all the data had been analysed, which allowed us to answer \textbf{RQ2}.
-This was accomplished by comparing our analysis and interpretation of the change motives against the opinions expressed during the interview.
-Success was determined by the amount of correct interpretations made about the motives of the changes.
-Our ability to correctly predict the motives, compared to the designers' actual motives which were made clear during the interviews, served as the basis for answering \textbf{RQ2}.
+To allow us to answer \textbf{RQ2}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview.
+Success was determined by comparing the inter-rater reliability, by performing calculating Cohen's Kappa gathered data.
+
+%RQ3
+The analysis of the changes and trends, combined with the information gathered from the interview, allowed us to answer \textbf{RQ3} by determining if Lehman's Laws apply to the changes made to the API.
 

### 2015-05-12 thesis/paper.tex
Fixed typo preventing compilation

@@
 \textbf{Adaptive  }
-No adaptive changes were found
+%Introduction and definition
+Adaptive changes are defined to be changes which involve changes to technology or resources used. 
+%Data and examples
+A single change was identified as being adaptive; the inclusion of new 3\textit{rd} part libraries.
+Glib existed in version 1.4 of the API its use was increased in version 2.0.
+Furthermore, other libraries were added for audio and data communication.
+
+This type of change made up 7.7\% of the total changes, however it had a broader impact than other individual changes.
+
+%Conclusion
 

### 2015-05-12 thesis/paper.tex
stuff

@@
 \subsection{API Design} \label{api_design}
-API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}.
+API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
+
  Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.
@@
 When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
-One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{stylos2006comparing} \cite{shi2011empirical}.
+One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{stylos2006comparing, shi2011empirical}.
 The design decisions reached during development of an API will affect the overall usability of the API.
@@
 Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman1980programs}.
-The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
-The laws are said to only apply to E-type systems, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.
+The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System.
+The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
 
@@
 \subsection{API Evolution} \label{related_work}
-The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}.
+The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring, shi2011empirical} and Smalltalk \cite{robbes2012developers}.
 Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
@@
 
-%%Possibly add a paragraph here to
+%%Possibly add a paragraph here to motivate the gap more
 
@@
 
-%The case company was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}.
-As such, the goal was to include as many companies as possible in this study.
-
-\newpage
-
 \section{Methodology} \label{methodology}
@@
 The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
-The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}.
+The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, runeson2009guidelines, yin2013case, robson2002real}.
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
@@
 
-The process used for examining the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
+The process used for examining the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines, seaman1999qualitative}.
 
@@
 \smallskip \noindent
-\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types} \cite{lehman1980programs}.
+\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types, lehman1980programs}.
 Due to restricted access to the company's source code, we were not able to include versions prior to version 1.4 in our analysis.
@@
 \textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to an accredited guide to case studies \cite{runeson2009guidelines}.
-In addition to that, strategies from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} \cite{robson2002real} have been used to increase the trustworthiness of the data gathering and data analysis.
+In addition to that, strategies from additional well-established papers \cite{andersson2007spiral, seaman1999qualitative, robson2002real} have been used to increase the trustworthiness of the data gathering and data analysis.
 The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study.
 The semi-structured nature of the interview, might threaten the reproducibility; however, large parts of it were structured around existing theories.
-
-\newpage
 

### 2015-05-12 thesis/paper.tex
Fixed referencing

@@
 APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
-There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api}.
+There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk, mcdonnell2013empirical, robbes2012developers, henning2007api}.
 The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
-Refactoring is the most common change that APIs undergo \cite{dig2005role} \cite{xing2006refactoring}.
+Refactoring is the most common change that APIs undergo \cite{dig2005role, xing2006refactoring}.
 %Software Evolution 
@@
 Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
-The area of programming language APIs is well-explored \cite{hou2011exploring} \cite{shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
+The area of programming language APIs is well-explored \cite{hou2011exploring, shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
 To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.

### 2015-05-12 thesis/paper.tex
Comments

@@
 %Structure of the paper
-The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the background and previously published work that is related to our study.
+The sections following the Introduction are structured as follows: In Section \ref{background}, we present the background and previously published work that is related to our study.
 Section \ref{case_company_description} describes the case company and the API which was studied.
@@
 
-\section{Background} \label{existing_literature}
+\section{Background} \label{background}
 This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.

### 2015-05-12 thesis/paper.tex
More changes to results

--- 2015-05-12 thesis/paper.tex
@@
 \subsection{API Design} \label{api_design}
-API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
-
+API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating} \cite{bloch2008effective} \cite{stylos2006comparing}.
 Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.
@@
 When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
-One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{stylos2006comparing, shi2011empirical}.
+One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{stylos2006comparing} \cite{shi2011empirical}.
 The design decisions reached during development of an API will affect the overall usability of the API.
@@
 Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman1980programs}.
-The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System.
-The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
+The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}.
+The laws are said to only apply to E-type systems, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.
 
@@
 \subsection{API Evolution} \label{related_work}
-The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring, shi2011empirical} and Smalltalk \cite{robbes2012developers}.
+The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring} \cite{shi2011empirical} and Smalltalk \cite{robbes2012developers}.
 Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
@@
 
-%%Possibly add a paragraph here to motivate the gap more
+%%Possibly add a paragraph here to
 
@@
 
+%The case company was selected using convenience sampling \cite{flyvbjerg2006five} and a maximum variation strategy was used \cite{benbasat1987case}.
+As such, the goal was to include as many companies as possible in this study.
+
 \section{Methodology} \label{methodology}
@@
 The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
-The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, runeson2009guidelines, yin2013case, robson2002real}.
+The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}.
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
@@
 
-The process used for examining the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines, seaman1999qualitative}.
+The process used for examining the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
 
@@
 \smallskip \noindent
-\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types, lehman1980programs}.
+\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types} \cite{lehman1980programs}.
 Due to restricted access to the company's source code, we were not able to include versions prior to version 1.4 in our analysis.
@@
 \textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to an accredited guide to case studies \cite{runeson2009guidelines}.
-In addition to that, strategies from additional well-established papers \cite{andersson2007spiral, seaman1999qualitative, robson2002real} have been used to increase the trustworthiness of the data gathering and data analysis.
+In addition to that, strategies from additional well-established papers \cite{andersson2007spiral} \cite{seaman1999qualitative} \cite{robson2002real} have been used to increase the trustworthiness of the data gathering and data analysis.
 The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study.
@@
 
-\subsubsection{Categories of Maintenance}
-
 The majority of changes between version 1.4 and version 2.0 have been additions to functionality of the API.
 Such additions include added functionality to mechanically and digitally control the camera, to utilise additional storage devices, to allow serial connectivity and to allow audio analysis on the cameras.
+Pure additions to the API did not have any secondary types of change attributed to them.
 
@@
 Such examples include the deprecation and re-implementation of an event system, dynamic web page generation and configuration utilities.
+These kinds of changes often had a secondary type of change that accompanied the primary type of change.
 
@@
 Such examples include a shift towards using interfaces to access features, improved maintainability, a different error-handling approach and the inclusion of additional 3\textit{rd} party libraries.
+With the exception of 3\textit{rd} party libraries, the general trends have secondary changes which help to categories what effect the changes had on the API.
 
@@
 This reductive change removed functionality that provided the ability to buffer individual images for closer analysis by a user.
-Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role} \cite{xing2006refactoring}, this was a surprising result.
+Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role, xing2006refactoring} this was a surprising result.
 %Don't know if I should discuss the finding in this much depth here?
@@
 Furthermore, other libraries were added for audio and data communication.
-
 This type of change made up 7.7\% of the total changes, however it had a broader impact than other individual changes.
-
 %Conclusion 
+The evolution of the API has not been primarily driven by adaptive changes.
+However, more information, possibly in the form of another study, would be required to fully conclude if these types of changes have a greater impact upon the evolution of an API.
 
@@
 \textbf{Performance  }
-No identified changes could be related to performance...
+%Define
+Performance changes are defined to be types of change that intentionally alter system performance.
+%Data and examples
+No performance types of change were identified in the API.
+Only having access to the public API and not the implementation meant that we were unable search for performance changes in existing code between the versions.
+There was no indication from the documentation nor the interview that any change had been performed with the intent of increasing system performance.
+%Conclusion
+As such, we conclude that the evolution of the API was not driven by performance changes.
+A proper benchmark could be performed on sample programs written with both versions of the API to test overall performance.
+However, this is outside the scope of our study.
 
@@
 \textbf{Preventive  }
-Preventive changes were...
+%Define
+Preventive changes are defined to be changes that attempt to avoid future maintenance. This should not be confused with changes that attempt to make the current state of the system more maintainable.
+%Data and examples
+15.8\% of the changes were given the type of Preventive.
+A new error handling system was one of these changes.
+It is unclear from version 1.4 what error handling was in place, however, version 2.0 saw the addition of specific error handling modules and functions.
+According to the interview, the error handling change coincided with the inclusion of more Glib features, which the new error handling system uses.
+The redesign of the system to use more interfaces was also deemed as a preventive change.
+Using interfaces to access modules helps to make them more maintainable and more easily extendable, which is a good example of a preventive change.
+%Concusion
+Preventive types of change appear to drive the evolution of an API more strongly than other types of changes do.
+This could be due to the fact that as the API grows, the need for higher maintenance also increase, a fact that also seems to be supported by Lehman's laws.
 
@@
 \textbf{Groomative  }
-A couple of groomative changes were found...
+%Define
+Groomative changes are defined to be changes that aim to make the code more maintainable immediately. This should not be confused with preventive changes.
+%Data and examples
+While none of the change identified were primarily groomative changes, three of them were secondarily categorised as being groomative.
+This seems to indicate that the groomative nature of a change is often a bonus of other kinds of changes.
+The move towards using interfaces can be seen as an example of this.
+While the primary motive of change was to make the API more maintainable in the future, making the API more maintainable immediately was also a reason for the change.
+%Conclusion
+While not a primary factor for any of the changes, groomative types of change should still be viewed as important for API evolution.
 
@@
 \textbf{Updative  }
-Updative changes only affected documentation and not code...
+%Define
+Updative changes are defined to be changes to documentation and are not changes that affect functionality in any way.
 
@@
 \textbf{Reformative  }
-Blabla...
+%Define
+Reformative changes are defined to be changes that update the documentation to the stakeholders needs.
 
 \smallskip \noindent
-\textbf{Evaluative  }
-Blabla...
-
-\smallskip \noindent
-\textbf{Consultive  }
-Blabla...
-
-\smallskip \noindent
-\textbf{Training  }
+\textbf{Evaluative, Consultive and Training  }
+%Define
 Blabla...
@@
 
-\newpage
 \subsection{RQ2 Results}
@@
 Our predictions were accurate enough to allow us to form a reliable conclusion which provided valuable discussion with the case company.
-
-\newpage
 
@@
 This suggests that including feedback from more sources and using this feedback to improve the evolution process should be a consideration for APIs.
-
-\newpage
 

### 2015-05-12 thesis/paper.tex
Finished new RQ1 Draft

@@
 Updative changes are defined to be changes to documentation and are not changes that affect functionality in any way.
+We also considered updates to example code and other training material to be Updative types of change.
+%Data and example
+A single change was determined to be Updative.
+This change was the updating of the API documentation to match the new API.
+The updates included a new API specification, deprecation list and the inclusion of the new features and libraries.
+%Conclusion
+Updative changes have very little impact on the functionality of the API yet they are still important changes for the usability of the API \cite{shi2011empirical}.
+We therefore conclude that the evolution of an API is not driven by updative changes.
 
@@
 Reformative changes are defined to be changes that update the documentation to the stakeholders needs.
+%Data and Example
+One reformative change was identified between version 1.4 and version 2.0 which involved a re-write of the existing example programs.
+The aim of the re-write was to update the examples to take advantage of the new functionality in the API while simultaneously showing how the modules interact and presenting a standard for how to use the API correctly.
+%Conclusion
+The reformative change that was found indicates therefore that updating documentation and example code is to some extent import for API evolution.
 
@@
 %Define
-Blabla...
+Evaluative, Consultive and Training are all types of activities, rather than changes that a system can undergo.
+Evaluative activities are defined as activities such as auditing or evaluating the software.
+Similarly, consultive activities involve consultations with customers about the software.
+Finally, Training activities involve training for customers and users of the software.
+%Data and example
+None of the aforementioned activities occurred as part of the APIs evolution as these activities do not play a role in API evolution.
+This is supported by the fact none of the activities were identified for the changes.
+%Conclusion
+We can therefore conclude that these change types are not important for API evolution.
 

### 2015-05-13 thesis/paper.tex
Minor changes to RQ1 sections

@@
 In total, thirteen unique changes were found.
-These changes are shown in Table \ref{table:categories}.
 
@@
 %Data and explanation
-No corrective changes were identified between V1.0 and V2.0.
+No corrective changes were identified between v1.0 and v2.0.
 There are two main reasons that we did not find any changes of this type.
 Firstly, the majority of changes were additions or re-implementations of functionality.
-This meant that most of the existing code was either removed, replaced or deprecated resulting in little to no obvious fixes.
+This meant that most of the existing code was either removed, replaced or deprecated, resulting in little to no obvious fixes.
 Secondly, we only had access to the public facing API and not the implementation itself.
@@
 This focus upon functionality was also emphasised partially due to a business goal.
-The more features the API can provide, the more applications developers can create for the cameras.
-This has a domino effect of increasing the appeal and therefore value of the products.
+The more features the API provides allows for more applications to be created for the cameras.
+This has a domino effect of increasing the appeal and value of the products the case company produces.
 
@@
 Groomative motives were only found to be secondary, and were never the main motive for a change.
-Changes to the example code are an instance of this.
+Changes to the example code are an example of this.
 The example code was updated purely to reflect the changes in functionality and not as a groomative effort.
@@
 \textbf{A majority of the laws apply  } %Reviewed by JW
-Sufficient evidence was found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System to establish that they apply to APIs.
+Evidence was found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System to establish that they apply to APIs.
 The most prominent explanation for this is that a large part of the introduced changes were related to functionality.

### 2015-05-13 thesis/paper.tex
Notes in disc

@@
 \usepackage{fixltx2e}
+
+\usepackage{url}
 
@@
 
+Implications for Practice tips: 
+       3.
+Each implications for practice section should include descriptions of a) problematic issue(s) being addressed, b) the specific audience(s) to which implications are addressed, c) a small number of recommendations about what the audience should/could/should not do based on the research findings, d) an expected outcome of carrying out recommendation(s), and e) some specific illustrations of what carrying out the recommendations might look like, perhaps in narrative form.
+
+\url{https://www.princeton.edu/futureofchildren/publications/journals/article/index.xml?journalid=46&articleid=212&sectionid=1379}
+
 \section{Acknowledgements}

### 2015-05-13 thesis/paper.tex
Changed Lehman source

@@
 
-%%Lehman's laws (!!!improve later)
-Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman1980programs}.
+%Re-write this section... it's wrong
+Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}.
 The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System.
@@
 The interview was conducted using a semi-structured approach \cite{robson2002real}.
-Structure to the interview was provided by organising it around the software evolution theories \cite{chapin2001types} \cite{lehman1980programs}.
+Structure to the interview was provided by organising it around the software evolution theories \cite{chapin2001types, lehman90sview}.
 Investigative and open-ended questions related to each category and law were asked to provide a basis for comparison between the answers and our initial analysis.
@@
 \smallskip \noindent
-\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types, lehman1980programs}.
+\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types, lehman90sview}.
 Due to restricted access to the company's source code, we were not able to include versions prior to version 1.4 in our analysis.
@@
 
-The results related to \textbf{RQ3} are structured around each of Lehman's laws of software evolution \cite{lehman1980programs} and to what extent our findings show that the laws apply to platform APIs.
+The results related to \textbf{RQ3} are structured around each of Lehman's laws of software evolution \cite{lehman90sview} and to what extent our findings show that the laws apply to platform APIs.
 A summary of our findings can be seen in Table \ref{table:lehman}.

### 2015-05-13 thesis/paper.tex
Added table to show counts of types. Included some brief explanations of the types of change for the introduction

@@
               \textbf{Type}                              & \textbf{Explanation}    \\ \midrule
-              Corrective    & [Explanation]                      \\ \hline
-              Reductive     & [Explanation]                     \\ \hline
-              Adaptive      & [Explanation]                      \\ \hline
-              Performance   & [Explanation]                     \\ \hline
-              Preventive    & [Explanation]                      \\ \hline
-              Groomative    & [Explanation]                      \\ \hline
-              Updative      & [Explanation]                     \\ \hline
-              Reformative   & [Explanation]                     \\ \hline
-              Evaluative    & [Explanation]                     \\ \hline
-              Consultive    & [Explanation]                     \\ \hline
-              Training      & [Explanation]                     \\
+              Corrective    & Corrections of functionality                   \\ \hline
+              Reductive     & Reductions of functionality                    \\ \hline
+              Adaptive      & Inclusion of new Technology                    \\ \hline
+              Performance   & Improvements to Performance                    \\ \hline
+              Preventive    & Improvements to future maintainability         \\ \hline
+              Groomative    & Improvements to maintainability                \\ \hline
+              Updative      & Updates to documentation                       \\ \hline
+              Reformative   & Changes to documentation                       \\ \hline
+              Evaluative    & Inspection activities                          \\ \hline
+              Consultive    & Consultations activities                       \\ \hline
+              Training      & Training activities                            \\
 
@@
 In total, thirteen unique changes were found.
+The count of change types is shown in table \ref{table:type_counts}.
+
+\begin{table}
+       \centering
+       \begin{tabular}[ht]{l|c|c}
+              \toprule
+
+              \textbf{Type}                              & \textbf{Main Types}   &\textbf{Sub Types} \\ \midrule
+              Enhancive     & 7 & 0                     \\ \hline
+              Corrective    & 0 & 0                     \\ \hline
+              Reductive     & 1 & 0                    \\ \hline
+              Adaptive      & 1 & 0                     \\ \hline
+              Performance   & 0 & 0                    \\ \hline
+              Preventive    & 2 & 0                     \\ \hline
+              Groomative    & 0 & 5                     \\ \hline
+              Updative      & 1 & 1                    \\ \hline
+              Reformative   & 1 & 1                     \\ \hline
+              Evaluative    & 0 & 0                    \\ \hline
+              Consultive    & 0 & 0                    \\ \hline
+              Training      & 0 & 0                    \\
+
+              \bottomrule
+
+       \end{tabular}
+       \caption{Identified Change Types}
+       \label{table:type_counts}
+\end{table}
 
@@
 
+%Implications for Industry
+%Implications for Academia
+%Future work / suggestions based on this RQ?
+
 \subsection{Discussion RQ2}

### 2015-05-13 thesis/paper.tex
Added glib to bib, cited it in the text. Also removed percentages from the results as the table only shows counts.

@@
 %Some Data and little explanation
-53.8\% of the identified changes were given the type of enhancive.
+Seven of the identified changes were given the type of enhancive.
 The majority of which were additions of new functionality to the API.
@@
 A single change was identified as being adaptive; the inclusion of new 3\textit{rd} part libraries.
-Glib existed in version 1.4 of the API its use was increased in version 2.0.
+Glib \cite{Glib} existed in version 1.4 of the API its use was increased in version 2.0.
 Furthermore, other libraries were added for audio and data communication.
-This type of change made up 7.7\% of the total changes, however it had a broader impact than other individual changes.
 %Conclusion 
@@
 %Data and examples
-15.8\% of the changes were given the type of Preventive.
+Two changes were identified to be Preventive types of change.
 A new error handling system was one of these changes.

### 2015-05-18 thesis/paper.tex
More minor changes to text
RQ2 RQ3 swap

@@
 \item[\textbf{RQ1}] How do companies actively drive API evolution?
-\item[\textbf{RQ2}] To what extent can we reverse engineer API change decisions?
-\item[\textbf{RQ3}] How do APIs ``passively'' evolve?
+\item[\textbf{RQ2}] How do APIs ``passively'' evolve?
+\item[\textbf{RQ3}] To what extent can we reverse engineer API change decisions?
 
@@
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ2}.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ3}.
 
@@
 %RQ2
-To allow us to answer \textbf{RQ2}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview.
-Success was determined by comparing the inter-rater reliability, by performing calculating Cohen's Kappa gathered data.
+The analysis of the changes and trends, combined with the information gathered from the interview, allowed us to answer \textbf{RQ2} by determining if Lehman's Laws apply to the changes made to the API.
 
 %RQ3
-The analysis of the changes and trends, combined with the information gathered from the interview, allowed us to answer \textbf{RQ3} by determining if Lehman's Laws apply to the changes made to the API.
+To allow us to answer \textbf{RQ3}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview.
+Success was determined by comparing the inter-rater reliability, by performing calculating Cohen's Kappa gathered data.
 
@@
 \section{Results} \label{results} 
-This section will present the findings of our study.
-The results related to \textbf{RQ1} and \textbf{RQ2} are introduced in Section \ref{results_rq1}, and the results of \textbf{RQ3} are presented in Section \ref{results_RQ3}
+%%Write new
 
@@
 A new error handling system was one of these changes.
-It is unclear from version 1.4 what error handling was in place, however, version 2.0 saw the addition of specific error handling modules and functions.
+It is unclear from version 1.4 what error handling was in place, however, version 2.0 added specific error handling modules and functions.
 According to the interview, the error handling change coincided with the inclusion of more Glib features, which the new error handling system uses.
@@
 
-\subsection{RQ2 Results}
+\subsection{RQ3 Results}
 
@@
 
-\subsection{RQ3 Results} \label{results_RQ3} 
+\subsection{RQ2 Results} \label{results_RQ2} 
 \noindent
-RQ3: \textbf{How do APIs ``passively'' evolve?}
+RQ2: \textbf{How do APIs ``passively'' evolve?}
 \smallskip
 
-The results related to \textbf{RQ3} are structured around each of Lehman's laws of software evolution \cite{lehman90sview} and to what extent our findings show that the laws apply to platform APIs.
+The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman90sview} and to what extent our findings show that the laws apply to platform APIs.
 A summary of our findings can be seen in Table \ref{table:lehman}.
@@
 %Implications for Industry
+%Important to understand the types of changes they are making so that they can better plan for them in the future.
+Design around them, design for them?
+Design to minimise them?
+Spin this into a design problem?
+**According to Lehman's laws, systems must keep changing otherwise they decline in quality.
+If they wish to maintain the quality of their system and provide new features, it would be helpful to know what kinds of changes are common for their APIs.
 %Implications for Academia

### 2015-05-18 thesis/paper.tex
small stuff

@@
 
-              \textbf{Type}                              & \textbf{Main Types}   &\textbf{Sub Types} \\ \midrule
+              \textbf{Type}                              & \textbf{Main Types}   &\textbf{Secondary Types} \\ \midrule
               Enhancive     & 7 & 0                     \\ \hline
@@
 
-\subsection{RQ3 Results}
-
-% After cross-examining our results with the interviewee and their responses, we found that 78\% of our main category predictions matched the actual motive of the changes and that 78\% of our secondary categorisations matched the actual motives.
-
-\noindent
-\textbf{Functionality is reverse engineerable  } %Reviewed by JW
-All changes whose main motive was to either add or remove functionality were accurately predicted.
-These changes were the most significant and it was expressed during the interview that these types of changes were the main driving factors behind the development of the new version.
-In summary, eleven out of a total of thirteen changes were correctly predicted.
-It is also interesting to note that all changes which were not assigned any sub-category were correctly predicted.
-This supports the fact that such changes have a clearer intent and are perhaps more well-defined.
-
-\smallskip \noindent
-\textbf{Design changes are reverse engineerable to some extent  }  %Reviewed by JW
-Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality, were correctly predicted.
-The two changes which were incorrectly predicted were inaccurate because the main motivation was confused with the secondary intent.
-This shows that, although the prediction was incorrect, the general reasoning was correct.
-Our predictions were accurate enough to allow us to form a reliable conclusion which provided valuable discussion with the case company.
-
 \subsection{RQ2 Results} \label{results_RQ2} 
@@
 
+\subsection{RQ3 Results}
+RQ3: \textbf{How do APIs ``passively'' evolve?}
+
+The
+
+% After cross-examining our results with the interviewee and their responses, we found that 78\% of our main category predictions matched the actual motive of the changes and that 78\% of our secondary categorisations matched the actual motives.
+
+\noindent
+\textbf{Functionality is reverse engineerable  } 
+All changes whose main motive was to either add or remove functionality were accurately predicted.
+These changes were the most significant and it was expressed during the interview that these types of changes were the main driving factors behind the development of the new version.
+In summary, eleven out of a total of thirteen changes were correctly predicted.
+It is also interesting to note that all changes which were not assigned any secondary type were correctly predicted.
+This supports the fact that such changes have a clearer intent and are perhaps more well-defined.
+
+\smallskip \noindent
+\textbf{Design changes are reverse engineerable to some extent  }  
+Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality, were correctly predicted.
+The two changes which were incorrectly predicted were inaccurate because the main motivation was confused with the secondary intent.
+This shows that, although the prediction was incorrect, the general reasoning was correct.
+Our predictions were accurate enough to allow us to form a reliable conclusion which provided valuable discussion with the case company.
+
 \section{Discussion} \label{discussion}
@@
 \end{document}
-
-% \subsection{RQ1 Results} \label{results_rq1} %Reviewed by JW
-% \noindent
-% RQ1: \textbf{How do companies actively drive API evolution?}
-
-% \noindent
-% RQ2: \textbf{To what extent can we reverse engineer API change decisions?}
-% \smallskip
-
-% Many changes were found between version 1.4 and version 2.0.
-The initial inspection revealed there to be many deprecations which were later re-implemented as new modules.
-We have group these changes into a single change instead of a deprecation and a re-implementation.
-In total, thirteen unique changes were found.
-These changes are shown in Table \ref{table:categories}.
-
-% The changes have been divided up into four specific categories, namely: \textit{new}, \textit{modified}, \textit{removed} and \textit{general trends}.
-The category \textit{new} concerns additions of modules, \textit{modified} concerns modifications to modules that existed in version 1.4 and \textit{removed} are changes where functionality was removed being deprecated or replaced by functionality.
-\textit{General trends} are broad changes that are mainly related to design.
-
-% After cross-examining our results with the interviewee and their responses, we found that 78\% of our main category predictions matched the actual motive of the changes and that 78\% of our secondary categorisations matched the actual motives.
-
-% \begin{table}
-%        \centering
-%        \begin{tabular}[ht]{c !{\vrule width 1.5pt} c|c !{\vrule width 1.5pt} c|c} 
-%               \toprule
-
-%               \multirow{2}{*}{\textbf{Change}}          & \multicolumn{2}{c !{\vrule width 1.5pt} }{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Sub}}        \\ \cline{2-5}
-
-%                                    & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \Xhline{2\arrayrulewidth}
-%               axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
-%               axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
-%               axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
-%               axserialport         & E                         & E                         & N/A                       & N/A                \\ \hline
-%               axevent              & E                         & E                         & G                         & G                  \\ \hline
-%               axhttp               & E                         & E                         & G                         & G                  \\ \hline
-%               ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
-%               Burst Mode           & R\textsubscript{d}        & R\textsubscript{d}        & N/A                       & N/A                \\ \hline
-%               Example Code         & U                         & R\textsubscript{f}        & R\textsubscript{f}        & U                  \\ \hline
-%               Documentation        & U                         & U                         & R\textsubscript{f}        & R\textsubscript{f} \\ \hline
-%               Interfaces           & G                         & P                         & P                         & G                  \\ \hline
-%               3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
-%               Error Handling       & P                         & P                         & G                         & G                  \\
-
-%               \bottomrule
-%        \end{tabular}
-%        \caption{Categorisation of Changes }
-%        \label{table:categories}
-% \end{table}
-
-% \subsubsection{axptz} %Reviewed by JW
-% The Pan, Tilt and Zoom (ptz) module concerns functionality related to manoeuvring the camera, both mechanically and digitally.
-We concluded that this change was enhancive, because it is a new feature of the API.
-There was no secondary motive behind this change, as the change was purely enhancive.
-The interviewee described how this change, as well as the other changes classified as additions, were all included in the new API at the request of API users.
-Prior to the change being introduced, there was no API functionality for controlling the camera and as such, it was a high priority addition to the new API.
-The interviewees' comments allowed us to conclude that we had correctly identified the change as being enhancive.
-Furthermore, we were also correct in our prediction that there was no secondary change category.
-
-% \subsubsection{axaudio} %Reviewed by JW
-% The most important functionality of the camera is to capture and analyse video data, however, some API users require the ability to analyse audio data.
-The addition of axaudio allows API users to perform audio analysis of audio streams captured by cameras.
-This change was determined to be enhancive, as it was an addition of a new feature to the API.
-We found no secondary motive for the change.
-Audio analysis had previously not been supported in version 1.4 of the API.
-However, during the interview, it was revealed that an API user had managed to implement their own audio analysis application using version 1.4 of the API.
-Given the apparent demand for audio analysis, it was included in version 2.0 of the API.Taking into account the interviewee's reasoning, we concluded that we had successfully determined that the change was enhancive.
-The addition of axaudio had no secondary motive.
-
-% \subsubsection{axstorage} %Reviewed by JW
-% Prior to the newest version of the API being released, the sole alternative for storing data was to use the Video Management System.
-Version 2.0 added the possibility of alternative storage solutions, by allowing the camera to interface with external storage devices, such as SD cards.
-Enhancive was chosen to be the primary category of change, given that axstorage was a new addition to version 2.0.
-No secondary motive was identified.
-The interviewee described how limited storage options for the cameras, in version 1.4, was the reason that increased functionality was strongly requested by API users.
-As such, axstorage was included in version 2.0 of the API.The information gathered from the interview therefore supported our original categorisation; it was an enhancive change.
-No secondary category was established.
-
-% \subsubsection{axserialport} %Reviewed by JW
-% The addition of axserialport allows API users to connect various devices to the cameras through the use of a serial port.
-This allows users to integrate multiple devices to create their own unique solutions.
-This was not possible in version 1.4 of the API.
-The addition of this module was determined to be an enhancive change, as it involved the addition of a new feature.
-No relevant secondary category was identified.
-The addition of axserialport was requested by API users to allow them to connect the cameras to other devices.
-A possible use case, that was given during the interview, involved a ticketing system which allows for joint analysis of data from multiple devices.
-As such, it was included in version 2.0, to meet the demand of the API users.
-Given this information, we concluded that we were correct in categorising this change as enhancive.
-The categorisation of the secondary category was also correct.
-
-% \subsubsection{axevent} %Reviewed by JW
-% Version 2.0 of the API was designed to be an event-driven system that makes use of callbacks.
-To achieve this, the old event system had to be re-designed.
-The new design is used by all features of version 2.0 of the API.
-An example of when an event would be generated, is when the camera detects movement.
-Given that this module was a re-implementation of the previous event system, we concluded that it should be categorised mainly as an enhancive change with the secondary change as groomative.
-Groomative was chosen as the secondary category due to the additional motive of bringing the new functionality into line with the new design.
-The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implementation of the new event system.
-One reason was that the case company was dissatisfied with certain usability aspects of API version 1.4.
-The module was then completely re-implemented and re-designed according to the new system design of version 2.0.
-From the discussion in the interview, it was clear that both of our categorisations were correct.
-The change was primarily enhancive and secondarily groomative.
-
-% \subsubsection{axhttp} %Reviewed by JW
-% The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically send data to web pages.
-The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards, and at the same time, additional functionality was added to the module.
-This change re-implemented an existing module while adhering to the new design of API version 2.0.
-The main categorisation therefore was chosen to be enhancive with groomative as the secondary category.
-The interviewee described that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, within the standards of the new design.
-Our categorisation of enhancive and groomative was therefore correct for this change.
-The primary intent was to add functionality while also allowing the re-implementation to make use of the new API design.
-
-% \subsubsection{ax\_parameter} %Reviewed by JW
-% The parameter setting module of the API allowed data and application settings to be saved so that they are not lost if the device is not running.
-This module was re-implemented as ax\_parameter with added functionality and conformance to the new design standards of API version 2.0.
-Given that this change re-implemented an existing module while also incorporating the new design standards, it has been categorised as being primarily enhancive with a secondary category of groomative.
-The interviewee clarified that this change was mainly concerned with re-implementing existing functionality, while simultaneously adopting the new standards of version 2.0.
-Given the information from the interview, we concluded that this change was correctly categorised; the primary intent was enhancive and the secondary intent was groomative.
-
-% \subsubsection{Burst Mode} %Reviewed by JW
-% The burst mode feature of the API allowed users to buffer a series of images for greater analysis.
-This feature was deprecated during the transition between version 1.4 and 2.0 and was not re-implemented.
-This change presented itself as a clear example of reductive maintenance, as it was simply removed and without being replaced.
-We therefore gave no secondary categorisation for this change.
-The interviewee described, that in order to continue using this feature, it would have to be re-implemented.
-An impact assessment was undertaken to determine if the removal of the function would be costly.
-Ultimately, the negative effects were not deemed significant enough and thus the function was removed of the API.
-We can therefore conclude that we correctly categorised this change as reductive and that there are indeed, no secondary categories to describe this change.
-
-% \subsubsection{Example Code} %Reviewed by JW
-% The case company included a selection of example programs to assist developers with creating applications.
-This trend continued in version 2.0, but there were some significant improvements.
-The number of example programs and the amount of comments accompanying the code increased, thus improving quality of the examples.
-We therefore concluded that this change was updative, as the example code was updated according to the new API and the new techniques that it utilises.
-We further decided that this change also had a secondary category of reformative.
-During the interview, it became clear that the improvement of the example code was an important change between the two versions.
-The interviewee described how the examples were used frequently by their customers, however, the old examples had many varied implementation techniques, even for similar tasks.
-This ultimately meant that the old examples were not satisfactory and that new examples would have to be written, preferably conforming to the same standards.
-The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.
-With this information, we concluded that our categorisation was incorrect.
-It became clear that this change was, in actual fact, primarily reformative.
-It was also clear that the subcategory should therefore have been updative.
-
-% \subsubsection{Documentation} %Reviewed by JW
-% As the API code was updated in version 2.0, the API documentation was updated to correspond with the new code.
-While there were no substantial changes, we found that the documentation is no longer offered as a PDF but is instead only offered as HTML.
-We categorised this change as being updative with a reformative secondary category for the reasons that the change only updated the documentation to reflect the recent changes in version 2.0.
-This sentiment was shared by the interviewee; the documentation was only changed according to the current workings of the API and how the new modules interact with each other.
-We can therefore say that our categorisations were correct, the change was updative and reformative.
-
-% \subsubsection{Interfaces} %Reviewed by JW
-% Version 1.4 of the API allowed direct access to the headers of each module available in the API.
-Version 2.0 changed this by including interfaces through which functionality is accessed.
-This design change has had an effect on the whole API, as it has changed the structure of modules, but not the functionality of them.We therefore concluded that this change would be best categorised as  groomative.
-The secondary category was categorised as preventive, as the change could be seen as an attempt to reduce future maintenance.
-The interview provided further insight into the reasoning behind this design change.
-Improvements to coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to use interfaces in versions 2.0 of the API.
-Furthermore, the re-design would hopefully avoid future maintenance, while also allowing the system to be easily extended.
-Taking this information into account, we concluded that our categorisation was incorrect.
-The interview showed that the primary categorisation should have been preventive, given the strong emphasis on avoiding future maintenance and improving usability.
-We further concluded that the secondary change should have been groomative, to better reflect the intent of improving the APIs maintainability.
-
-% \subsubsection{3\textsuperscript{rd} Party}
-% %% REMEMBER TO PROVIDE LINK TO GLIB:::: - https://developer.gnome.org/glib/
-% ATTN: (!!!We are waiting for more information from Johanna to confirm / add to this section!!!)
-% %%Describe the change 
-% 2.0 utilises more 3rd party libraries
-% axsound, for example, uses alsa
-% All modules use glib
-% The advent of the new API saw the inclusion of new 3\textsuperscript{rd} party libraries.
-For example, axsound utilises a library called Alsa, all interfaces use Glib and daemons have been provided for using D-Bus.
-These changes potentially make the library much more flexible both for the API designers in terms of features they can provide and for the application developers in terms of applications they can develop.
-% We therefore gave this change the main categorisation of adaptive with no suitable sub-categories being found.
-% The architects creating the API decided they wished to use Glib which came about primarily from internal discussions at the company.
-% %%Relate it to Categories
-% Architects decided to use glib, part of an internal decision. 
-% Glib (!!!ref to website) was therefore introduced to the new API to help alleviate this 
-% The new API utilises Glib in the majority of its interfaces and considering the fact that Glib has its own type of error handling, it seemed sensible to implement the same technique into the new API.
-However, it was expressed to us that the error handling would have changed between versions regardless of whether or not Glib was included.
-(!!!This is also too assume-y)
-
-% \subsubsection{Error Handling} %Reviewed by JW
-% A substantial change included in version 2.0 was the addition of header files, containing enums of error codes.
-While it was not evident how the error handling was implemented prior to version 2.0, we concluded that it had changed, given the addition of the new header files.
-We therefore categorised this change as being primarily preventive, as error handling is preventive by nature.
-Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability.
-During the interview, it was made clear that the previous error handling was lacking in expressiveness and usability.
-Glib was added to version 2.0 and the error handling functionality that Glib provides was incorporated into the new API design.
-We therefore concluded that our categorisation for this change was correct.
-The primary reason for the change was to improve the existing error handling while conforming to the new API standard.

### 2015-05-18 thesis/paper.tex
categories->types

@@
 \subsection{Software Evolution} \label{software_evolution}
-%%Categories of maintenance and types of maintenance
+%%Types of maintenance and types of maintenance
 Software evolution is a field that studies the application of software maintenance activities, changes in software processes and the resulting, evolved versions of the software.
@@
 Structure to the interview was provided by organising it around the software evolution theories \cite{chapin2001types, lehman90sview}.
-Investigative and open-ended questions related to each category and law were asked to provide a basis for comparison between the answers and our initial analysis.
+Investigative and open-ended questions related to each type and law were asked to provide a basis for comparison between the answers and our initial analysis.
 The interviewee was encouraged to speak freely, even if it required a change in direction or topic.
@@
 %Concepts
-Grouping the codes by module allowed us to form general concepts of change. However, changes that affected the whole API were categorised on their own.
+Grouping the codes by module allowed us to form general concepts of change. However, changes that affected the whole API were classified on their own. %"that affected the whole API" re-word this
 %Categories
@@
 Such examples include a shift towards using interfaces to access features, improved maintainability, a different error-handling approach and the inclusion of additional 3\textit{rd} party libraries.
-With the exception of 3\textit{rd} party libraries, the general trends have secondary changes which help to categories what effect the changes had on the API.
+With the exception of 3\textit{rd} party libraries, the general trends have secondary changes which help to classify what effect the changes had on the API.
 
@@
 %Data and examples
-While none of the change identified were primarily groomative changes, three of them were secondarily categorised as being groomative.
+While none of the change identified were primarily groomative changes, three of them were secondarily classified as being groomative.
 This seems to indicate that the groomative nature of a change is often a bonus of other kinds of changes.
@@
 \noindent
-\textbf{A majority of the laws apply  } %Reviewed by JW
+\textbf{A majority of the laws apply  } 
 Evidence was found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System to establish that they apply to APIs.
@@
 \smallskip \noindent
-\textbf{Two laws apply to a certain extent  } %Reviewed by JW
+\textbf{Two laws apply to a certain extent  } 
 The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but the extent to which they apply might not be as significant for APIs compared to other types of systems.
@@
 \smallskip \noindent
-\textbf{One law is not applicable  } %Reviewed by JW
+\textbf{One law is not applicable  } 
 Strong evidence was found to suggest that the law of Conservation of Organisational Stability does not apply to APIs.
@@
 \smallskip \noindent
-\textbf{The importance of a Feedback System  } %Reviewed by JW
+\textbf{The importance of a Feedback System  } 
 Especially interesting results were found in regards to the law of Feedback System.
@@
 \subsection{RQ3 Results}
-RQ3: \textbf{How do APIs ``passively'' evolve?}
+\noindent
+RQ3: \textbf{To what extent can we reverse engineer API change decisions?}
+\smallskip
 
-The
-
-% After cross-examining our results with the interviewee and their responses, we found that 78\% of our main category predictions matched the actual motive of the changes and that 78\% of our secondary categorisations matched the actual motives.
+After cross-examining our initial analysis with the interviewee's responses, we found that 85\% of our main type predictions matched the actual motive of the change and that 85\% of our secondary type predictions were correct.
 

### 2015-05-18 thesis/paper.tex
Results RQ3

@@
 \smallskip \noindent
-\textbf{Continuing Change} 
+\textbf{Continuing Change  } 
 The case company described that including new functional content was one of the top priorities for the release of version 2.0.
@@
 \smallskip \noindent
-\textbf{Increasing Complexity} \label{sec:law2} 
+\textbf{Increasing Complexity  } \label{sec:law2} 
 A majority of the changes introduced in version 2.0 aimed to improve the structure and the way that the API was used.
@@
 \smallskip \noindent
-\textbf{Self Regulation} \label{sec:law3} 
+\textbf{Self Regulation  } \label{sec:law3} 
 The release of version 1.4 did not include any changes related to the API interface.
@@
 \smallskip \noindent
-\textbf{Conservation of Organisational Stability} 
+\textbf{Conservation of Organisational Stability  } 
 The changes to the API have been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
@@
 \smallskip \noindent
-\textbf{Conservation of Familiarity} 
+\textbf{Conservation of Familiarity  } 
 The documentation that is included with the API was rigorously updated with the introduction of version 2.0.
@@
 \smallskip \noindent
-\textbf{Continuing Growth} 
+\textbf{Continuing Growth  } 
 Large parts of the changes between the versions were strictly additions of new functional content.
@@
 \smallskip \noindent
-\textbf{Declining Quality} 
+\textbf{Declining Quality  } 
 The interviews established that a groomative motive was not the primary reason for implementing any change.
@@
 \smallskip \noindent
-\textbf{Feedback System} 
+\textbf{Feedback System  } 
 One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
@@
 After cross-examining our initial analysis with the interviewee's responses, we found that 85\% of our main type predictions matched the actual motive of the change and that 85\% of our secondary type predictions were correct.
+The kappa value \cite{cohen1968weighted} for the predictions was 0.812, which shows that there is a high level of agreement between the predictions and the change decisions.
 
-\noindent
-\textbf{Functionality is reverse engineerable  } 
-All changes whose main motive was to either add or remove functionality were accurately predicted.
-These changes were the most significant and it was expressed during the interview that these types of changes were the main driving factors behind the development of the new version.
-In summary, eleven out of a total of thirteen changes were correctly predicted.
-It is also interesting to note that all changes which were not assigned any secondary type were correctly predicted.
-This supports the fact that such changes have a clearer intent and are perhaps more well-defined.
-
-\smallskip \noindent
-\textbf{Design changes are reverse engineerable to some extent  }  
-Three out of five changes which did not add functionality, but rather were introduced to reduce complexity and increase quality, were correctly predicted.
-The two changes which were incorrectly predicted were inaccurate because the main motivation was confused with the secondary intent.
+The changes related to functionality being added, modified (deprecated) or removed were predicted with a 100\% accuracy.
+These changes were deemed the most significant by the interviewee, and it was expressed during the interivew that the these types of changes were the main driving factor behind the development of the new version.
+On the contrary, three out of five changes which were unrelated to functionality were correctly predicted.
+The two changes which were not predicted correctly were inaccurate because the main type was confused with the secondary type.
 This shows that, although the prediction was incorrect, the general reasoning was correct.
-Our predictions were accurate enough to allow us to form a reliable conclusion which provided valuable discussion with the case company.
+The changes which had no secondary type were all predicted correctly, which further shows that changes with several types can be diffuse.
 

### 2015-05-18 thesis/paper.tex
resutls rq1 review

@@
 
-\subsection{RQ1 Results} \label{results_rq1}
+The majority of changes between version 1.4 and version 2.0 have been additions to functionality of the API.
+Such additions include added functionality to ( "add 'allow' here?") mechanically and digitally control the camera, to utilise additional storage devices, to allow serial connectivity and to allow audio analysis on the cameras.
+Pure additions ( "rephrase to 'changes which were pure additions' or something similar?") to the API did not have any secondary types of change attributed to them.
+( "rephrase to 'were not attributed with any secondary...' ?...
+just tense" )
 
-The majority of changes between version 1.4 and version 2.0 have been additions to functionality of the API.
-Such additions include added functionality to mechanically and digitally control the camera, to utilise additional storage devices, to allow serial connectivity and to allow audio analysis on the cameras.
-Pure additions to the API did not have any secondary types of change attributed to them.
-
-Many of the changes found many deprecations which were later re-implemented as new modules.
+Many of the changes found many deprecations which were later re-implemented as new modules ( "rephrase").
 We have grouped these kinds of changes into a single type instead of two.
 Such examples include the deprecation and re-implementation of an event system, dynamic web page generation and configuration utilities.
-These kinds of changes often had a secondary type of change that accompanied the primary type of change.
+These kinds of changes( "repeating these kinds of changes, consider changing it up") often had a secondary type of change that accompanied the primary type of change.
 
 The remainder of the changes were defined as general trends.
-These changes were not individual, but were instead larger changes that effected the whole API.
-Such examples include a shift towards using interfaces to access features, improved maintainability, a different error-handling approach and the inclusion of additional 3\textit{rd} party libraries.
+These changes were not individual ( "were not individual sounds weird"), but were instead larger changes that affected the whole API.
+Such examples include a shift towards using interfaces to access features, improved maintainability ( "improved maintainability is not an example, could remove it"), a different error-handling approach and the inclusion of additional 3\textit{rd} party libraries.
 With the exception of 3\textit{rd} party libraries, the general trends have secondary changes which help to classify what effect the changes had on the API.
+( "This last sentence is a bit weird...
+is it just fluff?
+if so remove")
 
+\subsection{RQ1 Results} \label{results_rq1}
+%Re-write this intro a bit (since I moved it)
 All of the identified changes have been given a type based the nature of the change according to the Types of Software Evolution and Software Maintenance decision tree \cite{chapin2001types}.
 In total, thirteen unique changes were found.
-The count of change types is shown in table \ref{table:type_counts}.
+( "This info should be in \ section{Results}, and not here") The count ( "explain the count better, since it is unclear from just the table") of change types is shown in table \ref{table:type_counts}.
 
@@
               \textbf{Type}        & \textbf{Main Types}       &\textbf{Secondary Types}   \\ \midrule
-              Enhancive     & 7 & 0                     \\ \hline
-              Corrective    & 0 & 0                     \\ \hline
-              Reductive     & 1 & 0                    \\ \hline
-              Adaptive      & 1 & 0                     \\ \hline
-              Performance   & 0 & 0                    \\ \hline
-              Preventive    & 2 & 0                     \\ \hline
-              Groomative    & 0 & 5                     \\ \hline
+              Enhancive            & 7                         & -                         \\ \hline
+              Corrective           & -                         & -                         \\ \hline
+              Reductive            & 1                         & -                         \\ \hline
+              Adaptive             & 1                         & -                         \\ \hline
+              Performance          & -                         & -                         \\ \hline
+              Preventive           & 2                         & -                         \\ \hline
+              Groomative           & -                         & 5                         \\ \hline
               Updative             & 1                         & 1                         \\ \hline
               Reformative          & 1                         & 1                         \\ \hline
-              Evaluative    & 0 & 0                    \\ \hline
-              Consultive    & 0 & 0                    \\ \hline
-              Training      & 0 & 0                    \\
+              Evaluative           & -                         & -                         \\ \hline
+              Consultive           & -                         & -                         \\ \hline
+              Training             & -                         & -                         \\
 
@@
        \end{tabular}
-       \caption{Identified Change Types}
+       \caption{Identified Types of Change}
        \label{table:type_counts}
@@
 %Data and explanation
-No corrective changes were identified between v1.0 and v2.0.
+No corrective changes were identified between v1.0 ( "1.4?") and v2.0.
 There are two main reasons that we did not find any changes of this type.
@@
 We therefore conclude that the evolution of the API was not driven by corrective changes.
+
 \smallskip \noindent
@@
 This reductive change removed functionality that provided the ability to buffer individual images for closer analysis by a user.
-Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role, xing2006refactoring} this was a surprising result.
+Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role, xing2006refactoring} this was a surprising ( "no subjectivity in results plz") result.
 %Don't know if I should discuss the finding in this much depth here?
@@
 A single change was identified as being adaptive; the inclusion of new 3\textit{rd} part libraries.
-Glib \cite{Glib} existed in version 1.4 of the API its use was increased in version 2.0.
+Glib \cite{Glib} ( "any point in mentioning Glib now that we dont talk details about functionality?") existed in version 1.4 of the API its use was increased in version 2.0.
 Furthermore, other libraries were added for audio and data communication.
@@
 However, more information, possibly in the form of another study, would be required to fully conclude if these types of changes have a greater impact upon the evolution of an API.
+( "remove future work stuff and try to form a conclusion based on what we have")
 
@@
 No performance types of change were identified in the API.
-Only having access to the public API and not the implementation meant that we were unable search for performance changes in existing code between the versions.
+Only having access to the public API and not the implementation meant that we were unable to search ( "we weren't unable to search, sounds like we're making excuses, can just say we didnt identify any") for performance changes in existing code between the versions.
 There was no indication from the documentation nor the interview that any change had been performed with the intent of increasing system performance.
@@
 As such, we conclude that the evolution of the API was not driven by performance changes.
-A proper benchmark could be performed on sample programs written with both versions of the API to test overall performance.
+( "remove benchmark stuff imo...
+it's unrelated") A proper benchmark could be performed on sample programs written with both versions of the API to test overall performance.
 However, this is outside the scope of our study.
@@
 %Data and examples
-Two changes were identified to be Preventive types of change.
+Two changes were identified to be Preventive ( "no capital P?
+make sure it's consistent") types of change.
 A new error handling system was one of these changes.
-It is unclear from version 1.4 what error handling was in place, however, version 2.0 added specific error handling modules and functions.
+It is unclear ( "too negative, rephrase")from version 1.4 what error handling was in place, however, version 2.0 added specific error handling modules and functions.
 According to the interview, the error handling change coincided with the inclusion of more Glib features, which the new error handling system uses.
@@
 %Define
-Groomative changes are defined to be changes that aim to make the code more maintainable immediately. This should not be confused with preventive changes.
+Groomative changes are defined to be changes that aim to immediately make the code more maintainable .
+This should not be confused with preventive changes.
+( "remove this sentence, since u already said that in the preventive paragraph, saying it once is enough")
 %Data and examples
 While none of the change identified were primarily groomative changes, three of them were secondarily classified as being groomative.
-This seems to indicate that the groomative nature of a change is often a bonus of other kinds of changes.
+This seems to indicate ( "too vague for results") that the groomative nature of a change is often a bonus ( "bonus=casual, consider added positive effect or something")of other kinds of changes.
 The move towards using interfaces can be seen as an example of this.
@@
 Updative changes are defined to be changes to documentation and are not changes that affect functionality in any way.
-We also considered updates to example code and other training material to be Updative types of change.
+( "this sentence reads weird") We also considered updates to example code and other training material to be Updative ( "capital U") types of change.
 %Data and example
 A single change was determined to be Updative.
-This change was the updating of the API documentation to match the new API.
-The updates included a new API specification, deprecation list and the inclusion of the new features and libraries.
+( "capital U")  This change was the updating of the API documentation to match the new API.
+( "this senetence reads weird") The updates included a new API specification, deprecation list and the inclusion of the new features and libraries.
 %Conclusion
@@
 We therefore conclude that the evolution of an API is not driven by updative changes.
+( "Think this paragraph is missing some information.
+It's important to mention that because of the nature of updative changes they dont drive evolution, but they rather are an effect of other types of changes" (if u change in one place it leads to a change somehwere else))
 
@@
 %Data and Example
-One reformative change was identified between version 1.4 and version 2.0 which involved a re-write of the existing example programs.
-The aim of the re-write was to update the examples to take advantage of the new functionality in the API while simultaneously showing how the modules interact and presenting a standard for how to use the API correctly.
+One reformative change was identified between version 1.4 and version 2.0 which involved a re-write ( "re-write, a bit informal") of the existing example programs.
+The aim of the re-write ( "same") was to update the examples to take advantage of the new functionality in the API while simultaneously showing how the modules interact and presenting a standard for how to use the API correctly.
 %Conclusion
-The reformative change that was found indicates therefore that updating documentation and example code is to some extent import for API evolution.
+The reformative change that was found indicates therefore that updating documentation and example code is to some extent import for API evolution. ( "weird sentence")
 
@@
 Similarly, consultive activities involve consultations with customers about the software.
-Finally, Training activities involve training for customers and users of the software.
+Finally, Training ( "capital T") activities involve training for customers and users of the software.
 %Data and example

### 2015-05-18 thesis/paper.tex
Stöff

@@
 \noindent
-\textbf{Functionality is a prime driver of API evolution  }  %Reviewed by JW
+\textbf{Functionality is a prime driver of API evolution  }  
 Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
@@
 \smallskip \noindent 
-\textbf{Maintainability does not drive change  }  %Reviewed by JW
+\textbf{Maintainability does not drive change  }  
 While maintainability is important, it is not a primary driving factor for change.
@@
 \smallskip \noindent
-\textbf{Standardising application development  } %Reviewed by JW%Reviewed by JW
+\textbf{Standardising application development  } 
 Supporting users of the API in creating correct and robust applications is a very important evolution factor for the case company.
@@
 \smallskip \noindent
-\textbf{Removing functionality  } %Reviewed by JW
+\textbf{Removing functionality  } 
 Previous literature has suggested that deprecating functionality is the most common technique used to remove support for specific functionality.
@@
 \smallskip \noindent
-\textbf{Documentation does not drive change  } %Reviewed by JW
+\textbf{Documentation does not drive change  } 
 The intent to update example code and documentation was described by the interviewee to be an important change between version 1.4 and 2.0.
@@
 \smallskip \noindent
-\textbf{Hardware is not a driving factor  } %Reviewed by JW
+\textbf{Hardware is not a driving factor  } 
 Our initial expectations included the view that changes to hardware would be one of the strongest driving factors of API evolution.
@@
 The reason that this doubt exists is because these motives were secondary to the motives of increased functionality.
-An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk} \cite{henning2007api} \cite{mcdonnell2013empirical} \cite{robbes2012developers} might dominate the need to improve simplicity and quality.
+An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers} might dominate the need to improve simplicity and quality.
 
@@
 Our results not only show that the law is not true for APIs, but that the opposite of what the law states is true for APIs.
-This is supported by the consensus in literature of the negative effects caused by modifications to APIs \cite{google_talk} \cite{henning2007api} \cite{mcdonnell2013empirical} \cite{robbes2012developers}.
+This is supported by the consensus in literature of the negative effects caused by modifications to APIs \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}.
 The results from our study also revealed that reluctance to change APIs causes the releases of new versions to be few and sporadic.

### 2015-05-18 thesis/paper.tex
Re-wrote rq2 results summary

@@
 
-The results related to \textbf{RQ2} are structured around each of Lehman's laws of software evolution \cite{lehman90sview} and to what extent our findings show that the laws apply to platform APIs.
+Our analysis of the results related to \textbf{RQ2} showed that seven out of the eight laws \cite{lehman90sview} do apply to APIs.
 A summary of our findings can be seen in Table \ref{table:lehman}.
+The evidence found for the laws of continuing change, self regulation, conservation of familiarity, continuing growth and feedback system mainly relate to enhancive changes that add functionality to the API.
+It was also found that the laws of increasing complexity and declining quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality.
+The only law which was found not to apply to the API analysed in this study was the law of conservation of organisational stability.
+Our results rather show the opposite, that the work rate is variant.
+
+In the remainder of this section we will discuss the results related to each law, and discuss if our results show that the laws apply to APIs or not.
 
@@
               Continuing Change                         & True                      \\ \hline
-              Increasing Complexity                     & Kinda                     \\ \hline
+              Increasing Complexity                     & True                     \\ \hline
               Self Regulation                           & True                      \\ \hline
@@
               Continuing Growth                         & True                      \\ \hline
-              Declining Quality                         & Kinda                     \\ \hline
+              Declining Quality                         & True                     \\ \hline
               Feedback System                           & True                      \\
@@
 The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that the company currently did not make use of these.
-Even though the importance of maintaining the API in order to reduce complexity was stated, arguments which support that it is of lesser importance than releasing functional content was also presented.
-One example of where this is evident in the evolution of the API, is in the module that handles the video capturing and video stream.
-It was decided that this module would not be re-designed to conform with the new interface standard, as the changes to functionality in this module were very minor.
-Thus, the law of increasing complexity holds for APIs, but there is evidence that suggests that decreasing the complexity is not of the highest priority.
+Although the importance of reducing the complexity was stated, it was made clear during the interview that one module was not updated between the versions, even though it did not follow the new standards of version 2.0.
+In conclusion, we establish that the law of increasing complexity is true for APIs.
 
@@
 These changes did, however, also increase the quality and were a substantial part of the update.
-A counterargument to this reasoning can be seen in the module which handles the video data and capturing, which was not changed between the versions, as mentioned in Section \ref{sec:law2}.
-We therefore settle that the law of declining quality can be applied to APIs, but that there is data that implies that reducing quality is not of high importance.
+Our analysis also shows that changes related to quality are bound to happen, as other types of changes often incorporate quality related aspects.
+We therefore settle that the law of declining quality applies to APIs.
 
@@
 Based on these factors and clearly expressed ambitions, we conclude that the law of feedback system is true for APIs.
-
-\subsubsection{Summary}
-
-\noindent
-\textbf{A majority of the laws apply  } 
-Evidence was found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System to establish that they apply to APIs.
-The most prominent explanation for this is that a large part of the introduced changes were related to functionality.
-It is especially interesting to note that the laws of Self Regulation and Conservation of Familiarity accurately match the API explored in this paper.
-
-\smallskip \noindent
-\textbf{Two laws apply to a certain extent  } 
-The laws of Increasing Complexity and Declining Quality were found to apply to APIs, but the extent to which they apply might not be as significant for APIs compared to other types of systems.
-The reason that this doubt exists is because these motives were secondary to the motives of increased functionality.
-An alternative explanation for these laws being of lesser significance in APIs could be that the general inertia to modify APIs which exists \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers} might dominate the need to improve simplicity and quality.
-
-\smallskip \noindent
-\textbf{One law is not applicable  } 
-Strong evidence was found to suggest that the law of Conservation of Organisational Stability does not apply to APIs.
-Our results not only show that the law is not true for APIs, but that the opposite of what the law states is true for APIs.
-This is supported by the consensus in literature of the negative effects caused by modifications to APIs \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}.
-The results from our study also revealed that reluctance to change APIs causes the releases of new versions to be few and sporadic.
-
-\smallskip \noindent
-\textbf{The importance of a Feedback System  } 
-Especially interesting results were found in regards to the law of Feedback System.
-The importance of having a structured and developed feedback loop was stressed during the interview and it was also expressed as one of the main points of improvement.
-This suggests that including feedback from more sources and using this feedback to improve the evolution process should be a consideration for APIs.
 

### 2015-05-18 thesis/paper.tex
Added notes

@@
 
+%%Small intro to this section. Mention that : In total, thirteen unique changes were found.
+
 The majority of changes between version 1.4 and version 2.0 have been additions to functionality of the API.
-Such additions include added functionality to ( "add 'allow' here?") mechanically and digitally control the camera, to utilise additional storage devices, to allow serial connectivity and to allow audio analysis on the cameras.
-Pure additions ( "rephrase to 'changes which were pure additions' or something similar?") to the API did not have any secondary types of change attributed to them.
-( "rephrase to 'were not attributed with any secondary...' ?...
-just tense" )
+Such additions include added functionality to allow mechanical and digital control of the camera, to utilise additional storage devices, to allow serial connectivity and to allow audio analysis on the cameras.
+Changes that were pure additions the API were not attributed with any secondary types of change.
 
-Many of the changes found many deprecations which were later re-implemented as new modules ( "rephrase").
-We have grouped these kinds of changes into a single type instead of two.
+Many of the changes were deprecations that were later re-implemented as new modules.
+Changes of these kinds were grouped into a single type instead of two.
 Such examples include the deprecation and re-implementation of an event system, dynamic web page generation and configuration utilities.
-These kinds of changes( "repeating these kinds of changes, consider changing it up") often had a secondary type of change that accompanied the primary type of change.
+Changes of this kind often had an accompanying secondary type of change.
 
 The remainder of the changes were defined as general trends.
-These changes were not individual ( "were not individual sounds weird"), but were instead larger changes that affected the whole API.
-Such examples include a shift towards using interfaces to access features, improved maintainability ( "improved maintainability is not an example, could remove it"), a different error-handling approach and the inclusion of additional 3\textit{rd} party libraries.
-With the exception of 3\textit{rd} party libraries, the general trends have secondary changes which help to classify what effect the changes had on the API.
-( "This last sentence is a bit weird...
-is it just fluff?
-if so remove")
+These changes were not changes to individual parts of the API, but were instead larger changes that affected the whole API.
+Such examples include a shift towards using interfaces to access features, a different error-handling approach and the inclusion of additional 3\textit{rd} party libraries.
+Typically, these general trends also have a secondary type of change attributed to them.
 
@@
 All of the identified changes have been given a type based the nature of the change according to the Types of Software Evolution and Software Maintenance decision tree \cite{chapin2001types}.
-In total, thirteen unique changes were found.
-( "This info should be in \ section{Results}, and not here") The count ( "explain the count better, since it is unclear from just the table") of change types is shown in table \ref{table:type_counts}.
+Table \ref{table:type_counts} shows the total count of each type of change found in the different versions of the API.
+
+Functionality is a prime driver of API evolution // Hardware is not a driving factor
+Maintainability does not drive change // Documentation does not drive change
+Standardising application development
+Removing functionality
 
@@
 %Data and explanation
-No corrective changes were identified between v1.0 ( "1.4?") and v2.0.
+No corrective changes were identified between v1.4 and v2.0.
 There are two main reasons that we did not find any changes of this type.
@@
 This reductive change removed functionality that provided the ability to buffer individual images for closer analysis by a user.
-Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role, xing2006refactoring} this was a surprising ( "no subjectivity in results plz") result.
-%Don't know if I should discuss the finding in this much depth here?
-%If OK - Talk more about the business side of things, and how we couldn't identify this change ourselves
-It was revealed during the interview that the functionality was removed because the case company no longer wished to support this feature, due to hardware constraints. 
+Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role, xing2006refactoring}.
+It was revealed during the interview that the functionality was removed because the case company no longer wished to support this feature.
 %Conclusion
@@
 %Data and examples
-A single change was identified as being adaptive; the inclusion of new 3\textit{rd} part libraries.
-Glib \cite{Glib} ( "any point in mentioning Glib now that we dont talk details about functionality?") existed in version 1.4 of the API its use was increased in version 2.0.
-Furthermore, other libraries were added for audio and data communication.
+A single change was identified as being adaptive; the inclusion of new 3\textit{rd} party libraries.
+Libraries were added for audio and data communication.
+The pre-existing low-level library was further incorporated into whole API.
+(!!!)
 %Conclusion 
-The evolution of the API has not been primarily driven by adaptive changes.
-However, more information, possibly in the form of another study, would be required to fully conclude if these types of changes have a greater impact upon the evolution of an API.
-( "remove future work stuff and try to form a conclusion based on what we have")
+We therefore conclude that the evolution of the API has not been primarily driven by adaptive changes.
 
@@
 %Data and examples
-No performance types of change were identified in the API.
-Only having access to the public API and not the implementation meant that we were unable to search ( "we weren't unable to search, sounds like we're making excuses, can just say we didnt identify any") for performance changes in existing code between the versions.
-There was no indication from the documentation nor the interview that any change had been performed with the intent of increasing system performance.
+No evidence of performance driven changes were identified in the API.
 %Conclusion
-As such, we conclude that the evolution of the API was not driven by performance changes.
-( "remove benchmark stuff imo...
-it's unrelated") A proper benchmark could be performed on sample programs written with both versions of the API to test overall performance.
-However, this is outside the scope of our study.
+This therefore leads us to conclude that API evolution is not driven by performance changes.
 
@@
 %Data and examples
-Two changes were identified to be Preventive ( "no capital P?
-make sure it's consistent") types of change.
+Two changes were identified to be preventive types of change.
 A new error handling system was one of these changes.
-It is unclear ( "too negative, rephrase")from version 1.4 what error handling was in place, however, version 2.0 added specific error handling modules and functions.
-According to the interview, the error handling change coincided with the inclusion of more Glib features, which the new error handling system uses.
-The redesign of the system to use more interfaces was also deemed as a preventive change.
-Using interfaces to access modules helps to make them more maintainable and more easily extendable, which is a good example of a preventive change.
+Version 2.0 of the API added specific error handling modules and functions which replaced the pre-existing error-handling in v1.4 of the API.
+The redesign of the system to make use of interfaces was also classified as a preventive change.
+Using interfaces to access modules helps to make them more maintainable and more easily extendable.
 %Concusion
-Preventive types of change appear to drive the evolution of an API more strongly than other types of changes do.
+Preventive types of change appear to drive the evolution of an API more strongly than other types of change.
 This could be due to the fact that as the API grows, the need for higher maintenance also increase, a fact that also seems to be supported by Lehman's laws.
@@
 %Define
-Groomative changes are defined to be changes that aim to immediately make the code more maintainable .
-This should not be confused with preventive changes.
-( "remove this sentence, since u already said that in the preventive paragraph, saying it once is enough")
+Groomative changes are defined to be changes that aim to immediately make the code more maintainable.
 %Data and examples
 While none of the change identified were primarily groomative changes, three of them were secondarily classified as being groomative.
-This seems to indicate ( "too vague for results") that the groomative nature of a change is often a bonus ( "bonus=casual, consider added positive effect or something")of other kinds of changes.
+This indicates that the groomative nature of a change is often a positive affect of other types of change.
 The move towards using interfaces can be seen as an example of this.
@@
 %Define
-Updative changes are defined to be changes to documentation and are not changes that affect functionality in any way.
-( "this sentence reads weird") We also considered updates to example code and other training material to be Updative ( "capital U") types of change.
+Updative changes are defined to be changes to documentation of a system.
 %Data and example
-A single change was determined to be Updative.
-( "capital U")  This change was the updating of the API documentation to match the new API.
-( "this senetence reads weird") The updates included a new API specification, deprecation list and the inclusion of the new features and libraries.
+A single change was determined to be updative; updating the API documentation to include the new functionality of v2.0.
+The updates included a new API specification, deprecation list and the inclusion of the new features and libraries.
 %Conclusion
 Updative changes have very little impact on the functionality of the API yet they are still important changes for the usability of the API \cite{shi2011empirical}.
+Changes to the API cause the need for updative changes to its documentation, without them, the usability of the API could suffer.
 We therefore conclude that the evolution of an API is not driven by updative changes.
-( "Think this paragraph is missing some information.
-It's important to mention that because of the nature of updative changes they dont drive evolution, but they rather are an effect of other types of changes" (if u change in one place it leads to a change somehwere else))
 
@@
 %Data and Example
-One reformative change was identified between version 1.4 and version 2.0 which involved a re-write ( "re-write, a bit informal") of the existing example programs.
-The aim of the re-write ( "same") was to update the examples to take advantage of the new functionality in the API while simultaneously showing how the modules interact and presenting a standard for how to use the API correctly.
+One reformative change was identified between v1.4 and v2.0; a redesign of the existing example programs.
+The aim of this change was to update the examples to illustrate the new functionality in the API, showing how the modules interact and at the same time, presenting a standard for how to use the API.
 %Conclusion
-The reformative change that was found indicates therefore that updating documentation and example code is to some extent import for API evolution. ( "weird sentence")
+We therefore conclude that reformative changes, while important for the usability of the API, do not drive the evolution of the API.
 
@@
 Similarly, consultive activities involve consultations with customers about the software.
-Finally, Training ( "capital T") activities involve training for customers and users of the software.
+Finally, training activities involve training for customers and users of the software.
 %Data and example
@@
 We can therefore conclude that these change types are not important for API evolution.
-
-\subsubsection{Summary}
-
-\noindent
-\textbf{Functionality is a prime driver of API evolution  }  
-Overwhelmingly, the primary driving factor behind API evolution was the desire for new API functionality.
-We found that a vast majority of the changes either added functionality or were a direct consequence of increased functionality.
-The main driver for these changes was the pressure from API users, but pressure from the case company developers who utilise the API also contributed.
-This focus upon functionality was also emphasised partially due to a business goal.
-The more features the API provides allows for more applications to be created for the cameras.
-This has a domino effect of increasing the appeal and value of the products the case company produces.
-
-\smallskip \noindent 
-\textbf{Maintainability does not drive change  }  
-While maintainability is important, it is not a primary driving factor for change.
-We found that where changes that effected maintainability, functionality had also been added or modified.
-Of the changes identified, none were considered to be primarily groomative.
-Groomative motives were only found to be secondary, and were never the main motive for a change.
-Changes to the example code are an example of this.
-The example code was updated purely to reflect the changes in functionality and not as a groomative effort.
-
-\smallskip \noindent
-\textbf{Standardising application development  } 
-Supporting users of the API in creating correct and robust applications is a very important evolution factor for the case company.
-Changes between the versions introduced improvements to error handling, the example code and the way in which the API utilises interfaces.
-This, coupled with removal of unwanted functionality and unsafe operations, has allowed the API to grow and become much more user-friendly.
-As mentioned previously, this could increase the amount of applications being created for the camera and as a consequence, could potentially increase the value of them.
-
-\smallskip \noindent
-\textbf{Removing functionality  } 
-Previous literature has suggested that deprecating functionality is the most common technique used to remove support for specific functionality.
-Removals are only suggested in specific circumstances.
-The successful removal of the burst function seems to indicate that under the correct circumstances, removing specific functionality is an alternative that should be considered.
-The case company removed this function from the API, after an internal review found that the potential negative effect the removal could have, would be less impactful than further maintenance of the function.
-We therefore recommend to remove functionality of an API if the effect of the removal has been thoroughly investigated and that the removals happen incrementally.
-
-\smallskip \noindent
-\textbf{Documentation does not drive change  } 
-The intent to update example code and documentation was described by the interviewee to be an important change between version 1.4 and 2.0.
-While important for the APIs usability, it was not a driving factor of change itself.
-The changes to the APIs' design and functionality caused the need to update the documentation and example code.
-
-\smallskip \noindent
-\textbf{Hardware is not a driving factor  } 
-Our initial expectations included the view that changes to hardware would be one of the strongest driving factors of API evolution.
-One example could be if new cameras are created or new hardware is added to an existing camera, which would require updates to the API to allow use of the new features.
-However, after analysing the changes and from the information gathered in the interview, we discovered that hardware has played a minimal role in the evolution of the API.
 

### 2015-05-18 thesis/paper.tex
Title
Restructured results

@@
 
-\title{The Types and Driving Forces of Modifications in the Evolution of an API}
+\title{The Driving Forces Behind API Evolution}
 
@@
 \subsection{RQ1 Results} \label{results_rq1}
+%Lehman Intro
+
+Our analysis of the results related to \textbf{RQ2} showed that seven out of the eight laws \cite{lehman90sview} do apply to APIs.
+A summary of our findings can be seen in Table \ref{table:lehman}.
+The evidence found for the laws of continuing change, self regulation, conservation of familiarity, continuing growth and feedback system mainly relate to enhancive changes that add functionality to the API.
+It was also found that the laws of increasing complexity and declining quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality.
+The only law which was found not to apply to the API analysed in this study was the law of conservation of organisational stability.
+Our results rather show the opposite, that the work rate is variant.
+
+In the remainder of this section we will discuss the results related to each law, and discuss if our results show that the laws apply to APIs or not.
+
+%Lehman Table
+% \begin{table}
+%        \centering
+%        \begin{tabular}[ht]{l|c}
+%               \toprule
+
+%               \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
+%               Continuing Change                         & True                      \\ \hline
+%               Increasing Complexity                     & True                     \\ \hline
+%               Self Regulation                           & True                      \\ \hline
+%               Conservation of Organisational Stability  & False                     \\ \hline
+%               Conservation of Familiarity               & True                      \\ \hline
+%               Continuing Growth                         & True                      \\ \hline
+%               Declining Quality                         & True                     \\ \hline
+%               Feedback System                           & True                      \\
+
+%               \bottomrule
+
+%        \end{tabular}
+%        \caption{The applicability of Lehman's laws}
+%        \label{table:lehman}
+% \end{table}
+
 %Re-write this intro a bit (since I moved it)
@@
 
-\begin{table}
-       \centering
-       \begin{tabular}[ht]{l|c|c}
-              \toprule
+% \begin{table}
+%        \centering
+%        \begin{tabular}[ht]{l|c|c}
+%               \toprule
 
-              \textbf{Type}        & \textbf{Main Types}       &\textbf{Secondary Types}   \\ \midrule
-              Enhancive            & 7                         & -                         \\ \hline
-              Corrective           & -                         & -                         \\ \hline
-              Reductive            & 1                         & -                         \\ \hline
-              Adaptive             & 1                         & -                         \\ \hline
-              Performance          & -                         & -                         \\ \hline
-              Preventive           & 2                         & -                         \\ \hline
-              Groomative           & -                         & 5                         \\ \hline
-              Updative             & 1                         & 1                         \\ \hline
-              Reformative          & 1                         & 1                         \\ \hline
-              Evaluative           & -                         & -                         \\ \hline
-              Consultive           & -                         & -                         \\ \hline
-              Training             & -                         & -                         \\
+%               \textbf{Type}        & \textbf{Main Types}       &\textbf{Secondary Types}   \\ \midrule
+%               Enhancive            & 7                         & -                         \\ \hline
+%               Corrective           & -                         & -                         \\ \hline
+%               Reductive            & 1                         & -                         \\ \hline
+%               Adaptive             & 1                         & -                         \\ \hline
+%               Performance          & -                         & -                         \\ \hline
+%               Preventive           & 2                         & -                         \\ \hline
+%               Groomative           & -                         & 5                         \\ \hline
+%               Updative             & 1                         & 1                         \\ \hline
+%               Reformative          & 1                         & 1                         \\ \hline
+%               Evaluative           & -                         & -                         \\ \hline
+%               Consultive           & -                         & -                         \\ \hline
+%               Training             & -                         & -                         \\
 
-              \bottomrule
+%               \bottomrule
 
-       \end{tabular}
-       \caption{Identified Types of Change}
-       \label{table:type_counts}
-\end{table}
+%        \end{tabular}
+%        \caption{Identified Types of Change}
+%        \label{table:type_counts}
+% \end{table}
+
+\subsubsection{Types 1by1}
 
@@
 
-\subsection{RQ2 Results} \label{results_RQ2} 
-\noindent
-RQ2: \textbf{How do APIs ``passively'' evolve?}
-\smallskip
-
-Our analysis of the results related to \textbf{RQ2} showed that seven out of the eight laws \cite{lehman90sview} do apply to APIs.
-A summary of our findings can be seen in Table \ref{table:lehman}.
-The evidence found for the laws of continuing change, self regulation, conservation of familiarity, continuing growth and feedback system mainly relate to enhancive changes that add functionality to the API.
-It was also found that the laws of increasing complexity and declining quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality.
-The only law which was found not to apply to the API analysed in this study was the law of conservation of organisational stability.
-Our results rather show the opposite, that the work rate is variant.
-
-In the remainder of this section we will discuss the results related to each law, and discuss if our results show that the laws apply to APIs or not.
-
-\begin{table}
-       \centering
-       \begin{tabular}[ht]{l|c}
-              \toprule
-
-              \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
-              Continuing Change                         & True                      \\ \hline
-              Increasing Complexity                     & True                     \\ \hline
-              Self Regulation                           & True                      \\ \hline
-              Conservation of Organisational Stability  & False                     \\ \hline
-              Conservation of Familiarity               & True                      \\ \hline
-              Continuing Growth                         & True                      \\ \hline
-              Declining Quality                         & True                     \\ \hline
-              Feedback System                           & True                      \\
-
-              \bottomrule
-
-       \end{tabular}
-       \caption{The applicability of Lehman's laws}
-       \label{table:lehman}
-\end{table}
-
-\subsubsection{Lehman's Laws}
+\subsubsection{Laws 1by1}
 

### 2015-05-19 thesis/paper.tex
Updates based on feedback
Disc draft

@@
 %Data and examples
-No evidence of performance driven changes were identified in the API.
+No evidence of performance-driven changes were identified in the API.
 %Conclusion
@@
 
-\subsection{Discussion RQ1}
+\subsection{RQ1 Answer}  
+RQ1: What drives API evolution?
+
+%Answer to RQ
+Talk about the results regarding the law of familiarity that didn't apply.
+
+%Point to results
+
+%Relate to literature
+Cite the papers that say u shoulnt change APIs and say that our results agree \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers} 
+Explain our results with this: 
+       1. The laws are not immutable, since they arise from the habits and practices of humans. [1980programs]
+       2.
+If laws governing large-program evolution can be formulated at all, they must certainly be weaker than those formulated in the biological sciences, where regularity stems from the collective behavior of cellular systems that, even though alive, are nonintelligent, i.e., are not influenced by conscious thought processes, at least at the level of human understanding.
+[On Understanding Laws, Evolution, and Conservation in the Large-Program Life Cycle]
+
+"1.1 Give a clear answer to the RQ. (Reject null / alternative)"
+
+"1.2 Point to results"
+%      -Bring up the most interesting/distinct trends
+
+"1.3 Compare to literature (i.e. relate to previous work)"
+ %      -Do our results agree with prev. work?
+
+\subsection{RQ2 Answer}
+RQ2: How reverse engineer?
+
+%1.1 Give a clear answer to the RQ. (Reject null / alternative)
+
+%1.2 Point to results
+%      -Bring up the most interesting/distinct trends
+
+%1.3 Compare to literature (i.e. relate to previous work)
+ %      -Do our results agree with prev. work?
+
+\subsection{Contribution to Academia} 
+%       -How will our study help other researchers?
+%       -How are the results valuable?
+
+\subsection{Contribution to Practice}
+%       -How will our study help Axis? (More important)
+The laws therefore form an environment within which the effectiveness of programming methodologies and management strategies and techniques can be evaluated, a backdrop against which better methodologies and techniques can be developed.
+[1980programs]
+
+The main thing will be:
+1. Our results found that feedback loop is, a) very importnat and b) the main thing that Axis wants to improve
+2. Relate to Swanson/Chapin saying the types help to budget/plan and facilitate communication between stakeholders
+       [quotes re. budget/plan]:
+
+       [quotes re. communication/stakeholders]:
+
+---------------------------------------------
+
+%       -How will our study help other companies? (Less important)
+
+%Discuss and evaluate conflicting explanations of the results. This is the sign of a good discussion.
 
@@
 %Future work / suggestions based on this RQ?
-
-\subsection{Discussion RQ2}
-
-\subsection{Discussion RQ3}
 

### 2015-05-19 thesis/paper.tex
Quotes from Swanson and Chapin

@@
 \subsection{RQ1 Results} \label{results_rq1}
+
+%Types intro
+The results show that certain types of change are more prevalent than others, these results are shown in \ref{table:type_counts}.
+Analysis of the results showed that enhancive changes were the primary types of change that drive API evolution and that they act as a catalyst for many of the other changes in the API.
+Updative changes were found to be consequences of enhancive changes, rather than being drivers of evolution.
+Supporting the users of the API through the combination of preventive and groomative types of change, together formed another strong driver of API evolution.
+Reductive and adaptive changes, while important, did not strongly drive the evolution of the API.
+No evidence was found for corrective, performance types of change.
+Similarly, there was no evidence found for evaluative, consultive nor training activities.
+
 %Lehman Intro
-
-Our analysis of the results related to \textbf{RQ2} showed that seven out of the eight laws \cite{lehman90sview} do apply to APIs.
+Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight laws \cite{lehman90sview} do apply to APIs.
 A summary of our findings can be seen in Table \ref{table:lehman}.
@@
 
-In the remainder of this section we will discuss the results related to each law, and discuss if our results show that the laws apply to APIs or not.
+In the remainder of this section we will discuss the results related to each type of change category, discussing the results for each of them with examples from the changes identified between the two versions of the API.
+Subsequently, each of Lehman's laws will be discussed and our results will be presented showing if the laws apply to APIs or not.
 
@@
 
+   ``Managers involved in software evolution and software maintenance have great difficulty in
+   defining, justifying, budgeting, staffing, supervising, accounting for, marshalling resources
+   for, and assessing the work when coarse non-objective measures are used [4]. Things not
+   appropriately named are often undervalued and treated as miscellaneous or trivial, since
+   communication about them is made more cumbersome.'' %Chapin
+
        [quotes re. communication/stakeholders]:
+       ``management must be thoroughly fami-liar with the organizational conventions and practices
+involved, in order to make intelligent decisions.'' //Swanson
+``provide a realistic and practical classification to facilitate communication about, and the
+management of, software evolution and maintenance among researchers, practitioners, and their
+managers;'' //Chapin
+
+%Whole bunch of Swanson stuff below.
+% The implications for the management of software
+% maintenance are several. First, insofar as maintenance
+% is performed informally, i.e. in the absence of an
+% established set of organizational conventions and prac-
+% tices, the measurement of maintenance performance w i l l
+% not be feasible. The establishment of a maintenance
+% data base, a precondition to performance measurement,
+% is not possible in the absense of organizational struc-
+% ture. In informal situations, performance must be assessed informally.
+
+% Secondly, in any given organization in which main-
+% tenance performance is formally assessed, in terms of
+% specific measures, management must be thoroughly fami-
+% l i a r with the organizational conventions and practices
+% involved, in order to make intelligent decisions. No
+% single measure or set of measures w i l l i t s e l f reveal
+% that maintenance is going "better" or "worse" than
+% management has a right to expect or desire. Such a
+% judgment must follow as a systemic inference from an
+% analysis of the performance measurements, made in the
+% context of f a m i l i a r i t y with the organizational struc-
+% ture which made these measurements possible.
+
+% Finally, in the absence of f a m i l i a r i t y with other,
+% alternative organizational structures for performing
+% maintenance, management w i l l be essentially unable to
+% assess i t s own established structure. Nothing in the
+% performance measurements made within the context of the
+% established structure w i l l indicate the opportunity
+% costs associated with this structure. Management must
+% look outside, to the performance measurements and
+% structures of other organizations, to assess what might
+% reasonably be achieved through organizational change.
+
+% In the context of a maintenance organizational
+% structure and a particular set of data gathered in the
+% performance of maintenance within this structure, i t
+% is possible to derive some performance measures which
+% should be appropriately "suggestive" to management.
+
+% Measures of maintenance performance are
+% not meaningful except within the context
+% of the organizational structure(s) upon
+% which they are based.
 

### 2015-05-19 thesis/paper.tex
disc draft

@@
 \subsection{Contribution to Academia} 
+Some laws don't apply. Consider inverting the law of org stab for APIs
+Since motives are reverse engineerable, it hsould encourage more ppl to do similar studies
+
 %       -How will our study help other researchers?
@@
 
+3. Suggest to Axis that they improve their feedback loop by using the types
+
+Also suggest that they keep evolving the API with reference to the laws
+
+Implications for Practice tips: 
+       3. Each implications for practice section should include descriptions of 
+       a) problematic issue(s) being addressed, 
+       b) the specific audience(s) to which implications are addressed, 
+       c) a small number of recommendations about what the audience should/could/should not do based on the research findings, 
+       d) an expected outcome of carrying out recommendation(s), and 
+       e) some specific illustrations of what carrying out the recommendations might look like, perhaps in narrative form.
+
+\url{https://www.princeton.edu/futureofchildren/publications/journals/article/index.xml?journalid=46&articleid=212&sectionid=1379}
+
 %       -How will our study help other companies? (Less important)
@@
 
-%Implications for Industry
-%Important to understand the types of changes they are making so that they can better plan for them in the future.
-Design around them, design for them?
-Design to minimise them?
-Spin this into a design problem?
-**According to Lehman's laws, systems must keep changing otherwise they decline in quality.
-If they wish to maintain the quality of their system and provide new features, it would be helpful to know what kinds of changes are common for their APIs.
-%Implications for Academia
-%Future work / suggestions based on this RQ?
-
 \section{Conclusion} \label{conclusion}
@@
 
-1. Small intro which: Summarises the findings of the discussion
+1. Summary of our results/discussion i.e. short conclusion
 
-2. Conclusions/outcomes:
-Industry
-Have a more structured feedback loop (include users) this can be future work too
-              Greater emphasis should be placed upon communicating with the end users / application developers.
-They should probably improve their feedback system to get more feedback from the API users.
-              Include more scientific theories
-              --> consider ecosystem stuff
+2. Future work:
+       a) Eco-system (rel. to feedback loop law and Chapin/Swanson communication to stakeholders)
+       b) Business motives instead of evolution theories
+       c) A study which analyses how the API applications change when new versions are introduced (rel. to controlling the behaviour etc.)
 
-Academia
-Some laws dont apply. Propose a new version of the law.
-Interesting that hardware did not drive change. This is cool cuz it means hardware apis can be generalised to any type of api.
-Since motives are reverse engineerable, it hsould encourage more ppl to do similar studies
-%%William add conclusion ideas here
-That the part about controlling how the API users use the API was such an important thing is interesting. (Not something we expected). 
-       MAke a study which looks the quality of applications before and after api changes have been introduced
-
-3. Future work: Summarise what the next steps could be.
-Obvious benefit for Axis is that the more features == more applications == higher value for their camera.
-If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase.
-This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
-       -->Suggest a similar study which looks at business factors
- in-depth study on each of the laws (more exhaustive) (suggested by Imed during Friday review)
-
-Random tips n trickz:
-       Look up the papers from the conference (especially regarding the discussion/conclusion)
-       discussion = revisiting research questions (and maybe structuring around industry/academia)
-       conclusion = summary part, main final points and future work 
-       look up implications for practitioners 
-       recommendations for the case company (need to put this somewhere)
-
-Implications for Practice tips: 
-       3.
-Each implications for practice section should include descriptions of a) problematic issue(s) being addressed, b) the specific audience(s) to which implications are addressed, c) a small number of recommendations about what the audience should/could/should not do based on the research findings, d) an expected outcome of carrying out recommendation(s), and e) some specific illustrations of what carrying out the recommendations might look like, perhaps in narrative form.
-
-\url{https://www.princeton.edu/futureofchildren/publications/journals/article/index.xml?journalid=46&articleid=212&sectionid=1379}
+       In-depth study on the laws or a specific law? Maybe less interesting.
 

### 2015-05-19 thesis/paper.tex
Disc draft

@@
 
+1. 
+       %Answer to RQ
+       Functionality is the main driver for change, and it catalyses other changes
+
+       %Point to results
+       relate to enhanicve types
+       relate to functuonality related laws
+
+       %Relate to literature
+       Refute refactorings paper
+       Maybe something else
+
+2. 
        %Answer to RQ
@@
 
-"1.1 Give a clear answer to the RQ. (Reject null / alternative)"
-
-"1.2 Point to results"
-%      -Bring up the most interesting/distinct trends
-
-"1.3 Compare to literature (i.e. relate to previous work)"
- %      -Do our results agree with prev. work?
-
 \subsection{RQ2 Answer}
@@
 
-\subsection{Contribution to Academia} 
+\subsection{Implications for Academia} 
+Reverse engineering/types: 
+       Since we were able to correctly analyse which types they were, it should encourage academia to do more studies which reverse engineer theories etc.
+
+Laws:
        Some laws don't apply. Consider inverting the law of org stab for APIs
-Since motives are reverse engineerable, it hsould encourage more ppl to do similar studies
+       Since motives are reverse engineerable, it should encourage more ppl to do similar studies
 
@@
 
-\subsection{Contribution to Practice}
+\subsection{Implications for Practitioners}
 %       -How will our study help Axis? (More important)
@@
        involved, in order to make intelligent decisions.'' //Swanson
+
        ``provide a realistic and practical classification to facilitate communication about, and the

### 2015-05-19 thesis/paper.tex
Started disc

@@
 The changes related to functionality being added, modified (deprecated) or removed were predicted with a 100\% accuracy.
-These changes were deemed the most significant by the interviewee, and it was expressed during the interivew that the these types of changes were the main driving factor behind the development of the new version.
+These changes were deemed the most significant by the interviewee, and it was expressed during the interview that the these types of changes were the main driving factor behind the development of the new version.
 On the contrary, three out of five changes which were unrelated to functionality were correctly predicted.
@@
 \section{Discussion} \label{discussion}
-Our results have provided valuable insight into the motives behind the evolution of APIs.
-The results show that APIs definitely can be studied from the point of view of long-established software evolution theories.
-Based on the results, we have formulated the subsequent outcomes.
+In this section, we will, based on the results of our study, answer the research questions and discuss the implications of our work, both for academia and practice.
 
@@
 
+Our results show that the major driving force for change in APIs is the push (!!!reword) for functionality.
+The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add brand-new (!!!reword) modules or adding functionality to existing modules were the most common.
+We also think that it is interesting to note that a majority of the changes which did not affect functionality, such as the updative changes, were spurred because of previous changes which were related to functionality.
+Following this line of thought, the hunger (!!!reword?) for functionality can be seen as a catalyst for other driving forces to occur (!!!reword).
+The view of considering functionality to be a major driver for change is supported by the analysis with Lehman's laws.
+In the law of Continuing Change, Lehman concludes that ``an E-type system must be continually adapted or it becomes progressively less satisfactory".
+The results of our work supports this view, as the changes did not only add functionality, but it was also found that the application developers most major concern were updates to functionality.
+
 1.
+
        %Answer to RQ
@@
        %Point to results
-       relate to enhanicve types
-       relate to functuonality related laws
+       relate to enhancive types
+       relate to functionality related laws
 

### 2015-05-19 thesis/paper.tex
Spellcheck

@@
 The study was conducted in two major phases \cite{andersson2007spiral}.
-The aim of the first phase was to generate hyptheses and to formulate clear research questions.
+The aim of the first phase was to generate hypotheses and to formulate clear research questions.
 This was achieved by using a data-driven approach to analysing the code and documentation.
-The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phsae.
+The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phase.
 Both phases were performed iteratively.
@@
 %Data and explanation
-No corrective changes were identified between v1.4 and v2.0.
+No corrective changes were identified between version 1.4 and version 2.0.
 There are two main reasons that we did not find any changes of this type.
@@
 The redesign of the system to make use of interfaces was also classified as a preventive change.
-Using interfaces to access modules helps to make them more maintainable and more easily extendable.
+Using interfaces to access modules helps to make them more maintainable and more easily extensible.
 %Concusion
@@
 %Data and Example
-One reformative change was identified between v1.4 and v2.0; a redesign of the existing example programs.
+One reformative change was identified between version 1.4 and version 2.0; a redesign of the existing example programs.
 The aim of this change was to update the examples to illustrate the new functionality in the API, showing how the modules interact and at the same time, presenting a standard for how to use the API.

### 2015-05-19 thesis/paper.tex
Discursion

@@
 
+\newpage
 \section{Discussion} \label{discussion}
@@
 
+\newpage
 \subsection{RQ1 Answer}
-RQ1: What drives API evolution?
 
@@
 
-1.
+In relation to this, previous work has identified that refactorings make up a substantial part of the changes APIs go through (!!!FIND PAPERS TO CITE HERE).
+These results are not in line with ours, since our results show that groomative changes are uncommon and that changes related to quality are not primary drivers of change and that they rather are ripple-effects of changes to functionality.
 
-       %Answer to RQ
-       Functionality is the main driver for change, and it catalyses other changes
+Our results found that seven out of eight of Lehman's laws do apply to API evolution.
+The law of Conservation of Organisational Stability was found not to apply, since changes to APIs are often discouraged (!!!reword) by the fear that it will disrupt the applications using the API.
+This inertia to change in API evolution is supported by other research, which also conclude that the negative effect that changes to APIs may have is a major factor to be considered \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}.
 
-       %Point to results
-       relate to enhancive types
-       relate to functionality related laws
-
-       %Relate to literature
-       Refute refactorings paper
-       Maybe something else
-
-2. 
-       %Answer to RQ
-       Talk about the results regarding the law of familiarity that didn't apply.
-
-       %Point to results
-
-       %Relate to literature
-       Cite the papers that say u shoulnt change APIs and say that our results agree \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers} 
-       Explain our results with this: 
-              1. The laws are not immutable, since they arise from the habits and practices of humans. [1980programs]
-              2.
-If laws governing large-program evolution can be formulated at all, they must certainly be weaker than those formulated in the biological sciences, where regularity stems from the collective behavior of cellular systems that, even though alive, are nonintelligent, i.e., are not influenced by conscious thought processes, at least at the level of human understanding.
-[On Understanding Laws, Evolution, and Conservation in the Large-Program Life Cycle]
+Based on our results, we form the conclusion that the hunger (reword) for functionality and the fear (reword) of changing are two opposing forces that cause updates to APIs to be infrequent.
+In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which causes the the law of Conservation of Organisational Stability to not apply (!!!reword).
+This occurring has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}.
+The underlying reason for this is that the laws are influenced by conscious thought processes, based on human understanding \cite{lehman1980understanding}, which in the case of APIs is the conscious decision to limit updates as much as possible.
 
@@
 
----------------------------------------------
-
 3. Suggest to Axis that they improve their feedback loop by using the types
@@
 
-%       -How will our study help other companies? (Less important)
-
-%Discuss and evaluate conflicting explanations of the results. This is the sign of a good discussion.
+--------------------------------------------------------------------------
 

### 2015-05-19 thesis/paper.tex
Purpose of the study and benefit to case company added in the introduction

@@
 
-%Gap in Literature
-Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
-The area of programming language APIs is well-explored \cite{hou2011exploring, shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
-To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.
-
-%switch places between ^ and v
-
 %Purpose
@@
 
-%Method %wrong tense %include RQs in here %include clear contribution (to johanna)
-In order to achieve this, an exploratory case study will be undertaken to investigate the underlying motives behind changes to APIs.
-Empirical analysis of the changes between two major versions of an API will be undertaken, following which, an interview with the architects will be used to validate the findings of our analysis.
+%Gap in Literature
+Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
+The area of programming language APIs is well-explored \cite{hou2011exploring, shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
+To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.
 
-%Can't find a place for this - it's repeated in the Purpose
-%Reverse engineering design decisions is a challenging yet interesting problem.
-The better we can understand why changes occur and what problems they are trying to solve, the better we can design around these problems to avoid them cropping up in the future.
+%Purpose of the study
+The goal of the study was twofold.
+Firstly, the aim was to explore what are the driving forces behind API evolution and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes.
+With this information, we could determine to what extent these change decisions can be reverse engineered.
+%Why this is important for the case company.
+Understanding what drives the evolution of their API could be significant value to the case company.
+Being aware of what types of changes occur more frequently can help the case company design their APIs to mitigate or assist these types of change.
+Furthermore, understanding which software evolution theories apply to APIs can help the case company control the evolution of their API and could help them better prepare for change in the future.
 
@@
 \section{Background} \label{background}
-This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.
-Follow that, we will introduce the company and API examined in this study.
+This section will introduce the fields of API design, software evolution and it will provide a review of studies that are related to our study.
+The subsequent section will introduce the case company with a description of the API used in this study.
 
 \subsection{API Design} \label{api_design}
-API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
 
+API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
 Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.
@@
 
-%Re-write this section... it's wrong
-Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}.
-The laws, known as Lehman's laws, are: 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conservation of Familiarity, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System.
+Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
+They are presented in table \ref{table:expl_laws}.
 The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
@@
        \centering
-       \begin{tabular}[ht]{l|c}
+       \begin{tabular}[ht]{p{3in}}
        \toprule
+              \begin{enumerate}
+              \item \textbf{Continuing Change} \newline
+              E-Type systems must be continually adapted else they become progressively less satisfactory.                     
+              \item \textbf{Increasing Complexity}\newline 
+              As an E-Type system evolves its complexity increases unless work is done to maintain or reduce it.                  
+              \item \textbf{Self Regulation}\newline 
+              E-Type system evolution process is self regulation with distribution of product and process measures close to normal.                     
+              \item \textbf{Conservation of Organisational Stability}\newline 
+              The average effective global rate in an evolving E-Type system is invariant over product lifetime.                     
+              \item \textbf{Conservation of Familiarity}\newline 
+              As an E-type system evolves all associated with it, developers, sales, personnel, users, for example, must maintain mastery of its content and behaviour to achieve satisfactory evolution.
+Excessive growth diminishes that mastery.
+Hence the average incremental growth remains invariant as the system evolves.
+              \item \textbf{Continuing Growth}\newline 
+              The functional content of E-Type systems must be continually increased to maintain user satisfaction over their lifetime.                
+              \item \textbf{Declining Quality}\newline 
+              The quality of E-Type systems will appear to be declining unless they are rigorously maintained and adapted to operational environment changes.                     
+              \item \textbf{Feedback System}\newline 
+              E-Type evolution process constitute multi-level, multi-loop, multi-agent feedback systems and must be treated as such to achieve significant improvement over any reasonable base.
 
-              \textbf{Law}                              & \textbf{Explanation}    \\ \midrule
-              Continuing Change                         & [Explanation]                      \\ \hline
-              Increasing Complexity                     & [Explanation]                     \\ \hline
-              Self Regulation                           & [Explanation]                      \\ \hline
-              Conservation of Organisational Stability  & [Explanation]                     \\ \hline
-              Conservation of Familiarity               & [Explanation]                      \\ \hline
-              Continuing Growth                         & [Explanation]                      \\ \hline
-              Declining Quality                         & [Explanation]                     \\ \hline
-              Feedback System                           & [Explanation]                      \\
-
+              \end{enumerate} \\
               \bottomrule
-
        \end{tabular}
@@
 This study has been conducted using the case study methodology \cite{runeson2009guidelines}.
-The goal of the study was twofold.
-Firstly, the aim was to empirically explore the motives behind changes to APIs and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of their motives.
 Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.
-
-%Reasons for choosing case study
 The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.

### 2015-05-19 thesis/paper.tex
Added small introduction to the results section

@@
 %%Small intro to this section. Mention that : In total, thirteen unique changes were found.
+This section will present the results of our study and is structured around the research questions.
+Each section begins with a summary of the results and a subsequent in depth description of the findings.
 
-The majority of changes between version 1.4 and version 2.0 have been additions to functionality of the API.
+In total, thirteen unique changes were identified when analysing the source code, the majority of which were additions of functionality of the API.
 Such additions include added functionality to allow mechanical and digital control of the camera, to utilise additional storage devices, to allow serial connectivity and to allow audio analysis on the cameras.

### 2015-05-19 thesis/paper.tex
implic academ

@@
 
+\newpage
+
 \subsection{RQ2 Answer}
@@
 
+\newpage
+
 \subsection{Implications for Academia} 
-Reverse engineering/types: 
-       Since we were able to correctly analyse which types they were, it should encourage academia to do more studies which reverse engineer theories etc.
+The implications of our findings should encourage academia to further study APIs by relating them to existing software evolution theories.
+Considering that we were able to successfully reverse engineer the changes made to the API in this study, it opens up possibilities to base future research on, for example, the types of software evolution and software maintenance.
+Since the kappa analysis showed that there was a high level of agreement between our predictions and the actual motives to the change, it shows that the types of software evolution and software maintenance could even be used as a base for a large-scale quantitative analysis to map the types of changes made to APIs.
 
-Laws:
-       Some laws don't apply. Consider inverting the law of org stab for APIs
-       Since motives are reverse engineerable, it should encourage more ppl to do similar studies
+By analysing the API based on Lehman's laws, we were able to find that the law of Conservation of Organisational Stability did not apply to the API examined in this study.
+Our results suggest that the opposite of what the law says in its current form is closer to the truth (!!!reword) for APIs.
+Since we only studied one API, we cannot safely refute the law or propose a new formulation of it.
+We do, however, believe that academia should be wary of assuming that this law is true for APIs.
 
-%       -How will our study help other researchers?
-%       -How are the results valuable?
+\newpage
 
@@
 
+\newpage
+
 \section{Conclusion} \label{conclusion}

### 2015-05-19 thesis/paper.tex
disc implic f pract

@@
 \newpage
+
+\newpage
+
 \section{Discussion} \label{discussion}
@@
 
-\newpage
 \subsection{RQ1 Answer}  
-
 Our results show that the major driving force for change in APIs is the push (!!!reword) for functionality.
@@
 
-\newpage
-
 \subsection{RQ2 Answer}
@@
 
-\newpage
-
 \subsection{Implications for Academia} 
@@
 
-\newpage
+\subsection{Implications for Practitioners}
+The changes introduced to the API are mainly based on the expertise and experiences of the API architects at the case company.
+There has not been a scientific approach to maintaining the system and the knowledge from academia has not directly affected the way that the API's evolution has been managed.
+With our work, we hope to provide a new angle of analysis
 
-\subsection{Implications for Practitioners}
+------------------------------------------------------------------------
+
 %       -How will our study help Axis? (More important)
@@
 
---------------------------------------------------------------------------
-
 \newpage

### 2015-05-19 thesis/paper.tex
Fixed sentence in meth

@@
 To allow us to answer \textbf{RQ3}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview.
-Success was determined by comparing the inter-rater reliability, by performing calculating Cohen's Kappa gathered data.
+Success was determined by comparing the inter-rater reliability, by calculating Cohen's kappa \cite{cohen1968weighted} for the gathered data.
 
@@
 The main thing will be:
-1. Our results found that feedback loop is, a) very importnat and b) the main thing that Axis wants to improve
+1. Our results found that feedback loop is, a) very important and b) the main thing that Axis wants to improve
 2. Relate to Swanson/Chapin saying the types help to budget/plan and facilitate communication between stakeholders
@@
 % of the organizational structure(s) upon
-% which they are based.
+% which they are based. p
 

### 2015-05-20 thesis/paper.tex
Improved importance for case company

@@
 %Why this is important for the case company.
-Understanding what drives the evolution of their API could be significant value to the case company.
-Being aware of what types of changes occur more frequently can help the case company design their APIs to mitigate or assist these types of change.
-Furthermore, understanding which software evolution theories apply to APIs can help the case company control the evolution of their API and could help them better prepare for change in the future.
+This study has many potential benefits for the case company.
+Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks.
+This improved communication could provide a common language that developers, users and management can use to discuss potential evolution of the APIs.
+Understanding the evolution theories could further assist understanding of how change will occur and how to plan for it.
+Lastly, by keeping a history of changes to an API over time, trends can be identified which could help with future API design.
 

### 2015-05-20 thesis/paper.tex
impl pract

@@
 
-\newpage
-
 \section{Discussion} \label{discussion}
@@
 Since we only studied one API, we cannot safely refute the law or propose a new formulation of it.
-We do, however, believe that academia should be wary of assuming that this law is true for APIs.
+We do, however, believe that academia should be wary of assuming (!!!reword) that this law is true for APIs.
 
@@
 There has not been a scientific approach to maintaining the system and the knowledge from academia has not directly affected the way that the API's evolution has been managed.
-With our work, we hope to provide a new angle of analysis
+With our work, we hope to provide a new type of insight (!!!reword) into how the API is maintained.
+Our analysis of the API based on Lehman's laws should further assure that the case company is moving the evolution of the API in the right direction.
+With our research, we leave a challenge (!!!reword) for the case company in how to tackle challenges related to the law of Conservation of Organisational Stability.
+Determining if the benefits of continuously and frequently updating the API outweigh the negative effects that these updates could have on the application developers, we leave up to the company (!!!reword so that it doesnt sound negative)
 
-------------------------------------------------------------------------
+An alternative way of addressing this problem could be by including the application developers in the feedback loop.
+
+----------------------------------------------------------------------
 
@@
 
-\newpage
-
 \section{Conclusion} \label{conclusion}

### 2015-05-20 thesis/paper.tex
impl pract done

@@
 
-An alternative way of addressing this problem could be by including the application developers in the feedback loop.
-
-----------------------------------------------------------------------
-
-%       -How will our study help Axis? (More important)
-The laws therefore form an environment within which the effectiveness of programming methodologies and management strategies and techniques can be evaluated, a backdrop against which better methodologies and techniques can be developed.
-[1980programs]
-
-The main thing will be:
-1. Our results found that feedback loop is, a) very important and b) the main thing that Axis wants to improve
-2. Relate to Swanson/Chapin saying the types help to budget/plan and facilitate communication between stakeholders
-       [quotes re. budget/plan]:
-
-   ``Managers involved in software evolution and software maintenance have great difficulty in
-   defining, justifying, budgeting, staffing, supervising, accounting for, marshalling resources
-   for, and assessing the work when coarse non-objective measures are used [4]. Things not
-   appropriately named are often undervalued and treated as miscellaneous or trivial, since
-   communication about them is made more cumbersome.'' %Chapin
-
-       [quotes re. communication/stakeholders]:
-       ``management must be thoroughly fami-liar with the organizational conventions and practices
-       involved, in order to make intelligent decisions.'' //Swanson
-
-       ``provide a realistic and practical classification to facilitate communication about, and the
-       management of, software evolution and maintenance among researchers, practitioners, and their
-       managers;'' //Chapin
-
-%Whole bunch of Swanson stuff below.
-% The implications for the management of software
-% maintenance are several. First, insofar as maintenance
-% is performed informally, i.e. in the absence of an
-% established set of organizational conventions and prac-
-% tices, the measurement of maintenance performance w i l l
-% not be feasible. The establishment of a maintenance
-% data base, a precondition to performance measurement,
-% is not possible in the absense of organizational struc-
-% ture. In informal situations, performance must be assessed informally.
-
-% Secondly, in any given organization in which main-
-% tenance performance is formally assessed, in terms of
-% specific measures, management must be thoroughly fami-
-% l i a r with the organizational conventions and practices
-% involved, in order to make intelligent decisions. No
-% single measure or set of measures w i l l i t s e l f reveal
-% that maintenance is going "better" or "worse" than
-% management has a right to expect or desire. Such a
-% judgment must follow as a systemic inference from an
-% analysis of the performance measurements, made in the
-% context of f a m i l i a r i t y with the organizational struc-
-% ture which made these measurements possible.
-
-% Finally, in the absence of f a m i l i a r i t y with other,
-% alternative organizational structures for performing
-% maintenance, management w i l l be essentially unable to
-% assess i t s own established structure. Nothing in the
-% performance measurements made within the context of the
-% established structure w i l l indicate the opportunity
-% costs associated with this structure. Management must
-% look outside, to the performance measurements and
-% structures of other organizations, to assess what might
-% reasonably be achieved through organizational change.
-
-% In the context of a maintenance organizational
-% structure and a particular set of data gathered in the
-% performance of maintenance within this structure, i t
-% is possible to derive some performance measures which
-% should be appropriately "suggestive" to management.
-
-% Measures of maintenance performance are
-% not meaningful except within the context
-% of the organizational structure(s) upon
-% which they are based. p
-
-3. Suggest to Axis that they improve their feedback loop by using the types
-
-Also suggest that they keep evolving the API with reference to the laws
-
-Implications for Practice tips: 
-       3. Each implications for practice section should include descriptions of 
-       a) problematic issue(s) being addressed, 
-       b) the specific audience(s) to which implications are addressed, 
-       c) a small number of recommendations about what the audience should/could/should not do based on the research findings, 
-       d) an expected outcome of carrying out recommendation(s), and 
-       e) some specific illustrations of what carrying out the recommendations might look like, perhaps in narrative form.
-
-\url{https://www.princeton.edu/futureofchildren/publications/journals/article/index.xml?journalid=46&articleid=212&sectionid=1379}
+One way of finding the solution to this problem would be by including the application developers in the feedback loop.
+Since the application developers are on the receiving end of the changes, we believe that their needs have to be assessed before the problem can be solved.
+With our study we identified both that the law of Feedback System is of great importance to the case company and that it is one of the main aspects of the development of their API which they want to improve (!!!reword).
+One challenge of software evolution is that the activities carried out are often intangible and non-objective \cite{chapin2001types, lientz1980software}.
+Based on this, we propose that our study which has granulated the activites is used as a basis for communicating the current stage of the evolution of their API.
+We hope that this classification can be used in its current form, to help quantify the activities and to provide an overview of them.
+We also hope that the approach we used can be used to predict which types of activites should be emphasised in the future evolution of the API.
+With our study we have also demonstrated that the classification of changes is achievable, which, in turn, should encourage the case company to follow suit (!!!casual).
 

### 2015-05-20 thesis/paper.tex
small

@@
 
-\subsection{Validity Threats} \label{validity_threats} %Review 1 or 2 more times (John first)
+\subsection{Validity Threats} \label{validity_threats} 
 In this section we discuss possible threats to construct validity, internal validity, external validity and reliability \cite{runeson2009guidelines}.
@@
 
-Based on our results, we form the conclusion that the hunger (reword) for functionality and the fear (reword) of changing are two opposing forces that cause updates to APIs to be infrequent.
+Based on our results, we form the conclusion that the hunger (!!!reword) for functionality and the fear (!!!reword) of changing are two opposing forces that cause updates to APIs to be infrequent.
 In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which causes the the law of Conservation of Organisational Stability to not apply (!!!reword).
@@
 \subsection{RQ2 Answer}
-RQ2: How reverse engineer?
+Based on the results
 

### 2015-05-20 thesis/paper.tex
disc rq2

@@
 \subsection{RQ2 Answer}
-Based on the results
-
-%1.1 Give a clear answer to the RQ. (Reject null / alternative)
-
-%1.2 Point to results
-%      -Bring up the most interesting/distinct trends
-
-%1.3 Compare to literature (i.e. relate to previous work)
- %      -Do our results agree with prev. work?
+We conclude that we were able to reverse engineer the change decisions to a large extent.
+This is clear from the results, which showed that 85\% of the changes were reverse engineered correctly.
+The kappa value of 0.812 further supports this.
+We interpret that the significance of this result suggests that reverse engineering of change decisions can be done in situations where a perfect result is not required.
+In cases where a near-perfect result is enough, we do, however, believe that reverse engineering change decisions is worthwhile (!!!this sentence weird).
+This line of thought is supported by our results, which, in summary, show that we are able to reverse engineer the most major trends with very high accuracy, but that certain nuances of the changes can be misinterpreted.
 

### 2015-05-20 thesis/paper.tex
Fixed refs
3rd texit -> 3rd super

@@
 These changes were not changes to individual parts of the API, but were instead larger changes that affected the whole API.
-Such examples include a shift towards using interfaces to access features, a different error-handling approach and the inclusion of additional 3\textit{rd} party libraries.
+Such examples include a shift towards using interfaces to access features, a different error-handling approach and the inclusion of additional 3\textsuperscript{rd} party libraries.
 Typically, these general trends also have a secondary type of change attributed to them.
@@
 %Data and examples
-A single change was identified as being adaptive; the inclusion of new 3\textit{rd} party libraries.
+A single change was identified as being adaptive; the inclusion of new 3\textsuperscript{rd} party libraries.
 Libraries were added for audio and data communication.

### 2015-05-20 thesis/paper.tex
Results intro tables

@@
 %Types intro
-The results show that certain types of change are more prevalent than others, these results are shown in \ref{table:type_counts}.
+The results show that certain types of change are more prevalent than others, these results are shown in Table \ref{table:type_counts}.
 Analysis of the results showed that enhancive changes were the primary types of change that drive API evolution and that they act as a catalyst for many of the other changes in the API.
@@
 Similarly, there was no evidence found for evaluative, consultive nor training activities.
+
+\begin{table}
+       \centering
+       \begin{tabular}[ht]{l|c|c}
+              \toprule
+
+              \textbf{Type}        & \textbf{Main Types}       &\textbf{Secondary Types}   \\ \midrule
+              Enhancive            & 7                         & -                         \\ \hline
+              Corrective           & -                         & -                         \\ \hline
+              Reductive            & 1                         & -                         \\ \hline
+              Adaptive             & 1                         & -                         \\ \hline
+              Performance          & -                         & -                         \\ \hline
+              Preventive           & 2                         & -                         \\ \hline
+              Groomative           & -                         & 5                         \\ \hline
+              Updative             & 1                         & 1                         \\ \hline
+              Reformative          & 1                         & 1                         \\ \hline
+              Evaluative           & -                         & -                         \\ \hline
+              Consultive           & -                         & -                         \\ \hline
+              Training             & -                         & -                         \\
+
+              \bottomrule
+
+       \end{tabular}
+       \caption{Identified Types of Change}
+       \label{table:type_counts}
+\end{table}
 
@@
 
+%Lehman Table
+\begin{table}
+       \centering
+       \begin{tabular}[ht]{l|c}
+              \toprule
+
+              \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
+              Continuing Change                         & True                      \\ \hline
+              Increasing Complexity                     & True                     \\ \hline
+              Self Regulation                           & True                      \\ \hline
+              Conservation of Organisational Stability  & False                     \\ \hline
+              Conservation of Familiarity               & True                      \\ \hline
+              Continuing Growth                         & True                      \\ \hline
+              Declining Quality                         & True                     \\ \hline
+              Feedback System                           & True                      \\
+
+              \bottomrule
+
+       \end{tabular}
+       \caption{The applicability of Lehman's laws}
+       \label{table:lehman}
+\end{table}
+
 In the remainder of this section we will discuss the results related to each type of change category, discussing the results for each of them with examples from the changes identified between the two versions of the API.
 Subsequently, each of Lehman's laws will be discussed and our results will be presented showing if the laws apply to APIs or not.
-
-%Lehman Table
-% \begin{table}
-%        \centering
-%        \begin{tabular}[ht]{l|c}
-%               \toprule
-
-%               \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
-%               Continuing Change                         & True                      \\ \hline
-%               Increasing Complexity                     & True                     \\ \hline
-%               Self Regulation                           & True                      \\ \hline
-%               Conservation of Organisational Stability  & False                     \\ \hline
-%               Conservation of Familiarity               & True                      \\ \hline
-%               Continuing Growth                         & True                      \\ \hline
-%               Declining Quality                         & True                     \\ \hline
-%               Feedback System                           & True                      \\
-
-%               \bottomrule
-
-%        \end{tabular}
-%        \caption{The applicability of Lehman's laws}
-%        \label{table:lehman}
-% \end{table}
 
@@
 Removing functionality
-
-% \begin{table}
-%        \centering
-%        \begin{tabular}[ht]{l|c|c}
-%               \toprule
-
-%               \textbf{Type}        & \textbf{Main Types}       &\textbf{Secondary Types}   \\ \midrule
-%               Enhancive            & 7                         & -                         \\ \hline
-%               Corrective           & -                         & -                         \\ \hline
-%               Reductive            & 1                         & -                         \\ \hline
-%               Adaptive             & 1                         & -                         \\ \hline
-%               Performance          & -                         & -                         \\ \hline
-%               Preventive           & 2                         & -                         \\ \hline
-%               Groomative           & -                         & 5                         \\ \hline
-%               Updative             & 1                         & 1                         \\ \hline
-%               Reformative          & 1                         & 1                         \\ \hline
-%               Evaluative           & -                         & -                         \\ \hline
-%               Consultive           & -                         & -                         \\ \hline
-%               Training             & -                         & -                         \\
-
-%               \bottomrule
-
-%        \end{tabular}
-%        \caption{Identified Types of Change}
-%        \label{table:type_counts}
-% \end{table}
 

### 2015-05-20 thesis/paper.tex
results rq1 intro

@@
 Reductive and adaptive changes, while important, did not strongly drive the evolution of the API.
-No evidence was found for corrective, performance types of change.
-Similarly, there was no evidence found for evaluative, consultive nor training activities.
+No evidence was found for corrective or performance types of change.
+Similarly, there was no evidence found for evaluative, consultive or training activities.
 
@@
 
-In the remainder of this section we will discuss the results related to each type of change category, discussing the results for each of them with examples from the changes identified between the two versions of the API.
+Following this section, we will discuss the results related to each type of change category, discussing the results for each of them with examples from the changes identified between the two versions of the API.
 Subsequently, each of Lehman's laws will be discussed and our results will be presented showing if the laws apply to APIs or not.
-
-%Re-write this intro a bit (since I moved it)
-All of the identified changes have been given a type based the nature of the change according to the Types of Software Evolution and Software Maintenance decision tree \cite{chapin2001types}.
-Table \ref{table:type_counts} shows the total count of each type of change found in the different versions of the API.
-
-Functionality is a prime driver of API evolution // Hardware is not a driving factor
-Maintainability does not drive change // Documentation does not drive change
-Standardising application development
-Removing functionality
 

### 2015-05-20 thesis/paper.tex
Removed RQ3

@@
 \begin{description}
-\item[\textbf{RQ1}] How do companies actively drive API evolution?
-\item[\textbf{RQ2}] How do APIs ``passively'' evolve?
-\item[\textbf{RQ3}] To what extent can we reverse engineer API change decisions?
+\item[\textbf{RQ1}] What are the driving forces to API evoltion?
+\item[\textbf{RQ2}] To what extent can we reverse engineer API change decisions?
 
@@
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ3}.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ2}.
 
@@
 Each of the previously identified trends were given a main type of maintenance and, if appropriate, a secondary type.
+In addition to this, we analysed the trends based on Lehman's Laws, to determine if they applied to the changes made to the API.
 This material, as well as the results of the interview, were then used as the basis for answering \textbf{RQ1}.
@@
 %RQ2
-The analysis of the changes and trends, combined with the information gathered from the interview, allowed us to answer \textbf{RQ2} by determining if Lehman's Laws apply to the changes made to the API.
-
-%RQ3
-To allow us to answer \textbf{RQ3}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview.
+To allow us to answer \textbf{RQ2}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview.
 Success was determined by comparing the inter-rater reliability, by calculating Cohen's kappa \cite{cohen1968weighted} for the gathered data.
@@
 
-\subsubsection{Types 1by1}
+\subsubsection{Types of Change}
 
@@
 
-\subsubsection{Laws 1by1}
+\subsubsection{Lehman's Laws}
 
@@
 
-\subsection{RQ3 Results}
+\subsection{RQ2 Results}
 \noindent
-RQ3: \textbf{To what extent can we reverse engineer API change decisions?}
+RQ2: \textbf{To what extent can we reverse engineer API change decisions?}
 \smallskip

### 2015-05-20 thesis/paper.tex
Changed heading names
Fixed typo
Typo in RQs
Updates to comments in discussion

@@
 \begin{description}
-\item[\textbf{RQ1}] What are the driving forces to API evoltion?
+\item[\textbf{RQ1}] What are the driving forces of API evolution?
 \item[\textbf{RQ2}] To what extent can we reverse engineer API change decisions?
@@
 Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
-They are presented in table \ref{table:expl_laws}.
+They are presented in Table \ref{table:expl_laws}.
 The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
@@
 
-\subsection{RQ1 Results} \label{results_rq1}
+\subsection{The Driving Forces of API Evolution} \label{results_rq1}
 
@@
 
-\subsection{RQ2 Results}
+\subsection{Reverse Engineering API Change Decisions}
 \noindent
@@
 \subsection{RQ1 Answer}  
-Our results show that the major driving force for change in APIs is the push (!!!reword) for functionality.
-The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add brand-new (!!!reword) modules or adding functionality to existing modules were the most common.
-We also think that it is interesting to note that a majority of the changes which did not affect functionality, such as the updative changes, were spurred because of previous changes which were related to functionality.
-Following this line of thought, the hunger (!!!reword?) for functionality can be seen as a catalyst for other driving forces to occur (!!!reword).
+Our results show that the major driving force for change in APIs is the call for increased functionality.
+The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add modules or new functionality to existing modules were the most common.
+We also think that it is interesting to note that a majority of the changes which did not affect functionality, such as the updative changes, were spurred because of previous changes that were related to functionality.
+Following this line of thought, the desire for new functionality can be seen as a catalyst that allows further driving forces to occur (!!!better?).
 The view of considering functionality to be a major driver for change is supported by the analysis with Lehman's laws.
@@
 
-In relation to this, previous work has identified that refactorings make up a substantial part of the changes APIs go through (!!!FIND PAPERS TO CITE HERE).
-These results are not in line with ours, since our results show that groomative changes are uncommon and that changes related to quality are not primary drivers of change and that they rather are ripple-effects of changes to functionality.
+In relation to this, previous work has identified that refactorings make up a substantial part of the changes APIs undergo (!!!FIND PAPERS TO CITE HERE).
+These results are not in line with ours, since our results show that groomative changes are uncommon and that changes related to quality are not primary drivers of change, rather, they are ripple-effects of changes to functionality \cite{robbes2012developers}.
 
 Our results found that seven out of eight of Lehman's laws do apply to API evolution.
-The law of Conservation of Organisational Stability was found not to apply, since changes to APIs are often discouraged (!!!reword) by the fear that it will disrupt the applications using the API.
+The law of Conservation of Organisational Stability was found not to apply, since changes to APIs are unfavourable due to the potential disruption the applications using the API could face.
 This inertia to change in API evolution is supported by other research, which also conclude that the negative effect that changes to APIs may have is a major factor to be considered \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}.
 
-Based on our results, we form the conclusion that the hunger (!!!reword) for functionality and the fear (!!!reword) of changing are two opposing forces that cause updates to APIs to be infrequent.
-In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which causes the the law of Conservation of Organisational Stability to not apply (!!!reword).
+Based on our results, we form the conclusion that the desire for functionality and the reluctance of changing are two opposing forces that cause updates to APIs to be infrequent.
+In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which causes the the law of Conservation of Organisational Stability to not apply (!!!
+which means the law of Conservation of Organisational Stability is inappropriate for APIs).
 This occurring has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}.
@@
 We interpret that the significance of this result suggests that reverse engineering of change decisions can be done in situations where a perfect result is not required.
-In cases where a near-perfect result is enough, we do, however, believe that reverse engineering change decisions is worthwhile (!!!this sentence weird).
+In cases where a near-perfect result is enough, we do, however, believe that reverse engineering change decisions is worthwhile (!!!this sentence weird - yeah).
 This line of thought is supported by our results, which, in summary, show that we are able to reverse engineer the most major trends with very high accuracy, but that certain nuances of the changes can be misinterpreted.
@@
 By analysing the API based on Lehman's laws, we were able to find that the law of Conservation of Organisational Stability did not apply to the API examined in this study.
-Our results suggest that the opposite of what the law says in its current form is closer to the truth (!!!reword) for APIs.
-Since we only studied one API, we cannot safely refute the law or propose a new formulation of it.
-We do, however, believe that academia should be wary of assuming (!!!reword) that this law is true for APIs.
+Our results suggest that the opposite of what the law suggests, in its current form, is more applicable for APIs.
+Since only a single API was studied, we cannot safely refute the law or propose a new formulation of it.
+Academia should therefore be wary of assuming that this law is true for APIs.
 
@@
 There has not been a scientific approach to maintaining the system and the knowledge from academia has not directly affected the way that the API's evolution has been managed.
-With our work, we hope to provide a new type of insight (!!!reword) into how the API is maintained.
+With our work, we hope to provide further insight into how the API is maintained.
 Our analysis of the API based on Lehman's laws should further assure that the case company is moving the evolution of the API in the right direction.
-With our research, we leave a challenge (!!!reword) for the case company in how to tackle challenges related to the law of Conservation of Organisational Stability.
-Determining if the benefits of continuously and frequently updating the API outweigh the negative effects that these updates could have on the application developers, we leave up to the company (!!!reword so that it doesnt sound negative)
+Our research proposes a challenge for the case company in how to tackle challenges related to the law of Conservation of Organisational Stability.
+Determining if the benefits of continuously and frequently updating the API outweigh the side-effects that these updates could have on the application developers, is something that the case company will need to consider.
 
@@
 Since the application developers are on the receiving end of the changes, we believe that their needs have to be assessed before the problem can be solved.
-With our study we identified both that the law of Feedback System is of great importance to the case company and that it is one of the main aspects of the development of their API which they want to improve (!!!reword).
-One challenge of software evolution is that the activities carried out are often intangible and non-objective \cite{chapin2001types, lientz1980software}.
-Based on this, we propose that our study which has granulated the activites is used as a basis for communicating the current stage of the evolution of their API.
+With our study we identified both that the law of Feedback System is of great importance to the case company and that it is one of the key areas of API development that the case company wishes to improve.
+One challenge of the challenges posed by software evolution is that the activities carried out are often intangible and non-objective \cite{chapin2001types, lientz1980software}.
+Based on this, we propose that our study which has granulated the activities is used as a basis for communicating the current stage of the evolution of their API.
 We hope that this classification can be used in its current form, to help quantify the activities and to provide an overview of them.
-We also hope that the approach we used can be used to predict which types of activites should be emphasised in the future evolution of the API.
-With our study we have also demonstrated that the classification of changes is achievable, which, in turn, should encourage the case company to follow suit (!!!casual).
+We also hope that the approach we used can be used to predict which types of activities should be emphasised in the future evolution of the API.
+With our study we have also demonstrated that the classification of changes is achievable, which, in turn, should encourage the case company adopt this method of classifying change.
 

### 2015-05-20 thesis/paper.tex
case company -> company A

@@
 
-\textbf{Background  } %Give a feeling of the need of this study, answer why Axis needs what is in the Objective (+Context)
+\textbf{Background  } %Give a feeling of the need of this study, answer why the case company needs what is in the Objective (+Context)
 The driving forces of modifications to APIs have been investigated before, however, platform APIs are, until now, unexplored.
@@
 \begin{description}
-\item[\textbf{RQ1}] What are the driving forces of API evolution?
+\item[\textbf{RQ1}] What drives API evolution?
 \item[\textbf{RQ2}] To what extent can we reverse engineer API change decisions?
-
 \end{description}
@@
 \subsection{Case Company Description} \label{case_company_description}
-The case company is a company operating in the domain of video surveillance.
-The company's headquarters are located in Lund, Sweden, with offices in 49 countries worldwide.
-The company is the global market leader in the markets of network cameras and video encoders.
+The case company of this studied will from here on be referred to as \textit{company A}.
+Company A operates in the domain of video surveillance.
+The company's headquarters is located in Lund, Sweden, with offices in 49 countries worldwide.
+Company A is the global market leader in the markets of network cameras and video encoders.
 They develop embedded software for security cameras.
@@
 Prior to version 1.4 being released, updates were only made to include additional built options and did not include any additional functionality.
-The API is used by company partners, which are companies who develop applications for the cameras.
+The API is used by company partners, which are other companies which develop applications for the cameras.
 These applications are, in turn, used by the end-users of the cameras.
@@
 \textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types, lehman90sview}.
-Due to restricted access to the company's source code, we were not able to include versions prior to version 1.4 in our analysis.
+Due to restricted access to company A's source code, we were not able to include versions prior to version 1.4 in our analysis.
 This means that the evolution of the API was studied during a rather short period of its lifetime.
@@
 Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role, xing2006refactoring}.
-It was revealed during the interview that the functionality was removed because the case company no longer wished to support this feature.
+It was revealed during the interview that the functionality was removed because the company A no longer wished to support this feature.
 %Conclusion
@@
 \textbf{Continuing Change  } 
-The case company described that including new functional content was one of the top priorities for the release of version 2.0.
+Company A described that including new functional content was one of the top priorities for the release of version 2.0.
 This is supported by the characteristic of the changes identified in this study.
@@
 It was also made clear that a contributing factor for changing certain parts of the API was to bring it into line with the new interface design.
-The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that the company currently did not make use of these.
+The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that company A currently did not make use of these.
 Although the importance of reducing the complexity was stated, it was made clear during the interview that one module was not updated between the versions, even though it did not follow the new standards of version 2.0.
@@
 The same pattern can be seen for the example code, which went through major changes as a result of the changes to the API code.
-The case company's intent to control the way that their API is used also suggests that the knowledge of how to use the API is of importance, since if the API is used in too many different ways, it will be more difficult for the case company to have relevant documentation and example code.
+Company A's intent to control the way that their API is used also suggests that the knowledge of how to use the API is of importance, since if the API is used in too many different ways, it will be more difficult for company A to have relevant documentation and example code.
 It was also expressed during the interview that further transparency in how the API should be used could be achieved.
@@
 This also ties in with the ambition of controlling the way that the API is used, as mentioned previously.
-It was also mentioned that the case company had received feedback from the API users that more frequent updates to the functional content was desirable, even though this may require them to update their application code.
+It was also mentioned that company A had received feedback from the API users that more frequent updates to the functional content was desirable, even though this may require them to update their application code.
 We therefore conclude that the law of continuing growth applies to APIs.
@@
 \textbf{Feedback System  } 
-One of the future goals of improvement of the case company is to better include the API users and end-users of the applications in their feedback loop.
+One of the future goals of improvement of company A is to better include the API users and end-users of the applications in their feedback loop.
 Currently, only the API users are included in this feedback loop and the API architect expressed the desire to also include the end-users.
@@
 \subsection{Reverse Engineering API Change Decisions}
-\noindent
-RQ2: \textbf{To what extent can we reverse engineer API change decisions?}
-\smallskip
 
@@
 \section{Discussion} \label{discussion}
-In this section, we will, based on the results of our study, answer the research questions and discuss the implications of our work, both for academia and practice.
 
-\subsection{RQ1 Answer}  
+\noindent
+RQ1: \textbf{What drives API evolution?}
+\smallskip
+
 Our results show that the major driving force for change in APIs is the call for increased functionality.
@@
 
-\subsection{RQ2 Answer}
+\smallskip
+\noindent
+RQ2: \textbf{To what extent can we reverse engineer API change decisions?}
+\smallskip
+
 We conclude that we were able to reverse engineer the change decisions to a large extent.
@@
 \subsection{Implications for Practitioners}
-The changes introduced to the API are mainly based on the expertise and experiences of the API architects at the case company.
+The changes introduced to the API are mainly based on the expertise and experiences of the API architects at company A.
 There has not been a scientific approach to maintaining the system and the knowledge from academia has not directly affected the way that the API's evolution has been managed.
 With our work, we hope to provide further insight into how the API is maintained.
-Our analysis of the API based on Lehman's laws should further assure that the case company is moving the evolution of the API in the right direction.
-Our research proposes a challenge for the case company in how to tackle challenges related to the law of Conservation of Organisational Stability.
-Determining if the benefits of continuously and frequently updating the API outweigh the side-effects that these updates could have on the application developers, is something that the case company will need to consider.
+Our analysis of the API based on Lehman's laws should further assure that company A is moving the evolution of the API in the right direction.
+Our research proposes a challenge (!!!reword cuz repeating) for company A in how to tackle challenges related to the law of Conservation of Organisational Stability.
+Determining if the benefits of continuously and frequently updating the API outweigh the side-effects that these updates could have on the application developers, is something that company A will need to consider.
 
@@
 Since the application developers are on the receiving end of the changes, we believe that their needs have to be assessed before the problem can be solved.
-With our study we identified both that the law of Feedback System is of great importance to the case company and that it is one of the key areas of API development that the case company wishes to improve.
+With our study we identified both that the law of Feedback System is of great importance to company A and that it is one of the key areas of API development that company A wishes to improve.
 One challenge of the challenges posed by software evolution is that the activities carried out are often intangible and non-objective \cite{chapin2001types, lientz1980software}.
@@
 We also hope that the approach we used can be used to predict which types of activities should be emphasised in the future evolution of the API.
-With our study we have also demonstrated that the classification of changes is achievable, which, in turn, should encourage the case company adopt this method of classifying change.
+With our study we have also demonstrated that the classification of changes is achievable, which, in turn, should encourage company A to adopt this method of classifying change.
 

### 2015-05-20 thesis/paper.tex
Removed refactoring stuff from intro
review intro
Grammar in intro+moved RQs to meth

@@
 \section{Introduction} \label{introduction}
-%API Design (and a little bit of ecosystems and a bit of problem statement)
+%1API Design (and a little bit of ecosystems and a bit of problem statement)
 As the software industry and the open-source movement continue to grow, the number of public APIs is steadily increasing.
@@
 The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
-Refactoring is the most common change that APIs undergo \cite{dig2005role, xing2006refactoring}.
-%Software Evolution 
+%2Software Evolution 
 In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint.
@@
 
-%Purpose
+%3Purpose
 Modifications to deployed APIs may negatively impact its users.
@@
 
-%Gap in Literature
+%4Gap in Literature
 Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
@@
 
-%Purpose of the study
+%5Purpose of the study
 The goal of the study was twofold.
-Firstly, the aim was to explore what are the driving forces behind API evolution and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes.
+Firstly, the aim was to explore what the driving forces behind API evolution are, and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes.
 With this information, we could determine to what extent these change decisions can be reverse engineered.
-%Why this is important for the case company.
+%6Why this is important for the case company.
 This study has many potential benefits for the case company.
@@
 
-\subsection{Research Questions} \label{rqs}
-\begin{description}
-\item[\textbf{RQ1}] What drives API evolution?
-\item[\textbf{RQ2}] To what extent can we reverse engineer API change decisions?
-\end{description}
+%I would suggest that paragraph #6 is merged with paragraph 3.
+(I.e.
+move #6 in between #3 and #4).
+Otherwise we have a purpose in two places and the most important part of the purpose in the end of the intro, which isn't good.
+
+%The first sentence of paragraph 6 is very subjective and doesn't really add much
+
+%I also think the gap (#4) has to be re-written. Right now it doesn't say much at all. And the 2nd sentence makes no sense at all (2refs="well-explored" and 1ref="few")
+
+%Otherwise really good... like the #6 a lot
 
@@
 The process used for examining the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines, seaman1999qualitative}.
+
+\subsection{Research Questions} \label{rqs}
+\begin{description}
+\item[\textbf{RQ1}] What drives API evolution?
+\item[\textbf{RQ2}] To what extent can we reverse engineer API change decisions?
+\end{description}
 

### 2015-05-20 thesis/paper.tex
Moved RQs to meth+headings disc

@@
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change and that input from the industry is vital to the success of the research, especially to be able to answer \textbf{RQ2}.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of drivers behind API change and that input from the industry is vital to the success of the research.
 
@@
 The process used for examining the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines, seaman1999qualitative}.
+The exploratory analysis lead us to formulate the following research questions.
 
-\subsection{Research Questions} \label{rqs}
 \begin{description}
@@
 In addition to that, strategies from additional well-established papers \cite{andersson2007spiral, seaman1999qualitative, robson2002real} have been used to increase the trustworthiness of the data gathering and data analysis.
-The analysis was based around well-defined theories that are cemented in academia, to further increase the reproducibility of the study.
+The analysis was based around well-defined theories that are cemented in research, to further increase the reproducibility of the study.
 The semi-structured nature of the interview, might threaten the reproducibility; however, large parts of it were structured around existing theories.
@@
 One benefit of having a more structured feedback loop, would be that the API developers would have greater awareness of potential errors in the implementation of the API.
-Another ambition which was mentioned, was to bring scientific theories and best practices from academia into consideration when developing the API.
+Another ambition which was mentioned, was to bring scientific theories and best practices from research into consideration when developing the API.
 This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects.
@@
 
-\subsection{Implications for Academia} 
-The implications of our findings should encourage academia to further study APIs by relating them to existing software evolution theories.
+\subsection{Implications for Research} 
+The implications of our findings should encourage research to further study APIs by relating them to existing software evolution theories.
 Considering that we were able to successfully reverse engineer the changes made to the API in this study, it opens up possibilities to base future research on, for example, the types of software evolution and software maintenance.
@@
 Since only a single API was studied, we cannot safely refute the law or propose a new formulation of it.
-Academia should therefore be wary of assuming that this law is true for APIs.
+Research should therefore be wary of assuming that this law is true for APIs.
 
-\subsection{Implications for Practitioners}
+\subsection{Implications for Company A}
 The changes introduced to the API are mainly based on the expertise and experiences of the API architects at company A.
-There has not been a scientific approach to maintaining the system and the knowledge from academia has not directly affected the way that the API's evolution has been managed.
+There has not been a scientific approach to maintaining the system and the knowledge from research has not directly affected the way that the API's evolution has been managed.
 With our work, we hope to provide further insight into how the API is maintained.

### 2015-05-20 thesis/paper.tex
Added+formatted refs

@@
 We also think that it is interesting to note that a majority of the changes which did not affect functionality, such as the updative changes, were spurred because of previous changes that were related to functionality.
-Following this line of thought, the desire for new functionality can be seen as a catalyst that allows further driving forces to occur (!!!better?).
+Following this line of thought, the desire for new functionality can be seen as a catalyst that allows new change to occur.
 The view of considering functionality to be a major driver for change is supported by the analysis with Lehman's laws.
@@
 
-In relation to this, previous work has identified that refactorings make up a substantial part of the changes APIs undergo (!!!FIND PAPERS TO CITE HERE).
+In relation to this, previous work has identified that refactorings make up a substantial part of the changes APIs undergo \cite{dig2005role, xing2006refactoring, henkel2005catchup, dig2006apis}.
 These results are not in line with ours, since our results show that groomative changes are uncommon and that changes related to quality are not primary drivers of change, rather, they are ripple-effects of changes to functionality \cite{robbes2012developers}.
@@
 Based on our results, we form the conclusion that the desire for functionality and the reluctance of changing are two opposing forces that cause updates to APIs to be infrequent.
-In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which causes the the law of Conservation of Organisational Stability to not apply (!!!
-which means the law of Conservation of Organisational Stability is inappropriate for APIs).
+In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which is the main cause for the law of Conservation of Organisational Stability not applying to APIs.
 This occurring has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}.
@@
 We interpret that the significance of this result suggests that reverse engineering of change decisions can be done in situations where a perfect result is not required.
-In cases where a near-perfect result is enough, we do, however, believe that reverse engineering change decisions is worthwhile (!!!this sentence weird - yeah).
+In cases where a near-perfect result is enough, we do, however, believe that reverse engineering change decisions is worthwhile.
 This line of thought is supported by our results, which, in summary, show that we are able to reverse engineer the most major trends with very high accuracy, but that certain nuances of the changes can be misinterpreted.
@@
 \section{Acknowledgements}
-We would like to thank Axis and that project at GU.
+We would like to thank company A and that project at GU.
 

### 2015-05-20 thesis/paper.tex
Updated introduction

@@
 Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.
+%3 cont.d - Why this is important for the case company.
 
-%4Gap in Literature
-Studies that explore the intent behind API modifications exist \cite{hou2011exploring}.
-The area of programming language APIs is well-explored \cite{hou2011exploring, shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}.
-To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.
-
-%5Purpose of the study
-The goal of the study was twofold.
-Firstly, the aim was to explore what the driving forces behind API evolution are, and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes.
-With this information, we could determine to what extent these change decisions can be reverse engineered.
-%6Why this is important for the case company.
-This study has many potential benefits for the case company.
-Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks.
+Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks for the case company.
 This improved communication could provide a common language that developers, users and management can use to discuss potential evolution of the APIs.
@@
 
-%I would suggest that paragraph #6 is merged with paragraph 3.
-(I.e.
-move #6 in between #3 and #4).
-Otherwise we have a purpose in two places and the most important part of the purpose in the end of the intro, which isn't good.
+%4Gap in Literature
+Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and affects of modifications to APIs \cite{hou2011exploring, shi2011empirical, dig2005role}.
+However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective.
 
-%The first sentence of paragraph 6 is very subjective and doesn't really add much
-
-%I also think the gap (#4) has to be re-written. Right now it doesn't say much at all. And the 2nd sentence makes no sense at all (2refs="well-explored" and 1ref="few")
-
-%Otherwise really good... like the #6 a lot
+%Goal of the study
+The goal of the study was twofold.
+Firstly, the aim was to explore what are the driving forces behind API evolution and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes.
+With this information, we could determine to what extent these change decisions can be reverse engineered.
 

### 2015-05-20 thesis/paper.tex
RQ2 results+table

@@
 \subsection{Reverse Engineering API Change Decisions}
-
 After cross-examining our initial analysis with the interviewee's responses, we found that 85\% of our main type predictions matched the actual motive of the change and that 85\% of our secondary type predictions were correct.
 The kappa value \cite{cohen1968weighted} for the predictions was 0.812, which shows that there is a high level of agreement between the predictions and the change decisions.
+In Table \ref{table:reverse_engineering}, a detailed view of each prediction juxtaposed against the actual change decision can be found for both the main and secondary types.
 
@@
 The changes which had no secondary type were all predicted correctly, which further shows that changes with several types can be diffuse.
+
+\begin{table}
+       \centering
+       \begin{tabular}[ht]{  c | c !{\vrule width 1.5pt} c|c} 
+              \toprule
+
+              \multicolumn{2}{c !{\vrule width 1.5pt} }{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Sub}}        \\ \hline
+
+              \textbf{Prediction}         & \textbf{Actual}            & \textbf{Prediction}       & \textbf{Actual}         \\ \Xhline{2\arrayrulewidth}
+              Enhancive                   & Enhancive                 & N/A                       & N/A                \\ \hline
+              Enhancive                   & Enhancive                 & N/A                       & N/A                \\ \hline
+              Enhancive                   & Enhancive                 & N/A                       & N/A                \\ \hline
+              Enhancive                   & Enhancive                 & N/A                       & N/A                \\ \hline
+              Enhancive                   & Enhancive                 & Groomative                & Groomative         \\ \hline
+              Enhancive                   & Enhancive                 & Groomative                & Groomative         \\ \hline
+              Enhancive                   & Enhancive                 & Groomative                & Groomative         \\ \hline
+              Reductive                   & Reductive                 & N/A                       & N/A                \\ \hline
+              Adaptive                    & Adaptive                  & N/A                       & N/A                \\ \hline
+              Preventive                  & Preventive                & Groomative                & Groomative         \\ \hline 
+              Updative                    & Updative                  & Reformative               & Reformative        \\ \hline
+              Updative                    & Reformative               & Reformative               & Updative           \\ \hline
+              Groomative                  & Preventive                & Preventive                & Groomative         \\
+
+              \bottomrule
+       \end{tabular}
+       \caption{Categorisation of Changes }
+       \label{table:reverse_engineering}
+\end{table}
 

### 2015-05-20 thesis/paper.tex
acks
Sub->secondary
Changes to ack

@@
 
-              \multicolumn{2}{c !{\vrule width 1.5pt} }{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Sub}}        \\ \hline
+              \multicolumn{2}{c !{\vrule width 1.5pt} }{\textbf{Main}}       & \multicolumn{2}{c}{\textbf{Secondary}}        \\ \hline
 
@@
 \section{Acknowledgements}
-We would like to thank company A and that project at GU.
+We would like to thank company A for allowing us to conduct this study in cooperation with them. We would also like to thank associate professor Imed Hammouda for assisting us with this research.
 

### 2015-05-20 thesis/paper.tex
summary concl

@@
               E-Type systems must be continually adapted else they become progressively less satisfactory.                     
-              \item \textbf{Increasing Complexity}\newline 
+              \item \textbf{Increasing Complexity} \newline
               As an E-Type system evolves its complexity increases unless work is done to maintain or reduce it.                  
-              \item \textbf{Self Regulation}\newline 
+              \item \textbf{Self Regulation} \newline
               E-Type system evolution process is self regulation with distribution of product and process measures close to normal.                     
-              \item \textbf{Conservation of Organisational Stability}\newline 
+              \item \textbf{Conservation of Organisational Stability} \newline
               The average effective global rate in an evolving E-Type system is invariant over product lifetime.                     
-              \item \textbf{Conservation of Familiarity}\newline 
+              \item \textbf{Conservation of Familiarity} \newline
               As an E-type system evolves all associated with it, developers, sales, personnel, users, for example, must maintain mastery of its content and behaviour to achieve satisfactory evolution.
@@
 Hence the average incremental growth remains invariant as the system evolves.
-              \item \textbf{Continuing Growth}\newline 
+              \item \textbf{Continuing Growth} \newline
               The functional content of E-Type systems must be continually increased to maintain user satisfaction over their lifetime.                
-              \item \textbf{Declining Quality}\newline 
+              \item \textbf{Declining Quality} \newline
               The quality of E-Type systems will appear to be declining unless they are rigorously maintained and adapted to operational environment changes.                     
-              \item \textbf{Feedback System}\newline 
+              \item \textbf{Feedback System} \newline
               E-Type evolution process constitute multi-level, multi-loop, multi-agent feedback systems and must be treated as such to achieve significant improvement over any reasonable base.
@@
 \section{Conclusion} \label{conclusion}
-ATTN: This section has not been started.
+With this study, we conclude that studying API evolution with help of existing theories, provides a new and structured approach to the field of API evolution.
+Our study shows that functionality is the largest driving force of change in the evolution of APIs.
+It also concludes that APIs do not change invariantly, and that maintenance of an API rather is infrequent and sporadic.
+This finding lead us to invalidate Lehman's law of Conservation of Organisational Stablity in the context of APIs.
 

### 2015-05-20 thesis/paper.tex
Conclusion

@@
 It also concludes that APIs do not change invariantly, and that maintenance of an API rather is infrequent and sporadic.
-This finding lead us to invalidate Lehman's law of Conservation of Organisational Stablity in the context of APIs.
+This finding lead us to invalidate Lehman's law of Conservation of Organisational Stability in the context of APIs.
+With this study we have also identified the importance of having a structured feedback loop when maintaining an API.
+We have also provided company A with a foundation for facilitating such a change.
 
-1. Summary of our results/discussion i.e. short conclusion
+To build on our study, we propose that a study on the eco-system's role in the evolution of APIs is conducted.
+We believe that this area is a major source of improvement for API maintenance, and that exploring the benefits including applications developers and additional entities of the eco-system in the feedback loop is a great place to start (!!!rephrase).
+In such a study, we would suggest that the types of software evolution and software maintenance \cite{chapin2001types} could be used as a mean of facilitating discussion between the entities.
+It could also be possible to study the effect that changes to APIs have on the application code, in such a study.
 
-2. Future work:
-       a) Eco-system (rel. to feedback loop law and Chapin/Swanson communication to stakeholders)
-       b) Business motives instead of evolution theories
-       c) A study which analyses how the API applications change when new versions are introduced (rel. to controlling the behaviour etc.)
+To further investigate what drives API evolution, we believe that API evolution has to be studied from a business point of view.
+We therefore suggest that a similar study is conducted, but with the goal of analysing the change of an API based on business motives.
+Positioning a study around business motives would help identifying the changes before they are formulated into technical changes, and it would provide a new and fresh angle to the field of API evolution.
 
-       In-depth study on the laws or a specific law? Maybe less interesting.
+Lastly, based on our successful attempt to reverse engineer the changes made to this API, we suggest that a quantitative study is conducted to investigate the distribution of the types of software evolution and software maintenance and the applicability of Lehman's laws on a large scale.
 

### 2015-05-20 thesis/paper.tex
reposiitoned tables in bg
Order of refs

@@
 APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
-There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk, mcdonnell2013empirical, robbes2012developers, henning2007api}.
+There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}.
 The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
@@
 %4Gap in Literature
-Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and affects of modifications to APIs \cite{hou2011exploring, shi2011empirical, dig2005role}.
+Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and affects of modifications to APIs \cite{dig2005role, hou2011exploring, shi2011empirical}.
 However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective.
@@
 When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
-One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{stylos2006comparing, shi2011empirical}.
+One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{shi2011empirical, stylos2006comparing}.
 The design decisions reached during development of an API will affect the overall usability of the API.
@@
 The twelve types of software evolution and software maintenance, as seen in Table \ref{table:expl_types}, describe a software evolution activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality.
-
-Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
-They are presented in Table \ref{table:expl_laws}.
-The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
 
@@
 \end{table}
+
+Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
+They are presented in Table \ref{table:expl_laws}.
+The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
 
@@
 The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
-The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, runeson2009guidelines, yin2013case, robson2002real}.
+The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, robson2002real, runeson2009guidelines, yin2013case}.
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
@@
 \textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to an accredited guide to case studies \cite{runeson2009guidelines}.
-In addition to that, strategies from additional well-established papers \cite{andersson2007spiral, seaman1999qualitative, robson2002real} have been used to increase the trustworthiness of the data gathering and data analysis.
+In addition to that, strategies from additional well-established papers \cite{andersson2007spiral, robson2002real, seaman1999qualitative} have been used to increase the trustworthiness of the data gathering and data analysis.
 The analysis was based around well-defined theories that are cemented in research, to further increase the reproducibility of the study.
@@
 %Define
-Evaluative, Consultive and Training are all types of activities, rather than changes that a system can undergo.
+Evaluative, consultive and training are all types of activities, rather than changes that a system can undergo.
 Evaluative activities are defined as activities such as auditing or evaluating the software.
@@
 
-In relation to this, previous work has identified that refactorings make up a substantial part of the changes APIs undergo \cite{dig2005role, xing2006refactoring, henkel2005catchup, dig2006apis}.
+In relation to this, previous work has identified that refactorings make up a substantial part of the changes APIs undergo \cite{dig2005role, dig2006apis, henkel2005catchup, xing2006refactoring}.
 These results are not in line with ours, since our results show that groomative changes are uncommon and that changes related to quality are not primary drivers of change, rather, they are ripple-effects of changes to functionality \cite{robbes2012developers}.

### 2015-05-20 thesis/paper.tex
rough draft of new abstract
Not finished - An

@@
 
-\textbf{Background  } %Give a feeling of the need of this study, answer why the case company needs what is in the Objective (+Context)
-The driving forces of modifications to APIs have been investigated before, however, platform APIs are, until now, unexplored.
+% \textbf{Background  } %Give a feeling of the need of this study, answer why the case company needs what is in the Objective (+Context)
+% The driving forces of modifications to APIs have been investigated before, however, platform APIs are, until now, unexplored.
 Previous studies have not considered APIs from the perspective of well-established software evolution theories.
 
-\smallskip \noindent
-\textbf{Objective  } %Done
-In this study, we explore how companies actively evolve their APIs and 'how APIs evolve from a passive point of view'.
+% \smallskip \noindent
+% \textbf{Objective  } %Done
+% In this study, we explore how companies actively evolve their APIs and 'how APIs evolve from a passive point of view'.
 We also aim to evaluate to what extent we are able to reverse engineer these evolutionary change decisions.
@@
 
-\smallskip \noindent
-\textbf{Method  } %Done
-This case study was conducted by analysing the changes between two versions of a platform API and its documentation.
+% \smallskip \noindent
+% \textbf{Method  } %Done
+% This case study was conducted by analysing the changes between two versions of a platform API and its documentation.
 The results were analysed from a qualitative and investigative perspective, and were then reviewed and validated with the architects of the API.
 
-\smallskip \noindent
-\textbf{Results  } %Done
-We identified thirteen major changes which were introduced in the new version of the API.
+% \smallskip \noindent
+% \textbf{Results  } %Done
+% We identified thirteen major changes which were introduced in the new version of the API.
 We concluded that the dominant driving force of the API evolution is demand for new functionality and that change decisions, to a large extent, are reverse engineerable.
@@
 
-\smallskip \noindent
-\textbf{Conclusion  }
-This study has provided valuable insight into the evolution of platform APIs.
+% \smallskip \noindent
+% \textbf{Conclusion  }
+% This study has provided valuable insight into the evolution of platform APIs.
 The qualitative analysis can help other companies to improve their API maintenance process.
@@
 The investigation of Lehman's laws show that APIs cannot be generalised and be compared to any type of system.
+
+%Background and need for study, make it interesting
+
+%Other studies
+Other studies have investigated why changes occur to APIs and how these changes affect systems, however, they do not attempt to understand the driving forces behind the evolution of the API according to software evolution theories.
+Understanding the driving forces of API evolution can potentially improve API design and aid communication between all aspects of a system's feedback loop.
+% How do we do it?
+Our study utilises a case-study to identify the types of changes that have driven the evolution of an existing API, belonging to a case company. 
+% Our results and future suggestions
+The results of this analysis showed that the largest driving force of API evolution is the desire for new functionality.
+It highlighted the fact that not all software evolution theories are applicable to APIs.
+We found that changes happen sporadically rather than slowly over time and the contradiction of a software evolution law that states the opposite is true.
+The research further supported the importance of a feedback loop of a software system, which is something that company A also wants.
+The study concludes by proposing suggestions for future studies based on our findings.
 

### 2015-05-21 thesis/paper.tex
Updated start of abstract

@@
 %Background and need for study, make it interesting
-
+Evolving a software system is a precipitous activity.
+Many software evolution theories have been created to assist changing systems.
+However, as modern systems are making greater use of APIs, do these software evolution theories apply to them?
 %Other studies
-Other studies have investigated why changes occur to APIs and how these changes affect systems, however, they do not attempt to understand the driving forces behind the evolution of the API according to software evolution theories.
+Other studies have investigated why changes are made to APIs and how these changes affect systems, however, they do not attempt to understand the driving forces behind the evolution of an API according to software evolution theories.
 Understanding the driving forces of API evolution can potentially improve API design and aid communication between all aspects of a system's feedback loop.

### 2015-05-21 thesis/paper.tex
title+author
Another update

--- 2015-05-20 thesis/paper.tex
@@
 
-\title{The Driving Forces Behind API Evolution}
+\title{The Driving Forces of API Evolution}
 
@@
 John Burchell\\
-%       \affaddr{Computer Science and Engineering}\\
+       \affaddr{Computer Science and Engineering}\\
        \affaddr{University of Gothenburg}\\
@@
 William Granli\\
-%       \affaddr{Computer Science and Engineering}\\
+       \affaddr{Computer Science and Engineering}\\
        \affaddr{University of Gothenburg}\\
@@
 %Background and need for study, make it interesting
-
+Evolving a software system is a precipitous activity.
+Many software evolution theories have been created to assist changing systems, however, as modern systems make greater use of APIs, a question must be asked: do these theories apply to the evolution of APIs?
+(!!!what is driving the evolution of APIs?
+- Might fit better with the title?)
 %Other studies
-Other studies have investigated why changes occur to APIs and how these changes affect systems, however, they do not attempt to understand the driving forces behind the evolution of the API according to software evolution theories.
+Studies have investigated why changes are made to APIs and how these changes affect systems, but they do not attempt to understand the driving forces behind the evolution of an API, according to software evolution theories.
 Understanding the driving forces of API evolution can potentially improve API design and aid communication between all aspects of a system's feedback loop.

### 2015-05-21 thesis/paper.tex
Updated abstract

--- 2015-05-20 thesis/paper.tex
@@
 
-% \textbf{Background  } %Give a feeling of the need of this study, answer why the case company needs what is in the Objective (+Context)
-% The driving forces of modifications to APIs have been investigated before, however, platform APIs are, until now, unexplored.
-Previous studies have not considered APIs from the perspective of well-established software evolution theories.
-
-% \smallskip \noindent
-% \textbf{Objective  } %Done
-% In this study, we explore how companies actively evolve their APIs and 'how APIs evolve from a passive point of view'.
-We also aim to evaluate to what extent we are able to reverse engineer these evolutionary change decisions.
-The goal is to study these factors by evaluating them against existing software evolution theories.
-
-% \smallskip \noindent
-% \textbf{Method  } %Done
-% This case study was conducted by analysing the changes between two versions of a platform API and its documentation.
-The results were analysed from a qualitative and investigative perspective, and were then reviewed and validated with the architects of the API.
-
-% \smallskip \noindent
-% \textbf{Results  } %Done
-% We identified thirteen major changes which were introduced in the new version of the API.
-We concluded that the dominant driving force of the API evolution is demand for new functionality and that change decisions, to a large extent, are reverse engineerable.
-We also found that long-established software evolution laws were largely applicable to APIs.
-
-% \smallskip \noindent
-% \textbf{Conclusion  }
-% This study has provided valuable insight into the evolution of platform APIs.
-The qualitative analysis can help other companies to improve their API maintenance process.
-The successful attempt to reverse engineer the change decisions should encourage similar studies to be conducted.
-The investigation of Lehman's laws show that APIs cannot be generalised and be compared to any type of system.
-
-%Background and need for study, make it interesting
-
-%Other studies
-Other studies have investigated why changes occur to APIs and how these changes affect systems, however, they do not attempt to understand the driving forces behind the evolution of the API according to software evolution theories.
+%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+% %Background and need for study, make it interesting
+% Evolving a software system is a precipitous activity.
+Many software evolution theories have been created to assist changing systems.
+However, as modern systems are making greater use of APIs, do these software evolution theories apply to them?
+% %Other studies
+% Other studies have investigated why changes are made to APIs and how these changes affect systems, however, they do not attempt to understand the driving forces behind the evolution of an API according to software evolution theories.
 Understanding the driving forces of API evolution can potentially improve API design and aid communication between all aspects of a system's feedback loop.
-% How do we do it?
-Our study utilises a case-study to identify the types of changes that have driven the evolution of an existing API, belonging to a case company. 
-% Our results and future suggestions
-The results of this analysis showed that the largest driving force of API evolution is the desire for new functionality.
+% % How do we do it?
+% Our study utilises a case-study to identify the types of changes that have driven the evolution of an existing API, belonging to a case company. 
+% % Our results and future suggestions
+% The results of this analysis showed that the largest driving force of API evolution is the desire for new functionality.
 It highlighted the fact that not all software evolution theories are applicable to APIs.
@@
 The study concludes by proposing suggestions for future studies based on our findings.
+%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+
+%What I did: 
+       %Tried to make the motivation/purpose more clear/'''''''crisp''''''''''
+       %Removed the background/other studies stuff. Don't think that's needed in abstract.
+       %Made it a bit more bold/selling
+       %Re-worded the results a bit
+       %Removed the last sentence, don't think we have to mention that we propose future work (since everyone does)
+
+%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+%Motivation/Purpose
+       %Why did you decide to do this study?
+       %Why is this research important?
+       %Why should someone read your entire study?
+Evolving an API is a precipitous activity, mainly because of the great implications modifications to it can have on the users of it.
+As modern systems are making greater use of APIs, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs.
+%Problem Statement
+       %What is your research trying to better understand or solve?
+       %What is the scope of your study - a general problem, or something specific?
+       %What is your main claim or argument?
+If no attempt at analysing or quantifying the evolution of an API is undertaken, there will be a lacking understanding of the evolution, and possible improvements to the maintenance strategy will be difficult to identify.
+We believe, that long-standing software evolution theories can provide additional insight to the field of APIs, and be of great use to companies maintaining APIs.
+%We believe, that by analysing APIs using existing software evolution theories, one can solve this problem. 
+%Method
+In this case study, we conduct a qualitative investigation on what drives the evolution of an industry company's existing API, by examining two versions of the API code.
+The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions were tested by interviewing the designer of the API.
+%Results
+The results of this analysis show that the largest driving force of API evolution is the desire for new functionality.
+Our findings which show that changes happen sporadically, rather than continuously,invalidate a law of software evolution, in the context of APIs.
+We also found that change decisions were highly reverse engineerable, and identified the feedback loop of an API to be the most major area of improvement.
+%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+
+%Stuff that should be improved:
+       %double 'it' in first sentence
+       %Greater use = more ppl use?
+       %does undertaken fit with attempt
+       %It's 239 words now... should try to cut it to 200. (maybe 2nd sentence of method can be removed) (maybe results can be shortened a bit)
 

### 2015-05-21 thesis/paper.tex
Fixed merge and added some changes in results

@@
 %Define how we identified the change type
-Additions or re-implementations of functionality are defined to be enhancive changes. In addition to this, we have included deprecations that have then been re-implemented to also be enhancive.
+Additions or re-implementations of functionality are defined to be enhancive changes. In addition to this, we have included deprecations that have been re-implemented to also be enhancive changes.
 %Some Data and little explanation
@@
 Two examples of added functionality are the addition of camera movement module and an audio analysis module.
-One example of a deprecation that was re-implemented is the event system.
+One example of a deprecation that was re-implemented, is the event system.
 %Conclusion
-Given that over half of the changes were identified to be enhancive, we conclude that the APIs evolution primary type of change was enhancive.
+Given that over half of the changes were identified to be enhancive, we conclude that enhancive types of change are the primary drivers of API evolution.
 
@@
 %Introduction and definition
-Adaptive changes are defined to be changes which involve changes to technology or resources used. 
+Adaptive changes are defined to be changes involving the technologies or resources used by a system. 
 %Data and examples
@@
 Libraries were added for audio and data communication.
-The pre-existing low-level library was further incorporated into whole API.
-(!!!)
+The pre-existing low-level library was further incorporated into the API.
 %Conclusion 
@@
 %Data and examples
-Two changes were identified to be preventive types of change.
-A new error handling system was one of these changes.
+Two changes were identified to be preventive.
+One example is the adoption of a new error handling system.
 Version 2.0 of the API added specific error handling modules and functions which replaced the pre-existing error-handling in v1.4 of the API.
@@
 %Define
-Groomative changes are defined to be changes that aim to immediately make the code more maintainable.
+Groomative changes are defined to be changes that aim to immediately improve maintainability.
 %Data and examples
@@
 This is supported by the characteristic of the changes identified in this study.
-4 of the 13 changes were additions of new modules, and additional functionality was also added to re-implemented modules.
+Four of the thirteen changes were additions of new modules, and additional functionality was also added to re-implemented modules.
 It was also mentioned that the API users had previously requested more frequent updates to the API, despite the drawbacks this could cause.
@@
 The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add modules or new functionality to existing modules were the most common.
-We also think that it is interesting to note that a majority of the changes which did not affect functionality, such as the updative changes, were spurred because of previous changes that were related to functionality.
+We also think that it is interesting to note that a majority of the changes that did not affect functionality, such as the updative changes, were spurred because of previous changes that were related to functionality.
 Following this line of thought, the desire for new functionality can be seen as a catalyst that allows new change to occur.
@@
 With our work, we hope to provide further insight into how the API is maintained.
-Our analysis of the API based on Lehman's laws should further assure that company A is moving the evolution of the API in the right direction.
+Our analysis of the API based on Lehman's laws should further assure company A that they are moving the evolution of the API in the right direction.
 Our research proposes a challenge (!!!reword cuz repeating) for company A in how to tackle challenges related to the law of Conservation of Organisational Stability.

### 2015-05-21 thesis/paper.tex
updated abstract

--- 2015-05-21 thesis/paper.tex
@@
 \begin{abstract}
-
-%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
-% %Background and need for study, make it interesting
-% Evolving a software system is a precipitous activity.
-Many software evolution theories have been created to assist changing systems.
-However, as modern systems are making greater use of APIs, do these software evolution theories apply to them?
-% %Other studies
-% Other studies have investigated why changes are made to APIs and how these changes affect systems, however, they do not attempt to understand the driving forces behind the evolution of an API according to software evolution theories.
-Understanding the driving forces of API evolution can potentially improve API design and aid communication between all aspects of a system's feedback loop.
-% % How do we do it?
-% Our study utilises a case-study to identify the types of changes that have driven the evolution of an existing API, belonging to a case company. 
-% % Our results and future suggestions
-% The results of this analysis showed that the largest driving force of API evolution is the desire for new functionality.
-It highlighted the fact that not all software evolution theories are applicable to APIs.
-We found that changes happen sporadically rather than slowly over time and the contradiction of a software evolution law that states the opposite is true.
-The research further supported the importance of a feedback loop of a software system, which is something that company A also wants.
-The study concludes by proposing suggestions for future studies based on our findings.
-%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
-
-%What I did: 
-       %Tried to make the motivation/purpose more clear/'''''''crisp''''''''''
-       %Removed the background/other studies stuff. Don't think that's needed in abstract.
-       %Made it a bit more bold/selling
-       %Re-worded the results a bit
-       %Removed the last sentence, don't think we have to mention that we propose future work (since everyone does)
-
-%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
-%Motivation/Purpose
-       %Why did you decide to do this study?
-       %Why is this research important?
-       %Why should someone read your entire study?
-Evolving an API is a precipitous activity, mainly because of the great implications modifications to it can have on the users of it.
-As modern systems are making greater use of APIs, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs.
-%Problem Statement
-       %What is your research trying to better understand or solve?
-       %What is the scope of your study - a general problem, or something specific?
-       %What is your main claim or argument?
-If no attempt at analysing or quantifying the evolution of an API is undertaken, there will be a lacking understanding of the evolution, and possible improvements to the maintenance strategy will be difficult to identify.
+%Motivation
+Evolving an API is a precipitous activity, mainly because of the great implications modifications can have on the users of it.
+As the usage of APIs increases, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs.
+%Problem
+If no attempt at analysing or quantifying the evolution of an API is made, there will be a lacking understanding of the evolution, and possible improvements to the maintenance strategy will be difficult to identify.
 We believe, that long-standing software evolution theories can provide additional insight to the field of APIs, and be of great use to companies maintaining APIs.
-%We believe, that by analysing APIs using existing software evolution theories, one can solve this problem. 
 %Method
@@
 The results of this analysis show that the largest driving force of API evolution is the desire for new functionality.
-Our findings which show that changes happen sporadically, rather than continuously,invalidate a law of software evolution, in the context of APIs.
+Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution, in the context of APIs.
 We also found that change decisions were highly reverse engineerable, and identified the feedback loop of an API to be the most major area of improvement.
-%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
-
-%Stuff that should be improved:
-       %double 'it' in first sentence
-       %Greater use = more ppl use?
-       %does undertaken fit with attempt
-       %It's 239 words now... should try to cut it to 200. (maybe 2nd sentence of method can be removed) (maybe results can be shortened a bit)
-
 \end{abstract}

### 2015-05-21 thesis/paper.tex
remove behind + capital laws

@@
 The goal of the study was twofold.
-Firstly, the aim was to explore what are the driving forces behind API evolution and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes.
+Firstly, the aim was to explore what are the driving forces of API evolution and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes.
 With this information, we could determine to what extent these change decisions can be reverse engineered.
@@
 The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring, shi2011empirical} and Smalltalk \cite{robbes2012developers}.
-Attempts to uncover the intents behind the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
+Attempts to uncover the intents of the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
 
@@
 An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of drivers behind API change and that input from the industry is vital to the success of the research.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of drivers of API change and that input from the industry is vital to the success of the research.
 
@@
 A summary of our findings can be seen in Table \ref{table:lehman}.
-The evidence found for the laws of continuing change, self regulation, conservation of familiarity, continuing growth and feedback system mainly relate to enhancive changes that add functionality to the API.
-It was also found that the laws of increasing complexity and declining quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality.
-The only law which was found not to apply to the API analysed in this study was the law of conservation of organisational stability.
+The evidence found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System mainly relate to enhancive changes that add functionality to the API.
+It was also found that the laws of Increasing Complexity and Declining Quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality.
+The only law which was found not to apply to the API analysed in this study was the law of Conservation of Organisational Stability.
 Our results rather show the opposite, that the work rate is variant.
@@
 These applications were fully functional, but there existed no standard method of implementation.
-We therefore conclude that the law of continuing change holds for APIs.
+We therefore conclude that the law of Continuing Change holds for APIs.
 
@@
 Although the importance of reducing the complexity was stated, it was made clear during the interview that one module was not updated between the versions, even though it did not follow the new standards of version 2.0.
-In conclusion, we establish that the law of increasing complexity is true for APIs.
+In conclusion, we establish that the law of Increasing Complexity is true for APIs.
 
@@
 The future updates to the API will also be made incrementally and there will not be a big bang update similar to that of version 2.0.
-This supports that the law of self regulation applies to APIs, assuming that version 2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
+This supports that the law of Self Regulation applies to APIs, assuming that version 2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
 
@@
 The internal development of the API has also been made sporadically and there have been periods where the API has not been actively developed.
-This suggests that the law of conservation of organisational stability does not apply to APIs.
+This suggests that the law of Conservation of Organisational Stability does not apply to APIs.
 
@@
 One example mentioned of how this could be achieved is by improving the expressiveness regarding which API functions are supported on which hardware types.
-These facts support that the law of conservation of familiarity is true for APIs.
+These facts support that the law of Conservation of Familiarity is true for APIs.
 
@@
 Our analysis also shows that changes related to quality are bound to happen, as other types of changes often incorporate quality related aspects.
-We therefore settle that the law of declining quality applies to APIs.
+We therefore settle that the law of Declining Quality applies to APIs.
 
@@
 This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects.
-Based on these factors and clearly expressed ambitions, we conclude that the law of feedback system is true for APIs.
+Based on these factors and clearly expressed ambitions, we conclude that the law of Feedback System is true for APIs.
 
@@
 The changes related to functionality being added, modified (deprecated) or removed were predicted with a 100\% accuracy.
-These changes were deemed the most significant by the interviewee, and it was expressed during the interview that the these types of changes were the main driving factor behind the development of the new version.
+These changes were deemed the most significant by the interviewee, and it was expressed during the interview that the these types of changes were the main driving factor of the development of the new version.
 On the contrary, three out of five changes which were unrelated to functionality were correctly predicted.

### 2015-05-21 thesis/paper.tex
fixed typos in lehman explanation table

@@
               \item \textbf{Self Regulation} \newline
-              E-Type system evolution process is self regulation with distribution of product and process measures close to normal.                     
+              E-Type system evolution process is self regulating with distribution of product and process measures close to normal.                     
               \item \textbf{Conservation of Organisational Stability} \newline
-              The average effective global rate in an evolving E-Type system is invariant over product lifetime.                     
+              The average effective global activity rate in an evolving E-Type system is invariant over product lifetime.                     
               \item \textbf{Conservation of Familiarity} \newline
-              As an E-type system evolves all associated with it, developers, sales, personnel, users, for example, must maintain mastery of its content and behaviour to achieve satisfactory evolution.
+              As an E-type system evolves all associated with it, developers, sales personnel, users, for example, must maintain mastery of its content and behaviour to achieve satisfactory evolution.
 Excessive growth diminishes that mastery.
@@
        \end{tabular}
-       \caption{Explanation of Lehman's Laws}
+       \caption{Lehman's Laws of Software Evolution \cite{lehman90sview}}
        \label{table:expl_laws}

### 2015-05-21 thesis/paper.tex
updated paper structure

@@
 \section{Introduction} \label{introduction}
-%1API Design (and a little bit of ecosystems and a bit of problem statement)
+%API Design background
 As the software industry and the open-source movement continue to grow, the number of public APIs is steadily increasing.
@@
 The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
-%2Software Evolution 
+%Software Evolution background
 In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint.
@@
 
-%3Purpose
+%Purpose, general
 Modifications to deployed APIs may negatively impact its users.
@@
 Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.
-%3 cont.d - Why this is important for the case company.
-
+%Purpose, case company
 Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks for the case company.
@@
 
-%4Gap in Literature
+%Gap in Literature
 Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and affects of modifications to APIs \cite{dig2005role, hou2011exploring, shi2011empirical}.
@@
 
-%Structure of the paper
-The sections following the Introduction are structured as follows: In Section \ref{background}, we present the background and previously published work that is related to our study.
-Section \ref{case_company_description} describes the case company and the API which was studied.
+%Structure of
+The sections following the Introduction are structured as follows: In Section \ref{background}, we present the background and previously published work that is related to our study and introduce the case company and their API.
 A description of our methodology is introduced in Section \ref{methodology}.
-In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the findings of our study.
-In Section \ref{conclusion} we propose the potential impact of our work and give suggestions for future work that builds on our research.
+In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the implications of our work.
+In Section \ref{conclusion} summarise the study and give suggestions for future work that builds on our research.
 

### 2015-05-21 thesis/paper.tex
Added draft of para and added ref in bib

@@
 
+The results also showed that usability was the second-most important driver of API evolution.
+The classified updative, groomative and reformative changes all affected the maintainability and usability of the API and involved activities that have been found to improve the usability and maintainability of an API \cite{afonso2012evaluating, clarke2004measuring,piccioni2013empirical, shi2011empirical}.
+The interviewee discussed how company A wanted to aid developers creating applications by improving the interfaces that the developers are using.
+This improvement to the interfaces would better communicate the design and intentions to the developer.
+Improving the documentation of the API was also important for v2.0, as were improvements to the example code.
+These updates were intended to aid developers and create a set of standards that should be followed when creating applications.
+These changes correspond with three of Lehman's laws: Conservation of Familiarity, Declining Quality and the Feedback Loop.
+
 Our results found that seven out of eight of Lehman's laws do apply to API evolution.

### 2015-05-21 thesis/paper.tex
changed numbers to 123123

@@
 However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective.
+%!!!
+still needs to be improved/increased (consider space re 1st page)
 
@@
 
-%Structure of
+%Structure ofpaper
 The sections following the Introduction are structured as follows: In Section \ref{background}, we present the background and previously published work that is related to our study and introduce the case company and their API.
@@
 \subsection{Case Company Description} \label{case_company_description}
-The case company of this studied will from here on be referred to as \textit{company A}.
+The case company of this study will from here on be referred to as \textit{company A}.
 Company A operates in the domain of video surveillance.

### 2015-05-21 thesis/paper.tex
version->v

@@
 The API analysed in this study is written in the programming language C and has been deployed for several years.
-It was recently updated from version 1.4 to version 2.0, which is the current active version.
+It was recently updated from v1.4 to version 2.0, which is the current active version.
 The changes between these two versions is what has been analysed in this study.
 Between the release of version 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms.
-Prior to version 1.4 being released, updates were only made to include additional built options and did not include any additional functionality.
+Prior to v1.4 being released, updates were only made to include additional built options and did not include any additional functionality.
 The API is used by company partners, which are other companies which develop applications for the cameras.
@@
 %How the initial inspection was performed
-The API code was inspected sequentially, starting with version 1.4.
+The API code was inspected sequentially, starting with v1.4.
 Both versions of the API underwent the same inspection.
@@
 \textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types, lehman90sview}.
-Due to restricted access to company A's source code, we were not able to include versions prior to version 1.4 in our analysis.
+Due to restricted access to company A's source code, we were not able to include versions prior to v1.4 in our analysis.
 This means that the evolution of the API was studied during a rather short period of its lifetime.
@@
 %Data and explanation
-No corrective changes were identified between version 1.4 and version 2.0.
+No corrective changes were identified between v1.4 and version 2.0.
 There are two main reasons that we did not find any changes of this type.
@@
 %Data and Example
-One reformative change was identified between version 1.4 and version 2.0; a redesign of the existing example programs.
+One reformative change was identified between v1.4 and version 2.0; a redesign of the existing example programs.
 The aim of this change was to update the examples to illustrate the new functionality in the API, showing how the modules interact and at the same time, presenting a standard for how to use the API.
@@
 \textbf{Self Regulation  } \label{sec:law3} 
-The release of version 1.4 did not include any changes related to the API interface.
+The release of v1.4 did not include any changes related to the API interface.
 Version 1.0 through to 1.4 strictly added support for additional build target platforms.
@@
 The changes to the API have been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
-As mentioned in Section \ref{sec:law3}, the changes introduced in version 1.4 did not involve any changes to the existing API functions.
+As mentioned in Section \ref{sec:law3}, the changes introduced in v1.4 did not involve any changes to the existing API functions.
 Consequently, the only significant update to the API was made in the transition to version 2.0.
@@
 Large parts of the changes between the versions were strictly additions of new functional content.
-4 new modules were added and significant additions of new functionality were added to the modules which were re-designed from version 1.4.
+4 new modules were added and significant additions of new functionality were added to the modules which were re-designed from v1.4.
 The interviewee also made it clear that increasing the functionality was one of the main goals with the 2.0 update.

### 2015-05-21 thesis/paper.tex
threats

@@
 \smallskip \noindent
-\textbf{Construct validity  } Threats to construct validity have largely been mitigated by structuring the results of the study around already established and accepted software evolution theories \cite{chapin2001types, lehman90sview}.
-Due to restricted access to company A's source code, we were not able to include versions prior to v1.4 in our analysis.
-This means that the evolution of the API was studied during a rather short period of its lifetime.
-It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes.
-We consider these factors to be the remaining threats to construct validity.
+\textbf{Construct validity  } Since our study is largely based on existing theories \cite{chapin2001types, lehman90sview}, the validity of it directly correlates to the validity of the theories and the applicability of them.
 
@@
 \smallskip \noindent
-\textbf{Reliability  } Potential threats to the reliability of our study have, to a great extent, been reduced by conducting the study according to an accredited guide to case studies \cite{runeson2009guidelines}.
+\textbf{Reliability  } Due to restricted access to company A's source code, we were not able to include versions prior to v1.4 in our analysis.
+This means that the evolution of the API was studied during a rather short period of its lifetime.
+It was also not possible to analyse the implementation of the API, something which might have contributed to more accurate predictions of the motives behind the changes.
+We consider these factors to be the remaining threats to reliability.
+Reliability has been increased by conducting the study according to an accredited guide to case studies \cite{runeson2009guidelines}.
 In addition to that, strategies from additional well-established papers \cite{andersson2007spiral, robson2002real, seaman1999qualitative} have been used to increase the trustworthiness of the data gathering and data analysis.
-The analysis was based around well-defined theories that are cemented in research, to further increase the reproducibility of the study.
-The semi-structured nature of the interview, might threaten the reproducibility; however, large parts of it were structured around existing theories.
 

### 2015-05-21 thesis/paper.tex
designer->architect

@@
 In this case study, we conduct a qualitative investigation on what drives the evolution of an industry company's existing API, by examining two versions of the API code.
-The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions were tested by interviewing the designer of the API.
+The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions were tested by interviewing the architect of the API.
 %Results
@@
 It is therefore important to investigate why these changes occur.
-Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs.
+Understanding the motives behind the changes could help API architects to prevent potential future changes to their APIs.
 Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.

### 2015-05-21 thesis/paper.tex
changed comments and minor chanes in other areas

@@
 %Concepts
-Grouping the codes by module allowed us to form general concepts of change. However, changes that affected the whole API were classified on their own. %"that affected the whole API" re-word this
+Grouping the codes by module allowed us to form general concepts of change. However, changes that affected multiple modules were classified on their own.
 %Categories
@@
 The remainder of the changes were defined as general trends.
-These changes were not changes to individual parts of the API, but were instead larger changes that affected the whole API.
+These changes were not changes to individual parts of the API, but were instead broader changes.
 Such examples include a shift towards using interfaces to access features, a different error-handling approach and the inclusion of additional 3\textsuperscript{rd} party libraries.
@@
 Libraries were added for audio and data communication.
-The pre-existing low-level library was further incorporated into whole API.
-(!!!)
+The pre-existing low-level library was incorporated into the API.
 %Conclusion 
@@
 Our analysis of the API based on Lehman's laws should further assure that company A is moving the evolution of the API in the right direction.
-Our research proposes a challenge (!!!reword cuz repeating) for company A in how to tackle challenges related to the law of Conservation of Organisational Stability.
+Our research proposes a dilemma for company A in how to tackle challenges related to the law of Conservation of Organisational Stability.
 Determining if the benefits of continuously and frequently updating the API outweigh the side-effects that these updates could have on the application developers, is something that company A will need to consider.
@@
 To build on our study, we propose that a study on the eco-system's role in the evolution of APIs is conducted.
-We believe that this area is a major source of improvement for API maintenance, and that exploring the benefits including applications developers and additional entities of the eco-system in the feedback loop is a great place to start (!!!rephrase).
+We believe that this area could be a major source of improvement for API evolution.
+Exploring the benefits of including application developers and additional entities of the eco-system in the feedback loop, is a good starting point for company A.
 In such a study, we would suggest that the types of software evolution and software maintenance \cite{chapin2001types} could be used as a mean of facilitating discussion between the entities.

### 2015-05-21 thesis/paper.tex
fixed new ref + minor stuff

@@
 The concept of software maintenance has existed since the 1960s when it was first introduced to the software development community \cite{lientz1980software}.
-A set of four categories describing different types of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}.
+A set of four categories describing different kinds of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}.
 The twelve types of software evolution and software maintenance, as seen in Table \ref{table:expl_types}, describe a software evolution activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality.
@@
        \end{tabular}
-       \caption{Explanation of Types of Software Maintenance}
+       \caption{Types of Software Evolution and Software Maintenance \cite{chapin2001types}}
        \label{table:expl_types}
@@
 The results also showed that usability was the second-most important driver of API evolution.
-The classified updative, groomative and reformative changes all affected the maintainability and usability of the API and involved activities that have been found to improve the usability and maintainability of an API \cite{afonso2012evaluating, clarke2004measuring,piccioni2013empirical, shi2011empirical}.
+The classified updative, groomative and reformative changes all affected the maintainability and usability of the API and involved activities that have been found to improve the usability and maintainability of an API \cite{afonso2012evaluating, clarke2004measuring, piccioni2013empirical, shi2011empirical}.
 The interviewee discussed how company A wanted to aid developers creating applications by improving the interfaces that the developers are using.
@@
 These updates were intended to aid developers and create a set of standards that should be followed when creating applications.
-These changes correspond with three of Lehman's laws: Conservation of Familiarity, Declining Quality and the Feedback Loop.
+These changes correspond with three of Lehman's laws: Conservation of Familiarity, Declining Quality and Feedback Loop.
 

### 2015-05-21 thesis/paper.tex
Updated last comment
improve->increse

@@
 However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective.
-%!!!
-still needs to be improved/increased (consider space re 1st page)
+Our study will fill this gap by analysing an embedded platform API by using software evolution theories and by classifying the types of changes that occur.
+These types will be used in place of quantitative data which will make the results more tangible and will increase their usability.
 

### 2015-05-25 thesis/paper.tex
stuff
Changes based on Imeds feedback.

@@
 %Motivation
-Evolving an API is a precipitous activity, mainly because of the great implications modifications can have on the users of it.
+Evolving an Application Programming Interface (API) is a precipitous activity, mainly because of the great implications modifications can have on the users of it.
 As the usage of APIs increases, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs.
@@
 
+\newpage
 \section{Introduction} \label{introduction}
@@
 Our study will fill this gap by analysing an embedded platform API by using software evolution theories and by classifying the types of changes that occur.
-These types will be used in place of quantitative data which will make the results more tangible and will increase their usability.
 
@@
 
+Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
+They are presented in Table \ref{table:expl_laws}.
+The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
+
 \begin{table}
@@
        \end{tabular}
-       \caption{Types of Software Evolution and Software Maintenance \cite{chapin2001types}}
+       \caption{Types of Software Evolution  \cite{chapin2001types}}
        \label{table:expl_types}
 \end{table}
-
-Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
-They are presented in Table \ref{table:expl_laws}.
-The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
 
@@
 The process followed the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}.
-Each of the previously identified trends were given a main type of maintenance and, if appropriate, a secondary type.
+Each of the previously identified trends were given a main type of change and, if appropriate, a secondary type.
+Main types of change identify the primary motive for a trend, whereas the secondary types are additional motivations for a trend.
+For example, a trend that consisted of adding a new module would be seen as an enhancive type of change with no secondary type of change.
 In addition to this, we analysed the trends based on Lehman's Laws, to determine if they applied to the changes made to the API.

### 2015-05-25 thesis/paper.tex
rel work lehman

@@
 Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
-They are presented in Table \ref{table:expl_laws}.
+The laws are presented in Table \ref{table:expl_laws}.
 The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
+Two other types of systems are also identified; S-type systems and P-type systems.
+S-type systems are programs which are exactly derivable from a specification.
+An example of such a program is one which finds the lowest common denominator for two integers.
+An example of a P-type system is a chess program.
+These types of programs can be derived from a specification, but the rules of the program have to be abstracted.
+In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible.
+Based on this, we consider APIs to be E-type systems, since they they are heavily dependant on the environment and its changes, and since it is not possible to create an exact specificaton of any considerably (!!!) large API.
 
@@
 The analysis of APIs in the context of software evolution has primarily focused on APIs that are part of large programming languages, such as Java \cite{hou2011exploring, shi2011empirical} and Smalltalk \cite{robbes2012developers}.
-Attempts to uncover the intents of the changes made in the AWT and Swing Java libraries have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
+Attempts to uncover the intents of the changes made in the Java libraries, AWT and Swing, have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
 
@@
 It was found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.
-
-%%Possibly add a paragraph here to motivate the gap more
 

### 2015-05-25 thesis/paper.tex
Table of meth

@@
 
+\begin{table}
+       \centering
+       \begin{tabular}[ht]{p{3in}}
+              \toprule
+
+              \begin{enumerate}
+              \item Inspect source code  
+              \item Inspect accompanying documentation 
+              \item Generate Hypotheses 
+              \item Conduct Interview 
+              \item Analyse source code 
+              \item Analyse interviews 
+              \item Classify trends according to types 
+              \item Compare classifications against interview responses 
+              \item Analyse from software evolution theory point of view 
+              \item Validate Hypotheses 
+              \end{enumerate} \\
+              \bottomrule
+       \end{tabular}
+       \caption{Methodology Steps}
+       \label{table:meth_steps}
+\end{table}
+
 \begin{description}
@@
 The module and file in which the change was identified was then logged together with an ID and a description of the change.
-The data collection from code and documentation was performed independently by both John Burchell and William Granli, to reduce the risk of human errors affecting the results.
+The data collection from code and documentation was performed independently by both researchers to reduce the risk of human errors affecting the results.
 If the data collected by each researcher differed, the cause of the discrepancy was investigated and resolved.

### 2015-05-25 thesis/paper.tex
API->apl pr int
review rel work elhamn

@@
 %API Design background
-As the software industry and the open-source movement continue to grow, the number of public APIs is steadily increasing.
+As the software industry and the open-source movement continue to grow, the number of public Application Programming Interfaces (APIs) is steadily increasing.
 APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.
@@
 In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible.
-Based on this, we consider APIs to be E-type systems, since they they are heavily dependant on the environment and its changes, and since it is not possible to create an exact specificaton of any considerably (!!!) large API.
+Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes.
+It is therefore not possible to create an exact specificaton of any non-trivial API.
 

### 2015-05-25 thesis/paper.tex
adssa

@@
 %Codes
-To analyse the data each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
+To analyse the data, each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
 %Concepts
@@
 %RQ1
-The trends identified previously were then classified according to the software maintenance types \cite{chapin2001types}.
-The process followed the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}.
+The trends identified previously were then classified with help of the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}.
 Each of the previously identified trends were given a main type of change and, if appropriate, a secondary type.

### 2015-05-25 thesis/paper.tex
Expanded example of main secondary

@@
 Main types of change identify the primary motive for a trend, whereas the secondary types are additional motivations for a trend.
-For example, a trend that consisted of adding a new module would be seen as an enhancive type of change with no secondary type of change.
+For example, if an identified trend was the re-implementation of an old module that included new functionality and made use of a new interface, it would be classified as mainly enahnacive and secondarily groomative.
 In addition to this, we analysed the trends based on Lehman's Laws, to determine if they applied to the changes made to the API.

### 2015-05-25 thesis/paper.tex
meth table

@@
 
-API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
-Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.
-More trivial design problems, such as assigning names to API features or correctly naming user-defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}.
-When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
-One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{shi2011empirical, stylos2006comparing}.
-The design decisions reached during development of an API will affect the overall usability of the API.
-Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.
-
-\subsection{Software Evolution} \label{software_evolution}
-%%Types of maintenance and types of maintenance
-Software evolution is a field that studies the application of software maintenance activities, changes in software processes and the resulting, evolved versions of the software.
-The concept of software maintenance has existed since the 1960s when it was first introduced to the software development community \cite{lientz1980software}.
-A set of four categories describing different kinds of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}.
-The twelve types of software evolution and software maintenance, as seen in Table \ref{table:expl_types}, describe a software evolution activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality.
-
-Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
-The laws are presented in Table \ref{table:expl_laws}.
-The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
-Two other types of systems are also identified; S-type systems and P-type systems.
-S-type systems are programs which are exactly derivable from a specification.
-An example of such a program is one which finds the lowest common denominator for two integers.
-An example of a P-type system is a chess program.
-These types of programs can be derived from a specification, but the rules of the program have to be abstracted.
-In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible.
-Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes.
-It is therefore not possible to create an exact specificaton of any non-trivial API.
-
 \begin{table}
@@
 
+API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
+Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.
+More trivial design problems, such as assigning names to API features or correctly naming user-defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}.
+When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
+One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{shi2011empirical, stylos2006comparing}.
+The design decisions reached during development of an API will affect the overall usability of the API.
+Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.
+
+\subsection{Software Evolution} \label{software_evolution}
+%%Types of maintenance and types of maintenance
+Software evolution is a field that studies the application of software maintenance activities, changes in software processes and the resulting, evolved versions of the software.
+The concept of software maintenance has existed since the 1960s when it was first introduced to the software development community \cite{lientz1980software}.
+A set of four categories describing different kinds of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}.
+The twelve types of software evolution and software maintenance, as seen in Table \ref{table:expl_types}, describe a software evolution activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality.
+
+Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
+The laws are presented in Table \ref{table:expl_laws}.
+The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
+Two other types of systems are also identified; S-type systems and P-type systems.
+S-type systems are programs which are exactly derivable from a specification.
+An example of such a program is one which finds the lowest common denominator for two integers.
+An example of a P-type system is a chess program.
+These types of programs can be derived from a specification, but the rules of the program have to be abstracted.
+In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible.
+Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes.
+It is therefore not possible to create an exact specificaton of any non-trivial API.
+
 \subsection{API Evolution} \label{related_work}
@@
 \section{Methodology} \label{methodology}
+\begin{table}
+       \centering
+       \begin{tabular}[ht]{p{3in}}
+              \toprule
+
+              \textbf{Phase 1: Generate Hypotheses}
+
+              \begin{enumerate}
+              \item Inspect source code  
+              \item Inspect accompanying documentation 
+              \item Generate Hypotheses 
+              \item Conduct Interview 
+              \item Analyse source code
+              \end{enumerate} \\
+
+              \textbf{Phase 2: Confirm Hypotheses}
+
+              \begin{enumerate}
+              \item Analyse interviews 
+              \item Classify trends according to types 
+              \item Compare classifications against interview responses 
+              \item Analyse from software evolution theory point of view 
+              \item Validate Hypotheses 
+              \end{enumerate} \\
+
+              \bottomrule
+       \end{tabular}
+       \caption{Methodology Steps}
+       \label{table:meth_steps}
+\end{table}
+
+\section{Methodology} \label{methodology}
+\begin{table}
+       \centering
+       \begin{tabular}[ht]{p{3in}}
+              \toprule
+
+              \textbf{Phase 1: Generate Hypotheses}
+
+              \begin{enumerate}
+				\item Inspect 1.4
+				\item Inspect 2.0
+				\item Identify changes between versions
+				\item Conduct interview
+				\item Structure gathered data
+              \end{enumerate} \\
+
+              \textbf{Phase 2: Confirm Hypotheses}
+
+              \begin{enumerate}
+              \item Code changes
+              \item Group changes
+              \item Categorise groups 
+              \item Identify and formulate trends
+              \item Analyse based on types \cite{chapin2001types}
+              \item Analyse based on laws \cite{lehman90sview}
+              \end{enumerate} \\
+
+              \bottomrule
+       \end{tabular}
+       \caption{Methodology Steps}
+       \label{table:meth_steps}
+\end{table}
+
 %Intro and summary
@@
 Both phases were performed iteratively.
-This created the opportunity to improve the data analysis as the study progressed, as well as allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.
+This created the opportunity to improve the data analysis as the study progressed, as well as, allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.
 
@@
 The exploratory analysis lead us to formulate the following research questions.
-
-\begin{table}
-       \centering
-       \begin{tabular}[ht]{p{3in}}
-              \toprule
-
-              \begin{enumerate}
-              \item Inspect source code  
-              \item Inspect accompanying documentation 
-              \item Generate Hypotheses 
-              \item Conduct Interview 
-              \item Analyse source code 
-              \item Analyse interviews 
-              \item Classify trends according to types 
-              \item Compare classifications against interview responses 
-              \item Analyse from software evolution theory point of view 
-              \item Validate Hypotheses 
-              \end{enumerate} \\
-              \bottomrule
-       \end{tabular}
-       \caption{Methodology Steps}
-       \label{table:meth_steps}
-\end{table}
 
@@
 The API code was inspected sequentially, starting with v1.4.
-Both versions of the API underwent the same inspection.
+Both versions of the API underwent the same type of inspection.
 This involved extracting method signatures, enums, structs, typedefs and macros, which were subsequently stored in spreadsheets.

### 2015-05-25 thesis/paper.tex
Smaller changes

@@
 %Motivation
-Evolving an Application Programming Interface (API) is a precipitous activity, mainly because of the great implications modifications can have on the users of it.
-As the usage of APIs increases, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs.
+Evolving an Application Programming Interface (API) is a precipitous activity since(!!!) modifying an API can significantly impact its users.
+As the usage of APIs increases, software development organisations must therefore take an empirical and scientific approach to the way they manage the evolution of their APIs.
 %Problem
@@
 The API is developed for a wide range of camera types that offer different functionality and are used for different purposes.
-
-\section{Methodology} \label{methodology}
-\begin{table}
-       \centering
-       \begin{tabular}[ht]{p{3in}}
-              \toprule
-
-              \textbf{Phase 1: Generate Hypotheses}
-
-              \begin{enumerate}
-              \item Inspect source code  
-              \item Inspect accompanying documentation 
-              \item Generate Hypotheses 
-              \item Conduct Interview 
-              \item Analyse source code
-              \end{enumerate} \\
-
-              \textbf{Phase 2: Confirm Hypotheses}
-
-              \begin{enumerate}
-              \item Analyse interviews 
-              \item Classify trends according to types 
-              \item Compare classifications against interview responses 
-              \item Analyse from software evolution theory point of view 
-              \item Validate Hypotheses 
-              \end{enumerate} \\
-
-              \bottomrule
-       \end{tabular}
-       \caption{Methodology Steps}
-       \label{table:meth_steps}
-\end{table}
 

### 2015-05-25 thesis/paper.tex
meth table
Small changes in meth

@@
 
+API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
+Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.
+More trivial design problems, such as assigning names to API features or correctly naming user-defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}.
+When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
+One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{shi2011empirical, stylos2006comparing}.
+The design decisions reached during development of an API will affect the overall usability of the API.
+Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.
 \begin{table}
        \centering
-       \begin{tabular}[ht]{l|c}
+       \begin{tabular}[Ht*]{l|c}
               \toprule
@@
        \centering
-       \begin{tabular}[ht]{p{3in}}
+       \begin{tabular}[Ht*]{p{3in}}
        \toprule
@@
 \end{table}
-
-API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
-Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.
-More trivial design problems, such as assigning names to API features or correctly naming user-defined types, can have a significant impact on the usability of an API \cite{shi2011empirical}.
-When facing such design challenges, the following four factors are important to consider: a) The API must be understandable through good documentation, b) the API must not be overly abstract, c) the API must be reusable and d) the API must be easy to learn \cite{shi2011empirical}.
-One of the most important qualities in an API is that the intent of the API must be clear to the user \cite{shi2011empirical, stylos2006comparing}.
-The design decisions reached during development of an API will affect the overall usability of the API.
-Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.
 
@@
 
-              \textbf{Phase 1: Generate Hypotheses}
+              \textbf{Phase 1: Data Collection}
 
               \begin{enumerate}
-				\item Inspect 1.4
-				\item Inspect 2.0
+				\item Inspect v1.4
+				\item Inspect v2.0
 				\item Identify changes between versions
@@
 				\item Structure gathered data
+				\item Formulate Hypotheses
               \end{enumerate} \\
 
-              \textbf{Phase 2: Confirm Hypotheses}
+              \textbf{Phase 2: Data Analysis}
 
@@
               \item Analyse based on laws \cite{lehman90sview}
+              \item Validate hypotheses
               \end{enumerate} \\
@@
        \end{tabular}
-       \caption{Methodology Steps}
+       \caption{Methodology Overview}
        \label{table:meth_steps}
@@
 %Intro to code inspection
-The data were collected primarily through inspections of the source code and the analysis of accompanying documentation.
+The data were collected primarily through inspections of the source code and of accompanying documentation.
 The source code was comprised of the two API versions previously mentioned.
@@
 %Purpose of the interview
-After the initial source code inspection and preliminary analysis had been performed, an interview was conducted.
+After the initial source code and documentation inspection, an interview was conducted.
 The main purpose of the interview was to validate our findings from the code inspection with the API architect.
-The interview also served the purpose of providing additional insight into what drove the evolution of the API, by complementing what was found from the code inspection.
+The interview also served the purpose of providing additional insight into what drove the evolution of the API, by complementing what was found from the inspections.
 The final reason for interviewing the API architect was to gather information about the API users and how their decisions, needs and requirements have affected the development of the API.
@@
 The interviewee was encouraged to speak freely, even if it required a change in direction or topic.
-This was allowed in order to fulfil our exploratory goal of the study.
+This was encouraged in order to fulfil our exploratory goal of the study.
 
@@
 In addition to this, we analysed the trends based on Lehman's Laws, to determine if they applied to the changes made to the API.
-This material, as well as the results of the interview, were then used as the basis for answering \textbf{RQ1}.
+This information, as well as the results of the interview, were then used as the basis for answering \textbf{RQ1}.
 

### 2015-05-25 thesis/paper.tex
layout

@@
 \usepackage{url}
+
+\usepackage{placeins}
 
@@
 %Motivation
-Evolving an Application Programming Interface (API) is a precipitous activity since(!!!) modifying an API can significantly impact its users.
+Evolving an Application Programming Interface (API) is a precipitous activity since (!!!) modifying an API can significantly impact its users.
 As the usage of APIs increases, software development organisations must therefore take an empirical and scientific approach to the way they manage the evolution of their APIs.
@@
 \subsection{API Design} \label{api_design}
-
 API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
@@
 Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.
+
+\subsection{Software Evolution} \label{software_evolution}
+%%Types of maintenance and types of maintenance
+Software evolution is a field that studies the application of software maintenance activities, changes in software processes and the resulting, evolved versions of the software.
+The concept of software maintenance has existed since the 1960s when it was first introduced to the software development community \cite{lientz1980software}.
+A set of four categories describing different kinds of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}.
+The twelve types of software evolution and software maintenance, as seen in Table \ref{table:expl_types}, describe a software evolution activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality.
+
 \begin{table}
        \centering
-       \begin{tabular}[Ht*]{l|c}
+       \begin{tabular}[ht]{l|c}
               \toprule
@@
        \centering
-       \begin{tabular}[Ht*]{p{3in}}
+       \begin{tabular}[ht!]{p{3in}}
        \toprule
@@
 \end{table}
-
-\subsection{Software Evolution} \label{software_evolution}
-%%Types of maintenance and types of maintenance
-Software evolution is a field that studies the application of software maintenance activities, changes in software processes and the resulting, evolved versions of the software.
-The concept of software maintenance has existed since the 1960s when it was first introduced to the software development community \cite{lientz1980software}.
-A set of four categories describing different kinds of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}.
-The twelve types of software evolution and software maintenance, as seen in Table \ref{table:expl_types}, describe a software evolution activity that relates to one of three particular areas; the code, the software and the customer-experienced functionality.
-
 Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
@@
 \section{Methodology} \label{methodology}
+
+%Intro and summary
+This study has been conducted using the case study methodology \cite{runeson2009guidelines}.
+Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.
+The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
+The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, robson2002real, runeson2009guidelines, yin2013case}.
+An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
+An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of drivers of API change and that input from the industry is vital to the success of the research.
+
+The study was conducted in two major phases \cite{andersson2007spiral}.
+The aim of the first phase was to generate hypotheses and to formulate clear research questions.
+This was achieved by using a data-driven approach to analysing the code and documentation.
+The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phase.
+Both phases were performed iteratively.
+This created the opportunity to improve the data analysis as the study progressed, as well as, allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.
 \begin{table}
@@
 				\item Structure gathered data
-				\item Formulate Hypotheses
+				\item Formulate hypotheses
               \end{enumerate} \\
@@
 \end{table}
-
-%Intro and summary
-This study has been conducted using the case study methodology \cite{runeson2009guidelines}.
-Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.
-The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
-The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case, robson2002real, runeson2009guidelines, yin2013case}.
-An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}.
-An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of drivers of API change and that input from the industry is vital to the success of the research.
-
-The study was conducted in two major phases \cite{andersson2007spiral}.
-The aim of the first phase was to generate hypotheses and to formulate clear research questions.
-This was achieved by using a data-driven approach to analysing the code and documentation.
-The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phase.
-Both phases were performed iteratively.
-This created the opportunity to improve the data analysis as the study progressed, as well as, allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.
 

### 2015-05-25 thesis/paper.tex
table layout
Small changes to meth, software evolution and abstract

@@
 %Motivation
-Evolving an Application Programming Interface (API) is a precipitous activity since (!!!) modifying an API can significantly impact its users.
-As the usage of APIs increases, software development organisations must therefore take an empirical and scientific approach to the way they manage the evolution of their APIs.
+Evolving an Application Programming Interface (API) is a precipitous activity considering that modifications to an API can significantly impact its users.
+As the usage of APIs increases, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs.
 %Problem
@@
 \subsection{API Design} \label{api_design}
-API design is notoriously difficult, a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
+API design is notoriously difficult; a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
 Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.
@@
        \centering
-       \begin{tabular}[ht!]{p{3in}}
+       \begin{tabular}[ht]{p{3in}}
        \toprule
@@
 Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes.
-It is therefore not possible to create an exact specificaton of any non-trivial API.
+It is therefore not possible to create an exact specification of any non-trivial API.
 

### 2015-05-25 thesis/paper.tex
wording

@@
 %Motivation
-Evolving an Application Programming Interface (API) is a precipitous activity considering that modifications to an API can significantly impact its users.
+Evolving an Application Programming Interface (API) is a precipitous activity considering that, modifications to them can significantly impact their users.
 As the usage of APIs increases, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs.
@@
 \subsection{API Design} \label{api_design}
-API design is notoriously difficult; a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
+API design is notoriously difficult as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
 Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.

### 2015-05-25 thesis/paper.tex
spell

@@
 Main types of change identify the primary motive for a trend, whereas the secondary types are additional motivations for a trend.
-For example, if an identified trend was the re-implementation of an old module that included new functionality and made use of a new interface, it would be classified as mainly enahnacive and secondarily groomative.
+For example, if an identified trend was the re-implementation of an old module that included new functionality and made use of a new interface, it would be classified as mainly enhancive and secondarily groomative.
 In addition to this, we analysed the trends based on Lehman's Laws, to determine if they applied to the changes made to the API.

### 2015-05-25 thesis/paper.tex
Changes to abstract

@@
 %Motivation
-Evolving an Application Programming Interface (API) is a precipitous activity considering that, modifications to them can significantly impact their users.
-As the usage of APIs increases, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs.
+Evolving an Application Programming Interface (API) is a precipitous activity, as modifications to them can significantly impact their users.
+The increasing use of APIs means that software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs.
 %Problem
-If no attempt at analysing or quantifying the evolution of an API is made, there will be a lacking understanding of the evolution, and possible improvements to the maintenance strategy will be difficult to identify.
-We believe, that long-standing software evolution theories can provide additional insight to the field of APIs, and be of great use to companies maintaining APIs.
+If no attempt at analysing or quantifying the evolution of an API is made, there will be a diminished understanding of the evolution, and possible improvements to the maintenance strategy will be difficult to identify.
+We believe that long-standing software evolution theories can provide additional insight to the field of APIs, and can be of great use to companies maintaining APIs.
 %Method
-In this case study, we conduct a qualitative investigation on what drives the evolution of an industry company's existing API, by examining two versions of the API code.
-The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions were tested by interviewing the architect of the API.
+In this case study, we conduct a qualitative investigation to understand what drives the evolution of an industry company's existing API, by examining two versions of the API code.
+The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions was determined by interviewing the architect of the API.
 %Results
 The results of this analysis show that the largest driving force of API evolution is the desire for new functionality.
-Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution, in the context of APIs.
-We also found that change decisions were highly reverse engineerable, and identified the feedback loop of an API to be the most major area of improvement.
+Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution in the context of APIs.
+We also found that change decisions were highly reverse engineerable, and identified that the feedback loop of an API to be the most important area of improvement.
 \end{abstract}

### 2015-05-25 thesis/paper.tex
Changes to final para in abstract

@@
 Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution in the context of APIs.
-We also found that change decisions were highly reverse engineerable, and identified that the feedback loop of an API to be the most important area of improvement.
+We also found that it is possible to reverse engineer change decisions and in doing so, identified that the feedback loop of an API is the most important area of improvement.
 \end{abstract}

### 2015-05-25 thesis/paper.tex
Improved section in introduction - filling the gap

@@
 However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective.
-Our study will fill this gap by analysing an embedded platform API by using software evolution theories and by classifying the types of changes that occur.
+Our study will fill this gap by analysing an embedded platform API, classifying the types of changes that occur and analysing them with the use of software evolution theories.
 

### 2015-05-25 thesis/paper.tex
Changes in introduction, API design background

@@
 There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}.
-The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
+The main reason being that API users are required to update their application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}.
 %Software Evolution background

### 2015-05-25 thesis/paper.tex
added ref to table
widows+orphans
camera rdy

@@
 
+\newpage
 %Structure ofpaper
@@
 The API analysed in this study is written in the programming language C and has been deployed for several years.
-It was recently updated from v1.4 to version 2.0, which is the current active version.
+It was recently updated from v1.4 to v2.0, which is the current active version.
 The changes between these two versions is what has been analysed in this study.
-Between the release of version 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms.
+Between the release of v1.0 and v1.4, no functionality was added, as it only added additional build options for other hardware platforms.
 Prior to v1.4 being released, updates were only made to include additional built options and did not include any additional functionality.
@@
 This created the opportunity to improve the data analysis as the study progressed, as well as, allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.
+An overview of the methodology can be found in Table \ref{table:meth_steps}.
+
 \begin{table}
@@
 \end{description}
+
+\newpage
 
@@
 
+\newpage
 \section{Results} \label{results} 
@@
 %Data and explanation
-No corrective changes were identified between v1.4 and version 2.0.
+No corrective changes were identified between v1.4 and v2.0.
 There are two main reasons that we did not find any changes of this type.
@@
 
+\newpage
 \smallskip \noindent
@@
 A new error handling system was one of these changes.
-Version 2.0 of the API added specific error handling modules and functions which replaced the pre-existing error-handling in v1.4 of the API.
+v2.0 of the API added specific error handling modules and functions which replaced the pre-existing error-handling in v1.4 of the API.
 The redesign of the system to make use of interfaces was also classified as a preventive change.
@@
 %Data and Example
-One reformative change was identified between v1.4 and version 2.0; a redesign of the existing example programs.
+One reformative change was identified between v1.4 and v2.0; a redesign of the existing example programs.
 The aim of this change was to update the examples to illustrate the new functionality in the API, showing how the modules interact and at the same time, presenting a standard for how to use the API.
@@
 \textbf{Continuing Change  } 
-Company A described that including new functional content was one of the top priorities for the release of version 2.0.
+Company A described that including new functional content was one of the top priorities for the release of v2.0.
 This is supported by the characteristic of the changes identified in this study.
@@
 One of the main reasons for continuously adapting the API is also to control the way API users use the API.
-Prior to version 2.0 being released, a number of API users used workarounds to implement applications which contained functionality which was not yet offered from the API.
+Prior to v2.0 being released, a number of API users used workarounds to implement applications which contained functionality which was not yet offered from the API.
 These applications were fully functional, but there existed no standard method of implementation.
@@
 \textbf{Increasing Complexity  } \label{sec:law2} 
-A majority of the changes introduced in version 2.0 aimed to improve the structure and the way that the API was used.
+A majority of the changes introduced in v2.0 aimed to improve the structure and the way that the API was used.
 Many of these changes were related to the same design choices, which enforced a certain implementation style on the whole API.
@@
 The interviewee mentioned that one way of achieving this was to follow guidelines or design best practices, but that company A currently did not make use of these.
-Although the importance of reducing the complexity was stated, it was made clear during the interview that one module was not updated between the versions, even though it did not follow the new standards of version 2.0.
+Although the importance of reducing the complexity was stated, it was made clear during the interview that one module was not updated between the versions, even though it did not follow the new standards of v2.0.
 In conclusion, we establish that the law of Increasing Complexity is true for APIs.
@@
 The release of v1.4 did not include any changes related to the API interface.
-Version 1.0 through to 1.4 strictly added support for additional build target platforms.
-When comparing the changes introduced in version 2.0 to the ones in previous versions, it is clear that the growth of the API has gradually increased.
+v1.0 through to v1.4 strictly added support for additional build target platforms.
+When comparing the changes introduced in v2.0 to the ones in previous versions, it is clear that the growth of the API has gradually increased.
 During the interview it was also mentioned that the future plans for the API did not include any major changes and that only a few minor changes were planned in the near future.
-The future updates to the API will also be made incrementally and there will not be a big bang update similar to that of version 2.0.
-This supports that the law of Self Regulation applies to APIs, assuming that version 2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
+The future updates to the API will also be made incrementally and there will not be a big bang update similar to that of v2.0.
+This supports that the law of Self Regulation applies to APIs, assuming that v2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
 
@@
 \textbf{Conservation of Organisational Stability  } 
-The changes to the API have been made very sporadically, where only two new versions have been released since the deployment of version 1.0.
+The changes to the API have been made very sporadically, where only two new versions have been released since the deployment of v1.0.
 As mentioned in Section \ref{sec:law3}, the changes introduced in v1.4 did not involve any changes to the existing API functions.
-Consequently, the only significant update to the API was made in the transition to version 2.0.
+Consequently, the only significant update to the API was made in the transition to v2.0.
 The internal development of the API has also been made sporadically and there have been periods where the API has not been actively developed.
@@
 \textbf{Conservation of Familiarity  } 
-The documentation that is included with the API was rigorously updated with the introduction of version 2.0.
-All functionality which was added or modified in version 2.0 was updated accordingly in the documentation.
+The documentation that is included with the API was rigorously updated with the introduction of v2.0.
+All functionality which was added or modified in v2.0 was updated accordingly in the documentation.
 The same pattern can be seen for the example code, which went through major changes as a result of the changes to the API code.
@@
 The reasoning for this was to increase the quality, and to be able to deliver content which is useful for the users and which leads to good applications being developed.
-Prior to version 2.0 being released, an example of how the API users were included in the feedback loop was when they implemented functionality related to sound, despite the fact there was no interface for this.
+Prior to v2.0 being released, an example of how the API users were included in the feedback loop was when they implemented functionality related to sound, despite the fact there was no interface for this.
 The experiences of this API user, were later considered when developing the axsound module.
@@
 \end{table}
+
+\newpage
 
@@
 
+\newpage
+
 \subsection{Implications for Company A}
@@
 
-\section{Acknowledgements}
+\section*{Acknowledgements}
 We would like to thank company A for allowing us to conduct this study in cooperation with them. We would also like to thank associate professor Imed Hammouda for assisting us with this research.
+
+\newpage
 

### 2015-05-27 thesis/paper.tex
just kidding
j/k x2
minor changes

@@
 \usepackage{placeins}
-
+\include{macro-edit}
 \begin{document}
@@
 \alignauthor
-John Burchell\\
+John Burchell and William Granli\\
        \affaddr{Computer Science and Engineering}\\
        \affaddr{University of Gothenburg}\\
-       \email{john.a.burchell@gmail.com}
+       \email{john.a.burchell@gmail.com},  \email{william.granli@gmail.com}
 % 2nd. author
-\alignauthor
-William Granli\\
-       \affaddr{Computer Science and Engineering}\\
-       \affaddr{University of Gothenburg}\\
-       \email{william.granli@gmail.com}
+%\alignauthor
+%William Granli\\
+%       \affaddr{Computer Science and Engineering}\\
+%       \affaddr{University of Gothenburg}\\
+%       \email{william.granli@gmail.com}
 %\and
 % 3rd. author
-%\alignauthor Imed Hammouda\titlenote{Co-author}\\
-%       \affaddr{Computer Science and Engineering}\\
-%       \affaddr{University of Gothenburg}\\
-%       \email{imed.hammouda@gu.se}
+\alignauthor Imed Hammouda and Eric Knauss\\
+\affaddr{Computer Science and Engineering}\\
+\affaddr{Chalmers $\mid$ University of Gothenburg}\\
+\email{\{imed.hammouda,eric.knauss\}@cse.gu.se}
 % 4th 
@@
 The results of this analysis show that the largest driving force of API evolution is the desire for new functionality.
-Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution in the context of APIs.
+Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution in the context of APIs \eric{name of the law?}.
 We also found that it is possible to reverse engineer change decisions and in doing so, identified that the feedback loop of an API is the most important area of improvement. 
@@
 %%Small intro to this section. Mention that : In total, thirteen unique changes were found.
-This section will present the results of our study and is structured around the research questions.
+This section \chg{will present}{presents} the results of our study and is structured around the research questions.
 Each section begins with a summary of the results and a subsequent in depth description of the findings.
@@
 %Lehman Intro
-Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight laws \cite{lehman90sview} do apply to APIs.
+Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight laws \ins{of Lehman} \cite{lehman90sview} do apply to APIs. 
 A summary of our findings can be seen in Table \ref{table:lehman}. 
@@
        \end{tabular}
-       \caption{The applicability of Lehman's laws}
+       \caption{The Applicability of Lehman's laws}
        \label{table:lehman}
@@
 
-\newpage
-
 \bibliographystyle{abbrv}

### 2015-05-27 thesis/paper.tex
Applied Eric's changes

@@
 The results of this analysis show that the largest driving force of API evolution is the desire for new functionality.
-Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution in the context of APIs \eric{name of the law?}.
+Our findings which show that changes happen sporadically, rather than continuously, invalidate the law of Conservation of Organisational Stability in the context of APIs.
 We also found that it is possible to reverse engineer change decisions and in doing so, identified that the feedback loop of an API is the most important area of improvement.
@@
 \section{Results} \label{results}
-%%Write new
 
-%%Small intro to this section. Mention that : In total, thirteen unique changes were found.
-This section \chg{will present}{presents} the results of our study and is structured around the research questions.
-Each section begins with a summary of the results and a subsequent in depth description of the findings.
+This section presents the results of our study and is structured around the research questions. Each section begins with a summary of the results and a subsequent in depth description of the findings.
 
@@
 %Lehman Intro
-Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight laws \ins{of Lehman} \cite{lehman90sview} do apply to APIs. 
+Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight of Lehman's laws \cite{lehman90sview} do apply to APIs. 
 A summary of our findings can be seen in Table \ref{table:lehman}. 

### 2015-06-01 thesis/paper.tex
Toned-down findings & clarified API/APIs

@@
 %Results
-The results of this analysis show that the largest driving force of API evolution is the desire for new functionality.
-Our findings which show that changes happen sporadically, rather than continuously, invalidate the law of Conservation of Organisational Stability in the context of APIs.
-We also found that it is possible to reverse engineer change decisions and in doing so, identified that the feedback loop of an API is the most important area of improvement.
+The results of this analysis show that the largest driving force of the APIs evolution was the desire for new functionality.
+Our findings which show that changes happen sporadically, rather than continuously, contradict the law of Conservation of Organisational Stability in the context of APIs.
+We also found that it is possible to reverse engineer change decisions and in doing so, identified that the feedback loop of an API is an important area of improvement.
 \end{abstract}
@@
 
-The study was conducted in two major phases \cite{andersson2007spiral}.
+The study was conducted in two phases.
 The aim of the first phase was to generate hypotheses and to formulate clear research questions.
@@
 
-Our results show that the major driving force for change in APIs is the call for increased functionality.
+Our results show that the major driving force for change the case company's API is the call for increased functionality.
 The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add modules or new functionality to existing modules were the most common.
@@
 
-The results also showed that usability was the second-most important driver of API evolution.
+The results also showed that usability was the second-most important driver of the studied API's evolution.
 The classified updative, groomative and reformative changes all affected the maintainability and usability of the API and involved activities that have been found to improve the usability and maintainability of an API \cite{afonso2012evaluating, clarke2004measuring, piccioni2013empirical, shi2011empirical}.
@@
 
-Our results found that seven out of eight of Lehman's laws do apply to API evolution.
+Our results found that seven out of eight of Lehman's laws do apply to the evolution of the studied API.
 The law of Conservation of Organisational Stability was found not to apply, since changes to APIs are unfavourable due to the potential disruption the applications using the API could face.
@@
 
-Based on our results, we form the conclusion that the desire for functionality and the reluctance of changing are two opposing forces that cause updates to APIs to be infrequent.
-In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which is the main cause for the law of Conservation of Organisational Stability not applying to APIs.
-This occurring has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}.
+Based on our results, we form the conclusion that the desire for functionality and the reluctance of changing are two opposing forces that cause updates to this API to be infrequent.
+In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which is the main indication that the law of Conservation of Organisational Stability is not applicable to APIs.
+This occurrence has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}.
 The underlying reason for this is that the laws are influenced by conscious thought processes, based on human understanding \cite{lehman1980understanding}, which in the case of APIs is the conscious decision to limit updates as much as possible.
@@
 Our results suggest that the opposite of what the law suggests, in its current form, is more applicable for APIs.
-Since only a single API was studied, we cannot safely refute the law or propose a new formulation of it.
-Research should therefore be wary of assuming that this law is true for APIs.
+However, since only a single API was studied, we cannot generalise this finding for all APIs.
+Research should therefore be wary of assuming that this law is true for APIs and future work could be undertaken to fully determine it's validity in regards to APIs.
 
@@
 With this study, we conclude that studying API evolution with help of existing theories, provides a new and structured approach to the field of API evolution.
-Our study shows that functionality is the largest driving force of change in the evolution of APIs.
-It also concludes that APIs do not change invariantly, and that maintenance of an API rather is infrequent and sporadic.
-This finding lead us to invalidate Lehman's law of Conservation of Organisational Stability in the context of APIs.
-With this study we have also identified the importance of having a structured feedback loop when maintaining an API.
+Our study shows that functionality is the largest driving force of change in the evolution of a single API.
+It also concludes that this API did not change invariantly, and that maintenance of an its maintenance was infrequent and sporadic which appears to contradict one of Lehman's law; the law of Conservation of Organisational Stability.
+However, given that this study was on performed on a single API, we cannot generalise this finding.
+Furthermore, we have identified the importance of having a structured feedback loop when maintaining an API.
 We have also provided company A with a foundation for facilitating such a change.
@@
 We therefore suggest that a similar study is conducted, but with the goal of analysing the change of an API based on business motives.
-Positioning a study around business motives would help identifying the changes before they are formulated into technical changes, and it would provide a new and fresh angle to the field of API evolution.
+Positioning a study around business motives would help with identifying the changes before they are formulated into technical changes, and it would provide a new and fresh angle to the field of API evolution.
 

### 2015-06-02 thesis/paper.tex
Changed authors back to two
Added new subsubsections in Background

@@
 \alignauthor
-John Burchell and William Granli\\
+John Burchell\\
        \affaddr{Computer Science and Engineering}\\
        \affaddr{University of Gothenburg}\\
-       \email{john.a.burchell@gmail.com},  \email{william.granli@gmail.com}
+       \email{john.a.burchell@gmail.com}
 % 2nd. author
-%\alignauthor
-%William Granli\\
-%       \affaddr{Computer Science and Engineering}\\
-%       \affaddr{University of Gothenburg}\\
-%       \email{william.granli@gmail.com}
-%\and
-% 3rd. author
-\alignauthor Imed Hammouda and Eric Knauss\\
+\alignauthor
+William Granli\\
        \affaddr{Computer Science and Engineering}\\
-\affaddr{Chalmers $\mid$ University of Gothenburg}\\
-\email{\{imed.hammouda,eric.knauss\}@cse.gu.se}
-% 4th 
-%\alignauthor Eric Knauss\titlenote{Co-author}\\
-%       \affaddr{Computer Science and Engineering}\\
-%       \affaddr{University of Gothenburg}\\
-%       \email{imed.hammouda@gu.se}
+       \affaddr{University of Gothenburg}\\
+       \email{william.granli@gmail.com}
 }
@@
 
+\subsubsection{APIs as Systems}
+Motivate why APIs are systems
+
 \subsection{Software Evolution} \label{software_evolution}
@@
 The concept of software maintenance has existed since the 1960s when it was first introduced to the software development community \cite{lientz1980software}.
+
+\subsubsection{Types of Software Evolution}
 A set of four categories describing different kinds of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}.
@@
 \end{table}
+
+\subsubsection{Lehman’s Laws}
 Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.

### 2015-06-02 thesis/paper.tex
Changes to layout and inclusions to bib

@@
 Motivate why APIs are systems
+\cite{761853,5733835}
 
@@
 
-\subsubsection{Types of Software Evolution}
 A set of four categories describing different kinds of software maintenance \cite{lientz1980software} became the basis upon which twelve new types were developed \cite{chapin2001types}.
@@
 
-\subsubsection{Lehman’s Laws}
 Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
@@
 In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible.
-Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes.
-It is therefore not possible to create an exact specification of any non-trivial API.
 
@@
 Attempts to uncover the intents of the changes made in the Java libraries, AWT and Swing, have also been undertaken \cite{hou2011exploring}, leading to suggestions that the use of a strong architecture is vital for ensuring the successful evolution of an API \cite{hou2011exploring}.
-
 Investigations of three frameworks and one library indicated that 80\% of refactoring changes to APIs negatively affected existing applications \cite{dig2005role}.
@@
 It was found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.
+
+\subsubsection{APIs as E-Type Systems}
+Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes.
+It is therefore not possible to create an exact specification of any non-trivial API.
 

### 2015-06-02 thesis/paper.tex
Notes based on feedback

@@
 
-\subsection{API Design} \label{api_design}
-API design is notoriously difficult as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
+\subsection{APIs} \label{api_design}
+%define what an API is for us
+%we consider APIs to be systems because x y z \cite{761853,5733835} 
+%Introduce different layers of an API.
+%Headers / Interfaces
+%Implementation
+%"Middle Layer"
+
+\subsubsection{API Design}
+API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
 Examples of such design decisions include how to structure an object's constructor parameters or if the API should display errors at compilation or at runtime \cite{stylos2006comparing}.
@@
 Measuring such an effect can be done by investigating the twelve cognitive dimensions that are impacted by interactions between the API and its users \cite{clarke2004measuring}.
-
-\subsubsection{APIs as Systems}
-Motivate why APIs are systems
-\cite{761853,5733835}
 
@@
 In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible.
+%SPE stuff in here.
 
@@
 It was found that 14\% of non-trivial API deprecations caused errors in at least one project, with the worst case of 79 projects being affected \cite{robbes2012developers}.
-
-\subsubsection{APIs as E-Type Systems}
-Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes.
-It is therefore not possible to create an exact specification of any non-trivial API.
 
@@
 The API is developed for a wide range of camera types that offer different functionality and are used for different purposes.
+
+\subsubsection{APIs as E-Type Systems}
+%Specifics about program type etc here
+Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes.
+It is therefore not possible to create an exact specification of any non-trivial API.
 

### 2015-06-02 thesis/paper.tex
Added SPE-prog definitions

@@
 
-Software evolution theory suggests that changes to software must obey one of eight laws \cite{lehman90sview}, known as Lehman's laws.
+Software evolution theory suggests that software programs can be grouped into three different types of systems, namely S-programs, P-programs and E-programs \cite{lehman1980programs}.
+S-programs are programs which are exactly derivable from a specification.
+An example of such a program is one which finds the lowest common denominator for two integers.
+A key characteristic of an S-program is that if its functionality is changed, the end product will be a new product and not an evolved version of the previous program, since the mapping between specification and program is exact.
+P-programs are programs which are inherently more complex, and ``solve a problem which can be precisely formulated, but whose solution must inevitably reflect an approximation of the real world''.
+Furthermore, P-programs are programs which are centered around the perception of users, analysts and/or programmers.
+This perception is often commonly a mathematical model of the problem.
+An example of such a program is a program which predicts weather, since it is derived from a set of hydrodynamic equations.
+E-programs are described as ``inherently even more change prone [than S-programs and P-programs].
+They are programs that mechanize a human or societal activity''.
+These factors can be explained by the difference between P-programs and a E-programs which is that E-programs ``change the very nature of the problem to be solved'' by ``becoming a part of the world it models''.
+Further, a characteristic of E-programs is that, during development, the specification must be developed by involving predictions of the consequences of the deployment of that system will have, since once the program is deployed ``questions of correctness, appropriateness, and satisfaction arise which inevitably leads to additional pressure for change".
+Lehman's eight laws of software evolution are said to apply to such E-programs.
 The laws are presented in Table \ref{table:expl_laws}.
-The laws are said to only apply to E-type systems, which are programs that solve problems or address applications in the real world.
-Two other types of systems are also identified; S-type systems and P-type systems.
-S-type systems are programs which are exactly derivable from a specification.
-An example of such a program is one which finds the lowest common denominator for two integers.
-An example of a P-type system is a chess program.
-These types of programs can be derived from a specification, but the rules of the program have to be abstracted.
-In the case of a chess program, the possible moves have to be abstracted, since exactly specifying all the possible permutations would be virtually impossible.
-%SPE stuff in here.
 

### 2015-06-02 thesis/paper.tex
Small section on APIs

@@
 \subsection{APIs} \label{api_design}
-%define what an API is for us
+%what is an API
+An API offers an interface through which developers can use to access functionality of a system.
+APIs can be seen as having three interacting layers; the interfaces, the implementation and additional functionality.
+Typically, the interfaces provide the definitions of functions and data structures while the implementation realises those interfaces.
+The additional functionality exists as a middle layer that provides things such as error handling, third party libraries and additional auxiliary features.
 %we consider APIs to be systems because x y z \cite{761853,5733835}
+Given that there is a combination of different interacting elements that does not only concern interfaces to implementations, we would argue that an API can be described as a system \cite{761853,5733835}.
 %Introduce different layers of an API.
@@
 P-programs are programs which are inherently more complex, and ``solve a problem which can be precisely formulated, but whose solution must inevitably reflect an approximation of the real world''.
-Furthermore, P-programs are programs which are centered around the perception of users, analysts and/or programmers.
+Furthermore, P-programs are programs which are centred around the perception of users, analysts and/or programmers.
 This perception is often commonly a mathematical model of the problem.

### 2015-06-02 thesis/paper.tex
Few changes

@@
 
-\subsection{APIs} \label{api_design}
+\subsection{APIs} 
 %what is an API
@@
 Typically, the interfaces provide the definitions of functions and data structures while the implementation realises those interfaces.
-The additional functionality exists as a middle layer that provides things such as error handling, third party libraries and additional auxiliary features.
+The additional functionality exists as a middle layer that provides utilities such as error handling, third party libraries and additional auxiliary features.
 %we consider APIs to be systems because x y z \cite{761853,5733835}
@@
 
-\subsubsection{API Design}
+\subsubsection{API Design} \label{api_design}
 API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
@@
 P-programs are programs which are inherently more complex, and ``solve a problem which can be precisely formulated, but whose solution must inevitably reflect an approximation of the real world''.
-Furthermore, P-programs are programs which are centred around the perception of users, analysts and/or programmers.
+Furthermore, P-programs are programs which are centred around the perception of users, analysts or programmers.
 This perception is often commonly a mathematical model of the problem.

### 2015-06-02 thesis/paper.tex
review johns

@@
 %what is an API
-An API offers an interface through which developers can use to access functionality of a system.
-APIs can be seen as having three interacting layers; the interfaces, the implementation and additional functionality.
+An API offers an interface through which developers can access programmatic functionality.
+APIs can be seen as having three interacting layers; the public interface, the actual implementation of the functionality and an intersecting layer which provides utilities such as error handling, third party libraries and additional auxiliary features.
 Typically, the interfaces provide the definitions of functions and data structures while the implementation realises those interfaces.
-The additional functionality exists as a middle layer that provides utilities such as error handling, third party libraries and additional auxiliary features.
 %we consider APIs to be systems because x y z \cite{761853,5733835}
-Given that there is a combination of different interacting elements that does not only concern interfaces to implementations, we would argue that an API can be described as a system \cite{761853,5733835}.
+Given that there is a combination of different interacting elements that do not only concern interfaces to implementations, we would argue that an API can be described as a system \cite{761853,5733835}.
 %Introduce different layers of an API.

### 2015-06-02 thesis/paper.tex
Minor changes

@@
 
-\subsection{APIs} 
+\subsection{APIs} \label{api_design}
 %what is an API
@@
 Typically, the interfaces provide the definitions of functions and data structures while the implementation realises those interfaces.
-%we consider APIs to be systems because x y z \cite{761853,5733835}
-Given that there is a combination of different interacting elements that do not only concern interfaces to implementations, we would argue that an API can be described as a system \cite{761853,5733835}.
-%Introduce different layers of an API.
-%Headers / Interfaces
-%Implementation
-%"Middle Layer"
 
-\subsubsection{API Design} \label{api_design}
 API design is notoriously difficult, as a myriad of design and performance decisions must be taken into consideration when creating APIs \cite{afonso2012evaluating, bloch2008effective, stylos2006comparing}.
@@
 It was recently updated from v1.4 to v2.0, which is the current active version.
-The changes between these two versions is what has been analysed in this study.
+The changes between these two versions are what has been analysed in this study.
 Between the release of v1.0 and v1.4, no functionality was added, as it only added additional build options for other hardware platforms.
@@
 The API is developed for a wide range of camera types that offer different functionality and are used for different purposes.
+
+% Given that there is a combination of different interacting elements that do not only concern interfaces to implementations, we would argue that an API can be described as a system \cite{761853,5733835}.
 

### 2015-06-02 thesis/paper.tex
case company descr

@@
 Between the release of v1.0 and v1.4, no functionality was added, as it only added additional build options for other hardware platforms.
-Prior to v1.4 being released, updates were only made to include additional built options and did not include any additional functionality.
-The API is used by company partners, which are other companies which develop applications for the cameras.
+Prior to v1.4 being released, updates were only made to include additional build options and did not include any additional functionality.
+The API is used by company partners, which are other companies developing applications for the cameras.
 These applications are, in turn, used by the end-users of the cameras.
-The API is developed for a wide range of camera types that offer different functionality and are used for different purposes.
+The API is compatible with a wide range of camera types that offer different functionality and are used for different purposes.
 
@@
 
-\subsubsection{APIs as E-Type Systems}
+\subsubsection{APIs as Systems}
+1. Clear up how "complex" API is. Explain error handling, 3rd party libs.
+2. Explain that our study strictly includes the interface and middle-layer parts (don't refer to it as middle-layer)
+3. Also explain that the documentation (SDK) and example code were studied
+4. We consider these "artefacts" as the system of our study
+...transition...
+1. Defnition of system
+2. Relate to previously made points
+...transition...
+1. Refer back to background (e-type)
+2. Make the case for why our API is an e-program
+
 %Specifics about program type etc here

### 2015-06-03 thesis/paper.tex
APIs as Systems
Drafted first two sections of this subsubsection

@@
 \subsubsection{APIs as Systems}
-1. Clear up how "complex" API is. Explain error handling, 3rd party libs.
-2. Explain that our study strictly includes the interface and middle-layer parts (don't refer to it as middle-layer)
-3. Also explain that the documentation (SDK) and example code were studied
-4. We consider these "artefacts" as the system of our study
-...transition...
-1. Defnition of system
-2. Relate to previously made points
-...transition...
-1. Refer back to background (e-type)
-2. Make the case for why our API is an e-program
+% 1. Clear up how "complex" API is. Explain error handling, 3rd party libs.
+% 2. Explain that our study strictly includes the interface and middle-layer parts (don't refer to it as middle-layer)
+% 3. Also explain that the documentation (SDK) and example code were studied
+% 4. We consider these "artefacts" as the system of our study
+% ...transition...
+The case company's API is a complex API.
+When studying the API, we have focused on the interfaces and the intersecting layer of the API.
+(!!!
+expand?).
+Given that the implementation of the API is usually hidden and irrelevant from the users perspective, we will not be inspecting it for changes.
+We are also inspecting the entire SDK which was made available to us by company A.
+The SDK includes artefacts such as the API documentation, user manuals and other miscellaneous documentation.
+We therefore believe that the use of third party libraries, error handling, daemons and an extensive interconnected API, combined with an extensive SDK, indicates to us that this API can be considered as a system.
+% 1. Definition of system
+% 2. Relate to previously made points
+% ...transition...
+The IEEE defines a system to be ``A combination of interacting elements organised to achieve one or more stated purposes...Organised to accomplish a specific function or set of functions within a specific environment".
+The combination of the interacting parts of the API, coupled with the specific nature of the problem the API is addressing and the fact that this API is developed for embedded systems, allows us to argue that this definition accurately supports our intent to classify this API as a system.
+
+% 1. Refer back to background (e-type)
+% 2. Make the case for why our API is an e-program
 

### 2015-06-03 thesis/paper.tex
l

--- 2015-06-02 thesis/paper.tex
@@
 \subsubsection{APIs as Systems}
-1. Clear up how "complex" API is. Explain error handling, 3rd party libs.
-2. Explain that our study strictly includes the interface and middle-layer parts (don't refer to it as middle-layer)
-3. Also explain that the documentation (SDK) and example code were studied
-4. We consider these "artefacts" as the system of our study
-...transition...
-1. Defnition of system
-2. Relate to previously made points
-...transition...
-1. Refer back to background (e-type)
-2. Make the case for why our API is an e-program
+The API is rather complex, and in addition to the API interface and implementation code, it includes a middle-layer which manages error handling and the access to various 3\textsuperscript{rd} party libraries.
+In this study, we use the API interface and the middle-layers as units of analysis.
+Examples of where the responsibilites exceed those of a primitive API interface is that it includes functionality such as error handling and a daemon which facilitates communication between hardware entities.
+In addition to that, the SDK which includes the API documentation, user manuals and example applications that utilise the API code.
+Based on these characteristics and the IEEE definition of a system, which reads as follows; ``A combination of interacting elements organised to achieve one or more stated purposes...
+Organised to accomplish a specific function or set of functions within a specific environment", we consider the API to be a system because of the combination of the interacting parts of the API, coupled with the specific nature of the problem the API is addressing.
+
+% 1. Refer back to background (e-type)
+% 2. Make the case for why our API is an e-program
 

### 2015-06-03 thesis/paper.tex
Further softened claims

@@
 In this case study, we conduct a qualitative investigation to understand what drives the evolution of an industry company's existing API, by examining two versions of the API code.
-The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions was determined by interviewing the architect of the API.
+The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions was determined by interviewing an architect of the API.
 %Results
 The results of this analysis show that the largest driving force of the APIs evolution was the desire for new functionality.
-Our findings which show that changes happen sporadically, rather than continuously, contradict the law of Conservation of Organisational Stability in the context of APIs.
+Our findings which show that changes happen sporadically, rather than continuously, appear to contradict the law of Conservation of Organisational Stability in the context of APIs.
 We also found that it is possible to reverse engineer change decisions and in doing so, identified that the feedback loop of an API is an important area of improvement.
@@
 Following this section, we will discuss the results related to each type of change category, discussing the results for each of them with examples from the changes identified between the two versions of the API.
-Subsequently, each of Lehman's laws will be discussed and our results will be presented showing if the laws apply to APIs or not.
+Subsequently, each of Lehman's laws will be discussed and our results will be presented showing if the laws apply to the API or not.
 
@@
 %Conclusion
-This therefore leads us to conclude that API evolution is not driven by performance changes.
+This therefore leads us to conclude that the API's evolution is not driven by performance changes.
 
@@
 %Concusion
-Preventive types of change appear to drive the evolution of an API more strongly than other types of change.
+Preventive types of change appear to drive the evolution this API more strongly than other types of change.
 This could be due to the fact that as the API grows, the need for higher maintenance also increase, a fact that also seems to be supported by Lehman's laws.
@@
 %Conclusion
-While not a primary factor for any of the changes, groomative types of change should still be viewed as important for API evolution.
+While not a primary factor for any of the changes, groomative types of change should still be viewed as important to the API's evolution.
 
@@
 Changes to the API cause the need for updative changes to its documentation, without them, the usability of the API could suffer.
-We therefore conclude that the evolution of an API is not driven by updative changes.
+We therefore conclude that the evolution of this API was not driven by updative changes.
 
@@
 %Conclusion
-We therefore conclude that reformative changes, while important for the usability of the API, do not drive the evolution of the API.
+We therefore conclude that reformative changes, while important for the usability of the API, they did not drive the evolution of the API.
 
@@
 %Conclusion
-We can therefore conclude that these change types are not important for API evolution.
+We can therefore conclude that these change types were unimportant for the evolution of the API.
 
@@
 These applications were fully functional, but there existed no standard method of implementation.
-We therefore conclude that the law of Continuing Change holds for APIs.
+We therefore conclude that the law of Continuing Change was a driving factor for this API.
 
@@
 Although the importance of reducing the complexity was stated, it was made clear during the interview that one module was not updated between the versions, even though it did not follow the new standards of v2.0.
-In conclusion, we establish that the law of Increasing Complexity is true for APIs.
+In conclusion, we establish that the law of Increasing Complexity was a driving factor for this API.
 
@@
 The future updates to the API will also be made incrementally and there will not be a big bang update similar to that of v2.0.
-This supports that the law of Self Regulation applies to APIs, assuming that v2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
+This supports that the law of Self Regulation applies was a driving force of the API's evolution, assuming that v2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
 
@@
 The internal development of the API has also been made sporadically and there have been periods where the API has not been actively developed.
-This suggests that the law of Conservation of Organisational Stability does not apply to APIs.
+This suggests that the law of Conservation of Organisational Stability did not drive the evolution of the API.
 
@@
 One example mentioned of how this could be achieved is by improving the expressiveness regarding which API functions are supported on which hardware types.
-These facts support that the law of Conservation of Familiarity is true for APIs.
+These facts support that the law of Conservation of Familiarity was a driving force for the evolution of the API.
 
@@
 It was also mentioned that company A had received feedback from the API users that more frequent updates to the functional content was desirable, even though this may require them to update their application code.
-We therefore conclude that the law of continuing growth applies to APIs.
+We therefore conclude that the law of continuing growth was a driving force for the evolution of the API.
 
@@
 Our analysis also shows that changes related to quality are bound to happen, as other types of changes often incorporate quality related aspects.
-We therefore settle that the law of Declining Quality applies to APIs.
+We therefore settle that the law of Declining Quality was a driving force for the evolution of the API.
 
@@
 This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects.
-Based on these factors and clearly expressed ambitions, we conclude that the law of Feedback System is true for APIs.
+Based on these factors and clearly expressed ambitions, we conclude that the law of Feedback System was a driving force for the evolution of the API.
 
@@
 With this study, we conclude that studying API evolution with help of existing theories, provides a new and structured approach to the field of API evolution.
-Our study shows that functionality is the largest driving force of change in the evolution of a single API.
-It also concludes that this API did not change invariantly, and that maintenance of an its maintenance was infrequent and sporadic which appears to contradict one of Lehman's law; the law of Conservation of Organisational Stability.
+Our study shows that functionality is the largest driving force of change in the evolution of the studied API.
+It also concludes that this API did not change invariantly, and that its maintenance was infrequent and sporadic which appears to contradict one of Lehman's law; the law of Conservation of Organisational Stability.
 However, given that this study was on performed on a single API, we cannot generalise this finding.

### 2015-06-03 thesis/paper.tex
etype motivation

@@
 An example of such a program is one which finds the lowest common denominator for two integers.
-A key characteristic of an S-program is that if its functionality is changed, the end product will be a new product and not an evolved version of the previous program, since the mapping between specification and program is exact.
+A key characteristic of an S-program is that if its functionality is changed, the end product will be a new program and not an evolved version of the previous program, since the mapping between specification and program is exact.
 P-programs are programs which are inherently more complex, and ``solve a problem which can be precisely formulated, but whose solution must inevitably reflect an approximation of the real world''.
@@
 
-% Given that there is a combination of different interacting elements that do not only concern interfaces to implementations, we would argue that an API can be described as a system \cite{761853,5733835}.
-
 \subsubsection{APIs as Systems}
@@
 In addition to that, the SDK which includes the API documentation, user manuals and example applications that utilise the API code.
-Based on these characteristics and the IEEE definition of a system, which reads as follows; ``A combination of interacting elements organised to achieve one or more stated purposes...
-Organised to accomplish a specific function or set of functions within a specific environment", we consider the API to be a system because of the combination of the interacting parts of the API, coupled with the specific nature of the problem the API is addressing.
+Based on these characteristics and the IEEE definition of a system, which reads as follows; ``A combination of interacting elements organised to achieve one or more stated purposes...Organised to accomplish a specific function or set of functions within a specific environment" \cite{5733835 }, we consider the API to be a system because of the combination of the interacting parts of the API, coupled with the specific nature of the problem the API is addressing.
 
-% 1. Refer back to background (e-type)
-% 2. Make the case for why our API is an e-program
-
-%Specifics about program type etc here
-Based on this, we consider APIs to be E-type systems, since they are heavily dependant on the environment and its changes. 
-It is therefore not possible to create an exact specification of any non-trivial API.
+Building on this, we regard the API examined in this study to be an E-type system based on that it is a part of the world it models.
+This is evident from that it is a vital part of the cameras' and the only option for developing software for the cameras.
+The API is also by company A considered to be a vital part of the cameras' software ecosystem.
+This factor also corresponds with the characteristic of E-type systems which relates to the system being susceptible to change from pressure that occurs after the system has been deployed.
+Similarly, we do not consider the API to be a P-type system, based on that the system is virtually impossible to model because of its high dependenace with the environment it operates in.
 
 \section{Methodology} \label{methodology}
-
-%Intro and summary
 This study has been conducted using the case study methodology \cite{runeson2009guidelines}.

### 2015-06-03 thesis/paper.tex
validity

@@
 \textbf{Construct validity  } Since our study is largely based on existing theories \cite{chapin2001types, lehman90sview}, the validity of it directly correlates to the validity of the theories and the applicability of them.
+With regards to Lehman's laws of software evolution, the laws are said to only apply to E-type systems.
+According to our analysis, we consider the API to be of the E-type, but our interpretations of Lehman's definitions are incorrect, it could be considered a threat to the construct of our study.
 
@@
 \smallskip \noindent
-\textbf{External validity  } The results of our study should be highly generalisable to similar studies conducted on any type of APIs, since the evolution of the API has largely been driven by software-related factors.
-Our study can especially be compared to similar studies conducted on platform or embedded APIs.
-Further comparability to our study is offered through how the results are structured around established software evolution theories.
+\textbf{External validity  } Since only two versions of the API were analysed, we cannot claim any generalisability for our study.
+We do, however, believe that our study can offer comparability for companies that chose to do a similar analysis on their API.
 

### 2015-06-03 thesis/paper.tex
Smaller changes to language

@@
 The results of this analysis show that the largest driving force of the APIs evolution was the desire for new functionality.
-Our findings which show that changes happen sporadically, rather than continuously, appear to contradict the law of Conservation of Organisational Stability in the context of APIs.
+Our findings which show that changes happen sporadically, rather than continuously, appear to show that the law of Conservation of Organisational Stability was not a considerable factor for the evolution of the API.
 We also found that it is possible to reverse engineer change decisions and in doing so, identified that the feedback loop of an API is an important area of improvement.
@@
 %Lehman Intro
-Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight of Lehman's laws \cite{lehman90sview} do apply to APIs. 
+Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight of Lehman's laws \cite{lehman90sview} are present in the API. 
 A summary of our findings can be seen in Table \ref{table:lehman}. 
@@
 It was also found that the laws of Increasing Complexity and Declining Quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality.
-The only law which was found not to apply to the API analysed in this study was the law of Conservation of Organisational Stability.
+The only law which was found to have little effect in the evolution of the API analysed in this study was the law of Conservation of Organisational Stability.
 Our results rather show the opposite, that the work rate is variant.
@@
 Following this section, we will discuss the results related to each type of change category, discussing the results for each of them with examples from the changes identified between the two versions of the API.
-Subsequently, each of Lehman's laws will be discussed and our results will be presented showing if the laws apply to the API or not.
+Subsequently, each of Lehman's laws will be discussed and our results will be presented showing if the laws were observed.
 
@@
 The future updates to the API will also be made incrementally and there will not be a big bang update similar to that of v2.0.
-This supports that the law of Self Regulation applies was a driving force of the API's evolution, assuming that v2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
+This supports that the law of Self Regulation was observed in the API's evolution, assuming that v2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
 
@@
 The internal development of the API has also been made sporadically and there have been periods where the API has not been actively developed.
-This suggests that the law of Conservation of Organisational Stability did not drive the evolution of the API.
+This suggests that the law of Conservation of Organisational Stability was not a considerable factor in the evolution of the API.
 
@@
 Our study shows that functionality is the largest driving force of change in the evolution of the studied API.
-It also concludes that this API did not change invariantly, and that its maintenance was infrequent and sporadic which appears to contradict one of Lehman's law; the law of Conservation of Organisational Stability.
+It also concludes that this API did not change invariantly, and that its maintenance was infrequent and sporadic.
+This seems to indicate that the law of Conservation of Organisational Stability was not held in the evolution of this API.
 However, given that this study was on performed on a single API, we cannot generalise this finding.

### 2015-06-03 thesis/paper.tex
removed newpages
review first half

@@
 \newpage
+
 \section{Introduction} \label{introduction}
@@
 In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the implications of our work.
-In Section \ref{conclusion} summarise the study and give suggestions for future work that builds on our research.
+In Section \ref{conclusion} we summarise the study and give suggestions for future work that builds on our research.
 
 \section{Background} \label{background}
-This section will introduce the fields of API design, software evolution and it will provide a review of studies that are related to our study.
+This section will introduce the fields of APIs, software evolution and it will provide a review of studies that are related to our study.
 The subsequent section will introduce the case company with a description of the API used in this study.
@@
 
+\newpage
+
 Software evolution theory suggests that software programs can be grouped into three different types of systems, namely S-programs, P-programs and E-programs \cite{lehman1980programs}.
@@
 
+\newpage
+
 The study was conducted in two phases.
@@
 
-\newpage
-
 \subsection{Data Collection} \label{data_collection}  
@@
 
+\newpage
 %RQ2
@@
 
-\newpage
 \section{Results} \label{results}
@@
 
-%Lehman Intro
-Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight of Lehman's laws \cite{lehman90sview} are present in the API. 
-A summary of our findings can be seen in Table \ref{table:lehman}. 
-The evidence found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System mainly relate to enhancive changes that add functionality to the API.
-It was also found that the laws of Increasing Complexity and Declining Quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality.
-The only law which was found to have little effect in the evolution of the API analysed in this study was the law of Conservation of Organisational Stability.
-Our results rather show the opposite, that the work rate is variant.
-
 %Lehman Table
@@
 \end{table}
+
+\newpage
+
+%Lehman Intro
+Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight of Lehman's laws \cite{lehman90sview} are present in the API. 
+A summary of our findings can be seen in Table \ref{table:lehman}. 
+The evidence found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System mainly relate to enhancive changes that add functionality to the API.
+It was also found that the laws of Increasing Complexity and Declining Quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality.
+The only law which was found to have little effect in the evolution of the API analysed in this study was the law of Conservation of Organisational Stability.
 
@@
 
-\newpage
 \smallskip \noindent
@@
 
-\newpage
-
 \subsection{Implications for Company A}

### 2015-06-03 thesis/paper.tex
Many small changes from section 4.1.1

@@
 The majority of which were additions of new functionality to the API.
-Two examples of added functionality are the addition of camera movement module and an audio analysis module.
+Two examples of added functionality are the additions of a camera movement module and an audio analysis module.
 One example of a deprecation that was re-implemented is the event system.
@@
 This meant that most of the existing code was either removed, replaced or deprecated, resulting in little to no obvious fixes.
-Secondly, we only had access to the public facing API and not the implementation itself.
-We therefore could not inspect the inner workings of the functionality that has remained between versions to determine if any corrective change took place.
+Secondly, we only inspected public facing API and not the implementation itself.
 %Conclusion
@@
 This reductive change removed functionality that provided the ability to buffer individual images for closer analysis by a user.
-Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role, xing2006refactoring}.
-It was revealed during the interview that the functionality was removed because the company A no longer wished to support this feature.
+Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role, xing2006refactoring}, this result was not surprising.
+It was revealed during the interview that the functionality was removed because company A no longer wished to support this feature.
 %Conclusion
@@
 A single change was identified as being adaptive; the inclusion of new 3\textsuperscript{rd} party libraries.
-Libraries were added for audio and data communication.
-The pre-existing low-level library was incorporated into the API.
+Libraries were added for audio and data communication with the pre-existing low-level library being incorporated into the API.
 %Conclusion 
@@
 %Data and examples
-While none of the change identified were primarily groomative changes, three of them were secondarily classified as being groomative.
+While none of the changes identified were primarily groomative changes, three of them were secondarily classified as being groomative.
 This indicates that the groomative nature of a change is often a positive affect of other types of change.
@@
 %Conclusion
-We therefore conclude that reformative changes, while important for the usability of the API, they did not drive the evolution of the API.
+We therefore conclude that reformative changes, while important for the usability of the API, did not drive the evolution of the API.
 
@@
 %Data and example
-None of the aforementioned activities occurred as part of the APIs evolution as these activities do not play a role in API evolution.
-This is supported by the fact none of the activities were identified for the changes.
+None of the aforementioned activities occurred as part of the APIs evolution.
 %Conclusion
@@
 One of the main reasons for continuously adapting the API is also to control the way API users use the API.
-Prior to v2.0 being released, a number of API users used workarounds to implement applications which contained functionality which was not yet offered from the API.
+Prior to v2.0 being released, a number of API users used workarounds to implement applications which contained functionality that was not yet offered by the API.
 These applications were fully functional, but there existed no standard method of implementation.
@@
 The future updates to the API will also be made incrementally and there will not be a big bang update similar to that of v2.0.
-This supports that the law of Self Regulation was observed in the API's evolution, assuming that v2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
+This supports that the law of Self Regulation was significant in the API's evolution, assuming that v2.0 can be considered to be the peak of the normal distribution curve of the APIs growth.
 
@@
 One example mentioned of how this could be achieved is by improving the expressiveness regarding which API functions are supported on which hardware types.
-These facts support that the law of Conservation of Familiarity was a driving force for the evolution of the API.
+These facts support that the law of Conservation of Familiarity played an important part in the evolution of the API.
 
@@
 This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects.
-Based on these factors and clearly expressed ambitions, we conclude that the law of Feedback System was a driving force for the evolution of the API.
+Based on these factors and clearly expressed ambitions, we conclude that the law of Feedback System was of significant important during the evolution of the API.
 
@@
 These changes were deemed the most significant by the interviewee, and it was expressed during the interview that the these types of changes were the main driving factor of the development of the new version.
-On the contrary, three out of five changes which were unrelated to functionality were correctly predicted.
-The two changes which were not predicted correctly were inaccurate because the main type was confused with the secondary type.
+Contrary to this, three out of five changes which were unrelated to functionality were accurately predicted.
+The two changes which were not predicted accurately were inaccurate because the main type was confused with the secondary type.
 This shows that, although the prediction was incorrect, the general reasoning was correct.
-The changes which had no secondary type were all predicted correctly, which further shows that changes with several types can be diffuse.
+The changes which had no secondary type were all predicted accurately, which further shows that changes with several types can be diffuse.
 
@@
 
-Our results show that the major driving force for change the case company's API is the call for increased functionality.
+Our results show that the major driving force for change in the case company's API was the call for increased functionality.
 The classification of the types of software evolution and software maintenance showed that enhancive changes which either aimed to add modules or new functionality to existing modules were the most common.
@@
 In the law of Continuing Change, Lehman concludes that ``an E-type system must be continually adapted or it becomes progressively less satisfactory".
-The results of our work supports this view, as the changes did not only add functionality, but it was also found that the application developers most major concern were updates to functionality.
+The results of our work support this view, as the changes did not only add functionality, but it was also found that the application developers most major concern were updates to functionality.
 
@@
 
-Our results found that seven out of eight of Lehman's laws do apply to the evolution of the studied API.
-The law of Conservation of Organisational Stability was found not to apply, since changes to APIs are unfavourable due to the potential disruption the applications using the API could face.
+Our results found that seven out of eight of Lehman's laws affected the evolution of the studied API.
+The law of Conservation of Organisational Stability was found to have less significance, since changes to APIs are unfavourable due to the potential disruption the applications using the API could face.
 This inertia to change in API evolution is supported by other research, which also conclude that the negative effect that changes to APIs may have is a major factor to be considered \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}.
 
-Based on our results, we form the conclusion that the desire for functionality and the reluctance of changing are two opposing forces that cause updates to this API to be infrequent.
-In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which is the main indication that the law of Conservation of Organisational Stability is not applicable to APIs.
+Based on our results, we form the conclusion that the desire for functionality and the reluctance of changing are two opposing forces that caused updates to this API to be infrequent.
+In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which is the main indication that the law of Conservation of Organisational Stability is less significant for this API.
 This occurrence has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}.
-The underlying reason for this is that the laws are influenced by conscious thought processes, based on human understanding \cite{lehman1980understanding}, which in the case of APIs is the conscious decision to limit updates as much as possible.
+The underlying reason for this is that the laws are influenced by conscious thought processes, based on human understanding \cite{lehman1980understanding}, which, in the case of this API, is the conscious decision to limit updates as much as possible.
 
@@
 We conclude that we were able to reverse engineer the change decisions to a large extent.
-This is clear from the results, which showed that 85\% of the changes were reverse engineered correctly.
+This is clear from the results, which showed that 85\% of the changes were reverse engineered accurately.
 The kappa value of 0.812 further supports this.
@@
 Considering that we were able to successfully reverse engineer the changes made to the API in this study, it opens up possibilities to base future research on, for example, the types of software evolution and software maintenance.
-Since the kappa analysis showed that there was a high level of agreement between our predictions and the actual motives to the change, it shows that the types of software evolution and software maintenance could even be used as a base for a large-scale quantitative analysis to map the types of changes made to APIs.
+Since the kappa analysis showed that there was a high level of agreement between our predictions and the actual motives to the change, it shows that the types of software evolution and software maintenance could even be used as the basis for a large-scale quantitative analysis to map the types of changes made to APIs.
 
-By analysing the API based on Lehman's laws, we were able to find that the law of Conservation of Organisational Stability did not apply to the API examined in this study.
-Our results suggest that the opposite of what the law suggests, in its current form, is more applicable for APIs.
+By analysing the API based on Lehman's laws, we were able to find that the law of Conservation of Organisational Stability had little impact upon the API investigated in this study.
+Our results show that the opposite of what the law suggests, in its current form, is true for this API.
 However, since only a single API was studied, we cannot generalise this finding for all APIs.
@@
 With our study we identified both that the law of Feedback System is of great importance to company A and that it is one of the key areas of API development that company A wishes to improve.
-One challenge of the challenges posed by software evolution is that the activities carried out are often intangible and non-objective \cite{chapin2001types, lientz1980software}.
+One of the challenges posed by software evolution is that the activities carried out are often intangible and non-objective \cite{chapin2001types, lientz1980software}.
 Based on this, we propose that our study which has granulated the activities is used as a basis for communicating the current stage of the evolution of their API.
@@
 It also concludes that this API did not change invariantly, and that its maintenance was infrequent and sporadic.
-This seems to indicate that the law of Conservation of Organisational Stability was not held in the evolution of this API.
+This seems to indicate that the law of Conservation of Organisational Stability did not play a significant role in the evolution of this API.
 However, given that this study was on performed on a single API, we cannot generalise this finding.
@@
 
-To further investigate what drives API evolution, we believe that API evolution has to be studied from a business point of view.
+To further investigate what drives API evolution, we believe that API evolution should be studied from a business point of view.
 We therefore suggest that a similar study is conducted, but with the goal of analysing the change of an API based on business motives.

### 2015-06-03 thesis/paper.tex
Reivew 2nd half

@@
 Preventive types of change appear to drive the evolution this API more strongly than other types of change.
-This could be due to the fact that as the API grows, the need for higher maintenance also increase, a fact that also seems to be supported by Lehman's laws.
+This could be due to the fact that as the API grows, the need for higher maintenance also increase, a fact that also is supported by Lehman's laws.
 
@@
 We therefore conclude that reformative changes, while important for the usability of the API, did not drive the evolution of the API.
+
+\newpage
 
@@
 
+\newpage
+
 \smallskip \noindent
@@
 This would aim to complement the current strategy which is largely based around the expertise and experiences of the API architects.
-Based on these factors and clearly expressed ambitions, we conclude that the law of Feedback System was of significant important during the evolution of the API.
+Based on these factors and clearly expressed ambitions, we conclude that the law of Feedback System was of significant importance during the evolution of the API.
 
@@
 However, since only a single API was studied, we cannot generalise this finding for all APIs.
-Research should therefore be wary of assuming that this law is true for APIs and future work could be undertaken to fully determine it's validity in regards to APIs.
+Research should therefore be wary of assuming that this law is true for APIs and future work could be undertaken to fully determine its validity in regards to APIs.
 
@@
 Our study shows that functionality is the largest driving force of change in the evolution of the studied API.
-It also concludes that this API did not change invariantly, and that its maintenance was infrequent and sporadic.
-This seems to indicate that the law of Conservation of Organisational Stability did not play a significant role in the evolution of this API.
+It also suggests that changes to APIs occur infrequently and sporadically.
+This indicates that the law of Conservation of Organisational Stability did not play a significant role in the evolution of this API.
 However, given that this study was on performed on a single API, we cannot generalise this finding.

### 2015-06-03 thesis/paper.tex
Further minor changes

@@
 Between the release of v1.0 and v1.4, no functionality was added, as it only added additional build options for other hardware platforms.
-Prior to v1.4 being released, updates were only made to include additional build options and did not include any additional functionality.
 The API is used by company partners, which are other companies developing applications for the cameras.
@@
 \subsubsection{APIs as Systems}
-The API is rather complex, and in addition to the API interface and implementation code, it includes a middle-layer which manages error handling and the access to various 3\textsuperscript{rd} party libraries.
+Company A's API is rather complex, and in addition to the API interface and implementation code, it includes a middle-layer which manages error handling and the access to various 3\textsuperscript{rd} party libraries.
 In this study, we use the API interface and the middle-layers as units of analysis.
-Examples of where the responsibilites exceed those of a primitive API interface is that it includes functionality such as error handling and a daemon which facilitates communication between hardware entities.
-In addition to that, the SDK which includes the API documentation, user manuals and example applications that utilise the API code.
+Examples of where the responsibilities exceed those of a primitive API interface is that it includes functionality such as error handling and a daemon which facilitates communication between hardware entities.
+In addition to that is an SDK which includes the API documentation, user manuals and example applications that utilise the API code.
 Based on these characteristics and the IEEE definition of a system, which reads as follows; ``A combination of interacting elements organised to achieve one or more stated purposes...Organised to accomplish a specific function or set of functions within a specific environment" \cite{5733835 }, we consider the API to be a system because of the combination of the interacting parts of the API, coupled with the specific nature of the problem the API is addressing.
@@
 This is evident from that it is a vital part of the cameras' and the only option for developing software for the cameras.
-The API is also by company A considered to be a vital part of the cameras' software ecosystem.
-This factor also corresponds with the characteristic of E-type systems which relates to the system being susceptible to change from pressure that occurs after the system has been deployed.
-Similarly, we do not consider the API to be a P-type system, based on that the system is virtually impossible to model because of its high dependenace with the environment it operates in.
+The API is also considered by company A to be a vital part of the cameras' software ecosystem.
+This factor corresponds with the characteristic of E-type systems which relates to the system being susceptible to change from pressure that occurs after the system has been deployed.
+Similarly, we do not consider the API to be a P-type system, based on the fact that the system is virtually impossible to model due to its high dependence on the environment in which it operates in.
 
@@
 With regards to Lehman's laws of software evolution, the laws are said to only apply to E-type systems.
-According to our analysis, we consider the API to be of the E-type, but our interpretations of Lehman's definitions are incorrect, it could be considered a threat to the construct of our study.
+According to our analysis, we consider the API to be of the E-type, but if our interpretations of Lehman's definitions are incorrect, it could be considered a threat to the construct validity of our study.
 
@@
 This has contributed to triangulating the results and discovering possible inconsistencies.
-Further triangulation of the results was performed by interviewing the API architect.
+Further triangulation of the results was performed by interviewing an architect of the API.
 Business-related factors might have had an impact on the evolution of the API, and these were not closely investigated.
@@
 \textbf{External validity  } Since only two versions of the API were analysed, we cannot claim any generalisability for our study.
-We do, however, believe that our study can offer comparability for companies that chose to do a similar analysis on their API.
+We do, however, believe that our study can offer comparability for companies that chose to do a similar analysis on their own APIs.
 
@@
 Such additions include added functionality to allow mechanical and digital control of the camera, to utilise additional storage devices, to allow serial connectivity and to allow audio analysis on the cameras.
-Changes that were pure additions the API were not attributed with any secondary types of change.
+Changes that were pure additions to the API were not attributed with any secondary types of change.
 
 Many of the changes were deprecations that were later re-implemented as new modules.
-Changes of these kinds were grouped into a single type instead of two.
+Changes of this kind were grouped into a single type instead of two.
 Such examples include the deprecation and re-implementation of an event system, dynamic web page generation and configuration utilities.
@@
 The results show that certain types of change are more prevalent than others, these results are shown in Table \ref{table:type_counts}.
-Analysis of the results showed that enhancive changes were the primary types of change that drive API evolution and that they act as a catalyst for many of the other changes in the API.
-Updative changes were found to be consequences of enhancive changes, rather than being drivers of evolution.
-Supporting the users of the API through the combination of preventive and groomative types of change, together formed another strong driver of API evolution.
+Analysis of the results showed that enhancive changes were the primary types of change that drove the evolution of this API and that they acted as a catalyst for many of the other changes in the API.
+Updative changes were found to be consequences of enhancive changes, rather than being drivers of evolution themselves.
+Supporting the users of the API through the combination of preventive and groomative types of change, together formed another strong driver of the API's evolution.
 Reductive and adaptive changes, while important, did not strongly drive the evolution of the API.

### 2015-06-04 thesis/paper.tex
widows+orphans
Fixed broken reference

@@
 In addition to that is an SDK which includes the API documentation, user manuals and example applications that utilise the API code.
-Based on these characteristics and the IEEE definition of a system, which reads as follows; ``A combination of interacting elements organised to achieve one or more stated purposes...Organised to accomplish a specific function or set of functions within a specific environment" \cite{5733835 }, we consider the API to be a system because of the combination of the interacting parts of the API, coupled with the specific nature of the problem the API is addressing.
+Based on these characteristics and the IEEE definition of a system, which reads as follows; ``A combination of interacting elements organised to achieve one or more stated purposes...Organised to accomplish a specific function or set of functions within a specific environment" \cite{5733835}, we consider the API to be a system because of the combination of the interacting parts of the API, coupled with the specific nature of the problem the API is addressing.
 
@@
 
-\newpage
-
 %Lehman Intro
@@
 As this was the only reductive change found, we conclude that the evolution of the API was not primarily driven by reductive changes.
+
+\newpage
 
@@
 We therefore conclude that reformative changes, while important for the usability of the API, did not drive the evolution of the API.
-
-\newpage
 
@@
 We therefore settle that the law of Declining Quality was a driving force for the evolution of the API.
-
-\newpage
 

### 2015-06-04 thesis/paper.tex
Reverted author blocks
Removed Acknowledgements
Also added capitals to reference in the bib

@@
 \alignauthor
-John Burchell\\
+John Burchell and William Granli\\
        \affaddr{Computer Science and Engineering}\\
        \affaddr{University of Gothenburg}\\
-       \email{john.a.burchell@gmail.com}
+       \email{john.a.burchell@gmail.com},  \email{william.granli@gmail.com}
 % 2nd. author
-\alignauthor
-William Granli\\
+%\alignauthor
+%William Granli\\
+%       \affaddr{Computer Science and Engineering}\\
+%       \affaddr{University of Gothenburg}\\
+%       \email{william.granli@gmail.com}
+%\and
+% 3rd. author
+\alignauthor Imed Hammouda and Eric Knauss\\
 \affaddr{Computer Science and Engineering}\\
-       \affaddr{University of Gothenburg}\\
-       \email{william.granli@gmail.com}
+\affaddr{Chalmers $\mid$ University of Gothenburg}\\
+\email{\{imed.hammouda,eric.knauss\}@cse.gu.se}
+% 4th 
+%\alignauthor Eric Knauss\titlenote{Co-author}\\
+%       \affaddr{Computer Science and Engineering}\\
+%       \affaddr{University of Gothenburg}\\
+%       \email{imed.hammouda@gu.se}
 }
@@
 
-\section*{Acknowledgements}
-We would like to thank company A for allowing us to conduct this study in cooperation with them. We would also like to thank associate professor Imed Hammouda for assisting us with this research.
-
 \bibliographystyle{abbrv}

### 2015-07-13 thesis/paper.tex
Camera Ready
1. Changes based on feedback from reviewers

2. Switched order of authors (john+william)

@@
 \alignauthor
-John Burchell and William Granli\\
+William Granli and John Burchell\\
        \affaddr{Computer Science and Engineering}\\
        \affaddr{University of Gothenburg}\\
-       \email{john.a.burchell@gmail.com},  \email{william.granli@gmail.com}
+       \email{william.granli@gmail.com},  \email{john.a.burchell@gmail.com}
 % 2nd. author
@@
 %Motivation
-Evolving an Application Programming Interface (API) is a precipitous activity, as modifications to them can significantly impact their users.
+Evolving an Application Programming Interface (API) is a delicate activity, as modifications to them can significantly impact their users.
 The increasing use of APIs means that software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs.
@@
 %Method
-In this case study, we conduct a qualitative investigation to understand what drives the evolution of an industry company's existing API, by examining two versions of the API code.
+In this case study, we conduct a qualitative investigation to understand what drives the evolution of an industry company's existing API, by examining two versions of the API interface.
 The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions was determined by interviewing an architect of the API.
@@
 It is therefore important to investigate why these changes occur.
-Understanding the motives behind the changes could help API architects to prevent potential future changes to their APIs.
+Understanding the motives behind the \newline changes could help API architects to prevent potential future changes to their APIs.
 Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.
@@
 %Gap in Literature
-Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and affects of modifications to APIs \cite{dig2005role, hou2011exploring, shi2011empirical}.
+Previous studies have investigated programming language APIs, libraries or frameworks focusing on causes and effects of modifications to APIs \cite{dig2005role, hou2011exploring, shi2011empirical}.
 However, to the best of our knowledge, no studies have been performed on embedded platform APIs from a software evolution perspective.
@@
               \textbf{Type}                              & \textbf{Explanation}    \\ \midrule
+              Enhancive     & Inclusion of new functionality                 \\ \hline
               Corrective    & Corrections of functionality                   \\ \hline
               Reductive     & Reductions of functionality                    \\ \hline
-              Adaptive      & Inclusion of new Technology                    \\ \hline
-              Performance   & Improvements to Performance                    \\ \hline
+              Adaptive      & Inclusion of new technology                    \\ \hline
+              Performance   & Improvements to performance                    \\ \hline
               Preventive    & Improvements to future maintainability         \\ \hline
@@
        \begin{tabular}[ht]{p{3in}}
-       \toprule
+
               \begin{enumerate}
@@
               \end{enumerate} \\
-              \bottomrule
+
        \end{tabular}
@@
 The case company of this study will from here on be referred to as \textit{company A}.
-Company A operates in the domain of video surveillance.
-The company's headquarters is located in Lund, Sweden, with offices in 49 countries worldwide.
+Company A operates in the domain of video surveillance and has offices in 49 countries worldwide.
 Company A is the global market leader in the markets of network cameras and video encoders.
@@
 \section{Methodology} \label{methodology}
-This study has been conducted using the case study methodology \cite{runeson2009guidelines}.
-Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have been used as units of analysis.
+This study has been conducted using the case study meth-odology \cite{runeson2009guidelines}.
+Our research can be classified as an embedded case study \cite{yin2013case}, since both the API interface and API documentation have been used as units of analysis.
 The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context.
@@
 The aim of the first phase was to generate hypotheses and to formulate clear research questions.
-This was achieved by using a data-driven approach to analysing the code and documentation.
+This was achieved by using a data-driven approach to analysing the interface code and documentation.
 The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phase.
@@
 %How the initial inspection was performed
-The API code was inspected sequentially, starting with v1.4.
+The API interface code was inspected sequentially, starting with v1.4.
 Both versions of the API underwent the same type of inspection.
@@
 %Codes
-To analyse the data, each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
+To analyse the data, each change identified in the spreadsheet was coded based on which module the change occurred in and based on if the change added, removed, modified or did not affect functionality.
 %Concepts
@@
 %Categories
-These concepts were then grouped into categories based on common patterns between the concepts.
+These concepts were then grouped into categories which were based on common patterns between the concepts.
+An example of a pattern found during the analysis was that several concepts followed the pattern of adding new functionality.
 %Theory
@@
 %RQ1
-The trends identified previously were then classified with help of the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}.
+The trends identified previously were then classified with the help of the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}.
 Each of the previously identified trends were given a main type of change and, if appropriate, a secondary type.
@@
 %Define
-Updative changes are defined to be changes to documentation of a system.
+Updative changes are defined to be changes to documentation of a system that are made to conform with changes in the code. 
 %Data and example
@@
 %Define
-Reformative changes are defined to be changes that update the documentation to the stakeholders needs.
+Reformative changes are defined to be \newline changes that update the documentation to the stakeholders needs. An example of such a change is that the structure of the documentation is changed. 
 %Data and Example
@@
 All functionality which was added or modified in v2.0 was updated accordingly in the documentation.
-The same pattern can be seen for the example code, which went through major changes as a result of the changes to the API code.
+The same pattern can be seen for the example code, which went through major changes as a result of the changes to the API interface.
 Company A's intent to control the way that their API is used also suggests that the knowledge of how to use the API is of importance, since if the API is used in too many different ways, it will be more difficult for company A to have relevant documentation and example code.
@@
 \textbf{Declining Quality  } 
-The interviews established that a groomative motive was not the primary reason for implementing any change.
+The interviews established that a groo-mative motive was not the primary reason for implementing any change.
 The changes to the example code and the documentation, as well as the re-designed modules are examples of these, where the main motive behind the change was to either prevent unwanted usage or to increase the functional content.
@@
 
-\subsection{Reverse Engineering API Change Decisions}
+\subsection{Reverse Engineering Change Decisions}
 After cross-examining our initial analysis with the interviewee's responses, we found that 85\% of our main type predictions matched the actual motive of the change and that 85\% of our secondary type predictions were correct.
@@
 
+\newpage
+
 Our results found that seven out of eight of Lehman's laws affected the evolution of the studied API.
@@
 Considering that we were able to successfully reverse engineer the changes made to the API in this study, it opens up possibilities to base future research on, for example, the types of software evolution and software maintenance.
-Since the kappa analysis showed that there was a high level of agreement between our predictions and the actual motives to the change, it shows that the types of software evolution and software maintenance could even be used as the basis for a large-scale quantitative analysis to map the types of changes made to APIs.
+Since the kappa analysis showed that there was a high level of agreement between our classification and the actual motives to the change, it shows that the types of software evolution and software maintenance could even be used as the basis for a large-scale quantitative analysis to map the types of changes made to APIs.
 
@@
 
-One way of finding the solution to this problem would be by including the application developers in the feedback loop.
+One way of finding the solution to this problem would be by in a more structured way including the application developers in the feedback loop.
 Since the application developers are on the receiving end of the changes, we believe that their needs have to be assessed before the problem can be solved.
@@
 
-\section{Conclusion} \label{conclusion}
-With this study, we conclude that studying API evolution with help of existing theories, provides a new and structured approach to the field of API evolution.
+\section{Future Work} \label{conclusion}
+With this study, we conclude that studying API evolution with the help of existing theories, provides a new and structured approach to the field of API evolution.
 Our study shows that functionality is the largest driving force of change in the evolution of the studied API.
@@
 This indicates that the law of Conservation of Organisational Stability did not play a significant role in the evolution of this API.
-However, given that this study was on performed on a single API, we cannot generalise this finding.
+However, given that this study was only performed on a single API, we cannot generalise this finding.
 Furthermore, we have identified the importance of having a structured feedback loop when maintaining an API.
